### 2015-02-05 tuningpredictor.tex
init

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{Tuning Learners before Predicitting: New Reflection in Defect Prediction }

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

%\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{ A, B, C
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
%\alignauthor
%Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{1932 Wallamaloo Lane}\\
%       \affaddr{Wallamaloo, New Zealand}\\
%       \email{trovato@corporation.com}
%% 2nd. author
%\alignauthor
%G.K.M. Tobin\titlenote{The secretary disavows
%any knowledge of this author's actions.}\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{P.O. Box 1212}\\
%       \affaddr{Dublin, Ohio 43017-6221}\\
%       \email{webmaster@marysville-ohio.com}
%% 3rd. author
%\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
%one who did all the really hard work.}\\
%       \affaddr{The Th{\o}rv{\"a}ld Group}\\
%       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
%       \affaddr{Hekla, Iceland}\\
%       \email{larst@affiliation.org}
%\and  % use '\and' if you need 'another row' of author names
%% 4th. author
%\alignauthor Lawrence P. Leipuner\\
%       \affaddr{Brookhaven Laboratories}\\
%       \affaddr{Brookhaven National Lab}\\
%       \affaddr{P.O. Box 5000}\\
%       \email{lleipuner@researchlabs.org}
%% 5th. author
%\alignauthor Sean Fogarty\\
%       \affaddr{NASA Ames Research Center}\\
%       \affaddr{Moffett Field}\\
%       \affaddr{California 94035}\\
%       \email{fogartys@amesres.org}
%% 6th. author
%\alignauthor Charles Palmer\\
%       \affaddr{Palmer Research Laboratories}\\
%       \affaddr{8600 Datapoint Drive}\\
%       \affaddr{San Antonio, Texas 78229}\\
%       \email{cpalmer@prl.com}
%}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.
}
\maketitle
\begin{abstract}
Data mining techniques have been widely applied to software defect prediction with various 
empirical data sets. Those proposed leaners are always evaluated against the state of the art 
predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
accuracy indicators, the newer predictors outperform counterparts in selected experimental 
settings. However,  most of data mining algorithm based predictors (e.g. CART, random forest, 
neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
forest algorithm. the impact of internal parameters in those methods have been neglected 
during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
predictors with search-based software engineering algorithm. Specifically, we used differential 
evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
and then predictors with optimal parameters obtained from tuning preocess will be applied to 
predict defects. By comparing the performance of predictors with and without tuning process,  
we observe that tuning improves the predictors' performance and predictors woking with 
different data sets need different parameters. Our results also suggest that we should not use 
the predictors of the shelf with their default parameters and tuning should be a processor 
combined with any predictor with built-in parameters.

%RQ1: Does tuning affect learners' performance?
%RQ2: How to choose

\end{abstract}

% A category with the (minimum) three required fields
\category{D.2.9}{Software Engineering}{Management}[Cost estimation]

\terms{Experimentation, Algorithm}

\keywords{Defect prediction, Data Mining, Tuning Parameters, CART, WHERE} % NOT 
required for Proceedings

\section{Introduction}

Software has becoming a large and complex system and delivering reliable and quality 
software is imperative for development teams. Empirical study shows that the longer the 
defects exist in software systems, the more the cost of time and money it will take to fix it 
\textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
defects in their system as early as possible. Defect prediction has been investigated extensively in industrial and academia during the past two decades. As an important research field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} over static code features of software system has been demonstrated to be a way to predict which models are more likely to contain defects.

Classification is an important approach to predict whether some modules in the projects are defective or non-defective. The general idea is to train the learners by using parts of data sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed based an different data mining classifier, including

What's the problem in those result?

RQ:

briefly describe our study and  our result; observation

structure of this paper.

\section{Learner and Tuner}

Description of WHERE-based predictor

brief description of CART, Randforest (????)

Description of DE

\section{Experiment}

Description of Data set

Experiment 1: naive where vs tuned where

Experiment 2: naive cart vs tuned cart vs random forest

\section{Discussion}

\section{Related Work}

Tuning in efforts estimation, software engineering.

Defect Prediction

\section{Threats to Validity}

Internal and external threats

\section{Conclusion}
%The \textit{proceedings} are the records of a conference.
%ACM seeks to give these conference by-products a uniform,
%high-quality appearance.  To do this, ACM has some rigid
%requirements for the format of the proceedings documents: there
%is a specified format (balanced  double columns), a specified
%set of fonts (Arial or Helvetica and Times Roman) in
%certain specified sizes (for instance, 9 point for body copy),
%a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
%the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
%and (1.9 cm [.75"]) left and right; specified column width
%(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
%
%The good news is, with only a handful of manual
%settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
%and {\texttt{\char'134 alignauthor}} commands, you have
%already used; another, {\texttt{\char'134 balancecolumns}}, will
%be used in your very last run of \LaTeX\ to ensure
%balanced column heights on the last page.}, the \LaTeX\ document
%class file handles all of this for you.
%
%The remainder of this document is concerned with showing, in
%the context of an ``actual'' document, the \LaTeX\ commands
%specifically available for denoting the structure of a
%proceedings paper, rather than with giving rigorous descriptions
%or explanations of such commands.
%
%\section{The {\secit Body} of The Paper}
%Typically, the body of a paper is organized
%into a hierarchical structure, with numbered or unnumbered
%headings for sections, subsections, sub-subsections, and even
%smaller sections.  The command \texttt{{\char'134}section} that
%precedes this paragraph is part of such a
%hierarchy.\footnote{This is the second footnote.  It
%starts a series of three footnotes that add nothing
%informational, but just give an idea of how footnotes work
%and look. It is a wordy one, just so you see
%how a longish one plays out.} \LaTeX\ handles the numbering
%and placement of these headings for you, when you use
%the appropriate heading commands around the titles
%of the headings.  If you want a sub-subsection or
%smaller part to be unnumbered in your output, simply append an
%asterisk to the command name.  Examples of both
%numbered and unnumbered headings will appear throughout the
%balance of this sample document.
%
%Because the entire article is contained in
%the \textbf{document} environment, you can indicate the
%start of a new paragraph with a blank line in your
%input file; that is why this sentence forms a separate paragraph.
%
%\subsection{Type Changes and {\subsecit Special} Characters}
%We have already seen several typeface changes in this sample.  You
%can indicate italicized words or phrases in your text with
%the command \texttt{{\char'134}textit}; emboldening with the
%command \texttt{{\char'134}textbf}
%and typewriter-style (for instance, for computer code) with
%\texttt{{\char'134}texttt}.  But remember, you do not
%have to indicate typestyle changes when such changes are
%part of the \textit{structural} elements of your
%article; for instance, the heading of this subsection will
%be in a sans serif\footnote{A third footnote, here.
%Let's make this a rather short one to
%see how it looks.} typeface, but that is handled by the
%document class file. Take care with the use
%of\footnote{A fourth, and last, footnote.}
%the curly braces in typeface changes; they mark
%the beginning and end of
%the text that is to be in the different typeface.
%
%You can use whatever symbols, accented characters, or
%non-English characters you need anywhere in your document;
%you can find a complete list of what is
%available in the \textit{\LaTeX\
%User's Guide}\cite{Lamport:LaTeX}.
%
%\subsection{Math Equations}
%You may want to display math equations in three distinct styles:
%inline, numbered or non-numbered display.  Each of
%the three are discussed in the next sections.
%
%\subsubsection{Inline (In-text) Equations}
%A formula that appears in the running text is called an
%inline or in-text formula.  It is produced by the
%\textbf{math} environment, which can be
%invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
%construction or with the short form \texttt{\$. . .\$}. You
%can use any of the symbols and structures,
%from $\alpha$ to $\omega$, available in
%\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
%few examples of in-text equations in context. Notice how
%this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
%set here in in-line math style, looks slightly different when
%set in display style.  (See next section).
%
%\subsubsection{Display Equations}
%A numbered display equation -- one set off by vertical space
%from the text and centered horizontally -- is produced
%by the \textbf{equation} environment. An unnumbered display
%equation is produced by the \textbf{displaymath} environment.
%
%Again, in either environment, you can use any of the symbols
%and structures available in \LaTeX; this section will just
%give a couple of examples of display equations in context.
%First, consider the equation, shown as an inline equation above:
%\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
%Notice how it is formatted somewhat differently in
%the \textbf{displaymath}
%environment.  Now, we'll enter an unnumbered equation:
%\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
%and follow it with another numbered equation:
%\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
%just to demonstrate \LaTeX's able handling of numbering.
%
%\subsection{Citations}
%Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
%conference
%proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
%in the Bibliography section of your
%article will occur throughout the text of your article.
%You should use BibTeX to automatically produce this bibliography;
%you simply need to insert one of several citation commands with
%a key of the item cited in the proper location in
%the \texttt{.tex} file \cite{Lamport:LaTeX}.
%The key is a short reference you invent to uniquely
%identify each work; in this sample document, the key is
%the first author's surname and a
%word from the title.  This identifying key is included
%with each item in the \texttt{.bib} file for your article.
%
%The details of the construction of the \texttt{.bib} file
%are beyond the scope of this sample document, but more
%information can be found in the \textit{Author's Guide},
%and exhaustive details in the \textit{\LaTeX\ User's
%Guide}\cite{Lamport:LaTeX}.
%
%This article shows only the plainest form
%of the citation command, using \texttt{{\char'134}cite}.
%This is what is stipulated in the SIGS style specifications.
%No other citation format is endorsed.
%
%\subsection{Tables}
%Because tables cannot be split across pages, the best
%placement for them is typically the top of the page
%nearest their initial cite.  To
%ensure this proper ``floating'' placement of tables, use the
%environment \textbf{table} to enclose the table's contents and
%the table caption.  The contents of the table itself must go
%in the \textbf{tabular} environment, to
%be aligned properly in rows and columns, with the desired
%horizontal and vertical rules.  Again, detailed instructions
%on \textbf{tabular} material
%is found in the \textit{\LaTeX\ User's Guide}.
%
%Immediately following this sentence is the point at which
%Table 1 is included in the input file; compare the
%placement of the table here with the table in the printed
%dvi output of this document.
%
%\begin{table}
%\centering
%\caption{Frequency of Special Characters}
%\begin{tabular}{|c|c|l|} \hline
%Non-English or Math&Frequency&Comments\\ \hline
%\O & 1 in 1,000& For Swedish names\\ \hline
%$\pi$ & 1 in 5& Common in math\\ \hline
%\$ & 4 in 5 & Used in business\\ \hline
%$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
%\hline\end{tabular}
%\end{table}
%
%To set a wider table, which takes up the whole width of
%the page's live area, use the environment
%\textbf{table*} to enclose the table's contents and
%the table caption.  As with a single-column table, this wide
%table will ``float" to a location deemed more desirable.
%Immediately following this sentence is the point at which
%Table 2 is included in the input file; again, it is
%instructive to compare the placement of the
%table here with the table in the printed dvi
%output of this document.
%
%
%\begin{table*}
%\centering
%\caption{Some Typical Commands}
%\begin{tabular}{|c|c|l|} \hline
%Command&A Number&Comments\\ \hline
%\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
%\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
%\texttt{{\char'134}table}& 300 & For tables\\ \hline
%\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
%\end{table*}
%% end the environment with {table*}, NOTE not {table}!
%
%\subsection{Figures}
%Like tables, figures cannot be split across pages; the
%best placement for them
%is typically the top or the bottom of the page nearest
%their initial cite.  To ensure this proper ``floating'' placement
%of figures, use the environment
%\textbf{figure} to enclose the figure and its caption.
%
%This sample document contains examples of \textbf{.eps}
%and \textbf{.ps} files to be displayable with \LaTeX.  More
%details on each of these is found in the \textit{Author's Guide}.
%
%\begin{figure}
%\centering
%\epsfig{file=fly.eps}
%\caption{A sample black and white graphic (.eps format).}
%\end{figure}
%
%\begin{figure}
%\centering
%\epsfig{file=fly.eps, height=1in, width=1in}
%\caption{A sample black and white graphic (.eps format)
%that has been resized with the \texttt{epsfig} command.}
%\end{figure}
%
%
%As was the case with tables, you may want a figure
%that spans two columns.  To do this, and still to
%ensure proper ``floating'' placement of tables, use the environment
%\textbf{figure*} to enclose the figure and its caption.
%
%Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
%used; use
%the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
%commands as appropriate for the different file types.
%
%\subsection{Theorem-like Constructs}
%Other common constructs that may occur in your article are
%the forms for logical constructs like theorems, axioms,
%corollaries and proofs.  There are
%two forms, one produced by the
%command \texttt{{\char'134}newtheorem} and the
%other by the command \texttt{{\char'134}newdef}; perhaps
%the clearest and easiest way to distinguish them is
%to compare the two in the output of this sample document:
%
%This uses the \textbf{theorem} environment, created by
%the\linebreak\texttt{{\char'134}newtheorem} command:
%\newtheorem{theorem}{Theorem}
%\begin{theorem}
%Let $f$ be continuous on $[a,b]$.  If $G$ is
%an antiderivative for $f$ on $[a,b]$, then
%\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
%\end{theorem}
%
%The other uses the \textbf{definition} environment, created
%by the \texttt{{\char'134}newdef} command:
%\newdef{definition}{Definition}
%\begin{definition}
%If $z$ is irrational, then by $e^z$ we mean the
%unique number which has
%logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
%\end{definition}
%
%\begin{figure}
%\centering
%\psfig{file=rosette.ps, height=1in, width=1in,}
%\caption{A sample black and white graphic (.ps format) that has
%been resized with the \texttt{psfig} command.}
%\end{figure}
%
%Two lists of constructs that use one of these
%forms is given in the
%\textit{Author's  Guidelines}.
%
%\begin{figure*}
%\centering
%\epsfig{file=flies.eps}
%\caption{A sample black and white graphic (.eps format)
%that needs to span two columns of text.}
%\end{figure*}
%and don't forget to end the environment with
%{figure*}, not {figure}!
% 
%There is one other similar construct environment, which is
%already set up
%for you; i.e. you must \textit{not} use
%a \texttt{{\char'134}newdef} command to
%create it: the \textbf{proof} environment.  Here
%is a example of its use:
%\begin{proof}
%Suppose on the contrary there exists a real number $L$ such that
%\begin{displaymath}
%\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
%\end{displaymath}
%Then
%\begin{displaymath}
%l=\lim_{x\rightarrow c} f(x)
%= \lim_{x\rightarrow c}
%\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
%= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
%\frac{f(x)}{g(x)} = 0\cdot L = 0,
%\end{displaymath}
%which contradicts our assumption that $l\neq 0$.
%\end{proof}
%
%Complete rules about using these environments and using the
%two different creation commands are in the
%\textit{Author's Guide}; please consult it for more
%detailed instructions.  If you need to use another construct,
%not listed therein, which you want to have the same
%formatting as the Theorem
%or the Definition\cite{salas:calculus} shown above,
%use the \texttt{{\char'134}newtheorem} or the
%\texttt{{\char'134}newdef} command,
%respectively, to create it.
%
%\subsection*{A {\secit Caveat} for the \TeX\ Expert}
%Because you have just been given permission to
%use the \texttt{{\char'134}newdef} command to create a
%new form, you might think you can
%use \TeX's \texttt{{\char'134}def} to create a
%new command: \textit{Please refrain from doing this!}
%Remember that your \LaTeX\ source code is primarily intended
%to create camera-ready copy, but may be converted
%to other forms -- e.g. HTML. If you inadvertently omit
%some or all of the \texttt{{\char'134}def}s recompilation will
%be, to say the least, problematic.
%
%\section{Conclusions}
%This paragraph will end the body of this sample document.
%Remember that you might still have Acknowledgments or
%Appendices; brief samples of these
%follow.  There is still the Bibliography to deal with; and
%we will make a disclaimer about that here: with the exception
%of the reference to the \LaTeX\ book, the citations in
%this paper are to articles which have nothing to
%do with the present subject and are used as
%examples only.
%%\end{document}  % This is where a 'short' article might terminate
%
%%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
%This section is optional; it is a location for you
%to acknowledge grants, funding, editing assistance and
%what have you.  In the present case, for example, the
%authors would like to thank Gerald Murray of ACM for
%his help in codifying this \textit{Author's Guide}
%and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{unsrt}
\bibliography{tuningpredictor}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
%%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%% This next section command marks the start of
%% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The acm\_proc\_article-sp document class file itself is chock-full of succinct
%and helpful comments.  If you consider yourself a moderately
%experienced to expert user of \LaTeX, you may find reading
%it useful but please remember not to change it.
%\balancecolumns
% That's all folks!
\end{document}

### 2015-02-12 tuningpredictor.tex
update

@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{acm_proc_article-sp}
+\usepackage{multirow}
+\usepackage{color}
+\usepackage{colortbl}
+\usepackage{picture}
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+\newcommand{\quart}[3]{\begin{picture}(100,6)%1
+{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
 
 \begin{document}
-
-\title{Tuning Learners before Predicitting: New Reflection in Defect Prediction }
-
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-%\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{ A, B, C
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-%\alignauthor
-%Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-%       \affaddr{Institute for Clarity in Documentation}\\
-%       \affaddr{1932 Wallamaloo Lane}\\
-%       \affaddr{Wallamaloo, New Zealand}\\
-%       \email{trovato@corporation.com}
-%% 2nd. author
-%\alignauthor
-%G.K.M. Tobin\titlenote{The secretary disavows
-%any knowledge of this author's actions.}\\
-%       \affaddr{Institute for Clarity in Documentation}\\
-%       \affaddr{P.O. Box 1212}\\
-%       \affaddr{Dublin, Ohio 43017-6221}\\
-%       \email{webmaster@marysville-ohio.com}
-%% 3rd. author
-%\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-%one who did all the really hard work.}\\
-%       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-%       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-%       \affaddr{Hekla, Iceland}\\
-%       \email{larst@affiliation.org}
-%\and  % use '\and' if you need 'another row' of author names
-%% 4th. author
-%\alignauthor Lawrence P. Leipuner\\
-%       \affaddr{Brookhaven Laboratories}\\
-%       \affaddr{Brookhaven National Lab}\\
-%       \affaddr{P.O. Box 5000}\\
-%       \email{lleipuner@researchlabs.org}
-%% 5th. author
-%\alignauthor Sean Fogarty\\
-%       \affaddr{NASA Ames Research Center}\\
-%       \affaddr{Moffett Field}\\
-%       \affaddr{California 94035}\\
-%       \email{fogartys@amesres.org}
-%% 6th. author
-%\alignauthor Charles Palmer\\
-%       \affaddr{Palmer Research Laboratories}\\
-%       \affaddr{8600 Datapoint Drive}\\
-%       \affaddr{San Antonio, Texas 78229}\\
-%       \email{cpalmer@prl.com}
-%}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-%\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
-}
+\title{Tuning Learners before Applying: New Reflection in Defect Prediction }
+\author{ A, B, C}
 \maketitle
@@
 accuracy indicators, the newer predictors outperform counterparts in selected experimental 
-settings. However,  most of data mining algorithm based predictors (e.g. CART, random forest, 
+settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
+forest, 
 neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
@@
 evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
-and then predictors with optimal parameters obtained from tuning preocess will be applied to 
+and then predictors with optimal parameters obtained from tuning process will be applied to 
 predict defects. By comparing the performance of predictors with and without tuning process,  
@@
 
-\keywords{Defect prediction, Data Mining, Tuning Parameters, CART, WHERE} % NOT 
-required for Proceedings
+\keywords{Defect prediction, Data Mining, Tuning Parameters, CART, WHERE} 
+% NOT required for Proceedings
 
@@
 \textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
-defects in their system as early as possible.
-Defect prediction has been investigated extensively in industrial and academia during the past two decades.
-As an important research field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} over static code features of software system has been demonstrated to be a way to predict which models are more likely to contain defects.
+defects in their system as early as possible. Defect prediction has been investigated 
+extensively in industrial and academia during the past two decades. As an important research 
+field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, 
+menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} 
+over static code features of software system has been demonstrated to be a way to predict 
+which models are more likely to contain defects.
 
-Classification is an important approach to predict whether some modules in the projects are defective or non-defective.
-The general idea is to train the learners by using parts of data sets(e.g.
-ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with remaining ones(ant 1.5, 1.6 and 1.7).
-Many types of defect predictors have been proposed based an different data mining classifier, including
+Classification is an important approach to predict whether some modules in the projects are 
+defective or non-defective. The general idea is to train the learners by using parts of data 
+sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with 
+remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed 
+based an different data mining classifiers, including CART, Random Forest 
+\cite{guo2004robust},  Naive Bayes\cite{menzies2007data},Logistic Regression 
+\cite{khoshgoftaar1999logistic}. During the past years, authors claimed that their new 
+defective learner outperformed others according to their experiment and statistical analysis. 
+To evalute those learners objectively in terms of accuracy, Lessmann et al
+\cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
+domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
+with $\alpha = 0.05$, they concluded that the predictive accuracy of most learners didn't differ 
+significantly in terms of the area under the receiver operating characteristics curve(AUC). 
+Furthermore, according to the fig.2 in \cite{lessmann2008benchmarking}, Random Forest is 
+significantly better than CART. Lessmann's paper motivates us to investigate whether tuning 
+those CART's parameters by search-based software engineering method can improve the 
+performance. Even though Lessmann considered unpruned tree and pruned tree, They didn't 
+consider other possible parameters in CART which would have impact on the structure of 
+trees, like the depth of the tree, the maximum and minimum number of leafs of the tree.
+
+Software metrics are the core of all the defective prediction model. Many types of metics
+are used to build models, like process metrics, McCabe and Halsted metrics  and CK metrics.
+By building prediction modes across 85 releases of 12 open source projects, Rahman et al
+\cite{rahman2013how}  concluded that code metrics are generally less useful than process
+metrics for prediction. And also the code metrics don't change much from release to release
+and lead to stagnation in the prediction model. In \cite{Radjenovi?20131397}, Radjenovi? et al
+\cite{Radjenovi?20131397} reviewed 106 papers regarding software prediction metrics. They found
+that CK objected-oriented and process metrics have been reported to be more successful in
+finding defects compared to traditional size and complexity metrics. Moreover, not all the CK
+metrics perform well equally. The best metrics from CK are CBO, WMC and RFC based on their 
+observation. It seems that the relationship between software metrics and defective prediction is
+still an open question and need to be addressed. This motivates us to see : whether the impact
+rankings of those metrics will change after tuning parameters
+is applied to model learners.
 
@@
 
-\section{Learner and Tuner}
+\section{Algorithm: Predictor and Tuner}
 
-Description of WHERE-based predictor
+In order to conduct the experiment of this paper, we need one tool that can predict defects 
+from the empirical data sets and a second tool to tune the built-in parameters associated with 
+predictor. To compare the effects of the tuning process, we have three different predictors: 
+WHERE-based Predictor, CART and Random Forest. Different Evolution(DE) as an optimizer 
+is used as a tuner in this paper.
 
-brief description of CART, Randforest (????)
+We choose CART and Random Forest as a predictor in this paper is motivated by 
+\cite{lessmann2008benchmarking}, where the performance of both tools as predictors are 
+significantly different based on authors' experiment as mentioned before. We'd like to 
+investigate whether tuning can change such conclusion. WHERE-based Predictor is a new 
+defect predictor based on WHERE\cite{menzies2013local} algorithm. A comparison with 
+standard predictor like CART and Random Forest will better evaluate and judge the 
+performance such new predictor. As for the tuner, there're many heuristic optimization 
+algorithms in wild. However, DE is a good but maybe not the best candidate for the tuning 
+process considering different performance measurements. To determine which optimizer is 
+fitable and results in better performance is beyond this work scope. We leave it to future 
+works. The rest of this section will describe each tool applied in this work.
 
-Description of DE
+\subsection{WHERE-based Learner}
+\textbf{WHERE-based Learner} is composed of WHERE clustering algorithm and CART 
+decision tree algorithm. The key idea of WHERE-based learner is that  instead of training the 
+CART decision tree based on the class labels associated with each training sample, it's using 
+CART to build decision trees based on the cluster labels, which are generated by the WHERE 
+clustering algorithm.
+
+% Given N instances, instead of building decision tree directly with CART, we use WHERE to 
+%cluster instances. 
+WHERE is a fast clustering algorithm designed by {\it menzies} for finding software artifacts 
+with similar attributes. It clusters data on dimensions synthesized along the axis of greatest 
+variability in the data. The way WHERE used to find such dimension is a linear-time heuristic 
+called ``FASTMAP" proposed by Faloutsos \& Lin\cite{faloutsos1995fastmap}. ``FASTMAP" 
+randomly picks one instance Z; find the instance {\it east} X that's furthest away form Z; find 
+the instance {\it west} Y that's furthest away from {\it east} X. Next, project all the remaining 
+points onto the line drawn between X and Y. Then choose the median point as the split and 
+recursively divide all the instances into {\it west} and {\it east} clusters until the number of 
+instances within each cluster is less than specific minimum size. The representation of the 
+clustering result is a tree, we call it Where-clustering tree. Such tree will be pruned if applicable 
+in some cases. Finally, cluster labels  will be assigned to instances in each of those 
+clusters(leaves).
+
+Then based on the attributes and the cluster labels in each instances,  we build a 
+decision tree based on CART algorithm. In each leaf of the tree, there're several instances 
+falling in. This will be the model trained for defect prediction. During testing process, a new 
+instance comes in and traverses the tree according to 
+values of the its attributes. If the instance could reach one leaf of the tree, the predicted value 
+of this instance will be the mean  of all the training data values associated with this leaf. 
+Otherwise if stops at intermediate nodes of tree, the predicted value will be the mean of the all 
+the training data value below this node. After estimating all the number of defectives in the test 
+data, whether each instance contains defectives will be determined by comparing with a threshold value.
+If the predicted value is greater than threshold, the Where-based learner will predict this instance as defective otherwise non-defective.
+
+%\begin{algorithm}
+%	\caption{Pesudocode for WHERE Algorithm }
+%	\label{alg:WHERE}
+%		\begin{algorithmic}[1]
+%			\Require $data$
+%			\Ensure $tree$
+%		\Function {Fastmap}{$ data$}
+%			\State $one \gets$ any$(data)$
+%			\State $west \gets$ furthest$(data, one)$
+%			\State $east \gets$ furthest$(data, west)$
+%			\State $c \gets$ distance($west, east$)
+%		\EndFunction
+%	 \end{algorithmic}            
+%\end{algorithm}
+
+\subsection{CART}
+\textbf{CART} is an {\em iterative dichotomization} algorithm
+that finds the attribute that most divides the data such that
+the variance of the goal variable in each division is
+minimized\cite{breiman84}.
+The algorithm then recurses on each division.
+Finally, the cost data in the leaf divisions
+is averaged to generate the estimate.
+
+\subsection{Random Forests}
+
+Breiman's website describes \textbf{Random Forests} as
+follows\cite{brieman00}. "Random Forests grows many classification
+trees. To classify a new object from an input vector, put the input
+vector down each of the trees in the forest. Each tree gives a
+classification, and we say the tree "votes" for that class. The forest
+chooses the classification having the most votes (over all the trees
+in the forest). Each tree is grown as follows.
+If the number of cases in the training set is N, sample N cases at
+random - but with replacement, from the original data. This sample
+will be the training set for growing the tree.
+Also, if there are M input variables, a number m$<<$M is specified such
+that at each node, m variables are selected at random out of the M and
+the best split on these m is used to split the node. The value of m is
+held constant during the forest growing.
+Finally, each tree is grown to the largest extent possible (there is
+no pruning)."
+
+%Suppose the cordinates of X and Y are $(0,0)$ and $(0,c)$, which are east and west 
+%instances within N samples. From the Pythegoras and cosine rule, each instance is projected 
+%at the point(x,y)
+%
+%\begin{equation}
+%	\begin{split}
+%	x &= (a^2 + c^2 - b^2)/(2c) \\
+%	y &= \sqrt{a^2 - x^2} 
+%	\end{split}
+%\end{equation}
+
+\subsection{Differential Evolution Algorithm}
+Differential Evolution (DE)\cite{storn1997differential} is a stochastic search algorithm that 
+optimizes a problem by iteratively trying to improve a  population of candidate solutions with 
+regard to a given quality measurement. Such method makes no assumptions about the 
+problem being optimized and has already been used as a parameter tuner
+\cite{omran2005differential, chiha2012tuning}.
+
+DE starts with creating a population of candidate solutions and then generates new 
+candidates based on $New = X+f*(Y-Z)$, where $X$, $Y$ and $Z$ are randomly selected 
+solutions from the current frontier and $f$ is a crossover factor. The newly generated solution 
+will be added into the next generation of solutions if dominating previous old points in the 
+frontier. To avoid meaning less iteration, early termination strategy is applied that is at the 
+beginning, assign a value to the $life$ parameter, it would be reduced by one each time   
+when the new generation of candidate solutions does not improve in terms of quality 
+measurement. The DE will stop when the $life$ equals to 0.
+
+Algorithm \ref{alg:DE} is a list of pseudocode of DE with early termination for maximizing a 
+score function, where $np$ is the number of population in each generation, $f$ is the 
+crossover factor as mentioned, $cf$ is the probability for crossover operation to generate new 
+candidate, $life$ is to control termination.
+
+\begin{algorithm}
+	\caption{Pesudocode for DE with Early Termination}
+	\label{alg:DE}
+		\begin{algorithmic}[1]
+			\Require $np$, $f$, $cf$, $life$
+			\Ensure $S_{best}$
+		  \State $Population  \gets $ InitializePopulation($np$)
+		  \State $S_{best} \gets $GetBestSolution($Population $)
+		  \While{$life > 0$}
+			\State $NewGeneration \gets \emptyset$
+			\For{$i=0 \to n-1$}
+				\State $S_i \gets$ GenNew($Population [i], Population , cf, f)$
+				\If {Score($S_i$) >Score($Population [i]$)}
+				 	\State $NewGeneration \gets S_i$
+				\Else
+					\State $NewGeneration \gets Population [i]$
+				\EndIf
+			\EndFor
+			\State $Population  \gets NewGeneration$
+			\If{$\neg$ Improve($Population $)}
+				\State $life -=1$
+			\EndIf
+			\State $S_{best} \gets$ GetBestSolution($Population $)
+		  \EndWhile
+		 \State \Return $S_{best}$
+                 \end{algorithmic}            
+\end{algorithm}
+
+%\begin{algorithm}
+%\begin{algorithmic}[1]
+% \KwData{this text}
+% \KwResult{how to write algorithm with \LaTeX2e }
+% initialization\;
+% \While{not at end of this document}{
+%  read current\;
+%  \eIf{understand}{
+%   go to next section\;
+%   current section becomes this one\;
+%   }{
+%   go back to the beginning of current section\;
+%  }
+% }
+% \caption{How to write algorithms}
+% \end{algorithmic}
+%\end{algorithm}
 
@@
 
-Description of Data set
+\subsection{Data Set}
 
-Experiment 1: naive where vs tuned where
+The data used in this study is from PROMISE repository. Ten software defect predicition data 
+sets are analyzed. They're {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene}, {\it 
+synapse}, {\it velocity}, {\it xalan} and {\it xerces}. Each of these data sets is composed of 
+several software modules with number of defects and code attributes. For more detailed 
+description of code attributes and the original data sets, please refer to  http://openscience.us/
+repo/
 
-Experiment 2: naive cart vs tuned cart vs random forest
+\subsection{Experiment Design}
+
+The experiment aims at investigate whether tuning helps learners improve performance in 
+terms of accuracy measurement. We choose compare WHERE-based learner with and 
+without tuning parameters and two {\it significantly different} learners Random Forest and 
+CART according to \cite{lessmann2008benchmarking}. As mentioned above, we'd like to see 
+whether tuning will help change the rank of CART and make it comparable with Random 
+Forest.
+
+To evaluate accuracy performance of learners, several measurements are proposed, like 
+probability of  detection({\it pd}) and probability of false alarm ({\it pf})\cite{menzies2007data}, 
+the area under the receiver operating characteristics curve ({\it AUC})
+\cite{lessmann2008benchmarking}, and precision\cite{zhang2007comments}. In this work, we 
+expect learners should identify as many defective modules as possible while avoiding false 
+alarm. Therefore, learners are evaluated by both of {\it pd} and {\it pf} simaltanieously. A single 
+measure, G-measure, defined as the harmonic mean of {\it pd} and $1-{\it pf}$  is used. The 
+G-measure value is between 0 and 1. The higher, the better.
+\begin{equation}
+G = \frac{2*(1-pf)*pd}{1-pf+pd}
+\end{equation}
+
+In this experiment, we use three different portions of one project data set for training, tuning 
+and testing process. In contrast to hold out way used in \cite{lessmann2008benchmarking, 
+menzies2007data}, we separate the data sets in order. Since learners are designed to predict 
+defects in future projects,  any randomly data set selection without taking into the time series 
+will not sufficient to evaluate the performance of predicting future. To the most, that is good to 
+evaluate the accuracy of classification but not predicting future. Since we have 10 different 
+project data, each of which contains least 3 evolutionary versions. We use the following policy 
+to select the data: in each project, we only use the last three data files for experiment. 
+Specifically, the $nth$,  $(n-1)th$, $(n-2)th$ versions of project data are selected for testing, 
+tuning and training learners, respectively. This will make sure that we don't use the future 
+project data to train learners and predict previous project.
+
+To investigates the impacts of parameters on learners, we use DE as the tuner and compare the G-measure 
+values of Where-based learner with and without tuning, CART with and without tuning and Random 
+Forests. Since the tuning time for Random Forests is very long, hopefully other researchers design
+new heuristics to speed up the tuning process for Random Forests.  For the time being, even though
+we don't tune Random Forests, if tuning help CART outperform Random Forests or improve itself performance ,
+we still could conclude that tuning is helpful and necessary when comparing learners.
+
+Besides the Where-based learner implemented by ourself,  we use the CART and Random Forest modules 
+from scikit-learn \cite{scikit-learn} for this experiment.
+The parameters associated with different learners are listed in Fig.\ref{fig:parameters}.
+(\textbf{NEED to elaborate that there're different versions of CART, what's the point to do this experiment}).
+For each data set, run CART, naive Where-based learner and Random Forests with corresponding default values.
+Then using DE to tune corresponding parameters for CART and Where-based Learner,  and run them again with the optimal parameters from tuning process to test the performance.
+This study ranks learners using the Scott-Knott procedure recommended by Mittas \& Angelis in their 2013
+IEEE TSE paper~\cite{mittas2013ranking}.
+This method sorts a list of $l$ treatments with $ls$ measurements by their median score.
+It then splits $l$ into sub-lists $m,n$ in order to maximize the expected value of differences  in the observed performances before and after divisions.
+
+\begin{figure*}[t!]
+\scriptsize
+  \centering
+	\begin{tabular}{|c|c|c|c|l|}
+	\hline
+	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
+\multicolumn{1}{c|}{Description} \\ \hline
+	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
+	& threshold & 0.5 &[0,1]& The value to determine defective or not .\\ \cline{2-5} 
+	& infogain & 0.33 &[0,1]& The percentage of features to consider  for the best 
+split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
+one is for clustering and the second one is building prediction model. we explicitly call Where-
+clustering tree and CART tree, respectively}. \\ \cline{2-5} 
+	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
+CART tree. \\ \cline{2-5} 
+	 & min\_Size & 0.5 &[0,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
+number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
+\end{tabular} \\ \cline{2-5} 
+	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
+clustering tree. \\ \cline{2-5} 
+	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
+	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5} 
+	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ 
+\hline
+	\multirow{5}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ 
+\cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5} 
+	 & max\_depth & None &[1,50]& The maximum depth of the tree. \\ \cline{2-5} 
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \hline  
+       \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & - & The value to determine defective or not. \\ 
+\cline{2-5} 
+	 & max\_feature & None &-& The number of features to consider when looking for the best 
+split. \\ \cline{2-5} 
+	 & max\_depth & None &-& The maximum depth of the tree. \\ \cline{2-5} 
+	 & min\_sample\_split & 2 &-& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_smaples\_leaf & 1 & -&The minimum number of samples required to be at a leaf 
+node. \\ \cline{2-5} 
+	 &  n\_estimators & 100 & -&The number of trees in the forest.\\ \hline
+
+	\end{tabular}
+    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
+\label{fig:parameters}
+\end{figure*}
+
+\section{Result}
+\begin{figure}[!th]
+
+{\scriptsize
+{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{0.75} Dataset     & Methods  & median &IQR&  \\ 
+\rowcolor[gray]{.9}ant & Naive\_WHERE & 0 & 0 & \quart{0.0}{0}{0.0}\\
+ & Naive\_Cart & 51 & 2 & \quart{51.0}{2}{52.0}\\
+ & Naive\_RFst & 53 & 1 & \quart{52.0}{1}{53.0}\\
+ & Tuned\_Cart & 63 & 0 & \quart{63.0}{0}{63.0}\\
+ & Tuned\_WHERE & 72 & 0 & \quart{72.0}{0}{72.0}\\
+\rowcolor[gray]{.9}camel & Naive\_WHERE & 45 & 0 & \quart{45.0}{0}{45.0}\\
+ & Naive\_Cart & 54 & 2 & \quart{54.0}{2}{54.0}\\
+ & Tuned\_WHERE & 56 & 0 & \quart{56.0}{0}{56.0}\\
+ & Tuned\_Cart & 56 & 2 & \quart{56.0}{2}{57.0}\\
+ & Naive\_RFst & 56 & 1 & \quart{57.0}{1}{57.0}\\
+\rowcolor[gray]{.9}ivy & Naive\_RFst & 50 & 1 & \quart{50.0}{1}{50.0}\\
+ & Naive\_WHERE & 54 & 0 & \quart{54.0}{0}{54.0}\\
+ & Naive\_Cart & 57 & 1 & \quart{58.0}{1}{58.0}\\
+ & Tuned\_Cart & 68 & 0 & \quart{68.0}{0}{68.0}\\
+ & Tuned\_WHERE & 70 & 0 & \quart{70.0}{0}{70.0}\\
+\rowcolor[gray]{.9} jedit & Naive\_WHERE & 49 & 0 & \quart{49.0}{0}{49.0}\\
+ & Naive\_Cart & 55 & 15 & \quart{55.0}{15}{55.0}\\
+ & Tuned\_WHERE & 62 & 0 & \quart{62.0}{0}{62.0}\\
+ & Tuned\_Cart & 65 & 3 & \quart{65.0}{3}{66.0}\\
+ & Naive\_RFst & 74 & 2 & \quart{73.0}{2}{74.0}\\
+ \rowcolor[gray]{.9} log4j & Naive\_Cart & 48 & 1 & \quart{47.0}{1}{48.0}\\
+ & Tuned\_WHERE & 50 & 0 & \quart{50.0}{0}{50.0}\\
+ & Naive\_WHERE & 53 & 0 & \quart{53.0}{0}{53.0}\\
+ & Tuned\_Cart & 55 & 4 & \quart{55.0}{4}{57.0}\\
+ & Naive\_RFst & 56 & 0 & \quart{57.0}{0}{57.0}\\
+\rowcolor[gray]{.9}lucene & Naive\_WHERE & 37 & 0 & \quart{37.0}{0}{37.0}\\
+ & Naive\_RFst & 56 & 1 & \quart{56.0}{1}{56.0}\\
+ & Naive\_Cart & 57 & 1 & \quart{57.0}{1}{58.0}\\
+ & Tuned\_Cart & 57 & 4 & \quart{57.0}{4}{58.0}\\
+ & Tuned\_WHERE & 61 & 0 & \quart{61.0}{0}{61.0}\\
+\rowcolor[gray]{.9}synapse & Naive\_WHERE & 0 & 0 & \quart{0.0}{0}{0.0}\\
+ & Naive\_Cart & 42 & 2 & \quart{41.0}{2}{42.0}\\
+ & Naive\_RFst & 43 & 4 & \quart{43.0}{4}{44.0}\\
+ & Tuned\_Cart & 49 & 11 & \quart{49.0}{11}{49.0}\\
+ & Tuned\_WHERE & 64 & 0 & \quart{64.0}{0}{64.0}\\
+\rowcolor[gray]{.9}velocity & Naive\_WHERE & 1 & 0 & \quart{1.0}{0}{1.0}\\
+ & Naive\_RFst & 9 & 0 & \quart{9.0}{0}{9.0}\\
+ & Naive\_Cart & 27 & 2 & \quart{26.0}{2}{27.0}\\
+ & Tuned\_Cart & 49 & 5 & \quart{46.0}{5}{50.0}\\
+ & Tuned\_WHERE & 57 & 0 & \quart{58.0}{0}{58.0}\\
+\rowcolor[gray]{.9}xalan & Tuned\_Cart & 51 & 4 & \quart{49.0}{4}{51.0}\\
+ & Tuned\_WHERE & 56 & 0 & \quart{57.0}{0}{57.0}\\
+ & Naive\_Cart & 66 & 0 & \quart{66.0}{0}{66.0}\\
+ & Naive\_WHERE & 69 & 0 & \quart{69.0}{0}{69.0}\\
+ & Naive\_RFst & 73 & 1 & \quart{73.0}{1}{73.0}\\
+\rowcolor[gray]{.9}xerces & Naive\_RFst & 18 & 1 & \quart{18.0}{1}{18.0}\\
+ & Naive\_Cart & 19 & 1 & \quart{18.0}{1}{19.0}\\
+ & Tuned\_Cart & 25 & 7 & \quart{24.0}{7}{26.0}\\
+ & Naive\_WHERE & 26 & 0 & \quart{26.0}{0}{26.0}\\
+ & Tuned\_WHERE & 34 & 1 & \quart{34.0}{1}{34.0}\\
+
+ \end{tabular}}
+
+}
+
+\caption{Results over Different Data Sets}\label{fig:g feature}
+\end{figure}
 
@@
 \section{Conclusion}
-%The \textit{proceedings} are the records of a conference.
-%ACM seeks to give these conference by-products a uniform,
-%high-quality appearance.  To do this, ACM has some rigid
-%requirements for the format of the proceedings documents: there
-%is a specified format (balanced  double columns), a specified
-%set of fonts (Arial or Helvetica and Times Roman) in
-%certain specified sizes (for instance, 9 point for body copy),
-%a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-%the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-%and (1.9 cm [.75"]) left and right; specified column width
-%(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
-%
-%The good news is, with only a handful of manual
-%settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-%and {\texttt{\char'134 alignauthor}} commands, you have
-%already used; another, {\texttt{\char'134 balancecolumns}}, will
-%be used in your very last run of \LaTeX\ to ensure
-%balanced column heights on the last page.}, the \LaTeX\ document
-%class file handles all of this for you.
-%
-%The remainder of this document is concerned with showing, in
-%the context of an ``actual'' document, the \LaTeX\ commands
-%specifically available for denoting the structure of a
-%proceedings paper, rather than with giving rigorous descriptions
-%or explanations of such commands.
-%
-%\section{The {\secit Body} of The Paper}
-%Typically, the body of a paper is organized
-%into a hierarchical structure, with numbered or unnumbered
-%headings for sections, subsections, sub-subsections, and even
-%smaller sections.  The command \texttt{{\char'134}section} that
-%precedes this paragraph is part of such a
-%hierarchy.\footnote{This is the second footnote.  It
-%starts a series of three footnotes that add nothing
-%informational, but just give an idea of how footnotes work
-%and look. It is a wordy one, just so you see
-%how a longish one plays out.} \LaTeX\ handles the numbering
-%and placement of these headings for you, when you use
-%the appropriate heading commands around the titles
-%of the headings.  If you want a sub-subsection or
-%smaller part to be unnumbered in your output, simply append an
-%asterisk to the command name.  Examples of both
-%numbered and unnumbered headings will appear throughout the
-%balance of this sample document.
-%
-%Because the entire article is contained in
-%the \textbf{document} environment, you can indicate the
-%start of a new paragraph with a blank line in your
-%input file; that is why this sentence forms a separate paragraph.
-%
-%\subsection{Type Changes and {\subsecit Special} Characters}
-%We have already seen several typeface changes in this sample.  You
-%can indicate italicized words or phrases in your text with
-%the command \texttt{{\char'134}textit}; emboldening with the
-%command \texttt{{\char'134}textbf}
-%and typewriter-style (for instance, for computer code) with
-%\texttt{{\char'134}texttt}.  But remember, you do not
-%have to indicate typestyle changes when such changes are
-%part of the \textit{structural} elements of your
-%article; for instance, the heading of this subsection will
-%be in a sans serif\footnote{A third footnote, here.
-%Let's make this a rather short one to
-%see how it looks.} typeface, but that is handled by the
-%document class file. Take care with the use
-%of\footnote{A fourth, and last, footnote.}
-%the curly braces in typeface changes; they mark
-%the beginning and end of
-%the text that is to be in the different typeface.
-%
-%You can use whatever symbols, accented characters, or
-%non-English characters you need anywhere in your document;
-%you can find a complete list of what is
-%available in the \textit{\LaTeX\
-%User's Guide}\cite{Lamport:LaTeX}.
-%
-%\subsection{Math Equations}
-%You may want to display math equations in three distinct styles:
-%inline, numbered or non-numbered display.  Each of
-%the three are discussed in the next sections.
-%
-%\subsubsection{Inline (In-text) Equations}
-%A formula that appears in the running text is called an
-%inline or in-text formula.  It is produced by the
-%\textbf{math} environment, which can be
-%invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-%construction or with the short form \texttt{\$. . .\$}. You
-%can use any of the symbols and structures,
-%from $\alpha$ to $\omega$, available in
-%\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-%few examples of in-text equations in context. Notice how
-%this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-%set here in in-line math style, looks slightly different when
-%set in display style.  (See next section).
-%
-%\subsubsection{Display Equations}
-%A numbered display equation -- one set off by vertical space
-%from the text and centered horizontally -- is produced
-%by the \textbf{equation} environment. An unnumbered display
-%equation is produced by the \textbf{displaymath} environment.
-%
-%Again, in either environment, you can use any of the symbols
-%and structures available in \LaTeX; this section will just
-%give a couple of examples of display equations in context.
-%First, consider the equation, shown as an inline equation above:
-%\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-%Notice how it is formatted somewhat differently in
-%the \textbf{displaymath}
-%environment.  Now, we'll enter an unnumbered equation:
-%\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-%and follow it with another numbered equation:
-%\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-%just to demonstrate \LaTeX's able handling of numbering.
-%
-%\subsection{Citations}
-%Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-%conference
-%proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-%in the Bibliography section of your
-%article will occur throughout the text of your article.
-%You should use BibTeX to automatically produce this bibliography;
-%you simply need to insert one of several citation commands with
-%a key of the item cited in the proper location in
-%the \texttt{.tex} file \cite{Lamport:LaTeX}.
-%The key is a short reference you invent to uniquely
-%identify each work; in this sample document, the key is
-%the first author's surname and a
-%word from the title.  This identifying key is included
-%with each item in the \texttt{.bib} file for your article.
-%
-%The details of the construction of the \texttt{.bib} file
-%are beyond the scope of this sample document, but more
-%information can be found in the \textit{Author's Guide},
-%and exhaustive details in the \textit{\LaTeX\ User's
-%Guide}\cite{Lamport:LaTeX}.
-%
-%This article shows only the plainest form
-%of the citation command, using \texttt{{\char'134}cite}.
-%This is what is stipulated in the SIGS style specifications.
-%No other citation format is endorsed.
-%
-%\subsection{Tables}
-%Because tables cannot be split across pages, the best
-%placement for them is typically the top of the page
-%nearest their initial cite.  To
-%ensure this proper ``floating'' placement of tables, use the
-%environment \textbf{table} to enclose the table's contents and
-%the table caption.  The contents of the table itself must go
-%in the \textbf{tabular} environment, to
-%be aligned properly in rows and columns, with the desired
-%horizontal and vertical rules.  Again, detailed instructions
-%on \textbf{tabular} material
-%is found in the \textit{\LaTeX\ User's Guide}.
-%
-%Immediately following this sentence is the point at which
-%Table 1 is included in the input file; compare the
-%placement of the table here with the table in the printed
-%dvi output of this document.
-%
-%\begin{table}
-%\centering
-%\caption{Frequency of Special Characters}
-%\begin{tabular}{|c|c|l|} \hline
-%Non-English or Math&Frequency&Comments\\ \hline
-%\O & 1 in 1,000& For Swedish names\\ \hline
-%$\pi$ & 1 in 5& Common in math\\ \hline
-%\$ & 4 in 5 & Used in business\\ \hline
-%$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-%\hline\end{tabular}
-%\end{table}
-%
-%To set a wider table, which takes up the whole width of
-%the page's live area, use the environment
-%\textbf{table*} to enclose the table's contents and
-%the table caption.  As with a single-column table, this wide
-%table will ``float" to a location deemed more desirable.
-%Immediately following this sentence is the point at which
-%Table 2 is included in the input file; again, it is
-%instructive to compare the placement of the
-%table here with the table in the printed dvi
-%output of this document.
-%
-%
-%\begin{table*}
-%\centering
-%\caption{Some Typical Commands}
-%\begin{tabular}{|c|c|l|} \hline
-%Command&A Number&Comments\\ \hline
-%\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-%\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-%\texttt{{\char'134}table}& 300 & For tables\\ \hline
-%\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-%\end{table*}
-%% end the environment with {table*}, NOTE not {table}!
-%
-%\subsection{Figures}
-%Like tables, figures cannot be split across pages; the
-%best placement for them
-%is typically the top or the bottom of the page nearest
-%their initial cite.  To ensure this proper ``floating'' placement
-%of figures, use the environment
-%\textbf{figure} to enclose the figure and its caption.
-%
-%This sample document contains examples of \textbf{.eps}
-%and \textbf{.ps} files to be displayable with \LaTeX.  More
-%details on each of these is found in the \textit{Author's Guide}.
-%
-%\begin{figure}
-%\centering
-%\epsfig{file=fly.eps}
-%\caption{A sample black and white graphic (.eps format).}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\epsfig{file=fly.eps, height=1in, width=1in}
-%\caption{A sample black and white graphic (.eps format)
-%that has been resized with the \texttt{epsfig} command.}
-%\end{figure}
-%
-%
-%As was the case with tables, you may want a figure
-%that spans two columns.  To do this, and still to
-%ensure proper ``floating'' placement of tables, use the environment
-%\textbf{figure*} to enclose the figure and its caption.
-%
-%Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-%used; use
-%the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-%commands as appropriate for the different file types.
-%
-%\subsection{Theorem-like Constructs}
-%Other common constructs that may occur in your article are
-%the forms for logical constructs like theorems, axioms,
-%corollaries and proofs.  There are
-%two forms, one produced by the
-%command \texttt{{\char'134}newtheorem} and the
-%other by the command \texttt{{\char'134}newdef}; perhaps
-%the clearest and easiest way to distinguish them is
-%to compare the two in the output of this sample document:
-%
-%This uses the \textbf{theorem} environment, created by
-%the\linebreak\texttt{{\char'134}newtheorem} command:
-%\newtheorem{theorem}{Theorem}
-%\begin{theorem}
-%Let $f$ be continuous on $[a,b]$.  If $G$ is
-%an antiderivative for $f$ on $[a,b]$, then
-%\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-%\end{theorem}
-%
-%The other uses the \textbf{definition} environment, created
-%by the \texttt{{\char'134}newdef} command:
-%\newdef{definition}{Definition}
-%\begin{definition}
-%If $z$ is irrational, then by $e^z$ we mean the
-%unique number which has
-%logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-%\end{definition}
-%
-%\begin{figure}
-%\centering
-%\psfig{file=rosette.ps, height=1in, width=1in,}
-%\caption{A sample black and white graphic (.ps format) that has
-%been resized with the \texttt{psfig} command.}
-%\end{figure}
-%
-%Two lists of constructs that use one of these
-%forms is given in the
-%\textit{Author's  Guidelines}.
-%
-%\begin{figure*}
-%\centering
-%\epsfig{file=flies.eps}
-%\caption{A sample black and white graphic (.eps format)
-%that needs to span two columns of text.}
-%\end{figure*}
-%and don't forget to end the environment with
-%{figure*}, not {figure}!
-% 
-%There is one other similar construct environment, which is
-%already set up
-%for you; i.e. you must \textit{not} use
-%a \texttt{{\char'134}newdef} command to
-%create it: the \textbf{proof} environment.  Here
-%is a example of its use:
-%\begin{proof}
-%Suppose on the contrary there exists a real number $L$ such that
-%\begin{displaymath}
-%\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-%\end{displaymath}
-%Then
-%\begin{displaymath}
-%l=\lim_{x\rightarrow c} f(x)
-%= \lim_{x\rightarrow c}
-%\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-%= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-%\frac{f(x)}{g(x)} = 0\cdot L = 0,
-%\end{displaymath}
-%which contradicts our assumption that $l\neq 0$.
-%\end{proof}
-%
-%Complete rules about using these environments and using the
-%two different creation commands are in the
-%\textit{Author's Guide}; please consult it for more
-%detailed instructions.  If you need to use another construct,
-%not listed therein, which you want to have the same
-%formatting as the Theorem
-%or the Definition\cite{salas:calculus} shown above,
-%use the \texttt{{\char'134}newtheorem} or the
-%\texttt{{\char'134}newdef} command,
-%respectively, to create it.
-%
-%\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-%Because you have just been given permission to
-%use the \texttt{{\char'134}newdef} command to create a
-%new form, you might think you can
-%use \TeX's \texttt{{\char'134}def} to create a
-%new command: \textit{Please refrain from doing this!}
-%Remember that your \LaTeX\ source code is primarily intended
-%to create camera-ready copy, but may be converted
-%to other forms -- e.g. HTML. If you inadvertently omit
-%some or all of the \texttt{{\char'134}def}s recompilation will
-%be, to say the least, problematic.
-%
-%\section{Conclusions}
-%This paragraph will end the body of this sample document.
-%Remember that you might still have Acknowledgments or
-%Appendices; brief samples of these
-%follow.  There is still the Bibliography to deal with; and
-%we will make a disclaimer about that here: with the exception
-%of the reference to the \LaTeX\ book, the citations in
-%this paper are to articles which have nothing to
-%do with the present subject and are used as
-%examples only.
-%%\end{document}  % This is where a 'short' article might terminate
-%
-%%ACKNOWLEDGMENTS are optional
+
 \section{Acknowledgments}
-%This section is optional; it is a location for you
-%to acknowledge grants, funding, editing assistance and
-%what have you.  In the present case, for example, the
-%authors would like to thank Gerald Murray of ACM for
-%his help in codifying this \textit{Author's Guide}
-%and the \textbf{.cls} and \textbf{.tex} files that it describes.
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
 \bibliographystyle{unsrt}
-\bibliography{tuningpredictor}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-%\appendix
-%%Appendix A
-%\section{Headings in Appendices}
-%The rules about hierarchical headings discussed above for
-%the body of the article are different in the appendices.
-%In the \textbf{appendix} environment, the command
-%\textbf{section} is used to
-%indicate the start of each Appendix, with alphabetic order
-%designation (i.e. the first is A, the second B, etc.) and
-%a title (if you include one).  So, if you need
-%hierarchical structure
-%\textit{within} an Appendix, start with \textbf{subsection} as the
-%highest level. Here is an outline of the body of this
-%document in Appendix-appropriate form:
-%\subsection{Introduction}
-%\subsection{The Body of the Paper}
-%\subsubsection{Type Changes and  Special Characters}
-%\subsubsection{Math Equations}
-%\paragraph{Inline (In-text) Equations}
-%\paragraph{Display Equations}
-%\subsubsection{Citations}
-%\subsubsection{Tables}
-%\subsubsection{Figures}
-%\subsubsection{Theorem-like Constructs}
-%\subsubsection*{A Caveat for the \TeX\ Expert}
-%\subsection{Conclusions}
-%\subsection{Acknowledgments}
-%\subsection{Additional Authors}
-%This section is inserted by \LaTeX; you do not insert it.
-%You just add the names and information in the
-%\texttt{{\char'134}additionalauthors} command at the start
-%of the document.
-%\subsection{References}
-%Generated by bibtex from your ~.bib file.  Run latex,
-%then bibtex, then latex twice (to resolve references)
-%to create the ~.bbl file.  Insert that ~.bbl file into
-%the .tex source file and comment out
-%the command \texttt{{\char'134}thebibliography}.
-%% This next section command marks the start of
-%% Appendix B, and does not continue the present hierarchy
-%\section{More Help for the Hardy}
-%The acm\_proc\_article-sp document class file itself is chock-full of succinct
-%and helpful comments.  If you consider yourself a moderately
-%experienced to expert user of \LaTeX, you may find reading
-%it useful but please remember not to change it.
-%\balancecolumns
-% That's all folks!
+\bibliography{tuningpredictor}  
 \end{document}

### 2015-02-18 tuningpredictor.tex
startting up

@@
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternative}
 \usepackage{multirow}
@@
 
+%% timm tricks
+\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
+\newcommand{\ei}{\end{itemize}}
+\newcommand{\be}{\begin{enumerate}}
+\newcommand{\ee}{\end{enumerate}}
+\newcommand{\tion}[1]{\S\ref{sect:#1}}
+\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
+\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
+
+%% space saving measures
+
+\usepackage[shortlabels]{enumitem} 
+\usepackage{times}
+
+\usepackage{url}
+\def\baselinestretch{1}
+
+\setlist{nosep}
+ \usepackage[font={small}]{caption, subfig}
+\setlength{\abovecaptionskip}{1ex}
+ \setlength{\belowcaptionskip}{1ex}
+
+ \setlength{\floatsep}{1ex}
+ \setlength{\textfloatsep}{1ex}
+\usepackage[compact,small]{titlesec}
+\DeclareMathSizes{7}{7}{7}{7} 
+\pagenumbering{arabic}
+\setlength{\columnsep}{7mm}
+
 \begin{document}
-\title{Tuning Learners before Applying: New Reflection in Defect Prediction }
-\author{ A, B, C}
+
+\conferenceinfo{FSE}{'15 Bergamo, Italy}
+\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
+\numberofauthors{1}
+\author{
+\alignauthor
+Wei Fung, TimMenzies\\
+       \affaddr{Computer Science, North Carolina State University, USA}\\
+       {wfu@ncsu.edu, tim.menzies@gmail.com}}
+
 \maketitle
@@
 % A category with the (minimum) three required fields
-\category{D.2.9}{Software Engineering}{Management}[Cost estimation]
+\vspace{1mm}
+\noindent
+{\bf Categories/Subject Descriptors:} 
+D.2.8 [Software Engineering]: Product metrics;
+I.2.6 [Artificial Intelligence]: Induction
 
-\terms{Experimentation, Algorithm}
+\vspace{1mm}
+\noindent
+{\bf General Terms:} Experimentation, Algorithm}
 
-\keywords{Defect prediction, Data Mining, Tuning Parameters, CART, WHERE} 
-% NOT required for Proceedings
+\vspace{1mm}
+\noindent
+{\bf Keywords:} defect prediction, CART, random forests,
+Fastmap,   bootstrap sampling, effect size, A12.
 
@@
 
+\begin{raggedleft}
+{\em ``The  common misunderstanding about science 
+is that scientists seek and find truth. They don't- 
+they make and test models.''}\\ -- Neil Gershenfeld
+
+{\em Essentially, all models are wrong, but some are useful."}\\ --George Box
+
+\end{raggedleft}
+
+How ``true'' are the  models generated by software analytics?
+Suppose we use a model generated from software project data to, for example,
+assess the relative value of OO metrics vs procedural metrics for predicting
+project defects. Are we reporting ``truth'' in any sense of the word? And for home
+many other projects might we find that same ``truth''?
+
+Our reading of the
+
+and we reflect on that model, are we
+
+will it reveal the `1`t
+A standard approach to software analutics
 Software has becoming a large and complex system and delivering reliable and quality 
@@
 
-\section{Acknowledgments}
+\section*{Acknowledgements}
+This work was partially funded by an National Science
+Foundation grant NSF-CISE 1302169.
+
+\vspace*{0.5mm}
+\scriptsize
 

### 2015-02-19 tuningpredictor.tex
typo

@@
 \alignauthor
-Wei Fung, TimMenzies\\
+Wei Fung, Tim Menzies\\
        \affaddr{Computer Science, North Carolina State University, USA}\\
@@
 
+good news:
+\bi 
+\item Tuning is easy (but one measure, at least an order of magnitude easier than 
+standard optimization problems)
+\item Tuning can dramatically improve the performance of a learner (in one case, from recalls
+of zero to 70\%)
+\ei
+interesting news
+\bi 
+\item tunings different for different data sets.
+\ei 
+bad news:
+\bi
+\item Tuning also changes what was learned
+\bi
+\item Supposedly ``bad'' learners start working much better than supposedly ``best'' learners;
+\item The models used in the tuned models were very different to those used in the untuned learners.
+\ei 
+\ei 
 and we reflect on that model, are we

### 2015-03-02 tuningpredictor.tex
add experimental results

@@
 \usepackage{color}
+\usepackage{graphics}
+\usepackage{rotating}
+\usepackage{graphics}
 \usepackage{colortbl}
@@
 \usepackage{algpseudocode}
+\definecolor{lightgray}{gray}{0.8}
+\definecolor{darkgray}{gray}{0.6}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+%%% graph
+\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
+\newcommand{\rone}{\crule{1mm}{1.95mm}}
+\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
+\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
+\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
+\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
 \newcommand{\quart}[3]{\begin{picture}(100,6)%1
 {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
+\definecolor{Gray}{gray}{0.95}
+\definecolor{LightGray}{gray}{0.975}
 
@@
 \alignauthor
-Wei Fung, Tim Menzies\\
+Wei Fu, Tim Menzies\\
        \affaddr{Computer Science, North Carolina State University, USA}\\
@@
 \noindent
-{\bf General Terms:} Experimentation, Algorithm}
+{\bf General Terms:} Experimentation, Algorithm
 
@@
 called ``FASTMAP" proposed by Faloutsos \& Lin\cite{faloutsos1995fastmap}. ``FASTMAP" 
-randomly picks one instance Z; find the instance {\it east} X that's furthest away form Z; find 
-the instance {\it west} Y that's furthest away from {\it east} X. Next, project all the remaining 
-points onto the line drawn between X and Y. Then choose the median point as the split and 
+randomly picks one instance $Z$; find the instance {\it east} $X$ that's furthest away form $Z$; find 
+the instance {\it west} $Y$ that's furthest away from {\it east} $X$. Next, project all the remaining 
+points onto the line drawn between $X$ and $Y$.  The line $\overline{XY}$ is an approximation of the 
+first component found by PCA.
+As shown in Figure \ref{Where}, $X$ and $Y$ are the furthest points found by ``FASTMAP'' and $\overline{XY}$ is of length $c$.
+Each point in this figure has a distance $a$
+to $X$ and distance $b$ to $Y$. According to the coisne rule and Pythagoras, each instance will be mapped 
+into 2-dimension by the following equations.
+\begin{equation}
+	\begin{split}
+			x  &= (a^2 +c^2-b^2)/(2c)\\ 
+		    y  &= \sqrt{a^2 -x^2}
+	\end{split}
+\end{equation}
+
+Then choose the median point $\hat{x}$ as the split and 
 recursively divide all the instances into {\it west} and {\it east} clusters until the number of 
@@
 
+\begin{figure}[!ht]
+\includegraphics[scale=0.5]{where.png}
+\caption{WHERE algoirthm }
+\label{Where}
+\end{figure}
 Then based on the attributes and the cluster labels in each instances,  we build a 
@@
 
-\begin{figure*}[t!]
-\scriptsize
-  \centering
-	\begin{tabular}{|c|c|c|c|l|}
-	\hline
-	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
-\multicolumn{1}{c|}{Description} \\ \hline
-	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
-	& threshold & 0.5 &[0,1]& The value to determine defective or not .\\ \cline{2-5} 
-	& infogain & 0.33 &[0,1]& The percentage of features to consider  for the best 
-split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
-one is for clustering and the second one is building prediction model. we explicitly call Where-
-clustering tree and CART tree, respectively}. \\ \cline{2-5} 
-	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
-CART tree. \\ \cline{2-5} 
-	 & min\_Size & 0.5 &[0,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
-number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
-\end{tabular} \\ \cline{2-5} 
-	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
-clustering tree. \\ \cline{2-5} 
-	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
-	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5} 
-	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ 
-\hline
-	\multirow{5}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ 
-\cline{2-5} 
-	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5} 
-	 & max\_depth & None &[1,50]& The maximum depth of the tree. \\ \cline{2-5} 
-	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \hline  
-       \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & - & The value to determine defective or not. \\ 
-\cline{2-5} 
-	 & max\_feature & None &-& The number of features to consider when looking for the best 
-split. \\ \cline{2-5} 
-	 & max\_depth & None &-& The maximum depth of the tree. \\ \cline{2-5} 
-	 & min\_sample\_split & 2 &-& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_smaples\_leaf & 1 & -&The minimum number of samples required to be at a leaf 
-node. \\ \cline{2-5} 
-	 &  n\_estimators & 100 & -&The number of trees in the forest.\\ \hline
-
-	\end{tabular}
-    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
-\label{fig:parameters}
-\end{figure*}
-
 \section{Result}
-\begin{figure}[!th]
-
-{\scriptsize
-{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{0.75} Dataset     & Methods  & median &IQR&  \\ 
-\rowcolor[gray]{.9}ant & Naive\_WHERE & 0 & 0 & \quart{0.0}{0}{0.0}\\
- & Naive\_Cart & 51 & 2 & \quart{51.0}{2}{52.0}\\
- & Naive\_RFst & 53 & 1 & \quart{52.0}{1}{53.0}\\
- & Tuned\_Cart & 63 & 0 & \quart{63.0}{0}{63.0}\\
- & Tuned\_WHERE & 72 & 0 & \quart{72.0}{0}{72.0}\\
-\rowcolor[gray]{.9}camel & Naive\_WHERE & 45 & 0 & \quart{45.0}{0}{45.0}\\
- & Naive\_Cart & 54 & 2 & \quart{54.0}{2}{54.0}\\
- & Tuned\_WHERE & 56 & 0 & \quart{56.0}{0}{56.0}\\
- & Tuned\_Cart & 56 & 2 & \quart{56.0}{2}{57.0}\\
- & Naive\_RFst & 56 & 1 & \quart{57.0}{1}{57.0}\\
-\rowcolor[gray]{.9}ivy & Naive\_RFst & 50 & 1 & \quart{50.0}{1}{50.0}\\
- & Naive\_WHERE & 54 & 0 & \quart{54.0}{0}{54.0}\\
- & Naive\_Cart & 57 & 1 & \quart{58.0}{1}{58.0}\\
- & Tuned\_Cart & 68 & 0 & \quart{68.0}{0}{68.0}\\
- & Tuned\_WHERE & 70 & 0 & \quart{70.0}{0}{70.0}\\
-\rowcolor[gray]{.9} jedit & Naive\_WHERE & 49 & 0 & \quart{49.0}{0}{49.0}\\
- & Naive\_Cart & 55 & 15 & \quart{55.0}{15}{55.0}\\
- & Tuned\_WHERE & 62 & 0 & \quart{62.0}{0}{62.0}\\
- & Tuned\_Cart & 65 & 3 & \quart{65.0}{3}{66.0}\\
- & Naive\_RFst & 74 & 2 & \quart{73.0}{2}{74.0}\\
- \rowcolor[gray]{.9} log4j & Naive\_Cart & 48 & 1 & \quart{47.0}{1}{48.0}\\
- & Tuned\_WHERE & 50 & 0 & \quart{50.0}{0}{50.0}\\
- & Naive\_WHERE & 53 & 0 & \quart{53.0}{0}{53.0}\\
- & Tuned\_Cart & 55 & 4 & \quart{55.0}{4}{57.0}\\
- & Naive\_RFst & 56 & 0 & \quart{57.0}{0}{57.0}\\
-\rowcolor[gray]{.9}lucene & Naive\_WHERE & 37 & 0 & \quart{37.0}{0}{37.0}\\
- & Naive\_RFst & 56 & 1 & \quart{56.0}{1}{56.0}\\
- & Naive\_Cart & 57 & 1 & \quart{57.0}{1}{58.0}\\
- & Tuned\_Cart & 57 & 4 & \quart{57.0}{4}{58.0}\\
- & Tuned\_WHERE & 61 & 0 & \quart{61.0}{0}{61.0}\\
-\rowcolor[gray]{.9}synapse & Naive\_WHERE & 0 & 0 & \quart{0.0}{0}{0.0}\\
- & Naive\_Cart & 42 & 2 & \quart{41.0}{2}{42.0}\\
- & Naive\_RFst & 43 & 4 & \quart{43.0}{4}{44.0}\\
- & Tuned\_Cart & 49 & 11 & \quart{49.0}{11}{49.0}\\
- & Tuned\_WHERE & 64 & 0 & \quart{64.0}{0}{64.0}\\
-\rowcolor[gray]{.9}velocity & Naive\_WHERE & 1 & 0 & \quart{1.0}{0}{1.0}\\
- & Naive\_RFst & 9 & 0 & \quart{9.0}{0}{9.0}\\
- & Naive\_Cart & 27 & 2 & \quart{26.0}{2}{27.0}\\
- & Tuned\_Cart & 49 & 5 & \quart{46.0}{5}{50.0}\\
- & Tuned\_WHERE & 57 & 0 & \quart{58.0}{0}{58.0}\\
-\rowcolor[gray]{.9}xalan & Tuned\_Cart & 51 & 4 & \quart{49.0}{4}{51.0}\\
- & Tuned\_WHERE & 56 & 0 & \quart{57.0}{0}{57.0}\\
- & Naive\_Cart & 66 & 0 & \quart{66.0}{0}{66.0}\\
- & Naive\_WHERE & 69 & 0 & \quart{69.0}{0}{69.0}\\
- & Naive\_RFst & 73 & 1 & \quart{73.0}{1}{73.0}\\
-\rowcolor[gray]{.9}xerces & Naive\_RFst & 18 & 1 & \quart{18.0}{1}{18.0}\\
- & Naive\_Cart & 19 & 1 & \quart{18.0}{1}{19.0}\\
- & Tuned\_Cart & 25 & 7 & \quart{24.0}{7}{26.0}\\
- & Naive\_WHERE & 26 & 0 & \quart{26.0}{0}{26.0}\\
- & Tuned\_WHERE & 34 & 1 & \quart{34.0}{1}{34.0}\\
-
- \end{tabular}}
-
-}
-
-\caption{Results over Different Data Sets}\label{fig:g feature}
-\end{figure}
 
@@
 
-\section*{Acknowledgements}
-This work was partially funded by an National Science
-Foundation grant NSF-CISE 1302169.
-
-\vspace*{0.5mm}
-\scriptsize
+\section{Acknowledgments}
 
@@
 \bibliography{tuningpredictor}
+
+%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
+\renewcommand\arraystretch{1.2}
+\begin{figure*}[t!]
+\scriptsize
+  \centering
+	\begin{tabular}{|c|c|c|c|l|}
+	\cline{1-5}
+	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
+\multicolumn{1}{c|}{Description} \\ \hline
+	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
+	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
+	& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
+split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
+one is for clustering and the second one is building prediction model. we explicitly call Where-
+clustering tree and CART tree, respectively}. \\ \cline{2-5} 
+	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
+CART tree. \\ \cline{2-5} 
+	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
+number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
+\end{tabular} \\ \cline{2-5} 
+    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
+	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
+clustering tree. \\ \cline{2-5} 
+	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
+	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
+	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
+\hline
+\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5}
+
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{1-5}  
+       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
+\cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5} 
+	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_smaples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{2-5} 
+	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
+	 \hline
+
+	\end{tabular}
+    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
+\label{fig:parameters}
+\end{figure*}
+
+%%%%%%%%%%%%%%%% optimal parameters from tuning process%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[t!]
+%\scriptsize
+%  \centering
+%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+%	\hline
+%	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default & 
+%ant  & camel &ivy & jedit & log4j & lucene & poi & synapse & velocity & xalan & xerces \\ \hline
+%	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
+%	& threshold & 0.5 & 0.16 & 0.87 &0.89 & 0.68 &0.58 &0.62&0.06&0.09&1&0.64 &0.02\\ \cline{2-14} 
+%	& infogain & 0.33 & 0.33 & 0.49 &1&0.82 &0.12 &0.54&0.38&0.01&1&0.36&0.25\\ \cline{2-14} 
+%	 & min\_sample\_size & 4& 8 &1 &1&5&8&1&5&9&1&5&5\\ \cline{2-14} 
+%	 & min\_Size & 0.5& 1 & 0.67 & 0.99&1&0.63&1&0.95&0.59&1&0.88 &0.64\\ \cline{2-14} 
+%	 & wriggle &
+%	 & depthMin & 2 & 3 & 4 &1&1&2&1&1&5&1&1&3\\ \cline{2-14} 
+%	 & depthMax & 10 & 8 &14 &16&18&1&16&13&5&9&18&20\\ \cline{2-14} 
+%	 & wherePrune & False & True & True &False&False&False&True&True&False&True&False &True\\ \cline{2-14} 
+%	 & treePrune & True& False & True &True&True&False&False&True&False&False&False &False\\ 
+%\hline
+%	\multirow{4}{*}{CART} 
+%	& threshold & 0.5 & 0.01 & 0.98 &0.94&0.67&0.47&1&0.01&0.12&0.9&0.57 &0.01\\ \cline{2-14} 
+%	 & max\_feature & None &0.01 & 1 &0.29&0.28&0.53&0.13&0.01&0.01&0.87&0.47 &0.01\\ \cline{2-14} 
+%	 %& max\_depth & None &27 & 46 &33&21&42&36&39&17&29&11&31\\ \cline{2-14} 
+%	 & min\_sample\_split & 2 &6 &2 &13&17&12&2&14&12&7&16 &13\\ \cline{2-14} 
+%	 & min\_smaples\_leaf & 1 &6 &3 &18&12&3&10&4&20&8&11&1\\ \hline  
+%    \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  
+%    & threshold & 0.5 & 0.06 &0.88 &1&0.73&0.41&0.81&0.11&0.16&1&0.63&0.29\\ \cline{2-14} 
+%	 & max\_feature & None & 0.21 &0.98 &0.78&0.73&0.36&0.35&0.01&0.01&0.01&0.65 &0.89\\ \cline{2-14} 
+%	 & max\_leaf\_nodes & None & 31 &35 &41&40&23&12&26&41&46&49&35\\ \cline{2-14} 
+%	 & min\_sample\_split & 2 &12 &14 &2&5&8&11&1&16&1&9&20\\ \cline{2-14} 
+%	 & min\_smaples\_leaf & 1 &6 &15 &2&17&3&9&19&8&2&14&9\\ \cline{2-14} 
+%	 &  n\_estimators & 100 &111 &120 &89&68&64&84&107&100&79&113&50\\ \hline
+%
+%	\end{tabular}
+%    \caption {Optimal parameters from tuning process with objetive of G measure over different data sets.}
+%\label{fig:parameters}
+%\end{figure*}
+
+%%%%parameters for pd %%%%%%
+\begin{figure*}[!ht]
+\resizebox{\textwidth}{!}{
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
+& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
+& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
+& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
+& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
+& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
+& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
+& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
+& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
+\hline
+\multirow{4}{*}{CART}
+& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
+& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
+& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
+& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
+& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
+& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
+& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of pd}
+\end{figure*}
+
+%%%%parameters for pf %%%%%%
+\begin{figure*}[!ht]
+\resizebox{\textwidth}{!}{
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.53& 0.71& 0.37& 0.23& 0.67& 1& 1& 0.48& 0.97& 0.81& 1& 0.98& 0.92& 0.93& 0.98& 0.5& 0.99\\ \cline{2-20}
+& infoPrune& 0.33& 0.68& 0.97& 0.43& 0.01& 0.22& 1& 0.76& 0.48& 0.61& 0.23& 0.04& 0.92& 0.59& 0.41& 0.88& 0.9& 0.23\\ \cline{2-20}
+& min\_sample\_size& 4& 3& 1& 2& 1& 6& 4& 3& 5& 3& 9& 7& 3& 3& 8& 7& 2& 9\\ \cline{2-20}
+& min\_Size& 0.5& 0.07& 0.03& 0.36& 0.06& 0.21& 0.38& 0.15& 0.19& 0.29& 0.08& 0.35& 0.24& 0.38& 0.67& 0.01& 0.25& 0.58\\ \cline{2-20}
+& wriggle& 0.2& 0.91& 0.97& 0.47& 0.96& 0.82& 0.11& 0.37& 0.37& 0.06& 0.68& 0.23& 0.01& 0.51& 0.79& 0.53& 0.05& 0.08\\ \cline{2-20}
+& depthMin& 2& 4& 1& 3& 3& 1& 1& 3& 4& 2& 3& 3& 1& 1& 1& 1& 3& 1\\ \cline{2-20}
+& depthMax& 10& 10& 15& 7& 4& 14& 3& 15& 16& 15& 18& 6& 6& 5& 18& 10& 6& 16\\ \cline{2-20}
+& wherePrune& False& True& True& False& True& True& True& True& True& True& False& True& True& True& True& True& True& False\\ \cline{2-20}
+& treePrune& True& True& False& True& False& False& True& True& False& False& False& False& True& False& False& False& True& False\\ \cline{2-20}
+\hline
+\multirow{4}{*}{CART}
+& threshold& 0.5& 1& 1& 0.96& 0.88& 1& 1& 0.99& 0.88& 1& 0.83& 1& 1& 0.92& 0.9& 1& 1& 1\\ \cline{2-20}
+& max\_feature& None& 0.01& 1& 0.93& 0.58& 0.01& 0.73& 1& 0.44& 0.01& 0.88& 0.01& 0.38& 0.48& 0.65& 0.86& 0.28& 0.01\\ \cline{2-20}
+& min\_samples\_split& 2& 4& 4& 18& 3& 14& 19& 14& 16& 19& 12& 6& 2& 9& 8& 3& 6& 16\\ \cline{2-20}
+& min\_samples\_leaf& 1& 12& 16& 19& 18& 1& 2& 5& 8& 8& 1& 10& 6& 12& 12& 13& 3& 10\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.89& 0.58& 0.88& 0.86& 1& 1& 1& 1& 1& 1& 1& 1& 0.78& 0.73& 1& 1& 0.93\\ \cline{2-20}
+& max\_feature& None& 0.47& 0.04& 0.12& 0.38& 0.96& 0.87& 0.11& 0.01& 1& 0.16& 0.85& 0.99& 0.78& 0.77& 0.01& 0.35& 0.23\\ \cline{2-20}
+& max\_leaf\_nodes& None& 35& 37& 38& 23& 13& 34& 36& 29& 10& 10& 10& 10& 33& 49& 50& 24& 37\\ \cline{2-20}
+& min\_samples\_split& 2& 18& 10& 5& 16& 1& 20& 2& 1& 10& 5& 11& 5& 16& 4& 5& 19& 19\\ \cline{2-20}
+& min\_samples\_leaf& 1& 16& 11& 6& 13& 2& 4& 2& 2& 2& 19& 6& 2& 4& 14& 2& 3& 18\\ \cline{2-20}
+& n\_estimators& 100& 103& 95& 76& 88& 68& 88& 136& 90& 144& 115& 150& 99& 110& 114& 53& 108& 99\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of pf}
+\end{figure*}
+
+%%%%parameters for prec %%%%%%
+\begin{figure*}[!ht]
+\resizebox{\textwidth}{!}{
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.53& 0.48& 0.41& 0.35& 0.88& 1& 1& 0.9& 0.96& 0.57& 1& 1& 0.56& 0.57& 0.8& 0.26& 0.65\\ \cline{2-20}
+& infoPrune& 0.33& 0.68& 0.74& 0.31& 0.45& 0.78& 0.31& 0.53& 0.85& 0.04& 0.73& 0.54& 0.15& 1& 0.98& 0.23& 0.9& 0.19\\ \cline{2-20}
+& min\_sample\_size& 4& 3& 6& 5& 2& 1& 5& 7& 1& 7& 5& 2& 8& 1& 1& 1& 2& 2\\ \cline{2-20}
+& min\_Size& 0.5& 0.07& 0.23& 0.2& 0.21& 0.25& 0.54& 0.18& 0.36& 0.28& 0.51& 1.0& 0.33& 0.5& 0.84& 0.83& 0.04& 0.21\\ \cline{2-20}
+& wriggle& 0.2& 0.91& 0.77& 0.58& 0.85& 0.17& 0.66& 0.33& 0.88& 0.13& 0.72& 0.18& 0.07& 0.43& 0.63& 0.74& 0.18& 0.75\\ \cline{2-20}
+& depthMin& 2& 4& 2& 5& 2& 4& 2& 2& 2& 4& 2& 3& 4& 1& 5& 1& 2& 1\\ \cline{2-20}
+& depthMax& 10& 10& 14& 6& 13& 7& 16& 15& 14& 13& 19& 16& 9& 16& 14& 11& 13& 15\\ \cline{2-20}
+& wherePrune& False& True& False& True& True& True& True& True& True& True& True& True& True& True& True& False& True& False\\ \cline{2-20}
+& treePrune& True& True& True& True& True& True& True& False& False& False& True& False& True& True& False& False& False& False\\ \cline{2-20}
+\hline
+\multirow{4}{*}{CART}
+& threshold& 0.5& 0.76& 0.99& 0.86& 0.48& 1& 1& 1& 0.71& 0.62& 0.65& 1& 0.95& 0.64& 0.5& 1& 0.99& 1\\ \cline{2-20}
+& max\_feature& None& 0.09& 0.13& 0.05& 0.01& 0.01& 0.47& 0.01& 0.1& 0.63& 0.62& 0.44& 0.27& 0.28& 0.04& 0.75& 0.96& 0.21\\ \cline{2-20}
+& min\_samples\_split& 2& 4& 19& 9& 9& 17& 14& 14& 16& 14& 12& 17& 3& 10& 12& 20& 13& 6\\ \cline{2-20}
+& min\_samples\_leaf& 1& 15& 17& 8& 7& 1& 20& 1& 9& 12& 15& 10& 13& 7& 10& 4& 7& 20\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.92& 0.99& 0.71& 0.7& 1& 0.82& 1& 1& 1& 0.96& 0.73& 1& 0.76& 0.33& 1& 1& 0.98\\ \cline{2-20}
+& max\_feature& None& 0.23& 0.13& 0.46& 0.69& 0.37& 0.56& 0.71& 0.01& 1& 0.01& 0.85& 0.48& 0.34& 0.02& 0.01& 0.08& 0.62\\ \cline{2-20}
+& max\_leaf\_nodes& None& 12& 49& 23& 39& 10& 17& 20& 10& 10& 44& 37& 18& 35& 11& 31& 35& 28\\ \cline{2-20}
+& min\_samples\_split& 2& 18& 8& 14& 1& 11& 3& 2& 1& 4& 14& 2& 1& 13& 8& 18& 2& 13\\ \cline{2-20}
+& min\_samples\_leaf& 1& 11& 5& 11& 3& 2& 4& 20& 2& 2& 10& 3& 7& 7& 15& 6& 2& 9\\ \cline{2-20}
+& n\_estimators& 100& 130& 146& 66& 96& 50& 50& 136& 84& 83& 129& 51& 150& 99& 58& 88& 85& 61\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of prec}
+\end{figure*}
+
+%%%%parameters for F %%%%%%
+\begin{figure*}[!ht]
+\resizebox{\textwidth}{!}{
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.12& 0.78& 0.3& 0.01& 0.78& 1& 0.99& 0.44& 0.72& 0.21& 0.41& 1& 0.04& 0.7& 0.36& 0.66& 0.42\\ \cline{2-20}
+& infoPrune& 0.33& 0.58& 0.2& 0.41& 0.19& 0.82& 0.91& 0.35& 1& 0.85& 0.46& 0.24& 1.0& 0.85& 0.36& 0.48& 0.42& 0.82\\ \cline{2-20}
+& min\_sample\_size& 4& 6& 1& 1& 6& 8& 6& 7& 5& 1& 5& 8& 2& 7& 5& 3& 1& 1\\ \cline{2-20}
+& min\_Size& 0.5& 0.8& 0.75& 0.47& 0.01& 1& 0.64& 0.99& 0.43& 0.23& 0.47& 0.72& 1& 0.89& 0.69& 0.88& 0.38& 0.75\\ \cline{2-20}
+& wriggle& 0.2& 0.21& 0.7& 0.83& 0.25& 0.55& 0.01& 0.63& 0.93& 0.43& 0.33& 0.52& 0.32& 0.72& 0.1& 0.43& 0.34& 0.1\\ \cline{2-20}
+& depthMin& 2& 4& 5& 4& 3& 1& 6& 1& 4& 1& 1& 4& 1& 2& 2& 4& 5& 1\\ \cline{2-20}
+& depthMax& 10& 16& 11& 5& 19& 8& 10& 14& 19& 5& 6& 6& 16& 3& 11& 5& 18& 12\\ \cline{2-20}
+& wherePrune& False& True& True& True& False& True& False& False& True& True& True& False& True& True& False& True& False& True\\ \cline{2-20}
+& treePrune& True& False& True& True& True& True& False& False& True& False& False& False& True& True& False& False& True& True\\ \cline{2-20}
+\hline
+\multirow{4}{*}{CART}
+& threshold& 0.5& 0.01& 0.62& 0.13& 0.01& 1& 0.8& 0.7& 0.66& 0.72& 0.32& 0.09& 0.7& 0.01& 0.01& 0.91& 0.84& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.24& 0.88& 0.19& 0.01& 0.01& 0.8& 0.76& 0.28& 0.5& 0.22& 0.18& 0.01& 0.58& 0.01& 0.01& 0.3& 0.01\\ \cline{2-20}
+& min\_samples\_split& 2& 19& 3& 13& 5& 2& 10& 8& 9& 11& 12& 7& 10& 20& 5& 4& 14& 11\\ \cline{2-20}
+& min\_samples\_leaf& 1& 15& 18& 11& 13& 3& 13& 9& 10& 15& 8& 15& 15& 7& 10& 10& 4& 1\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.01& 0.49& 0.14& 0.01& 1& 1& 1& 1& 1& 0.66& 0.53& 1& 0.01& 0.21& 1& 1& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.89& 0.21& 0.01& 0.04& 0.81& 0.45& 0.01& 0.49& 0.01& 0.01& 0.12& 0.81& 0.01& 0.07& 0.01& 0.62& 0.61\\ \cline{2-20}
+& max\_leaf\_nodes& None& 21& 16& 49& 10& 26& 32& 39& 22& 10& 42& 24& 43& 38& 10& 10& 10& 20\\ \cline{2-20}
+& min\_samples\_split& 2& 11& 9& 19& 15& 6& 14& 6& 3& 4& 10& 18& 2& 8& 7& 10& 10& 16\\ \cline{2-20}
+& min\_samples\_leaf& 1& 6& 11& 13& 7& 16& 4& 2& 18& 2& 6& 19& 2& 9& 4& 17& 2& 5\\ \cline{2-20}
+& n\_estimators& 100& 88& 99& 124& 148& 56& 101& 116& 55& 122& 112& 75& 55& 92& 129& 58& 107& 121\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of F}
+\end{figure*}
+
+%%%%parameters for G %%%%%%
+\begin{figure*}[!ht]
+\resizebox{\textwidth}{!}{
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.16& 0.44& 0.07& 0.01& 0.5& 0.9& 0.75& 0.5& 0.7& 0.38& 0.68& 1& 0.01& 0.15& 1.0& 0.84& 0.01\\ \cline{2-20}
+& infoPrune& 0.33& 0.54& 1.0& 0.07& 0.55& 0.79& 0.74& 0.36& 0.47& 0.65& 0.27& 0.69& 0.9& 0.73& 0.44& 0.73& 0.87& 0.01\\ \cline{2-20}
+& min\_sample\_size& 4& 8& 9& 1& 9& 1& 5& 7& 1& 8& 5& 2& 1& 3& 4& 3& 1& 6\\ \cline{2-20}
+& min\_Size& 0.5& 0.76& 0.71& 0.91& 0.42& 0.63& 0.64& 0.88& 0.45& 1& 0.92& 0.94& 0.9& 0.4& 0.55& 0.68& 0.49& 0.65\\ \cline{2-20}
+& wriggle& 0.2& 0.57& 0.11& 0.79& 1& 0.5& 0.25& 0.51& 0.28& 0.46& 0.06& 0.61& 0.28& 0.01& 0.61& 0.57& 0.65& 0.02\\ \cline{2-20}
+& depthMin& 2& 4& 1& 1& 6& 4& 2& 2& 3& 3& 1& 1& 6& 1& 4& 2& 5& 2\\ \cline{2-20}
+& depthMax& 10& 8& 6& 4& 9& 9& 18& 4& 10& 6& 6& 7& 20& 9& 16& 14& 19& 6\\ \cline{2-20}
+& wherePrune& False& True& True& True& False& True& True& True& True& True& True& True& True& True& False& False& True& True\\ \cline{2-20}
+& treePrune& True& True& False& True& False& False& False& False& False& True& False& False& False& True& True& True& False& True\\ \cline{2-20}
+\hline
+\multirow{4}{*}{CART}
+& threshold& 0.5& 0.17& 0.47& 0.01& 0.01& 0.88& 0.59& 0.98& 0.49& 0.45& 0.99& 0.69& 1& 0.01& 0.01& 0.95& 0.69& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.01& 0.28& 0.61& 0.01& 0.87& 0.98& 0.77& 0.83& 0.01& 0.6& 0.01& 0.78& 0.29& 0.01& 0.81& 0.72& 1\\ \cline{2-20}
+& min\_samples\_split& 2& 18& 17& 12& 2& 2& 18& 3& 10& 15& 12& 2& 10& 18& 9& 8& 10& 13\\ \cline{2-20}
+& min\_samples\_leaf& 1& 11& 18& 14& 15& 1& 10& 2& 18& 12& 20& 7& 1& 1& 11& 9& 1& 1\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.35& 0.42& 0.17& 0.01& 0.78& 1& 0.86& 0.39& 0.71& 0.42& 0.87& 1& 0.06& 0.06& 1& 1& 0.2\\ \cline{2-20}
+& max\_feature& None& 0.13& 0.98& 0.01& 0.36& 0.53& 0.79& 0.98& 1& 0.01& 0.12& 0.75& 0.82& 0.79& 0.64& 0.01& 0.71& 0.8\\ \cline{2-20}
+& max\_leaf\_nodes& None& 13& 22& 42& 18& 10& 43& 23& 37& 49& 47& 15& 10& 45& 16& 36& 13& 39\\ \cline{2-20}
+& min\_samples\_split& 2& 9& 8& 13& 1& 10& 14& 10& 1& 1& 4& 6& 1& 5& 14& 1& 8& 12\\ \cline{2-20}
+& min\_samples\_leaf& 1& 3& 14& 15& 2& 17& 6& 5& 2& 14& 2& 9& 3& 18& 16& 2& 2& 4\\ \cline{2-20}
+& n\_estimators& 100& 107& 131& 114& 125& 138& 138& 57& 84& 50& 58& 83& 70& 83& 121& 150& 150& 132\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of G}
+\end{figure*}
+
+%%%%%%%%%%%%%%%% defectives and non-defectives for each datasets%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c c c c c c c c c c }
+  \hline\hline
+  Dataset &ant&antV1&antV2&camel&camelV1&ivy&jedit&jeditV1&jeditV2
+\\\hline
+  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
+\\  tunning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
+\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
+\\  \end{tabular}
+   \caption{The percentage of defective instances in each experimental data set. For each experiment,  training, tuning and testing data are composed of single chronological data file}
+\end{figure*}
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c c c c c c c c c c }
+  \hline\hline
+  Dataset &log4j&lucene&poi&poiV1&synapse&velocity&xerces&xercesV1
+\\\hline
+  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
+\\  tunning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
+\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
+\\  \end{tabular}
+
+   \caption{The percentage of defective instances in each experimental data set. For each experiment,  training, tuning and testing data are composed of single chronological data file}
+\end{figure*}
+
+%\begin{figure*}[!th]
+%  \scriptsize
+%  \centering
+%		\begin{tabular}{|l|l|l|}
+%		\hline
+%		\multicolumn{1}{|c|}{Data Set} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}} Feature Selections\\ with  Default Parameters\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Feature Selection\\ with Tuning Parameters\end{tabular}} \\ \hline
+%	   ant  & mfa, lcom3, cam, ic, dam   & wmc, lcom3, cam, dam, npm, rfc  \\ \hline
+%		camel & cam, wmc, dit, mfa, rfc, loc & rfc, cam, loc, wmc, dam, dit, mfa, lcom3, npm\\ \hline
+%		ivy & cam, dit, dam, ic, lcom3& cam, dam, mfa\\ \hline
+%		jedit& mfa, dam, cam, dit, cbm, ic& mfa, loc, dit, dam, cam, wmc  \\ \hline
+%		log4j & lcom3, mfa, loc, ic, dit& mfa, wmc  \\ \hline
+%		lucene & mfa, lcom3, cam, dam, ic& wmc, lcom3, avg\_cc, rfc, ce, mfa, dam, npm, cam \\ \hline
+%		poi & mfa, dam, amc, lcom3, cbm, loc& loc, lcom3, cam, amc, dam                                                     \\ \hline
+%		synapse & dam, loc, mfa, cam & loc  \\ \hline
+%		velocity& dit, dam, lcom3, ic, mfa& mfa, cam, avg\_cc, loc, lcom3, cbo, dam, ic, rfc, lcom \\ \hline
+%		xalan  & mfa, cam, wmc, lcom3, rfc, dit & mfa, rfc, loc, dam, lcom3, wmc, npm \\ \hline
+%		xerces & cam, wmc, mfa, rfc, amc, loc& mfa, loc, cam, amc, avg\_cc\\ \hline
+%		\end{tabular}
+%		\caption{Features selection before and after tuning over objective of G values }
+%\end{figure*}
+
+%%%%%%%%%%%%%%%% feature selection over pd%%%%%%%%%%%%%%%%%%%%%
+
+\setlength{\tabcolsep}{3pt}
+\renewcommand\arraystretch{1.2}
+
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
+  \hline\hline
+  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
+\\\hline
+  npm& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+loc& & & $\star$& & & & $\star$& & $\star$& & & & & & & & & & $\star$& & & & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& $\circ$\\
+amc& & & & & & & & & & & & & & & & & & & & & & & $\star$& & $\star$& & & & & & $\star$& & $\star$& \\
+max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+lcom& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+dam& $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & \\
+ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+cbo& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+ce& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+rfc& & & & & & & $\star$& & $\star$& & & & & & & & & & & & & & $\star$& & & & & & & & & & $\star$& \\
+dit& & & $\star$& & & & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & & & & & & & & $\star$& $\circ$& & & & \\
+mfa& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & $\star$& \\
+cam& & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & & & $\star$& & & & $\star$& & & & & & $\star$& & & & $\star$& & $\star$& \\
+avg\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+wmc& $\star$& & $\star$& & & & & & $\star$& & & & & & & & & & & & & & $\star$& & & & & & & & & & $\star$& \\
+moa& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+cbm& & & & & & & & & & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & & & $\star$& & & & $\star$& & & & & \\
+ic& $\star$& & & & $\star$& & & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & & & & & & & $\star$& $\circ$& & & & \\
+lcom3& & & & & $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& & & & $\star$& & & & $\star$& & & & & \\
+
+  \end{tabular}
+    \caption{Feature seleciton for different datasets with  and without the tuning process over the objective of pd.
+For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.
+ }
+\end{figure*}
+
+%%%%%%%%%%%%%% pd bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\renewcommand{\baselinestretch}{0.5} 
+\scriptsize
+\begin{minipage}{0.81\linewidth}
+\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
+  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(pd) } \\
+  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
+\multicolumn{1}{c}{~}\\
+antV0 & 53 & {\rone} & 100 & {\rfour} & 38 &         & 100 & {\rfour} & 78 & {\rthree} & 97 & {\rfour}\\
+antV1 & 7 &         & 100 & {\rfour} & 39 & {\rone} & 100 & {\rfour} & 95 & {\rfour} & 100 & {\rfour}\\
+antV2 & 0 &         & 100 & {\rfour} & 37 & {\rone} & 100 & {\rfour} & 92 & {\rfour} & 100 & {\rfour}\\
+camelV0 & 0 &         & 100 & {\rfour} & 6 &         & 100 & {\rfour} & 66 & {\rthree} & 99 & {\rfour}\\
+camelV1 & 80 & {\rthree} & 100 & {\rfour} & 46 &         & 100 & {\rfour} & 80 & {\rthree} & 100 & {\rfour}\\
+ivyV0 & 93 & {\rtwo} & 100 & {\rfour} & 88 &         & 100 & {\rfour} & 95 & {\rtwo} & 100 & {\rfour}\\
+jeditV0 & 89 & {\rthree} & 100 & {\rfour} & 66 &         & 95 & {\rfour} & 96 & {\rfour} & 100 & {\rfour}\\
+jeditV1 & 75 & {\rtwo} & 100 & {\rfour} & 50 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
+jeditV2 & 45 &         & 100 & {\rfour} & 36 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
+log4jV0 & 46 & {\rone} & 100 & {\rfour} & 31 &         & 100 & {\rfour} & 88 & {\rfour} & 100 & {\rfour}\\
+luceneV0 & 81 & {\rthree} & 100 & {\rfour} & 48 &         & 100 & {\rfour} & 98 & {\rfour} & 100 & {\rfour}\\
+poiV0 & 89 & {\rtwo} & 100 & {\rfour} & 79 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
+poiV1 & 2 &         & 100 & {\rfour} & 12 &         & 100 & {\rfour} & 89 & {\rfour} & 100 & {\rfour}\\
+synapseV0 & 0 &         & 100 & {\rfour} & 28 & {\rone} & 100 & {\rfour} & 90 & {\rfour} & 100 & {\rfour}\\
+velocityV0 & 100 & {\rfour} & 100 & {\rfour} & 86 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
+xercesV0 & 64 & {\rone} & 100 & {\rfour} & 46 &         & 100 & {\rfour} & 78 & {\rtwo} & 91 & {\rfour}\\
+xercesV1 & 15 &         & 100 & {\rfour} & 11 &         & 100 & {\rfour} & 68 & {\rthree} & 87 & {\rfour}\\
+%Albrecht  &   7         &   24   &   Projects from IBM   & 28 &     & 40 & {\rtwo} & 38 & {\rtwo} & 38 & {\rtwo} & 49 & {\rfour} \\
+%China      &   18       &   488   &   Projects from Chinese software companies   &   38   &  {\rtwo}  &   34   &       &   34   &       &   35   &  {\rone}   &   41   &   {\rfour}\\
+%Cosmic     &   y   &   y   &   Projects described in functiion points   &   98   &   {\rfour}   &   75   &       &   85   &    {\rtwo}   &   85   &   {\rtwo}    &   89   &   {\rtwo}\\
+%ISBSG10    &   y   &   y   &   From the ISBSG benchmark suite   &   56   &       &   62   &     &   126   &   {\rfour}   &   66   &   {\rone}   &   65   &   {\rone}\\
+%Kemerer    &   7   &   15   &   Large business applications   &   42   &  {\rtwo}  &   24   &   &   55   &  {\rfour} &   55   &   {\rfour}   &   55   &   {\rfour}\\
+%Kitchenham &    6   &   145   &  y    &   34   &   &   43   &   {\rthree}   &   34   &  &   43   &  {\rthree}  &   47   &  {\rfour}  \\
+%Maxwell    &   27  &   62  & Projects from commercial banks in Finland   &   57   &   {\rtwo}   &   56   &   {\rtwo}   &   47   &   &   53   &  {\rone} &   64   &   {\rfour}\\
+%Miyazaki   &   8   &   48 &Japanese software projects developed in COBOL   &   39   &       &   41   &   &   41   &    &   57   &   {\rfour}   &   57   &   {\rfour}\\
+%Telecom    &   3   &   18   &   Maintenance projects for telecom companies   &   23   &       &   26   &   {\rtwo}   &   31   & {\rfour}  &   31   &   {\rfour}   &   31   &   {\rfour}\\
+%Usp05      &   7   &  203  &  Collected from university student projects   &   30   &    &   50   & {\rfour} &   45   & {\rthree}  &   40   &   {\rtwo}  &   50   &   {\rfour}\\
+\end{tabular}
+\end{minipage}\begin{minipage}{.15\linewidth}
+\begin{tabular}{|p{\linewidth}|}\hline
+
+~\\
+
+{\bf KEY:}
+
+~\\
+
+pd percentile ranges:
+
+~\\
+
+80th to 100th = {\rfour}
+
+60th to 80th ~ = {\rthree}
+
+40th to 60th  ~ = {\rtwo}
+
+20th to 40th  ~ = {\rone}
+
+~\\
+
+An absent bar denotes\newline 0th to 20th percentile.
+
+~\\
+
+Percentiles computed  separately
+for each data set.\\\hline
+\end{tabular}
+\end{minipage}
+\caption{Median pd values in tune once and test ten times experiment. 
+Gray bars  show  pd values
+discretized into 20th percentiles ranges from min to max.
+All data available from http://openscience.us/repo/effort.
+}\label{fig:nonc}
+\end{figure*}
+
+%%%%%%%%%%%%%% pd bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%% features selection over pf%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
+  \hline\hline
+  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
+\\\hline
+  npm& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+loc& & & $\star$& & & & $\star$& & $\star$& & & $\circ$& & & & & & $\circ$& $\star$& & & & & & $\star$& & $\star$& $\circ$& & & $\star$& & $\star$& $\circ$\\
+amc& & & & & & & & & & & & & & & & & & & & & & & $\star$& & $\star$& & & & & & $\star$& & $\star$& \\
+max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+lcom& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
+dam& $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& & & $\star$& & $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& & & \\
+ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+cbo& & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & & & \\
+ce& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+rfc& & & & & & & $\star$& & $\star$& & & & & & & & & & & & & & $\star$& $\circ$& & & & $\circ$& & & & & $\star$& $\circ$\\
+dit& & & $\star$& & & $\circ$& & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & & & & & $\circ$& & & $\star$& & & & & \\
+mfa& $\star$& & $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& & & & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$\\
+cam& & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & & & $\star$& & & & $\star$& & & & & & $\star$& $\circ$& & & $\star$& & $\star$& $\circ$\\
+avg\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+wmc& $\star$& & $\star$& & & & & & $\star$& & & & & & & & & & & & & & $\star$& & & & & $\circ$& & & & & $\star$& \\
+moa& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+cbm& & & & & & & & & & & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& & & & & & & $\star$& $\circ$& & & $\star$& & & & & \\
+ic& $\star$& & & & $\star$& & & & & & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & & & $\circ$& & & $\star$& & & & & \\
+lcom3& & & & & $\star$& & $\star$& & & & & & $\star$& & $\star$& & & $\circ$& $\star$& & $\star$& & & & $\star$& & & $\circ$& $\star$& & & & & \\
+
+  \end{tabular}
+      \caption{Feature seleciton for different datasets with  and without the tuning process over the objective of pf.
+For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.
+ }
+\end{figure*}
+
+%%%%%%%%%%%%%% pf bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure*}
+\renewcommand{\baselinestretch}{0.5} 
+\scriptsize
+\begin{minipage}{0.81\linewidth}
+\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
+  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(pf) } \\
+  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
+\multicolumn{1}{c}{~}\\
+antV0 & 15 &       & 0 & {\rfour} & 12 & {\rone} & 0 & {\rfour} & 9 & {\rtwo} & 0 & {\rfour}\\
+antV1 & 5 & {\rthree} & 0 & {\rfour} & 20 &       & 0 & {\rfour} & 14 & {\rone} & 0 & {\rfour}\\
+antV2 & 0 & {\rfour} & 0 & {\rfour} & 10 &       & 0 & {\rfour} & 2 & {\rfour} & 0 & {\rfour}\\
+camelV0 & 0 & {\rfour} & 0 & {\rfour} & 3 &       & 0 & {\rfour} & 0 & {\rfour} & 0 & {\rfour}\\
+camelV1 & 69 &       & 0 & {\rfour} & 36 & {\rtwo} & 20 & {\rthree} & 26 & {\rthree} & 18 & {\rthree}\\
+ivyV0 & 63 &       & 0 & {\rfour} & 50 & {\rone} & 34 & {\rtwo} & 42 & {\rone} & 40 & {\rone}\\
+jeditV0 & 56 &       & 0 & {\rfour} & 24 & {\rtwo} & 0 & {\rfour} & 23 & {\rtwo} & 24 & {\rtwo}\\
+jeditV1 & 35 &       & 0 & {\rfour} & 20 & {\rtwo} & 1 & {\rfour} & 17 & {\rtwo} & 14 & {\rthree}\\
+jeditV2 & 46 &       & 0 & {\rfour} & 31 & {\rone} & 3 & {\rfour} & 21 & {\rtwo} & 16 & {\rthree}\\
+log4jV0 & 31 &       & 0 & {\rfour} & 13 & {\rtwo} & 0 & {\rfour} & 0 & {\rfour} & 0 & {\rfour}\\
+luceneV0 & 76 &       & 0 & {\rfour} & 35 & {\rtwo} & 24 & {\rthree} & 30 & {\rthree} & 21 & {\rthree}\\
+poiV0 & 70 &       & 0 & {\rfour} & 38 & {\rtwo} & 32 & {\rtwo} & 34 & {\rtwo} & 34 & {\rtwo}\\
+poiV1 & 0 & {\rfour} & 0 & {\rfour} & 8 &       & 0 & {\rfour} & 0 & {\rfour} & 0 & {\rfour}\\
+synapseV0 & 0 & {\rfour} & 0 & {\rfour} & 6 &       & 0 & {\rfour} & 1 & {\rfour} & 0 & {\rfour}\\
+velocityV0 & 99 &       & 0 & {\rfour} & 85 &       & 43 & {\rtwo} & 63 & {\rone} & 54 & {\rtwo}\\
+xercesV0 & 74 &       & 0 & {\rfour} & 52 & {\rone} & 1 & {\rfour} & 40 & {\rtwo} & 43 & {\rtwo}\\
+xercesV1 & 36 &       & 0 & {\rfour} & 26 & {\rone} & 0 & {\rfour} & 19 & {\rtwo} & 0 & {\rfour}\\
+\end{tabular}
+\end{minipage}\begin{minipage}{.15\linewidth}
+\begin{tabular}{|p{\linewidth}|}\hline
+
+~\\
+
+{\bf KEY:}
+
+~\\
+
+pf percentile ranges:
+
+~\\
+
+80th to 100th = {\rfour}
+
+60th to 80th ~ = {\rthree}
+
+40th to 60th  ~ = {\rtwo}
+
+20th to 40th  ~ = {\rone}
+
+~\\
+
+An absent bar denotes\newline 0th to 20th percentile.
+
+~\\
+
+Percentiles computed  separately
+for each data set.\\\hline
+\end{tabular}
+\end{minipage}
+\caption{Median pf values in tune once and test ten times experiment. 
+Gray bars  show  pf values
+discretized into 20th percentiles ranges from min to max.
+All data available from http://openscience.us/repo/effort.
+}\label{fig:nonc}
+\end{figure*}
+
+%%%%%%%%%%%%%% pf bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%% features selection over precision%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
+  \hline\hline
+  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
+\\\hline
+  npm& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & $\circ$& & & & & & \\
+loc& & & $\star$& & & & $\star$& & $\star$& & & & & & & $\circ$& & & $\star$& $\circ$& & & $\star$& & $\star$& $\circ$& $\star$& $\circ$& & & $\star$& & $\star$& \\
+amc& & & & & & & & & & & & & & & & & & & & & & & $\star$& & $\star$& $\circ$& & & & & $\star$& & $\star$& \\
+max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
+lcom& & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & & & \\
+dam& $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& & & \\
+ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
+cbo& & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & & & \\
+ce& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & $\circ$& & $\circ$& & & & & & \\
+noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+rfc& & & & & & & $\star$& & $\star$& & & & & & & & & & & & & $\circ$& $\star$& & & $\circ$& & $\circ$& & $\circ$& & & $\star$& \\
+dit& & & $\star$& & & & & & $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& & & & $\circ$& & & & $\circ$& $\star$& & & & & \\
+mfa& $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& \\
+cam& & & & & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& & & & & $\star$& & & & $\star$& $\circ$& & & & $\circ$& $\star$& & & & $\star$& & $\star$& \\
+avg\_cc& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & $\circ$& & $\circ$& & & & & & \\
+wmc& $\star$& & $\star$& & & & & & $\star$& & & & & & & & & & & & & $\circ$& $\star$& & & $\circ$& & $\circ$& & & & & $\star$& \\
+moa& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
+cbm& & & & & & & & & & & & & $\star$& & $\star$& & $\star$& & & & & & & & $\star$& & & & & $\circ$& & & & \\
+ic& $\star$& & & & $\star$& & & & & & $\star$& $\circ$& $\star$& & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & & & & & & $\star$& $\circ$& & & & \\
+lcom3& & & & & $\star$& & $\star$& & & & & $\circ$& $\star$& & $\star$& & & & $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& & $\circ$& $\star$& & & & & \\
+
+  \end{tabular}
+  \caption{Feature seleciton for different datasets with and without the tuning process over the objective of precision.
+For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.}
+\end{figure*}
+
+%%%%%%%%%%%%%% precision bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\renewcommand{\baselinestretch}{0.5} 
+\scriptsize
+\begin{minipage}{0.81\linewidth}
+\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
+  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(precision) } \\
+  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
+\multicolumn{1}{c}{~}\\
+antV0 & 30 &         & $\bigstar$ 89 & {\rfour} & 27 &         &$\bigstar$ 89 & {\rfour} & 40 & {\rone} &$\bigstar$ 89 & {\rfour}\\
+antV1 & 32 &         &$\bigstar$ 74 & {\rfour} & 41 & {\rone} &$\bigstar$ 74 & {\rfour} & 57 & {\rtwo} &$\bigstar$ 74 & {\rfour}\\
+antV2 & 78 & {\rfour} &$\bigstar$ 78 & {\rfour} & 52 &         & 67 & {\rthree} & 66 & {\rtwo} & 50 &        \\
+camelV0 &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour} & 26 &         & 37 &         &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour}\\
+camelV1 & 22 &         &$\bigstar$ 81 & {\rfour} & 23 &         & 25 &         & 28 &         & 28 &        \\
+ivyV0 & 16 &         & 23 & {\rthree} & 18 & {\rone} &$\bigstar$ 25 & {\rfour} & 18 & {\rone} & 19 & {\rone}\\
+jeditV0 & 35 &         & 75 & {\rthree} & 49 & {\rone} &$\bigstar$ 86 & {\rfour} & 52 & {\rone} & 50 & {\rone}\\
+jeditV1 & 24 &         &$\bigstar$ 87 & {\rfour} & 28 &         & 62 & {\rthree} & 36 &         & 42 & {\rone}\\
+jeditV2 & 2 &         &$\bigstar$ 98 & {\rfour} & 3 &         & 4 &         & 5 &         & 6 &        \\
+log4jV0 & 94 &         &$\bigstar$100 & {\rfour} & 97 & {\rtwo} & 98 & {\rthree} &$\bigstar$ 100 & {\rfour} &$\bigstar$100 & {\rfour}\\
+luceneV0 & 61 &         & 71 & {\rtwo} & 67 & {\rone} &$\bigstar$ 78 & {\rfour} & 69 & {\rtwo} & 70 & {\rtwo}\\
+poiV0 & 70 &         &$\bigstar$ 92 & {\rfour} & 77 & {\rone} & 79 & {\rtwo} & 79 & {\rtwo} & 75 & {\rone}\\
+poiV1 & 100 & {\rfour} &$\bigstar$ 89 & {\rfour} & 73 & {\rtwo} &$\bigstar$ 89 & {\rfour} & 86 & {\rthree} & 36 &        \\
+synapseV0 & 66 & {\rthree} & 0 &         & 71 & {\rthree} &$\bigstar$ 95 & {\rfour} & 59 & {\rthree} & 67 & {\rthree}\\
+velocityV0 & 34 &         & 34 &         & 34 &         &$\bigstar$ 45 & {\rfour} & 40 & {\rtwo} & 41 & {\rthree}\\
+xercesV0 & 13 &         &$\bigstar$ 85 & {\rfour} & 14 &         & 73 & {\rfour} & 16 &         & 13 &        \\
+xercesV1 &$\bigstar$ 56 & {\rfour} & 26 &         & 55 & {\rfour} & 26 &         & 41 & {\rtwo} & 26 &        \\
+\end{tabular}
+\end{minipage}\begin{minipage}{.15\linewidth}
+\begin{tabular}{|p{\linewidth}|}\hline
+
+~\\
+
+{\bf KEY:}
+
+~\\
+
+precision percentile ranges:
+
+~\\
+
+80th to 100th = {\rfour}
+
+60th to 80th ~ = {\rthree}
+
+40th to 60th  ~ = {\rtwo}
+
+20th to 40th  ~ = {\rone}
+
+~\\
+
+An absent bar denotes\newline 0th to 20th percentile.
+
+~\\
+
+Percentiles computed  separately
+for each data set.\\\hline
+\end{tabular}
+\end{minipage}
+\caption{Median precision values in tune once and test ten times experiment. 
+Gray bars  show  precision values
+discretized into 20th percentiles ranges from min to max.
+All data available from http://openscience.us/repo/effort.
+}\label{fig:nonc}
+\end{figure*}
+
+%%%%%%%%%%%%%% precision bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%% features selection over F%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
+  \hline\hline
+  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
+\\\hline
+  npm& & & & $\circ$& & & & & & & & $\circ$& & & & & & & & & & & & $\circ$& & & & & & $\circ$& & & & \\
+loc& & & $\star$& & & & $\star$& & $\star$& & & & & $\circ$& & $\circ$& & $\circ$& $\star$& & & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$\\
+amc& & & & & & $\circ$& & & & & & $\circ$& & & & & & & & & & & $\star$& $\circ$& $\star$& & & & & & $\star$& $\circ$& $\star$& $\circ$\\
+max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+lcom& & $\circ$& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & $\circ$& & $\circ$& & & & \\
+dam& $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& & $\circ$\\
+ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+cbo& & $\circ$& & & & & & & & & & $\circ$& & & & & & & & & & & & $\circ$& & & & & & & & & & \\
+ce& & $\circ$& & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & \\
+noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+rfc& & $\circ$& & & & & $\star$& & $\star$& $\circ$& & $\circ$& & $\circ$& & $\circ$& & & & $\circ$& & & $\star$& & & & & $\circ$& & & & $\circ$& $\star$& $\circ$\\
+dit& & & $\star$& & & $\circ$& & & $\star$& & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& & $\circ$& & $\circ$& & $\circ$& & & & & $\star$& & & $\circ$& & $\circ$\\
+mfa& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$\\
+cam& & $\circ$& & & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& & & & $\circ$& $\star$& & & & $\star$& & & & & $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& \\
+avg\_cc& & & & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & $\circ$\\
+wmc& $\star$& & $\star$& $\circ$& & & & & $\star$& $\circ$& & $\circ$& & & & $\circ$& & & & & & & $\star$& $\circ$& & & & & & $\circ$& & & $\star$& $\circ$\\
+moa& & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & & & & & \\
+cbm& & & & & & $\circ$& & & & & & & $\star$& & $\star$& & $\star$& & & & & & & & $\star$& & & & & & & & & $\circ$\\
+ic& $\star$& $\circ$& & & $\star$& $\circ$& & & & & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & & & & & & & $\star$& $\circ$& & & & $\circ$\\
+lcom3& & & & $\circ$& $\star$& $\circ$& $\star$& & & $\circ$& & $\circ$& $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& & $\circ$& & $\circ$\\
+
+  \end{tabular}
+    \caption{Feature seleciton for different datasets with and without the tuning process over the objective of F measure.
+For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.}
+\end{figure*}
+
+\begin{figure*}
+\renewcommand{\baselinestretch}{0.5} 
+\scriptsize
+\begin{minipage}{0.81\linewidth}
+\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
+  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(F ) } \\
+  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
+\multicolumn{1}{c}{~}\\
+antV0 &$\bigstar$ 39 & {\rfour} & 26 & {\rone} & 32 & {\rtwo} & 25 &         & 25 &         & 22 &        \\
+antV1 & 11 &         &$\bigstar$ 85 & {\rfour} & 40 & {\rone} & 49 & {\rtwo} & 39 & {\rone} & 33 & {\rone}\\
+antV2 & 0 &         &$\bigstar$ 86 & {\rfour} & 44 & {\rtwo} & 51 & {\rtwo} & 52 & {\rthree} & 56 & {\rthree}\\
+camelV0 & 0 &         &$\bigstar$ 28 & {\rfour} & 9 & {\rone} &$\bigstar$ 28 & {\rfour} & 34 & {\rfour} & 31 & {\rfour}\\
+camelV1 & 34 & {\rthree} &$\bigstar$ 35 & {\rfour} & 31 &         & 33 & {\rtwo} & 33 & {\rtwo} & 30 &        \\
+ivyV0 & 27 &         & 30 & {\rone} & 30 & {\rone} & 32 & {\rthree} &$\bigstar$ 35 & {\rfour} &$\bigstar$ 35 & {\rfour}\\
+jeditV0 & 50 &         & 55 & {\rtwo} & 56 & {\rtwo} & 55 & {\rtwo} &$\bigstar$ 61 & {\rfour} & 60 & {\rfour}\\
+jeditV1 & 37 & {\rone} & 34 &         & 36 &         & 47 & {\rfour} & 45 & {\rthree} &$\bigstar$ 48 & {\rfour}\\
+jeditV2 & 4 &         &$\bigstar$ 99 & {\rfour} & 5 &         & 9 &         & 9 &         & 11 &        \\
+log4jV0 & 62 & {\rfour} & 7 &         & 47 & {\rthree} &$\bigstar$ 64 & {\rfour} & 53 & {\rfour} & 45 & {\rthree}\\
+luceneV0 & 70 & {\rthree} & 73 & {\rfour} & 56 &         &$\bigstar$ 75 & {\rfour} & 70 & {\rthree} &$\bigstar$ 75 & {\rfour}\\
+poiV0 &$\bigstar$ 78 & {\rfour} & 63 &         & 74 & {\rthree} & 70 & {\rtwo} & 73 & {\rthree} & 72 & {\rtwo}\\
+poiV1 & 5 &         &$\bigstar$ 78 & {\rfour} & 21 & {\rone} &$\bigstar$ 78 & {\rfour} & 76 & {\rfour} &$\bigstar$ 78 & {\rfour}\\
+synapseV0 & 0 &         & 2 &         & 40 & {\rthree} &$\bigstar$ 56 & {\rfour} & 52 & {\rfour} & 55 & {\rfour}\\
+velocityV0 & 51 &         & 51 &         & 49 &         & 51 &         & 53 & {\rone} &$\bigstar$ 59 & {\rfour}\\
+xercesV0 & 22 & {\rthree} & 20 & {\rone} & 21 & {\rtwo} & 18 &         & 23 & {\rfour} & 22 & {\rthree}\\
+xercesV1 & 23 & {\rone} & 2 &         & 18 & {\rone} & 36 & {\rtwo} & 68 & {\rfour} &$\bigstar$ 71 & {\rfour}\\
+\end{tabular}
+\end{minipage}\begin{minipage}{.15\linewidth}
+\begin{tabular}{|p{\linewidth}|}\hline
+
+~\\
+
+{\bf KEY:}
+
+~\\
+
+F percentile ranges:
+
+~\\
+
+80th to 100th = {\rfour}
+
+60th to 80th ~ = {\rthree}
+
+40th to 60th  ~ = {\rtwo}
+
+20th to 40th  ~ = {\rone}
+
+~\\
+
+An absent bar denotes\newline 0th to 20th percentile.
+
+~\\
+
+Percentiles computed  separately
+for each data set.\\\hline
+\end{tabular}
+\end{minipage}
+\caption{Median F values in tune once and test ten times experiment. 
+Gray bars  show  F values
+discretized into 20th percentiles ranges from min to max.
+All data available from http://openscience.us/repo/effort.
+}\label{fig:nonc}
+\end{figure*}
+
+%%%%%%%%%%%%%% F bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%% features selection over G%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
+  \hline\hline
+  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
+\\\hline
+  npm& & & & $\circ$& & & & & & $\circ$& & $\circ$& & & & & & & & & & $\circ$& & $\circ$& & & & & & & & & & \\
+loc& & & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& & & & $\circ$& & & & $\circ$& $\star$& $\circ$& & & & $\circ$& $\star$& & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$\\
+amc& & & & & & & & $\circ$& & $\circ$& & $\circ$& & & & & & & & & & & $\star$& $\circ$& $\star$& & & & & $\circ$& $\star$& $\circ$& $\star$& \\
+max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & $\circ$& & \\
+lcom& & & & $\circ$& & & & & & $\circ$& & & & & & & & & & & & $\circ$& & $\circ$& & & & $\circ$& & & & & & \\
+dam& $\star$& & $\star$& & $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & \\
+ca& & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & & & \\
+cbo& & & & & & & & & & $\circ$& & & & & & & & & & & & $\circ$& & $\circ$& & & & & & $\circ$& & $\circ$& & \\
+ce& & & & & & & & & & $\circ$& & & & $\circ$& & & & & & & & $\circ$& & $\circ$& & $\circ$& & & & & & $\circ$& & \\
+noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
+rfc& & $\circ$& & $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& & $\circ$& & $\circ$& & $\circ$& & & & $\circ$& & $\circ$& $\star$& & & & & & & $\circ$& & $\circ$& $\star$& \\
+dit& & & $\star$& $\circ$& & & & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& & & & & $\circ$& & & & & $\star$& $\circ$& & $\circ$& & \\
+mfa& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& \\
+cam& & & & $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & & $\circ$& $\star$& $\circ$& & $\circ$& $\star$& & & & & $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& \\
+avg\_cc& & & & & & & & & & & & & & $\circ$& & & & & & & & $\circ$& & & & $\circ$& & & & & & $\circ$& & \\
+wmc& $\star$& & $\star$& & & $\circ$& & $\circ$& $\star$& $\circ$& & $\circ$& & & & $\circ$& & $\circ$& & $\circ$& & $\circ$& $\star$& $\circ$& & & & $\circ$& & $\circ$& & $\circ$& $\star$& \\
+moa& & & & $\circ$& & & & & & & & & & & & & & & & & & $\circ$& & $\circ$& & & & & & & & & & \\
+cbm& & & & & & & & & & $\circ$& & & $\star$& & $\star$& $\circ$& $\star$& & & & & & & & $\star$& & & & $\star$& $\circ$& & $\circ$& & \\
+ic& $\star$& & & $\circ$& $\star$& & & $\circ$& & & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& & $\star$& & & & & & & & $\star$& $\circ$& & & & \\
+lcom3& & & & $\circ$& $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& & & $\star$& $\circ$& & $\circ$& & \\
+
+  \end{tabular}
+    \caption{Feature seleciton for different datasets with and without the tuning process over the objective of G measure.
+For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.}
+\end{figure*}
+
+\begin{figure*}
+\renewcommand{\baselinestretch}{0.5} 
+\scriptsize
+\begin{minipage}{0.81\linewidth}
+\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
+  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(G ) } \\
+  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
+\multicolumn{1}{c}{~}\\
+antV0 & 65 & {\rtwo} & 68 & {\rthree} & 53 &         &$\bigstar$ 75 & {\rfour} & 71 & {\rfour} & 72 & {\rfour}\\
+antV1 & 12 &         &$\bigstar$ 60 & {\rfour} & 52 & {\rfour} &$\bigstar$ 60 & {\rfour} & 57 & {\rfour} &$\bigstar$ 60 & {\rfour}\\
+antV2 & 0 &         &$\bigstar$ 72 & {\rfour} & 53 & {\rthree} & 63 & {\rfour} & 62 & {\rfour} & 69 & {\rfour}\\
+camelV0 & 0 &         & 60 & {\rfour} & 10 &         & 55 & {\rfour} & 60 & {\rfour} &$\bigstar$ 62 & {\rfour}\\
+camelV1 & 45 &         & 56 & {\rfour} & 53 & {\rthree} & 56 & {\rfour} &$\bigstar$ 57 & {\rfour} &$\bigstar$ 57 & {\rfour}\\
+ivyV0 & 53 &         & 60 & {\rone} & 63 & {\rtwo} &$\bigstar$ 74 & {\rfour} & 70 & {\rfour} & 68 & {\rthree}\\
+jeditV0 & 59 &         & 71 & {\rthree} & 71 & {\rthree} & 67 & {\rtwo} &$\bigstar$ 75 & {\rfour} &$\bigstar$ 75 & {\rfour}\\
+jeditV1 & 70 & {\rtwo} & 69 & {\rtwo} & 62 &         & 75 & {\rfour} & 75 & {\rfour} &$\bigstar$ 76 & {\rfour}\\
+jeditV2 & 49 &         & 62 & {\rthree} & 48 &         & 61 & {\rthree} & 61 & {\rthree} &$\bigstar$ 66 & {\rfour}\\
+log4jV0 & 53 & {\rtwo} & 53 & {\rtwo} & 46 &         & 46 &         &$\bigstar$ 61 & {\rfour} & 57 & {\rthree}\\
+luceneV0 & 37 &         & 61 & {\rfour} & 55 & {\rthree} & 56 & {\rthree} & 61 & {\rfour} &$\bigstar$ 64 & {\rfour}\\
+poiV0 & 45 &         & 59 & {\rthree} & 66 & {\rfour} & 55 & {\rtwo} &$\bigstar$ 67 & {\rfour} & 61 & {\rthree}\\
+poiV1 & 5 &         & 51 & {\rfour} & 22 & {\rone} & 39 & {\rtwo} &$\bigstar$ 62 & {\rfour} & 56 & {\rfour}\\
+synapseV0 & 0 &         & 55 & {\rfour} & 43 & {\rthree} & 64 & {\rfour} & 63 & {\rfour} &$\bigstar$ 65 & {\rfour}\\
+velocityV0 & 3 &         & 56 & {\rfour} & 26 & {\rtwo} &$\bigstar$ 59 & {\rfour} & 51 & {\rfour} & 56 & {\rfour}\\
+xercesV0 & 37 &         & 43 & {\rtwo} & 47 & {\rfour} & 43 & {\rtwo} &$\bigstar$ 49 & {\rfour} & 48 & {\rfour}\\
+xercesV1 & 26 &         &$\bigstar$ 71 & {\rfour} & 19 &         & 36 & {\rone} & 36 & {\rone} & 33 & {\rone}\\
+%Albrecht  &   7         &   24   &   Projects from IBM   & 28 &     & 40 & {\rtwo} & 38 & {\rtwo} & 38 & {\rtwo} & 49 & {\rfour} \\
+%China      &   18       &   488   &   Projects from Chinese software companies   &   38   &  {\rtwo}  &   34   &       &   34   &       &   35   &  {\rone}   &   41   &   {\rfour}\\
+%Cosmic     &   y   &   y   &   Projects described in functiion points   &   98   &   {\rfour}   &   75   &       &   85   &    {\rtwo}   &   85   &   {\rtwo}    &   89   &   {\rtwo}\\
+%ISBSG10    &   y   &   y   &   From the ISBSG benchmark suite   &   56   &       &   62   &     &   126   &   {\rfour}   &   66   &   {\rone}   &   65   &   {\rone}\\
+%Kemerer    &   7   &   15   &   Large business applications   &   42   &  {\rtwo}  &   24   &   &   55   &  {\rfour} &   55   &   {\rfour}   &   55   &   {\rfour}\\
+%Kitchenham &    6   &   145   &  y    &   34   &   &   43   &   {\rthree}   &   34   &  &   43   &  {\rthree}  &   47   &  {\rfour}  \\
+%Maxwell    &   27  &   62  & Projects from commercial banks in Finland   &   57   &   {\rtwo}   &   56   &   {\rtwo}   &   47   &   &   53   &  {\rone} &   64   &   {\rfour}\\
+%Miyazaki   &   8   &   48 &Japanese software projects developed in COBOL   &   39   &       &   41   &   &   41   &    &   57   &   {\rfour}   &   57   &   {\rfour}\\
+%Telecom    &   3   &   18   &   Maintenance projects for telecom companies   &   23   &       &   26   &   {\rtwo}   &   31   & {\rfour}  &   31   &   {\rfour}   &   31   &   {\rfour}\\
+%Usp05      &   7   &  203  &  Collected from university student projects   &   30   &    &   50   & {\rfour} &   45   & {\rthree}  &   40   &   {\rtwo}  &   50   &   {\rfour}\\
+\end{tabular}
+\end{minipage}\begin{minipage}{.15\linewidth}
+\begin{tabular}{|p{\linewidth}|}\hline
+
+~\\
+
+{\bf KEY:}
+
+~\\
+
+G percentile ranges:
+
+~\\
+
+80th to 100th = {\rfour}
+
+60th to 80th ~ = {\rthree}
+
+40th to 60th  ~ = {\rtwo}
+
+20th to 40th  ~ = {\rone}
+
+~\\
+
+An absent bar denotes\newline 0th to 20th percentile.
+
+~\\
+
+Percentiles computed  separately
+for each data set.\\\hline
+\end{tabular}
+\end{minipage}
+\caption{Median G values in tune once and test ten times experiment. 
+Gray bars  show  G values
+discretized into 20th percentiles ranges from min to max.
+All data available from http://openscience.us/repo/effort.
+}\label{fig:nonc}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%  time for different objectives %%%%%%%%%%%%%%%%%%%%%
+\clearpage
+%%%%time for pd %%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{l|c |c |c |c |c |c }
+    \hline\hline
+    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
+    \hline
+    ant & 241.5 & 12.6 & 7.4 & 0.8 & 13.3 & 1.4\\
+    antV1 & 347.5 & 23.5 & 11.6 & 0.8 & 19.5 & 2.0\\
+    antV2 & 696.5 & 60.0 & 23.6 & 1.5 & 22.6 & 3.1\\
+    camel & 1412.6 & 76.5 & 34.7 & 1.7 & 51.1 & 3.0\\
+    camelV1 & 3391.9 & 230.6 & 36.1 & 2.4 & 46.3 & 6.9\\
+    ivy & 93.9 & 9.9 & 5.1 & 0.6 & 9.7 & 1.6\\
+    jedit & 679.2 & 51.1 & 12.7 & 0.8 & 18.1 & 2.8\\
+    jeditV1 & 1078.5 & 64.9 & 17.2 & 0.9 & 24.6 & 3.0\\
+    jeditV2 & 838.0 & 68.2 & 16.4 & 1.1 & 23.4 & 3.4\\
+    log4j & 190.8 & 13.4 & 5.2 & 0.4 & 11.0 & 1.4\\
+    lucene & 421.0 & 27.6 & 9.2 & 0.7 & 13.3 & 2.3\\
+    poi & 348.6 & 40.4 & 10.6 & 0.9 & 21.7 & 2.7\\
+    poiV1 & 1060.7 & 69.4 & 20.8 & 1.0 & 26.3 & 2.6\\
+    synapse & 350.9 & 18.5 & 9.5 & 0.5 & 14.4 & 1.5\\
+    velocity & 257.0 & 28.3 & 7.5 & 0.5 & 13.3 & 1.9\\
+    xerces & 239.9 & 21.4 & 14.8 & 0.8 & 15.2 & 2.1\\
+    xercesV1 & 2433.9 & 130.3 & 27.6 & 1.4 & 25.3 & 3.7\\
+  \end{tabular}
+  \caption{Time (in seconds) spent on different models over the objective of pd}
+\end{figure*}
+
+%%%%time for pf %%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{l|c |c |c |c |c |c }
+    \hline\hline
+    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
+    \hline
+    ant & 33.3 & 14.1 & 2.4 & 0.7 & 2.6 & 1.7\\
+    antV1 & 59.3 & 25.5 & 4.2 & 0.9 & 3.0 & 2.2\\
+    antV2 & 131.4 & 67.4 & 3.0 & 1.7 & 4.2 & 3.7\\
+    camel & 167.8 & 85.7 & 3.9 & 2.0 & 5.1 & 3.5\\
+    camelV1 & 503.5 & 325.1 & 68.5 & 3.6 & 146.6 & 8.8\\
+    ivy & 116.4 & 11.5 & 8.5 & 1.3 & 23.9 & 1.9\\
+    jedit & 336.6 & 59.9 & 6.7 & 0.9 & 29.3 & 3.4\\
+    jeditV1 & 159.9 & 79.2 & 2.1 & 1.2 & 36.9 & 3.5\\
+    jeditV2 & 151.4 & 80.0 & 21.8 & 1.4 & 38.6 & 3.9\\
+    log4j & 37.4 & 15.5 & 1.9 & 0.5 & 5.0 & 1.8\\
+    lucene & 436.4 & 33.9 & 17.0 & 1.0 & 49.4 & 3.2\\
+    poi & 202.7 & 48.5 & 24.6 & 1.3 & 50.4 & 3.5\\
+    poiV1 & 184.3 & 79.9 & 2.5 & 1.5 & 5.5 & 3.2\\
+    synapse & 36.9 & 20.5 & 1.4 & 0.7 & 2.7 & 1.7\\
+    velocity & 157.9 & 31.6 & 10.4 & 0.7 & 33.2 & 2.2\\
+    xerces & 59.5 & 23.5 & 19.6 & 1.2 & 31.0 & 2.4\\
+    xercesV1 & 286.6 & 151.8 & 8.0 & 1.8 & 5.4 & 4.5\\
+  \end{tabular}
+  \caption{Time (in seconds) spent on different models over the objective of pf}
+\end{figure*}
+
+%%%%time for prec %%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{l|c |c |c |c |c |c }
+    \hline\hline
+    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
+    \hline
+    ant & 158.6 & 13.3 & 8.8 & 0.7 & 18.1 & 1.6\\
+    antV1 & 298.9 & 25.4 & 13.5 & 0.9 & 15.8 & 2.2\\
+    antV2 & 632.0 & 65.0 & 14.4 & 1.7 & 29.3 & 3.6\\
+    camel & 566.3 & 94.3 & 26.0 & 1.8 & 20.8 & 5.5\\
+    camelV1 & 4954.0 & 243.0 & 52.1 & 2.3 & 42.7 & 7.2\\
+    ivy & 148.7 & 10.0 & 8.6 & 0.6 & 11.0 & 1.6\\
+    jedit & 972.5 & 51.9 & 15.8 & 0.8 & 22.3 & 2.9\\
+    jeditV1 & 1102.5 & 73.6 & 19.7 & 0.9 & 46.5 & 3.5\\
+    jeditV2 & 837.5 & 76.9 & 15.7 & 1.3 & 65.3 & 3.7\\
+    log4j & 289.2 & 17.1 & 6.8 & 0.6 & 17.1 & 1.6\\
+    lucene & 471.6 & 29.6 & 8.7 & 0.8 & 16.8 & 2.5\\
+    poi & 651.4 & 52.0 & 11.4 & 1.1 & 23.1 & 3.3\\
+    poiV1 & 1666.8 & 86.2 & 13.8 & 1.4 & 25.7 & 3.2\\
+    synapse & 209.2 & 23.7 & 9.2 & 0.7 & 15.8 & 1.7\\
+    velocity & 345.5 & 33.5 & 11.5 & 0.7 & 12.7 & 2.3\\
+    xerces & 392.2 & 27.2 & 13.9 & 1.2 & 43.0 & 3.0\\
+    xercesV1 & 1619.8 & 157.1 & 23.8 & 1.7 & 34.8 & 5.0\\
+  \end{tabular}
+  \caption{Time (in seconds) spent on different models over the objective of prec}
+\end{figure*}
+
+%%%%time for F %%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{l|c |c |c |c |c |c }
+    \hline\hline
+    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
+    \hline
+    ant & 302.5 & 13.3 & 6.9 & 0.7 & 13.8 & 1.6\\
+    antV1 & 328.7 & 27.2 & 12.7 & 0.8 & 15.4 & 2.0\\
+    antV2 & 1030.2 & 73.0 & 31.3 & 1.7 & 34.6 & 4.2\\
+    camel & 1838.4 & 92.5 & 33.4 & 2.0 & 43.7 & 3.4\\
+    camelV1 & 4352.4 & 275.8 & 46.2 & 5.4 & 42.8 & 7.8\\
+    ivy & 167.9 & 11.9 & 4.1 & 0.7 & 18.8 & 1.8\\
+    jedit & 830.6 & 62.9 & 7.8 & 1.0 & 45.7 & 3.3\\
+    jeditV1 & 1055.2 & 81.8 & 13.6 & 1.1 & 30.7 & 3.6\\
+    jeditV2 & 1322.7 & 92.2 & 18.1 & 1.3 & 35.3 & 4.1\\
+    log4j & 370.7 & 16.3 & 5.6 & 0.5 & 16.1 & 1.7\\
+    lucene & 385.3 & 31.9 & 8.8 & 0.8 & 21.3 & 2.6\\
+    poi & 720.7 & 46.2 & 10.2 & 0.9 & 19.9 & 3.0\\
+    poiV1 & 1229.0 & 79.4 & 14.9 & 1.2 & 25.9 & 2.9\\
+    synapse & 377.0 & 21.6 & 10.3 & 0.6 & 21.0 & 1.7\\
+    velocity & 275.6 & 39.6 & 8.9 & 0.7 & 13.2 & 2.1\\
+    xerces & 310.7 & 25.4 & 13.3 & 0.9 & 21.6 & 2.3\\
+    xercesV1 & 1792.1 & 147.9 & 37.1 & 1.6 & 35.4 & 4.0\\
+  \end{tabular}
+  \caption{Time (in seconds) spent on different models over the objective of F}
+\end{figure*}
+
+%%%%time for G %%%%%%
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{l|c |c |c |c |c |c }
+    \hline\hline
+    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
+    \hline
+    ant & 164.0 & 13.9 & 9.2 & 0.9 & 14.5 & 1.5\\
+    antV1 & 560.3 & 27.3 & 15.5 & 1.0 & 17.2 & 2.4\\
+    antV2 & 1743.9 & 77.3 & 18.9 & 1.7 & 25.5 & 3.6\\
+    camel & 1823.1 & 93.0 & 39.8 & 1.9 & 39.1 & 3.4\\
+    camelV1 & 6679.7 & 234.3 & 39.7 & 2.2 & 74.5 & 7.0\\
+    ivy & 261.9 & 10.9 & 9.9 & 0.6 & 17.4 & 1.6\\
+    jedit & 993.8 & 54.4 & 11.1 & 0.8 & 23.7 & 2.8\\
+    jeditV1 & 1110.0 & 68.5 & 12.3 & 0.9 & 27.2 & 3.0\\
+    jeditV2 & 858.2 & 72.5 & 15.4 & 1.1 & 23.3 & 3.4\\
+    log4j & 247.7 & 15.2 & 3.8 & 0.4 & 9.1 & 1.4\\
+    lucene & 610.9 & 30.6 & 6.1 & 0.7 & 28.7 & 2.4\\
+    poi & 1466.6 & 47.4 & 18.3 & 0.9 & 33.0 & 2.7\\
+    poiV1 & 1365.6 & 77.4 & 17.2 & 1.1 & 31.1 & 2.7\\
+    synapse & 202.6 & 21.9 & 8.0 & 0.5 & 19.8 & 1.5\\
+    velocity & 869.8 & 31.4 & 10.5 & 0.6 & 29.8 & 1.9\\
+    xerces & 534.1 & 27.1 & 12.6 & 0.8 & 24.1 & 2.0\\
+    xercesV1 & 2825.7 & 143.5 & 22.4 & 1.5 & 48.1 & 3.8\\
+  \end{tabular}
+  \caption{Time (in seconds) spent on different models over the objective of G}
+\end{figure*}
+
 \end{document}

### 2015-03-02 tuningpredictor.tex
add the counts of features over different goals

@@
 
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c|c c|c }
+  \hline\hline
+  Features & \multicolumn{2}{c}{Pd} & \multicolumn{2}{c}{Pf} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{F} & \multicolumn{2}{c}{G} & SUM
+\\\hline
+  noc& 0& 0& 0& 0& 0& 0& 0& 0& 0& 0& 0\\
+ca& 0& 0& 0& 0& 0& 1& 0& 0& 0& 1& 2\\
+max\_cc& 0& 0& 0& 0& 0& 1& 0& 0& 0& 2& 3\\
+moa& 0& 0& 0& 0& 0& 1& 0& 1& 0& 3& 5\\
+avg\_cc& 0& 0& 0& 0& 0& 3& 0& 2& 0& 4& 9\\
+cbo& 0& 0& 0& 1& 0& 1& 0& 3& 0& 5& 10\\
+npm& 0& 0& 0& 0& 0& 2& 0& 4& 0& 5& 11\\
+lcom& 0& 0& 0& 1& 0& 1& 0& 4& 0& 5& 11\\
+ce& 0& 0& 0& 0& 0& 3& 0& 2& 0& 6& 11\\
+amc& 4& 0& 4& 0& 4& 1& 4& 5& 4& 6& 32\\
+cbm& 6& 0& 6& 2& 4& 1& 4& 2& 5& 4& 34\\
+rfc& 4& 0& 4& 3& 4& 4& 4& 9& 4& 11& 47\\
+wmc& 5& 0& 5& 1& 5& 3& 5& 7& 5& 12& 48\\
+ic& 8& 1& 8& 1& 9& 3& 8& 8& 9& 5& 60\\
+dit& 8& 1& 8& 3& 8& 5& 7& 8& 8& 8& 64\\
+cam& 9& 0& 9& 2& 9& 3& 9& 8& 9& 11& 69\\
+loc& 9& 1& 8& 4& 9& 4& 9& 8& 8& 10& 70\\
+lcom3& 9& 0& 8& 2& 8& 5& 8& 13& 9& 10& 72\\
+dam& 14& 0& 14& 5& 14& 6& 14& 12& 14& 12& 105\\
+mfa& 16& 3& 16& 7& 16& 6& 16& 16& 16& 13& 125\\
+
+  \end{tabular}
+\end{figure*}
+
 \end{document}

### 2015-03-02 tuningpredictor.tex
update
safety save

--- 2015-03-02 tuningpredictor.tex
@@
  \setlength{\textfloatsep}{1ex}
+ \newcommand{\subparagraph}{}
+
 \usepackage[compact,small]{titlesec}
@@
 structure of this paper.
+
+\subsection{Implications}
+
+time for an end to era of data mining in se? moving on to a new phase of learning-as-optimization
+
+1) learning is actually an optimization tasks (e.g. see fig2 of  learners climbing the roc curve hill in http://goo.gl/x2EaAm)
+
+2) our learners are all contorted to do some tasks X (e.g.
+minimize expected value of entropy), then we assess them on score Y (recall).
+which is nuts.
+maybe we should build the goal predicate into the learner (e.g http://menzies.us/pdf/10which.pdf)
+
+3) given 1 + 2, maybe the whole paradigm of optimizing param selection is wrong.
+maybe what we need is a library of bees buzzing around making random choices (e.g.
+about descritziation) which other bees use, plus their own random choices (e.g.
+max depth of tree learned from discretized data) which is used by other bees, plus their own random choices (e.g.
+business users reading the models).
+the funky thing here is that it can take some time before some of the bees (the discretizers) get feedback from the community of people using their decision (the tree learners).
 
@@
 \begin{figure*}[t!]
+\renewcommand{\baselinestretch}{0.7}
 \scriptsize
@@
 %%%%parameters for pd %%%%%%
-\begin{figure*}[!ht]
+\begin{figure*}[!t]
+
+\renewcommand{\baselinestretch}{0.7}
 \resizebox{\textwidth}{!}{
@@
 %%%%parameters for pf %%%%%%
-\begin{figure*}[!ht]
+\begin{figure*}[!t]
+
+\renewcommand{\baselinestretch}{0.7}
 \resizebox{\textwidth}{!}{
@@
 \begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.7}
 \resizebox{\textwidth}{!}{
@@
 \begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.7}
 \scriptsize
@@
 \begin{figure*}
-\renewcommand{\baselinestretch}{0.5} 
+\renewcommand{\baselinestretch}{0.7}
 \scriptsize
@@
 \begin{figure*}[!ht]
+\renewcommand{\baselinestretch}{0.7}
 \scriptsize
@@
 \begin{figure*}
-\renewcommand{\baselinestretch}{0.5} 
+\renewcommand{\baselinestretch}{0.7} 
 \scriptsize
@@
 
+%%%%%%%%%%%%%%%%  counts of features for different goals%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.7}
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c|c c|c c }
+  \hline\hline
+  Features & \multicolumn{2}{c}{Pd} & \multicolumn{2}{c}{Pf} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{F} & \multicolumn{2}{c}{G} & \multicolumn{2}{c}{SUM}
+\\\hline
+  noc& 0& 0& 0& 0& 0& 0& 0& 0& 0& 0& 0& 0\\
+ca& 0& 0& 0& 0& 0& 1& 0& 0& 0& 1& 0& 2\\
+max\_cc& 0& 0& 0& 0& 0& 1& 0& 0& 0& 2& 0& 3\\
+moa& 0& 0& 0& 0& 0& 1& 0& 1& 0& 3& 0& 5\\
+avg\_cc& 0& 0& 0& 0& 0& 3& 0& 2& 0& 4& 0& 9\\
+cbo& 0& 0& 0& 1& 0& 1& 0& 3& 0& 5& 0& 10\\
+npm& 0& 0& 0& 0& 0& 2& 0& 4& 0& 5& 0& 11\\
+lcom& 0& 0& 0& 1& 0& 1& 0& 4& 0& 5& 0& 11\\
+ce& 0& 0& 0& 0& 0& 3& 0& 2& 0& 6& 0& 11\\
+amc& 4& 0& 4& 0& 4& 1& 4& 5& 4& 6& 20& 12\\
+cbm& 6& 0& 6& 2& 4& 1& 4& 2& 5& 4& 25& 9\\
+rfc& 4& 0& 4& 3& 4& 4& 4& 9& 4& 11& 20& 27\\
+wmc& 5& 0& 5& 1& 5& 3& 5& 7& 5& 12& 25& 23\\
+ic& 8& 1& 8& 1& 9& 3& 8& 8& 9& 5& 42& 18\\
+dit& 8& 1& 8& 3& 8& 5& 7& 8& 8& 8& 39& 25\\
+cam& 9& 0& 9& 2& 9& 3& 9& 8& 9& 11& 45& 24\\
+loc& 9& 1& 8& 4& 9& 4& 9& 8& 8& 10& 43& 27\\
+lcom3& 9& 0& 8& 2& 8& 5& 8& 13& 9& 10& 42& 30\\
+dam& 14& 0& 14& 5& 14& 6& 14& 12& 14& 12& 70& 35\\
+mfa& 16& 3& 16& 7& 16& 6& 16& 16& 16& 13& 80& 45\\
+
+  \end{tabular}
+    \caption{Counts of features selected by different goals.
+For each goal, the numbers in right and left columns represent the counts of features selected for all the data sets with and without tuning processes.}
+\end{figure*}
+
+%%%%time for G %%%%%%
+\begin{figure}[!ht]
+
+\renewcommand{\baselinestretch}{0.7}
+\scriptsize
+\centering
+  \begin{tabular}{l|rrr|rrr|rrr}
+    & \multicolumn{3}{c|}{Where}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10}\\
+    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
+pd&242&13&19&7&1&9&13&1&10\\
+pf&33&14&2&2&1&3&3&2&2\\
+prec&159&13&12&9&1&13&18&2&11\\
+f&303&13&23&7&1&10&14&2&9\\
+G&164&14&12&9&1&10&15&2&10\\
+total&900&67&13&35&4&9&62&8&8\\
+  \end{tabular}
+  \caption{For one train/test set pair (ANT),  time (in seconds) spent optimizing for different goals.}
+\end{figure}
+
 \end{document}

### 2015-03-03 tuningpredictor.tex
safety commit

--- 2015-03-02 tuningpredictor.tex
@@
 \conferenceinfo{FSE}{'15 Bergamo, Italy}
-\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
+\title{Implications of Differential Evolution for  Defect Prediction:
+Analytics Without Parameter Tuning Considered Harmful}
 \numberofauthors{1}
@@
 \begin{abstract}
-Data mining techniques have been widely applied to software defect prediction with various 
+
+software defect prediction with various 
 empirical data sets. Those proposed leaners are always evaluated against the state of the art 
@@
 assess the relative value of OO metrics vs procedural metrics for predicting
-project defects. Are we reporting ``truth'' in any sense of the word? And for home
-many other projects might we find that same ``truth''?
+project defects. Are we reporting ``truth'' in any sense of the word? And for how
+many other projects  and how many kinds of questions might we find that same ``truth''?
+
+This is not some abstract question-- it is an open and pressing matter.
+Any reading of the recent proceedings of FSE, ICSE, ASE, etc will discover hundreds
+of papers using data miners to make conclusions about software projects. 
+For example, some  analysts have made conclusions
+about 
+{\em what attributes
+have most influence on a software project}.
+For example, in 2013,
+Rahman et al
+\cite{rahman2013how}  used results from logistic regression to conclude
+that code metrics are generally less useful than process
+metrics for  predicting defects from static code analysis.  
+In the same year, Bell et al. (who also used negative binomial regression) argued that
+software defect prediction was not improved by adding in~\cite{bell2013limited}.
+
+@article{bell2013limited,
+  title={The limited impact of individual developer data on software defect prediction},
+  author={Bell, Robert M and Ostrand, Thomas J and Weyuker, Elaine J},
+  journal={Empirical Software Engineering},
+  volume={18},
+  number={3},
+  pages={478--505},
+  year={2013},
+  publisher={Springer}
+}
+
+The results of this paper offer a very different picture  to recent prominent results from prior authors.
+Lessmann et al.~\cite{lessmann2008benchmarking}, Rahman et al.~\cite{rahman2013how} and Arshiholm et al.~\cite{arisholm06} argue that when it comes to defect prediction, different learners often
+produce statistically similar results. For this reason  Rahman et al. only present results their logistic
+regression results, commenting that ``dor brevity, only results from LR are
+presented; other learning models give similar results''~\cite{rahman2013how}. Note that those prior results,
+where most learners achieved the same results, arose from the default parameter settings from those learners.
+
+Our results, on the other hand, come from tuning a data miner's parameters. In those results,
+we found that the choice of parameters had dramatic impacts on data mining performance.
+For example, we show results below where:   
+\bi 
+\item 
+Tuning improved precision values from  2\% to 98\%; or
+\item 
+Tuning improved false alarm values from 69\% to 0\%; or
+\item 
+Tuning improved recall values from 0 to 100\%; or
+\item 
+Tuning improved the f-measure (which is the harmonic mean of recall and precision) from 0 to 86\%.
+\ei   
+In terms of changing SE research methodologies, an important aspect of these results is that usually XXXX always different.
+cannot determine without experimentation which learner will, after tuning, yield the best results for a particular data set.
+Hence it is no longer viable for researchers to trust the recommendations
+of other researchers working with other data sets that ``data miner XYZ is best''. Before
+offering a conclusion about a particular data set, researchers need now augment  their 
+papers with preliminary tuning studies (the results of which select the tunings+data miners to be used
+to make conclusions for the second half of their paper).
+
+The good news is that such tuning is not an arduous task. The differential evolution algorithm 
+used in this study is wdiely available in many standard  toolkits and languages\footnote{See the long list at
+www1.icsi.berkeley.edu/~storn/code.html.}
+And even if somehow those tools and prior implementations are not workable at a local site, 
+differential evolution is very simple to code. Hence, it can readily and quickly implemented.
+
+When we discuss these results with colleagues, one response we get is ``enough of the parameter tuning.. lets use simpler methods''. 
+While we understand their motivation (to keep thing simple), software project
+data cannot necessarily be condensed to (say) a simple univariate analysis that
+reports how one independent variable effects a dependent variable.
+Such a simplistic analysis can miss significant interaction
+effects when multiple factors combine to effect the target variable. For example,
+one of the base results in defect prediction is that predictors formed from
+a single variable perform much worse than those can combined multiple variables (three or more)~\cite{me07b}.
+
+If those results come from an analysis of a complex interactions between attributes,
+then some kind of data mining method\footnote{By this term we mean the
+full gamut of methods for large-scale analysis of
+data including statistical
+parametric methods (that assume a particular distribution then strive to learn the parameters of that distribution); kernel methods;
+dimensionality  synthesis methods; 
+instance weighting schemes; feature subset selection methods
+outlier removal methods;
+decision tree learners; neural networks; and instance-based
+methods including clustering and/or   case-based reasoning.} then there is the
+{\em tuning problem} of how to set the myriad of parameters that 
+control the learner.
+
+\item
+What data miners are better than others for particular tasks
+in software analytics. 
+\ei
+
+Also, in 2007, one of us (Menzies) claimed that Naive Bayes
+classifiers with a certain lind of pre-processor were better than entropy-based decision trees for defect prediction~\cite{me07b}.
+Similarly, in 2008 Lessmann et al.~\cite{lessmann2008benchmarking} argued  that 
+Random Forests~\cite{brieman00} and CART ~\cite{brieman84} work best, worst for learning software defect predictors from
+static code attributes. Similar claims that one learner was better than another
+have been made by many other authors; e.g.
+
+We write to suggest that all those conclusions may be wrong or, at the very most,
+correct within a very limited context. At the very least, the conclusions
+of those papers (and literally dozens of similar papers, include severl
+of our own~\cite{me02e,me02k,me03a,me06d,me07b}) need to be revisited
+in light of this paper's results on the effects of tuning on data miners.
+
+Machine learners
+are controlled by parameters that decide (e.g.) when to stop recursively
+dividing data into smaller section or (e.g.) what thresholds for errors are small
+enough to be acceptable. When used ``off-the-shelf'', analytst
+use default settings for those parameters. We find that  a 
+simple optimization scheme (differential evolution) can find much
+better tunings that can dramatically change the performance of
+the learned model (measured in terms of false alarm rates, recall,
+precision, f-measure, and g-measure).  From this first result,
+we conclude that {\bf parameter tuning with some optimizer such as differential
+evolution should become standard practice}.
+
+Our next observation is that observations about miner1 being better
+than miner2 do not survive tuning. To be specific: given some
+ranking of data miners for some task such as defect prediction,
+we find that tuning can reverse those rankings such that the worst untu
+
+Tuning the data miners with different evolution takes some
+times (around an order of magnitude slower than the learning), but not an impractically slower amount of time. Further, when we look at what
+attrub
 
@@
 \cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
+\begin{figure}
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+When applying case-based reasoning, researchers use different settings including how they measure dis- tance between instances (examples include the Euclidean measure, Manhattan and Chebyshev).
+Other settings control if numerics are normalized min..max to 0..1, before they are used in the distance measure.
+
+Another set of settings refers to how to handle non-numeric distances or missing values.
+Some researchers delete training data with missing information while others compute missing values via, say, median values.
+
+After feature selection comes instance selection.
+There are many settings for instance selectors such as use outlier removal or prototype generation.
+Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
+The next set of settings concern how many neighbors to use (k=1,2,5,etc).
+Some researchers set “k” in dynamic pre-learning phase that checks the training data to find what “k” works best for that data.
+
+Once the neighbors are known, the next settings control how to summarize their information.
+Some researchers use means, other use medians, or a weighted sum that uses the distance of the neighbor from the test instance (and that weighting might be determined by some kernel such as uniform, triangular, Gaussian, cosine, or Epanechnikov).
+Researchers may use other settings to control different pre-processors.
+E.g.
+some discretize numeric values (via equal width or equal frequency) using some binning policy (and researchers differ on how many bins are best).\\\hline
+\end{tabular}
+\caption{Some tunings for SE predictive systems.
+Found by this author while preparing this proposal in a day of reading the SE predictive modeling literature on case-based reasoning and effort estimation.
+Note that other kinds of prediction systems (decision trees, neural nets, linear repression, etc) have yet more adjustable design options.}\label{fig:adjust}
+\end{figure}
+
 domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
@@
 
+\subsection{Implications}
+
+time for an end to era of data mining in se? moving on to a new phase of learning-as-optimization
+
+1) learning is actually an optimization tasks (e.g. see fig2 of  learners climbing the roc curve hill in http://goo.gl/x2EaAm)
+
+2) our learners are all contorted to do some tasks X (e.g.
+minimize expected value of entropy), then we assess them on score Y (recall).
+which is nuts.
+maybe we should build the goal predicate into the learner (e.g http://menzies.us/pdf/10which.pdf)
+
+3) given 1 + 2, maybe the whole paradigm of optimizing param selection is wrong.
+maybe what we need is a library of bees buzzing around making random choices (e.g.
+about descritziation) which other bees use, plus their own random choices (e.g.
+max depth of tree learned from discretized data) which is used by other bees, plus their own random choices (e.g.
+business users reading the models).
+the funky thing here is that it can take some time before some of the bees (the discretizers) get feedback from the community of people using their decision (the tree learners).
+
 \section{Algorithm: Predictor and Tuner}
@@
 clustering algorithm.
+
+\begin{figure}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
+    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
+    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
+pd&242&13&19&7&1&9&13&1&10\\ 
+prec&159&13&12&9&1&13&18&2&11\\
+f&303&13&23&7&1&10&14&2&9 
+  \end{tabular}
+  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
+  for different goals, or just running the ``off-the-shelf'' learner.}
+\end{figure}
+
+\begin{figure}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+\begin{tabular}{r|rrr}
+goal &	WHERE	&CART&	Random Forest\\\hline
+f	&15	&13	&9\\ 
+pd	&15	&16	&8\\ 
+prec&	14	&14	&8
+\end{tabular}
+\caption{How much slower is tuning vs just running the default
+settings of the learner? E.g. bottom right, tuning to increase
+precision with Random Forests is eight times slower than
+just running Random Forests.}
+\end{figure}
 
@@
 \begin{figure*}[t!]
+\renewcommand{\baselinestretch}{0.8}
 \scriptsize
@@
 %%%%parameters for pd %%%%%%
-\begin{figure*}[!ht]
+\begin{figure*}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
 \resizebox{\textwidth}{!}{
@@
 
-%%%%parameters for pf %%%%%%
-\begin{figure*}[!ht]
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.53& 0.71& 0.37& 0.23& 0.67& 1& 1& 0.48& 0.97& 0.81& 1& 0.98& 0.92& 0.93& 0.98& 0.5& 0.99\\ \cline{2-20}
-& infoPrune& 0.33& 0.68& 0.97& 0.43& 0.01& 0.22& 1& 0.76& 0.48& 0.61& 0.23& 0.04& 0.92& 0.59& 0.41& 0.88& 0.9& 0.23\\ \cline{2-20}
-& min\_sample\_size& 4& 3& 1& 2& 1& 6& 4& 3& 5& 3& 9& 7& 3& 3& 8& 7& 2& 9\\ \cline{2-20}
-& min\_Size& 0.5& 0.07& 0.03& 0.36& 0.06& 0.21& 0.38& 0.15& 0.19& 0.29& 0.08& 0.35& 0.24& 0.38& 0.67& 0.01& 0.25& 0.58\\ \cline{2-20}
-& wriggle& 0.2& 0.91& 0.97& 0.47& 0.96& 0.82& 0.11& 0.37& 0.37& 0.06& 0.68& 0.23& 0.01& 0.51& 0.79& 0.53& 0.05& 0.08\\ \cline{2-20}
-& depthMin& 2& 4& 1& 3& 3& 1& 1& 3& 4& 2& 3& 3& 1& 1& 1& 1& 3& 1\\ \cline{2-20}
-& depthMax& 10& 10& 15& 7& 4& 14& 3& 15& 16& 15& 18& 6& 6& 5& 18& 10& 6& 16\\ \cline{2-20}
-& wherePrune& False& True& True& False& True& True& True& True& True& True& False& True& True& True& True& True& True& False\\ \cline{2-20}
-& treePrune& True& True& False& True& False& False& True& True& False& False& False& False& True& False& False& False& True& False\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 1& 1& 0.96& 0.88& 1& 1& 0.99& 0.88& 1& 0.83& 1& 1& 0.92& 0.9& 1& 1& 1\\ \cline{2-20}
-& max\_feature& None& 0.01& 1& 0.93& 0.58& 0.01& 0.73& 1& 0.44& 0.01& 0.88& 0.01& 0.38& 0.48& 0.65& 0.86& 0.28& 0.01\\ \cline{2-20}
-& min\_samples\_split& 2& 4& 4& 18& 3& 14& 19& 14& 16& 19& 12& 6& 2& 9& 8& 3& 6& 16\\ \cline{2-20}
-& min\_samples\_leaf& 1& 12& 16& 19& 18& 1& 2& 5& 8& 8& 1& 10& 6& 12& 12& 13& 3& 10\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.89& 0.58& 0.88& 0.86& 1& 1& 1& 1& 1& 1& 1& 1& 0.78& 0.73& 1& 1& 0.93\\ \cline{2-20}
-& max\_feature& None& 0.47& 0.04& 0.12& 0.38& 0.96& 0.87& 0.11& 0.01& 1& 0.16& 0.85& 0.99& 0.78& 0.77& 0.01& 0.35& 0.23\\ \cline{2-20}
-& max\_leaf\_nodes& None& 35& 37& 38& 23& 13& 34& 36& 29& 10& 10& 10& 10& 33& 49& 50& 24& 37\\ \cline{2-20}
-& min\_samples\_split& 2& 18& 10& 5& 16& 1& 20& 2& 1& 10& 5& 11& 5& 16& 4& 5& 19& 19\\ \cline{2-20}
-& min\_samples\_leaf& 1& 16& 11& 6& 13& 2& 4& 2& 2& 2& 19& 6& 2& 4& 14& 2& 3& 18\\ \cline{2-20}
-& n\_estimators& 100& 103& 95& 76& 88& 68& 88& 136& 90& 144& 115& 150& 99& 110& 114& 53& 108& 99\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of pf}
-\end{figure*}
-
 %%%%parameters for prec %%%%%%
 \begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.8}
 \resizebox{\textwidth}{!}{
@@
 \begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.8}
 \resizebox{\textwidth}{!}{
@@
 
-%%%%parameters for G %%%%%%
+%%%%%%%%%%%%%%%% defectives and non-defectives for each datasets%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure*}[!ht]
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.16& 0.44& 0.07& 0.01& 0.5& 0.9& 0.75& 0.5& 0.7& 0.38& 0.68& 1& 0.01& 0.15& 1.0& 0.84& 0.01\\ \cline{2-20}
-& infoPrune& 0.33& 0.54& 1.0& 0.07& 0.55& 0.79& 0.74& 0.36& 0.47& 0.65& 0.27& 0.69& 0.9& 0.73& 0.44& 0.73& 0.87& 0.01\\ \cline{2-20}
-& min\_sample\_size& 4& 8& 9& 1& 9& 1& 5& 7& 1& 8& 5& 2& 1& 3& 4& 3& 1& 6\\ \cline{2-20}
-& min\_Size& 0.5& 0.76& 0.71& 0.91& 0.42& 0.63& 0.64& 0.88& 0.45& 1& 0.92& 0.94& 0.9& 0.4& 0.55& 0.68& 0.49& 0.65\\ \cline{2-20}
-& wriggle& 0.2& 0.57& 0.11& 0.79& 1& 0.5& 0.25& 0.51& 0.28& 0.46& 0.06& 0.61& 0.28& 0.01& 0.61& 0.57& 0.65& 0.02\\ \cline{2-20}
-& depthMin& 2& 4& 1& 1& 6& 4& 2& 2& 3& 3& 1& 1& 6& 1& 4& 2& 5& 2\\ \cline{2-20}
-& depthMax& 10& 8& 6& 4& 9& 9& 18& 4& 10& 6& 6& 7& 20& 9& 16& 14& 19& 6\\ \cline{2-20}
-& wherePrune& False& True& True& True& False& True& True& True& True& True& True& True& True& True& False& False& True& True\\ \cline{2-20}
-& treePrune& True& True& False& True& False& False& False& False& False& True& False& False& False& True& True& True& False& True\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.17& 0.47& 0.01& 0.01& 0.88& 0.59& 0.98& 0.49& 0.45& 0.99& 0.69& 1& 0.01& 0.01& 0.95& 0.69& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.28& 0.61& 0.01& 0.87& 0.98& 0.77& 0.83& 0.01& 0.6& 0.01& 0.78& 0.29& 0.01& 0.81& 0.72& 1\\ \cline{2-20}
-& min\_samples\_split& 2& 18& 17& 12& 2& 2& 18& 3& 10& 15& 12& 2& 10& 18& 9& 8& 10& 13\\ \cline{2-20}
-& min\_samples\_leaf& 1& 11& 18& 14& 15& 1& 10& 2& 18& 12& 20& 7& 1& 1& 11& 9& 1& 1\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.35& 0.42& 0.17& 0.01& 0.78& 1& 0.86& 0.39& 0.71& 0.42& 0.87& 1& 0.06& 0.06& 1& 1& 0.2\\ \cline{2-20}
-& max\_feature& None& 0.13& 0.98& 0.01& 0.36& 0.53& 0.79& 0.98& 1& 0.01& 0.12& 0.75& 0.82& 0.79& 0.64& 0.01& 0.71& 0.8\\ \cline{2-20}
-& max\_leaf\_nodes& None& 13& 22& 42& 18& 10& 43& 23& 37& 49& 47& 15& 10& 45& 16& 36& 13& 39\\ \cline{2-20}
-& min\_samples\_split& 2& 9& 8& 13& 1& 10& 14& 10& 1& 1& 4& 6& 1& 5& 14& 1& 8& 12\\ \cline{2-20}
-& min\_samples\_leaf& 1& 3& 14& 15& 2& 17& 6& 5& 2& 14& 2& 9& 3& 18& 16& 2& 2& 4\\ \cline{2-20}
-& n\_estimators& 100& 107& 131& 114& 125& 138& 138& 57& 84& 50& 58& 83& 70& 83& 121& 150& 150& 132\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of G}
-\end{figure*}
-
-%%%%%%%%%%%%%%%% defectives and non-defectives for each datasets%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.8}
 \scriptsize
@@
 
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
-  \hline\hline
-  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
-\\\hline
-  npm& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-loc& & & $\star$& & & & $\star$& & $\star$& & & & & & & & & & $\star$& & & & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& $\circ$\\
-amc& & & & & & & & & & & & & & & & & & & & & & & $\star$& & $\star$& & & & & & $\star$& & $\star$& \\
-max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-lcom& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-dam& $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & \\
-ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-cbo& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-ce& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-rfc& & & & & & & $\star$& & $\star$& & & & & & & & & & & & & & $\star$& & & & & & & & & & $\star$& \\
-dit& & & $\star$& & & & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & & & & & & & & $\star$& $\circ$& & & & \\
-mfa& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & $\star$& \\
-cam& & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & & & $\star$& & & & $\star$& & & & & & $\star$& & & & $\star$& & $\star$& \\
-avg\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-wmc& $\star$& & $\star$& & & & & & $\star$& & & & & & & & & & & & & & $\star$& & & & & & & & & & $\star$& \\
-moa& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-cbm& & & & & & & & & & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & & & $\star$& & & & $\star$& & & & & \\
-ic& $\star$& & & & $\star$& & & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & & & & & & & $\star$& $\circ$& & & & \\
-lcom3& & & & & $\star$& & $\star$& & & & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& & & & $\star$& & & & $\star$& & & & & \\
-
-  \end{tabular}
-    \caption{Feature seleciton for different datasets with  and without the tuning process over the objective of pd.
-For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.
- }
-\end{figure*}
-
 %%%%%%%%%%%%%% pd bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure*}
-\renewcommand{\baselinestretch}{0.5} 
+\renewcommand{\baselinestretch}{0.8}
 \scriptsize
@@
 
-%%%%%%%%%%%%%%%% features selection over pf%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
-  \hline\hline
-  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
-\\\hline
-  npm& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-loc& & & $\star$& & & & $\star$& & $\star$& & & $\circ$& & & & & & $\circ$& $\star$& & & & & & $\star$& & $\star$& $\circ$& & & $\star$& & $\star$& $\circ$\\
-amc& & & & & & & & & & & & & & & & & & & & & & & $\star$& & $\star$& & & & & & $\star$& & $\star$& \\
-max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-lcom& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
-dam& $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& & & $\star$& & $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& & & \\
-ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-cbo& & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & & & \\
-ce& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-rfc& & & & & & & $\star$& & $\star$& & & & & & & & & & & & & & $\star$& $\circ$& & & & $\circ$& & & & & $\star$& $\circ$\\
-dit& & & $\star$& & & $\circ$& & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & & & & & $\circ$& & & $\star$& & & & & \\
-mfa& $\star$& & $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& & & & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$\\
-cam& & & & & $\star$& & $\star$& & $\star$& & $\star$& & & & & & $\star$& & & & $\star$& & & & & & $\star$& $\circ$& & & $\star$& & $\star$& $\circ$\\
-avg\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-wmc& $\star$& & $\star$& & & & & & $\star$& & & & & & & & & & & & & & $\star$& & & & & $\circ$& & & & & $\star$& \\
-moa& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-cbm& & & & & & & & & & & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& & & & & & & $\star$& $\circ$& & & $\star$& & & & & \\
-ic& $\star$& & & & $\star$& & & & & & & & $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & & & $\circ$& & & $\star$& & & & & \\
-lcom3& & & & & $\star$& & $\star$& & & & & & $\star$& & $\star$& & & $\circ$& $\star$& & $\star$& & & & $\star$& & & $\circ$& $\star$& & & & & \\
-
-  \end{tabular}
-      \caption{Feature seleciton for different datasets with  and without the tuning process over the objective of pf.
-For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.
- }
-\end{figure*}
-
-%%%%%%%%%%%%%% pf bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%%%%%%%%%%%%%% precision bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure*}
-\renewcommand{\baselinestretch}{0.5} 
-\scriptsize
-\begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
-  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(pf) } \\
-  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
-\multicolumn{1}{c}{~}\\
-antV0 & 15 &       & 0 & {\rfour} & 12 & {\rone} & 0 & {\rfour} & 9 & {\rtwo} & 0 & {\rfour}\\
-antV1 & 5 & {\rthree} & 0 & {\rfour} & 20 &       & 0 & {\rfour} & 14 & {\rone} & 0 & {\rfour}\\
-antV2 & 0 & {\rfour} & 0 & {\rfour} & 10 &       & 0 & {\rfour} & 2 & {\rfour} & 0 & {\rfour}\\
-camelV0 & 0 & {\rfour} & 0 & {\rfour} & 3 &       & 0 & {\rfour} & 0 & {\rfour} & 0 & {\rfour}\\
-camelV1 & 69 &       & 0 & {\rfour} & 36 & {\rtwo} & 20 & {\rthree} & 26 & {\rthree} & 18 & {\rthree}\\
-ivyV0 & 63 &       & 0 & {\rfour} & 50 & {\rone} & 34 & {\rtwo} & 42 & {\rone} & 40 & {\rone}\\
-jeditV0 & 56 &       & 0 & {\rfour} & 24 & {\rtwo} & 0 & {\rfour} & 23 & {\rtwo} & 24 & {\rtwo}\\
-jeditV1 & 35 &       & 0 & {\rfour} & 20 & {\rtwo} & 1 & {\rfour} & 17 & {\rtwo} & 14 & {\rthree}\\
-jeditV2 & 46 &       & 0 & {\rfour} & 31 & {\rone} & 3 & {\rfour} & 21 & {\rtwo} & 16 & {\rthree}\\
-log4jV0 & 31 &       & 0 & {\rfour} & 13 & {\rtwo} & 0 & {\rfour} & 0 & {\rfour} & 0 & {\rfour}\\
-luceneV0 & 76 &       & 0 & {\rfour} & 35 & {\rtwo} & 24 & {\rthree} & 30 & {\rthree} & 21 & {\rthree}\\
-poiV0 & 70 &       & 0 & {\rfour} & 38 & {\rtwo} & 32 & {\rtwo} & 34 & {\rtwo} & 34 & {\rtwo}\\
-poiV1 & 0 & {\rfour} & 0 & {\rfour} & 8 &       & 0 & {\rfour} & 0 & {\rfour} & 0 & {\rfour}\\
-synapseV0 & 0 & {\rfour} & 0 & {\rfour} & 6 &       & 0 & {\rfour} & 1 & {\rfour} & 0 & {\rfour}\\
-velocityV0 & 99 &       & 0 & {\rfour} & 85 &       & 43 & {\rtwo} & 63 & {\rone} & 54 & {\rtwo}\\
-xercesV0 & 74 &       & 0 & {\rfour} & 52 & {\rone} & 1 & {\rfour} & 40 & {\rtwo} & 43 & {\rtwo}\\
-xercesV1 & 36 &       & 0 & {\rfour} & 26 & {\rone} & 0 & {\rfour} & 19 & {\rtwo} & 0 & {\rfour}\\
-\end{tabular}
-\end{minipage}\begin{minipage}{.15\linewidth}
-\begin{tabular}{|p{\linewidth}|}\hline
-
-~\\
-
-{\bf KEY:}
-
-~\\
-
-pf percentile ranges:
-
-~\\
-
-80th to 100th = {\rfour}
-
-60th to 80th ~ = {\rthree}
-
-40th to 60th  ~ = {\rtwo}
-
-20th to 40th  ~ = {\rone}
-
-~\\
-
-An absent bar denotes\newline 0th to 20th percentile.
-
-~\\
-
-Percentiles computed  separately
-for each data set.\\\hline
-\end{tabular}
-\end{minipage}
-\caption{Median pf values in tune once and test ten times experiment. 
-Gray bars  show  pf values
-discretized into 20th percentiles ranges from min to max.
-All data available from http://openscience.us/repo/effort.
-}\label{fig:nonc}
-\end{figure*}
-
-%%%%%%%%%%%%%% pf bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%% features selection over precision%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
-  \hline\hline
-  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
-\\\hline
-  npm& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & $\circ$& & & & & & \\
-loc& & & $\star$& & & & $\star$& & $\star$& & & & & & & $\circ$& & & $\star$& $\circ$& & & $\star$& & $\star$& $\circ$& $\star$& $\circ$& & & $\star$& & $\star$& \\
-amc& & & & & & & & & & & & & & & & & & & & & & & $\star$& & $\star$& $\circ$& & & & & $\star$& & $\star$& \\
-max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
-lcom& & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & & & \\
-dam& $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& & & \\
-ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
-cbo& & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & & & \\
-ce& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & $\circ$& & $\circ$& & & & & & \\
-noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-rfc& & & & & & & $\star$& & $\star$& & & & & & & & & & & & & $\circ$& $\star$& & & $\circ$& & $\circ$& & $\circ$& & & $\star$& \\
-dit& & & $\star$& & & & & & $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& & & & $\circ$& & & & $\circ$& $\star$& & & & & \\
-mfa& $\star$& & $\star$& & $\star$& & $\star$& & $\star$& & & & $\star$& & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& \\
-cam& & & & & $\star$& & $\star$& & $\star$& & $\star$& $\circ$& & & & & $\star$& & & & $\star$& $\circ$& & & & $\circ$& $\star$& & & & $\star$& & $\star$& \\
-avg\_cc& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & $\circ$& & $\circ$& & & & & & \\
-wmc& $\star$& & $\star$& & & & & & $\star$& & & & & & & & & & & & & $\circ$& $\star$& & & $\circ$& & $\circ$& & & & & $\star$& \\
-moa& & & & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & \\
-cbm& & & & & & & & & & & & & $\star$& & $\star$& & $\star$& & & & & & & & $\star$& & & & & $\circ$& & & & \\
-ic& $\star$& & & & $\star$& & & & & & $\star$& $\circ$& $\star$& & $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & & & & & & $\star$& $\circ$& & & & \\
-lcom3& & & & & $\star$& & $\star$& & & & & $\circ$& $\star$& & $\star$& & & & $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& & $\circ$& $\star$& & & & & \\
-
-  \end{tabular}
-  \caption{Feature seleciton for different datasets with and without the tuning process over the objective of precision.
-For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.}
-\end{figure*}
-
-%%%%%%%%%%%%%% precision bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\renewcommand{\baselinestretch}{0.5} 
+\renewcommand{\baselinestretch}{0.8}
 \scriptsize
@@
 
-%%%%%%%%%%%%%%%% features selection over F%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
-  \hline\hline
-  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
-\\\hline
-  npm& & & & $\circ$& & & & & & & & $\circ$& & & & & & & & & & & & $\circ$& & & & & & $\circ$& & & & \\
-loc& & & $\star$& & & & $\star$& & $\star$& & & & & $\circ$& & $\circ$& & $\circ$& $\star$& & & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$\\
-amc& & & & & & $\circ$& & & & & & $\circ$& & & & & & & & & & & $\star$& $\circ$& $\star$& & & & & & $\star$& $\circ$& $\star$& $\circ$\\
-max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-lcom& & $\circ$& & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & $\circ$& & $\circ$& & & & \\
-dam& $\star$& & $\star$& & $\star$& $\circ$& $\star$& & & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& $\circ$& & $\circ$\\
-ca& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-cbo& & $\circ$& & & & & & & & & & $\circ$& & & & & & & & & & & & $\circ$& & & & & & & & & & \\
-ce& & $\circ$& & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & \\
-noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-rfc& & $\circ$& & & & & $\star$& & $\star$& $\circ$& & $\circ$& & $\circ$& & $\circ$& & & & $\circ$& & & $\star$& & & & & $\circ$& & & & $\circ$& $\star$& $\circ$\\
-dit& & & $\star$& & & $\circ$& & & $\star$& & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& & $\circ$& & $\circ$& & $\circ$& & & & & $\star$& & & $\circ$& & $\circ$\\
-mfa& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$\\
-cam& & $\circ$& & & $\star$& $\circ$& $\star$& & $\star$& & $\star$& $\circ$& & & & $\circ$& $\star$& & & & $\star$& & & & & $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& \\
-avg\_cc& & & & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & $\circ$\\
-wmc& $\star$& & $\star$& $\circ$& & & & & $\star$& $\circ$& & $\circ$& & & & $\circ$& & & & & & & $\star$& $\circ$& & & & & & $\circ$& & & $\star$& $\circ$\\
-moa& & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & & & & & \\
-cbm& & & & & & $\circ$& & & & & & & $\star$& & $\star$& & $\star$& & & & & & & & $\star$& & & & & & & & & $\circ$\\
-ic& $\star$& $\circ$& & & $\star$& $\circ$& & & & & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & & & & & & & $\star$& $\circ$& & & & $\circ$\\
-lcom3& & & & $\circ$& $\star$& $\circ$& $\star$& & & $\circ$& & $\circ$& $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& & $\circ$& & $\circ$\\
-
-  \end{tabular}
-    \caption{Feature seleciton for different datasets with and without the tuning process over the objective of F measure.
-For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.}
-\end{figure*}
-
 \begin{figure*}
-\renewcommand{\baselinestretch}{0.5} 
+\renewcommand{\baselinestretch}{0.8}
 \scriptsize
@@
 
-%%%%%%%%%%%%%%%% features selection over G%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}[!ht]
+%%%%%%%%%%%%%%%%  counts of features for different goals%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+
+\renewcommand{\baselinestretch}{0.8}
 \scriptsize
 \centering
-  \begin{tabular}{c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c c|c }
-  \hline\hline
-  Features & \multicolumn{2}{c}{ant}&\multicolumn{2}{c}{antV1}&\multicolumn{2}{c}{antV2}&\multicolumn{2}{c}{camel}&\multicolumn{2}{c}{camelV1}&\multicolumn{2}{c}{ivy}&\multicolumn{2}{c}{jedit}&\multicolumn{2}{c}{jeditV1}&\multicolumn{2}{c}{jeditV2}&\multicolumn{2}{c}{log4j}&\multicolumn{2}{c}{lucene}&\multicolumn{2}{c}{poi}&\multicolumn{2}{c}{poiV1}&\multicolumn{2}{c}{synapse}&\multicolumn{2}{c}{velocity}&\multicolumn{2}{c}{xerces}&\multicolumn{2}{c}{xercesV1}
+  \begin{tabular}{c|c c|c c|c c|c c| c c }
+
+    & \multicolumn{2}{c|}{Pd} &  \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{F} &  \multicolumn{2}{c|}{SUM}\\
+ &&&&&&&&\\
+Features& \begin{sideways}naive\end{sideways}
+& \begin{sideways}tuned\end{sideways}
+& \begin{sideways}naive\end{sideways}
+& \begin{sideways}tuned\end{sideways}
+& \begin{sideways}naive\end{sideways}
+& \begin{sideways}tuned\end{sideways}
+& \begin{sideways}naive\end{sideways}
+& \begin{sideways}tuned\end{sideways}
 \\\hline
-  npm& & & & $\circ$& & & & & & $\circ$& & $\circ$& & & & & & & & & & $\circ$& & $\circ$& & & & & & & & & & \\
-loc& & & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& & & & $\circ$& & & & $\circ$& $\star$& $\circ$& & & & $\circ$& $\star$& & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$\\
-amc& & & & & & & & $\circ$& & $\circ$& & $\circ$& & & & & & & & & & & $\star$& $\circ$& $\star$& & & & & $\circ$& $\star$& $\circ$& $\star$& \\
-max\_cc& & & & & & & & & & & & & & & & & & & & & & & & & & $\circ$& & & & & & $\circ$& & \\
-lcom& & & & $\circ$& & & & & & $\circ$& & & & & & & & & & & & $\circ$& & $\circ$& & & & $\circ$& & & & & & \\
-dam& $\star$& & $\star$& & $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & \\
-ca& & & & & & & & & & & & $\circ$& & & & & & & & & & & & & & & & & & & & & & \\
-cbo& & & & & & & & & & $\circ$& & & & & & & & & & & & $\circ$& & $\circ$& & & & & & $\circ$& & $\circ$& & \\
-ce& & & & & & & & & & $\circ$& & & & $\circ$& & & & & & & & $\circ$& & $\circ$& & $\circ$& & & & & & $\circ$& & \\
-noc& & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & & \\
-rfc& & $\circ$& & $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& & $\circ$& & $\circ$& & $\circ$& & & & $\circ$& & $\circ$& $\star$& & & & & & & $\circ$& & $\circ$& $\star$& \\
-dit& & & $\star$& $\circ$& & & & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& & & & & $\circ$& & & & & $\star$& $\circ$& & $\circ$& & \\
-mfa& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& \\
-cam& & & & $\circ$& $\star$& & $\star$& $\circ$& $\star$& $\circ$& $\star$& $\circ$& & & & $\circ$& $\star$& $\circ$& & $\circ$& $\star$& & & & & $\circ$& $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& \\
-avg\_cc& & & & & & & & & & & & & & $\circ$& & & & & & & & $\circ$& & & & $\circ$& & & & & & $\circ$& & \\
-wmc& $\star$& & $\star$& & & $\circ$& & $\circ$& $\star$& $\circ$& & $\circ$& & & & $\circ$& & $\circ$& & $\circ$& & $\circ$& $\star$& $\circ$& & & & $\circ$& & $\circ$& & $\circ$& $\star$& \\
-moa& & & & $\circ$& & & & & & & & & & & & & & & & & & $\circ$& & $\circ$& & & & & & & & & & \\
-cbm& & & & & & & & & & $\circ$& & & $\star$& & $\star$& $\circ$& $\star$& & & & & & & & $\star$& & & & $\star$& $\circ$& & $\circ$& & \\
-ic& $\star$& & & $\circ$& $\star$& & & $\circ$& & & $\star$& $\circ$& $\star$& & $\star$& $\circ$& $\star$& & $\star$& & $\star$& & & & & & & & $\star$& $\circ$& & & & \\
-lcom3& & & & $\circ$& $\star$& & $\star$& $\circ$& & $\circ$& $\star$& $\circ$& $\star$& & $\star$& $\circ$& & & $\star$& $\circ$& $\star$& $\circ$& & & $\star$& $\circ$& & & $\star$& $\circ$& & $\circ$& & \\
+noc&	&	&	&	&	&	&	 &	 &	\\
+ca&	&	&	&	1&	&	&	 &	1&	\\
+max\_cc&	&	&	&	1&	&	&	 &	1&	\\
+moa&	&	&	&	1&	&	1&	 &	2&	\\
+avg\_cc&	&	&	&	3&	&	2&	 &	5&	\\
+cbo&	&	&	&	1&	&	3&	 &	4&	\\
+npm&	&	&	&	2&	&	4&	 &	6&	\\
+lcom&	&	&	&	1&	&	4&	 &	5&	\\
+ce&	&	&	&	3&	&	2&	 &	5&	\\
+amc&	4&	&	4&	1&	4&	5&	12&	6&	\\
+cbm&	6&	&	4&	1&	4&	2&	14&	3&	\\
+rfc&	4&	&	4&	4&	4&	9&	12&	13&	\\
+wmc&	5&	&	5&	3&	5&	7&	15&	10&	\\
+ic&	8&	1&	9&	3&	8&	8&	25&	12&	\\
+dit&	8&	1&	8&	5&	7&	8&	23&	14&	\\
+cam&	9&	&	9&	3&	9&	8&	27&	11&	\\
+loc&	9&	1&	9&	4&	9&	8&	27&	13&	\\
+lcom3&	9&	&	8&	5&	8&	13&	25&	18&	\\
+dam&	14&	&	14&	6&	14&	12&	42&	18&	\\
+mfa&	16&	3&	16&	6&	16&	16&	48&	25&	\\
 
   \end{tabular}
-    \caption{Feature seleciton for different datasets with and without the tuning process over the objective of G measure.
-For each data set, the stars in left and right columns are representing the features used to build defect prediction model without and with the tuning process, respectively.}
-\end{figure*}
-
-\begin{figure*}
-\renewcommand{\baselinestretch}{0.5} 
-\scriptsize
-\begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
-  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(G ) } \\
-  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
-\multicolumn{1}{c}{~}\\
-antV0 & 65 & {\rtwo} & 68 & {\rthree} & 53 &         &$\bigstar$ 75 & {\rfour} & 71 & {\rfour} & 72 & {\rfour}\\
-antV1 & 12 &         &$\bigstar$ 60 & {\rfour} & 52 & {\rfour} &$\bigstar$ 60 & {\rfour} & 57 & {\rfour} &$\bigstar$ 60 & {\rfour}\\
-antV2 & 0 &         &$\bigstar$ 72 & {\rfour} & 53 & {\rthree} & 63 & {\rfour} & 62 & {\rfour} & 69 & {\rfour}\\
-camelV0 & 0 &         & 60 & {\rfour} & 10 &         & 55 & {\rfour} & 60 & {\rfour} &$\bigstar$ 62 & {\rfour}\\
-camelV1 & 45 &         & 56 & {\rfour} & 53 & {\rthree} & 56 & {\rfour} &$\bigstar$ 57 & {\rfour} &$\bigstar$ 57 & {\rfour}\\
-ivyV0 & 53 &         & 60 & {\rone} & 63 & {\rtwo} &$\bigstar$ 74 & {\rfour} & 70 & {\rfour} & 68 & {\rthree}\\
-jeditV0 & 59 &         & 71 & {\rthree} & 71 & {\rthree} & 67 & {\rtwo} &$\bigstar$ 75 & {\rfour} &$\bigstar$ 75 & {\rfour}\\
-jeditV1 & 70 & {\rtwo} & 69 & {\rtwo} & 62 &         & 75 & {\rfour} & 75 & {\rfour} &$\bigstar$ 76 & {\rfour}\\
-jeditV2 & 49 &         & 62 & {\rthree} & 48 &         & 61 & {\rthree} & 61 & {\rthree} &$\bigstar$ 66 & {\rfour}\\
-log4jV0 & 53 & {\rtwo} & 53 & {\rtwo} & 46 &         & 46 &         &$\bigstar$ 61 & {\rfour} & 57 & {\rthree}\\
-luceneV0 & 37 &         & 61 & {\rfour} & 55 & {\rthree} & 56 & {\rthree} & 61 & {\rfour} &$\bigstar$ 64 & {\rfour}\\
-poiV0 & 45 &         & 59 & {\rthree} & 66 & {\rfour} & 55 & {\rtwo} &$\bigstar$ 67 & {\rfour} & 61 & {\rthree}\\
-poiV1 & 5 &         & 51 & {\rfour} & 22 & {\rone} & 39 & {\rtwo} &$\bigstar$ 62 & {\rfour} & 56 & {\rfour}\\
-synapseV0 & 0 &         & 55 & {\rfour} & 43 & {\rthree} & 64 & {\rfour} & 63 & {\rfour} &$\bigstar$ 65 & {\rfour}\\
-velocityV0 & 3 &         & 56 & {\rfour} & 26 & {\rtwo} &$\bigstar$ 59 & {\rfour} & 51 & {\rfour} & 56 & {\rfour}\\
-xercesV0 & 37 &         & 43 & {\rtwo} & 47 & {\rfour} & 43 & {\rtwo} &$\bigstar$ 49 & {\rfour} & 48 & {\rfour}\\
-xercesV1 & 26 &         &$\bigstar$ 71 & {\rfour} & 19 &         & 36 & {\rone} & 36 & {\rone} & 33 & {\rone}\\
-%Albrecht  &   7         &   24   &   Projects from IBM   & 28 &     & 40 & {\rtwo} & 38 & {\rtwo} & 38 & {\rtwo} & 49 & {\rfour} \\
-%China      &   18       &   488   &   Projects from Chinese software companies   &   38   &  {\rtwo}  &   34   &       &   34   &       &   35   &  {\rone}   &   41   &   {\rfour}\\
-%Cosmic     &   y   &   y   &   Projects described in functiion points   &   98   &   {\rfour}   &   75   &       &   85   &    {\rtwo}   &   85   &   {\rtwo}    &   89   &   {\rtwo}\\
-%ISBSG10    &   y   &   y   &   From the ISBSG benchmark suite   &   56   &       &   62   &     &   126   &   {\rfour}   &   66   &   {\rone}   &   65   &   {\rone}\\
-%Kemerer    &   7   &   15   &   Large business applications   &   42   &  {\rtwo}  &   24   &   &   55   &  {\rfour} &   55   &   {\rfour}   &   55   &   {\rfour}\\
-%Kitchenham &    6   &   145   &  y    &   34   &   &   43   &   {\rthree}   &   34   &  &   43   &  {\rthree}  &   47   &  {\rfour}  \\
-%Maxwell    &   27  &   62  & Projects from commercial banks in Finland   &   57   &   {\rtwo}   &   56   &   {\rtwo}   &   47   &   &   53   &  {\rone} &   64   &   {\rfour}\\
-%Miyazaki   &   8   &   48 &Japanese software projects developed in COBOL   &   39   &       &   41   &   &   41   &    &   57   &   {\rfour}   &   57   &   {\rfour}\\
-%Telecom    &   3   &   18   &   Maintenance projects for telecom companies   &   23   &       &   26   &   {\rtwo}   &   31   & {\rfour}  &   31   &   {\rfour}   &   31   &   {\rfour}\\
-%Usp05      &   7   &  203  &  Collected from university student projects   &   30   &    &   50   & {\rfour} &   45   & {\rthree}  &   40   &   {\rtwo}  &   50   &   {\rfour}\\
-\end{tabular}
-\end{minipage}\begin{minipage}{.15\linewidth}
-\begin{tabular}{|p{\linewidth}|}\hline
-
-~\\
-
-{\bf KEY:}
-
-~\\
-
-G percentile ranges:
-
-~\\
-
-80th to 100th = {\rfour}
-
-60th to 80th ~ = {\rthree}
-
-40th to 60th  ~ = {\rtwo}
-
-20th to 40th  ~ = {\rone}
-
-~\\
-
-An absent bar denotes\newline 0th to 20th percentile.
-
-~\\
-
-Percentiles computed  separately
-for each data set.\\\hline
-\end{tabular}
-\end{minipage}
-\caption{Median G values in tune once and test ten times experiment. 
-Gray bars  show  G values
-discretized into 20th percentiles ranges from min to max.
-All data available from http://openscience.us/repo/effort.
-}\label{fig:nonc}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%  time for different objectives %%%%%%%%%%%%%%%%%%%%%
-\clearpage
-%%%%time for pd %%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{l|c |c |c |c |c |c }
-    \hline\hline
-    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
-    \hline
-    ant & 241.5 & 12.6 & 7.4 & 0.8 & 13.3 & 1.4\\
-    antV1 & 347.5 & 23.5 & 11.6 & 0.8 & 19.5 & 2.0\\
-    antV2 & 696.5 & 60.0 & 23.6 & 1.5 & 22.6 & 3.1\\
-    camel & 1412.6 & 76.5 & 34.7 & 1.7 & 51.1 & 3.0\\
-    camelV1 & 3391.9 & 230.6 & 36.1 & 2.4 & 46.3 & 6.9\\
-    ivy & 93.9 & 9.9 & 5.1 & 0.6 & 9.7 & 1.6\\
-    jedit & 679.2 & 51.1 & 12.7 & 0.8 & 18.1 & 2.8\\
-    jeditV1 & 1078.5 & 64.9 & 17.2 & 0.9 & 24.6 & 3.0\\
-    jeditV2 & 838.0 & 68.2 & 16.4 & 1.1 & 23.4 & 3.4\\
-    log4j & 190.8 & 13.4 & 5.2 & 0.4 & 11.0 & 1.4\\
-    lucene & 421.0 & 27.6 & 9.2 & 0.7 & 13.3 & 2.3\\
-    poi & 348.6 & 40.4 & 10.6 & 0.9 & 21.7 & 2.7\\
-    poiV1 & 1060.7 & 69.4 & 20.8 & 1.0 & 26.3 & 2.6\\
-    synapse & 350.9 & 18.5 & 9.5 & 0.5 & 14.4 & 1.5\\
-    velocity & 257.0 & 28.3 & 7.5 & 0.5 & 13.3 & 1.9\\
-    xerces & 239.9 & 21.4 & 14.8 & 0.8 & 15.2 & 2.1\\
-    xercesV1 & 2433.9 & 130.3 & 27.6 & 1.4 & 25.3 & 3.7\\
-  \end{tabular}
-  \caption{Time (in seconds) spent on different models over the objective of pd}
-\end{figure*}
-
-%%%%time for pf %%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{l|c |c |c |c |c |c }
-    \hline\hline
-    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
-    \hline
-    ant & 33.3 & 14.1 & 2.4 & 0.7 & 2.6 & 1.7\\
-    antV1 & 59.3 & 25.5 & 4.2 & 0.9 & 3.0 & 2.2\\
-    antV2 & 131.4 & 67.4 & 3.0 & 1.7 & 4.2 & 3.7\\
-    camel & 167.8 & 85.7 & 3.9 & 2.0 & 5.1 & 3.5\\
-    camelV1 & 503.5 & 325.1 & 68.5 & 3.6 & 146.6 & 8.8\\
-    ivy & 116.4 & 11.5 & 8.5 & 1.3 & 23.9 & 1.9\\
-    jedit & 336.6 & 59.9 & 6.7 & 0.9 & 29.3 & 3.4\\
-    jeditV1 & 159.9 & 79.2 & 2.1 & 1.2 & 36.9 & 3.5\\
-    jeditV2 & 151.4 & 80.0 & 21.8 & 1.4 & 38.6 & 3.9\\
-    log4j & 37.4 & 15.5 & 1.9 & 0.5 & 5.0 & 1.8\\
-    lucene & 436.4 & 33.9 & 17.0 & 1.0 & 49.4 & 3.2\\
-    poi & 202.7 & 48.5 & 24.6 & 1.3 & 50.4 & 3.5\\
-    poiV1 & 184.3 & 79.9 & 2.5 & 1.5 & 5.5 & 3.2\\
-    synapse & 36.9 & 20.5 & 1.4 & 0.7 & 2.7 & 1.7\\
-    velocity & 157.9 & 31.6 & 10.4 & 0.7 & 33.2 & 2.2\\
-    xerces & 59.5 & 23.5 & 19.6 & 1.2 & 31.0 & 2.4\\
-    xercesV1 & 286.6 & 151.8 & 8.0 & 1.8 & 5.4 & 4.5\\
-  \end{tabular}
-  \caption{Time (in seconds) spent on different models over the objective of pf}
-\end{figure*}
-
-%%%%time for prec %%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{l|c |c |c |c |c |c }
-    \hline\hline
-    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
-    \hline
-    ant & 158.6 & 13.3 & 8.8 & 0.7 & 18.1 & 1.6\\
-    antV1 & 298.9 & 25.4 & 13.5 & 0.9 & 15.8 & 2.2\\
-    antV2 & 632.0 & 65.0 & 14.4 & 1.7 & 29.3 & 3.6\\
-    camel & 566.3 & 94.3 & 26.0 & 1.8 & 20.8 & 5.5\\
-    camelV1 & 4954.0 & 243.0 & 52.1 & 2.3 & 42.7 & 7.2\\
-    ivy & 148.7 & 10.0 & 8.6 & 0.6 & 11.0 & 1.6\\
-    jedit & 972.5 & 51.9 & 15.8 & 0.8 & 22.3 & 2.9\\
-    jeditV1 & 1102.5 & 73.6 & 19.7 & 0.9 & 46.5 & 3.5\\
-    jeditV2 & 837.5 & 76.9 & 15.7 & 1.3 & 65.3 & 3.7\\
-    log4j & 289.2 & 17.1 & 6.8 & 0.6 & 17.1 & 1.6\\
-    lucene & 471.6 & 29.6 & 8.7 & 0.8 & 16.8 & 2.5\\
-    poi & 651.4 & 52.0 & 11.4 & 1.1 & 23.1 & 3.3\\
-    poiV1 & 1666.8 & 86.2 & 13.8 & 1.4 & 25.7 & 3.2\\
-    synapse & 209.2 & 23.7 & 9.2 & 0.7 & 15.8 & 1.7\\
-    velocity & 345.5 & 33.5 & 11.5 & 0.7 & 12.7 & 2.3\\
-    xerces & 392.2 & 27.2 & 13.9 & 1.2 & 43.0 & 3.0\\
-    xercesV1 & 1619.8 & 157.1 & 23.8 & 1.7 & 34.8 & 5.0\\
-  \end{tabular}
-  \caption{Time (in seconds) spent on different models over the objective of prec}
-\end{figure*}
-
-%%%%time for F %%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{l|c |c |c |c |c |c }
-    \hline\hline
-    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
-    \hline
-    ant & 302.5 & 13.3 & 6.9 & 0.7 & 13.8 & 1.6\\
-    antV1 & 328.7 & 27.2 & 12.7 & 0.8 & 15.4 & 2.0\\
-    antV2 & 1030.2 & 73.0 & 31.3 & 1.7 & 34.6 & 4.2\\
-    camel & 1838.4 & 92.5 & 33.4 & 2.0 & 43.7 & 3.4\\
-    camelV1 & 4352.4 & 275.8 & 46.2 & 5.4 & 42.8 & 7.8\\
-    ivy & 167.9 & 11.9 & 4.1 & 0.7 & 18.8 & 1.8\\
-    jedit & 830.6 & 62.9 & 7.8 & 1.0 & 45.7 & 3.3\\
-    jeditV1 & 1055.2 & 81.8 & 13.6 & 1.1 & 30.7 & 3.6\\
-    jeditV2 & 1322.7 & 92.2 & 18.1 & 1.3 & 35.3 & 4.1\\
-    log4j & 370.7 & 16.3 & 5.6 & 0.5 & 16.1 & 1.7\\
-    lucene & 385.3 & 31.9 & 8.8 & 0.8 & 21.3 & 2.6\\
-    poi & 720.7 & 46.2 & 10.2 & 0.9 & 19.9 & 3.0\\
-    poiV1 & 1229.0 & 79.4 & 14.9 & 1.2 & 25.9 & 2.9\\
-    synapse & 377.0 & 21.6 & 10.3 & 0.6 & 21.0 & 1.7\\
-    velocity & 275.6 & 39.6 & 8.9 & 0.7 & 13.2 & 2.1\\
-    xerces & 310.7 & 25.4 & 13.3 & 0.9 & 21.6 & 2.3\\
-    xercesV1 & 1792.1 & 147.9 & 37.1 & 1.6 & 35.4 & 4.0\\
-  \end{tabular}
-  \caption{Time (in seconds) spent on different models over the objective of F}
-\end{figure*}
+    \caption{Counts of features selected by different goals.
+For each goal, the numbers in right and left columns represent the counts of features selected for all the data sets with and without tuning processes.}
+\end{figure}
 
 %%%%time for G %%%%%%
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{l|c |c |c |c |c |c }
-    \hline\hline
-    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
-    \hline
-    ant & 164.0 & 13.9 & 9.2 & 0.9 & 14.5 & 1.5\\
-    antV1 & 560.3 & 27.3 & 15.5 & 1.0 & 17.2 & 2.4\\
-    antV2 & 1743.9 & 77.3 & 18.9 & 1.7 & 25.5 & 3.6\\
-    camel & 1823.1 & 93.0 & 39.8 & 1.9 & 39.1 & 3.4\\
-    camelV1 & 6679.7 & 234.3 & 39.7 & 2.2 & 74.5 & 7.0\\
-    ivy & 261.9 & 10.9 & 9.9 & 0.6 & 17.4 & 1.6\\
-    jedit & 993.8 & 54.4 & 11.1 & 0.8 & 23.7 & 2.8\\
-    jeditV1 & 1110.0 & 68.5 & 12.3 & 0.9 & 27.2 & 3.0\\
-    jeditV2 & 858.2 & 72.5 & 15.4 & 1.1 & 23.3 & 3.4\\
-    log4j & 247.7 & 15.2 & 3.8 & 0.4 & 9.1 & 1.4\\
-    lucene & 610.9 & 30.6 & 6.1 & 0.7 & 28.7 & 2.4\\
-    poi & 1466.6 & 47.4 & 18.3 & 0.9 & 33.0 & 2.7\\
-    poiV1 & 1365.6 & 77.4 & 17.2 & 1.1 & 31.1 & 2.7\\
-    synapse & 202.6 & 21.9 & 8.0 & 0.5 & 19.8 & 1.5\\
-    velocity & 869.8 & 31.4 & 10.5 & 0.6 & 29.8 & 1.9\\
-    xerces & 534.1 & 27.1 & 12.6 & 0.8 & 24.1 & 2.0\\
-    xercesV1 & 2825.7 & 143.5 & 22.4 & 1.5 & 48.1 & 3.8\\
-  \end{tabular}
-  \caption{Time (in seconds) spent on different models over the objective of G}
-\end{figure*}
+
+\section{Discussion}
+Data torturing, on not? Offer insight on the complexities of data sets, demanding
+that before they are used, we spend more time describing the context of use. Not offering
+conclusions that are over-stated. Taking care to precisely describe the boundaries of a 
+conclusion. While at the same time showing how to makde better conclusions on new
+data, whenever it arrives. And ensuring that those new conclusions are tuned
+to the goals of the business users who are funding the analysis and will use its results.
 

### 2015-03-03 tuningpredictor.tex

@@
 The next set of settings concern how many neighbors to use (k=1,2,5,etc).
-Some researchers set “k” in dynamic pre-learning phase that checks the training data to find what “k” works best for that data.
+Some researchers set ``k'' in dynamic pre-learning phase that checks the training data to find what ``k'' works best for that data.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \renewcommand{\baselinestretch}{0.8}
+
 \scriptsize  
-\begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
-  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(precision) } \\
-  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
-\multicolumn{1}{c}{~}\\
+\begin{tabular}{r|r@{~}l@{~}|r@{~}l|r@{~}l|r@{~}l|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
+      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forests}         \\\hline
+  Data set   &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{Naive}  &   \multicolumn{2}{c}{Tuned}\\\hline
+
 antV0 & 30 &         & $\bigstar$ 89 & {\rfour} & 27 &         &$\bigstar$ 89 & {\rfour} & 40 & {\rone} &$\bigstar$ 89 & {\rfour}\\
@@
 \end{tabular}
-\end{minipage}\begin{minipage}{.15\linewidth}
-\begin{tabular}{|p{\linewidth}|}\hline
-
-~\\
-
-{\bf KEY:}
-
-~\\
-
-precision percentile ranges:
-
-~\\
-
-80th to 100th = {\rfour}
-
-60th to 80th ~ = {\rthree}
-
-40th to 60th  ~ = {\rtwo}
-
-20th to 40th  ~ = {\rone}
-
-~\\
-
-An absent bar denotes\newline 0th to 20th percentile.
-
-~\\
-
+
+\caption{Precision values in tune   and naive runs.
+All data available from http://openscience.us/repo/effort. {\bf KEY:}
+  percentile ranges:\newline
+80th to 100th= {\rfour};
+60th to 80th= {\rthree}; 
+40th to 60th= {\rtwo};
+20th to 40th= {\rone};
+an absent bar shows  0th to 20th.
 Percentiles computed  separately
-for each data set.\\\hline
-\end{tabular}
-\end{minipage}
-\caption{Median precision values in tune once and test ten times experiment. 
-Gray bars  show  precision values
-discretized into 20th percentiles ranges from min to max.
-All data available from http://openscience.us/repo/effort.
+for each row.
+
 }\label{fig:nonc}
-\end{figure*}
+\end{figure}
 
@@
 \begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
+\begin{tabular}{r@{~}|r@{~}l|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|@{~}r@{~}l|r@{~}l|@{~}r@{~}l}
   \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(F ) } \\
@@
 \multicolumn{1}{c}{~}\\
-antV0 &$\bigstar$ 39 & {\rfour} & 26 & {\rone} & 32 & {\rtwo} & 25 &         & 25 &         & 22 &        \\
-antV1 & 11 &         &$\bigstar$ 85 & {\rfour} & 40 & {\rone} & 49 & {\rtwo} & 39 & {\rone} & 33 & {\rone}\\
-antV2 & 0 &         &$\bigstar$ 86 & {\rfour} & 44 & {\rtwo} & 51 & {\rtwo} & 52 & {\rthree} & 56 & {\rthree}\\
-camelV0 & 0 &         &$\bigstar$ 28 & {\rfour} & 9 & {\rone} &$\bigstar$ 28 & {\rfour} & 34 & {\rfour} & 31 & {\rfour}\\
-camelV1 & 34 & {\rthree} &$\bigstar$ 35 & {\rfour} & 31 &         & 33 & {\rtwo} & 33 & {\rtwo} & 30 &        \\
-ivyV0 & 27 &         & 30 & {\rone} & 30 & {\rone} & 32 & {\rthree} &$\bigstar$ 35 & {\rfour} &$\bigstar$ 35 & {\rfour}\\
-jeditV0 & 50 &         & 55 & {\rtwo} & 56 & {\rtwo} & 55 & {\rtwo} &$\bigstar$ 61 & {\rfour} & 60 & {\rfour}\\
-jeditV1 & 37 & {\rone} & 34 &         & 36 &         & 47 & {\rfour} & 45 & {\rthree} &$\bigstar$ 48 & {\rfour}\\
-jeditV2 & 4 &         &$\bigstar$ 99 & {\rfour} & 5 &         & 9 &         & 9 &         & 11 &        \\
-log4jV0 & 62 & {\rfour} & 7 &         & 47 & {\rthree} &$\bigstar$ 64 & {\rfour} & 53 & {\rfour} & 45 & {\rthree}\\
-luceneV0 & 70 & {\rthree} & 73 & {\rfour} & 56 &         &$\bigstar$ 75 & {\rfour} & 70 & {\rthree} &$\bigstar$ 75 & {\rfour}\\
-poiV0 &$\bigstar$ 78 & {\rfour} & 63 &         & 74 & {\rthree} & 70 & {\rtwo} & 73 & {\rthree} & 72 & {\rtwo}\\
-poiV1 & 5 &         &$\bigstar$ 78 & {\rfour} & 21 & {\rone} &$\bigstar$ 78 & {\rfour} & 76 & {\rfour} &$\bigstar$ 78 & {\rfour}\\
-synapseV0 & 0 &         & 2 &         & 40 & {\rthree} &$\bigstar$ 56 & {\rfour} & 52 & {\rfour} & 55 & {\rfour}\\
-velocityV0 & 51 &         & 51 &         & 49 &         & 51 &         & 53 & {\rone} &$\bigstar$ 59 & {\rfour}\\
-xercesV0 & 22 & {\rthree} & 20 & {\rone} & 21 & {\rtwo} & 18 &         & 23 & {\rfour} & 22 & {\rthree}\\
-xercesV1 & 23 & {\rone} & 2 &         & 18 & {\rone} & 36 & {\rtwo} & 68 & {\rfour} &$\bigstar$ 71 & {\rfour}\\
+ant0 &$\bigstar$ 39 & {\rfour} & 26 & {\rone} & 32 & {\rtwo} & 25 &         & 25 &         & 22 &        \\
+ant1 & 11 &         &$\bigstar$ 85 & {\rfour} & 40 & {\rone} & 49 & {\rtwo} & 39 & {\rone} & 33 & {\rone}\\
+ant2 & 0 &         &$\bigstar$ 86 & {\rfour} & 44 & {\rtwo} & 51 & {\rtwo} & 52 & {\rthree} & 56 & {\rthree}\\
+camel0 & 0 &         &$\bigstar$ 28 & {\rfour} & 9 & {\rone} &$\bigstar$ 28 & {\rfour} & 34 & {\rfour} & 31 & {\rfour}\\
+camel1 & 34 & {\rthree} &$\bigstar$ 35 & {\rfour} & 31 &         & 33 & {\rtwo} & 33 & {\rtwo} & 30 &        \\
+ivy0 & 27 &         & 30 & {\rone} & 30 & {\rone} & 32 & {\rthree} &$\bigstar$ 35 & {\rfour} &$\bigstar$ 35 & {\rfour}\\
+jedit0 & 50 &         & 55 & {\rtwo} & 56 & {\rtwo} & 55 & {\rtwo} &$\bigstar$ 61 & {\rfour} & 60 & {\rfour}\\
+jedit1 & 37 & {\rone} & 34 &         & 36 &         & 47 & {\rfour} & 45 & {\rthree} &$\bigstar$ 48 & {\rfour}\\
+jedit2 & 4 &         &$\bigstar$ 99 & {\rfour} & 5 &         & 9 &         & 9 &         & 11 &        \\
+log4j0 & 62 & {\rfour} & 7 &         & 47 & {\rthree} &$\bigstar$ 64 & {\rfour} & 53 & {\rfour} & 45 & {\rthree}\\
+lucene0 & 70 & {\rthree} & 73 & {\rfour} & 56 &         &$\bigstar$ 75 & {\rfour} & 70 & {\rthree} &$\bigstar$ 75 & {\rfour}\\
+poi0 &$\bigstar$ 78 & {\rfour} & 63 &         & 74 & {\rthree} & 70 & {\rtwo} & 73 & {\rthree} & 72 & {\rtwo}\\
+poi1 & 5 &         &$\bigstar$ 78 & {\rfour} & 21 & {\rone} &$\bigstar$ 78 & {\rfour} & 76 & {\rfour} &$\bigstar$ 78 & {\rfour}\\
+synapse0 & 0 &         & 2 &         & 40 & {\rthree} &$\bigstar$ 56 & {\rfour} & 52 & {\rfour} & 55 & {\rfour}\\
+velocity0 & 51 &         & 51 &         & 49 &         & 51 &         & 53 & {\rone} &$\bigstar$ 59 & {\rfour}\\
+xerces0 & 22 & {\rthree} & 20 & {\rone} & 21 & {\rtwo} & 18 &         & 23 & {\rfour} & 22 & {\rthree}\\
+xerces1 & 23 & {\rone} & 2 &         & 18 & {\rone} & 36 & {\rtwo} & 68 & {\rfour} &$\bigstar$ 71 & {\rfour}\\
 \end{tabular}
@@
 
+\begin{figure}[!t]
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+Some goals related to aspects of defect prediction:
+\be
+\item
+Mission-critical systems are risk averse and may accept very high false alarm rates,
+just as long as they catch any life-threatening possibility. That is, such projects
+do not care about effort- they want to {\em maximize recall} regardless of any impact
+that might have on the false alarm rate.
+\item
+Cost averse managers may accept lower probabilities of
+detection (the recall measure), just as long as they {\em do not waste budgets on false alarms}. This community
+seeks to {\em minimize false alarms} while maintaining {\em some level of adequate recall}.
+\item  Suppose a new hire wants
+ to impress their manager. That 
+ new hire might want to ensure that no result presented to  management contains  true negative;
+i.e. they wish to {\em maximize precision}.
+\item
+Some communities do not care about   low precision,
+just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction 
+{\em selectivity} and offer an
+extensive discussion of the merits of this measure~\cite{hayes06}.
+\ee
+\\\hline
+Beyond defect prediction are other goals that combine defect prediction with other economic
+factors:
+\be
+\setcounter{enumi}{4}
+\item
+Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
+say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
+that contain the most bugs.
+\item In other work, Yin et al. are concerned about
+ {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
+These bugs occur  when (say) developers try to fix parts of the code
+where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
+for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
+\item In {\em Better-faster-cheaper}, we seek  project changes that lead
+to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
+\item {\em  Rush-to-market} is another economic-based optimization measure.
+A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
+as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
+in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
+used to subsequently fix any issues with version 1.0)~\cite{huang06}.
+\ee
+\\\hline
+All the above measures relate to the tendency of a predictor to find something. Another style
+of measure would be to check the {\em variability} of that predictor:
+\be
+\setcounter{enumi}{8}
+\item
+In their study on reproducibility of SE results,
+ Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
+Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
+\ee
+\\\hline
+\end{tabular}
+\caption{Reasoning about software many have many different goals including the nine shown here. Many of
+these goals are defined in terms of 
+\fig{criteria}.
+}\label{fig:goals}
+\end{figure}
+\fig{goals} lists other performance measures that we have seen at client sites or in the literature. Note that:
+\be
+\item This list is very long.
+\item This list keeps growing.
+\ee As to this second point,
+often when we work
+with new clients, they surprise us with yet another domain-specific criteria that is important for the business.
+That is, neither \fig{criteria} or \fig{goals} is not a complete list of all possible assessment criteria.
+
+Our reading of the defect prediction literature is that most papers only explore a small subset of 
+ \fig{criteria} or \fig{goals}. We think this is a mistake and researchers should more to a more general
+framework where they explore a wide and changing set of evaluation criteria. 
+Hence, this paper.
+
 \end{document}

### 2015-03-05 tuningpredictor.tex
Updates from ShareLaTeX

@@
 
+XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores.
+Given that, the next question becomes ``what performance scores do you want?''.
+This is an interesting issue since there is no single best answer.
+XXX
+
 How ``true'' are the  models generated by software analytics?
@@
     Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
-pd&242&13&19&7&1&9&13&1&10\\ 
-prec&159&13&12&9&1&13&18&2&11\\
-f&303&13&23&7&1&10&14&2&9 
+pd&71.4&1.2&60&4.4&0.1&44&7.1&0.2&36\\ 
+prec&82.8&1.4&59&3.9&0.1&39&7.4&0.2&37\\
+f&86.1&1.2&72&3.3&0.1&33&6.7&0.2&34
   \end{tabular}

### 2015-03-10 dm101.tex
working on pages 1,2

Software assessment budgets are finite
while assessment effectiveness increases 
exponentially with assessment effort.
Lowry et al. warn that  
the state space explosion problem imposes
strict limits on how much a system can be explored
via automatic formal methods~\cite{lowrey98}.
For standard black-box testing methods,
a {\em linear} increase
in the confidence $C$ that we have found all defects
can take {\em exponentially} more effort.
For example, for one-in-a-thousand detects,
moving $C$ from  
90\% to 94\% to 98\% takes 2301, 2812, and 3910 black box
probes, respectively.\footnote{A randomly selected 
input to a program will find a fault with probability $p$.
After $N$ random black-box tests, the chances of the inputs 
not revealing any fault 
is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
which can be rearranged to 
 $N(C,p)=\frac{log(1 -
C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}

Exponential costs quickly exhaust finite resources.
Standard practice is to apply the best
available assessment methods on the sections of the program that the
best available domain knowledge declares is most critical.  We endorse
this approach.  Clearly, the most critical sections require the best
known assessment methods. However, this focus on certain sections
can blind us to defects in other areas.
Therefore, standard practice should be augmented
with a  {\em
lightweight sampling policy} to explore the rest of the system.  This
sampling policy will always be incomplete.
Nevertheless, it is the recommended option when
resources do not permit a complete assessment of the whole system.

There are many reasons to study defect  defect predictors learned from
static code attributes: they are   {\em easy to
use}, {\em widely-used}, and {\em useful} to use.

{\em Easy to use:} Static code attributes can be automatically and cheaply collected, even for very large systems~\cite{nagappan05}.
By contrast, 
other methods such as manual code reviews are labor-intensive.
Depending on the review methods 8 to 20 LOC/minute can be
inspected and this effort repeats for all members of the review team,
which can be as large as four or six~\cite{me02f}.

{\em Widely used:} Many researchers use static attributes to guide software 
quality predictions.
Verification and validation (V\&V) textbooks
(\cite{rakitin01}) advise using static code complexity attributes
to decide which modules are worthy of manual inspections.  
For several  years, one of us (Menzies) worked on-site at the NASA software Independent Verification
and Validation facility
and he
knows of several large government software contractors that won't
review software modules {\em unless} tools like McCabe predict that
they are fault prone.

{\em Useful:}
A
standard result for defect predictors is that they find the location of  70\% (or more)
of the defects in code.
This is markedly
higher than other currently-used
industrial
methods such as manual code reviews:
\bi
\item
A panel at {\em IEEE Metrics
2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
of defects.
\item
Raffo found that the defect detection capability of
industrial review methods have mode defect detection rates
of around 50\%
 for full Fagan inspections~\cite{fagan76} to
21\% for less-structured inspections.
\ei
Defect prediction scales well to a commercial
context. Defect predicting technology has been
commercialized in {\it Predictive}~\cite{turner06} a
%scalable product suite to analyze and predict
defects in software projects. Predictive was observed to
highlight simimilar issues to those found   with the more expensive tools. But,
Predictive was able to faster process a larger code
base than the more expensive tool~\cite{turner06}.

In addition, defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey). When the inspection teams focused on the modules that trigger the defect predictors, they found up to 70\% of the defects using just 40\% of their QA effort (measured in staff hours)~\cite{tosun10}.

Finally, a subsequent study on the Turkish software
compared how much code needs to be inspected using
random selection vs. selection via defect
predictors. Using random testing, 87\% of the files
would have to be inspected in order to detect 87\%
of the defects. However, if the inspection process
was restricted to the 25\% of the files that trigger
the defect predictors, then 88\% of the defects
could be found. That is, the same level of defect
detection (after inspection) can be achieved using
$(87-25)/87=71$\%less effort
\cite{tosun09}.

### 2015-03-10 tuningpredictor.tex
add more functions in DE pseudo code
working on pages 1,2

@@
 \begin{abstract}
-
-software defect prediction with various 
-empirical data sets. Those proposed leaners are always evaluated against the state of the art 
-predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
-accuracy indicators, the newer predictors outperform counterparts in selected experimental 
-settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
-forest, 
-neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
-forest algorithm. the impact of internal parameters in those methods have been neglected 
-during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
-predictors with search-based software engineering algorithm. Specifically, we used differential 
-evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
-and then predictors with optimal parameters obtained from tuning process will be applied to 
-predict defects. By comparing the performance of predictors with and without tuning process,  
-we observe that tuning improves the predictors' performance and predictors woking with 
-different data sets need different parameters. Our results also suggest that we should not use 
-the predictors of the shelf with their default parameters and tuning should be a processor 
-combined with any predictor with built-in parameters.
+When learning
+software defect predictors from static code attributes,   a
+very simple optimizer called differential evolution needs can quickly
+find  good tunings for that learner.
+Such tunings can have a dramatic change to the performance of a learner;
+e.g. in this paper we show that tuning can alter the precision of
+a software defect predictor from 2\% to 98\%.
+
+These results suggest that it is time to change standard practice in
+software analytics. Specifically,
+it is no longer enough to just run a data miner and present the result
+{\em without} first conducting an tuning optimizations study.
 
@@
 
-\begin{raggedleft}
-{\em ``The  common misunderstanding about science 
-is that scientists seek and find truth. They don't- 
-they make and test models.''}\\ -- Neil Gershenfeld
-
-{\em Essentially, all models are wrong, but some are useful."}\\ --George Box
-
-\end{raggedleft}
-
+%\begin{raggedleft}
+%{\em ``The  common misunderstanding about science 
+%%is that scientists seek and find truth. They don't- 
+%they make and test models.''}\\ -- Neil Gershenfeld
+
+%{\em Essentially, all models are wrong, but some are useful."}\\ --George Box
+%%
+%\end{raggedleft}
+
+One of the ``black arts'' of data mining is setting the tuning
+parameters that control  the choices within that data miner.
+Such tunings can have a dramatic change to the performance of a learner;
+e.g. in this paper we show that tuning can alter the precision of
+a software defect predictor from 2\% to 98\%.
+
+Many researchers have applied automatic optimizers to find good tunings.
+This paper shows that for at least one software analytics problem
+(software defect prediction from static code attributes),   a
+very simple optimizer called differential evolution needs only   seconds
+to just  few minutes to find good tunings.
+
+These results   challenge much prior work into defect prediction:
+\bi 
+\item 
+Several recent high profile papers have claimed 
+that learnerX is better than learnerY for some software analytics task.
+For example, a recent IEEE TSE article claimed that the 
+CART decision tree learner was far worse than Random Forests for
+softwre defect predition. 
+We show that tuning can reverse the rankings of data miners such
+that, after tuning, the worst untuned learner (CART) can out-perform the supposedly
+best learner (Random Forests).
+\item
+The improvements achieved via differential evolution are too large to discount.
+Yet those result show that different attributes are ``best'' for different
+data sets and even differnt goals for the tunings. Hence, it is no longer
+supportable to use data mining to argue that certain kinds of attributes
+are better than others. 
+\ei 
+Given the simplicity and effectiveness of differential evolution,
+and also given the effects this method has on defect prediction, this
+paper  motivates  a change to the entire field of software analytics.
+It is no longer enough to just run a data miner and present the result
+{\em without} first conducting an tuning optimizations study.
+
+\section{Background}
+\subsection{Defect Prediction}
+
+This section is our standard introduction to defect prediction~\cite{aa},
+plus   some new results from Rahman et al.'s   2014 FSE paper~\cite{rahman14:icse}.
+
+XXXX need our standard table
+
+\input{dm101}
+
+\begin{figure*}[!t]
+\renewcommand{\baselinestretch}{0.8}\begin{center}
+{\scriptsize
+\begin{tabular}{c|l|p{4in}}
+amc & average method complexity & e.g. number of JAVA byte codes\\\hline
+avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
+in class\\\hline
+ca & afferent couplings & how many other classes use the specific
+class. \\\hline
+cam & cohesion amongst classes & summation of number of different
+types of method parameters in every method divided by a multiplication
+of number of different method parameter types in whole class and
+number of methods. \\\hline
+cbm &coupling between methods &  total number of new/redefined methods
+to which all the inherited methods are coupled\\\hline
+cbo & coupling between objects & increased when the methods of one
+class access services of another.\\\hline
+ce & efferent couplings & how many other classes is used by the
+specific class. \\\hline
+dam & data access & ratio of the number of private (protected)
+attributes to the total number of attributes\\\hline
+dit & depth of inheritance tree &\\\hline
+ic & inheritance coupling &  number of parent classes to which a given
+class is coupled (includes counts of methods and variables inherited)
+\\\hline
+lcom & lack of cohesion in methods &number of pairs of methods that do
+not share a reference to an instance variable.\\\hline
+locm3 & another lack of cohesion measure & if $m,a$ are  the number of
+$methods,attributes$
+in a class number and $\mu(a)$  is the number of methods accessing an
+attribute,\newline
+then
+$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
+\\\hline
+loc & lines of code &\\\hline
+max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
+in class\\\hline
+mfa & functional abstraction & number of methods inherited by a class
+plus number of methods accessible by member methods of the
+class\\\hline
+moa &  aggregation &  count of the number of data declarations (class
+fields) whose types are user defined classes\\\hline
+noc &  number of children &\\\hline
+npm & number of public methods & \\\hline
+rfc & response for a class &number of  methods invoked in response to
+a message to the object.\\\hline
+wmc & weighted methods per class &\\\hline
+\rowcolor{lightgray}
+defect & defect & Boolean: where defects found in post-release bug-tracking systems.
+\end{tabular}
+}
+\end{center}
+\caption{OO measures used in our defect data sets. The last line shows
+the dependent attribute (whether any defect is reported to  a
+post-release bug-tracking system).}\label{fig:ck}
+\end{figure*}
+
+We formulate and present two cost-effectiveness-based
+accounting approaches to the comparability of bugginess
+identification problem (CBI).
+We find no significant differences in the cost-effectiveness
+of the DP and the two SBF techniques —
+FindBugs and pmd— we could evaluate
+
+\section{Other sutff}
 XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores.
@@
 
+Note that we do not claim that differntial evolution is the {\em best} way to
+optimize data miners for defect prediction. In this paper, we only show that
+differential evolution is {\em simple}, {\em fast} and {\em effective} at that task. As to   finding the best optimizer for defect prediction, that task would require
+the input of many researchers (and we hope this paper inspires
+much subsequent work into that issue).
+
 \subsection{Implications}
@@
 		\begin{algorithmic}[1]
-			\Require $np$, $f$, $cf$, $life$
+			\Require $np = 10$, $f=0.75$, $cr=0.3$, $life = 5$
 			\Ensure $S_{best}$
+
+	      \Function{DE}{$np$, $f$, $cr$, $life$}
 		  \State $Population  \gets $ InitializePopulation($np$)
@@
 			\State $NewGeneration \gets \emptyset$
-			\For{$i=0 \to n-1$}
-				\State $S_i \gets$ GenNew($Population [i], Population , cf, f)$
+			\For{$i=0 \to np-1$}
+				\State $S_i \gets$ GenNew($Population [i], Population , cr, f$)
 				\If {Score($S_i$) >Score($Population [i]$)}
-				 	\State $NewGeneration \gets S_i$
+				 	\State $NewGeneration$.append($S_i$)
 				\Else
-					\State $NewGeneration \gets Population [i]$
+					\State $NewGeneration$.append($Population [i]$)
 				\EndIf
@@
 		 \State \Return $S_{best}$
+		 \EndFunction
+		 \Function{Score}{$Candidate$}
+		    \State set tuned parameters according to $Candidate$
+		    \State TrainLearner()
+		    \State $scores \gets$TestLearner()
+		    \State \% scocres = [pd, f, precision]
+		    \State $s \gets scores[i] $ 
+		    \State \% i determines the goal of tuning
+		    \State \Return$s$
+		 \EndFunction
+		 \Function{GenNew}{$old, pop, cr, f$}
+		   \State $a, b, c\gets threeOthers(pop,old)$ 
+		   \State \% pick 3 other points from the population
+		   \State $newf \gets \emptyset$
+		   \For{$i=0 \to np-1$}
+		        \If{$cr < random()$}
+		          \State $newf$.append($old[i]$)
+                \Else
+                  \If{typeof(old[i]) == bool}
+                    \State $newf$.append(not $old[i]$)
+		          \Else
+		           \State $newf$.append(trim($i$,($a[i] + f * (b[i] - c[i]$))))
+		           \State \%trim() will make new value fall in the range
+		          \EndIf
+		        \EndIf
+		   \EndFor
+		 \EndFunction
         \end{algorithmic}            

### 2015-03-10 dm101.tex
Updates from ShareLaTeX

@@
+Human programmers are clever, but flawed. Coding  adds functionality, but also defects.
+Hence, software sometimes crashes (perhaps at the most awkward or dangerous moment) or delivers
+the wrong functionality. For a very long list of software-related errors,
+see  Peter Neumann's ``Risk Digest''\footnote{http://catless.ncl.ac.uk/Risks/}.
+
+Because of the above, is important to thoroughly {\em test} software before it is {\em used}.
+Such testing  can be very expensive.
 Software assessment budgets are finite
@@
 moving $C$ from  
-90\% to 94\% to 98\% takes 2301, 2812, and 3910 black box
-probes, respectively.\footnote{A randomly selected 
+90\% to 98\% nearly doubles the number of required tests (2301 to   3910 black box
+probes, respectively)\footnote{A randomly selected 
 input to a program will find a fault with probability $p$.
@@
  $N(C,p)=\frac{log(1 -
-C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}
+C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}.
 
@@
 
-There are many reasons to study defect  defect predictors learned from
-static code attributes: they are   {\em easy to
+One such lightweight sampling policy is defect predictors learned from static code attributes.
+Given software described using (for example) the attributes of \fig{ck} it is possible
+to use standard data mining technology to learn where the probability of software defects is highest.
+Such defect  defect predictors learned from
+static code attributes are   {\em easy to
 use}, {\em widely-used}, and {\em useful} to use.
 
-{\em Easy to use:} Static code attributes can be automatically and cheaply collected, even for very large systems~\cite{nagappan05}.
-By contrast, 
-other methods such as manual code reviews are labor-intensive.
-Depending on the review methods 8 to 20 LOC/minute can be
+{\em Easy to use:} Static code attributes can be automatically collected, even for very large systems~\cite{nagappan05}.
+Other methods, like  manual code reviews, are far slower and far more labor-intensive.
+For example, depending on the review methods 8 to 20 LOC/minute can be
 inspected and this effort repeats for all members of the review team,
@@
 standard result for defect predictors is that they find the location of  70\% (or more)
-of the defects in code.
-This is markedly
-higher than other currently-used
-industrial
-methods such as manual code reviews:
-\bi
-\item
-A panel at {\em IEEE Metrics
-2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
-of defects.
-\item
-Raffo found that the defect detection capability of
-industrial review methods have mode defect detection rates
-of around 50\%
- for full Fagan inspections~\cite{fagan76} to
-21\% for less-structured inspections.
-\ei
-Defect prediction scales well to a commercial
-context. Defect predicting technology has been
-commercialized in {\it Predictive}~\cite{turner06} a
-%scalable product suite to analyze and predict
-defects in software projects. Predictive was observed to
-highlight simimilar issues to those found   with the more expensive tools. But,
-Predictive was able to faster process a larger code
-base than the more expensive tool~\cite{turner06}.
-
-In addition, defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey).
+of the defects in code~\cite{me70b}.
+Defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey).
 When the inspection teams focused on the modules that trigger the defect predictors, they found up to 70\% of the defects using just 40\% of their QA effort (measured in staff hours)~\cite{tosun10}.
-
-Finally, a subsequent study on the Turkish software
+A subsequent study on the Turkish software
 compared how much code needs to be inspected using
@@
 \cite{tosun09}.
+
+This is markedly
+higher than other currently-used
+industrial
+methods such as manual code reviews. For example, 
+A panel at {\em IEEE Metrics
+2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
+of defects.
+In other work, 
+Raffo found that the defect detection capability of
+industrial review methods have mode defect detection rates
+of around 50\%
+ for full Fagan inspections~\cite{fagan76} to
+21\% for less-structured inspections.
+
+Defect prediction scales well to a commercial
+context. Defect predicting technology has been
+commercialized in many tools including {\it Predictive}~\cite{turner06}, a
+ product suite to analyze and predict
+defects in software projects. Predictive was observed to
+highlight simimilar issues to those found   with the more expensive tools. Significantly,
+Predictive was able to faster process a larger code
+base than the more expensive tool~\cite{turner06}.

### 2015-03-10 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \usepackage{algpseudocode}
+\renewcommand{\footnotesize}{\scriptsize}
 \definecolor{lightgray}{gray}{0.8}
@@
 \title{Implications of Differential Evolution for  Defect Prediction:
-Analytics Without Parameter Tuning Considered Harmful}
+Analytics Without Parameter Tuning Considered Harmful?}
 \numberofauthors{1}
@@
 \alignauthor
-Wei Fu, Tim Menzies\\
-       \affaddr{Computer Science, North Carolina State University, USA}\\
-       {wfu@ncsu.edu, tim.menzies@gmail.com}}
+Wei Fu, Tim Menzies, Vivek Nair\\
+       \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
+       {wfu@ncsu.edu, tim.menzies@gmail.com, vivekaxl@gmail.com}}
 
@@
 When learning
-software defect predictors from static code attributes,   a
+software defect predictors,   a
 very simple optimizer called differential evolution needs can quickly
@@
 
-These results suggest that it is time to change standard practice in
-software analytics. Specifically,
+These results prompt for a change to standard methods in software analytics.
+At least for defect prediction, 
 it is no longer enough to just run a data miner and present the result
 {\em without} first conducting an tuning optimizations study.
+The implications for other kinds of software analytics is now an open and pressing questions.
 
@@
 {\bf Keywords:} defect prediction, CART, random forests,
-Fastmap,   bootstrap sampling, effect size, A12.
+Fastmap,   bootstrap sampling, effect size, A12,differential evolution,
+search-based software engineering.
 
@@
 to just  few minutes to find good tunings.  
-
 These results   challenge much prior work into defect prediction:
@@
 \item 
-Several recent high profile papers have claimed 
-that learnerX is better than learnerY for some software analytics task.
+Numerous   prominent papers have claimed 
+that learnerX is better than learnerY for some software analytics task~\cite{lessmann2008benchmarking,hall11,me07b}.
 For example, a recent IEEE TSE article claimed that the 
 CART decision tree learner was far worse than Random Forests for
-softwre defect predition. 
-We show that tuning can reverse the rankings of data miners such
-that, after tuning, the worst untuned learner (CART) can out-perform the supposedly
+softwre defect predition~\cite{lessmann2008benchmarking}. 
+Such conclusions do not survive tuning.
+For example,
+after tuning, the worst untuned learner (CART) can out-perform the supposedly
 best learner (Random Forests).
@@
 Yet those result show that different attributes are ``best'' for different
-data sets and even differnt goals for the tunings. Hence, it is no longer
+data sets and even different goals for the tunings. Hence, it is no longer
 supportable to use data mining to argue that certain kinds of attributes 
-are better than others. 
+are better than others; e.g. as  done by~\cite{rahman2013how}. 
 \ei 
@@
 paper  motivates  a change to the entire field of software analytics.
-It is no longer enough to just run a data miner and present the result
+At least for softwre defect prediction,
+it is no longer enough to just run a data miner and present the result
 {\em without} first conducting an tuning optimizations study.
+
+The implications for other kinds of data mining tasks is unclear.
+While this paper reports success with tuning defect predictors,
+we were not so successful with
+other analytics tasks (software development effort estimation).
+Hence, we assert that it is now an open and pressing research question is whether or not  
+tuning studies are now   required for research reports on software analytics.
 
@@
 
-This section is our standard introduction to defect prediction~\cite{aa},
+This section is our standard introduction to defect prediction~\cite{me15:book1},
 plus   some new results from Rahman et al.'s   2014 FSE paper~\cite{rahman14:icse}.
-
-XXXX need our standard table
-
-\input{dm101}
 
@@
 \end{center}
-\caption{OO measures used in our defect data sets. The last line shows
-the dependent attribute (whether any defect is reported to  a
+\caption{OO measures used in our defect data sets.  Last line is
+the dependent attribute (whether a defect is reported to  a
 post-release bug-tracking system).}\label{fig:ck}
 \end{figure*}
+
+\input{dm101}
 

### 2015-03-11 dm101.tex
Updates from ShareLaTeX

@@
 the wrong functionality. For a very long list of software-related errors,
-see  Peter Neumann's ``Risk Digest''\footnote{http://catless.ncl.ac.uk/Risks/}.
+see  Peter Neumann's ``Risk Digest'' at catless.ncl.ac.uk/Risks.
 
-Because of the above, is important to thoroughly {\em test} software before it is {\em used}.
+Since programming inherently
+introduces defects into  programs, is important to thoroughly {\em test} software before it is {\em used}.
 Such testing  can be very expensive.
@@
 
-{\em Widely used:} Many researchers use static attributes to guide software 
+{\em Widely used:} Many researchers and industrial practitioners  use static attributes to guide software 
 quality predictions.
+ Defect prediction models have been reported
+to have been used at Google~\cite{lewis13}.
 Verification and validation (V\&V) textbooks
@@
 standard result for defect predictors is that they find the location of  70\% (or more)
-of the defects in code~\cite{me70b}.
+of the defects in code~\cite{me07b}.
 Defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey).
@@
 would have to be inspected in order to detect 87\%
-of the defects. However, if the inspection process
+of the defects. Further, if the inspection process
 was restricted to the 25\% of the files that trigger
@@
 \cite{tosun09}.
-
-This is markedly
-higher than other currently-used
-industrial
-methods such as manual code reviews. For example, 
-A panel at {\em IEEE Metrics
-2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
-of defects.
-In other work, 
-Raffo found that the defect detection capability of
-industrial review methods have mode defect detection rates
-of around 50\%
- for full Fagan inspections~\cite{fagan76} to
-21\% for less-structured inspections.
 
@@
 base than the more expensive tool~\cite{turner06}.
+
+The success of this method in  predictors in finding bugs is   markedly
+higher than other currently-used
+industrial
+methods such as manual code reviews. For example, 
+a  panel at {\em IEEE Metrics
+2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
+of defects.
+In other work, 
+Raffo documents the typical    defect detection capability of
+industrial review methods:   around 50\%
+ for full Fagan inspections~\cite{fagan76} to
+21\% for less-structured inspections.
+
+Note only do static code defect predictors perform well compared to manual methods,
+they also are competititve with certain automatic methods.
+At ICSE'14, Rahman et al.~\cite{rahman14:icse} offered an extensive comparison of:
+\bi
+\item The static code analysis tools FindBugs, Jlint, and Pmd;
+\item Against static code defect predictors
+(which they called ``statistical defect prediction'') build using logistic regression.
+\ei
+That study assessed the cost-effectiveness of finding bugs using either method.
+They found   no significant differences in the cost-effectiveness
+of the two approaches. Given this equivalence, it is significant to note that 
+static code defect prediction can be quickly adapted to new languages, just by building lightweight
+parsers that can extract information like \fig{ck}. The same cannot be said for   static code analyzers that require extensive modification before they can be applied to a new
+language.

### 2015-03-11 learners.tex
Updates from ShareLaTeX

--- 2015-03-05 tuningpredictor.tex
@@
-\documentclass{sig-alternative}
-\usepackage{multirow}
-\usepackage{color}
-\usepackage{graphics}
-\usepackage{rotating}
-\usepackage{graphics}
-\usepackage{colortbl} 
-\usepackage{picture}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\definecolor{lightgray}{gray}{0.8}
-\definecolor{darkgray}{gray}{0.6}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-%%% graph
-\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
-\newcommand{\rone}{\crule{1mm}{1.95mm}}
-\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
-\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
-\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
-\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
-\newcommand{\quart}[3]{\begin{picture}(100,6)%1
-{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
-\definecolor{Gray}{gray}{0.95}
-\definecolor{LightGray}{gray}{0.975}
+Dta miners find generalizations (a.k.a. summaries)
+of the data. All such generalizations must be smaller than the data it generalizes (otherwise we might as well just keep the original data and ignore the generalization)\footnote{Technical note:
+even instance-based reasoners uses generalizations when they partially match new cases to old;
+or if they use some  clustering algorithm to restrict the case matching
+to just the subset of old cases most similar  to new  cases.}. 
+Generalization is important since,
+without generalization, all we can do is perform exact matches
+of new situations to a database of old examples. This is not recommended practice since,
+ if the new situation has not occurred  before, then nothing in the data  will
+ matches the new situation
+(and we cannot make any predictions).
 
-%% timm tricks
-\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\be}{\begin{enumerate}}
-\newcommand{\ee}{\end{enumerate}}
-\newcommand{\tion}[1]{\S\ref{sect:#1}}
-\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
-\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
-
-%% space saving measures
-
-\usepackage[shortlabels]{enumitem} 
-\usepackage{times}
-
-\usepackage{url}
-\def\baselinestretch{1}
-
-\setlist{nosep}
- \usepackage[font={small}]{caption, subfig}
-\setlength{\abovecaptionskip}{1ex}
- \setlength{\belowcaptionskip}{1ex}
-
- \setlength{\floatsep}{1ex}
- \setlength{\textfloatsep}{1ex}
- \newcommand{\subparagraph}{}
-
-\usepackage[compact,small]{titlesec}
-\DeclareMathSizes{7}{7}{7}{7} 
-\pagenumbering{arabic}
-\setlength{\columnsep}{7mm}
-
-\begin{document}
-
-\conferenceinfo{FSE}{'15 Bergamo, Italy}
-\title{Implications of Differential Evolution for  Defect Prediction:
-Analytics Without Parameter Tuning Considered Harmful}
-\numberofauthors{1}
-\author{
-\alignauthor
-Wei Fu, Tim Menzies\\
-       \affaddr{Computer Science, North Carolina State University, USA}\\
-       {wfu@ncsu.edu, tim.menzies@gmail.com}}
-
-\maketitle
-\begin{abstract}
-
-software defect prediction with various 
-empirical data sets. Those proposed leaners are always evaluated against the state of the art 
-predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
-accuracy indicators, the newer predictors outperform counterparts in selected experimental 
-settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
-forest, 
-neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
-forest algorithm. the impact of internal parameters in those methods have been neglected 
-during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
-predictors with search-based software engineering algorithm. Specifically, we used differential 
-evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
-and then predictors with optimal parameters obtained from tuning process will be applied to 
-predict defects. By comparing the performance of predictors with and without tuning process,  
-we observe that tuning improves the predictors' performance and predictors woking with 
-different data sets need different parameters. Our results also suggest that we should not use 
-the predictors of the shelf with their default parameters and tuning should be a processor 
-combined with any predictor with built-in parameters.
-
-%RQ1: Does tuning affect learners' performance?
-%RQ2: How to choose
-
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\vspace{1mm}
-\noindent
-{\bf Categories/Subject Descriptors:} 
-D.2.8 [Software Engineering]: Product metrics;
-I.2.6 [Artificial Intelligence]: Induction
-
-\vspace{1mm}
-\noindent
-{\bf General Terms:} Experimentation, Algorithm
-
-\vspace{1mm}
-\noindent
-{\bf Keywords:} defect prediction, CART, random forests,
-Fastmap,   bootstrap sampling, effect size, A12.
-
-\section{Introduction}
-
-\begin{raggedleft}
-{\em ``The  common misunderstanding about science 
-is that scientists seek and find truth. They don't- 
-they make and test models.''}\\ -- Neil Gershenfeld
-
-{\em Essentially, all models are wrong, but some are useful."}\\ --George Box
-
-\end{raggedleft}
-
-XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores.
-Given that, the next question becomes ``what performance scores do you want?''.
-This is an interesting issue since there is no single best answer.
-XXX
-
-How ``true'' are the  models generated by software analytics?
-Suppose we use a model generated from software project data to, for example,
-assess the relative value of OO metrics vs procedural metrics for predicting
-project defects. Are we reporting ``truth'' in any sense of the word? And for how
-many other projects  and how many kinds of questions might we find that same ``truth''?
-
-This is not some abstract question-- it is an open and pressing matter.
-Any reading of the recent proceedings of FSE, ICSE, ASE, etc will discover hundreds
-of papers using data miners to make conclusions about software projects. 
-For example, some  analysts have made conclusions
-about 
-{\em what attributes
-have most influence on a software project}.
-For example, in 2013,
-Rahman et al
-\cite{rahman2013how}  used results from logistic regression to conclude
-that code metrics are generally less useful than process
-metrics for  predicting defects from static code analysis.  
-In the same year, Bell et al. (who also used negative binomial regression) argued that
-software defect prediction was not improved by adding in~\cite{bell2013limited}.
-
-@article{bell2013limited,
-  title={The limited impact of individual developer data on software defect prediction},
-  author={Bell, Robert M and Ostrand, Thomas J and Weyuker, Elaine J},
-  journal={Empirical Software Engineering},
-  volume={18},
-  number={3},
-  pages={478--505},
-  year={2013},
-  publisher={Springer}
-}
-
-The results of this paper offer a very different picture  to recent prominent results from prior authors.
-Lessmann et al.~\cite{lessmann2008benchmarking}, Rahman et al.~\cite{rahman2013how} and Arshiholm et al.~\cite{arisholm06} argue that when it comes to defect prediction, different learners often
-produce statistically similar results. For this reason  Rahman et al. only present results their logistic
-regression results, commenting that ``dor brevity, only results from LR are
-presented; other learning models give similar results''~\cite{rahman2013how}. Note that those prior results,
-where most learners achieved the same results, arose from the default parameter settings from those learners.
-
-Our results, on the other hand, come from tuning a data miner's parameters. In those results,
-we found that the choice of parameters had dramatic impacts on data mining performance.
-For example, we show results below where:   
-\bi 
-\item 
-Tuning improved precision values from  2\% to 98\%; or
-\item 
-Tuning improved false alarm values from 69\% to 0\%; or
-\item 
-Tuning improved recall values from 0 to 100\%; or
-\item 
-Tuning improved the f-measure (which is the harmonic mean of recall and precision) from 0 to 86\%.
-\ei   
-In terms of changing SE research methodologies, an important aspect of these results is that usually XXXX always different.
-cannot determine without experimentation which learner will, after tuning, yield the best results for a particular data set.
-Hence it is no longer viable for researchers to trust the recommendations
-of other researchers working with other data sets that ``data miner XYZ is best''. Before
-offering a conclusion about a particular data set, researchers need now augment  their 
-papers with preliminary tuning studies (the results of which select the tunings+data miners to be used
-to make conclusions for the second half of their paper).
-
-The good news is that such tuning is not an arduous task. The differential evolution algorithm 
-used in this study is wdiely available in many standard  toolkits and languages\footnote{See the long list at
-www1.icsi.berkeley.edu/~storn/code.html.}
-And even if somehow those tools and prior implementations are not workable at a local site, 
-differential evolution is very simple to code. Hence, it can readily and quickly implemented.
-
-When we discuss these results with colleagues, one response we get is ``enough of the parameter tuning.. lets use simpler methods''. 
-While we understand their motivation (to keep thing simple), software project
-data cannot necessarily be condensed to (say) a simple univariate analysis that
-reports how one independent variable effects a dependent variable.
-Such a simplistic analysis can miss significant interaction
-effects when multiple factors combine to effect the target variable. For example,
-one of the base results in defect prediction is that predictors formed from
-a single variable perform much worse than those can combined multiple variables (three or more)~\cite{me07b}.
-
-If those results come from an analysis of a complex interactions between attributes,
-then some kind of data mining method\footnote{By this term we mean the
-full gamut of methods for large-scale analysis of
-data including statistical
-parametric methods (that assume a particular distribution then strive to learn the parameters of that distribution); kernel methods;
-dimensionality  synthesis methods; 
-instance weighting schemes; feature subset selection methods
-outlier removal methods;
-decision tree learners; neural networks; and instance-based
-methods including clustering and/or   case-based reasoning.} then there is the
-{\em tuning problem} of how to set the myriad of parameters that 
-control the learner.
-
-\item
-What data miners are better than others for particular tasks
-in software analytics. 
-\ei
-
-Also, in 2007, one of us (Menzies) claimed that Naive Bayes
-classifiers with a certain lind of pre-processor were better than entropy-based decision trees for defect prediction~\cite{me07b}.
-Similarly, in 2008 Lessmann et al.~\cite{lessmann2008benchmarking} argued  that 
-Random Forests~\cite{brieman00} and CART ~\cite{brieman84} work best, worst for learning software defect predictors from
-static code attributes. Similar claims that one learner was better than another
-have been made by many other authors; e.g.
-
-We write to suggest that all those conclusions may be wrong or, at the very most,
-correct within a very limited context. At the very least, the conclusions
-of those papers (and literally dozens of similar papers, include severl
-of our own~\cite{me02e,me02k,me03a,me06d,me07b}) need to be revisited
-in light of this paper's results on the effects of tuning on data miners.
-
-Machine learners
-are controlled by parameters that decide (e.g.) when to stop recursively
-dividing data into smaller section or (e.g.) what thresholds for errors are small
-enough to be acceptable. When used ``off-the-shelf'', analytst
-use default settings for those parameters. We find that  a 
-simple optimization scheme (differential evolution) can find much
-better tunings that can dramatically change the performance of
-the learned model (measured in terms of false alarm rates, recall,
-precision, f-measure, and g-measure).  From this first result,
-we conclude that {\bf parameter tuning with some optimizer such as differential
-evolution should become standard practice}.
-
-Our next observation is that observations about miner1 being better
-than miner2 do not survive tuning. To be specific: given some
-ranking of data miners for some task such as defect prediction,
-we find that tuning can reverse those rankings such that the worst untu
-
-Tuning the data miners with different evolution takes some
-times (around an order of magnitude slower than the learning), but not an impractically slower amount of time. Further, when we look at what
-attrub
-
-Our reading of the
-
-good news:
-\bi 
-\item Tuning is easy (but one measure, at least an order of magnitude easier than 
-standard optimization problems)
-\item Tuning can dramatically improve the performance of a learner (in one case, from recalls
-of zero to 70\%)
-\ei
-interesting news
-\bi 
-\item tunings different for different data sets.
-\ei 
-bad news:
-\bi
-\item Tuning also changes what was learned
-\bi
-\item Supposedly ``bad'' learners start working much better than supposedly ``best'' learners;
-\item The models used in the tuned models were very different to those used in the untuned learners.
-\ei 
-\ei 
-and we reflect on that model, are we
-
-will it reveal the `1`t
-A standard approach to software analutics
-Software has becoming a large and complex system and delivering reliable and quality 
-software is imperative for development teams. Empirical study shows that the longer the 
-defects exist in software systems, the more the cost of time and money it will take to fix it 
-\textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
-defects in their system as early as possible. Defect prediction has been investigated 
-extensively in industrial and academia during the past two decades. As an important research 
-field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, 
-menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} 
-over static code features of software system has been demonstrated to be a way to predict 
-which models are more likely to contain defects.
-
-Classification is an important approach to predict whether some modules in the projects are 
-defective or non-defective. The general idea is to train the learners by using parts of data 
-sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with 
-remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed 
-based an different data mining classifiers, including CART, Random Forest 
-\cite{guo2004robust},  Naive Bayes\cite{menzies2007data},Logistic Regression 
-\cite{khoshgoftaar1999logistic}. During the past years, authors claimed that their new 
-defective learner outperformed others according to their experiment and statistical analysis. 
-To evalute those learners objectively in terms of accuracy, Lessmann et al
-\cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
-\begin{figure}
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-When applying case-based reasoning, researchers use different settings including how they measure dis- tance between instances (examples include the Euclidean measure, Manhattan and Chebyshev).
-Other settings control if numerics are normalized min..max to 0..1, before they are used in the distance measure.
-
-Another set of settings refers to how to handle non-numeric distances or missing values.
-Some researchers delete training data with missing information while others compute missing values via, say, median values.
-
-After feature selection comes instance selection.
-There are many settings for instance selectors such as use outlier removal or prototype generation.
-Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
-The next set of settings concern how many neighbors to use (k=1,2,5,etc).
-Some researchers set ``k'' in dynamic pre-learning phase that checks the training data to find what ``k'' works best for that data.
-
-Once the neighbors are known, the next settings control how to summarize their information.
-Some researchers use means, other use medians, or a weighted sum that uses the distance of the neighbor from the test instance (and that weighting might be determined by some kernel such as uniform, triangular, Gaussian, cosine, or Epanechnikov).
-Researchers may use other settings to control different pre-processors.
-E.g.
-some discretize numeric values (via equal width or equal frequency) using some binning policy (and researchers differ on how many bins are best).\\\hline
-\end{tabular}
-\caption{Some tunings for SE predictive systems.
-Found by this author while preparing this proposal in a day of reading the SE predictive modeling literature on case-based reasoning and effort estimation.
-Note that other kinds of prediction systems (decision trees, neural nets, linear repression, etc) have yet more adjustable design options.}\label{fig:adjust}
-\end{figure}
-
-domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
-with $\alpha = 0.05$, they concluded that the predictive accuracy of most learners didn't differ 
-significantly in terms of the area under the receiver operating characteristics curve(AUC). 
-Furthermore, according to the fig.2 in \cite{lessmann2008benchmarking}, Random Forest is 
-significantly better than CART. Lessmann's paper motivates us to investigate whether tuning 
-those CART's parameters by search-based software engineering method can improve the 
-performance. Even though Lessmann considered unpruned tree and pruned tree, They didn't 
-consider other possible parameters in CART which would have impact on the structure of 
-trees, like the depth of the tree, the maximum and minimum number of leafs of the tree.
-
-Software metrics are the core of all the defective prediction model. Many types of metics
-are used to build models, like process metrics, McCabe and Halsted metrics  and CK metrics.
-By building prediction modes across 85 releases of 12 open source projects, Rahman et al
-\cite{rahman2013how}  concluded that code metrics are generally less useful than process
-metrics for prediction. And also the code metrics don't change much from release to release
-and lead to stagnation in the prediction model. In \cite{Radjenovi?20131397}, Radjenovi? et al
-\cite{Radjenovi?20131397} reviewed 106 papers regarding software prediction metrics. They found
-that CK objected-oriented and process metrics have been reported to be more successful in
-finding defects compared to traditional size and complexity metrics. Moreover, not all the CK
-metrics perform well equally. The best metrics from CK are CBO, WMC and RFC based on their 
-observation. It seems that the relationship between software metrics and defective prediction is
-still an open question and need to be addressed. This motivates us to see : whether the impact
-rankings of those metrics will change after tuning parameters
-is applied to model learners.
-
-What's the problem in those result?
-
-RQ:
-
-briefly describe our study and  our result; observation
-
-structure of this paper.
-
-\subsection{Implications}
-
-time for an end to era of data mining in se? moving on to a new phase of learning-as-optimization
-
-1) learning is actually an optimization tasks (e.g. see fig2 of  learners climbing the roc curve hill in http://goo.gl/x2EaAm)
-
-2) our learners are all contorted to do some tasks X (e.g.
-minimize expected value of entropy), then we assess them on score Y (recall).
-which is nuts.
-maybe we should build the goal predicate into the learner (e.g http://menzies.us/pdf/10which.pdf)
-
-3) given 1 + 2, maybe the whole paradigm of optimizing param selection is wrong.
-maybe what we need is a library of bees buzzing around making random choices (e.g.
-about descritziation) which other bees use, plus their own random choices (e.g.
-max depth of tree learned from discretized data) which is used by other bees, plus their own random choices (e.g.
-business users reading the models).
-the funky thing here is that it can take some time before some of the bees (the discretizers) get feedback from the community of people using their decision (the tree learners).
+The key point here is that there are many ways to summarize data and exceConsider some learner that
+builds predictive rules form a subset of  attributes $A$ ranges. Assuming numeric attributes
+divided into five ranges, then the 20 attributes of \fig{ck} can be combined into 
+$2^{5*20}> 10^{30}$
+possible rules
 
@@
 %\end{equation}
-
-\subsection{Differential Evolution Algorithm}
-Differential Evolution (DE)\cite{storn1997differential} is a stochastic search algorithm that 
-optimizes a problem by iteratively trying to improve a  population of candidate solutions with 
-regard to a given quality measurement. Such method makes no assumptions about the 
-problem being optimized and has already been used as a parameter tuner
-\cite{omran2005differential, chiha2012tuning}.
-
-DE starts with creating a population of candidate solutions and then generates new 
-candidates based on $New = X+f*(Y-Z)$, where $X$, $Y$ and $Z$ are randomly selected 
-solutions from the current frontier and $f$ is a crossover factor. The newly generated solution 
-will be added into the next generation of solutions if dominating previous old points in the 
-frontier. To avoid meaning less iteration, early termination strategy is applied that is at the 
-beginning, assign a value to the $life$ parameter, it would be reduced by one each time   
-when the new generation of candidate solutions does not improve in terms of quality 
-measurement. The DE will stop when the $life$ equals to 0.
-
-Algorithm \ref{alg:DE} is a list of pseudocode of DE with early termination for maximizing a 
-score function, where $np$ is the number of population in each generation, $f$ is the 
-crossover factor as mentioned, $cf$ is the probability for crossover operation to generate new 
-candidate, $life$ is to control termination.
-
-\begin{algorithm}
-	\caption{Pesudocode for DE with Early Termination}
-	\label{alg:DE}
-		\begin{algorithmic}[1]
-			\Require $np$, $f$, $cf$, $life$
-			\Ensure $S_{best}$
-		  \State $Population  \gets $ InitializePopulation($np$)
-		  \State $S_{best} \gets $GetBestSolution($Population $)
-		  \While{$life > 0$}
-			\State $NewGeneration \gets \emptyset$
-			\For{$i=0 \to n-1$}
-				\State $S_i \gets$ GenNew($Population [i], Population , cf, f)$
-				\If {Score($S_i$) >Score($Population [i]$)}
-				 	\State $NewGeneration \gets S_i$
-				\Else
-					\State $NewGeneration \gets Population [i]$
-				\EndIf
-			\EndFor
-			\State $Population  \gets NewGeneration$
-			\If{$\neg$ Improve($Population $)}
-				\State $life -=1$
-			\EndIf
-			\State $S_{best} \gets$ GetBestSolution($Population $)
-		  \EndWhile
-		 \State \Return $S_{best}$
-                 \end{algorithmic}            
-\end{algorithm}
-
-%\begin{algorithm}
-%\begin{algorithmic}[1]
-% \KwData{this text}
-% \KwResult{how to write algorithm with \LaTeX2e }
-% initialization\;
-% \While{not at end of this document}{
-%  read current\;
-%  \eIf{understand}{
-%   go to next section\;
-%   current section becomes this one\;
-%   }{
-%   go back to the beginning of current section\;
-%  }
-% }
-% \caption{How to write algorithms}
-% \end{algorithmic}
-%\end{algorithm}
-
-\section{Experiment}
-
-\subsection{Data Set}
-
-The data used in this study is from PROMISE repository. Ten software defect predicition data 
-sets are analyzed. They're {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene}, {\it 
-synapse}, {\it velocity}, {\it xalan} and {\it xerces}. Each of these data sets is composed of 
-several software modules with number of defects and code attributes. For more detailed 
-description of code attributes and the original data sets, please refer to  http://openscience.us/
-repo/
-
-\subsection{Experiment Design}
-
-The experiment aims at investigate whether tuning helps learners improve performance in 
-terms of accuracy measurement. We choose compare WHERE-based learner with and 
-without tuning parameters and two {\it significantly different} learners Random Forest and 
-CART according to \cite{lessmann2008benchmarking}. As mentioned above, we'd like to see 
-whether tuning will help change the rank of CART and make it comparable with Random 
-Forest.
-
-To evaluate accuracy performance of learners, several measurements are proposed, like 
-probability of  detection({\it pd}) and probability of false alarm ({\it pf})\cite{menzies2007data}, 
-the area under the receiver operating characteristics curve ({\it AUC})
-\cite{lessmann2008benchmarking}, and precision\cite{zhang2007comments}. In this work, we 
-expect learners should identify as many defective modules as possible while avoiding false 
-alarm. Therefore, learners are evaluated by both of {\it pd} and {\it pf} simaltanieously. A single 
-measure, G-measure, defined as the harmonic mean of {\it pd} and $1-{\it pf}$  is used. The 
-G-measure value is between 0 and 1. The higher, the better.
-\begin{equation}
-G = \frac{2*(1-pf)*pd}{1-pf+pd}
-\end{equation}
-
-In this experiment, we use three different portions of one project data set for training, tuning 
-and testing process. In contrast to hold out way used in \cite{lessmann2008benchmarking, 
-menzies2007data}, we separate the data sets in order. Since learners are designed to predict 
-defects in future projects,  any randomly data set selection without taking into the time series 
-will not sufficient to evaluate the performance of predicting future. To the most, that is good to 
-evaluate the accuracy of classification but not predicting future. Since we have 10 different 
-project data, each of which contains least 3 evolutionary versions. We use the following policy 
-to select the data: in each project, we only use the last three data files for experiment. 
-Specifically, the $nth$,  $(n-1)th$, $(n-2)th$ versions of project data are selected for testing, 
-tuning and training learners, respectively. This will make sure that we don't use the future 
-project data to train learners and predict previous project.
-
-To investigates the impacts of parameters on learners, we use DE as the tuner and compare the G-measure 
-values of Where-based learner with and without tuning, CART with and without tuning and Random 
-Forests. Since the tuning time for Random Forests is very long, hopefully other researchers design
-new heuristics to speed up the tuning process for Random Forests.  For the time being, even though
-we don't tune Random Forests, if tuning help CART outperform Random Forests or improve itself performance ,
-we still could conclude that tuning is helpful and necessary when comparing learners.
-
-Besides the Where-based learner implemented by ourself,  we use the CART and Random Forest modules 
-from scikit-learn \cite{scikit-learn} for this experiment.
-The parameters associated with different learners are listed in Fig.\ref{fig:parameters}.
-(\textbf{NEED to elaborate that there're different versions of CART, what's the point to do this experiment}).
-For each data set, run CART, naive Where-based learner and Random Forests with corresponding default values.
-Then using DE to tune corresponding parameters for CART and Where-based Learner,  and run them again with the optimal parameters from tuning process to test the performance.
-This study ranks learners using the Scott-Knott procedure recommended by Mittas \& Angelis in their 2013
-IEEE TSE paper~\cite{mittas2013ranking}.
-This method sorts a list of $l$ treatments with $ls$ measurements by their median score.
-It then splits $l$ into sub-lists $m,n$ in order to maximize the expected value of differences  in the observed performances before and after divisions.
-
-\section{Result}
-
-\section{Discussion}
-
-\section{Related Work}
-
-Tuning in efforts estimation, software engineering.
-
-Defect Prediction
-
-\section{Threats to Validity}
-
-Internal and external threats
-
-\section{Conclusion}
-
-\section{Acknowledgments}
-
-\bibliographystyle{unsrt}
-\bibliography{tuningpredictor}
-
-%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
-\renewcommand\arraystretch{1.2}
-\begin{figure*}[t!]
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-  \centering
-	\begin{tabular}{|c|c|c|c|l|}
-	\cline{1-5}
-	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
-\multicolumn{1}{c|}{Description} \\ \hline
-	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
-	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
-	& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
-split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
-one is for clustering and the second one is building prediction model. we explicitly call Where-
-clustering tree and CART tree, respectively}. \\ \cline{2-5} 
-	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
-CART tree. \\ \cline{2-5} 
-	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
-number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
-\end{tabular} \\ \cline{2-5} 
-    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
-	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
-clustering tree. \\ \cline{2-5} 
-	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
-	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
-	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
-\hline
-\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
-	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5}
-
-	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{1-5}  
-       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
-\cline{2-5} 
-	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5} 
-	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
-	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_smaples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{2-5} 
-	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
-	 \hline
-
-	\end{tabular}
-    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
-\label{fig:parameters}
-\end{figure*}
-
-%%%%%%%%%%%%%%%% optimal parameters from tuning process%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[t!]
-%\scriptsize
-%  \centering
-%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-%	\hline
-%	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default & 
-%ant  & camel &ivy & jedit & log4j & lucene & poi & synapse & velocity & xalan & xerces \\ \hline
-%	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
-%	& threshold & 0.5 & 0.16 & 0.87 &0.89 & 0.68 &0.58 &0.62&0.06&0.09&1&0.64 &0.02\\ \cline{2-14} 
-%	& infogain & 0.33 & 0.33 & 0.49 &1&0.82 &0.12 &0.54&0.38&0.01&1&0.36&0.25\\ \cline{2-14} 
-%	 & min\_sample\_size & 4& 8 &1 &1&5&8&1&5&9&1&5&5\\ \cline{2-14} 
-%	 & min\_Size & 0.5& 1 & 0.67 & 0.99&1&0.63&1&0.95&0.59&1&0.88 &0.64\\ \cline{2-14} 
-%	 & wriggle &
-%	 & depthMin & 2 & 3 & 4 &1&1&2&1&1&5&1&1&3\\ \cline{2-14} 
-%	 & depthMax & 10 & 8 &14 &16&18&1&16&13&5&9&18&20\\ \cline{2-14} 
-%	 & wherePrune & False & True & True &False&False&False&True&True&False&True&False &True\\ \cline{2-14} 
-%	 & treePrune & True& False & True &True&True&False&False&True&False&False&False &False\\ 
-%\hline
-%	\multirow{4}{*}{CART} 
-%	& threshold & 0.5 & 0.01 & 0.98 &0.94&0.67&0.47&1&0.01&0.12&0.9&0.57 &0.01\\ \cline{2-14} 
-%	 & max\_feature & None &0.01 & 1 &0.29&0.28&0.53&0.13&0.01&0.01&0.87&0.47 &0.01\\ \cline{2-14} 
-%	 %& max\_depth & None &27 & 46 &33&21&42&36&39&17&29&11&31\\ \cline{2-14} 
-%	 & min\_sample\_split & 2 &6 &2 &13&17&12&2&14&12&7&16 &13\\ \cline{2-14} 
-%	 & min\_smaples\_leaf & 1 &6 &3 &18&12&3&10&4&20&8&11&1\\ \hline  
-%    \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  
-%    & threshold & 0.5 & 0.06 &0.88 &1&0.73&0.41&0.81&0.11&0.16&1&0.63&0.29\\ \cline{2-14} 
-%	 & max\_feature & None & 0.21 &0.98 &0.78&0.73&0.36&0.35&0.01&0.01&0.01&0.65 &0.89\\ \cline{2-14} 
-%	 & max\_leaf\_nodes & None & 31 &35 &41&40&23&12&26&41&46&49&35\\ \cline{2-14} 
-%	 & min\_sample\_split & 2 &12 &14 &2&5&8&11&1&16&1&9&20\\ \cline{2-14} 
-%	 & min\_smaples\_leaf & 1 &6 &15 &2&17&3&9&19&8&2&14&9\\ \cline{2-14} 
-%	 &  n\_estimators & 100 &111 &120 &89&68&64&84&107&100&79&113&50\\ \hline
-%
-%	\end{tabular}
-%    \caption {Optimal parameters from tuning process with objetive of G measure over different data sets.}
-%\label{fig:parameters}
-%\end{figure*}
-
-%%%%parameters for pd %%%%%%
-\begin{figure*}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
-& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
-& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
-& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
-& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
-& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
-& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
-& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
-& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
-& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
-& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
-& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
-& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
-& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
-& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of pd}
-\end{figure*}
-
-%%%%parameters for prec %%%%%%
-\begin{figure*}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.53& 0.48& 0.41& 0.35& 0.88& 1& 1& 0.9& 0.96& 0.57& 1& 1& 0.56& 0.57& 0.8& 0.26& 0.65\\ \cline{2-20}
-& infoPrune& 0.33& 0.68& 0.74& 0.31& 0.45& 0.78& 0.31& 0.53& 0.85& 0.04& 0.73& 0.54& 0.15& 1& 0.98& 0.23& 0.9& 0.19\\ \cline{2-20}
-& min\_sample\_size& 4& 3& 6& 5& 2& 1& 5& 7& 1& 7& 5& 2& 8& 1& 1& 1& 2& 2\\ \cline{2-20}
-& min\_Size& 0.5& 0.07& 0.23& 0.2& 0.21& 0.25& 0.54& 0.18& 0.36& 0.28& 0.51& 1.0& 0.33& 0.5& 0.84& 0.83& 0.04& 0.21\\ \cline{2-20}
-& wriggle& 0.2& 0.91& 0.77& 0.58& 0.85& 0.17& 0.66& 0.33& 0.88& 0.13& 0.72& 0.18& 0.07& 0.43& 0.63& 0.74& 0.18& 0.75\\ \cline{2-20}
-& depthMin& 2& 4& 2& 5& 2& 4& 2& 2& 2& 4& 2& 3& 4& 1& 5& 1& 2& 1\\ \cline{2-20}
-& depthMax& 10& 10& 14& 6& 13& 7& 16& 15& 14& 13& 19& 16& 9& 16& 14& 11& 13& 15\\ \cline{2-20}
-& wherePrune& False& True& False& True& True& True& True& True& True& True& True& True& True& True& True& False& True& False\\ \cline{2-20}
-& treePrune& True& True& True& True& True& True& True& False& False& False& True& False& True& True& False& False& False& False\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.76& 0.99& 0.86& 0.48& 1& 1& 1& 0.71& 0.62& 0.65& 1& 0.95& 0.64& 0.5& 1& 0.99& 1\\ \cline{2-20}
-& max\_feature& None& 0.09& 0.13& 0.05& 0.01& 0.01& 0.47& 0.01& 0.1& 0.63& 0.62& 0.44& 0.27& 0.28& 0.04& 0.75& 0.96& 0.21\\ \cline{2-20}
-& min\_samples\_split& 2& 4& 19& 9& 9& 17& 14& 14& 16& 14& 12& 17& 3& 10& 12& 20& 13& 6\\ \cline{2-20}
-& min\_samples\_leaf& 1& 15& 17& 8& 7& 1& 20& 1& 9& 12& 15& 10& 13& 7& 10& 4& 7& 20\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.92& 0.99& 0.71& 0.7& 1& 0.82& 1& 1& 1& 0.96& 0.73& 1& 0.76& 0.33& 1& 1& 0.98\\ \cline{2-20}
-& max\_feature& None& 0.23& 0.13& 0.46& 0.69& 0.37& 0.56& 0.71& 0.01& 1& 0.01& 0.85& 0.48& 0.34& 0.02& 0.01& 0.08& 0.62\\ \cline{2-20}
-& max\_leaf\_nodes& None& 12& 49& 23& 39& 10& 17& 20& 10& 10& 44& 37& 18& 35& 11& 31& 35& 28\\ \cline{2-20}
-& min\_samples\_split& 2& 18& 8& 14& 1& 11& 3& 2& 1& 4& 14& 2& 1& 13& 8& 18& 2& 13\\ \cline{2-20}
-& min\_samples\_leaf& 1& 11& 5& 11& 3& 2& 4& 20& 2& 2& 10& 3& 7& 7& 15& 6& 2& 9\\ \cline{2-20}
-& n\_estimators& 100& 130& 146& 66& 96& 50& 50& 136& 84& 83& 129& 51& 150& 99& 58& 88& 85& 61\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of prec}
-\end{figure*}
-
-%%%%parameters for F %%%%%%
-\begin{figure*}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.12& 0.78& 0.3& 0.01& 0.78& 1& 0.99& 0.44& 0.72& 0.21& 0.41& 1& 0.04& 0.7& 0.36& 0.66& 0.42\\ \cline{2-20}
-& infoPrune& 0.33& 0.58& 0.2& 0.41& 0.19& 0.82& 0.91& 0.35& 1& 0.85& 0.46& 0.24& 1.0& 0.85& 0.36& 0.48& 0.42& 0.82\\ \cline{2-20}
-& min\_sample\_size& 4& 6& 1& 1& 6& 8& 6& 7& 5& 1& 5& 8& 2& 7& 5& 3& 1& 1\\ \cline{2-20}
-& min\_Size& 0.5& 0.8& 0.75& 0.47& 0.01& 1& 0.64& 0.99& 0.43& 0.23& 0.47& 0.72& 1& 0.89& 0.69& 0.88& 0.38& 0.75\\ \cline{2-20}
-& wriggle& 0.2& 0.21& 0.7& 0.83& 0.25& 0.55& 0.01& 0.63& 0.93& 0.43& 0.33& 0.52& 0.32& 0.72& 0.1& 0.43& 0.34& 0.1\\ \cline{2-20}
-& depthMin& 2& 4& 5& 4& 3& 1& 6& 1& 4& 1& 1& 4& 1& 2& 2& 4& 5& 1\\ \cline{2-20}
-& depthMax& 10& 16& 11& 5& 19& 8& 10& 14& 19& 5& 6& 6& 16& 3& 11& 5& 18& 12\\ \cline{2-20}
-& wherePrune& False& True& True& True& False& True& False& False& True& True& True& False& True& True& False& True& False& True\\ \cline{2-20}
-& treePrune& True& False& True& True& True& True& False& False& True& False& False& False& True& True& False& False& True& True\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.01& 0.62& 0.13& 0.01& 1& 0.8& 0.7& 0.66& 0.72& 0.32& 0.09& 0.7& 0.01& 0.01& 0.91& 0.84& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.24& 0.88& 0.19& 0.01& 0.01& 0.8& 0.76& 0.28& 0.5& 0.22& 0.18& 0.01& 0.58& 0.01& 0.01& 0.3& 0.01\\ \cline{2-20}
-& min\_samples\_split& 2& 19& 3& 13& 5& 2& 10& 8& 9& 11& 12& 7& 10& 20& 5& 4& 14& 11\\ \cline{2-20}
-& min\_samples\_leaf& 1& 15& 18& 11& 13& 3& 13& 9& 10& 15& 8& 15& 15& 7& 10& 10& 4& 1\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.01& 0.49& 0.14& 0.01& 1& 1& 1& 1& 1& 0.66& 0.53& 1& 0.01& 0.21& 1& 1& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.89& 0.21& 0.01& 0.04& 0.81& 0.45& 0.01& 0.49& 0.01& 0.01& 0.12& 0.81& 0.01& 0.07& 0.01& 0.62& 0.61\\ \cline{2-20}
-& max\_leaf\_nodes& None& 21& 16& 49& 10& 26& 32& 39& 22& 10& 42& 24& 43& 38& 10& 10& 10& 20\\ \cline{2-20}
-& min\_samples\_split& 2& 11& 9& 19& 15& 6& 14& 6& 3& 4& 10& 18& 2& 8& 7& 10& 10& 16\\ \cline{2-20}
-& min\_samples\_leaf& 1& 6& 11& 13& 7& 16& 4& 2& 18& 2& 6& 19& 2& 9& 4& 17& 2& 5\\ \cline{2-20}
-& n\_estimators& 100& 88& 99& 124& 148& 56& 101& 116& 55& 122& 112& 75& 55& 92& 129& 58& 107& 121\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of F}
-\end{figure*}
-
-%%%%%%%%%%%%%%%% defectives and non-defectives for each datasets%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{c c c c c c c c c c }
-  \hline\hline
-  Dataset &ant&antV1&antV2&camel&camelV1&ivy&jedit&jeditV1&jeditV2
-\\\hline
-  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
-\\  tunning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
-\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
-\\  \end{tabular}
-   \caption{The percentage of defective instances in each experimental data set. For each experiment,  training, tuning and testing data are composed of single chronological data file}
-\end{figure*}
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{c c c c c c c c c c }
-  \hline\hline
-  Dataset &log4j&lucene&poi&poiV1&synapse&velocity&xerces&xercesV1
-\\\hline
-  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
-\\  tunning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
-\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
-\\  \end{tabular}
-
-   \caption{The percentage of defective instances in each experimental data set. For each experiment,  training, tuning and testing data are composed of single chronological data file}
-\end{figure*}
-
-%\begin{figure*}[!th]
-%  \scriptsize
-%  \centering
-%		\begin{tabular}{|l|l|l|}
-%		\hline
-%		\multicolumn{1}{|c|}{Data Set} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}} Feature Selections\\ with  Default Parameters\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Feature Selection\\ with Tuning Parameters\end{tabular}} \\ \hline
-%	   ant  & mfa, lcom3, cam, ic, dam   & wmc, lcom3, cam, dam, npm, rfc  \\ \hline
-%		camel & cam, wmc, dit, mfa, rfc, loc & rfc, cam, loc, wmc, dam, dit, mfa, lcom3, npm\\ \hline
-%		ivy & cam, dit, dam, ic, lcom3& cam, dam, mfa\\ \hline
-%		jedit& mfa, dam, cam, dit, cbm, ic& mfa, loc, dit, dam, cam, wmc  \\ \hline
-%		log4j & lcom3, mfa, loc, ic, dit& mfa, wmc  \\ \hline
-%		lucene & mfa, lcom3, cam, dam, ic& wmc, lcom3, avg\_cc, rfc, ce, mfa, dam, npm, cam \\ \hline
-%		poi & mfa, dam, amc, lcom3, cbm, loc& loc, lcom3, cam, amc, dam                                                     \\ \hline
-%		synapse & dam, loc, mfa, cam & loc  \\ \hline
-%		velocity& dit, dam, lcom3, ic, mfa& mfa, cam, avg\_cc, loc, lcom3, cbo, dam, ic, rfc, lcom \\ \hline
-%		xalan  & mfa, cam, wmc, lcom3, rfc, dit & mfa, rfc, loc, dam, lcom3, wmc, npm \\ \hline
-%		xerces & cam, wmc, mfa, rfc, amc, loc& mfa, loc, cam, amc, avg\_cc\\ \hline
-%		\end{tabular}
-%		\caption{Features selection before and after tuning over objective of G values }
-%\end{figure*}
-
-%%%%%%%%%%%%%%%% feature selection over pd%%%%%%%%%%%%%%%%%%%%%
-
-\setlength{\tabcolsep}{3pt}
-\renewcommand\arraystretch{1.2}
-
-%%%%%%%%%%%%%% pd bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
-  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(pd) } \\
-  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
-\multicolumn{1}{c}{~}\\
-antV0 & 53 & {\rone} & 100 & {\rfour} & 38 &         & 100 & {\rfour} & 78 & {\rthree} & 97 & {\rfour}\\
-antV1 & 7 &         & 100 & {\rfour} & 39 & {\rone} & 100 & {\rfour} & 95 & {\rfour} & 100 & {\rfour}\\
-antV2 & 0 &         & 100 & {\rfour} & 37 & {\rone} & 100 & {\rfour} & 92 & {\rfour} & 100 & {\rfour}\\
-camelV0 & 0 &         & 100 & {\rfour} & 6 &         & 100 & {\rfour} & 66 & {\rthree} & 99 & {\rfour}\\
-camelV1 & 80 & {\rthree} & 100 & {\rfour} & 46 &         & 100 & {\rfour} & 80 & {\rthree} & 100 & {\rfour}\\
-ivyV0 & 93 & {\rtwo} & 100 & {\rfour} & 88 &         & 100 & {\rfour} & 95 & {\rtwo} & 100 & {\rfour}\\
-jeditV0 & 89 & {\rthree} & 100 & {\rfour} & 66 &         & 95 & {\rfour} & 96 & {\rfour} & 100 & {\rfour}\\
-jeditV1 & 75 & {\rtwo} & 100 & {\rfour} & 50 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-jeditV2 & 45 &         & 100 & {\rfour} & 36 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-log4jV0 & 46 & {\rone} & 100 & {\rfour} & 31 &         & 100 & {\rfour} & 88 & {\rfour} & 100 & {\rfour}\\
-luceneV0 & 81 & {\rthree} & 100 & {\rfour} & 48 &         & 100 & {\rfour} & 98 & {\rfour} & 100 & {\rfour}\\
-poiV0 & 89 & {\rtwo} & 100 & {\rfour} & 79 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-poiV1 & 2 &         & 100 & {\rfour} & 12 &         & 100 & {\rfour} & 89 & {\rfour} & 100 & {\rfour}\\
-synapseV0 & 0 &         & 100 & {\rfour} & 28 & {\rone} & 100 & {\rfour} & 90 & {\rfour} & 100 & {\rfour}\\
-velocityV0 & 100 & {\rfour} & 100 & {\rfour} & 86 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-xercesV0 & 64 & {\rone} & 100 & {\rfour} & 46 &         & 100 & {\rfour} & 78 & {\rtwo} & 91 & {\rfour}\\
-xercesV1 & 15 &         & 100 & {\rfour} & 11 &         & 100 & {\rfour} & 68 & {\rthree} & 87 & {\rfour}\\
-%Albrecht  &   7         &   24   &   Projects from IBM   & 28 &     & 40 & {\rtwo} & 38 & {\rtwo} & 38 & {\rtwo} & 49 & {\rfour} \\
-%China      &   18       &   488   &   Projects from Chinese software companies   &   38   &  {\rtwo}  &   34   &       &   34   &       &   35   &  {\rone}   &   41   &   {\rfour}\\
-%Cosmic     &   y   &   y   &   Projects described in functiion points   &   98   &   {\rfour}   &   75   &       &   85   &    {\rtwo}   &   85   &   {\rtwo}    &   89   &   {\rtwo}\\
-%ISBSG10    &   y   &   y   &   From the ISBSG benchmark suite   &   56   &       &   62   &     &   126   &   {\rfour}   &   66   &   {\rone}   &   65   &   {\rone}\\
-%Kemerer    &   7   &   15   &   Large business applications   &   42   &  {\rtwo}  &   24   &   &   55   &  {\rfour} &   55   &   {\rfour}   &   55   &   {\rfour}\\
-%Kitchenham &    6   &   145   &  y    &   34   &   &   43   &   {\rthree}   &   34   &  &   43   &  {\rthree}  &   47   &  {\rfour}  \\
-%Maxwell    &   27  &   62  & Projects from commercial banks in Finland   &   57   &   {\rtwo}   &   56   &   {\rtwo}   &   47   &   &   53   &  {\rone} &   64   &   {\rfour}\\
-%Miyazaki   &   8   &   48 &Japanese software projects developed in COBOL   &   39   &       &   41   &   &   41   &    &   57   &   {\rfour}   &   57   &   {\rfour}\\
-%Telecom    &   3   &   18   &   Maintenance projects for telecom companies   &   23   &       &   26   &   {\rtwo}   &   31   & {\rfour}  &   31   &   {\rfour}   &   31   &   {\rfour}\\
-%Usp05      &   7   &  203  &  Collected from university student projects   &   30   &    &   50   & {\rfour} &   45   & {\rthree}  &   40   &   {\rtwo}  &   50   &   {\rfour}\\
-\end{tabular}
-\end{minipage}\begin{minipage}{.15\linewidth}
-\begin{tabular}{|p{\linewidth}|}\hline
-
-~\\
-
-{\bf KEY:}
-
-~\\
-
-pd percentile ranges:
-
-~\\
-
-80th to 100th = {\rfour}
-
-60th to 80th ~ = {\rthree}
-
-40th to 60th  ~ = {\rtwo}
-
-20th to 40th  ~ = {\rone}
-
-~\\
-
-An absent bar denotes\newline 0th to 20th percentile.
-
-~\\
-
-Percentiles computed  separately
-for each data set.\\\hline
-\end{tabular}
-\end{minipage}
-\caption{Median pd values in tune once and test ten times experiment. 
-Gray bars  show  pd values
-discretized into 20th percentiles ranges from min to max.
-All data available from http://openscience.us/repo/effort.
-}\label{fig:nonc}
-\end{figure*}
-
-%%%%%%%%%%%%%% pd bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%% precision bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-\renewcommand{\baselinestretch}{0.8}
-
-\scriptsize  
-\begin{tabular}{r|r@{~}l@{~}|r@{~}l|r@{~}l|r@{~}l|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
-      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forests}         \\\hline
-  Data set   &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{Naive}  &   \multicolumn{2}{c}{Tuned}\\\hline
-
-antV0 & 30 &         & $\bigstar$ 89 & {\rfour} & 27 &         &$\bigstar$ 89 & {\rfour} & 40 & {\rone} &$\bigstar$ 89 & {\rfour}\\
-antV1 & 32 &         &$\bigstar$ 74 & {\rfour} & 41 & {\rone} &$\bigstar$ 74 & {\rfour} & 57 & {\rtwo} &$\bigstar$ 74 & {\rfour}\\
-antV2 & 78 & {\rfour} &$\bigstar$ 78 & {\rfour} & 52 &         & 67 & {\rthree} & 66 & {\rtwo} & 50 &        \\
-camelV0 &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour} & 26 &         & 37 &         &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour}\\
-camelV1 & 22 &         &$\bigstar$ 81 & {\rfour} & 23 &         & 25 &         & 28 &         & 28 &        \\
-ivyV0 & 16 &         & 23 & {\rthree} & 18 & {\rone} &$\bigstar$ 25 & {\rfour} & 18 & {\rone} & 19 & {\rone}\\
-jeditV0 & 35 &         & 75 & {\rthree} & 49 & {\rone} &$\bigstar$ 86 & {\rfour} & 52 & {\rone} & 50 & {\rone}\\
-jeditV1 & 24 &         &$\bigstar$ 87 & {\rfour} & 28 &         & 62 & {\rthree} & 36 &         & 42 & {\rone}\\
-jeditV2 & 2 &         &$\bigstar$ 98 & {\rfour} & 3 &         & 4 &         & 5 &         & 6 &        \\
-log4jV0 & 94 &         &$\bigstar$100 & {\rfour} & 97 & {\rtwo} & 98 & {\rthree} &$\bigstar$ 100 & {\rfour} &$\bigstar$100 & {\rfour}\\
-luceneV0 & 61 &         & 71 & {\rtwo} & 67 & {\rone} &$\bigstar$ 78 & {\rfour} & 69 & {\rtwo} & 70 & {\rtwo}\\
-poiV0 & 70 &         &$\bigstar$ 92 & {\rfour} & 77 & {\rone} & 79 & {\rtwo} & 79 & {\rtwo} & 75 & {\rone}\\
-poiV1 & 100 & {\rfour} &$\bigstar$ 89 & {\rfour} & 73 & {\rtwo} &$\bigstar$ 89 & {\rfour} & 86 & {\rthree} & 36 &        \\
-synapseV0 & 66 & {\rthree} & 0 &         & 71 & {\rthree} &$\bigstar$ 95 & {\rfour} & 59 & {\rthree} & 67 & {\rthree}\\
-velocityV0 & 34 &         & 34 &         & 34 &         &$\bigstar$ 45 & {\rfour} & 40 & {\rtwo} & 41 & {\rthree}\\
-xercesV0 & 13 &         &$\bigstar$ 85 & {\rfour} & 14 &         & 73 & {\rfour} & 16 &         & 13 &        \\
-xercesV1 &$\bigstar$ 56 & {\rfour} & 26 &         & 55 & {\rfour} & 26 &         & 41 & {\rtwo} & 26 &        \\
-\end{tabular}
-
-\caption{Precision values in tune   and naive runs.
-All data available from http://openscience.us/repo/effort. {\bf KEY:}
-  percentile ranges:\newline
-80th to 100th= {\rfour};
-60th to 80th= {\rthree}; 
-40th to 60th= {\rtwo};
-20th to 40th= {\rone};
-an absent bar shows  0th to 20th.
-Percentiles computed  separately
-for each row.
-
-}\label{fig:nonc}
-\end{figure}
-
-%%%%%%%%%%%%%% precision bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|@{~}r@{~}l|r@{~}l|@{~}r@{~}l}
-  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(F ) } \\
-  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
-\multicolumn{1}{c}{~}\\
-ant0 &$\bigstar$ 39 & {\rfour} & 26 & {\rone} & 32 & {\rtwo} & 25 &         & 25 &         & 22 &        \\
-ant1 & 11 &         &$\bigstar$ 85 & {\rfour} & 40 & {\rone} & 49 & {\rtwo} & 39 & {\rone} & 33 & {\rone}\\
-ant2 & 0 &         &$\bigstar$ 86 & {\rfour} & 44 & {\rtwo} & 51 & {\rtwo} & 52 & {\rthree} & 56 & {\rthree}\\
-camel0 & 0 &         &$\bigstar$ 28 & {\rfour} & 9 & {\rone} &$\bigstar$ 28 & {\rfour} & 34 & {\rfour} & 31 & {\rfour}\\
-camel1 & 34 & {\rthree} &$\bigstar$ 35 & {\rfour} & 31 &         & 33 & {\rtwo} & 33 & {\rtwo} & 30 &        \\
-ivy0 & 27 &         & 30 & {\rone} & 30 & {\rone} & 32 & {\rthree} &$\bigstar$ 35 & {\rfour} &$\bigstar$ 35 & {\rfour}\\
-jedit0 & 50 &         & 55 & {\rtwo} & 56 & {\rtwo} & 55 & {\rtwo} &$\bigstar$ 61 & {\rfour} & 60 & {\rfour}\\
-jedit1 & 37 & {\rone} & 34 &         & 36 &         & 47 & {\rfour} & 45 & {\rthree} &$\bigstar$ 48 & {\rfour}\\
-jedit2 & 4 &         &$\bigstar$ 99 & {\rfour} & 5 &         & 9 &         & 9 &         & 11 &        \\
-log4j0 & 62 & {\rfour} & 7 &         & 47 & {\rthree} &$\bigstar$ 64 & {\rfour} & 53 & {\rfour} & 45 & {\rthree}\\
-lucene0 & 70 & {\rthree} & 73 & {\rfour} & 56 &         &$\bigstar$ 75 & {\rfour} & 70 & {\rthree} &$\bigstar$ 75 & {\rfour}\\
-poi0 &$\bigstar$ 78 & {\rfour} & 63 &         & 74 & {\rthree} & 70 & {\rtwo} & 73 & {\rthree} & 72 & {\rtwo}\\
-poi1 & 5 &         &$\bigstar$ 78 & {\rfour} & 21 & {\rone} &$\bigstar$ 78 & {\rfour} & 76 & {\rfour} &$\bigstar$ 78 & {\rfour}\\
-synapse0 & 0 &         & 2 &         & 40 & {\rthree} &$\bigstar$ 56 & {\rfour} & 52 & {\rfour} & 55 & {\rfour}\\
-velocity0 & 51 &         & 51 &         & 49 &         & 51 &         & 53 & {\rone} &$\bigstar$ 59 & {\rfour}\\
-xerces0 & 22 & {\rthree} & 20 & {\rone} & 21 & {\rtwo} & 18 &         & 23 & {\rfour} & 22 & {\rthree}\\
-xerces1 & 23 & {\rone} & 2 &         & 18 & {\rone} & 36 & {\rtwo} & 68 & {\rfour} &$\bigstar$ 71 & {\rfour}\\
-\end{tabular}
-\end{minipage}\begin{minipage}{.15\linewidth}
-\begin{tabular}{|p{\linewidth}|}\hline
-
-~\\
-
-{\bf KEY:}
-
-~\\
-
-F percentile ranges:
-
-~\\
-
-80th to 100th = {\rfour}
-
-60th to 80th ~ = {\rthree}
-
-40th to 60th  ~ = {\rtwo}
-
-20th to 40th  ~ = {\rone}
-
-~\\
-
-An absent bar denotes\newline 0th to 20th percentile.
-
-~\\
-
-Percentiles computed  separately
-for each data set.\\\hline
-\end{tabular}
-\end{minipage}
-\caption{Median F values in tune once and test ten times experiment. 
-Gray bars  show  F values
-discretized into 20th percentiles ranges from min to max.
-All data available from http://openscience.us/repo/effort.
-}\label{fig:nonc}
-\end{figure*}
-
-%%%%%%%%%%%%%% F bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%  counts of features for different goals%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{c|c c|c c|c c|c c| c c }
-
-    & \multicolumn{2}{c|}{Pd} &  \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{F} &  \multicolumn{2}{c|}{SUM}\\
- &&&&&&&&\\
-Features& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-\\\hline
-noc&	&	&	&	&	&	&	 &	 &	\\
-ca&	&	&	&	1&	&	&	 &	1&	\\
-max\_cc&	&	&	&	1&	&	&	 &	1&	\\
-moa&	&	&	&	1&	&	1&	 &	2&	\\
-avg\_cc&	&	&	&	3&	&	2&	 &	5&	\\
-cbo&	&	&	&	1&	&	3&	 &	4&	\\
-npm&	&	&	&	2&	&	4&	 &	6&	\\
-lcom&	&	&	&	1&	&	4&	 &	5&	\\
-ce&	&	&	&	3&	&	2&	 &	5&	\\
-amc&	4&	&	4&	1&	4&	5&	12&	6&	\\
-cbm&	6&	&	4&	1&	4&	2&	14&	3&	\\
-rfc&	4&	&	4&	4&	4&	9&	12&	13&	\\
-wmc&	5&	&	5&	3&	5&	7&	15&	10&	\\
-ic&	8&	1&	9&	3&	8&	8&	25&	12&	\\
-dit&	8&	1&	8&	5&	7&	8&	23&	14&	\\
-cam&	9&	&	9&	3&	9&	8&	27&	11&	\\
-loc&	9&	1&	9&	4&	9&	8&	27&	13&	\\
-lcom3&	9&	&	8&	5&	8&	13&	25&	18&	\\
-dam&	14&	&	14&	6&	14&	12&	42&	18&	\\
-mfa&	16&	3&	16&	6&	16&	16&	48&	25&	\\
-
-  \end{tabular}
-    \caption{Counts of features selected by different goals.
-For each goal, the numbers in right and left columns represent the counts of features selected for all the data sets with and without tuning processes.}
-\end{figure}
-
-%%%%time for G %%%%%%
-
-\section{Discussion}
-Data torturing, on not? Offer insight on the complexities of data sets, demanding
-that before they are used, we spend more time describing the context of use. Not offering
-conclusions that are over-stated. Taking care to precisely describe the boundaries of a 
-conclusion. While at the same time showing how to makde better conclusions on new
-data, whenever it arrives. And ensuring that those new conclusions are tuned
-to the goals of the business users who are funding the analysis and will use its results.
-
-\begin{figure}[!t]
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-Some goals related to aspects of defect prediction:
-\be
-\item
-Mission-critical systems are risk averse and may accept very high false alarm rates,
-just as long as they catch any life-threatening possibility. That is, such projects
-do not care about effort- they want to {\em maximize recall} regardless of any impact
-that might have on the false alarm rate.
-\item
-Cost averse managers may accept lower probabilities of
-detection (the recall measure), just as long as they {\em do not waste budgets on false alarms}. This community
-seeks to {\em minimize false alarms} while maintaining {\em some level of adequate recall}.
-\item  Suppose a new hire wants
- to impress their manager. That 
- new hire might want to ensure that no result presented to  management contains  true negative;
-i.e. they wish to {\em maximize precision}.
-\item
-Some communities do not care about   low precision,
-just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction 
-{\em selectivity} and offer an
-extensive discussion of the merits of this measure~\cite{hayes06}.
-\ee
-\\\hline
-Beyond defect prediction are other goals that combine defect prediction with other economic
-factors:
-\be
-\setcounter{enumi}{4}
-\item
-Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
-say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
-that contain the most bugs.
-\item In other work, Yin et al. are concerned about
- {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
-These bugs occur  when (say) developers try to fix parts of the code
-where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
-for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
-\item In {\em Better-faster-cheaper}, we seek  project changes that lead
-to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
-\item {\em  Rush-to-market} is another economic-based optimization measure.
-A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
-as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
-in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
-used to subsequently fix any issues with version 1.0)~\cite{huang06}.
-\ee
-\\\hline
-All the above measures relate to the tendency of a predictor to find something. Another style
-of measure would be to check the {\em variability} of that predictor:
-\be
-\setcounter{enumi}{8}
-\item
-In their study on reproducibility of SE results,
- Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
-Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
-\ee
-\\\hline
-\end{tabular}
-\caption{Reasoning about software many have many different goals including the nine shown here. Many of
-these goals are defined in terms of 
-\fig{criteria}.
-}\label{fig:goals}
-\end{figure}
-\fig{goals} lists other performance measures that we have seen at client sites or in the literature. Note that:
-\be
-\item This list is very long.
-\item This list keeps growing.
-\ee As to this second point,
-often when we work
-with new clients, they surprise us with yet another domain-specific criteria that is important for the business.
-That is, neither \fig{criteria} or \fig{goals} is not a complete list of all possible assessment criteria.
-
-Our reading of the defect prediction literature is that most papers only explore a small subset of 
- \fig{criteria} or \fig{goals}. We think this is a mistake and researchers should more to a more general
-framework where they explore a wide and changing set of evaluation criteria. 
-Hence, this paper.
-
-\end{document}

### 2015-03-11 tuningpredictor.tex
Updates from ShareLaTeX

@@
 {\bf Keywords:} defect prediction, CART, random forests,
-Fastmap,   bootstrap sampling, effect size, A12,differential evolution,
+differential evolution,
 search-based software engineering.
@@
 to just  few minutes to find good tunings.
+
 These results   challenge much prior work into defect prediction:
-\bi 
-\item 
 Numerous   prominent papers have claimed 
@@
 best learner (Random Forests).
-\item
-The improvements achieved via differential evolution are too large to discount.
-Yet those result show that different attributes are ``best'' for different
+
+Another class of conclusions challenged by this paper are research papers
+that use data miners to   show that different attributes are ``best'' for different
 data sets and even different goals for the tunings. Hence, it is no longer
@@
 are better than others; e.g. as  done by~\cite{rahman2013how}. 
-\ei 
+For example, in 2013,
+Rahman et al
+\cite{rahman2013how}  used results from logistic regression to conclude
+that code metrics are generally less useful than process
+metrics for  predicting defects from static code analysis.  
+In the same year, Bell et al. (who also used negative binomial regression) argued that
+software defect prediction was not improved by adding attributes relating to the social
+structure of programmer teams~\cite{bell2013limited}.
+
 Given the simplicity and effectiveness of differential evolution,
@@
 
-We formulate and present two cost-effectiveness-based
-accounting approaches to the comparability of bugginess
-identification problem (CBI).
-We find no significant differences in the cost-effectiveness
-of the DP and the two SBF techniques —
-FindBugs and pmd— we could evaluate
-
-\section{Other sutff}
-XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores.
-Given that, the next question becomes ``what performance scores do you want?''.
-This is an interesting issue since there is no single best answer.
-XXX
-
-How ``true'' are the  models generated by software analytics?
-Suppose we use a model generated from software project data to, for example,
-assess the relative value of OO metrics vs procedural metrics for predicting
-project defects. Are we reporting ``truth'' in any sense of the word? And for how
-many other projects  and how many kinds of questions might we find that same ``truth''?
-
-This is not some abstract question-- it is an open and pressing matter.
-Any reading of the recent proceedings of FSE, ICSE, ASE, etc will discover hundreds
-of papers using data miners to make conclusions about software projects. 
-For example, some  analysts have made conclusions
-about 
-{\em what attributes
-have most influence on a software project}.
-For example, in 2013,
-Rahman et al
-\cite{rahman2013how}  used results from logistic regression to conclude
-that code metrics are generally less useful than process
-metrics for  predicting defects from static code analysis.  
-In the same year, Bell et al. (who also used negative binomial regression) argued that
-software defect prediction was not improved by adding in~\cite{bell2013limited}.
-
-@article{bell2013limited,
-  title={The limited impact of individual developer data on software defect prediction},
-  author={Bell, Robert M and Ostrand, Thomas J and Weyuker, Elaine J},
-  journal={Empirical Software Engineering},
-  volume={18},
-  number={3},
-  pages={478--505},
-  year={2013},
-  publisher={Springer}
-}
-
-The results of this paper offer a very different picture  to recent prominent results from prior authors.
-Lessmann et al.~\cite{lessmann2008benchmarking}, Rahman et al.~\cite{rahman2013how} and Arshiholm et al.~\cite{arisholm06} argue that when it comes to defect prediction, different learners often
-produce statistically similar results. For this reason  Rahman et al. only present results their logistic
-regression results, commenting that ``dor brevity, only results from LR are
-presented; other learning models give similar results''~\cite{rahman2013how}. Note that those prior results,
-where most learners achieved the same results, arose from the default parameter settings from those learners.
-
-Our results, on the other hand, come from tuning a data miner's parameters. In those results,
-we found that the choice of parameters had dramatic impacts on data mining performance.
-For example, we show results below where:   
-\bi 
-\item 
-Tuning improved precision values from  2\% to 98\%; or
-\item 
-Tuning improved false alarm values from 69\% to 0\%; or
-\item 
-Tuning improved recall values from 0 to 100\%; or
-\item 
-Tuning improved the f-measure (which is the harmonic mean of recall and precision) from 0 to 86\%.
-\ei   
-In terms of changing SE research methodologies, an important aspect of these results is that usually XXXX always different.
-cannot determine without experimentation which learner will, after tuning, yield the best results for a particular data set.
-Hence it is no longer viable for researchers to trust the recommendations
-of other researchers working with other data sets that ``data miner XYZ is best''. Before
-offering a conclusion about a particular data set, researchers need now augment  their 
-papers with preliminary tuning studies (the results of which select the tunings+data miners to be used
-to make conclusions for the second half of their paper).
-
-The good news is that such tuning is not an arduous task. The differential evolution algorithm 
-used in this study is wdiely available in many standard  toolkits and languages\footnote{See the long list at
-www1.icsi.berkeley.edu/~storn/code.html.}
-And even if somehow those tools and prior implementations are not workable at a local site, 
-differential evolution is very simple to code. Hence, it can readily and quickly implemented.
-
-When we discuss these results with colleagues, one response we get is ``enough of the parameter tuning.. lets use simpler methods''. 
-While we understand their motivation (to keep thing simple), software project
-data cannot necessarily be condensed to (say) a simple univariate analysis that
-reports how one independent variable effects a dependent variable.
-Such a simplistic analysis can miss significant interaction
-effects when multiple factors combine to effect the target variable. For example,
-one of the base results in defect prediction is that predictors formed from
-a single variable perform much worse than those can combined multiple variables (three or more)~\cite{me07b}.
-
-If those results come from an analysis of a complex interactions between attributes,
-then some kind of data mining method\footnote{By this term we mean the
-full gamut of methods for large-scale analysis of
-data including statistical
-parametric methods (that assume a particular distribution then strive to learn the parameters of that distribution); kernel methods;
-dimensionality  synthesis methods; 
-instance weighting schemes; feature subset selection methods
-outlier removal methods;
-decision tree learners; neural networks; and instance-based
-methods including clustering and/or   case-based reasoning.} then there is the
-{\em tuning problem} of how to set the myriad of parameters that 
-control the learner.
-
-\item
-What data miners are better than others for particular tasks
-in software analytics. 
-\ei
-
-Also, in 2007, one of us (Menzies) claimed that Naive Bayes
-classifiers with a certain lind of pre-processor were better than entropy-based decision trees for defect prediction~\cite{me07b}.
-Similarly, in 2008 Lessmann et al.~\cite{lessmann2008benchmarking} argued  that 
-Random Forests~\cite{brieman00} and CART ~\cite{brieman84} work best, worst for learning software defect predictors from
-static code attributes. Similar claims that one learner was better than another
-have been made by many other authors; e.g.
-
-We write to suggest that all those conclusions may be wrong or, at the very most,
-correct within a very limited context. At the very least, the conclusions
-of those papers (and literally dozens of similar papers, include severl
-of our own~\cite{me02e,me02k,me03a,me06d,me07b}) need to be revisited
-in light of this paper's results on the effects of tuning on data miners.
-
-Machine learners
-are controlled by parameters that decide (e.g.) when to stop recursively
-dividing data into smaller section or (e.g.) what thresholds for errors are small
-enough to be acceptable. When used ``off-the-shelf'', analytst
-use default settings for those parameters. We find that  a 
-simple optimization scheme (differential evolution) can find much
-better tunings that can dramatically change the performance of
-the learned model (measured in terms of false alarm rates, recall,
-precision, f-measure, and g-measure).  From this first result,
-we conclude that {\bf parameter tuning with some optimizer such as differential
-evolution should become standard practice}.
-
-Our next observation is that observations about miner1 being better
-than miner2 do not survive tuning. To be specific: given some
-ranking of data miners for some task such as defect prediction,
-we find that tuning can reverse those rankings such that the worst untu
-
-Tuning the data miners with different evolution takes some
-times (around an order of magnitude slower than the learning), but not an impractically slower amount of time. Further, when we look at what
-attrub
-
-Our reading of the
-
-good news:
-\bi 
-\item Tuning is easy (but one measure, at least an order of magnitude easier than 
-standard optimization problems)
-\item Tuning can dramatically improve the performance of a learner (in one case, from recalls
-of zero to 70\%)
-\ei
-interesting news
-\bi 
-\item tunings different for different data sets.
-\ei 
-bad news:
-\bi
-\item Tuning also changes what was learned
-\bi
-\item Supposedly ``bad'' learners start working much better than supposedly ``best'' learners;
-\item The models used in the tuned models were very different to those used in the untuned learners.
-\ei 
-\ei 
-and we reflect on that model, are we
-
-will it reveal the `1`t
-A standard approach to software analutics
-Software has becoming a large and complex system and delivering reliable and quality 
-software is imperative for development teams. Empirical study shows that the longer the 
-defects exist in software systems, the more the cost of time and money it will take to fix it 
-\textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
-defects in their system as early as possible. Defect prediction has been investigated 
-extensively in industrial and academia during the past two decades. As an important research 
-field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, 
-menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} 
-over static code features of software system has been demonstrated to be a way to predict 
-which models are more likely to contain defects.
-
-Classification is an important approach to predict whether some modules in the projects are 
-defective or non-defective. The general idea is to train the learners by using parts of data 
-sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with 
-remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed 
-based an different data mining classifiers, including CART, Random Forest 
-\cite{guo2004robust},  Naive Bayes\cite{menzies2007data},Logistic Regression 
-\cite{khoshgoftaar1999logistic}. During the past years, authors claimed that their new 
-defective learner outperformed others according to their experiment and statistical analysis. 
-To evalute those learners objectively in terms of accuracy, Lessmann et al
-\cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
-\begin{figure}
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-When applying case-based reasoning, researchers use different settings including how they measure dis- tance between instances (examples include the Euclidean measure, Manhattan and Chebyshev).
-Other settings control if numerics are normalized min..max to 0..1, before they are used in the distance measure.
-
-Another set of settings refers to how to handle non-numeric distances or missing values.
-Some researchers delete training data with missing information while others compute missing values via, say, median values.
-
-After feature selection comes instance selection.
-There are many settings for instance selectors such as use outlier removal or prototype generation.
-Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
-The next set of settings concern how many neighbors to use (k=1,2,5,etc).
-Some researchers set ``k'' in dynamic pre-learning phase that checks the training data to find what ``k'' works best for that data.
-
-Once the neighbors are known, the next settings control how to summarize their information.
-Some researchers use means, other use medians, or a weighted sum that uses the distance of the neighbor from the test instance (and that weighting might be determined by some kernel such as uniform, triangular, Gaussian, cosine, or Epanechnikov).
-Researchers may use other settings to control different pre-processors.
-E.g.
-some discretize numeric values (via equal width or equal frequency) using some binning policy (and researchers differ on how many bins are best).\\\hline
-\end{tabular}
-\caption{Some tunings for SE predictive systems.
-Found by this author while preparing this proposal in a day of reading the SE predictive modeling literature on case-based reasoning and effort estimation.
-Note that other kinds of prediction systems (decision trees, neural nets, linear repression, etc) have yet more adjustable design options.}\label{fig:adjust}
-\end{figure}
-
-domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
-with $\alpha = 0.05$, they concluded that the predictive accuracy of most learners didn't differ 
-significantly in terms of the area under the receiver operating characteristics curve(AUC). 
-Furthermore, according to the fig.2 in \cite{lessmann2008benchmarking}, Random Forest is 
-significantly better than CART. Lessmann's paper motivates us to investigate whether tuning 
-those CART's parameters by search-based software engineering method can improve the 
-performance. Even though Lessmann considered unpruned tree and pruned tree, They didn't 
-consider other possible parameters in CART which would have impact on the structure of 
-trees, like the depth of the tree, the maximum and minimum number of leafs of the tree.
-
-Software metrics are the core of all the defective prediction model. Many types of metics
-are used to build models, like process metrics, McCabe and Halsted metrics  and CK metrics.
-By building prediction modes across 85 releases of 12 open source projects, Rahman et al
-\cite{rahman2013how}  concluded that code metrics are generally less useful than process
-metrics for prediction. And also the code metrics don't change much from release to release
-and lead to stagnation in the prediction model. In \cite{Radjenovi?20131397}, Radjenovi? et al
-\cite{Radjenovi?20131397} reviewed 106 papers regarding software prediction metrics. They found
-that CK objected-oriented and process metrics have been reported to be more successful in
-finding defects compared to traditional size and complexity metrics. Moreover, not all the CK
-metrics perform well equally. The best metrics from CK are CBO, WMC and RFC based on their 
-observation. It seems that the relationship between software metrics and defective prediction is
-still an open question and need to be addressed. This motivates us to see : whether the impact
-rankings of those metrics will change after tuning parameters
-is applied to model learners.
-
-What's the problem in those result?
-
-RQ:
-
-briefly describe our study and  our result; observation
-
-structure of this paper.
-
-Note that we do not claim that differntial evolution is the {\em best} way to
-optimize data miners for defect prediction. In this paper, we only show that
-differential evolution is {\em simple}, {\em fast} and {\em effective} at that task. As to   finding the best optimizer for defect prediction, that task would require
-the input of many researchers (and we hope this paper inspires
-much subsequent work into that issue).
-
-\subsection{Implications}
-
-time for an end to era of data mining in se? moving on to a new phase of learning-as-optimization
-
-1) learning is actually an optimization tasks (e.g. see fig2 of  learners climbing the roc curve hill in http://goo.gl/x2EaAm)
-
-2) our learners are all contorted to do some tasks X (e.g.
-minimize expected value of entropy), then we assess them on score Y (recall).
-which is nuts.
-maybe we should build the goal predicate into the learner (e.g http://menzies.us/pdf/10which.pdf)
-
-3) given 1 + 2, maybe the whole paradigm of optimizing param selection is wrong.
-maybe what we need is a library of bees buzzing around making random choices (e.g.
-about descritziation) which other bees use, plus their own random choices (e.g.
-max depth of tree learned from discretized data) which is used by other bees, plus their own random choices (e.g.
-business users reading the models).
-the funky thing here is that it can take some time before some of the bees (the discretizers) get feedback from the community of people using their decision (the tree learners).
-
-\section{Algorithm: Predictor and Tuner}
-
-In order to conduct the experiment of this paper, we need one tool that can predict defects 
-from the empirical data sets and a second tool to tune the built-in parameters associated with 
-predictor. To compare the effects of the tuning process, we have three different predictors: 
-WHERE-based Predictor, CART and Random Forest. Different Evolution(DE) as an optimizer 
-is used as a tuner in this paper.
-
-We choose CART and Random Forest as a predictor in this paper is motivated by 
-\cite{lessmann2008benchmarking}, where the performance of both tools as predictors are 
-significantly different based on authors' experiment as mentioned before. We'd like to 
-investigate whether tuning can change such conclusion. WHERE-based Predictor is a new 
-defect predictor based on WHERE\cite{menzies2013local} algorithm. A comparison with 
-standard predictor like CART and Random Forest will better evaluate and judge the 
-performance such new predictor. As for the tuner, there're many heuristic optimization 
-algorithms in wild. However, DE is a good but maybe not the best candidate for the tuning 
-process considering different performance measurements. To determine which optimizer is 
-fitable and results in better performance is beyond this work scope. We leave it to future 
-works. The rest of this section will describe each tool applied in this work.
-
- \subsection{WHERE-based Learner}
-\textbf{WHERE-based Learner} is composed of WHERE clustering algorithm and CART 
-decision tree algorithm. The key idea of WHERE-based learner is that  instead of training the 
-CART decision tree based on the class labels associated with each training sample, it's using 
-CART to build decision trees based on the cluster labels, which are generated by the WHERE 
-clustering algorithm.
-
-\begin{figure}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
-    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
-    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
-pd&71.4&1.2&60&4.4&0.1&44&7.1&0.2&36\\ 
-prec&82.8&1.4&59&3.9&0.1&39&7.4&0.2&37\\
-f&86.1&1.2&72&3.3&0.1&33&6.7&0.2&34
-  \end{tabular}
-  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
-  for different goals, or just running the ``off-the-shelf'' learner.}
-\end{figure}
-
-\begin{figure}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-\begin{tabular}{r|rrr}
-goal &	WHERE	&CART&	Random Forest\\\hline
-f	&15	&13	&9\\ 
-pd	&15	&16	&8\\ 
-prec&	14	&14	&8
-\end{tabular}
-\caption{How much slower is tuning vs just running the default
-settings of the learner? E.g. bottom right, tuning to increase
-precision with Random Forests is eight times slower than
-just running Random Forests.}
-\end{figure}
-
-% Given N instances, instead of building decision tree directly with CART, we use WHERE to 
-%cluster instances. 
-WHERE is a fast clustering algorithm designed by {\it menzies} for finding software artifacts 
-with similar attributes. It clusters data on dimensions synthesized along the axis of greatest 
-variability in the data. The way WHERE used to find such dimension is a linear-time heuristic 
-called ``FASTMAP" proposed by Faloutsos \& Lin\cite{faloutsos1995fastmap}. ``FASTMAP" 
-randomly picks one instance $Z$; find the instance {\it east} $X$ that's furthest away form $Z$; find 
-the instance {\it west} $Y$ that's furthest away from {\it east} $X$. Next, project all the remaining 
-points onto the line drawn between $X$ and $Y$.  The line $\overline{XY}$ is an approximation of the 
-first component found by PCA.
-As shown in Figure \ref{Where}, $X$ and $Y$ are the furthest points found by ``FASTMAP'' and $\overline{XY}$ is of length $c$.
-Each point in this figure has a distance $a$
-to $X$ and distance $b$ to $Y$. According to the coisne rule and Pythagoras, each instance will be mapped 
-into 2-dimension by the following equations.
-\begin{equation}
-	\begin{split}
-			x  &= (a^2 +c^2-b^2)/(2c)\\ 
-		    y  &= \sqrt{a^2 -x^2}
-	\end{split}
-\end{equation}
-
-Then choose the median point $\hat{x}$ as the split and 
-recursively divide all the instances into {\it west} and {\it east} clusters until the number of 
-instances within each cluster is less than specific minimum size. The representation of the 
-clustering result is a tree, we call it Where-clustering tree. Such tree will be pruned if applicable 
-in some cases. Finally, cluster labels  will be assigned to instances in each of those 
-clusters(leaves).
-
-\begin{figure}[!ht]
-\includegraphics[scale=0.5]{where.png}
-\caption{WHERE algoirthm }
-\label{Where}
-\end{figure}
-Then based on the attributes and the cluster labels in each instances,  we build a 
-decision tree based on CART algorithm. In each leaf of the tree, there're several instances 
-falling in. This will be the model trained for defect prediction. During testing process, a new 
-instance comes in and traverses the tree according to 
-values of the its attributes. If the instance could reach one leaf of the tree, the predicted value 
-of this instance will be the mean  of all the training data values associated with this leaf. 
-Otherwise if stops at intermediate nodes of tree, the predicted value will be the mean of the all 
-the training data value below this node. After estimating all the number of defectives in the test 
-data, whether each instance contains defectives will be determined by comparing with a threshold value.
-If the predicted value is greater than threshold, the Where-based learner will predict this instance as defective otherwise non-defective.
-
-%\begin{algorithm}
-%	\caption{Pesudocode for WHERE Algorithm }
-%	\label{alg:WHERE}
-%		\begin{algorithmic}[1]
-%			\Require $data$
-%			\Ensure $tree$
-%		\Function {Fastmap}{$ data$}
-%			\State $one \gets$ any$(data)$
-%			\State $west \gets$ furthest$(data, one)$
-%			\State $east \gets$ furthest$(data, west)$
-%			\State $c \gets$ distance($west, east$)
-%		\EndFunction
-%	 \end{algorithmic}            
-%\end{algorithm}
-
-\subsection{CART}
-\textbf{CART} is an {\em iterative dichotomization} algorithm
-that finds the attribute that most divides the data such that
-the variance of the goal variable in each division is
-minimized\cite{breiman84}.
-The algorithm then recurses on each division.
-Finally, the cost data in the leaf divisions
-is averaged to generate the estimate.
-
-\subsection{Random Forests}
-
-Breiman's website describes \textbf{Random Forests} as
-follows\cite{brieman00}. "Random Forests grows many classification
-trees. To classify a new object from an input vector, put the input
-vector down each of the trees in the forest. Each tree gives a
-classification, and we say the tree "votes" for that class. The forest
-chooses the classification having the most votes (over all the trees
-in the forest). Each tree is grown as follows.
-If the number of cases in the training set is N, sample N cases at
-random - but with replacement, from the original data. This sample
-will be the training set for growing the tree.
-Also, if there are M input variables, a number m$<<$M is specified such
-that at each node, m variables are selected at random out of the M and
-the best split on these m is used to split the node. The value of m is
-held constant during the forest growing.
-Finally, each tree is grown to the largest extent possible (there is
-no pruning)."
-
-%Suppose the cordinates of X and Y are $(0,0)$ and $(0,c)$, which are east and west 
-%instances within N samples. From the Pythegoras and cosine rule, each instance is projected 
-%at the point(x,y)
-%
-%\begin{equation}
-%	\begin{split}
-%	x &= (a^2 + c^2 - b^2)/(2c) \\
-%	y &= \sqrt{a^2 - x^2} 
-%	\end{split}
-%\end{equation}
+\subsection{Data Mining}
+Static code defect prediction applies data miners to build its predictors. How does data mining work?
+
+\input{learners}
 
@@
 \end{document}
+
+O 
+PEEKING2's PCA tool used an accelerated   principle component analysis that synthesises  new
+attributes $e_i, e_2,...$
+that extends across the dimension of greatest  variance in the data  with attributes $d$.  
+PCA  combines
+redundant  variables into a smaller set of variables  (so $e \ll d$) since those
+redundancies become (approximately) parallel lines
+in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
+can ignore $j$ 
+since effects that change over $j$ also
+change in the same way over $i$.
+PCA is also useful for skipping over noisy variables from $d$-- these
+variables are effectively ignored since    they  do not contribute to the variance in the data.
+
+In the case of WHERE, this reduction incluFor CART, the measure of compression is
+
+XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores.
+Given that, the next question becomes ``what performance scores do you want?''.
+This is an interesting issue since there is no single best answer.
+XXX
+
+How ``true'' are the  models generated by software analytics?
+Suppose we use a model generated from software project data to, for example,
+assess the relative value of OO metrics vs procedural metrics for predicting
+project defects. Are we reporting ``truth'' in any sense of the word? And for how
+many other projects  and how many kinds of questions might we find that same ``truth''?
+
+This is not some abstract question-- it is an open and pressing matter.
+Any reading of the recent proceedings of FSE, ICSE, ASE, etc will discover hundreds
+of papers using data miners to make conclusions about software projects. 
+For example, some  analysts have made conclusions
+about 
+{\em what attributes
+have most influence on a software project}.
+For example, in 2013,
+Rahman et al
+\cite{rahman2013how}  used results from logistic regression to conclude
+that code metrics are generally less useful than process
+metrics for  predicting defects from static code analysis.  
+In the same year, Bell et al. (who also used negative binomial regression) argued that
+software defect prediction was not improved by adding attributes relating to the social
+structure of programmer teams~\cite{bell2013limited}.
+
+@article{bell2013limited,
+  title={The limited impact of individual developer data on software defect prediction},
+  author={Bell, Robert M and Ostrand, Thomas J and Weyuker, Elaine J},
+  journal={Empirical Software Engineering},
+  volume={18},
+  number={3},
+  pages={478--505},
+  year={2013},
+  publisher={Springer}
+}
+
+The results of this paper offer a very different picture  to recent prominent results from prior authors.
+Lessmann et al.~\cite{lessmann2008benchmarking}, Rahman et al.~\cite{rahman2013how} and Arshiholm et al.~\cite{arisholm06} argue that when it comes to defect prediction, different learners often
+produce statistically similar results. For this reason  Rahman et al. only present results their logistic
+regression results, commenting that ``dor brevity, only results from LR are
+presented; other learning models give similar results''~\cite{rahman2013how}. Note that those prior results,
+where most learners achieved the same results, arose from the default parameter settings from those learners.
+
+Our results, on the other hand, come from tuning a data miner's parameters. In those results,
+we found that the choice of parameters had dramatic impacts on data mining performance.
+For example, we show results below where:   
+\bi 
+\item 
+Tuning improved precision values from  2\% to 98\%; or
+\item 
+Tuning improved false alarm values from 69\% to 0\%; or
+\item 
+Tuning improved recall values from 0 to 100\%; or
+\item 
+Tuning improved the f-measure (which is the harmonic mean of recall and precision) from 0 to 86\%.
+\ei   
+In terms of changing SE research methodologies, an important aspect of these results is that usually XXXX always different.
+cannot determine without experimentation which learner will, after tuning, yield the best results for a particular data set.
+Hence it is no longer viable for researchers to trust the recommendations
+of other researchers working with other data sets that ``data miner XYZ is best''. Before
+offering a conclusion about a particular data set, researchers need now augment  their 
+papers with preliminary tuning studies (the results of which select the tunings+data miners to be used
+to make conclusions for the second half of their paper).
+
+The good news is that such tuning is not an arduous task. The differential evolution algorithm 
+used in this study is wdiely available in many standard  toolkits and languages\footnote{See the long list at
+www1.icsi.berkeley.edu/~storn/code.html.}
+And even if somehow those tools and prior implementations are not workable at a local site, 
+differential evolution is very simple to code. Hence, it can readily and quickly implemented.
+
+When we discuss these results with colleagues, one response we get is ``enough of the parameter tuning.. lets use simpler methods''. 
+While we understand their motivation (to keep thing simple), software project
+data cannot necessarily be condensed to (say) a simple univariate analysis that
+reports how one independent variable effects a dependent variable.
+Such a simplistic analysis can miss significant interaction
+effects when multiple factors combine to effect the target variable. For example,
+one of the base results in defect prediction is that predictors formed from
+a single variable perform much worse than those can combined multiple variables (three or more)~\cite{me07b}.
+
+If those results come from an analysis of a complex interactions between attributes,
+then some kind of data mining method\footnote{By this term we mean the
+full gamut of methods for large-scale analysis of
+data including statistical
+parametric methods (that assume a particular distribution then strive to learn the parameters of that distribution); kernel methods;
+dimensionality  synthesis methods; 
+instance weighting schemes; feature subset selection methods
+outlier removal methods;
+decision tree learners; neural networks; and instance-based
+methods including clustering and/or   case-based reasoning.} then there is the
+{\em tuning problem} of how to set the myriad of parameters that 
+control the learner.
+
+\item
+What data miners are better than others for particular tasks
+in software analytics. 
+\ei
+
+Also, in 2007, one of us (Menzies) claimed that Naive Bayes
+classifiers with a certain lind of pre-processor were better than entropy-based decision trees for defect prediction~\cite{me07b}.
+Similarly, in 2008 Lessmann et al.~\cite{lessmann2008benchmarking} argued  that 
+Random Forests~\cite{brieman00} and CART ~\cite{brieman84} work best, worst for learning software defect predictors from
+static code attributes. Similar claims that one learner was better than another
+have been made by many other authors; e.g.
+
+We write to suggest that all those conclusions may be wrong or, at the very most,
+correct within a very limited context. At the very least, the conclusions
+of those papers (and literally dozens of similar papers, include severl
+of our own~\cite{me02e,me02k,me03a,me06d,me07b}) need to be revisited
+in light of this paper's results on the effects of tuning on data miners.
+
+Machine learners
+are controlled by parameters that decide (e.g.) when to stop recursively
+dividing data into smaller section or (e.g.) what thresholds for errors are small
+enough to be acceptable. When used ``off-the-shelf'', analytst
+use default settings for those parameters. We find that  a 
+simple optimization scheme (differential evolution) can find much
+better tunings that can dramatically change the performance of
+the learned model (measured in terms of false alarm rates, recall,
+precision, f-measure, and g-measure).  From this first result,
+we conclude that {\bf parameter tuning with some optimizer such as differential
+evolution should become standard practice}.
+
+Our next observation is that observations about miner1 being better
+than miner2 do not survive tuning. To be specific: given some
+ranking of data miners for some task such as defect prediction,
+we find that tuning can reverse those rankings such that the worst untu
+
+Tuning the data miners with different evolution takes some
+times (around an order of magnitude slower than the learning), but not an impractically slower amount of time. Further, when we look at what
+attrub
+
+Our reading of the
+
+good news:
+\bi 
+\item Tuning is easy (but one measure, at least an order of magnitude easier than 
+standard optimization problems)
+\item Tuning can dramatically improve the performance of a learner (in one case, from recalls
+of zero to 70\%)
+\ei
+interesting news
+\bi 
+\item tunings different for different data sets.
+\ei 
+bad news:
+\bi
+\item Tuning also changes what was learned
+\bi
+\item Supposedly ``bad'' learners start working much better than supposedly ``best'' learners;
+\item The models used in the tuned models were very different to those used in the untuned learners.
+\ei 
+\ei 
+and we reflect on that model, are we
+
+will it reveal the `1`t
+A standard approach to software analutics
+Software has becoming a large and complex system and delivering reliable and quality 
+software is imperative for development teams. Empirical study shows that the longer the 
+defects exist in software systems, the more the cost of time and money it will take to fix it 
+\textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
+defects in their system as early as possible. Defect prediction has been investigated 
+extensively in industrial and academia during the past two decades. As an important research 
+field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, 
+menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} 
+over static code features of software system has been demonstrated to be a way to predict 
+which models are more likely to contain defects.
+
+Classification is an important approach to predict whether some modules in the projects are 
+defective or non-defective. The general idea is to train the learners by using parts of data 
+sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with 
+remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed 
+based an different data mining classifiers, including CART, Random Forest 
+\cite{guo2004robust},  Naive Bayes\cite{menzies2007data},Logistic Regression 
+\cite{khoshgoftaar1999logistic}. During the past years, authors claimed that their new 
+defective learner outperformed others according to their experiment and statistical analysis. 
+To evalute those learners objectively in terms of accuracy, Lessmann et al
+\cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
+\begin{figure}
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+When applying case-based reasoning, researchers use different settings including how they measure dis- tance between instances (examples include the Euclidean measure, Manhattan and Chebyshev).
+Other settings control if numerics are normalized min..max to 0..1, before they are used in the distance measure.
+
+Another set of settings refers to how to handle non-numeric distances or missing values.
+Some researchers delete training data with missing information while others compute missing values via, say, median values.
+
+After feature selection comes instance selection.
+There are many settings for instance selectors such as use outlier removal or prototype generation.
+Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
+The next set of settings concern how many neighbors to use (k=1,2,5,etc).
+Some researchers set ``k'' in dynamic pre-learning phase that checks the training data to find what ``k'' works best for that data.
+
+Once the neighbors are known, the next settings control how to summarize their information.
+Some researchers use means, other use medians, or a weighted sum that uses the distance of the neighbor from the test instance (and that weighting might be determined by some kernel such as uniform, triangular, Gaussian, cosine, or Epanechnikov).
+Researchers may use other settings to control different pre-processors.
+E.g.
+some discretize numeric values (via equal width or equal frequency) using some binning policy (and researchers differ on how many bins are best).\\\hline
+\end{tabular}
+\caption{Some tunings for SE predictive systems.
+Found by this author while preparing this proposal in a day of reading the SE predictive modeling literature on case-based reasoning and effort estimation.
+Note that other kinds of prediction systems (decision trees, neural nets, linear repression, etc) have yet more adjustable design options.}\label{fig:adjust}
+\end{figure}
+
+domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
+with $\alpha = 0.05$, they concluded that the predictive accuracy of most learners didn't differ 
+significantly in terms of the area under the receiver operating characteristics curve(AUC). 
+Furthermore, according to the fig.2 in \cite{lessmann2008benchmarking}, Random Forest is 
+significantly better than CART. Lessmann's paper motivates us to investigate whether tuning 
+those CART's parameters by search-based software engineering method can improve the 
+performance. Even though Lessmann considered unpruned tree and pruned tree, They didn't 
+consider other possible parameters in CART which would have impact on the structure of 
+trees, like the depth of the tree, the maximum and minimum number of leafs of the tree.
+
+Software metrics are the core of all the defective prediction model. Many types of metics
+are used to build models, like process metrics, McCabe and Halsted metrics  and CK metrics.
+By building prediction modes across 85 releases of 12 open source projects, Rahman et al
+\cite{rahman2013how}  concluded that code metrics are generally less useful than process
+metrics for prediction. And also the code metrics don't change much from release to release
+and lead to stagnation in the prediction model. In \cite{Radjenovi?20131397}, Radjenovi? et al
+\cite{Radjenovi?20131397} reviewed 106 papers regarding software prediction metrics. They found
+that CK objected-oriented and process metrics have been reported to be more successful in
+finding defects compared to traditional size and complexity metrics. Moreover, not all the CK
+metrics perform well equally. The best metrics from CK are CBO, WMC and RFC based on their 
+observation. It seems that the relationship between software metrics and defective prediction is
+still an open question and need to be addressed. This motivates us to see : whether the impact
+rankings of those metrics will change after tuning parameters
+is applied to model learners.
+
+What's the problem in those result?
+
+RQ:
+
+briefly describe our study and  our result; observation
+
+structure of this paper.
+
+Note that we do not claim that differntial evolution is the {\em best} way to
+optimize data miners for defect prediction. In this paper, we only show that
+differential evolution is {\em simple}, {\em fast} and {\em effective} at that task. As to   finding the best optimizer for defect prediction, that task would require
+the input of many researchers (and we hope this paper inspires
+much subsequent work into that issue).
+
+\subsection{Implications}
+
+time for an end to era of data mining in se? moving on to a new phase of learning-as-optimization
+
+1) learning is actually an optimization tasks (e.g. see fig2 of  learners climbing the roc curve hill in http://goo.gl/x2EaAm)
+
+2) our learners are all contorted to do some tasks X (e.g.
+minimize expected value of entropy), then we assess them on score Y (recall).
+which is nuts.
+maybe we should build the goal predicate into the learner (e.g http://menzies.us/pdf/10which.pdf)
+
+3) given 1 + 2, maybe the whole paradigm of optimizing param selection is wrong.
+maybe what we need is a library of bees buzzing around making random choices (e.g.
+about descritziation) which other bees use, plus their own random choices (e.g.
+max depth of tree learned from discretized data) which is used by other bees, plus their own random choices (e.g.
+business users reading the models).
+the funky thing here is that it can take some time before some of the bees (the discretizers) get feedback from the community of people using their decision (the tree learners).

### 2015-03-11 dm101.tex
Updates from ShareLaTeX

@@
 moving $C$ from  
-90\% to 98\% nearly doubles the number of required tests (2301 to   3910 black box
+90\% to 98\% nearly doubles the number of  tests (2301 to   3910 black box
 probes, respectively)\footnote{A randomly selected 

### 2015-03-11 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \usepackage{graphics}
+\usepackage{cite}
 \usepackage{rotating}
@@
 \conferenceinfo{FSE}{'15 Bergamo, Italy}
-\title{Implications of Differential Evolution for  Defect Prediction:
+\title{ 
 Analytics Without Parameter Tuning Considered Harmful?}
@@
        \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
-       {wfu@ncsu.edu, tim.menzies@gmail.com, vivekaxl@gmail.com}}
+       fuwei.ee, tim.menzies, vivekaxl@gmail.com}
 
@@
 \noindent
-{\bf General Terms:} Experimentation, Algorithm
-
-\vspace{1mm}
-\noindent
 {\bf Keywords:} defect prediction, CART, random forests,
@@
 %\end{raggedleft}
+
+In the $21^{st}$ century, it is now impossible
+to manually browse all the available software project
+data. The PROMISE repository of SE data has grown to 200+ projects~\cite{promise15}
+and this is just one of over a dozen open-source repositories
+that are readily available to researchers~\cite{rod12}.
+For example,  the time of this writing (Feb  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub hosts over 14 million projects.
+
+Faced with this information overload,
+researchers in empirical SE
+use  data miners  to (e.g.) generate 
+defect predictors from static code measures.
+Such   measures can be
+automatically extracted from the code base, with very little effort
+even for very large software systems~\cite{nagappan05}. 
+In addition, they have  some generality
+across multiple projects: e.g. defect
+predictors developed at NASA~\cite{me07b} have also been successfully
+applied in Turkey~\cite{tosun09}.
+Such detectors reduce the effort required for 
+defect prediction: if 
+inspection teams let themselves be guided by defect predictors then
+they can find 80\% to 88\% of the defects
+after inspecting  20\% to 25\% of the code~\cite{ostrand04,tosun10}.
 
@@
 
-Many researchers have applied automatic optimizers to find good tunings.
+Many researchers have applied automatic optimizers to find good tunings~\cite{cora10}  but not in the arean
+of adjusting the parameters of data miners learning
+static code defect predictors.
+(to the best of our knowledge, this is the first such study).
 This paper shows that for at least one software analytics problem
 (software defect prediction from static code attributes),   a
-very simple optimizer called differential evolution needs only   seconds
-to just  few minutes to find good tunings.
-
-These results   challenge much prior work into defect prediction:
-Numerous   prominent papers have claimed 
-that learnerX is better than learnerY for some software analytics task~\cite{lessmann2008benchmarking,hall11,me07b}.
+very simple optimizer called 
+{\em differential evolution} can  find good tunings.
+
+The good news here is that that tuning defect predictors is very easy. Differential
+evolution is so simple to implement that many
+researchers just ``roll their own'' rather
+than relying on some standard package.
+By various measures
+(presented below),  
+tuning defect predictors is at least an order of magnitude
+simpler than other standard optimization tasks. 
+Further, measured in terms on runtimes, 
+differental evolution takes just seconds
+to a few minutes to propose highy effective tunings.
+
+The not-so-good-news is that these results   challenge much prior work into defect prediction.
+Several   prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
+that learnerX is better than learnerY for some software analytics task~.
 For example, a recent IEEE TSE article claimed that the 
@@
 Another class of conclusions challenged by this paper are research papers
-that use data miners to   show that different attributes are ``best'' for different
-data sets and even different goals for the tunings. Hence, it is no longer
-supportable to use data mining to argue that certain kinds of attributes 
-are better than others; e.g. as  done by~\cite{rahman2013how}. 
-For example, in 2013,
+that use data miners to   show that certain factors
+are more important than others for (say)
+predicting defects. We show in this paper
+that cuch conclusions
+do not survive tuning. It turns out the after tuning,
+different data sets show  that very different 
+factors are ``best''. Also, even within the same data set, if we adjust the goals of the tuning then we arrive at different ``best'' factors.
+
+Given this locality effect in what is ``best'',
+then there are many   papers that may
+need to be rewritten.
+For example, one of us (Menzies) used data miners
+to assert that some factors were more important than others for predicting
+successful software reuse~\cite{me02k}. That assertion should now be doubted.
+
+Similarly,   we should now revisit
+all other conclusions that used data miners to rank different factors including:
+\bi
+\item
+Bell et al.~\cite{bell2013limited} who say that
+software defect prediction is not improved by adding attributes relating to the social
+structure of programmer teams;
+\item
 Rahman et al
-\cite{rahman2013how}  used results from logistic regression to conclude
-that code metrics are generally less useful than process
-metrics for  predicting defects from static code analysis.  
-In the same year, Bell et al. (who also used negative binomial regression) argued that
-software defect prediction was not improved by adding attributes relating to the social
-structure of programmer teams~\cite{bell2013limited}.
-
-Given the simplicity and effectiveness of differential evolution,
-and also given the effects this method has on defect prediction, this
-paper  motivates  a change to the entire field of software analytics.
+\cite{rahman2013how}  who say
+ code metrics are  less useful than process
+metrics for  predicting defects from static code analysis; 
+\item Mosser et al.~\cite{moser2008comparative} who also say  that process metrics are better. 
+\ei
+There are many other examples of researchers
+using data mining to claim that certain
+factors are more important than others; e.g. ~\cite{zimmermann2007predicting,herzig2013predicting}.
+All those results must  now be called into question.
 At least for softwre defect prediction,
-it is no longer enough to just run a data miner and present the result
+since is no longer enough to just run a data miner and present the result
 {\em without} first conducting an tuning optimizations study.
@@
 While this paper reports success with tuning defect predictors,
-we were not so successful with
-other analytics tasks (software development effort estimation).
-Hence, we assert that it is now an open and pressing research question is whether or not  
-tuning studies are now   required for research reports on software analytics.
+there are many of software analytics tasks 
+(software development effort estimation, social network mining,
+detecting duplicate issue reports, etc).
+Since those other tasks often use the same kinds of learners
+explored in this paper, it is clearly possible that
+the conclusions of this paper apply to other tasks as well. 
+Hence, we assert that it is now an open and pressing research question if
+``analytics without parameter tuning is considered harmful?''.
+Note that if the answer is ``yes'' then:
+conferences like FSE
+should routinely reject software analytics papers that do not
+have a tuning study.
+
+The rest of this paper is structured as follows.
+
+One caveat before beginning- this paper explores
+optimization via differential evolution.
+XXX
 

### 2015-03-12 learners.tex
Updates from ShareLaTeX

@@
 without generalization, all we can do is perform exact matches
-of new situations to a database of old examples. This is not recommended practice since,
+of new situations against  a database of old examples. This is not recommended practice since,
  if the new situation has not occurred  before, then nothing in the data  will
@@
 
-The key point here is that there are many ways to summarize data and exceConsider some learner that
+The key point here is that, at least is software engineering,
+the raw data contains noise and superflous details (e.g. highly correleated attributes
+or repeated/very similar rows). Recent results show
+
+are many ways to summarize data.  A repeated result is
+that a table of data with R rows and C columns can be reduced to around Consider some learner that
 builds predictive rules form a subset of  attributes $A$ ranges. Assuming numeric attributes

### 2015-03-12 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \begin{abstract}
-When learning
-software defect predictors,   a
-very simple optimizer called differential evolution needs can quickly
-find  good tunings for that learner.
-Such tunings can have a dramatic change to the performance of a learner;
-e.g. in this paper we show that tuning can alter the precision of
-a software defect predictor from 2\% to 98\%.
+One of the ``black arts'' of data mining is setting the tuning
+parameters that control   choices within a data miner.  We offer a simple,
+automatic, and very effective  method for finding those tunings.
+
+For the purposes of learning
+software defect predictors this optimization strategy can quickly
+find  good tunings that  dramatically change   the performance of a learner.
+For example,
+in this paper we show   tunings that  alter deection  precision  
+ from 2\% to 98\%.
 
@@
 parameters that control  the choices within that data miner.
-Such tunings can have a dramatic change to the performance of a learner;
-e.g. in this paper we show that tuning can alter the precision of
-a software defect predictor from 2\% to 98\%.
-
-Many researchers have applied automatic optimizers to find good tunings~\cite{cora10}  but not in the arean
-of adjusting the parameters of data miners learning
-static code defect predictors.
-(to the best of our knowledge, this is the first such study).
-This paper shows that for at least one software analytics problem
+Many researchers have applied automatic optimizers to find good tunings.
+For example, 
+the search-based SE community has   developed techniques
+for tuning that treating parameters  as a configuration
+search space~\cite{cora10,Krogmann10}. More generally,
+the field of {\em hyper-heuristics} explores methods for auto-adapting
+options within the device searching for solutions~\cite{jia2013learning}.
+
+To the best of our knowledge, this paper is the first exploration in software engineering
+of applying automatic optimizers to the task of tuning data miners for defect prediction
+(though see~\cite{cora10,balogh12} for work on effort estiamtion and genetic optimizers).
+We shows that for at least one software analytics problem
 (software defect prediction from static code attributes),   a
@@
 
-The good news here is that that tuning defect predictors is very easy. Differential
+The good news here is that  tuning defect predictors is very easy and very effective. 
+Differential
 evolution is so simple to implement that many
@@
 simpler than other standard optimization tasks. 
-Further, measured in terms on runtimes, 
-differental evolution takes just seconds
-to a few minutes to propose highy effective tunings.
+Also, measured in terms on runtimes, 
+differental evolution takes  seconds
+to a just few minutes to propose highy effective tunings.
+Further, the tunings found by differential evolution
+can have a dramatic change to the performance of a learner;
+e.g. in this paper we show that tuning can alter the precision of
+a software defect predictor from 2\% to 98\%.
 
@@
 after tuning, the worst untuned learner (CART) can out-perform the supposedly
-best learner (Random Forests).
+best learner (Random Forests). Hence, all those prior results that ranked learners for software
+analytics now need to be revisited and perhaps revised.
 
@@
 that use data miners to   show that certain factors
-are more important than others for (say)
-predicting defects. We show in this paper
-that cuch conclusions
-do not survive tuning. It turns out the after tuning,
-different data sets show  that very different 
-factors are ``best''. Also, even within the same data set, if we adjust the goals of the tuning then we arrive at different ``best'' factors.
-
-Given this locality effect in what is ``best'',
-then there are many   papers that may
-need to be rewritten.
+are more inflential than others for (say)
+predicting defects. As shown below, such conclusions can be dramatically
+changed by the tuning process since those  ``influential'' factors are very different pre- and post- tuning. Also, those factors tend to  change from project to project or if the goal
+of the tuning is altered.
+Hence, many old papers    need to be revisted  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
 For example, one of us (Menzies) used data miners
 to assert that some factors were more important than others for predicting
-successful software reuse~\cite{me02k}. That assertion should now be doubted.
-
-Similarly,   we should now revisit
-all other conclusions that used data miners to rank different factors including:
-\bi
-\item
-Bell et al.~\cite{bell2013limited} who say that
-software defect prediction is not improved by adding attributes relating to the social
-structure of programmer teams;
-\item
-Rahman et al
-\cite{rahman2013how}  who say
- code metrics are  less useful than process
-metrics for  predicting defects from static code analysis; 
-\item Mosser et al.~\cite{moser2008comparative} who also say  that process metrics are better. 
-\ei
-There are many other examples of researchers
-using data mining to claim that certain
-factors are more important than others; e.g. ~\cite{zimmermann2007predicting,herzig2013predicting}.
-All those results must  now be called into question.
-At least for softwre defect prediction,
-since is no longer enough to just run a data miner and present the result
+successful software reuse~\cite{me02k}. That assertion should now be doubted since that
+Menzies study did conduct a tuning study before reporting what factors the data miners
+found where most influential.
+
+In summary,it is now an open and pressing research issue to check if
+analytics without parameter tuning is considered {\em harmful} or, at the 
+very least, {\em misleading}.
+At least for defect prediction,
+it is no longer enough to just run a data miner and present the result
 {\em without} first conducting an tuning optimizations study.
-
-The implications for other kinds of data mining tasks is unclear.
-While this paper reports success with tuning defect predictors,
-there are many of software analytics tasks 
+There are many other kinds of software analytics tasks 
 (software development effort estimation, social network mining,
-detecting duplicate issue reports, etc).
-Since those other tasks often use the same kinds of learners
-explored in this paper, it is clearly possible that
-the conclusions of this paper apply to other tasks as well. 
-Hence, we assert that it is now an open and pressing research question if
-``analytics without parameter tuning is considered harmful?''.
-Note that if the answer is ``yes'' then:
-conferences like FSE
-should routinely reject software analytics papers that do not
-have a tuning study.
+detecting duplicate issue reports, etc) and the implication of this
+study for those tasks is unclear. 
+However,  those other tasks often use the same kinds of learners
+explored in this paper so it is clearly possible that
+the conclusions of this paper apply to other SE analytics tasks as well.
 
@@
 
+Two caveats before beginning. Firstly, we are {\em not} saying that {\em all learning requires
+tuning}. For example, when proposing fixes to software, Weimar et al. use a genetic learner
+to propose patches~\cite{Weimer:2009}. Suppose  the performance criteria for that work is how many known bugs can be found
+and fixed automatically. Note that there is no {\em better than} in that performance criteria so
+that study does not need tuning. However, once {\em better than} enters the performance criteria
+then this becomes a race between competing methods or attributes.  In such a race, it is unfair
+to hobble one competitor with poor tunings. Hence, we recommend tuning for  all the data mining
+studies mentioned above\cite{lessmann2008benchmarking,hall11,me07b,bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting} since
+they are arguing that one learner or one set of attributes
+is {\em better than} another.
+
+Secondly,
 One caveat before beginning- this paper explores

### 2015-03-13 learners.tex
Updates from ShareLaTeX

--- 2015-03-11 learners.tex
@@
-Dta miners find generalizations (a.k.a. summaries)
-of the data. All such generalizations must be smaller than the data it generalizes (otherwise we might as well just keep the original data and ignore the generalization)\footnote{Technical note:
-even instance-based reasoners uses generalizations when they partially match new cases to old;
-or if they use some  clustering algorithm to restrict the case matching
+This section describes the learners used in this study. While there are many differences
+in those learners, they have the same goal: to summarize a large data set into a small model\footnote{Technical note: proponents of instance-based reasoning might argue that
+their goal is to retain, and not summarize, the training data.
+However, 
+even instance-based reasoners use some degree of summarizing when they learn
+ways to bias the instance matching away from irrelevant training data.
+Those bias tools include  generalizing points to ranges (to allow for partial matches)
+or  clustering algorithm that restrict the case matching
 to just the subset of old cases most similar  to new  cases.}.
-Generalization is important since,
-without generalization, all we can do is perform exact matches
-of new situations to a database of old examples. This is not recommended practice since,
- if the new situation has not occurred  before, then nothing in the data  will
- matches the new situation
-(and we cannot make any predictions).
 
-The key point here is that there are many ways to summarize data and exceConsider some learner that
-builds predictive rules form a subset of  attributes $A$ ranges. Assuming numeric attributes
-divided into five ranges, then the 20 attributes of \fig{ck} can be combined into 
-$2^{5*20}> 10^{30}$
-possible rules
+For example,
+consider some learner that
+builds predictive rules from a subset of  attributes $A$ ranges. Assuming numeric attributes
+divided into $d=5$ divisions, then the 20 attributes of \fig{ck} can be combined into 
+$2^{A*d} = 2^{5*20} > 10^{30}$
+possible rules. The key thing to note here is that many of these rules will have similar effects
+since, at least in software engineering, data sets containing rows $R$ and columns $C$ can contain much redundancy:
+\bi
+\item When $c \subset C$ columns of data that are correlated to each other, then those
+$c$ columns can be replaced by one column.
+\item When $r \subset R$ rows of data are very similar (e.g. they come from similar projects), 
+then those $r$ rows can be replaced
+by one cluster centroid that stands in $r$.
+\item
+Kocagenunil~\cite{me13a} and Papakroni~\cite{papa13} conduct  different experiments
+to  show  that tables of software defect data in the form of \fig{ck} contain around 90\% redundant
+data. Specifically, they show that such tables can be be pruned back to around
+25\% of the columns and 10\% of the rows without losing the essential information in the data set.
+\ei
+Given this high level of redundancy, learners need only explore a small fraction of these $2^{A*d}$ rules.
+Most learners exploit this fact to optimize their reasoning. Rather than explore all options,
+they employ some {\em search bias} that lets them quickly focus on a small set of promising rules.
+
+Different biases work best for different data sets so it is standard practice to allow an analyst
+to control these biases via tuning parameters. For example, consider the search biases
+$B_i$ of decision tree learner that :
+\bi
+\item Splits the data on some criteria $B_1$;
+\item Assesses each split using some criteria $B_2$;
+\item Selects which split(s) to explore further using $B_3$;
+\item Recurses into each split until some stopping criteria $B_4$ is encountered.
+\ei
+These biases also appear when the learned decision tree makes a decision:
+\bi
+\item To declare a software module to be XXX
+\ei
 

### 2015-03-13 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \conferenceinfo{FSE}{'15 Bergamo, Italy}
-\title{ 
-Analytics Without Parameter Tuning Considered Harmful?}
+\title{ Analytics Without Parameter Tuning Considered Harmful?}
 \numberofauthors{1}
-\author{
-\alignauthor
-Wei Fu, Tim Menzies, Vivek Nair\\
+\author{\alignauthor Wei Fu, Tim Menzies, Vivek Nair\\
        \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
        fuwei.ee, tim.menzies, vivekaxl@gmail.com}
-
 \maketitle
@@
 Many researchers have applied automatic optimizers to find good tunings.
-For example, 
-the search-based SE community has   developed techniques
-for tuning that treating parameters  as a configuration
-search space~\cite{cora10,Krogmann10}. More generally,
-the field of {\em hyper-heuristics} explores methods for auto-adapting
-options within the device searching for solutions~\cite{jia2013learning}.
-
-To the best of our knowledge, this paper is the first exploration in software engineering
-of applying automatic optimizers to the task of tuning data miners for defect prediction
-(though see~\cite{cora10,balogh12} for work on effort estiamtion and genetic optimizers).
-We shows that for at least one software analytics problem
-(software defect prediction from static code attributes),   a
-very simple optimizer called 
-{\em differential evolution} can  find good tunings.
-
-The good news here is that  tuning defect predictors is very easy and very effective. 
-Differential
-evolution is so simple to implement that many
-researchers just ``roll their own'' rather
-than relying on some standard package.
-By various measures
-(presented below),  
-tuning defect predictors is at least an order of magnitude
-simpler than other standard optimization tasks. 
-Also, measured in terms on runtimes, 
-differental evolution takes  seconds
-to a just few minutes to propose highy effective tunings.
-Further, the tunings found by differential evolution
-can have a dramatic change to the performance of a learner;
-e.g. in this paper we show that tuning can alter the precision of
+The search-based SE community has   developed techniques
+for tuning that treat parameters  as a configuration
+search space~\cite{cora10,Krogmann10}. 
+The field of {\em hyper-heuristics} explores methods for auto-adapting
+options within the device searching for solutions~\cite{jia2013learning} in applications
+like test-case generation and code refactorings.
+
+To the best of our knowledge, this paper is the first extensive exploration 
+of applying automatic optimizers to tune data miners for defect prediction,
+(though see~\cite{cora10,balogh12,Minku13,minku13z} for tuning effort estimators).
+The one similar study  we can find in the period 2004 to 2014\footnote{See the GECCO and SSBSE proceedings at    goo.gl/2MY602 and goo.gl/uzvU8e.} was
+Bouktiff et al.~\cite{Bouktif06} who used  simulated annealing to tune Bayes classifiers.
+That was a very limited study, applied to a  single defect data set.
+The analysis of this paper is far more extensive and offers the following novel result:
+\bi
+\item
+Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
+of those learners. 
+\ei
+Prior to these experiments, our expectation was tuning
+would be an  extensive and expensive evolutionary optimization procedure. 
+A standard run of such evolutionary optimizers requires   thousands,
+if not millions, of evaluations.
+To
+our surprise, we achieved dramatic improvements in the performance scores
+of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
+optimizer  called differential evolution~\cite{storn1997differential}.
+Better yet,  those  tunings (found so quickly)   
+  have a dramatic change to the performance of a learner. For example,
+in this paper we show that tuning can alter the precision of
 a software defect predictor from 2\% to 98\%.
 
-The not-so-good-news is that these results  challenge much prior work into defect prediction.
-Several   prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
-that learnerX is better than learnerY for some software analytics task~.
-For example, a recent IEEE TSE article claimed that the 
-CART decision tree learner was far worse than Random Forests for
-softwre defect predition~\cite{lessmann2008benchmarking}. 
-Such conclusions do not survive tuning.
-For example,
-after tuning, the worst untuned learner (CART) can out-perform the supposedly
-best learner (Random Forests). Hence, all those prior results that ranked learners for software
-analytics now need to be revisited and perhaps revised.
-
-Another class of conclusions challenged by this paper are research papers
+Our tuning results  challenge much prior work in software analytics. 
+Firstly, there exist research papers
 that use data miners to   show that certain factors
-are more inflential than others for (say)
+are more influential than others for (say)
 predicting defects. As shown below, such conclusions can be dramatically
@@
 
+Secondly, several   prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
+that learnerX is better than learnerY for some software analytics task~.
+For example, a recent IEEE TSE article claimed that the 
+CART decision tree learner was far worse than Random Forests for
+software defect prediction~\cite{lessmann2008benchmarking}. 
+Such conclusions do not survive tuning.
+For example,
+after tuning, the worst untuned learner (CART) can out-perform the supposedly
+best learner (Random Forests). Hence, all those prior results that ranked learners for software
+analytics now need to be revisited and perhaps revised.
+
+Thirdly, it is standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
+we have defended that approach on methodological grounds arguing that it
+encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
+can no longer be condoned. For example, one such default setting
+  in the Python SciKitLearn toolkit~\cite{scikit-learn}
+is to use $T=10$ decision trees in  Random Forest classifiers.
+Our optimizer settled on  $T$ values that were were nowhere near that default:
+
+{\scriptsize
+\[T \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
+                                108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
+\]}
+
 In summary,it is now an open and pressing research issue to check if
@@
 very least, {\em misleading}.
-At least for defect prediction,
+At the very least, there is now cause to doubt many conclusions based on
+``off-the-shelf'' tunings.
+At the very most, 
 it is no longer enough to just run a data miner and present the result
 {\em without} first conducting an tuning optimizations study.
+
+The rest of this paper is structured as follows.
+
+\section{Preliminaries}
+
+Before beginning, this section offers certain caveats on these results.
+
+Firstly, we are {\em not} saying that {\em all} learning requires
+tuning. For example, when proposing fixes to software, Weimar et al. use a genetic learner
+to propose patches~\cite{Weimer:2009}. Consider one performance criteria for that work; i.e. 
+that   that that method can find and fix known bugs. Note that this is a {\em competency criteria}
+which does not include the phrase  {\em better than}. Such performance criteria do
+not requiring tuning.  However, once {\em better than} enters the performance criteria
+(as done in \cite{lessmann2008benchmarking,hall11,me07b,bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting})
+then this becomes a race between competing methods (or attributes).  In such a race, it is unfair
+to hobble one competitor with poor tunings.
+
+Secondly, the tuning results shown here only came from one particular software analytics task 
+(defect prediction from static code attributes).
 There are many other kinds of software analytics tasks 
@@
 However,  those other tasks often use the same kinds of learners
-explored in this paper so it is clearly possible that
+explored in this paper so it is quite possible that
 the conclusions of this paper apply to other SE analytics tasks as well.
 
-The rest of this paper is structured as follows.
-
-Two caveats before beginning. Firstly, we are {\em not} saying that {\em all learning requires
-tuning}. For example, when proposing fixes to software, Weimar et al. use a genetic learner
-to propose patches~\cite{Weimer:2009}. Suppose  the performance criteria for that work is how many known bugs can be found
-and fixed automatically. Note that there is no {\em better than} in that performance criteria so
-that study does not need tuning. However, once {\em better than} enters the performance criteria
-then this becomes a race between competing methods or attributes.  In such a race, it is unfair
-to hobble one competitor with poor tunings. Hence, we recommend tuning for  all the data mining
-studies mentioned above\cite{lessmann2008benchmarking,hall11,me07b,bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting} since
-they are arguing that one learner or one set of attributes
-is {\em better than} another.
-
-Secondly,
-One caveat before beginning- this paper explores
-optimization via differential evolution.
-XXX
+Thirdly, this paper explores {\em some} learners using {\em one}  optimizer. Hence, it makes
+no claim that this is the {\em best} optimizer for {\em all} learners.
+Rather, our point is that there exists at least some learners
+whose performance can be dramatically improved by 
+at least one simple optimization scheme.  We hope that this work inspires
+much future work as this community develops and debugs best practices for tuning
+software analytics.
+
+Fourthly, it would be incorrect to say that this paper is arguing that
+software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
+In the age of the Internet and global access to software engineering data,
+there exists the  problem of information overload. {\em Something} must be done to
+allow analysts to make conclusions via an automatic analysis over a lot of data.
+The results of this paper is that for a particular local context
+(a specific data set and a specific goal) there exists  
+methods for optimizing the conclusions reached in that context.  Those conclusions
+may not generalize to other contexts but this  is not a council for despair. While there may
+not exist general conclusions, there does seem to exist general methods for finding
+local conclusions in a particular context. Further, as shown below, those
+methods may be very simple to implement and very fast to execute.
 

### 2015-03-13 tuningpredictor.tex
Updates from ShareLaTeX

@@
 
-%\begin{raggedleft}
-%{\em ``The  common misunderstanding about science 
-%%is that scientists seek and find truth. They don't- 
-%they make and test models.''}\\ -- Neil Gershenfeld
-
-%{\em Essentially, all models are wrong, but some are useful."}\\ --George Box
-%%
-%\end{raggedleft}
+\begin{raggedleft}
+{\em ``So those who are last now will be first then, \\
+and those who are first will be last.''}\\ 
+-- Matthew 20:16
+
+ \end{raggedleft}
 
@@
 methods may be very simple to implement and very fast to execute.
+
+\section{Motivating Example}
+
+This section offers a small demonstration
+of the impact of tuning parameters. It also demonstrates that this issue of tuning effects not jist the complex data miners discussed later in the paper but also 
+applies for even very simple  learning schemes.
+
+One way to generate a  defect predictor from
+static code is to use 
+linear  regression.
+This is a standard statistical
+method that fits a straight line to a set of points. The line
+offers a set of predicted values.
+If the points are somewhat
+scattered, then a single regression line cannot pass through all points and the distance from these predicted values to the actual
+values is a measure of the error associated with that line.
+Linear regression search for a line that minimizes that
+error and maximizes the correlation\footnote{
+$Correlation$
+measures how closely two variables co-vary.  It ranges from   from -1
+(perfect negative correlation) through 0 (no correlation) to +1
+ (perfect positive correlation).
+Let  $a_i$ and $p_i$ denote some actual and predicted values respectively; and  $n$ and $\overline{x}$ denote
+ the number of observations and the mean of the $n$ observations, 
+respectively. Then:
+$S_{PA}=\frac{\sum_i (p_i - \overline{p})(a_i -
+  \overline{a})}{n-1}$ and
+$S_{p}=\frac{\sum_i (p_i - \overline{p})^2}{n-1}$
+and 
+$S_{a}=\frac{\sum_i (a_i - \overline{a})^2}{n-1}$ and
+correlation is  $c=\frac{S_{PA}}{\sqrt{S_pS_a}}$.}  denoted as $c$.
+
+Suppose  a researcher wants to use linear regression
+to test if Halstead's~\cite{halstead77} measures
+of   function complexity
+(number of symbols programmers has to understand) are   {\em better than}
+mere lines of code for predicting
+software defects.  That researcher might argue that Halstead's cognitive approach to
+software bugs is better suited to code refactoring tools since it offers 
+more ways to alter functions that just some coarse grained lines of code measure.
+
+That researcher might test that belief by using studying historical
+defect logs with 
+linear regression. Here are two equations (learned from NASA data)
+that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$.
+Note that the Halstead correlations $c_2$
+are worse than those from lines of code $c_1$-- which seems to suggest that
+despite their potential support for refactoring, our researchers should not use Halstead.
+
+{\scriptsize \[\begin{array}{l|l|ll}
+\mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
+\mathit{LOC}   &d_i= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
+\mathid{Halstead & d_2= 0.231 + 0.00344N     \\    
+           & +  0.0009V   - 0.185L \\
+           & - 0.0343D      - 0.00541I \\
+           & + 0.000019E + 0.711B \\ 
+            &   - 0.00047T  & c_2=-0.36 
+            \end{array}
+\end{eqnarray}}
+
+\begin{figure}[!t]
+{\scriptsize
+\begin{tabular}{rl}
+recall   &
+ \includegraphics[width=3.2in]{lsrvscostpd.pdf}\\
+  false alarms:  \includegraphics[width=3.2in]{lsrvscostpf.pdf}\\
+\end{tabular}}
+\caption{
+ probability of false alarm,
+  and
+  probability of recognizing defective modules  seen using \mbox{$d_i \ge T$} for
+  \mbox{$0.1 \le T \le 3$} 
+  Curves calculated from the KC2 dataset from the PROMISE repository goo.gl/pGDfvp
+ }\label{fig:pd1}
+ \end{figure}
+
+Using these equations, a blind-spot sampling policy might be to
+assess some module if $defects_i$ is more than some threshold $X_i$.
+\fig{pd1} shows this for both $defects_1$ (the ``LSR'' curve) and
+$defects_2$ (the ``HALSTEAD'' curve).  Not surprisingly, the detector's
+$PD$ depends on the value selected for $X_i$.  At $X_i=0$ there are no
+blind spots. Every part of the code is assessed so all modules with defects are found and $PD$ is very high.  But as $X_i$ increases fewer
+modules are inspected, so less is found and $PD$ decreases.
+
+ Note that either $defects_1$ or $defects_2$ can reach some desired
+level of $PD$, {\em regardless of their correlations}, merely by
+selecting the appropriate threshold value. For example, PD=75\% using {\em either} $defects_1\ge 0.65$ or $defects_2\ge 0.45$ (see
+\fig{pd1}).
 

### 2015-03-13 learners.tex
Updates from ShareLaTeX

@@
-This section describes the learners used in this study. While there are many differences
-in those learners, they have the same goal: to summarize a large data set into a small model\footnote{Technical note: proponents of instance-based reasoning might argue that
+This section describes the learners used in this study: CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
+and WHERE~\cite{menzies2013local}. The implementations
+for CART and Random Forest comes from 
+SciKitLearn~\cite{scikit-learn}.
+WHERE is available from
+github.com/ai-se/where\footnote{\wei{ need a nice  where repo. with an
+data and code examples sub-directory. clean code. throw out anything not needed. before april1.}}
+
+CART, Random Forest, and WHERE are all  tree learners that divide a data set, then recurses
+on each split.
+All our learners use the following tuning parameters to control that splitting process.
+These learners
+generate numeric predictions which are converted
+into binary ``yes/no'' decisions via \eq{yesno}. Hence, they all use the threshold value $T$ discussed in \tion{eq}.
+Also, if data contains more than {\em min sample split}, then a split is attempted.
+On the other hand, if a split contains no more than {\em min samples leaf}, then recursion stops. For CART and Random Forest use a 
+user-supplied constant for this parameter while
+WHERE computes $m$={\em min samples leaf} from the size of the data
+sets via  $m=\mathit{size}^\mathif{min size}$ (so, for WHERE,
+{\em min size} is the parameter to be tuned).
+
+These learners use different techniques to explore the splits:
+\bi
+\item
+CART finds the attributes whose ranges contain rows with least variance in the number
+of defects\footnote{If an attribute ranges $r_i$ is found in 
+$n_i$ rows each with a  defect count variance of $v_i$, then CART seeks the attributes
+whose ranges minimizes $\sum_i \left(\sqrt{v_i}\times n_i/(\sum_i n_i)\right)$.}.
+\item
+Random Forest    divides data like CART,
+but it builds more than one tree, each time using some subset of
+the attributes (selected at random). 
+\item
+WHERE projects the data on to dimensions synthesizes from the raw data using
+a process analogous to principle component analysis\footnote{
+PCA  synthesises  new
+attributes $e_i, e_2,...$
+that extends across the dimension of greatest  variance in the data  with attributes $d$.  
+This process  combines
+redundant  variables into a smaller set of variables  (so $e \ll d$) since those
+redundancies become (approximately) parallel lines
+in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
+can ignore $j$ 
+since effects that change over $j$ also
+change in the same way over $i$.
+PCA is also useful for skipping over noisy variables from $d$-- these
+variables are effectively ignored since    they  do not contribute to the variance in the data.}.
+WHERE   divides  at the median point of that projection. On recursion,
+this generates a dendogram, the leaves of which are clusters of  very similar examples.
+\ei
+WHERE's {\em infoPrune} tuning parameter then uses  what attributes are used in this process.
+
+XXX
+
+Once WHERE's dengogram is generated, some mechanism must be used to map test cases into specific 
+clusters. To this end, WHERE pretends its clusters are ``classes'' and 
+a entropy-based decision tree learner   to find
+the decisions that best select for each ``class'' (i.e. each cluster).
+This entropy-based learner  finds the attributes that build sub-trees that best select
+for the fewest  clusters\footnote{In entropy based decision-tree learning,  the
+the splitting attribute is the one that most  minimizes $\sum_i \left( e_i\times n_i/(\sum_i n_i)\right)$,
+defined as follows.
+Let    attribute ranges $r_i$ select
+$n_i$ rows that are found in $c_j$ clusters.  Then the probability of
+arriving at those clusters is $p_j = c_j/n_i$ and the entropy
+of those rows is $e_i = \sum_j \left( -p_j \ldot log_2p_j\right)$.}.
+\ei
+After b
+
+If WHERE's {\em tree prune} parameter is enabled, then WHERE also prunes  superfluous sub-trees
+in the cluster-selection trees. For example, if a sub-tree and its parent have the same 
+majority cluster
+(one that occurs most frequently), then we prune the sub-tree.
+
+Other tuning parameters are learner specific. For example,
+{\em max feature} is used by
+CART and Random Forest to select the number of attributes
+used to build one tree.
+CART's default is to use all the attributes while 
+Random Forest usually selects the square root of the number
+of attributes.
+Also,
+$F$ is the number of trees built by Random Forest 
+(and was
+  discussed in our introduction).
+ Further,
+  {\em max leaf nodes} is the upper bound on leaf notes generated in a 
+  Random Forest.
+
+Of all our learners, WHERE has the most tuning parameters. This turns out
+to be significant since, in the experiments shown below, tuned WHERE 
+out-performed the other learners. This suggests the heuristic that if
+you are going to tune learners, use one with the most tuning options.
+
+After building its tree, WHERE ranks all attributes by how well
+they select for fewest leaves (using the  infogain measure
+from the Fayyad-Irani discretizer~\cite{FayIra93Multi}, where ``class'' is really the leaf cluster ids). It then only uses the best {\em infoPrune} percent of the attributes to build
+its cluster selection tree. Also, the {\em tree prune} parameter (described above) sometimes
+prunes aways all  cluster selectors branches. To tame this effect, the {\em wriggle} parameter
+blocks tree pruning for at least the the   {\em wriggle} number of initial branches.
+
+We choose CART and Random Forest since  these were used in 
+a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 21 different 
+learners for software defect prediction:
+\bi
+\item
+{\em Statistical classifiers:}
+Linear    discriminant analysis,
+Quadratic discriminant analysis,
+Logistic regression,
+Naive Bayes,
+Bayesian networks,
+Least-angle regression,
+Relevance vector machine,
+
+\item
+{\em Nearest neighbor methods:}
+k-nearest neighbor,
+K-Star
+
+\item
+{\em Neural networks:}
+Multi-Layer Perceptron,
+Radial bias function network,
+
+\item
+{\em Support vector machine-based classifiers:}
+Support vector machine,
+Lagrangian SVM
+Least squares SVM,
+Linear programming,
+Voted perceptron,
+
+\item
+{\em Decision-tree approaches:}
+C4.5 decision tree,
+CART,
+Alternating decision tree.
+\item
+{\em Ensemble methods:}
+Random Forest,
+Logistic Model Tree.
+\ei
+In that study, CART was severely trounced (was ranked last) and Random Forest was
+the standout best method. The experiments shown below both confirm and refute
+that ranking. In a result consistent with the prior result, untuned Random Forest performs best.
+However, after tuning, the worst learner found by Lessmann et al. (CART) performed better
+than Random Forest.
+
+, where the performance of both tools as predictors are 
+significantly different based on authors' experiment as mentioned before. We'd like to 
+investigate whether tuning can change such conclusion. WHERE-based Predictor is a new 
+defect predictor based on WHERE\cite{menzies2013local} algorithm. A comparison with 
+standard predictor like CART and Random Forest will better evaluate and judge the 
+performance such new predictor. As for the tuner, there're many heuristic optimization 
+algorithms in wild. However, DE is a good but maybe not the best candidate for the tuning 
+process considering different performance measurements. To determine which optimizer is 
+fitable and results in better performance is beyond this work scope. We leave it to future 
+works. The rest of this section will describe each tool applied in this work.
+
+While there are many technical
+differences
+in those learners, they have certain similarities.
+
+To begin with, all the learners in this study generate numeric predictions which are converted
+into binary ``yes/no'' decisions via \eq{yesno}. Hence, they all have some threshold  value $T$ 
+that can be tuned.
+
+same goal: to summarize a large data set into a small model\footnote{Technical note: proponents of instance-based reasoning might argue that
 their goal is to retain, and not summarize, the training data.
@@
 \item
-Kocagenunil~\cite{me13a} and Papakroni~\cite{papa13} conduct  different experiments
-to  show  that tables of software defect data in the form of \fig{ck} contain around 90\% redundant
-data. Specifically, they show that such tables can be be pruned back to around
+The seperate experiments of
+Kocagenunil~\cite{me13a} and Papakroni~\cite{papa13}  show that  tables  of data
+like \fig{ck} can be be pruned back to around
 25\% of the columns and 10\% of the rows without losing the essential information in the data set.
+This reduced space contains $0.25*0.1 = 2.5\%$ of the cells in the original table.
+While some of that reduction is due to the removal of noise, their conclusion is correlated
+columns and similar rows are very common in SE data sets.
 \ei

### 2015-03-13 tuningpredictor.tex
Updates from ShareLaTeX

--- 2015-03-13 tuningpredictor.tex
@@
 
+\newcommand{\wei}[1]{\textcolor{red}{Wei: #1}}
+
 %% timm tricks
@@
 can no longer be condoned. For example, one such default setting
-  in the Python SciKitLearn toolkit~\cite{scikit-learn}
-is to use $T=10$ decision trees in  Random Forest classifiers.
-Our optimizer settled on  $T$ values that were were nowhere near that default:
+  in the Python \mbox{SciKitLearn} toolkit~\cite{scikit-learn}
+is to use $F=10$ decision trees in  Random Forest classifiers.
+Our optimizer settled on  $F$ values that were were nowhere near that default:
 
 {\scriptsize
-\[T \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
+\[F \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
                                 108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
@@
 very least, {\em misleading}.
-At the very least, there is now cause to doubt many conclusions based on
+Clearly, we must now doubt  conclusions based on
 ``off-the-shelf'' tunings.
-At the very most, 
-it is no longer enough to just run a data miner and present the result
+Further,
+it is no longer enough to just run a data miner and report the result
 {\em without} first conducting an tuning optimizations study.
 
-The rest of this paper is structured as follows.
-
-\section{Preliminaries}
-
-Before beginning, this section offers certain caveats on these results.
+\subsection{Preliminaries}
+
+Before beginning, we offer four caveats on these results.
 
@@
 
-Secondly, the tuning results shown here only came from one particular software analytics task 
+Secondly, the tuning results shown here only came from one  software analytics task 
 (defect prediction from static code attributes).
@@
 
-\section{Background}
+\section{Motivating Example}\label{sec:eg}
+
+This section offers a small demonstration
+of the impact of tuning parameters. It also demonstrates that this issue of tuning effects not jist the complex data miners discussed later in the paper bu t also 
+applies for even very simple  learning schemes.
+
+One way to generate a  defect predictor from
+static code is to use 
+linear  regression.
+This is a standard statistical
+method that fits a straight line to a set of points. The line
+offers a set of predicted values.
+If the points are somewhat
+scattered, then a single regression line cannot pass through all points and the distance from these predicted values to the actual
+values is a measure of the error associated with that line.
+Linear regression search for a line that minimizes that
+error and maximizes the correlation\footnote{
+$Correlation$
+measures how closely two variables co-vary.  It ranges from   from -1
+(perfect negative correlation) through 0 (no correlation) to +1
+ (perfect positive correlation).
+Let  $a_i$ and $p_i$ denote some actual and predicted values respectively; and  $n$ and $\overline{x}$ denote
+ the number of observations and the mean of the $n$ observations, 
+respectively. Then:
+$S_{PA}=(\sum_i (p_i - \overline{p})(a_i -
+  \overline{a}))/(n-1)$ and
+$S_{p}=(\sum_i (p_i - \overline{p})^2)(n-1)$
+and 
+$S_{a}=(\sum_i (a_i - \overline{a})^2)/(n-1)$ and
+correlation is  $c=S_{PA}/\sqrt{S_pS_a}$.}  denoted as $c$.
+
+Suppose  a researcher wants to use linear regression
+to test if Halstead's~\cite{halstead77} measures
+of   function complexity
+(number of symbols programmers has to understand) are   {\em better than}
+mere lines of code for predicting
+software defects.  That researcher might argue that Halstead's cognitive approach to
+software bugs is better suited to code refactoring tools since it offers 
+more ways to alter functions that just some coarse grain lines of code measure.
+
+That researcher might test that belief by using studying historical
+defect logs with 
+linear regression. Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
+that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
+software module (in this case, a ``C'' function).
+Note that the Halstead correlation $c_2$
+is worse than those from lines of code $c_1$. This result  seems to suggest that
+despite their potential support for refactoring, our researchers should not use Halstead.
+
+{\scriptsize \[\begin{array}{l|l|ll}
+\mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
+\mathit{LOC}   &d_i= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
+\mathid{Halstead & d_2= 0.231 + 0.00344N     \\    
+           & +  0.0009V   - 0.185L \\
+           & - 0.0343D      - 0.00541I \\
+           & + 0.000019E + 0.711B \\ 
+            &   - 0.00047T  & c_2=-0.36 
+            \end{array}
+\end{eqnarray}}
+
+\noindent
+Enter tuning. Suppose the defect predictors $d_1$ and $d_2$  learned from LOC or Halstead
+are used to to call an inspection
+team to check for errors in certain parts of the code using the rule
+\begin{equation}\label{eq:yesno}\scriptsize
+\mathit{inspect}= \left\{
+\begin{array}{ll}
+d_i \ge T \rightarrow \mathit{Yes}\\
+d_i <   T \rightarrow \mathit{No}
+\end{array}
+\end{equation}
+\fig{pd1} shows the effects of tuning the $T$ variable. Not surprisingly,
+at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
+problem, we can increase $T$. \fig{pd1} reports that the false alarm rate falls below
+20\% at $T=0.45$ (for Halstead).
+
+\begin{figure}[!t]
+{\scriptsize
+\begin{center}
+
+\% recall (probability of detection):
+
+\includegraphics[width=3in]{lsrvscostpd.pdf}
+
+\% false alarms:
+
+\includegraphics[width=3in]{lsrvscostpf.pdf}
+\end{center}}
+\caption{
+ Y-axis shows probability of false alarm,
+  and
+  probability of recognizing defective modules  seen using \mbox{$d_i \ge T$}.
+  Curves calculated from the KC2 dataset from the PROMISE repository goo.gl/pGDfvp.
+ }\label{fig:pd1}
+ \end{figure}
+
+One  important lesson from  \fig{pd1} is that the ``best'' tunings are context
+specific. For mission critical systems (e.g. a nuclear power plant), management
+might accept the cost of high false alarm rates if it meant increasing the probability
+of detecting errors. For such contexts, we might recommend some very small value of $T$.
+
+The other  important lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
+detector can work just as well as seemingly better ones.
+Note that either the Halstead or LOC detector can reach some desired
+level of recall, regardless of their correlations, just by
+selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
+found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
+were very similar: 14\% and 19\%).
+
+The core point of this example is that    the true value of a detector
+could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
+issuing a request to an inspection team to review some module).  
+This is strong motivation to explore the issue of tunings.
+
+\section{Background Notes}
+
+The rest of this paper repeats the analyis of the last section, but for much
+more complex learners. In those results, shown  below, we will find
+examples of {\em rank reversals};
+i.e.  after tuning the top ranked defector becomes last and vice versa.
+Such examples motivate the extensive exploration of tuning in software analytics.
+Before presenting those results, this section offers some background notes on defect prediction,
+performance measures, and optimization with differential evolution.
+
 \subsection{Defect Prediction}
@@
 
-\subsection{Data Mining}
-Static code defect prediction applies data miners to build its predictors. How does data mining work?
+\subsection{Data Mining Algorithms}
 

### 2015-03-14 learners.tex
Updates from ShareLaTeX

--- 2015-03-12 learners.tex
@@
-Dta miners find generalizations (a.k.a. summaries)
-of the data. All such generalizations must be smaller than the data it generalizes (otherwise we might as well just keep the original data and ignore the generalization)\footnote{Technical note:
-even instance-based reasoners uses generalizations when they partially match new cases to old;
-or if they use some  clustering algorithm to restrict the case matching
-to just the subset of old cases most similar  to new  cases.}. 
-Generalization is important since,
-without generalization, all we can do is perform exact matches
-of new situations against  a database of old examples. This is not recommended practice since,
- if the new situation has not occurred  before, then nothing in the data  will
- matches the new situation
-(and we cannot make any predictions).
+This section describes this study's learners (CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
+and WHERE~\cite{menzies2013local}) and their
+tuning parameters (summarised in \fig{parameters}).
 
-The key point here is that, at least is software engineering,
-the raw data contains noise and superflous details (e.g. highly correleated attributes
-or repeated/very similar rows). Recent results show
+Our implementations
+for CART and Random Forest comes from 
+SciKitLearn~\cite{scikit-learn}.
+WHERE is available from
+github.com/ai-se/where\footnote{\wei{ need a nice  where repo. with an
+data and code examples sub-directory. clean code. throw out anything not needed. before april1.}}.
+WHERE has the most tuning parameters. This turns out
+to be important since, in the experiments shown below, tuned WHERE 
+out-performed the other learners-- a result suggesting that
+if you are going to tune learners, then use one with many tuning options.
 
-are many ways to summarize data.  A repeated result is
-that a table of data with R rows and C columns can be reduced to around Consider some learner that
-builds predictive rules form a subset of  attributes $A$ ranges. Assuming numeric attributes
-divided into five ranges, then the 20 attributes of \fig{ck} can be combined into 
-$2^{5*20}> 10^{30}$
-possible rules
-
-\section{Algorithm: Predictor and Tuner}
-
-In order to conduct the experiment of this paper, we need one tool that can predict defects 
-from the empirical data sets and a second tool to tune the built-in parameters associated with 
-predictor. To compare the effects of the tuning process, we have three different predictors: 
-WHERE-based Predictor, CART and Random Forest. Different Evolution(DE) as an optimizer 
-is used as a tuner in this paper.
-
-We choose CART and Random Forest as a predictor in this paper is motivated by 
-\cite{lessmann2008benchmarking}, where the performance of both tools as predictors are 
-significantly different based on authors' experiment as mentioned before. We'd like to 
-investigate whether tuning can change such conclusion. WHERE-based Predictor is a new 
-defect predictor based on WHERE\cite{menzies2013local} algorithm. A comparison with 
-standard predictor like CART and Random Forest will better evaluate and judge the 
-performance such new predictor. As for the tuner, there're many heuristic optimization 
-algorithms in wild. However, DE is a good but maybe not the best candidate for the tuning 
-process considering different performance measurements. To determine which optimizer is 
-fitable and results in better performance is beyond this work scope. We leave it to future 
-works. The rest of this section will describe each tool applied in this work.
-
- \subsection{WHERE-based Learner}
-\textbf{WHERE-based Learner} is composed of WHERE clustering algorithm and CART 
-decision tree algorithm. The key idea of WHERE-based learner is that  instead of training the 
-CART decision tree based on the class labels associated with each training sample, it's using 
-CART to build decision trees based on the cluster labels, which are generated by the WHERE 
-clustering algorithm.
-
-\begin{figure}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
+%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
+\renewcommand\arraystretch{1.2}
+\begin{figure*}[t!]
 \scriptsize
   \centering
-  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
-    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
-    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
-pd&71.4&1.2&60&4.4&0.1&44&7.1&0.2&36\\ 
-prec&82.8&1.4&59&3.9&0.1&39&7.4&0.2&37\\
-f&86.1&1.2&72&3.3&0.1&33&6.7&0.2&34
+	\begin{tabular}{|c|c|c|c|l|}
+	\cline{1-5}
+	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
+\multicolumn{1}{c|}{Description} \\ \hline
+	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
+	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
+	& infoPrune & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
+split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
+one is for clustering and the second one is building prediction model. we explicitly call Where-
+clustering tree and CART tree, respectively}. \\ \cline{2-5} 
+	 & min\_sample\_split & 4& [1,10]& The minimum number of samples required to split an internal node of
+CART tree. \\ \cline{2-5} 
+	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
+number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
+\end{tabular} \\ \cline{2-5} 
+    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
+	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
+clustering tree. \\ \cline{2-5} 
+	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
+	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
+	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
+\hline
+\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5}
+
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_samples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{1-5}  
+       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
+\cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5} 
+	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_samples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{2-5} 
+	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
+	 \hline
+
 	\end{tabular}
-  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
-  for different goals, or just running the ``off-the-shelf'' learner.}
-\end{figure}
+    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
+\label{fig:parameters}
+\end{figure*}
 
-\begin{figure}[!t]
+\subsection{Why Study These Algorithms?}
 
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-\begin{tabular}{r|rrr}
-goal &	WHERE	&CART&	Random Forest\\\hline
-f	&15	&13	&9\\ 
-pd	&15	&16	&8\\ 
-prec&	14	&14	&8
-\end{tabular}
-\caption{How much slower is tuning vs just running the default
-settings of the learner? E.g. bottom right, tuning to increase
-precision with Random Forests is eight times slower than
-just running Random Forests.}
-\end{figure}
+This paper studies WHERE since this was the first learner we tried to tune and, as shown below,
+it offers an interesting case study on the benefits of tuning.
 
-% Given N instances, instead of building decision tree directly with CART, we use WHERE to 
-%cluster instances. 
-WHERE is a fast clustering algorithm designed by {\it menzies} for finding software artifacts 
-with similar attributes. It clusters data on dimensions synthesized along the axis of greatest 
-variability in the data. The way WHERE used to find such dimension is a linear-time heuristic 
-called ``FASTMAP" proposed by Faloutsos \& Lin\cite{faloutsos1995fastmap}. ``FASTMAP" 
-randomly picks one instance $Z$; find the instance {\it east} $X$ that's furthest away form $Z$; find 
-the instance {\it west} $Y$ that's furthest away from {\it east} $X$. Next, project all the remaining 
-points onto the line drawn between $X$ and $Y$.  The line $\overline{XY}$ is an approximation of the 
-first component found by PCA.
-As shown in Figure \ref{Where}, $X$ and $Y$ are the furthest points found by ``FASTMAP'' and $\overline{XY}$ is of length $c$.
-Each point in this figure has a distance $a$
-to $X$ and distance $b$ to $Y$. According to the coisne rule and Pythagoras, each instance will be mapped 
-into 2-dimension by the following equations.
-\begin{equation}
-\begin{split}
-x  &= (a^2 +c^2-b^2)/(2c)\\ 
-   y  &= \sqrt{a^2 -x^2}
-\end{split}
-\end{equation}
+This paper also studies  CART and Random Forest since  these were used in 
+a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 21 different 
+learners for software defect prediction:
+\bi
+\item
+{\em Statistical classifiers:}
+Linear    discriminant analysis,
+Quadratic discriminant analysis,
+Logistic regression,
+Naive Bayes,
+Bayesian networks,
+Least-angle regression,
+Relevance vector machine,
 
-Then choose the median point $\hat{x}$ as the split and 
-recursively divide all the instances into {\it west} and {\it east} clusters until the number of 
-instances within each cluster is less than specific minimum size. The representation of the 
-clustering result is a tree, we call it Where-clustering tree. Such tree will be pruned if applicable 
-in some cases. Finally, cluster labels  will be assigned to instances in each of those 
-clusters(leaves).
+\item
+{\em Nearest neighbor methods:}
+k-nearest neighbor,
+K-Star
 
-\begin{figure}[!ht]
-\includegraphics[scale=0.5]{where.png}
-\caption{WHERE algoirthm }
-\label{Where}
-\end{figure}
-Then based on the attributes and the cluster labels in each instances,  we build a 
-decision tree based on CART algorithm. In each leaf of the tree, there're several instances 
-falling in. This will be the model trained for defect prediction. During testing process, a new 
-instance comes in and traverses the tree according to 
-values of the its attributes. If the instance could reach one leaf of the tree, the predicted value 
-of this instance will be the mean  of all the training data values associated with this leaf. 
-Otherwise if stops at intermediate nodes of tree, the predicted value will be the mean of the all 
-the training data value below this node. After estimating all the number of defectives in the test 
-data, whether each instance contains defectives will be determined by comparing with a threshold value.
-If the predicted value is greater than threshold, the Where-based learner will predict this instance as defective otherwise non-defective.
+\item
+{\em Neural networks:}
+Multi-Layer Perceptron,
+Radial bias function network,
 
-%\begin{algorithm}
-%	\caption{Pesudocode for WHERE Algorithm }
-%	\label{alg:WHERE}
-%	\begin{algorithmic}[1]
-%	\Require $data$
-%	\Ensure $tree$
-%	\Function {Fastmap}{$ data$}
-%	\State $one \gets$ any$(data)$
-%	\State $west \gets$ furthest$(data, one)$
-%	\State $east \gets$ furthest$(data, west)$
-%	\State $c \gets$ distance($west, east$)
-%	\EndFunction
-%	\end{algorithmic}            
-%\end{algorithm}
+\item
+{\em Support vector machine-based classifiers:}
+Support vector machine,
+Lagrangian SVM
+Least squares SVM,
+Linear programming,
+Voted perceptron,
 
-\subsection{CART}
-\textbf{CART} is an {\em iterative dichotomization} algorithm
-that finds the attribute that most divides the data such that
-the variance of the goal variable in each division is
-minimized\cite{breiman84}.
-The algorithm then recurses on each division.
-Finally, the cost data in the leaf divisions
-is averaged to generate the estimate.
+\item
+{\em Decision-tree approaches:}
+C4.5 decision tree,
+CART,
+Alternating decision tree.
+\item
+{\em Ensemble methods:}
+Random Forest,
+Logistic Model Tree.
+\ei
+In that study, CART was severely trounced (was ranked last) and Random Forest was
+the standout best method. The experiments shown below both confirm and refute
+that ranking. In a result consistent with the prior result, untuned Random Forest performs best.
+However, after tuning, the worst learner found by Lessmann et al. (CART) performed better
+than Random Forest.
 
-\subsection{Random Forests}
+\subsection{Learners and Their Tunings}
 
-Breiman's website describes \textbf{Random Forests} as
-follows\cite{brieman00}. "Random Forests grows many classification
-trees. To classify a new object from an input vector, put the input
-vector down each of the trees in the forest. Each tree gives a
-classification, and we say the tree "votes" for that class. The forest
-chooses the classification having the most votes (over all the trees
-in the forest). Each tree is grown as follows.
-If the number of cases in the training set is N, sample N cases at
-random - but with replacement, from the original data. This sample
-will be the training set for growing the tree.
-Also, if there are M input variables, a number m$<<$M is specified such
-that at each node, m variables are selected at random out of the M and
-the best split on these m is used to split the node. The value of m is
-held constant during the forest growing.
-Finally, each tree is grown to the largest extent possible (there is
-no pruning)."
+CART, Random Forest, and WHERE are all  tree learners that divide a data set, then recurse
+on each split.
+If data contains more than {\em min sample split}, then a split is attempted.
+On the other hand, if a split contains no more than {\em min samples leaf}, then recursion stops. For CART and Random Forest use a 
+user-supplied constant for this parameter while
+WHERE computes $m$={\em min samples leaf} from the size of the data
+sets via  $m=\mathit{size}^\mathit{min size}$ (so, for WHERE,
+{\em min size} is the parameter to be tuned).
 
-%Suppose the cordinates of X and Y are $(0,0)$ and $(0,c)$, which are east and west 
-%instances within N samples. From the Pythegoras and cosine rule, each instance is projected 
-%at the point(x,y)
-%
-%\begin{equation}
-%	\begin{split}
-%	x &= (a^2 + c^2 - b^2)/(2c) \\
-%	y &= \sqrt{a^2 - x^2} 
-%	\end{split}
-%\end{equation}
+These learners
+generate numeric predictions which are converted
+into binary ``yes/no'' decisions via \eq{yesno}. Hence, they all use the {\em threshold} value $T$ discussed in \tion{eg}.
+
+These learners use different techniques to explore the splits:
+\bi
+\item
+CART finds the attributes whose ranges contain rows with least variance in the number
+of defects\footnote{If an attribute ranges $r_i$ is found in 
+$n_i$ rows each with a  defect count variance of $v_i$, then CART seeks the attributes
+whose ranges minimizes $\sum_i \left(\sqrt{v_i}\times n_i/(\sum_i n_i)\right)$.}.
+\item
+Random Forest    divides data like CART,
+but it builds $F>1$  trees, each time with a subset of
+the attributes (selected at random). 
+\item
+WHERE projects the data on to a dimension it synthesizes from the raw data using
+a process analogous to principle component analysis\footnote{
+PCA  synthesises  new
+attributes $e_i, e_2,...$
+that extends across the dimension of greatest  variance in the data  with attributes $d$.  
+This process  combines
+redundant  variables into a smaller set of variables  (so $e \ll d$) since those
+redundancies become (approximately) parallel lines
+in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
+can ignore $j$ 
+since effects that change over $j$ also
+change in the same way over $i$.
+PCA is also useful for skipping over noisy variables from $d$-- these
+variables are effectively ignored since    they  do not contribute to the variance in the data.}.
+WHERE   divides  at the median point of that projection. On recursion,
+this generates a dendogram, the leaves of which are clusters of  very similar examples.
+\ei
+WHERE's {\em infoPrune} tuning parameter then choices the
+attributes   that best select  different clusters.
+WHERE pretends its clusters are ``classes'', then 
+asks the InfoGain of the
+Fayyad-Irani discretizer~\cite{FayIra93Multi}, to rank the attriubutes.
+WHERE then ignores everything except the top   {\em infoPrune} percent of the sorted
+attributes.
+
+Optionally, if the {\em where prune} option is set, 
+WHERE  continues to applies infogain criteria  recursively to build a tree that selects for the
+different clusters. If WHERE's {\em tree prune} parameter is enabled, then WHERE also prunes  superfluous sub-trees. For example, if a sub-tree and its parent have the same 
+majority cluster
+(one that occurs most frequently), then we prune the sub-tree.
+This tree pruning  sometimes
+prunes aways all  cluster selectors branches. To tame this effect, the {\em wriggle} parameter
+blocks tree pruning for at least the the {\em wriggle} number of initial branches.
+
+Other tuning parameters are learner specific. For example,
+{\em max feature} is used by
+CART and Random Forest to select the number of attributes
+used to build one tree.
+CART's default is to use all the attributes while 
+Random Forest usually selects the square root of the number
+of attributes.
+Also,
+  {\em max leaf nodes} is the upper bound on leaf notes generated in a 
+  Random Forest.
+
+\subsection{Tuning Algorithms}
+
+ \subsubsection{Parametric Tuning Algorithms}
+The  goal of this paper is to adjust the tuning parameters of \fig{parameters}
+in order to   optimize (improve) some particular performance scores
+generated by a particular learner being applied to  a particular data set.
+For this task, we do not use traditional parametric numeric optimizer  
+such as  gradient descent optimizers~\cite{saltelli00} that require models comprise
+differential functions (i.e. functions of real-valued variables whose derivative exists at each point in its domain).
+This is impractical  for  our learners since their internal states are   not a smoothly differential continuous function.
+Rather, learners being tuned  contains many regions with many different properties (tuning options can
+drive the learner into very different modes with very different performance properties).
+
+ \subsubsection{Non-Parametric Tuning Algorithms}
+
+Non-parametric  optimizers   make no assumption
+about the model being only differential functions. One such optimizer
+is simulated annealing. SA generates {\em new} solutions
+ by randomly perturbing (a.k.a. ``mutating'') some part of an {\em old}
+ solution.  {\em New} replaces {\em old} if (a) it scores higher; or
+ (b) it reaches some probability set by a ``temperature'' constant. Initially,
+ temperature is high so SA jumps to sub-optimal solutions (this allows
+ the algorithm to escape from local minima). Subsequently, the
+ ``temperature'' cools and SA only ever moves to better {\em new}
+ solutions. 
+ SA is often used in search-based SE
+ e.g.~\cite{fea02a,me07f}, perhaps due to its simplicity.
+
+SA was invented   in the 1950s, when
+ computer RAM was very small~\cite{kirkpatrick83}. A standard SA algorithm needs
+ only space for three solutions {\em new, old} and the {\em best} seen so far.
+  In the 1960s, when more RAM became available, it became standard to
+ generate many {\em new} mutants, and then combine together parts of
+ promising solutions~\cite{goldberg79}.  Such {\em evolutionary
+   algorithms} (EA) work in {\em generations} over a population of
+ candidate solutions.  Initially, the population is created at random.
+ Subsequently, each generation makes use of select+crossover+mutate
+ operators to pick promising solutions, mix them up in some way, and
+ then slightly adjust them.
+ EAs are also often used in search-based
+ software engineering, particularly in test case generation~\cite{andrews07,andrews10}
+ or refactoring~\cite{Weimer:2009}
+
+ Later work focused on creative ways to control the
+ mutation process. Tabu search and scatter search
+ work to bias new mutations away from prior
+ mutations~\cite{Glover1986563,Beausoleil2006426,Molina05sspmo:a,4455350}.
+ Particle swarm
+ optimization randomly mutates multiple solutions
+ (which are called ``particles''), but biases those
+ mutations towards the best solution seen by one
+ particle and/or by the neighborhood around that
+ particle~\cite{pan08}.
+ Differential evolution mutates solutions by
+ interpolating between members of the current
+ population~\cite{storn1997differential}.
+
+Another more recent technique that has claimed much attention
+are   heuristics that decompose the total space into many smaller problems, and then which use a simpler optimizer for each region. 
+For example, in $\mathcal{E}$-domination~\cite{deb05}, the  user is asked
+`what is the lower threshold $\mathcal{E}$ on the size of a useful effect?''. The solution space
+is then divided into boxes of size $\mathcal{E}$ and linked such that  the  set $X.\mathit{lower}$ contains boxes with worse objective scores that $X$.
+Solutions in pairs boxes are  quickly compared  using   small samples from each  and, if some box $X$ is found to be inferior, then it is quickly pruned along with all
+solutions in the $X.\mathit{lower}$ boxes.
+Later research generalized this approach. MOEA/D (multiobjective
+evolutionary algorithm based on decomposition~\cite{zhang07}) is a generic framework that decomposes a multiobjective optimization problem into many smaller single problems, then applies a second optimizer to each smaller subproblem, simultaneously.
+Other work in this arena are the response surface methods
+that quickly find multiple approximations to the problem, each of which holds for a very tiny region.
+Each region has a ``slope'' and examples in that region are pushed along the slope towards better
+solutions~\cite{krall15,Zuluaga:13}.
+
+ \subsubsection{Selecting a Tuning Algorithm}
+
+From all the above methods, how do we select which optimizers to apply to tuning data miners.
+Cohen~\cite{cohen95} advises comparing any supposedly more
+sophisticated method against the simplest possible alternative. For
+example, in one study with ``floor effects'', Holte showed that,
+often, much of the performance of complex multi-level decision trees
+could be easily achieved using a much simpler single-level decision
+tree learner called 1R~\cite{holte93}. He therefore recommends a very simple rule learner
+(called ``1R'') as a
+kind of ``scout'' that can do a quick preliminary analysis of a data
+set and which can report back if that data really requires a more
+complex analysis.
+
+To find our ``scout'',  we sorted  the above algorithms from simplest to most complex.
+The three simplest optimizers are SA, $\mathcal{E}$-domination, and 
+differential evolution (each can be coded in less than a page of some high-level scripting language). Our reading of the current literature is that there are more current advocated for
+differential evolution than
+  SA or $\mathcal{E}$-domination. when the MOEA/D community select a secondary optimizer, then often use  differential evolution~\cite{zhang07,5583335}.
+  Also, Vesterstrom and Thomsen~\cite{Vesterstrom04} found that  differential evolution was competitive with 
+   particle swarm optimization and a genetic algorithm.

### 2015-03-14 tuningpredictor.tex
Updates from ShareLaTeX

@@
 that   that that method can find and fix known bugs. Note that this is a {\em competency criteria}
-which does not include the phrase  {\em better than}. Such performance criteria do
+which does not include the phrase  ``{\em better than}''. Such performance criteria do
 not requiring tuning.  However, once {\em better than} enters the performance criteria
@@
 
-\section{Motivating Example}\label{sec:eg}
+\section{Motivating Example}\label{sect:eg}
 
@@
 respectively. Then:
-$S_{PA}=(\sum_i (p_i - \overline{p})(a_i -
+$S_{\mathit{PA}}=(\sum_i (p_i - \overline{p})(a_i -
   \overline{a}))/(n-1)$ and
@@
 $S_{a}=(\sum_i (a_i - \overline{a})^2)/(n-1)$ and
-correlation is  $c=S_{PA}/\sqrt{S_pS_a}$.}  denoted as $c$.
+correlation is  $c=S_{\mathit{PA}}/\sqrt{S_pS_a}$.}  denoted as $c$.
 
@@
 
-{\scriptsize \[\begin{array}{l|l|ll}
+{\scriptsize \[
+\begin{array}{l|l|ll}
 \mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
 \mathit{LOC}   &d_i= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
-\mathid{Halstead & d_2= 0.231 + 0.00344N     \\    
+\mathit{Halstead} & d_2= 0.231 + 0.00344N     \\    
                  & +  0.0009V   - 0.185L \\
@@
 \end{array}
-\end{eqnarray}}
+\]
+}
 
@@
 d_i <   T \rightarrow \mathit{No} 
-\end{array}
+\end{array}\right.
 \end{equation}
@@
 
-\subsection{Differential Evolution Algorithm}
+The psuedocde for differential evolution is shown in Algorithm \ref{alg:DE}
+
+for 
 Differential Evolution (DE)\cite{storn1997differential} is a stochastic search algorithm that 
@@
 
-The experiment aims at investigate whether tuning helps learners improve performance in 
+The experiment aims at investigating whether tuning helps learners improve performance in 
 terms of accuracy measurement. We choose compare WHERE-based learner with and 
@@
 
-To evaluate accuracy performance of learners, several measurements are proposed, like 
+To evaluate accuracy performance of learners, several measurements are proposed to use, like 
 probability of  detection({\it pd}) and probability of false alarm ({\it pf})\cite{menzies2007data}, 
 the area under the receiver operating characteristics curve ({\it AUC})
-\cite{lessmann2008benchmarking}, and precision\cite{zhang2007comments}. In this work, we 
+\cite{lessmann2008benchmarking}, precision and F measure\cite{zhang2007comments}. In this work, we 
 expect learners should identify as many defective modules as possible while avoiding false 
@@
 
-In this experiment, we use three different portions of one project data set for training, tuning 
-and testing process. In contrast to hold out way used in \cite{lessmann2008benchmarking, 
+In this experiment, we divide one project data set into training, tuning 
+and testing datasets. In contrast to hold out way used in \cite{lessmann2008benchmarking, 
 menzies2007data}, we separate the data sets in order. Since learners are designed to predict 
 defects in future projects,  any randomly data set selection without taking into the time series 
-will not sufficient to evaluate the performance of predicting future. To the most, that is good to 
-evaluate the accuracy of classification but not predicting future. Since we have 10 different 
-project data, each of which contains least 3 evolutionary versions. We use the following policy 
-to select the data: in each project, we only use the last three data files for experiment. 
-Specifically, the $nth$,  $(n-1)th$, $(n-2)th$ versions of project data are selected for testing, 
-tuning and training learners, respectively. This will make sure that we don't use the future 
-project data to train learners and predict previous project.
+will not sufficient to evaluate the performance of predicting future. Since we have data from 
+10 different projects, each of which contains at least 3 evolutionary versions. We use the following policy 
+to select the data for experiments: for each project, we use every three chronological data files 
+to do testing, tuning and training in one experiment. For example, in ant project,
+we have versions of $ant1.3$, $1.4$, $1.5$, $1.6$, and $1.7$, which will generate data sets called
+ $antV0$, $antV1$ and $antV2$ for three experiments.
 
@@
 
-Besides the Where-based learner implemented by ourself,  we use the CART and Random Forest modules 
-from scikit-learn \cite{scikit-learn} for this experiment.
+Besides the Where-based learner implemented by ourselves,  we use the CART and Random Forest modules 
+from scikit-learn \cite{scikit-learn} to do a comparative study.
 The parameters associated with different learners are listed in Fig.\ref{fig:parameters}.
-(\textbf{NEED to elaborate that there're different versions of CART, what's the point to do this experiment}).
 For each data set, run CART, naive Where-based learner and Random Forests with corresponding default values.
 Then using DE to tune corresponding parameters for CART and Where-based Learner,  and run them again with the optimal parameters from tuning process to test the performance.
-This study ranks learners using the Scott-Knott procedure recommended by Mittas \& Angelis in their 2013
-IEEE TSE paper~\cite{mittas2013ranking}.
+% This study ranks learners using the Scott-Knott procedure recommended by Mittas \& Angelis in their 2013
+% IEEE TSE paper~\cite{mittas2013ranking}.
 This method sorts a list of $l$ treatments with $ls$ measurements by their median score.
@@
 
+\begin{figure}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
+    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
+    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
+pd&71.4&1.2&60&4.4&0.1&44&7.1&0.2&36\\ 
+prec&82.8&1.4&59&3.9&0.1&39&7.4&0.2&37\\
+f&86.1&1.2&72&3.3&0.1&33&6.7&0.2&34
+  \end{tabular}
+  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
+  for different goals, or just running the ``off-the-shelf'' learner.}
+\end{figure}
+
+\begin{figure}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+\begin{tabular}{r|rrr}
+goal &	WHERE	&CART&	Random Forest\\\hline
+f	&15	&13	&9\\ 
+pd	&15	&16	&8\\ 
+prec&	14	&14	&8
+\end{tabular}
+\caption{How much slower is tuning vs just running the default
+settings of the learner? E.g. bottom right, tuning to increase
+precision with Random Forests is eight times slower than
+just running Random Forests.}
+\end{figure}
+
 \section{Discussion}
@@
 
+\vspace*{0.5mm}
+
+ \scriptsize
 \bibliographystyle{unsrt}
@@
 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
-number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
+number of samples to be an internal node of the Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
 \end{tabular} \\ \cline{2-5} 
@@
 correct within a very limited context. At the very least, the conclusions
-of those papers (and literally dozens of similar papers, include severl
+of those papers (and literally dozens of similar papers, include several
 of our own~\cite{me02e,me02k,me03a,me06d,me07b}) need to be revisited

### 2015-03-14 dm101.tex
Updates from ShareLaTeX
safey save

@@
 which can be rearranged to 
- $N(C,p)=\frac{log(1 -
-C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}.
+ $N(C,p)=log(1 -
+C)/log(1-p)$. For example, $N(0.90,10^{-3})=2301$.}.
 
@@
 One such lightweight sampling policy is defect predictors learned from static code attributes.
-Given software described using (for example) the attributes of \fig{ck} it is possible
+Given software described using (for example) the attributes of \fig{ck}, it is possible
 to use standard data mining technology to learn where the probability of software defects is highest.

### 2015-03-14 learners.tex
safey save

@@
 	\end{tabular}
-    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
+    \caption {List of parameters to be tuned.}
 \label{fig:parameters}
@@
 prunes aways all  cluster selectors branches. To tame this effect, the {\em wriggle} parameter
-blocks tree pruning for at least the the {\em wriggle} number of initial branches.
+blocks tree pruning for at least the first {\em wriggle} number of initial branches.
 
@@
 
-To find our ``scout'',  we sorted  the above algorithms from simplest to most complex.
+To find our ``scout'',  we used engineering judgement to sort  the above algorithms from simplest to most complex.
 The three simplest optimizers are SA, $\mathcal{E}$-domination, and 
-differential evolution (each can be coded in less than a page of some high-level scripting language). Our reading of the current literature is that there are more current advocated for
+differential evolution (each can be coded in less than a page of some high-level scripting language). Our reading of the current literature is that there are more  advocates for
 differential evolution than
-  SA or $\mathcal{E}$-domination. when the MOEA/D community select a secondary optimizer, then often use  differential evolution~\cite{zhang07,5583335}.
-  Also, Vesterstrom and Thomsen~\cite{Vesterstrom04} found that  differential evolution was competitive with 
+  SA or $\mathcal{E}$-domination:
+  \bi
+  \item
+  When the MOEA/D community requires a secondary optimizer, then often use  differential evolution~\cite{zhang07,5583335}.
+  \item
+ Vesterstrom and Thomsen~\cite{Vesterstrom04} report that DE is competitive with 
    particle swarm optimization and a genetic algorithm. 
+   \ei
+DEs have been applied before for   parameter tuning (e.g. see~\cite{omran2005differential, chiha2012tuning}) but this is the first time they have been applied to
+optimizing defect prediction from static code attributes.

### 2015-03-14 tuningpredictor.tex
safey save

@@
 \usepackage{rotating}
+\usepackage{eqparbox}
 \usepackage{graphics}
@@
 For example,
-in this paper we show   tunings that  alter deection  precision  
+in this paper we show   tunings that  alter detection  precision  
  from 2\% to 98\%.
@@
 it is no longer enough to just run a data miner and present the result
-{\em without} first conducting an tuning optimizations study.
+{\em without} first conducting a tuning optimization study.
 The implications for other kinds of software analytics is now an open and pressing questions.
@@
 that are readily available to researchers~\cite{rod12}.
-For example,  the time of this writing (Feb  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub hosts over 14 million projects.
+For example,  the time of this writing (Feb  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
 
@@
 successful software reuse~\cite{me02k}. That assertion should now be doubted since that
-Menzies study did conduct a tuning study before reporting what factors the data miners
+Menzies study did not conduct a tuning study before reporting what factors the data miners
 found where most influential.
@@
 Secondly, several  prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
-that learnerX is better than learnerY for some software analytics task~.
+that learnerX is better than learnerY for some software analytics task.
 For example, a recent IEEE TSE article claimed that the 
@@
 is to use $F=10$ decision trees in  Random Forest classifiers.
-Our optimizer settled on  $F$ values that were were nowhere near that default:
+Our optimizer settled on  $F$ values that were nowhere near that default:
 
@@
 This section offers a small demonstration
-of the impact of tuning parameters. It also demonstrates that this issue of tuning effects not jist the complex data miners discussed later in the paper bu t also 
+of the impact of tuning parameters. It also demonstrates that this issue of tuning effects 
+not just the complex data miners discussed later in the paper but also 
 applies for even very simple  learning schemes.
@@
 that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
-software module (in this case, a ``C'' function).
+software module (in this case, a  function).
 Note that the Halstead correlation $c_2$
@@
 
-The rest of this paper repeats the analyis of the last section, but for much
+The rest of this paper repeats the analysis of the last section, but for much
 more complex learners. In those results, shown  below, we will find
@@
 
-The psuedocde for differential evolution is shown in Algorithm \ref{alg:DE}
-
-for 
-Differential Evolution (DE)\cite{storn1997differential} is a stochastic search algorithm that 
-optimizes a problem by iteratively trying to improve a  population of candidate solutions with 
-regard to a given quality measurement. Such method makes no assumptions about the 
-problem being optimized and has already been used as a parameter tuner
-\cite{omran2005differential, chiha2012tuning}.
-
-DE starts with creating a population of candidate solutions and then generates new 
-candidates based on $New = X+f*(Y-Z)$, where $X$, $Y$ and $Z$ are randomly selected 
-solutions from the current frontier and $f$ is a crossover factor. The newly generated solution 
-will be added into the next generation of solutions if dominating previous old points in the 
-frontier. To avoid meaning less iteration, early termination strategy is applied that is at the 
-beginning, assign a value to the $life$ parameter, it would be reduced by one each time   
-when the new generation of candidate solutions does not improve in terms of quality 
-measurement. The DE will stop when the $life$ equals to 0.
-
-Algorithm \ref{alg:DE} is a list of pseudocode of DE with early termination for maximizing a 
-score function, where $np$ is the number of population in each generation, $f$ is the 
-crossover factor as mentioned, $cf$ is the probability for crossover operation to generate new 
-candidate, $life$ is to control termination.
-
-\begin{algorithm}
-\caption{Pesudocode for DE with Early Termination}
-\label{alg:DE}
-\begin{algorithmic}[1]
-\Require $np = 10$, $f=0.75$, $cr=0.3$, $life = 5$
-\Ensure $S_{best}$
-
-     \Function{DE}{$np$, $f$, $cr$, $life$}
- \State $Population  \gets $ InitializePopulation($np$)
- \State $S_{best} \gets $GetBestSolution($Population $)
- \While{$life > 0$}
-\State $NewGeneration \gets \emptyset$
-\For{$i=0 \to np-1$}
-\State $S_i \gets$ GenNew($Population [i], Population , cr, f$)
-\If {Score($S_i$) >Score($Population [i]$)}
-\State $NewGeneration$.append($S_i$)
-\Else
-\State $NewGeneration$.append($Population [i]$)
-\EndIf
-\EndFor
-\State $Population  \gets NewGeneration$
-\If{$\neg$ Improve($Population $)}
-\State $life -=1$
-\EndIf
-\State $S_{best} \gets$ GetBestSolution($Population $)
- \EndWhile
-\State \Return $S_{best}$
-\EndFunction
-\Function{Score}{$Candidate$}
-   \State set tuned parameters according to $Candidate$
-   \State TrainLearner()
-   \State $scores \gets$TestLearner()
-   \State \% scocres = [pd, f, precision]
-   \State $s \gets scores[i] $ 
-   \State \% i determines the goal of tuning
-   \State \Return$s$
-\EndFunction
-\Function{GenNew}{$old, pop, cr, f$}
-  \State $a, b, c\gets threeOthers(pop,old)$ 
-  \State \% pick 3 other points from the population
-  \State $newf \gets \emptyset$
-  \For{$i=0 \to np-1$}
-       \If{$cr < random()$}
-         \State $newf$.append($old[i]$)
-                \Else
-                  \If{typeof(old[i]) == bool}
-                    \State $newf$.append(not $old[i]$)
-         \Else
-          \State $newf$.append(trim($i$,($a[i] + f * (b[i] - c[i]$))))
-          \State \%trim() will make new value fall in the range
-         \EndIf
-       \EndIf
-  \EndFor
-\EndFunction
-        \end{algorithmic}            
-\end{algorithm}
+\subsubsection{Differential Evolution: The Details}
+
+\input{algo}
+The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
+Note that, as we describe the algorithm,
+  any superscript number denotes a line in that algorithm.
+
+DE is an evolutionary algorithm; i.e. the next {\em NewGeneration} is learnt from
+a current {\em Population}.  If the new is no better than the current, then
+we lose one life, terminating when we run out of lives$^5$.
+
+Each candidate solution in the {\em Population}  
+is a pair of {\em (Tunings, Scores)}. In this paper, {\em Tunings} are selected from
+\fig{parameters} and {\em Scores} come from training a learner using those parameters
+and applying it to some test data$^{23-28}$.
+
+The premise of this algorithm is that the best way to mutate existing tunings
+is to {\em Extrapolate}$^{29}$
+between current solutions.  Three solutions $a,b,c$ are selected at random.
+For each tuning parameter $i$, at some probability {\em cr}, we replace  new tuning is created
+via:
+\bi
+\item For numerics: $a_i+f \times (b_i - c_i)$   where $f$ is a parameter
+controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
+value to the legal range min..max of that parameter.
+\item For booleans:  negate the current value$^{37}$.
+\ei
+The main loop of DE$^7$ runs over the {\em Population}, replacing old items
+with new {\em Candidate}s (if the new candidate is better than the old item).
+This means that, as the loop progresses, the {\em Population} is full of increasiningly
+more valuable solutions. This, in turn, also improves  the candidates (which are generated
+from the {\em Population}.
+
+For this experiments of this paper, we collect performance
+values from a data mining, from which a {\em Goal} function extracts one 
+performance value$^{27}$ (so we tun this code many times, each time with
+a different {\em Goal}$^2$).  Technically, this makes this a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
 
@@
 
-\section{Experiment}
-
-\subsection{Data Set}
-
-The data used in this study is from PROMISE repository. Ten software defect predicition data 
-sets are analyzed. They're {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene}, {\it 
-synapse}, {\it velocity}, {\it xalan} and {\it xerces}. Each of these data sets is composed of 
-several software modules with number of defects and code attributes. For more detailed 
-description of code attributes and the original data sets, please refer to  http://openscience.us/
-repo/
-
-\subsection{Experiment Design}
-
-The experiment aims at investigating whether tuning helps learners improve performance in 
-terms of accuracy measurement. We choose compare WHERE-based learner with and 
-without tuning parameters and two {\it significantly different} learners Random Forest and 
-CART according to \cite{lessmann2008benchmarking}. As mentioned above, we'd like to see 
-whether tuning will help change the rank of CART and make it comparable with Random 
-Forest.
-
-To evaluate accuracy performance of learners, several measurements are proposed to use, like 
+\begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{c c c c c c c c c c }\hline
+  Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
+\\\hline
+  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
+\\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
+\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
+\\  \end{tabular}
+   \caption{Ratios of defective instances in each experimental data set. 
+   E.g., the top left data set has 20 defective classes out of 125 total.
+   This paper runs one experiment for each column
+   shown in this figure. The {\em training} set is used by an untuned learner
+   to build a model, which is then tested on the {\em testing} data.
+   {\em Training} data is used by  differential evolution when it builds
+    a model (using one set of possible tunings) and that model is tested on {\em tunings}.
+    Finally, the best model from by DE is applied to {\em testing}. 
+   This information is continued  in \fig{data2}. 
+   }\label{fig:data1}
+\end{figure*}
+\begin{figure*}[!ht]
+\scriptsize
+\centering
+  \begin{tabular}{c c c c c c c c c c }
+  \hline\hline
+  Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
+\\\hline
+  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
+\\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
+\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
+\\  \end{tabular}
+
+   \caption{More ratios of  defective instances in each experimental data set. 
+   Same format as \fig{data1}.}\label{fig:data2}
+\end{figure*}
+
+\section{Experiments}
+
+The following experiments compare the performance of three learners, tuned and untuned, on 17
+sets of data.
+
+\subsection{Data Sets}
+
+Our defect data comes from the PROMISE repository\footnote{http://openscience.us/repo}.
+It pertains to 
+open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene}, {\it 
+synapse}, {\it velocity}, {\it xalan} and {\it xerces}.
+
+An important principle in data mining is not to test on the data used
+in training.  There are many ways to design a experiment that satisfies this principle:
+\bi
+\item  Leave-one-out experiments can be impractically slow for large data sets;
+\item Cross-validation can mix up older and newer data sets so it may well be that
+data from the {\em future} is used to train on {\em past data}.
+\ei
+To avoid these problems, we used an incremental learning approach. The following
+experiment ensures that the training data was created at some time before the test
+data.
+
+For this experiment, we looked for data sets that had at least three  
+releases in PROMISE:
+\bi 
+\item The {\em first} release was used for some  {\em training}, to collect a baseline
+   using an untuned learner.
+   \item
+   The {\em first} release was also used  on line 24 of Algorithm~\ref{alg:DE} to
+   build some model using some the tunings found in some {\em Candidate}.
+   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
+   test the model found on line 24.
+   \item Finally the {\em third} release was used to gather the performance statistics
+   reported below from (a)~the model generated by the untuned learner or (b)~the
+   best model found by differential evolution.
+
+   \ei
+ Note that the above ensures that all treatments get tested on the same final data set.
+
+ Some data sets have more than three releases and, for those data, we could run more
+ than one experiment. For example, {\em ant} has five versions in PROMISE so
+ we ran three experiments called V0,V1,V2:
+ \bi
+ \item AntV0: first,second,third = versions 1,2,3
+ \item AntV1: first,second,third = versions 2,3,4
+ \item AntV2: first,second,third = versions 3,4,5
+ \ei 
+These data sets are displayed in \fig{data1} and \fig{data2}.
+
+\subsection{Performance Scores}
+
+To evaluate accuracy performance of learners, several measurements are used.
+The 
 probability of  detection({\it pd}) and probability of false alarm ({\it pf})\cite{menzies2007data}, 
@@
 \section{Result}
-
-\begin{figure}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
-    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
-    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
-pd&71.4&1.2&60&4.4&0.1&44&7.1&0.2&36\\ 
-prec&82.8&1.4&59&3.9&0.1&39&7.4&0.2&37\\
-f&86.1&1.2&72&3.3&0.1&33&6.7&0.2&34
-  \end{tabular}
-  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
-  for different goals, or just running the ``off-the-shelf'' learner.}
-\end{figure}
-
-\begin{figure}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-\begin{tabular}{r|rrr}
-goal &	WHERE	&CART&	Random Forest\\\hline
-f	&15	&13	&9\\ 
-pd	&15	&16	&8\\ 
-prec&	14	&14	&8
-\end{tabular}
-\caption{How much slower is tuning vs just running the default
-settings of the learner? E.g. bottom right, tuning to increase
-precision with Random Forests is eight times slower than
-just running Random Forests.}
-\end{figure}
 
@@
 %%%%%%%%%%%%%%%% defectives and non-defectives for each datasets%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{c c c c c c c c c c }
-  \hline\hline
-  Dataset &ant&antV1&antV2&camel&camelV1&ivy&jedit&jeditV1&jeditV2
-\\\hline
-  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
-\\  tunning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
-\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
-\\  \end{tabular}
-   \caption{The percentage of defective instances in each experimental data set. For each experiment,  training, tuning and testing data are composed of single chronological data file}
-\end{figure*}
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{c c c c c c c c c c }
-  \hline\hline
-  Dataset &log4j&lucene&poi&poiV1&synapse&velocity&xerces&xercesV1
-\\\hline
-  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
-\\  tunning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
-\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
-\\  \end{tabular}
-
-   \caption{The percentage of defective instances in each experimental data set. For each experiment,  training, tuning and testing data are composed of single chronological data file}
-\end{figure*}
 

### 2015-03-15 tuningpredictor.tex
Updates from ShareLaTeX

@@
 
-\input{algo}
 The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
@@
 between current solutions.  Three solutions $a,b,c$ are selected at random.
-For each tuning parameter $i$, at some probability {\em cr}, we replace  new tuning is created
-via:
+For each tuning parameter $i$, at some probability {\em cr}, we replace
+the old tuning $x_i$ with $y_i$ found as follows:
 \bi
-\item For numerics: $a_i+f \times (b_i - c_i)$   where $f$ is a parameter
+\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
 controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
 value to the legal range min..max of that parameter.
-\item For booleans:  negate the current value$^{37}$.
+\item (For booleans) $y_i= \neg x_i$ (see line 37).
 \ei
@@
 
-\section{Experiments}
-
-The following experiments compare the performance of three learners, tuned and untuned, on 17
+\section{Experimental Design}
+
+The following experimental aims to compare the performance of three learners, tuned and untuned, on 17
 sets of data.
@@
 An important principle in data mining is not to test on the data used
-in training.  There are many ways to design a experiment that satisfies this principle:
+in training.  There are many ways to design a experiment that satisfies this principle.
+Some of those methods have certain drawbacks:
 \bi
-\item  Leave-one-out experiments can be impractically slow for large data sets;
+\item  Leave-one-out is too slow for large data sets;
 \item Cross-validation can mix up older and newer data sets so it may well be that
-data from the {\em future} is used to train on {\em past data}.
+data from the {\em future} is used to test on {\em past data}.
 \ei
@@
 For this experiment, we looked for data sets that had at least three  
-releases in PROMISE:
+releases in PROMISE. Note that the following ensures that all treatments 
+get assessed on the same test  set.
 \bi 
@@
    best model found by differential evolution.
-
    \ei
- Note that the above ensures that all treatments get tested on the same final data set.
-
 Some data sets have more than three releases and, for those data, we could run more
@@
 
-\subsection{Performance Scores}
-
-To evaluate accuracy performance of learners, several measurements are used.
-The 
-probability of  detection({\it pd}) and probability of false alarm ({\it pf})\cite{menzies2007data}, 
-the area under the receiver operating characteristics curve ({\it AUC})
-\cite{lessmann2008benchmarking}, precision and F measure\cite{zhang2007comments}. In this work, we 
-expect learners should identify as many defective modules as possible while avoiding false 
-alarm. Therefore, learners are evaluated by both of {\it pd} and {\it pf} simaltanieously. A single 
-measure, G-measure, defined as the harmonic mean of {\it pd} and $1-{\it pf}$  is used. The 
-G-measure value is between 0 and 1. The higher, the better.
-\begin{equation}
-G = \frac{2*(1-pf)*pd}{1-pf+pd}
-\end{equation}
-
-In this experiment, we divide one project data set into training, tuning 
-and testing datasets. In contrast to hold out way used in \cite{lessmann2008benchmarking, 
-menzies2007data}, we separate the data sets in order. Since learners are designed to predict 
-defects in future projects,  any randomly data set selection without taking into the time series 
-will not sufficient to evaluate the performance of predicting future. Since we have data from 
-10 different projects, each of which contains at least 3 evolutionary versions. We use the following policy 
-to select the data for experiments: for each project, we use every three chronological data files 
-to do testing, tuning and training in one experiment. For example, in ant project,
-we have versions of $ant1.3$, $1.4$, $1.5$, $1.6$, and $1.7$, which will generate data sets called
- $antV0$, $antV1$ and $antV2$ for three experiments.
-
-To investigates the impacts of parameters on learners, we use DE as the tuner and compare the G-measure 
-values of Where-based learner with and without tuning, CART with and without tuning and Random 
-Forests. Since the tuning time for Random Forests is very long, hopefully other researchers design
-new heuristics to speed up the tuning process for Random Forests.  For the time being, even though
-we don't tune Random Forests, if tuning help CART outperform Random Forests or improve itself performance ,
-we still could conclude that tuning is helpful and necessary when comparing learners.
-
-Besides the Where-based learner implemented by ourselves,  we use the CART and Random Forest modules 
-from scikit-learn \cite{scikit-learn} to do a comparative study.
-The parameters associated with different learners are listed in Fig.\ref{fig:parameters}.
-For each data set, run CART, naive Where-based learner and Random Forests with corresponding default values.
-Then using DE to tune corresponding parameters for CART and Where-based Learner,  and run them again with the optimal parameters from tuning process to test the performance.
-% This study ranks learners using the Scott-Knott procedure recommended by Mittas \& Angelis in their 2013
-% IEEE TSE paper~\cite{mittas2013ranking}.
-This method sorts a list of $l$ treatments with $ls$ measurements by their median score.
-It then splits $l$ into sub-lists $m,n$ in order to maximize the expected value of differences  in the observed performances before and after divisions.
-
-\section{Result}
+\subsection{Optimization Goals}
+
+Recall from Algorithm~! that we call differential evolution one time for each
+goal we are trying to optimize. This section lists those optimization goals.
+
+Let $\{A,B,C,D\}$ denote the
+true negatives, 
+false negatives, 
+false positives, and 
+true positives
+(respectively) found by a binary detector. 
+Certain standard measures can be computed from
+$A,B,C,D$: 
+\[
+\begin{array}{ll}
+pd=recall=&\frac{D}{B+D}\\
+pf=&\frac{C}{A+C}\\
+pf'=& 1 - pf\\
+prec=precision=&\frac{D}{D+C}\\ 
+ g = & \frac{2*pd*pf'}{pd + pf'}
+\end{array}
+\]
+All the above vary from zero to one. For $pf$, the {\em better} scores and {\em smaller}.
+For all other scores, the {\em better} scores are {\em larger}.
+
+The following results make no assumption that (e.g.) minimizing false alarms are 
+more important that maximizing recall or precision. That determination 
+should be make with respect to current business conditions:
+\bi
+\item
+For safety critical applications, low false alarm rates are irrelevant since the cost
+of overlooking any critical might outweigh the inconvenience of having to inspect a few more
+modules. 
+\item
+On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
+avoid the extra rework associated with false alarms.  In that business context, 
+managers might be willing to lower the recall somewhat in order to minimize the false alarms.
+\ei
+What the falling results do show is that once the optimization goal changes, so does everything
+else. Hence, it is important not to overstate  empirical results from software analytics.
+Rather, those results need to be expressed {\em along with} the context within which they are
+relevant.
+
+\section{Experimental Results}
+
+The introduction of this article made several claims about tuning defect predictor
+that use static code attributes. This section presents
+our results in order of those claims:
+\be
+\item Such tuning was easy (see \tion{easy});
+\item Such tuning is fast (see \tion{fast});
+\item Such tuning is can dramatically change the performance scores of a predictor;
+e.g. one result where precision changes from 2\% to 98\% (see \tion{precision});
+\item Tuning changes conclusions about what factors are most important (see \tion{import});
+\item Tuning changes conclusions about what learners are better than others (see \tion{rank};)
+\ee
+
+\subsection{Tuning is Easy}
+
+All the following results are generated with a a very simple optimizer
+(differential evolution). Further, our DE  is actually much simpler
+than a standard implementation. Recall from Algorithm~1 that
+DE explores a {\em Population} of size {\em np=10}. This is a very small population size:
+the standard recommendation is to set {\em np} to be ten times larger than the number
+of attributes being optimized~\cite{stron97}
+
+The results of this paper are presented
 
@@
 
-%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
-\renewcommand\arraystretch{1.2}
-\begin{figure*}[t!]
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-  \centering
-\begin{tabular}{|c|c|c|c|l|}
-\cline{1-5}
-\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
-\multicolumn{1}{c|}{Description} \\ \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
-& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
-& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
-split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
-one is for clustering and the second one is building prediction model. we explicitly call Where-
-clustering tree and CART tree, respectively}. \\ \cline{2-5} 
-& min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
-CART tree. \\ \cline{2-5} 
-& min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
-number of samples to be an internal node of the Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
-\end{tabular} \\ \cline{2-5} 
-    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
-& depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
-clustering tree. \\ \cline{2-5} 
-& depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
-& wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
-& treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
-\hline
-\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
-& max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5}
-
-& min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-& min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{1-5}  
-       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
-\cline{2-5} 
-& max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5} 
-& max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
-& min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-& min\_smaples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{2-5} 
-&  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
-\hline
-
-\end{tabular}
-    \caption {List of parameters to be tuned in Where-based learner and CART in scikit-learn.}
-\label{fig:parameters}
-\end{figure*}
-
-%%%%%%%%%%%%%%%% optimal parameters from tuning process%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[t!]
-%\scriptsize
-%  \centering
-%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-%	\hline
-%	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default & 
-%ant  & camel &ivy & jedit & log4j & lucene & poi & synapse & velocity & xalan & xerces \\ \hline
-%	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
-%	& threshold & 0.5 & 0.16 & 0.87 &0.89 & 0.68 &0.58 &0.62&0.06&0.09&1&0.64 &0.02\\ \cline{2-14} 
-%	& infogain & 0.33 & 0.33 & 0.49 &1&0.82 &0.12 &0.54&0.38&0.01&1&0.36&0.25\\ \cline{2-14} 
-%	& min\_sample\_size & 4& 8 &1 &1&5&8&1&5&9&1&5&5\\ \cline{2-14} 
-%	& min\_Size & 0.5& 1 & 0.67 & 0.99&1&0.63&1&0.95&0.59&1&0.88 &0.64\\ \cline{2-14} 
-%	& wriggle &
-%	& depthMin & 2 & 3 & 4 &1&1&2&1&1&5&1&1&3\\ \cline{2-14} 
-%	& depthMax & 10 & 8 &14 &16&18&1&16&13&5&9&18&20\\ \cline{2-14} 
-%	& wherePrune & False & True & True &False&False&False&True&True&False&True&False &True\\ \cline{2-14} 
-%	& treePrune & True& False & True &True&True&False&False&True&False&False&False &False\\ 
-%\hline
-%	\multirow{4}{*}{CART} 
-%	& threshold & 0.5 & 0.01 & 0.98 &0.94&0.67&0.47&1&0.01&0.12&0.9&0.57 &0.01\\ \cline{2-14} 
-%	& max\_feature & None &0.01 & 1 &0.29&0.28&0.53&0.13&0.01&0.01&0.87&0.47 &0.01\\ \cline{2-14} 
-%	%& max\_depth & None &27 & 46 &33&21&42&36&39&17&29&11&31\\ \cline{2-14} 
-%	& min\_sample\_split & 2 &6 &2 &13&17&12&2&14&12&7&16 &13\\ \cline{2-14} 
-%	& min\_smaples\_leaf & 1 &6 &3 &18&12&3&10&4&20&8&11&1\\ \hline  
-%    \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  
-%    & threshold & 0.5 & 0.06 &0.88 &1&0.73&0.41&0.81&0.11&0.16&1&0.63&0.29\\ \cline{2-14} 
-%	& max\_feature & None & 0.21 &0.98 &0.78&0.73&0.36&0.35&0.01&0.01&0.01&0.65 &0.89\\ \cline{2-14} 
-%	& max\_leaf\_nodes & None & 31 &35 &41&40&23&12&26&41&46&49&35\\ \cline{2-14} 
-%	& min\_sample\_split & 2 &12 &14 &2&5&8&11&1&16&1&9&20\\ \cline{2-14} 
-%	& min\_smaples\_leaf & 1 &6 &15 &2&17&3&9&19&8&2&14&9\\ \cline{2-14} 
-%	&  n\_estimators & 100 &111 &120 &89&68&64&84&107&100&79&113&50\\ \hline
-%
-%	\end{tabular}
-%    \caption {Optimal parameters from tuning process with objetive of G measure over different data sets.}
-%\label{fig:parameters}
-%\end{figure*}
-
-%%%%parameters for pd %%%%%%
-\begin{figure*}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
-& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
-& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
-& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
-& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
-& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
-& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
-& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
-& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
-& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
-& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
-& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
-& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
-& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
-& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of pd}
-\end{figure*}
-
-%%%%parameters for prec %%%%%%
-\begin{figure*}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.53& 0.48& 0.41& 0.35& 0.88& 1& 1& 0.9& 0.96& 0.57& 1& 1& 0.56& 0.57& 0.8& 0.26& 0.65\\ \cline{2-20}
-& infoPrune& 0.33& 0.68& 0.74& 0.31& 0.45& 0.78& 0.31& 0.53& 0.85& 0.04& 0.73& 0.54& 0.15& 1& 0.98& 0.23& 0.9& 0.19\\ \cline{2-20}
-& min\_sample\_size& 4& 3& 6& 5& 2& 1& 5& 7& 1& 7& 5& 2& 8& 1& 1& 1& 2& 2\\ \cline{2-20}
-& min\_Size& 0.5& 0.07& 0.23& 0.2& 0.21& 0.25& 0.54& 0.18& 0.36& 0.28& 0.51& 1.0& 0.33& 0.5& 0.84& 0.83& 0.04& 0.21\\ \cline{2-20}
-& wriggle& 0.2& 0.91& 0.77& 0.58& 0.85& 0.17& 0.66& 0.33& 0.88& 0.13& 0.72& 0.18& 0.07& 0.43& 0.63& 0.74& 0.18& 0.75\\ \cline{2-20}
-& depthMin& 2& 4& 2& 5& 2& 4& 2& 2& 2& 4& 2& 3& 4& 1& 5& 1& 2& 1\\ \cline{2-20}
-& depthMax& 10& 10& 14& 6& 13& 7& 16& 15& 14& 13& 19& 16& 9& 16& 14& 11& 13& 15\\ \cline{2-20}
-& wherePrune& False& True& False& True& True& True& True& True& True& True& True& True& True& True& True& False& True& False\\ \cline{2-20}
-& treePrune& True& True& True& True& True& True& True& False& False& False& True& False& True& True& False& False& False& False\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.76& 0.99& 0.86& 0.48& 1& 1& 1& 0.71& 0.62& 0.65& 1& 0.95& 0.64& 0.5& 1& 0.99& 1\\ \cline{2-20}
-& max\_feature& None& 0.09& 0.13& 0.05& 0.01& 0.01& 0.47& 0.01& 0.1& 0.63& 0.62& 0.44& 0.27& 0.28& 0.04& 0.75& 0.96& 0.21\\ \cline{2-20}
-& min\_samples\_split& 2& 4& 19& 9& 9& 17& 14& 14& 16& 14& 12& 17& 3& 10& 12& 20& 13& 6\\ \cline{2-20}
-& min\_samples\_leaf& 1& 15& 17& 8& 7& 1& 20& 1& 9& 12& 15& 10& 13& 7& 10& 4& 7& 20\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.92& 0.99& 0.71& 0.7& 1& 0.82& 1& 1& 1& 0.96& 0.73& 1& 0.76& 0.33& 1& 1& 0.98\\ \cline{2-20}
-& max\_feature& None& 0.23& 0.13& 0.46& 0.69& 0.37& 0.56& 0.71& 0.01& 1& 0.01& 0.85& 0.48& 0.34& 0.02& 0.01& 0.08& 0.62\\ \cline{2-20}
-& max\_leaf\_nodes& None& 12& 49& 23& 39& 10& 17& 20& 10& 10& 44& 37& 18& 35& 11& 31& 35& 28\\ \cline{2-20}
-& min\_samples\_split& 2& 18& 8& 14& 1& 11& 3& 2& 1& 4& 14& 2& 1& 13& 8& 18& 2& 13\\ \cline{2-20}
-& min\_samples\_leaf& 1& 11& 5& 11& 3& 2& 4& 20& 2& 2& 10& 3& 7& 7& 15& 6& 2& 9\\ \cline{2-20}
-& n\_estimators& 100& 130& 146& 66& 96& 50& 50& 136& 84& 83& 129& 51& 150& 99& 58& 88& 85& 61\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of prec}
-\end{figure*}
-
-%%%%parameters for F %%%%%%
-\begin{figure*}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.12& 0.78& 0.3& 0.01& 0.78& 1& 0.99& 0.44& 0.72& 0.21& 0.41& 1& 0.04& 0.7& 0.36& 0.66& 0.42\\ \cline{2-20}
-& infoPrune& 0.33& 0.58& 0.2& 0.41& 0.19& 0.82& 0.91& 0.35& 1& 0.85& 0.46& 0.24& 1.0& 0.85& 0.36& 0.48& 0.42& 0.82\\ \cline{2-20}
-& min\_sample\_size& 4& 6& 1& 1& 6& 8& 6& 7& 5& 1& 5& 8& 2& 7& 5& 3& 1& 1\\ \cline{2-20}
-& min\_Size& 0.5& 0.8& 0.75& 0.47& 0.01& 1& 0.64& 0.99& 0.43& 0.23& 0.47& 0.72& 1& 0.89& 0.69& 0.88& 0.38& 0.75\\ \cline{2-20}
-& wriggle& 0.2& 0.21& 0.7& 0.83& 0.25& 0.55& 0.01& 0.63& 0.93& 0.43& 0.33& 0.52& 0.32& 0.72& 0.1& 0.43& 0.34& 0.1\\ \cline{2-20}
-& depthMin& 2& 4& 5& 4& 3& 1& 6& 1& 4& 1& 1& 4& 1& 2& 2& 4& 5& 1\\ \cline{2-20}
-& depthMax& 10& 16& 11& 5& 19& 8& 10& 14& 19& 5& 6& 6& 16& 3& 11& 5& 18& 12\\ \cline{2-20}
-& wherePrune& False& True& True& True& False& True& False& False& True& True& True& False& True& True& False& True& False& True\\ \cline{2-20}
-& treePrune& True& False& True& True& True& True& False& False& True& False& False& False& True& True& False& False& True& True\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.01& 0.62& 0.13& 0.01& 1& 0.8& 0.7& 0.66& 0.72& 0.32& 0.09& 0.7& 0.01& 0.01& 0.91& 0.84& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.24& 0.88& 0.19& 0.01& 0.01& 0.8& 0.76& 0.28& 0.5& 0.22& 0.18& 0.01& 0.58& 0.01& 0.01& 0.3& 0.01\\ \cline{2-20}
-& min\_samples\_split& 2& 19& 3& 13& 5& 2& 10& 8& 9& 11& 12& 7& 10& 20& 5& 4& 14& 11\\ \cline{2-20}
-& min\_samples\_leaf& 1& 15& 18& 11& 13& 3& 13& 9& 10& 15& 8& 15& 15& 7& 10& 10& 4& 1\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.01& 0.49& 0.14& 0.01& 1& 1& 1& 1& 1& 0.66& 0.53& 1& 0.01& 0.21& 1& 1& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.89& 0.21& 0.01& 0.04& 0.81& 0.45& 0.01& 0.49& 0.01& 0.01& 0.12& 0.81& 0.01& 0.07& 0.01& 0.62& 0.61\\ \cline{2-20}
-& max\_leaf\_nodes& None& 21& 16& 49& 10& 26& 32& 39& 22& 10& 42& 24& 43& 38& 10& 10& 10& 20\\ \cline{2-20}
-& min\_samples\_split& 2& 11& 9& 19& 15& 6& 14& 6& 3& 4& 10& 18& 2& 8& 7& 10& 10& 16\\ \cline{2-20}
-& min\_samples\_leaf& 1& 6& 11& 13& 7& 16& 4& 2& 18& 2& 6& 19& 2& 9& 4& 17& 2& 5\\ \cline{2-20}
-& n\_estimators& 100& 88& 99& 124& 148& 56& 101& 116& 55& 122& 112& 75& 55& 92& 129& 58& 107& 121\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of F}
-\end{figure*}
-
-%%%%%%%%%%%%%%%% defectives and non-defectives for each datasets%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure*}[!th]
-%  \scriptsize
-%  \centering
-%	\begin{tabular}{|l|l|l|}
-%	\hline
-%	\multicolumn{1}{|c|}{Data Set} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}} Feature Selections\\ with  Default Parameters\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Feature Selection\\ with Tuning Parameters\end{tabular}} \\ \hline
-%	  ant  & mfa, lcom3, cam, ic, dam   & wmc, lcom3, cam, dam, npm, rfc  \\ \hline
-%	camel & cam, wmc, dit, mfa, rfc, loc & rfc, cam, loc, wmc, dam, dit, mfa, lcom3, npm\\ \hline
-%	ivy & cam, dit, dam, ic, lcom3& cam, dam, mfa\\ \hline
-%	jedit& mfa, dam, cam, dit, cbm, ic& mfa, loc, dit, dam, cam, wmc  \\ \hline
-%	log4j & lcom3, mfa, loc, ic, dit& mfa, wmc  \\ \hline
-%	lucene & mfa, lcom3, cam, dam, ic& wmc, lcom3, avg\_cc, rfc, ce, mfa, dam, npm, cam \\ \hline
-%	poi & mfa, dam, amc, lcom3, cbm, loc& loc, lcom3, cam, amc, dam                                                     \\ \hline
-%	synapse & dam, loc, mfa, cam & loc  \\ \hline
-%	velocity& dit, dam, lcom3, ic, mfa& mfa, cam, avg\_cc, loc, lcom3, cbo, dam, ic, rfc, lcom \\ \hline
-%	xalan  & mfa, cam, wmc, lcom3, rfc, dit & mfa, rfc, loc, dam, lcom3, wmc, npm \\ \hline
-%	xerces & cam, wmc, mfa, rfc, amc, loc& mfa, loc, cam, amc, avg\_cc\\ \hline
-%	\end{tabular}
-%	\caption{Features selection before and after tuning over objective of G values }
-%\end{figure*}
-
-%%%%%%%%%%%%%%%% feature selection over pd%%%%%%%%%%%%%%%%%%%%%
-
-\setlength{\tabcolsep}{3pt}
-\renewcommand\arraystretch{1.2}
-
-%%%%%%%%%%%%%% pd bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
-  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(pd) } \\
-  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
-\multicolumn{1}{c}{~}\\
-antV0 & 53 & {\rone} & 100 & {\rfour} & 38 &         & 100 & {\rfour} & 78 & {\rthree} & 97 & {\rfour}\\
-antV1 & 7 &         & 100 & {\rfour} & 39 & {\rone} & 100 & {\rfour} & 95 & {\rfour} & 100 & {\rfour}\\
-antV2 & 0 &         & 100 & {\rfour} & 37 & {\rone} & 100 & {\rfour} & 92 & {\rfour} & 100 & {\rfour}\\
-camelV0 & 0 &         & 100 & {\rfour} & 6 &         & 100 & {\rfour} & 66 & {\rthree} & 99 & {\rfour}\\
-camelV1 & 80 & {\rthree} & 100 & {\rfour} & 46 &         & 100 & {\rfour} & 80 & {\rthree} & 100 & {\rfour}\\
-ivyV0 & 93 & {\rtwo} & 100 & {\rfour} & 88 &         & 100 & {\rfour} & 95 & {\rtwo} & 100 & {\rfour}\\
-jeditV0 & 89 & {\rthree} & 100 & {\rfour} & 66 &         & 95 & {\rfour} & 96 & {\rfour} & 100 & {\rfour}\\
-jeditV1 & 75 & {\rtwo} & 100 & {\rfour} & 50 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-jeditV2 & 45 &         & 100 & {\rfour} & 36 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-log4jV0 & 46 & {\rone} & 100 & {\rfour} & 31 &         & 100 & {\rfour} & 88 & {\rfour} & 100 & {\rfour}\\
-luceneV0 & 81 & {\rthree} & 100 & {\rfour} & 48 &         & 100 & {\rfour} & 98 & {\rfour} & 100 & {\rfour}\\
-poiV0 & 89 & {\rtwo} & 100 & {\rfour} & 79 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-poiV1 & 2 &         & 100 & {\rfour} & 12 &         & 100 & {\rfour} & 89 & {\rfour} & 100 & {\rfour}\\
-synapseV0 & 0 &         & 100 & {\rfour} & 28 & {\rone} & 100 & {\rfour} & 90 & {\rfour} & 100 & {\rfour}\\
-velocityV0 & 100 & {\rfour} & 100 & {\rfour} & 86 &         & 100 & {\rfour} & 100 & {\rfour} & 100 & {\rfour}\\
-xercesV0 & 64 & {\rone} & 100 & {\rfour} & 46 &         & 100 & {\rfour} & 78 & {\rtwo} & 91 & {\rfour}\\
-xercesV1 & 15 &         & 100 & {\rfour} & 11 &         & 100 & {\rfour} & 68 & {\rthree} & 87 & {\rfour}\\
-%Albrecht  &   7         &   24   &   Projects from IBM   & 28 &     & 40 & {\rtwo} & 38 & {\rtwo} & 38 & {\rtwo} & 49 & {\rfour} \\
-%China      &   18       &   488   &   Projects from Chinese software companies   &   38   &  {\rtwo}  &   34   &       &   34   &       &   35   &  {\rone}   &   41   &   {\rfour}\\
-%Cosmic     &   y   &   y   &   Projects described in functiion points   &   98   &   {\rfour}   &   75   &       &   85   &    {\rtwo}   &   85   &   {\rtwo}    &   89   &   {\rtwo}\\
-%ISBSG10    &   y   &   y   &   From the ISBSG benchmark suite   &   56   &       &   62   &     &   126   &   {\rfour}   &   66   &   {\rone}   &   65   &   {\rone}\\
-%Kemerer    &   7   &   15   &   Large business applications   &   42   &  {\rtwo}  &   24   &   &   55   &  {\rfour} &   55   &   {\rfour}   &   55   &   {\rfour}\\
-%Kitchenham &    6   &   145   &  y    &   34   &   &   43   &   {\rthree}   &   34   &  &   43   &  {\rthree}  &   47   &  {\rfour}  \\
-%Maxwell    &   27  &   62  & Projects from commercial banks in Finland   &   57   &   {\rtwo}   &   56   &   {\rtwo}   &   47   &   &   53   &  {\rone} &   64   &   {\rfour}\\
-%Miyazaki   &   8   &   48 &Japanese software projects developed in COBOL   &   39   &       &   41   &   &   41   &    &   57   &   {\rfour}   &   57   &   {\rfour}\\
-%Telecom    &   3   &   18   &   Maintenance projects for telecom companies   &   23   &       &   26   &   {\rtwo}   &   31   & {\rfour}  &   31   &   {\rfour}   &   31   &   {\rfour}\\
-%Usp05      &   7   &  203  &  Collected from university student projects   &   30   &    &   50   & {\rfour} &   45   & {\rthree}  &   40   &   {\rtwo}  &   50   &   {\rfour}\\
-\end{tabular}
-\end{minipage}\begin{minipage}{.15\linewidth}
-\begin{tabular}{|p{\linewidth}|}\hline
-
-~\\
-
-{\bf KEY:}
-
-~\\
-
-pd percentile ranges:
-
-~\\
-
-80th to 100th = {\rfour}
-
-60th to 80th ~ = {\rthree}
-
-40th to 60th  ~ = {\rtwo}
-
-20th to 40th  ~ = {\rone}
-
-~\\
-
-An absent bar denotes\newline 0th to 20th percentile.
-
-~\\
-
-Percentiles computed  separately
-for each data set.\\\hline
-\end{tabular}
-\end{minipage}
-\caption{Median pd values in tune once and test ten times experiment. 
-Gray bars  show  pd values
-discretized into 20th percentiles ranges from min to max.
-All data available from http://openscience.us/repo/effort.
-}\label{fig:nonc}
-\end{figure*}
-
-%%%%%%%%%%%%%% pd bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%% precision bars%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-\renewcommand{\baselinestretch}{0.8}
-
-\scriptsize  
-\begin{tabular}{r|r@{~}l@{~}|r@{~}l|r@{~}l|r@{~}l|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
-      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forests}         \\\hline
-  Data set   &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{Naive}  &   \multicolumn{2}{c}{Tuned}\\\hline
-
-antV0 & 30 &         & $\bigstar$ 89 & {\rfour} & 27 &         &$\bigstar$ 89 & {\rfour} & 40 & {\rone} &$\bigstar$ 89 & {\rfour}\\
-antV1 & 32 &         &$\bigstar$ 74 & {\rfour} & 41 & {\rone} &$\bigstar$ 74 & {\rfour} & 57 & {\rtwo} &$\bigstar$ 74 & {\rfour}\\
-antV2 & 78 & {\rfour} &$\bigstar$ 78 & {\rfour} & 52 &         & 67 & {\rthree} & 66 & {\rtwo} & 50 &        \\
-camelV0 &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour} & 26 &         & 37 &         &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour}\\
-camelV1 & 22 &         &$\bigstar$ 81 & {\rfour} & 23 &         & 25 &         & 28 &         & 28 &        \\
-ivyV0 & 16 &         & 23 & {\rthree} & 18 & {\rone} &$\bigstar$ 25 & {\rfour} & 18 & {\rone} & 19 & {\rone}\\
-jeditV0 & 35 &         & 75 & {\rthree} & 49 & {\rone} &$\bigstar$ 86 & {\rfour} & 52 & {\rone} & 50 & {\rone}\\
-jeditV1 & 24 &         &$\bigstar$ 87 & {\rfour} & 28 &         & 62 & {\rthree} & 36 &         & 42 & {\rone}\\
-jeditV2 & 2 &         &$\bigstar$ 98 & {\rfour} & 3 &         & 4 &         & 5 &         & 6 &        \\
-log4jV0 & 94 &         &$\bigstar$100 & {\rfour} & 97 & {\rtwo} & 98 & {\rthree} &$\bigstar$ 100 & {\rfour} &$\bigstar$100 & {\rfour}\\
-luceneV0 & 61 &         & 71 & {\rtwo} & 67 & {\rone} &$\bigstar$ 78 & {\rfour} & 69 & {\rtwo} & 70 & {\rtwo}\\
-poiV0 & 70 &         &$\bigstar$ 92 & {\rfour} & 77 & {\rone} & 79 & {\rtwo} & 79 & {\rtwo} & 75 & {\rone}\\
-poiV1 & 100 & {\rfour} &$\bigstar$ 89 & {\rfour} & 73 & {\rtwo} &$\bigstar$ 89 & {\rfour} & 86 & {\rthree} & 36 &        \\
-synapseV0 & 66 & {\rthree} & 0 &         & 71 & {\rthree} &$\bigstar$ 95 & {\rfour} & 59 & {\rthree} & 67 & {\rthree}\\
-velocityV0 & 34 &         & 34 &         & 34 &         &$\bigstar$ 45 & {\rfour} & 40 & {\rtwo} & 41 & {\rthree}\\
-xercesV0 & 13 &         &$\bigstar$ 85 & {\rfour} & 14 &         & 73 & {\rfour} & 16 &         & 13 &        \\
-xercesV1 &$\bigstar$ 56 & {\rfour} & 26 &         & 55 & {\rfour} & 26 &         & 41 & {\rtwo} & 26 &        \\
-\end{tabular}
-
-\caption{Precision values in tune and naive runs.
-All data available from http://openscience.us/repo/effort. {\bf KEY:}
-  percentile ranges:\newline
-80th to 100th= {\rfour};
-60th to 80th= {\rthree}; 
-40th to 60th= {\rtwo};
-20th to 40th= {\rone};
-an absent bar shows  0th to 20th.
-Percentiles computed  separately
-for each row.
-
-}\label{fig:nonc}
-\end{figure}
-
-%%%%%%%%%%%%%% precision bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\begin{minipage}{0.81\linewidth}
-\begin{tabular}{r@{~}|r@{~}l|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|@{~}r@{~}l|r@{~}l|@{~}r@{~}l}
-  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(F ) } \\
-  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
-\multicolumn{1}{c}{~}\\
-ant0 &$\bigstar$ 39 & {\rfour} & 26 & {\rone} & 32 & {\rtwo} & 25 &         & 25 &         & 22 &        \\
-ant1 & 11 &         &$\bigstar$ 85 & {\rfour} & 40 & {\rone} & 49 & {\rtwo} & 39 & {\rone} & 33 & {\rone}\\
-ant2 & 0 &         &$\bigstar$ 86 & {\rfour} & 44 & {\rtwo} & 51 & {\rtwo} & 52 & {\rthree} & 56 & {\rthree}\\
-camel0 & 0 &         &$\bigstar$ 28 & {\rfour} & 9 & {\rone} &$\bigstar$ 28 & {\rfour} & 34 & {\rfour} & 31 & {\rfour}\\
-camel1 & 34 & {\rthree} &$\bigstar$ 35 & {\rfour} & 31 &         & 33 & {\rtwo} & 33 & {\rtwo} & 30 &        \\
-ivy0 & 27 &         & 30 & {\rone} & 30 & {\rone} & 32 & {\rthree} &$\bigstar$ 35 & {\rfour} &$\bigstar$ 35 & {\rfour}\\
-jedit0 & 50 &         & 55 & {\rtwo} & 56 & {\rtwo} & 55 & {\rtwo} &$\bigstar$ 61 & {\rfour} & 60 & {\rfour}\\
-jedit1 & 37 & {\rone} & 34 &         & 36 &         & 47 & {\rfour} & 45 & {\rthree} &$\bigstar$ 48 & {\rfour}\\
-jedit2 & 4 &         &$\bigstar$ 99 & {\rfour} & 5 &         & 9 &         & 9 &         & 11 &        \\
-log4j0 & 62 & {\rfour} & 7 &         & 47 & {\rthree} &$\bigstar$ 64 & {\rfour} & 53 & {\rfour} & 45 & {\rthree}\\
-lucene0 & 70 & {\rthree} & 73 & {\rfour} & 56 &         &$\bigstar$ 75 & {\rfour} & 70 & {\rthree} &$\bigstar$ 75 & {\rfour}\\
-poi0 &$\bigstar$ 78 & {\rfour} & 63 &         & 74 & {\rthree} & 70 & {\rtwo} & 73 & {\rthree} & 72 & {\rtwo}\\
-poi1 & 5 &         &$\bigstar$ 78 & {\rfour} & 21 & {\rone} &$\bigstar$ 78 & {\rfour} & 76 & {\rfour} &$\bigstar$ 78 & {\rfour}\\
-synapse0 & 0 &         & 2 &         & 40 & {\rthree} &$\bigstar$ 56 & {\rfour} & 52 & {\rfour} & 55 & {\rfour}\\
-velocity0 & 51 &         & 51 &         & 49 &         & 51 &         & 53 & {\rone} &$\bigstar$ 59 & {\rfour}\\
-xerces0 & 22 & {\rthree} & 20 & {\rone} & 21 & {\rtwo} & 18 &         & 23 & {\rfour} & 22 & {\rthree}\\
-xerces1 & 23 & {\rone} & 2 &         & 18 & {\rone} & 36 & {\rtwo} & 68 & {\rfour} &$\bigstar$ 71 & {\rfour}\\
-\end{tabular}
-\end{minipage}\begin{minipage}{.15\linewidth}
-\begin{tabular}{|p{\linewidth}|}\hline
-
-~\\
-
-{\bf KEY:}
-
-~\\
-
-F percentile ranges:
-
-~\\
-
-80th to 100th = {\rfour}
-
-60th to 80th ~ = {\rthree}
-
-40th to 60th  ~ = {\rtwo}
-
-20th to 40th  ~ = {\rone}
-
-~\\
-
-An absent bar denotes\newline 0th to 20th percentile.
-
-~\\
-
-Percentiles computed  separately
-for each data set.\\\hline
-\end{tabular}
-\end{minipage}
-\caption{Median F values in tune once and test ten times experiment. 
-Gray bars  show  F values
-discretized into 20th percentiles ranges from min to max.
-All data available from http://openscience.us/repo/effort.
-}\label{fig:nonc}
-\end{figure*}
-
-%%%%%%%%%%%%%% F bars end%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%  counts of features for different goals%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{c|c c|c c|c c|c c| c c }
-
-    & \multicolumn{2}{c|}{Pd} &  \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{F} &  \multicolumn{2}{c|}{SUM}\\
- &&&&&&&&\\
-Features& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-& \begin{sideways}naive\end{sideways}
-& \begin{sideways}tuned\end{sideways}
-\\\hline
-noc&	&	&	&	&	&	&	&	&	\\
-ca&	&	&	&	1&	&	&	&	1&	\\
-max\_cc&	&	&	&	1&	&	&	&	1&	\\
-moa&	&	&	&	1&	&	1&	&	2&	\\
-avg\_cc&	&	&	&	3&	&	2&	&	5&	\\
-cbo&	&	&	&	1&	&	3&	&	4&	\\
-npm&	&	&	&	2&	&	4&	&	6&	\\
-lcom&	&	&	&	1&	&	4&	&	5&	\\
-ce&	&	&	&	3&	&	2&	&	5&	\\
-amc&	4&	&	4&	1&	4&	5&	12&	6&	\\
-cbm&	6&	&	4&	1&	4&	2&	14&	3&	\\
-rfc&	4&	&	4&	4&	4&	9&	12&	13&	\\
-wmc&	5&	&	5&	3&	5&	7&	15&	10&	\\
-ic&	8&	1&	9&	3&	8&	8&	25&	12&	\\
-dit&	8&	1&	8&	5&	7&	8&	23&	14&	\\
-cam&	9&	&	9&	3&	9&	8&	27&	11&	\\
-loc&	9&	1&	9&	4&	9&	8&	27&	13&	\\
-lcom3&	9&	&	8&	5&	8&	13&	25&	18&	\\
-dam&	14&	&	14&	6&	14&	12&	42&	18&	\\
-mfa&	16&	3&	16&	6&	16&	16&	48&	25&	\\
-
-  \end{tabular}
-    \caption{Counts of features selected by different goals.
-For each goal, the numbers in right and left columns represent the counts of features selected for all the data sets with and without tuning processes.}
-\end{figure}
-
-%%%%time for G %%%%%%
-
-\section{Discussion}
-Data torturing, on not? Offer insight on the complexities of data sets, demanding
-that before they are used, we spend more time describing the context of use. Not offering
-conclusions that are over-stated. Taking care to precisely describe the boundaries of a 
-conclusion. While at the same time showing how to makde better conclusions on new
-data, whenever it arrives. And ensuring that those new conclusions are tuned
-to the goals of the business users who are funding the analysis and will use its results.
-
-\begin{figure}[!t]
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-Some goals related to aspects of defect prediction:
-\be
-\item
-Mission-critical systems are risk averse and may accept very high false alarm rates,
-just as long as they catch any life-threatening possibility. That is, such projects
-do not care about effort- they want to {\em maximize recall} regardless of any impact
-that might have on the false alarm rate.
-\item
-Cost averse managers may accept lower probabilities of
-detection (the recall measure), just as long as they {\em do not waste budgets on false alarms}. This community
-seeks to {\em minimize false alarms} while maintaining {\em some level of adequate recall}.
-\item  Suppose a new hire wants
- to impress their manager. That 
- new hire might want to ensure that no result presented to  management contains  true negative;
-i.e. they wish to {\em maximize precision}.
-\item
-Some communities do not care about   low precision,
-just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction 
-{\em selectivity} and offer an
-extensive discussion of the merits of this measure~\cite{hayes06}.
-\ee
-\\\hline
-Beyond defect prediction are other goals that combine defect prediction with other economic
-factors:
-\be
-\setcounter{enumi}{4}
-\item
-Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
-say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
-that contain the most bugs.
-\item In other work, Yin et al. are concerned about
- {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
-These bugs occur  when (say) developers try to fix parts of the code
-where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
-for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
-\item In {\em Better-faster-cheaper}, we seek  project changes that lead
-to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
-\item {\em  Rush-to-market} is another economic-based optimization measure.
-A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
-as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
-in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
-used to subsequently fix any issues with version 1.0)~\cite{huang06}.
-\ee
-\\\hline
-All the above measures relate to the tendency of a predictor to find something. Another style
-of measure would be to check the {\em variability} of that predictor:
-\be
-\setcounter{enumi}{8}
-\item
-In their study on reproducibility of SE results,
- Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
-Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
-\ee
-\\\hline
-\end{tabular}
-\caption{Reasoning about software many have many different goals including the nine shown here. Many of
-these goals are defined in terms of 
-\fig{criteria}.
-}\label{fig:goals}
-\end{figure}
-\fig{goals} lists other performance measures that we have seen at client sites or in the literature. Note that:
-\be
-\item This list is very long.
-\item This list keeps growing.
-\ee As to this second point,
-often when we work
-with new clients, they surprise us with yet another domain-specific criteria that is important for the business.
-That is, neither \fig{criteria} or \fig{goals} is not a complete list of all possible assessment criteria.
-
-Our reading of the defect prediction literature is that most papers only explore a small subset of 
- \fig{criteria} or \fig{goals}. We think this is a mistake and researchers should more to a more general
-framework where they explore a wide and changing set of evaluation criteria. 
-Hence, this paper.
-
 \end{document}
-
-O 
-PEEKING2's PCA tool used an accelerated   principle component analysis that synthesises  new
-attributes $e_i, e_2,...$
-that extends across the dimension of greatest  variance in the data  with attributes $d$.  
-PCA  combines
-redundant  variables into a smaller set of variables  (so $e \ll d$) since those
-redundancies become (approximately) parallel lines
-in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
-can ignore $j$ 
-since effects that change over $j$ also
-change in the same way over $i$.
-PCA is also useful for skipping over noisy variables from $d$-- these
-variables are effectively ignored since    they  do not contribute to the variance in the data.
-
-In the case of WHERE, this reduction incluFor CART, the measure of compression is
-
-XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores.
-Given that, the next question becomes ``what performance scores do you want?''.
-This is an interesting issue since there is no single best answer.
-XXX
-
-How ``true'' are the  models generated by software analytics?
-Suppose we use a model generated from software project data to, for example,
-assess the relative value of OO metrics vs procedural metrics for predicting
-project defects. Are we reporting ``truth'' in any sense of the word? And for how
-many other projects  and how many kinds of questions might we find that same ``truth''?
-
-This is not some abstract question-- it is an open and pressing matter.
-Any reading of the recent proceedings of FSE, ICSE, ASE, etc will discover hundreds
-of papers using data miners to make conclusions about software projects. 
-For example, some  analysts have made conclusions
-about 
-{\em what attributes
-have most influence on a software project}.
-For example, in 2013,
-Rahman et al
-\cite{rahman2013how}  used results from logistic regression to conclude
-that code metrics are generally less useful than process
-metrics for  predicting defects from static code analysis.  
-In the same year, Bell et al. (who also used negative binomial regression) argued that
-software defect prediction was not improved by adding attributes relating to the social
-structure of programmer teams~\cite{bell2013limited}.
-
-@article{bell2013limited,
-  title={The limited impact of individual developer data on software defect prediction},
-  author={Bell, Robert M and Ostrand, Thomas J and Weyuker, Elaine J},
-  journal={Empirical Software Engineering},
-  volume={18},
-  number={3},
-  pages={478--505},
-  year={2013},
-  publisher={Springer}
-}
-
-The results of this paper offer a very different picture  to recent prominent results from prior authors.
-Lessmann et al.~\cite{lessmann2008benchmarking}, Rahman et al.~\cite{rahman2013how} and Arshiholm et al.~\cite{arisholm06} argue that when it comes to defect prediction, different learners often
-produce statistically similar results. For this reason  Rahman et al. only present results their logistic
-regression results, commenting that ``dor brevity, only results from LR are
-presented; other learning models give similar results''~\cite{rahman2013how}. Note that those prior results,
-where most learners achieved the same results, arose from the default parameter settings from those learners.
-
-Our results, on the other hand, come from tuning a data miner's parameters. In those results,
-we found that the choice of parameters had dramatic impacts on data mining performance.
-For example, we show results below where:   
-\bi 
-\item 
-Tuning improved precision values from  2\% to 98\%; or
-\item 
-Tuning improved false alarm values from 69\% to 0\%; or
-\item 
-Tuning improved recall values from 0 to 100\%; or
-\item 
-Tuning improved the f-measure (which is the harmonic mean of recall and precision) from 0 to 86\%.
-\ei   
-In terms of changing SE research methodologies, an important aspect of these results is that usually XXXX always different.
-cannot determine without experimentation which learner will, after tuning, yield the best results for a particular data set.
-Hence it is no longer viable for researchers to trust the recommendations
-of other researchers working with other data sets that ``data miner XYZ is best''. Before
-offering a conclusion about a particular data set, researchers need now augment  their 
-papers with preliminary tuning studies (the results of which select the tunings+data miners to be used
-to make conclusions for the second half of their paper).
-
-The good news is that such tuning is not an arduous task. The differential evolution algorithm 
-used in this study is wdiely available in many standard  toolkits and languages\footnote{See the long list at
-www1.icsi.berkeley.edu/~storn/code.html.}
-And even if somehow those tools and prior implementations are not workable at a local site, 
-differential evolution is very simple to code. Hence, it can readily and quickly implemented.
-
-When we discuss these results with colleagues, one response we get is ``enough of the parameter tuning.. lets use simpler methods''. 
-While we understand their motivation (to keep thing simple), software project
-data cannot necessarily be condensed to (say) a simple univariate analysis that
-reports how one independent variable effects a dependent variable.
-Such a simplistic analysis can miss significant interaction
-effects when multiple factors combine to effect the target variable. For example,
-one of the base results in defect prediction is that predictors formed from
-a single variable perform much worse than those can combined multiple variables (three or more)~\cite{me07b}.
-
-If those results come from an analysis of a complex interactions between attributes,
-then some kind of data mining method\footnote{By this term we mean the
-full gamut of methods for large-scale analysis of
-data including statistical
-parametric methods (that assume a particular distribution then strive to learn the parameters of that distribution); kernel methods;
-dimensionality  synthesis methods; 
-instance weighting schemes; feature subset selection methods
-outlier removal methods;
-decision tree learners; neural networks; and instance-based
-methods including clustering and/or   case-based reasoning.} then there is the
-{\em tuning problem} of how to set the myriad of parameters that 
-control the learner.
-
-\item
-What data miners are better than others for particular tasks
-in software analytics. 
-\ei
-
-Also, in 2007, one of us (Menzies) claimed that Naive Bayes
-classifiers with a certain lind of pre-processor were better than entropy-based decision trees for defect prediction~\cite{me07b}.
-Similarly, in 2008 Lessmann et al.~\cite{lessmann2008benchmarking} argued  that 
-Random Forests~\cite{brieman00} and CART ~\cite{brieman84} work best, worst for learning software defect predictors from
-static code attributes. Similar claims that one learner was better than another
-have been made by many other authors; e.g.
-
-We write to suggest that all those conclusions may be wrong or, at the very most,
-correct within a very limited context. At the very least, the conclusions
-of those papers (and literally dozens of similar papers, include several
-of our own~\cite{me02e,me02k,me03a,me06d,me07b}) need to be revisited
-in light of this paper's results on the effects of tuning on data miners.
-
-Machine learners
-are controlled by parameters that decide (e.g.) when to stop recursively
-dividing data into smaller section or (e.g.) what thresholds for errors are small
-enough to be acceptable. When used ``off-the-shelf'', analytst
-use default settings for those parameters. We find that  a 
-simple optimization scheme (differential evolution) can find much
-better tunings that can dramatically change the performance of
-the learned model (measured in terms of false alarm rates, recall,
-precision, f-measure, and g-measure).  From this first result,
-we conclude that {\bf parameter tuning with some optimizer such as differential
-evolution should become standard practice}.
-
-Our next observation is that observations about miner1 being better
-than miner2 do not survive tuning. To be specific: given some
-ranking of data miners for some task such as defect prediction,
-we find that tuning can reverse those rankings such that the worst untu
-
-Tuning the data miners with different evolution takes some
-times (around an order of magnitude slower than the learning), but not an impractically slower amount of time. Further, when we look at what
-attrub
-
-Our reading of the
-
-good news:
-\bi 
-\item Tuning is easy (but one measure, at least an order of magnitude easier than 
-standard optimization problems)
-\item Tuning can dramatically improve the performance of a learner (in one case, from recalls
-of zero to 70\%)
-\ei
-interesting news
-\bi 
-\item tunings different for different data sets.
-\ei 
-bad news:
-\bi
-\item Tuning also changes what was learned
-\bi
-\item Supposedly ``bad'' learners start working much better than supposedly ``best'' learners;
-\item The models used in the tuned models were very different to those used in the untuned learners.
-\ei 
-\ei 
-and we reflect on that model, are we
-
-will it reveal the `1`t
-A standard approach to software analutics
-Software has becoming a large and complex system and delivering reliable and quality 
-software is imperative for development teams. Empirical study shows that the longer the 
-defects exist in software systems, the more the cost of time and money it will take to fix it 
-\textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
-defects in their system as early as possible. Defect prediction has been investigated 
-extensively in industrial and academia during the past two decades. As an important research 
-field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, 
-menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} 
-over static code features of software system has been demonstrated to be a way to predict 
-which models are more likely to contain defects.
-
-Classification is an important approach to predict whether some modules in the projects are 
-defective or non-defective. The general idea is to train the learners by using parts of data 
-sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with 
-remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed 
-based an different data mining classifiers, including CART, Random Forest 
-\cite{guo2004robust},  Naive Bayes\cite{menzies2007data},Logistic Regression 
-\cite{khoshgoftaar1999logistic}. During the past years, authors claimed that their new 
-defective learner outperformed others according to their experiment and statistical analysis. 
-To evalute those learners objectively in terms of accuracy, Lessmann et al
-\cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
-\begin{figure}
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-When applying case-based reasoning, researchers use different settings including how they measure dis- tance between instances (examples include the Euclidean measure, Manhattan and Chebyshev).
-Other settings control if numerics are normalized min..max to 0..1, before they are used in the distance measure.
-
-Another set of settings refers to how to handle non-numeric distances or missing values.
-Some researchers delete training data with missing information while others compute missing values via, say, median values.
-
-After feature selection comes instance selection.
-There are many settings for instance selectors such as use outlier removal or prototype generation.
-Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
-The next set of settings concern how many neighbors to use (k=1,2,5,etc).
-Some researchers set ``k'' in dynamic pre-learning phase that checks the training data to find what ``k'' works best for that data.
-
-Once the neighbors are known, the next settings control how to summarize their information.
-Some researchers use means, other use medians, or a weighted sum that uses the distance of the neighbor from the test instance (and that weighting might be determined by some kernel such as uniform, triangular, Gaussian, cosine, or Epanechnikov).
-Researchers may use other settings to control different pre-processors.
-E.g.
-some discretize numeric values (via equal width or equal frequency) using some binning policy (and researchers differ on how many bins are best).\\\hline
-\end{tabular}
-\caption{Some tunings for SE predictive systems.
-Found by this author while preparing this proposal in a day of reading the SE predictive modeling literature on case-based reasoning and effort estimation.
-Note that other kinds of prediction systems (decision trees, neural nets, linear repression, etc) have yet more adjustable design options.}\label{fig:adjust}
-\end{figure}
-
-domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
-with $\alpha = 0.05$, they concluded that the predictive accuracy of most learners didn't differ 
-significantly in terms of the area under the receiver operating characteristics curve(AUC). 
-Furthermore, according to the fig.2 in \cite{lessmann2008benchmarking}, Random Forest is 
-significantly better than CART. Lessmann's paper motivates us to investigate whether tuning 
-those CART's parameters by search-based software engineering method can improve the 
-performance. Even though Lessmann considered unpruned tree and pruned tree, They didn't 
-consider other possible parameters in CART which would have impact on the structure of 
-trees, like the depth of the tree, the maximum and minimum number of leafs of the tree.
-
-Software metrics are the core of all the defective prediction model. Many types of metics
-are used to build models, like process metrics, McCabe and Halsted metrics  and CK metrics.
-By building prediction modes across 85 releases of 12 open source projects, Rahman et al
-\cite{rahman2013how}  concluded that code metrics are generally less useful than process
-metrics for prediction. And also the code metrics don't change much from release to release
-and lead to stagnation in the prediction model. In \cite{Radjenovi?20131397}, Radjenovi? et al
-\cite{Radjenovi?20131397} reviewed 106 papers regarding software prediction metrics. They found
-that CK objected-oriented and process metrics have been reported to be more successful in
-finding defects compared to traditional size and complexity metrics. Moreover, not all the CK
-metrics perform well equally. The best metrics from CK are CBO, WMC and RFC based on their 
-observation. It seems that the relationship between software metrics and defective prediction is
-still an open question and need to be addressed. This motivates us to see : whether the impact
-rankings of those metrics will change after tuning parameters
-is applied to model learners.
-
-What's the problem in those result?
-
-RQ:
-
-briefly describe our study and  our result; observation
-
-structure of this paper.
-
-Note that we do not claim that differntial evolution is the {\em best} way to
-optimize data miners for defect prediction. In this paper, we only show that
-differential evolution is {\em simple}, {\em fast} and {\em effective} at that task. As to   finding the best optimizer for defect prediction, that task would require
-the input of many researchers (and we hope this paper inspires
-much subsequent work into that issue).
 

### 2015-03-15 deltas.sh
asda

@@ -1,0 +1,66 @@
+#WHERE		CART		RF
+precision() { cat<<EOF | sed 's?\\t\\t?\\t?g' | cat -n 
+-30		-24		-43
+-10		-5		-15
+-2		-1		-3
+0		1		-2
+0		3		-2
+0		3		-1
+5		3		0
+6		6		0
+6		7		0
+7		7		1
+13		15		1
+40		16		3
+42		16		5
+59		29		11
+63		33		19
+72		58		21
+96		62		50
+EOF
+	    }
+#WHERE				CART                             RF
+F() { cat <<EOF | sed 's?\\t\\t\\t?\\t?g' | cat -n 
+-14				-43				-27
+-14				-6				-10
+-6				-2				-4
+-5				-1				-4
+-4				1				-3
+-2				2				-2
+0				5				-2
+0				6				-2
+2				6				0
+4				8				0
+5				12				1
+6				13				2
+7				16				2
+14				19				2
+28				19				4
+73				35				5
+87				57				5
+EOF
+}
+precision > /tmp/precision.dat
+F > /tmp/F.dat
+
+draw() {
+gnuplot<<EOF
+set key top left
+set output "$1.eps
+set title "Tuning's improvements to $1"
+set terminal postscript eps color "Helvetica" 15
+set size 0.5,0.5
+set yrange [-50:100]
+set ytics (-50,0,50,100)
+set xlabel "Improvements in 17 experiments, sorted"
+set xtics (1,4,8,12,16)
+set arrow 1 from 1,0 to 17,0 nohead
+plot "/tmp/$1.dat" using 1:2 title "WHERE"  with linesp,\
+     "/tmp/$1.dat"  using 1:3 title "CART" with linesp,\
+     "/tmp/$1.dat"  using 1:4 title "Random Forest" with linesp,
+EOF
+ps2pdf -dEPSCrop $1.eps 
+}
+
+draw precision 
+draw F

### 2015-03-15 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \usepackage{cite}
+
 \usepackage{rotating}
@@
 \newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
-\newcommand{\rone}{\crule{1mm}{1.95mm}}
-\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
-\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
-\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
-\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
+%\newcommand{\rone}{\crule{1mm}{1.95mm}}
+%\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
+%\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
+%\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
+%\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
 \newcommand{\quart}[3]{\begin{picture}(100,6)%1
@@
 \definecolor{LightGray}{gray}{0.975}
+
+\newcommand{\rone}{}
+\newcommand{\rtwo}{}
+\newcommand{\rthree}{}
+\newcommand{\rfour}{} 
+\newcommand{\rfive}{}
 
@@
 more important that maximizing recall or precision. That determination 
-should be make with respect to current business conditions:
-\bi
+should be make with respect to current business conditions. 
+\be
 \item
-For safety critical applications, low false alarm rates are irrelevant since the cost
-of overlooking any critical might outweigh the inconvenience of having to inspect a few more
+For safety critical applications, high false alarm rates may be not be of concern since the cost
+of overlooking any critical can outweigh the inconvenience of having to inspect a few more
 modules. 
@@
 managers might be willing to lower the recall somewhat in order to minimize the false alarms.
-\ei
-What the falling results do show is that once the optimization goal changes, so does everything
-else. Hence, it is important not to overstate  empirical results from software analytics.
+\ee
+These two examples are just the tip of the iceberg. There are many, many other goals we might consider
+for our defect predictors.
+All the above measures relate to the tendency of a predictor to find something. Another style
+of measure would be to check the {\em variability} of that predictor.
+For example,
+in their study on reproducibility of SE results,
+ Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
+Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
+Further, 
+there exist other goals that combine defect prediction with other economic
+factors.
+For example, Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
+say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
+that contain the most bugs.
+In other work, Yin et al. are concerned about
+ {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
+These bugs occur  when (say) developers try to fix parts of the code
+where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
+for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
+Also, in {\em Better-faster-cheaper}, we seek  project changes that lead
+to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
+Another  {\em  rush-to-market} approach is yet another economic-based optimization measure.
+A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
+as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
+in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
+used to subsequently fix any issues with version 1.0)~\cite{huang06}.
+
+There is insufficient space in this paper to explore all the above optimization goals.
+What we can do, however, is show examples of how  changing  optimization goals can also change 
+the conclusions made from that learner on that data. Those examples only relate to precision, recall, and the F-measure
+but the general principle (that the search bias changes the search conclusions) would hold for all the goals
+listed in the previous paragraph.  Hence, we warn that it is important not to overstate  empirical results from software analytics.
 Rather, those results need to be expressed {\em along with} the context within which they are
-relevant.
+relevant (and by ``context'', we mean the optimization goal).
 
@@
 that use static code attributes. This section presents
-our results in order of those claims:
+support for those claims:
 \be
-\item Such tuning was easy (see \tion{easy});
-\item Such tuning is fast (see \tion{fast});
-\item Such tuning is can dramatically change the performance scores of a predictor;
+\item  Tuning  can  improve the performance scores of a predictor;
 e.g. one result where precision changes from 2\% to 98\% (see \tion{precision});
+\item Tuning changes conclusions about what learners are better than others (see \tion{rank};)
 \item Tuning changes conclusions about what factors are most important (see \tion{import});
-\item Tuning changes conclusions about what learners are better than others (see \tion{rank};)
+\item  Tuning is easy (see \tion{easy});
+\item Tuning is fast (see \tion{fast});
+\item Data miners should not be used ``off-the-shelf'' with their default tunings (see \tion{variance});
 \ee
 
-\subsection{Tuning is Easy}
+\subsection{Tuning Can  Improves Performance Scores}\label{sect:precision}
 
-All the following results are generated with a a very simple optimizer
-(differential evolution). Further, our DE  is actually much simpler
-than a standard implementation. Recall from Algorithm~1 that
+\fig{precisionbars} shows precision results before and after tuning using three different learners.
+For each data set, the maximum precision values for each data set are shown in {\bf bold}.
+
+These results offer support for the prior conclusions of  
+ Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
+\bi
+\item
+Untuned CART is indeed the worst learner (none of its
+untuned results are best and {\bf bold}). 
+\item 
+Untuned Random Forest performs better than untuned CART in $\frac{15}{17}$ of these results.
+\ei
+
+Some of the data sets in \fig{precisionbars} proved challenging for all learners.
+To some extend, this can be explained by
+the properties of of the data set. For example, the precision results for {\em ivy} are less
+that impressive since, as shown in \fig{data1}, defective classes in {\em ivy} are very rare.
+
+That said, tuning can repair at least some of the challenging data sets seen in \fig{precisionbars}:
+\bi
+\item
+Observe the {\em xercesV0} results: nearly all learners report precisions of under 20\%. However,
+the WHERE tuned results report an 85\% precision.  
+\item A similar pattern can be seen in results from {\em camelV0},   and {\em jeditV2}.
+In those two data sets, nearly all the precision values are   low {\em except} for
+tuned WHERE that scored 83 and 98\%.
+\ei
+Finally, note the  {\em jeditV2} result for the WHERE learner.
+Here, tuning changes precision fro 2\% to 98\% (!!).
+
+\begin{figure}[!h]
+\renewcommand{\baselinestretch}{0.8}
+
+\scriptsize
+
+\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
+%\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
+      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
+  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
+antV0 & 30 &         & {\bf 89} & {\rfour} & 27 &         & {\bf 89} & {\rfour} & 39 &         & {\bf 89 }& {\rfour}\\
+antV1 & 32 & {\rtwo} & {\bf 74} & {\rfour} & 41 & {\rtwo} & {\bf 74 }& {\rfour} & 43 & {\rtwo} & 0 &        \\
+antV2 & {\bf 78} & {\rfour} & {\bf 78} & {\rfour} & 52 &         & 68 & {\rthree} & 66 & {\rtwo} & 67 & {\rtwo}\\
+camelV0 & {\bf 83} & {\rfour} & {\bf 83} & {\rfour} & 26 &         & 33 &         & 34 &         & 45 & {\rone}\\
+camelV1 & 22 &         & {\bf 28} & {\rfour} & 23 &         & 24 & {\rone} & {\bf 28} & {\rfour} & {\bf 28} & {\rfour}\\
+ivy & 16 &         & {\bf 23} & {\rfour} & 18 & {\rone} & 21 & {\rthree} & 21 & {\rthree} & 20 & {\rtwo}\\
+jeditV0 & 35 &         & {\bf 75} & {\rfour} & 49 & {\rone} & 56 & {\rtwo} & 50 & {\rone} & 48 & {\rone}\\
+jeditV1 & 24 &         & {\bf 87} & {\rfour} & 28 &         & 86 & {\rfour} & 36 &         & 39 & {\rone}\\
+jeditV2 & 2 &         & {\bf 98 }& {\rfour} & 3 &         & 18 &         & 5 &         & 5 &        \\
+log4j & 94 &         & {\bf 100} & {\rfour} & 97 & {\rtwo} & {\bf 100} & {\rfour} & {\bf 100} & {\rfour} & {\bf 100 }& {\rfour}\\
+lucene & 61 &         & 74 & {\rfour} & 67 & {\rone} & 70 & {\rtwo} & 72 & {\rthree} & {\bf 77} & {\rfour}\\
+poiV0 & 70 &         & 68 &         & 77 & {\rfour} & 72 & {\rone} & {\bf 79} & {\rfour} & 76 & {\rthree}\\
+poiV1 & {\bf  100} & {\rfour} & 90 & {\rthree} & 73 &         & 89 & {\rtwo} & 81 & {\rone} & {\bf 100} & {\rfour}\\
+synapse & 66 &         & 66 &         & 71 & {\rone} & {\bf 100} & {\rfour} & 59 &         & 80 & {\rtwo}\\
+velocity & 34 &         & 39 & {\rthree} & 34 &         & 40 & {\rfour} & 40 & {\rfour} & {\bf 41} & {\rfour}\\
+xercesV0 & 13 &         & {\bf 85} & {\rfour} & 14 &         & 13 &         & 15 &         & 13 &        \\
+xercesV1 & {\bf 56} & {\rfour} & 26 &         & 50 & {\rthree} & 26 &         & 41 & {\rtwo} & 26 &        \\
+\end{tabular}
+\caption{Precision results (best results  shown in {\bf bold}).}
+\label{fig:precisionbars}
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+{\small\[\begin{array}{r|rrrrrrrrrrrrrrrrrr}\hline
+          &      &      &       &   &       & 25th  &   & &  & 50th     &   &  &      & 75th  &   &   &     &\\
+Precision & WHERE&	-30	&-10	&-2 &	0	&0	&0	&5&	6&	6	&7	&13&	40&	42&	59&	63&	72	&96\\
+
+&CART&	-24&	-5	&-1	&1	&3	&3	&3	&6	&7	&7	&15&	16	&16&	29	&33&	58&	62\\
+
+&RF &	-43&	-15&	-3	&-2	&-2&	-1	&0	&0	&0	&1	&1	&3	&5&	11&	19&	21	&50\\\hline 
+f-measure &	WHERE&	-14&	-14	&-6&	-5	&-4	&-2&	0	&0	&2	&4	&5	&6	&7&	14&	28	&73	&87\\
+	&CART	&-43	&-6	&-2&	-1&	1	&2	&5&	6&	6	&8	&12&	13&	16&	19&	19	&35&	57\\
+	&RF	&-27	&-10	&-4	&-4&	-3	&-2	&-2	&-2&	0	&0	1&	2	&2	&2	&4	&5	&5
+	\end{array} \]}
+	\end{center}
+\caption{Sorted performance deltas, {\em tuned - default} when tuning on precision in \fig{precisionbars}
+and the F-measure in \fig{f-bars}.}
+\end{figure*}
+\subsection{Tuning Changes Learner Rankings}\label{sect:rank}
+
+Suppose we reflected on \fig{precisionbars} to decide which learners were better than others.
+Given the poor showing of untuned CART and the good performance of tuned WHERE, we might recommend
+{\em not} to use CART and {\em always} used tuned WHERE.
+
+Note that this conclusion is not stable and is changed if we elect to tune for different goals. 
+\fig{fbars} shows what happens when we tune for the f-measure. 
+As before, untuned Random Forest generally beats CART. However:
+\bi
+\item
+In  a result that is the direct opposite of   
+ Lessmann et al.~\cite{lessmann2008benchmarking}, tuned CART does better than Random Forest;
+ \item 
+ In another result that is the reverse of \fig{precisionbars}, tuned WHERE is not necessarily
+ any better than anything else.
+ \ei
+The lesson here is that, given a particular task (e.g. optimizing for precision), tuning can offer
+substantial benefits. However, when that task changes (e.g. to optimizing for the F-measure),
+it should not be assumed that conclusions from the previous tuning will hold in the new context.
+In practice, this means that tuning needs to be repeated for each new context.
+
+\begin{figure}[!h]
+\renewcommand{\baselinestretch}{0.8}
+
+\scriptsize  
+~~~\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
+      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
+  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
+antV0 & {\bf 39} & {\rfour} & 25 & {\rtwo} & 32 & {\rthree} & 31 & {\rthree} & {\bf 39} & {\rfour} & 12 &        \\
+antV1 & 11 &         & 6 &         & 40 & {\rfour} & {\bf 45} & {\rfour} & 39 & {\rfour} & 44 & {\rfour}\\
+antV2 & 0 &         & {\bf 87} & {\rfour} & 44 & {\rtwo} & 1 &         & 50 & {\rtwo} & 51 & {\rtwo}\\
+camelV0 & 0 &         & 28 & {\rfour} & 9 & {\rone} & 28 & {\rfour} & {\bf 34} & {\rfour} & 30 & {\rfour}\\
+camelV1 & {\bf 34} & {\rfour} & {\bf 34} & {\rfour} & 31 &         & 32 & {\rone} & 33 & {\rthree} & 31 &        \\
+ivyV0 & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
+jeditV0 & 50 &         & 56 & {\rtwo} & 56 & {\rtwo} & 54 & {\rone} & {\bf 61} & {\rfour} & 59 & {\rfour}\\
+jeditV1 & 37 & {\rone} & 33 &         & 36 &         & {\bf 49} & {\rfour} & 45 & {\rthree} & 47 & {\rfour}\\
+jeditV2 & 4 &         & 8 & {\rtwo} & 5 &         & {\bf 11} & {\rfour} & 9 & {\rthree} & 9 & {\rthree}\\
+log4jV0 & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
+luceneV0 & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
+poiV0 & {\bf 78} & {\rfour} & 64 &         & 74 & {\rthree} & 68 & {\rone} & 73 & {\rthree} & 69 & {\rone}\\
+poiV1 & 5 &         & {\bf 78} & {\rfour} & 21 & {\rone} & {\bf 78} & {\rfour} & 76 & {\rfour} & {\bf 78} & {\rfour}\\
+synapseV0 & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
+velocityV0 & {\bf 51 & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
+xercesV0 & 22 & {\rone} & 20 &         & 21 &         & {\bf 27} & {\rfour} & 23 & {\rtwo} & 20 &        \\
+xercesV1 & 25 &         & 39 & {\rone} & 18 &         & 53 & {\rthree} & 68 & {\rfour} & {\bf 73} & {\rfour}\\
+\end{tabular}
+\caption{F-value results (best results  shown in {\bf bold}).}
+\label{fig:fbars}
+\end{figure}
+
+\subsection{Tuning Changes Factors Rankings }\label{sect:rank}
+
+\fig{counts} shows how the objective goal (in this case,
+{\em pd} (recall) or precision, or the f-measure) changes what factors are most important.
+In this table, ``important'' is defined by how often some factor was used when WHERE generated
+its final trees. Given that we are processing 17 data sets, the maximum counts for any 
+one learner is 17.
+
+The first thing to note in \fig{counts} is that the counts in the {\em tuned} column are always usually
+much less than in the {\em default} columns. That is, after tuning, different and fewer factors
+are used to make conclusions. Further, given the imr
+\begin{figure}[!h]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c| c c }
+
+    & \multicolumn{2}{c|}{Pd} &  \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{F} &  \multicolumn{2}{c|}{SUM}\\
+ &&&&&&&&\\
+Features& \begin{sideways}default\end{sideways}
+& \begin{sideways}tuned\end{sideways}
+& \begin{sideways}default\end{sideways}
+& \begin{sideways}tuned\end{sideways}
+& \begin{sideways}default\end{sideways}
+& \begin{sideways}tuned\end{sideways}
+& \begin{sideways}default\end{sideways}
+& \begin{sideways}tuned\end{sideways}
+\\\hline
+noc& & & & & & &  & \\
+ca& & & & & & &  & \\
+max\_cc& & & & 1& & 1&  & 2\\
+ce& & & & 1& & 2&  & 3\\
+moa& & 1& & 1& & 2&  & 4\\
+cbo& & & & 1& & 4&  & 5\\
+avg\_cc& & & & 3& & 2&  & 5\\
+lcom& & & & 3& & 3&  & 6\\
+npm& & 1& & 5& & 4&  & 10\\
+cbm& 4& & 6& 3& 4& 3& 14 & 6\\
+amc& 4& 1& 4& 3& 4& 5& 12 & 9\\
+rfc& 4& 1& 4& 5& 4& 9& 12 & 15\\
+ic& 8& & 7& 4& 9& 4& 24 & 8\\
+wmc& 5& 2& 5& 6& 5& 11& 15 & 19\\
+dit& 8& & 8& 6& 8& 6& 24 & 12\\
+lcom3& 9& 1& 9& 7& 9& 7& 27 & 15\\
+loc& 9& 2& 8& 6& 9& 12& 26 & 20\\
+cam& 9& 1& 9& 8& 9& 10& 27 & 19\\
+dam& 14& 3& 14& 9& 14& 11& 42 & 23\\
+mfa& 16& 3& 16& 11& 16& 13& 48 & 27\\
+
+  \end{tabular}
+    \caption{Counts of features selected by different goals.
+For each goal, the numbers in right and left columns represent the counts of features selected for all the data sets with and without tuning processes.
+    }\label{fig:counts}
+\end{figure}
+
+\subsection{Tuning is Easy}\label{sect:easy}
+
+Measured in terms of the search space
+required to achieve large changes in learner performance, optimizing defect prediction from static code
+measures is about an order of magnitude {\em easier} than standard optimization.
+Recall from Algorithm~1 that
 DE explores a {\em Population} of size {\em np=10}. This is a very small population size:
 the standard recommendation is to set {\em np} to be ten times larger than the number
-of attributes being optimized~\cite{stron97}
+of attributes being optimized~\cite{stron97}.
+
+Another measure showing that tuning is easy is the number of evaluations required to complete optimization.
+This is covered in the next section.
+
+\subsection{Tuning is Easy}\label{sect:easy}
+
+\begin{figure}
+
+{\scriptsize
+
+\renewcommand{\baselinestretch}{0.8}
+\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
+      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forests}         \\\hline
+  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
+antV0 & 65 & {\rtwo} & 68 & {\rthree} & 53 &         & $\bigstar$75 & {\rfour} & 69 & {\rthree} & 72 & {\rfour}\\
+antV1 & 12 &         & $\bigstar$70 & {\rfour} & 52 & {\rthree} & 56 & {\rthree} & 62 & {\rfour} & 69 & {\rfour}\\
+antV2 & 0 &         & $\bigstar$69 & {\rfour} & 53 & {\rthree} & 64 & {\rfour} & 68 & {\rfour} & 67 & {\rfour}\\
+camelV0 & 0 &         & 51 & {\rfour} & 10 &         & 56 & {\rfour} & 60 & {\rfour} & $\bigstar$61 & {\rfour}\\
+camelV1 & 45 &         & 55 & {\rthree} & 53 & {\rtwo} & $\bigstar$59 & {\rfour} & 56 & {\rthree} & 57 & {\rfour}\\
+ivyV0 & 53 &         & 71 & {\rfour} & 63 & {\rtwo} & $\bigstar$74 & {\rfour} & 70 & {\rfour} & 71 & {\rfour}\\
+jeditV0 & 59 &         & 69 & {\rthree} & 71 & {\rfour} & 72 & {\rfour} & $\bigstar$73 & {\rfour} & $\bigstar$73 & {\rfour}\\
+jeditV1 & 70 & {\rthree} & 69 & {\rtwo} & 62 &         & 73 & {\rfour} & $\bigstar$75 & {\rfour} & $\bigstar$75 & {\rfour}\\
+jeditV2 & 49 &         & 56 & {\rone} & 48 &         & 61 & {\rtwo} & $\bigstar$78 & {\rfour} & 67 & {\rthree}\\
+log4jV0 & 53 & {\rtwo} & 56 & {\rthree} & 46 &         & $\bigstar$59 & {\rfour} & 56 & {\rthree} & 56 & {\rthree}\\
+luceneV0 & 37 &         & 65 & {\rfour} & 55 & {\rthree} & 56 & {\rthree} & 60 & {\rthree} & $\bigstar$66 & {\rfour}\\
+poiV0 & 45 &         & 60 & {\rthree} & 66 & {\rfour} & 62 & {\rthree} & $\bigstar$68 & {\rfour} & 56 & {\rtwo}\\
+poiV1 & 6 &         & $\bigstar$62 & {\rfour} & 22 & {\rone} & 60 & {\rfour} & 56 & {\rfour} & 57 & {\rfour}\\
+synapseV0 & 0 &         & 61 & {\rfour} & 43 & {\rthree} & 64 & {\rfour} & 63 & {\rfour} & $\bigstar$67 & {\rfour}\\
+velocityV0 & 3 &         & $\bigstar$56 & {\rfour} & 26 & {\rtwo} & 51 & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
+xercesV0 & 37 &         & 46 & {\rthree} & 47 & {\rfour} & $\bigstar$49 & {\rfour} & $\bigstar$49 & {\rfour} & 48 & {\rfour}\\
+xercesV1 & 24 &         & $\bigstar$68 & {\rfour} & 19 &         & 32 & {\rone} & 32 & {\rone} & 17 &        \\
+\end{tabular}
+}
+\caption{g values in tune and default runs.
+All data available from http://openscience.us/repo/defect/. {\bf KEY:}
+  percentile ranges:\newline
+80th to 100th= {\rfour};
+60th to 80th= {\rthree};
+40th to 60th= {\rtwo};
+20th to 40th= {\rone};
+an absent bar shows  0th to 20th.
+Percentiles computed  separately
+for each row.}
+\label{fig:gbars}
+
+\end{figure}
 

### 2015-03-15 learners.tex
Updates from ShareLaTeX

@@
 In that study, CART was severely trounced (was ranked last) and Random Forest was
-the standout best method. The experiments shown below both confirm and refute
-that ranking. In a result consistent with the prior result, untuned Random Forest performs best.
-However, after tuning, the worst learner found by Lessmann et al. (CART) performed better
+the standout best method. However, in a result consistent with the theme of this paper,
+we show below that we can reverse those rankings such that, under certain conditions,
+  the worst learner found by Lessmann et al. (CART) performed better
 than Random Forest.
@@
 
+\input{algo} 
  \subsubsection{Selecting a Tuning Algorithm}
@@
   \item
-  When the MOEA/D community requires a secondary optimizer, then often use  differential evolution~\cite{zhang07,5583335}.
+  When the MOEA/D community requires a secondary optimizer, they often use  differential evolution~\cite{zhang07,5583335}.
   \item

### 2015-03-15 deltas.sh
new files

@@ -45,19 +45,19 @@ F > /tmp/F.dat
 
 draw() {
 gnuplot<<EOF
-set key top left
+set key bottom right
 set output "$1.eps
-set title "Tuning's improvements to $1"
+set title "$1"
 set terminal postscript eps color "Helvetica" 15
-set size 0.5,0.5
-set yrange [-50:100]
+set size 0.3,0.5
+set yrange [-100:100]
 set ytics (-50,0,50,100)
-set xlabel "Improvements in 17 experiments, sorted"
+set xlabel "Improvements , sorted"
 set xtics (1,4,8,12,16)
 set arrow 1 from 1,0 to 17,0 nohead
 plot "/tmp/$1.dat" using 1:2 title "WHERE"  with linesp,\
      "/tmp/$1.dat"  using 1:3 title "CART" with linesp,\
-     "/tmp/$1.dat"  using 1:4 title "Random Forest" with linesp,
+     "/tmp/$1.dat"  using 1:4 title "R.Forest" with linesp,
 EOF
 ps2pdf -dEPSCrop $1.eps 
 }

### 2015-03-15 tuningpredictor.tex
Updates from ShareLaTeX

@@
 
-\begin{figure*}
-\begin{center}
-{\small\[\begin{array}{r|rrrrrrrrrrrrrrrrrr}\hline
-          &      &      &       &   &       & 25th  &   & &  & 50th     &   &  &      & 75th  &   &   &     &\\
-Precision & WHERE&	-30	&-10	&-2 &	0	&0	&0	&5&	6&	6	&7	&13&	40&	42&	59&	63&	72	&96\\
+\includegraphics[width=2.5in]{F.pdf}
 
-&CART&	-24&	-5	&-1	&1	&3	&3	&3	&6	&7	&7	&15&	16	&16&	29	&33&	58&	62\\
+\includegraphics[width=2.5in]{precision.pdf}
 
-&RF &	-43&	-15&	-3	&-2	&-2&	-1	&0	&0	&0	&1	&1	&3	&5&	11&	19&	21	&50\\\hline 
-f-measure &	WHERE&	-14&	-14	&-6&	-5	&-4	&-2&	0	&0	&2	&4	&5	&6	&7&	14&	28	&73	&87\\
-	&CART	&-43	&-6	&-2&	-1&	1	&2	&5&	6&	6	&8	&12&	13&	16&	19&	19	&35&	57\\
-	&RF	&-27	&-10	&-4	&-4&	-3	&-2	&-2	&-2&	0	&0	1&	2	&2	&2	&4	&5	&5
-	\end{array} \]}
-	\end{center}
-\caption{Sorted performance deltas, {\em tuned - default} when tuning on precision in \fig{precisionbars}
-and the F-measure in \fig{f-bars}.}
-\end{figure*}
 \subsection{Tuning Changes Learner Rankings}\label{sect:rank}

### 2015-03-15 deltas.sh
typo

@@ -49,7 +49,7 @@ set key bottom right
 set output "$1.eps
 set title "$1"
 set terminal postscript eps color "Helvetica" 15
-set size 0.3,0.5
+set size 0.3,0.75
 set yrange [-100:100]
 set ytics (-50,0,50,100)
 set xlabel "Improvements , sorted"

### 2015-03-15 deltas.sh
typo

@@ -52,8 +52,8 @@ set terminal postscript eps color "Helvetica" 15
 set size 0.3,0.75
 set yrange [-100:100]
 set ytics (-50,0,50,100)
-set xlabel "Improvements , sorted"
-set xtics (1,4,8,12,16)
+set xlabel "Improvements, sorted"
+set xtics (1,4,8,12,17)
 set arrow 1 from 1,0 to 17,0 nohead
 plot "/tmp/$1.dat" using 1:2 title "WHERE"  with linesp,\
      "/tmp/$1.dat"  using 1:3 title "CART" with linesp,\

### 2015-03-15 deltas.sh
typo

@@ -46,7 +46,7 @@ F > /tmp/F.dat
 draw() {
 gnuplot<<EOF
 set key bottom right
-set output "$1.eps
+set output "${1}1.eps
 set title "$1"
 set terminal postscript eps color "Helvetica" 15
 set size 0.3,0.75
@@ -59,7 +59,7 @@ plot "/tmp/$1.dat" using 1:2 title "WHERE"  with linesp,\
      "/tmp/$1.dat"  using 1:3 title "CART" with linesp,\
      "/tmp/$1.dat"  using 1:4 title "R.Forest" with linesp,
 EOF
-ps2pdf -dEPSCrop $1.eps 
+ps2pdf -dEPSCrop ${1}1.eps 
 }
 
 draw precision 

### 2015-03-15 dm101.tex
Updates from ShareLaTeX

@@
 
+%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
+\renewcommand\arraystretch{1.2}
+\begin{figure*}[t!]
+\scriptsize
+  \centering
+	\begin{tabular}{|c|c|c|c|l|}
+	\cline{1-5}
+	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
+\multicolumn{1}{c|}{Description} \\ \hline
+	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
+	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
+	& infoPrune & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
+split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
+one is for clustering and the second one is building prediction model. we explicitly call Where-
+clustering tree and CART tree, respectively}. \\ \cline{2-5} 
+	 & min\_sample\_split & 4& [1,10]& The minimum number of samples required to split an internal node of
+CART tree. \\ \cline{2-5} 
+	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_sample 
+in Where-clustering trees  using  ${n\_samples}^ {min\_Size}$.
+\end{tabular} \\ \cline{2-5} 
+    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
+	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
+clustering tree. \\ \cline{2-5} 
+	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
+	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
+	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
+\hline
+\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5}
+
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_samples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{1-5}  
+       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
+\cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5} 
+	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_samples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{2-5} 
+	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
+	 \hline
+
+	\end{tabular}
+    \caption {List of parameters to be tuned.}
+\label{fig:parameters}
+\end{figure*}
 {\em Widely used:} Many researchers and industrial practitioners  use static attributes to guide software 
@@
 {\em Useful:}
-A
-standard result for defect predictors is that they find the location of  70\% (or more)
+Defect predictors often  find the location of  70\% (or more)
 of the defects in code~\cite{me07b}.
@@
 
-Defect prediction scales well to a commercial
-context. Defect predicting technology has been
+Defect predicting technology has been
 commercialized in many tools including {\it Predictive}~\cite{turner06}, a
@@
 defects in software projects. Predictive was observed to
-highlight simimilar issues to those found   with the more expensive tools. Significantly,
+highlight similar issues to those found   with the more expensive tools. Significantly,
 Predictive was able to faster process a larger code
@@
 they also are competititve with certain automatic methods.
-At ICSE'14, Rahman et al.~\cite{rahman14:icse} offered an extensive comparison of:
+At ICSE'14, Rahman et al.~\cite{rahman14:icse} compared:
 \bi
@@
 \ei
-That study assessed the cost-effectiveness of finding bugs using either method.
 They found  no significant differences in the cost-effectiveness
-of the two approaches. Given this equivalence, it is significant to note that 
-static code defect prediction can be quickly adapted to new languages, just by building lightweight
-parsers that can extract information like \fig{ck}. The same cannot be said for   static code analyzers that require extensive modification before they can be applied to a new
-language.
+of these  approaches. Given this equivalence, it is significant to note that 
+static code defect prediction can be quickly adapted to new languages by building lightweight
+parsers that find   information like \fig{ck}. The same is not true for   static code analyzers-- these need  extensive modification before they can be used on new
+languages.

### 2015-03-15 learners.tex
Updates from ShareLaTeX

@@
-This section describes this study's learners (CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
-and WHERE~\cite{menzies2013local}) and their
-tuning parameters (summarised in \fig{parameters}).
-
-Our implementations
+This section describes this study's learners: CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
+and WHERE~\cite{menzies2013local}.
+The implementations
 for CART and Random Forest comes from 
@@
 WHERE is available from
-github.com/ai-se/where\footnote{\wei{ need a nice  where repo. with an
-data and code examples sub-directory. clean code. throw out anything not needed. before april1.}}.
+github.com/ai-se/where.
+
+\fig{parameters} shows the tuning parameters of these learners.
 WHERE has the most tuning parameters. This turns out
@@
 
-%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
-\renewcommand\arraystretch{1.2}
-\begin{figure*}[t!]
-\scriptsize
-  \centering
-	\begin{tabular}{|c|c|c|c|l|}
-	\cline{1-5}
-	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
-\multicolumn{1}{c|}{Description} \\ \hline
-	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
-	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
-	& infoPrune & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
-split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
-one is for clustering and the second one is building prediction model. we explicitly call Where-
-clustering tree and CART tree, respectively}. \\ \cline{2-5} 
-	 & min\_sample\_split & 4& [1,10]& The minimum number of samples required to split an internal node of
-CART tree. \\ \cline{2-5} 
-	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
-number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
-\end{tabular} \\ \cline{2-5} 
-    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
-	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
-clustering tree. \\ \cline{2-5} 
-	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
-	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
-	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
-\hline
-\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
-	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5}
-
-	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_samples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{1-5}  
-       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
-\cline{2-5} 
-	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5} 
-	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
-	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_samples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{2-5} 
-	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
-	 \hline
-
-	\end{tabular}
-    \caption {List of parameters to be tuned.}
-\label{fig:parameters}
-\end{figure*}
-
 \subsection{Why Study These Algorithms?}
 
-This paper studies WHERE since this was the first learner we tried to tune and, as shown below,
+This paper presents results with WHERE since, as shown below,
 it offers an interesting case study on the benefits of tuning.
@@
 Multi-Layer Perceptron,
-Radial bias function network,
+Radial bias functions,
 
@@
 {\em Decision-tree approaches:}
-C4.5 decision tree,
+C4.5,
 CART,
-Alternating decision tree.
+Alternating DTs
 \item
@@
 \ei
-In that study, CART was severely trounced (was ranked last) and Random Forest was
-the standout best method. However, in a result consistent with the theme of this paper,
-we show below that we can reverse those rankings such that, under certain conditions,
+In that study, CART  was ranked last  and Random Forest was
+the standout best method.
+We show below that we can reverse those rankings such that, under certain conditions,
   the worst learner found by Lessmann et al. (CART) performed better
@@
 \item
-Random Forest    divides data like CART,
-but it builds $F>1$  trees, each time with a subset of
-the attributes (selected at random). 
+Random Forest    divides data like CART then  builds $F>1$  trees,
+each time using some random subset of
+the attributes. 
 \item
@@
 
- Later work focused on creative ways to control the
- mutation process. Tabu search and scatter search
+ Later work focused on smarter  
+ mutations. Tabu search and scatter search
  work to bias new mutations away from prior
@@
  Differential evolution mutates solutions by
- interpolating between members of the current
+ interpolating between items in the current
  population~\cite{storn1997differential}.
 
-Another more recent technique that has claimed much attention
-are   heuristics that decompose the total space into many smaller problems, and then which use a simpler optimizer for each region. 
-For example, in $\mathcal{E}$-domination~\cite{deb05}, the  user is asked
+\input{algo}
+
+Another approach uses
+    heuristics to decompose the total space into   small problems,   then applies a
+    simpler optimizer to each region. 
+In $\mathcal{E}$-domination~\cite{deb05}, the  user is asked
 `what is the lower threshold $\mathcal{E}$ on the size of a useful effect?''. The solution space
@@
 
-\input{algo} 
  \subsubsection{Selecting a Tuning Algorithm}

### 2015-03-15 tuningpredictor.tex
Updates from ShareLaTeX

--- 2015-03-15 tuningpredictor.tex
@@
 \usepackage{colortbl} 
+\usepackage{balance}
 \usepackage{picture}
@@
 
-Our tuning results  challenge much prior work in software analytics. 
+These results challenge much prior work. 
 Firstly, there exist research papers
@@
 
-\subsection{Preliminaries}
-
-Before beginning, we offer four caveats on these results.
-
-Firstly, we are {\em not} saying that {\em all} learning requires
-tuning. For example, when proposing fixes to software, Weimar et al. use a genetic learner
-to propose patches~\cite{Weimer:2009}. Consider one performance criteria for that work; i.e. 
-that   that that method can find and fix known bugs. Note that this is a {\em competency criteria}
-which does not include the phrase  ``{\em better than}''. Such performance criteria do
-not requiring tuning.  However, once {\em better than} enters the performance criteria
-(as done in \cite{lessmann2008benchmarking,hall11,me07b,bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting})
-then this becomes a race between competing methods (or attributes).  In such a race, it is unfair
-to hobble one competitor with poor tunings.
-
-Secondly, the tuning results shown here only came from one  software analytics task 
-(defect prediction from static code attributes).
-There are many other kinds of software analytics tasks 
-(software development effort estimation, social network mining,
-detecting duplicate issue reports, etc) and the implication of this
-study for those tasks is unclear. 
-However,  those other tasks often use the same kinds of learners
-explored in this paper so it is quite possible that
-the conclusions of this paper apply to other SE analytics tasks as well.
-
-Thirdly, this paper explores {\em some} learners using {\em one}  optimizer. Hence, it makes
-no claim that this is the {\em best} optimizer for {\em all} learners.
-Rather, our point is that there exists at least some learners
-whose performance can be dramatically improved by 
-at least one simple optimization scheme.  We hope that this work inspires
-much future work as this community develops and debugs best practices for tuning
-software analytics.
-
-Fourthly, it would be incorrect to say that this paper is arguing that
-software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
-In the age of the Internet and global access to software engineering data,
-there exists the  problem of information overload. {\em Something} must be done to
-allow analysts to make conclusions via an automatic analysis over a lot of data.
-The results of this paper is that for a particular local context
-(a specific data set and a specific goal) there exists  
-methods for optimizing the conclusions reached in that context.  Those conclusions
-may not generalize to other contexts but this  is not a council for despair. While there may
-not exist general conclusions, there does seem to exist general methods for finding
-local conclusions in a particular context. Further, as shown below, those
-methods may be very simple to implement and very fast to execute.
-
 \section{Motivating Example}\label{sect:eg}
@@
 error and maximizes the correlation\footnote{
-$Correlation$
+{\em Correlation}
 measures how closely two variables co-vary.  It ranges from   from -1
@@
 \mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
-\mathit{LOC}   &d_i= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
-\mathit{Halstead} & d_2= 0.231 + 0.00344N     \\    
-                 & +  0.0009V   - 0.185L \\
-                 & - 0.0343D      - 0.00541I \\
-                 & + 0.000019E + 0.711B \\ 
-                 &   - 0.00047T  & c_2=-0.36  
+\mathit{LOC}   &d_1= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
+\mathit{Halstead} & d_2= 0.231 + 0.00344N  +  0.0009V    \\    
+                 &   - 0.185L- 0.0343D      - 0.00541I  \\ 
+                 & + 0.000019E + 0.711B  - 0.00047T  & c_2=-0.36  
 \end{array}
@@
 \noindent
-Enter tuning. Suppose the defect predictors $d_1$ and $d_2$  learned from LOC or Halstead
-are used to to call an inspection
-team to check for errors in certain parts of the code using the rule
+We now explore how tuning can alter the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
+are used to call an inspection
+team to check for errors in   parts of the code using:
 \begin{equation}\label{eq:yesno}\scriptsize
@@
 \end{equation}
-\fig{pd1} shows the effects of tuning the $T$ variable. Not surprisingly,
+\fig{pd1} shows the effects of tuning. Not surprisingly,
 at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
@@
 \begin{figure}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
 {\scriptsize
@@
 
-One  important lesson from  \fig{pd1} is that the ``best'' tunings are context
+One   lesson from  \fig{pd1} is that the ``best'' tunings are context
 specific. For mission critical systems (e.g. a nuclear power plant), management
@@
 
-The other  important lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
+The other   lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
 detector can work just as well as seemingly better ones.
@@
 
-The core point of this example is that    the true value of a detector
+The  point here is that   the true value of a detector
 could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
 issuing a request to an inspection team to review some module).  
-This is strong motivation to explore the issue of tunings.
+Hence, it is important to explore tuning
+so the rest of this paper repeats the analysis of this section, but for 
+more complex learners.
 
 \section{Background Notes}
-
-The rest of this paper repeats the analysis of the last section, but for much
-more complex learners. In those results, shown  below, we will find
-examples of {\em rank reversals};
-i.e.  after tuning the top ranked defector becomes last and vice versa.
-Such examples motivate the extensive exploration of tuning in software analytics.
-Before presenting those results, this section offers some background notes on defect prediction,
-performance measures, and optimization with differential evolution.
 
@@
 {\scriptsize
-\begin{tabular}{c|l|p{4in}}
+\begin{tabular}{c|l|p{4.7in}}
 amc & average method complexity & e.g. number of JAVA byte codes\\\hline
@@
 in a class number and $\mu(a)$  is the number of methods accessing an
-attribute,\newline
+attribute, 
 then
@@
 
-\subsubsection{Differential Evolution: The Details}
-
 The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
@@
 
-DE is an evolutionary algorithm; i.e. the next {\em NewGeneration} is learnt from
-a current {\em Population}.  If the new is no better than the current, then
-we lose one life, terminating when we run out of lives$^5$.
+DE is an evolutionary algorithm where next {\em NewGeneration} is learnt from
+a current {\em Population}.  If the new is no better than  current, then
+we lose one life (terminating when lives is zero)$^5$.
 
 Each candidate solution in the {\em Population}  
-is a pair of {\em (Tunings, Scores)}. In this paper, {\em Tunings} are selected from
+is a pair of {\em (Tunings, Scores)}.  {\em Tunings} are selected from
 \fig{parameters} and {\em Scores} come from training a learner using those parameters
-and applying it to some test data$^{23-28}$.
+and applying it     test data$^{23-28}$.
 
-The premise of this algorithm is that the best way to mutate existing tunings
+The premise of DE  is that the best way to mutate existing tunings
 is to {\em Extrapolate}$^{29}$
@@
 For each tuning parameter $i$, at some probability {\em cr}, we replace
-the old tuning $x_i$ with $y_i$ found as follows:
+the old tuning $x_i$ with $y_i$:
 \bi
@@
 
-\begin{figure*}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{c c c c c c c c c c }\hline
-  Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
-\\\hline
-  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
-\\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
-\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
-\\  \end{tabular}
-   \caption{Ratios of defective instances in each experimental data set. 
-   E.g., the top left data set has 20 defective classes out of 125 total.
-   This paper runs one experiment for each column
-   shown in this figure. The {\em training} set is used by an untuned learner
-   to build a model, which is then tested on the {\em testing} data.
-   {\em Training} data is used by  differential evolution when it builds
-    a model (using one set of possible tunings) and that model is tested on {\em tunings}.
-    Finally, the best model from by DE is applied to {\em testing}. 
-   This information is continued  in \fig{data2}. 
-   }\label{fig:data1}
-\end{figure*}
-\begin{figure*}[!ht]
-\scriptsize
-\centering
-  \begin{tabular}{c c c c c c c c c c }
-  \hline\hline
-  Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
-\\\hline
-  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
-\\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
-\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
-\\  \end{tabular}
-
-   \caption{More ratios of  defective instances in each experimental data set. 
-   Same format as \fig{data1}.}\label{fig:data2}
-\end{figure*}
-
 \section{Experimental Design}
@@
 in training.  There are many ways to design a experiment that satisfies this principle.
-Some of those methods have certain drawbacks:
+Some of those methods have  limitations:
 \bi
@@
 
-For this experiment, we looked for data sets that had at least three  
-releases in PROMISE. Note that the following ensures that all treatments 
-get assessed on the same test  set.
+For this experiment, we uses data sets with at least three  
+consecutive releases  (where release $i+1$ was built after release $i$).
 \bi 
 \item The {\em first} release was used for some  {\em training}, to collect a baseline
-   using an untuned learner.
-   \item
-   The {\em first} release was also used  on line 24 of Algorithm~\ref{alg:DE} to
+   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
    build some model using some the tunings found in some {\em Candidate}.
@@
    \ei
+This approach ensures   all treatments 
+are assessed on the same tests.
+
 Some data sets have more than three releases and, for those data, we could run more
@@
  \ei 
-These data sets are displayed in \fig{data1} and \fig{data2}.
+These data sets are displayed in \fig{data1}.
+
+\begin{figure}[!b]
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+One style
+of measure is to check the {\em variability} of that predictor.
+For example,
+in their study on reproducibility of SE results,
+ Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
+Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
+
+There exist other goals that combine defect prediction with other economic
+factors.
+Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
+say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
+that contain the most bugs.
+
+Yin et al. are concerned about
+ {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
+These bugs occur  when (say) developers try to fix parts of the code
+where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
+for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
+
+In {\em Better-faster-cheaper}, we seek  project changes that lead
+to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
+
+Another  {\em  rush-to-market} approach is yet another economic-based optimization measure.
+A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
+as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
+in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
+used to subsequently fix any issues with version 1.0)~\cite{huang06}.\\\hline
+\end{tabular}
+\caption{Many ways to assess defect predictors.}\label{fig:criteria}
+\end{figure}
+ \begin{figure*}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{c c c c c c c c c c }\hline
+  Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
+\\\hline
+  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
+\\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
+\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
+\\ \hline
+  Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
+\\\hline
+  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
+\\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
+\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
+\\  \end{tabular}
+
+   \caption{Ratios of defective instances in each experimental data set. 
+   E.g., the top left data set has 20 defective classes out of 125 total.
+   This paper runs one experiment for each column
+   shown in this figure. The {\em training} set is used by an untuned learner
+   to build a model, which is then tested on the {\em testing} data.
+   {\em Training} data is used by  differential evolution when it builds
+    a model (using one set of possible tunings) and that model is tested on {\em tunings}.
+    Finally, the best model from by DE is applied to {\em testing}.  
+   }\label{fig:data1}
+\end{figure*}
 
@@
 
-Recall from Algorithm~! that we call differential evolution one time for each
-goal we are trying to optimize. This section lists those optimization goals.
+Recall from Algorithm~1 that we call differential evolution once for each
+ optimization goal. This section lists those optimization goals.
 
@@
 $A,B,C,D$:
-\[
+
+{\scriptsize\[
 \begin{array}{ll}
-pd=recall=&\frac{D}{B+D}\\
-pf=&\frac{C}{A+C}\\
+pd=recall=&D/(B+D)\\
+pf=&C/(A+C)\\
 pf'=& 1 - pf\\
-prec=precision=&\frac{D}{D+C}\\ 
- g = & \frac{2*pd*pf'}{pd + pf'}
+prec=precision=&D/(D+C) 
 \end{array}
-\]
+\]}
+
 All the above vary from zero to one. For $pf$, the {\em better} scores and {\em smaller}.
@@
 
-The following results make no assumption that (e.g.) minimizing false alarms are 
-more important that maximizing recall or precision. That determination 
-should be make with respect to current business conditions:
-\bi
+The following results make no assumption that (e.g.) minimizing false alarms is 
+more important than maximizing   precision. That determination 
+depends on current business conditions:
+\be
 \item
-For safety critical applications, low false alarm rates are irrelevant since the cost
-of overlooking any critical might outweigh the inconvenience of having to inspect a few more
+For safety critical applications, high false alarm rates may be acceptable if the cost
+of overlooking any critical can outweigh the inconvenience of having to inspect a few more
 modules. 
@@
 managers might be willing to lower the recall somewhat in order to minimize the false alarms.
-\ei
-What the falling results do show is that once the optimization goal changes, so does everything
-else. Hence, it is important not to overstate  empirical results from software analytics.
+\ee
+These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
+and there is insufficient space in this paper to explore all the above optimization goals.
+What we can do, however, is show examples of how  changing  optimization goals can also change 
+the conclusions made from that learner on that data. Those examples only relate to precision, recall, and the F-measure
+but the general principle (that the search bias changes the search conclusions) would hold for all the goals
+listed in the previous paragraph.  Hence, we warn that it is important not to overstate  empirical results from software analytics.
 Rather, those results need to be expressed {\em along with} the context within which they are
-relevant.
+relevant (and by ``context'', we mean the optimization goal).
 
@@
 that use static code attributes. This section presents
-our results in order of those claims:
+support for those claims:
 \be
-\item Such tuning was easy (see \tion{easy});
-\item Such tuning is fast (see \tion{fast});
-\item Such tuning is can dramatically change the performance scores of a predictor;
-e.g. one result where precision changes from 2\% to 98\% (see \tion{precision});
-\item Tuning changes conclusions about what factors are most important (see \tion{import});
-\item Tuning changes conclusions about what learners are better than others (see \tion{rank};)
+\item  Tuning    improves the performance scores of a predictor;
+e.g.  precision changes from 2\% to 98\%: see \tion{precision};
+\item Tuning changes conclusions on what learners are better than others: see \tion{rank};
+\item Tuning changes conclusions about what factors are most important: see \tion{import};
+\item  Tuning is easy: see \tion{easy};
+\item Tuning is fast: see \tion{fast};
+\item Data miners should not be used ``off-the-shelf'' with their default tunings: see \tion{variance}.
 \ee
 
-\subsection{Tuning is Easy}
+One comment before continuing. The following text does not
+show results for tuning on recall
+or false alarms. The reason is that false alarm and recall focus on {\em only}
+the non-defective and defective modules (respectively). Hence:
+\bi
+\item
+When DE tunes for recall, we can achieve near
+100\% recall-- but the cost of a near 100\% false alarms.
+\item
+Similarly, the tuner
+could achieve near zero false alarm rates by effectively turning off
+the detector (driving recall to zero).
+\ei
+Hence, in the
+following, we explore performance measures that comment on all the possible
+target classes (i.e. precision and ``F'').
 
-All the following results are generated with a a very simple optimizer
-(differential evolution). Further, our DE  is actually much simpler
-than a standard implementation. Recall from Algorithm~1 that
-DE explores a {\em Population} of size {\em np=10}. This is a very small population size:
-the standard recommendation is to set {\em np} to be ten times larger than the number
-of attributes being optimized~\cite{stron97}
+\subsection{Tuning Can  Improves Performance Scores}\label{sect:precision}
 
-The results of this paper are presented
+\fig{precisionbars} shows precision results before and after tuning using three different learners.
+For each data set, the maximum precision values for each data set are shown in {\bf bold}.
 
-\section{Discussion}
+These results offer support for the prior conclusions of  
+ Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
+\bi
+\item
+Untuned CART is indeed the worst learner (none of its
+untuned results are best and {\bf bold}). 
+\item 
+In $\frac{15}{17}$ cases, untuned Random Forest out-performs  untuned CART.  
+\ei
+Some of the data sets in \fig{precisionbars} proved challenging for all learners;
+e.g. the precision results for {\em ivy} are less
+that impressive.
+To some extend, this can be explained by
+the properties of of the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare).
 
-\section{Related Work}
+That said,  tuning can improve those poor performing detectors:
+\bi
+\item
+For {\em xercesV0}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 85\% precision.  
+\item A similar pattern can be seen in results from {\em camelV0},   and {\em jeditV2}.
+In those two data sets, nearly all the precision values are   low {\em except} for
+tuned WHERE that scored 83\% and 98\%.
+\ei
+Finally, note the  {\em jeditV2} result for the WHERE learner.
+Here, tuning changes precision from 2\% to 98\%.
 
-Tuning in efforts estimation, software engineering.
+\fig{deltas} shows that tuning usually has a positive effect on performance scores. This figure sorts
+the deltas in the precision and the F-measure    between tuned and untuned learners. Our reading of this
+figure is that, overall, tuning rarely makes performance   worse and usually can make it much better.
 
-Defect Prediction
+\begin{figure}[!t]
+\renewcommand{\baselinestretch}{0.8}
 
-\section{Threats to Validity}
+\scriptsize
 
-Internal and external threats
+\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
+%\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
+      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
+  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
+antV0 & 30 &         & {\bf 89} & {\rfour} & 27 &         & {\bf 89} & {\rfour} & 39 &         & {\bf 89 }& {\rfour}\\
+antV1 & 32 & {\rtwo} & {\bf 74} & {\rfour} & 41 & {\rtwo} & {\bf 74 }& {\rfour} & 43 & {\rtwo} & 0 &        \\
+antV2 & {\bf 78} & {\rfour} & {\bf 78} & {\rfour} & 52 &         & 68 & {\rthree} & 66 & {\rtwo} & 67 & {\rtwo}\\
+camelV0 & {\bf 83} & {\rfour} & {\bf 83} & {\rfour} & 26 &         & 33 &         & 34 &         & 45 & {\rone}\\
+camelV1 & 22 &         & {\bf 28} & {\rfour} & 23 &         & 24 & {\rone} & {\bf 28} & {\rfour} & {\bf 28} & {\rfour}\\
+ivy & 16 &         & {\bf 23} & {\rfour} & 18 & {\rone} & 21 & {\rthree} & 21 & {\rthree} & 20 & {\rtwo}\\
+jeditV0 & 35 &         & {\bf 75} & {\rfour} & 49 & {\rone} & 56 & {\rtwo} & 50 & {\rone} & 48 & {\rone}\\
+jeditV1 & 24 &         & {\bf 87} & {\rfour} & 28 &         & 86 & {\rfour} & 36 &         & 39 & {\rone}\\
+jeditV2 & 2 &         & {\bf 98 }& {\rfour} & 3 &         & 18 &         & 5 &         & 5 &        \\
+log4j & 94 &         & {\bf 100} & {\rfour} & 97 & {\rtwo} & {\bf 100} & {\rfour} & {\bf 100} & {\rfour} & {\bf 100 }& {\rfour}\\
+lucene & 61 &         & 74 & {\rfour} & 67 & {\rone} & 70 & {\rtwo} & 72 & {\rthree} & {\bf 77} & {\rfour}\\
+poiV0 & 70 &         & 68 &         & 77 & {\rfour} & 72 & {\rone} & {\bf 79} & {\rfour} & 76 & {\rthree}\\
+poiV1 & {\bf  100} & {\rfour} & 90 & {\rthree} & 73 &         & 89 & {\rtwo} & 81 & {\rone} & {\bf 100} & {\rfour}\\
+synapse & 66 &         & 66 &         & 71 & {\rone} & {\bf 100} & {\rfour} & 59 &         & 80 & {\rtwo}\\
+velocity & 34 &         & 39 & {\rthree} & 34 &         & 40 & {\rfour} & 40 & {\rfour} & {\bf 41} & {\rfour}\\
+xercesV0 & 13 &         & {\bf 85} & {\rfour} & 14 &         & 13 &         & 15 &         & 13 &        \\
+xercesV1 & {\bf 56} & {\rfour} & 26 &         & 50 & {\rthree} & 26 &         & 41 & {\rtwo} & 26 &        \\
+\end{tabular}
+\caption{Precision results (best results  shown in {\bf bold}).}
+\label{fig:precisionbars}
+\end{figure}
 
-\section{Conclusion}
+\begin{figure}[!b]
+\begin{center}
+\includegraphics[width=1.25in]{precision1.pdf}\includegraphics[width=1.25in]{F1.pdf}
+ \end{center}
+\caption{Deltas in performance  seen in \fig{precisionbars} (left)
+and \fig{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
+ \end{figure}
+
+\subsection{Tuning Changes Learner Rankings}\label{sect:rank}
+Researchers often use performance criteria to assert that one learner is better is another~\cite{lessmann2008benchmarking,hall11,me07b}.
+Such conclusions are   not reliable since they can change when we elect to tune for different goals.
+
+For example, given the poor showing of untuned CART and the good performance of tuned WHERE
+in   \fig{precisionbars}, we might recommend
+{\em not} to use CART and {\em always} used tuned WHERE. In turns out that this
+conclusion is not stable across the tuning process.
+
+\fig{fbars} shows what happens when we tune for the f-measure. 
+As before, untuned Random Forest generally beats CART. However:
+\bi
+\item
+In  a result that is the direct opposite of   
+ Lessmann et al.~\cite{lessmann2008benchmarking}, tuned CART does better than Random Forest;
+ \item 
+ In another result that is the reverse of \fig{precisionbars}, tuned WHERE is not necessarily
+ any better than anything else.
+ \ei
+The lesson here is that, given a particular task (e.g. optimizing for precision), tuning can offer
+substantial benefits. However, when that task changes (e.g. to optimizing for the F-measure),
+it should not be assumed that conclusions from the previous tuning will hold in the new context.
+In practice, this means that tuning needs to be repeated for each new context.
+
+\begin{figure}[!t]
+\renewcommand{\baselinestretch}{0.8}
+
+\scriptsize  
+~~~\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
+      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
+  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
+antV0 & {\bf 39} & {\rfour} & 25 & {\rtwo} & 32 & {\rthree} & 31 & {\rthree} & {\bf 39} & {\rfour} & 12 &        \\
+antV1 & 11 &         & 6 &         & 40 & {\rfour} & {\bf 45} & {\rfour} & 39 & {\rfour} & 44 & {\rfour}\\
+antV2 & 0 &         & {\bf 87} & {\rfour} & 44 & {\rtwo} & 1 &         & 50 & {\rtwo} & 51 & {\rtwo}\\
+camelV0 & 0 &         & 28 & {\rfour} & 9 & {\rone} & 28 & {\rfour} & {\bf 34} & {\rfour} & 30 & {\rfour}\\
+camelV1 & {\bf 34} & {\rfour} & {\bf 34} & {\rfour} & 31 &         & 32 & {\rone} & 33 & {\rthree} & 31 &        \\
+ivyV0 & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
+jeditV0 & 50 &         & 56 & {\rtwo} & 56 & {\rtwo} & 54 & {\rone} & {\bf 61} & {\rfour} & 59 & {\rfour}\\
+jeditV1 & 37 & {\rone} & 33 &         & 36 &         & {\bf 49} & {\rfour} & 45 & {\rthree} & 47 & {\rfour}\\
+jeditV2 & 4 &         & 8 & {\rtwo} & 5 &         & {\bf 11} & {\rfour} & 9 & {\rthree} & 9 & {\rthree}\\
+log4jV0 & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
+luceneV0 & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
+poiV0 & {\bf 78} & {\rfour} & 64 &         & 74 & {\rthree} & 68 & {\rone} & 73 & {\rthree} & 69 & {\rone}\\
+poiV1 & 5 &         & {\bf 78} & {\rfour} & 21 & {\rone} & {\bf 78} & {\rfour} & 76 & {\rfour} & {\bf 78} & {\rfour}\\
+synapseV0 & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
+velocityV0 & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
+xercesV0 & 22 & {\rone} & 20 &         & 21 &         & {\bf 27} & {\rfour} & 23 & {\rtwo} & 20 &        \\
+xercesV1 & 25 &         & 39 & {\rone} & 18 &         & 53 & {\rthree} & 68 & {\rfour} & {\bf 73} & {\rfour}\\
+\end{tabular}
+\caption{F-value results (best results  shown in {\bf bold}).}
+\label{fig:fbars}
+\end{figure}
+
+\subsection{Tuning Changes Factors Rankings }\label{sect:import}
+
+Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.
+As above, we can show that such conclusions are not reliable since they can be changed by tuning.
+
+\fig{counts} shows how the objective goal (in this case,
+{\em pd} (recall) or precision, or the f-measure) changed what attributes were used
+in the decision tree learners
+(in this case, WHERE building trees to select for different clusters).
+
+Note that the counts in the {\em tuned} column are   usually
+different to those in the {\em default} columns (the tuned learners used more attributes
+than otherwise as witnessed by the taller columns of numbers in the ``tuned'' column).
+
+\subsection{Tuning is Easy}\label{sect:easy}
+
+In terms of the search space
+explored via tuning, optimizing defect prediction from static code
+measures is much {\em smaller} than standard optimization.
+
+To see this,
+recall from Algorithm~1 that
+DE explores a {\em Population} of size {\em np=10}. This is a very small population size since
+Rainer Storm (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
+of attributes being optimized~\cite{storn1997differential}.
+
+From \fig{parameters},
+we see that Storn would therefore recommend {\em np} values of
+90, 50, 60 for WHERE, CART and Random Forests (respectively). Yet we achieve our results
+using a constant {\em np=10}; i.e. $\frac{10}{90}, \frac{10}{50}, \frac{10}{60}$ of the
+recommended search space.
+
+Another measure showing that tuning is easy 
+(for static code defect predictors)
+is the number of evaluations required to complete optimization
+(see next section).
+
+\begin{figure}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|c c|c c|c c| c c }
+
+    &   \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{F} &  \multicolumn{2}{c|}{SUM}\\
+ &&&&&&&\\
+Features&   
+  default
+& tuned
+& default
+& tuned
+& default
+& tuned
+\\\hline
+
+noc &		  &    &    &   \\
+ca  &    &    &    &    &    &\\   
+max\_cc  &    &  1  &    &  1  &    &  2\\
+ce  &    &  1  &    &  2  &    &  3\\
+moa  &    &  1  &    &  2  &    &  3\\
+cbo  &    &  1  &    &  4  &    &  5\\
+avg\_cc  &    &  3  &    &  2  &    &  5\\
+lcom  &    &  3  &    &  3  &    &  6\\
+npm  &    &  5  &    &  4  &    &  9\\
+cbm  &  6  &  3  &  4  &  3  &  10  &  6\\
+amc  &  4  &  3  &  4  &  5  &  8  &  8\\
+rfc  &  4  &  5  &  4  &  9  &  8  &  14\\
+ic  &  7  &  4  &  9  &  4  &  16  &  8\\
+wmc  &  5  &  6  &  5  &  11  &  10  &  17\\
+dit  &  8  &  6  &  8  &  6  &  16  &  12\\
+lcom3  &  9  &  7  &  9  &  7  &  18  &  14\\
+loc  &  8  &  6  &  9  &  12  &  17  &  18\\
+cam  &  9  &  8  &  9  &  10  &  18  &  18\\
+dam  &  14  &  9  &  14  &  11  &  28  &  20\\
+mfa  &  16  &  11  &  16  &  13  &  32  &  24
+
+  \end{tabular}
+    \caption{Counts of features selected by different goals.Given that we are processing 17 data sets, the maximum counts for any 
+one cell in the ``precision'' or ``F'' column is 17.  
+    }\label{fig:counts}
+\end{figure}
+
+\begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{r|c |c |c |c |c |c }
+    \hline\hline
+    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
+    \hline
+    antV0 & 50 /  77.16 & 1.30 & 60 /  3.47 & 0.07 & 50 /  6.54 & 0.14\\
+    antV1 & 50 /  135.16 & 2.33 & 60 /  4.84 & 0.08 & 50 /  8.61 & 0.19\\
+    antV2 & 50 /  368.50 & 6.23 & 60 /  6.67 & 0.14 & 50 /  11.75 & 0.40\\
+    camelV0 & 50 /  479.03 & 8.25 & 60 /  11.73 & 0.18 & 60 /  15.69 & 0.31\\
+    camelV1 & 60 /  1551.51 & 26.87 & 60 /  18.47 & 0.28 & 80 /  37.96 & 0.73\\
+    ivyV0 & 80 /  83.80 & 1.01 & 50 /  3.07 & 0.07 & 60 /  7.63 & 0.17\\
+    jeditV0 & 60 /  349.99 & 5.95 & 70 /  8.33 & 0.11 & 50 /  13.40 & 0.30\\
+    jeditV1 & 50 /  442.35 & 7.48 & 70 /  8.63 & 0.11 & 70 /  15.52 & 0.37\\
+    jeditV2 & 50 /  360.04 & 7.90 & 60 /  8.63 & 0.12 & 60 /  14.33 & 0.38\\
+    log4jV0 & 60 /  97.23 & 1.49 & 70 /  3.31 & 0.06 & 80 /  8.79 & 0.17\\
+    luceneV0 & 70 /  206.41 & 2.89 & 80 /  6.90 & 0.08 & 60 /  10.30 & 0.25\\
+    poiV0 & 70 /  338.44 & 4.28 & 60 /  6.47 & 0.13 & 60 /  12.45 & 0.29\\
+    poiV1 & 60 /  468.73 & 7.95 & 50 /  7.24 & 0.14 & 70 /  17.66 & 0.30\\
+    synapseV0 & 50 /  111.30 & 1.87 & 60 /  3.85 & 0.05 & 60 /  7.82 & 0.15\\
+    velocityV0 & 60 /  192.83 & 2.66 & 90 /  6.11 & 0.06 & 80 /  12.99 & 0.22\\
+    xercesV0 & 70 /  139.33 & 2.23 & 60 /  6.47 & 0.11 & 50 /  8.89 & 0.25\\
+    xercesV1 & 50 /  759.82 & 13.11 & 50 /  8.62 & 0.14 & 60 /  16.90 & 0.37\\
+  \end{tabular}
+  \caption{Evaluations/runtimes  (in seconds), optimizing for  precision.  }\label{fig:etimes}
+\end{figure*}
+
+%%%%parameters for prec %%%%%%
+\begin{figure*}[!ht]
+
+\resizebox{\textwidth}{!}{
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.53& 0.57& 0.14& 0.67& 0.9& 1& 1& 0.72& 0.91& 0.96& 0.67& 1.0& 0.41& 0.24& 1& 0.47& 0.74\\ \cline{2-20}
+& infoPrune& 0.33& 0.68& 0.45& 0.53& 0.26& 0.81& 0.42& 0.39& 0.21& 0.05& 0.57& 0.35& 0.53& 0.68& 0.52& 0.56& 0.5& 0.75\\ \cline{2-20}
+& min\_sample\_split& 4& 3& 9& 9& 8& 6& 5& 2& 8& 6& 1& 3& 7& 1& 4& 6& 9& 7\\ \cline{2-20}
+& min\_Size& 0.5& 0.07& 0.26& 0.39& 0.73& 0.29& 0.49& 0.19& 0.44& 0.36& 1.0& 0.93& 0.45& 0.52& 0.22& 0.91& 0.19& 0.87\\ \cline{2-20}
+& wriggle& 0.2& 0.91& 0.63& 0.31& 0.18& 0.97& 0.74& 0.98& 0.59& 0.61& 0.34& 0.92& 0.71& 1& 0.95& 0.25& 0.01& 0.17\\ \cline{2-20}
+& depthMin& 2& 4& 5& 1& 5& 3& 1& 4& 1& 3& 3& 1& 3& 1& 2& 5& 3& 2\\ \cline{2-20}
+& depthMax& 10& 10& 17& 6& 6& 12& 19& 14& 15& 12& 12& 18& 19& 11& 8& 10& 11& 18\\ \cline{2-20}
+& wherePrune& False& True& True& True& False& True& True& True& True& False& False& True& True& True& True& False& True& True\\ \cline{2-20}
+& treePrune& True& True& True& False& False& False& True& True& False& False& False& False& False& True& False& False& True& False\\ \cline{2-20}
+\hline
+\multirow{4}{*}{CART}
+& threshold& 0.5& 0.83& 1& 0.99& 0.85& 0.9& 0.93& 1& 0.98& 0.88& 0.9& 0.7& 1& 0.63& 1& 1& 0.91& 0.81\\ \cline{2-20}
+& max\_feature& None& 0.01& 0.35& 0.35& 0.73& 0.63& 0.76& 0.76& 0.01& 0.13& 0.01& 0.83& 0.01& 0.02& 0.19& 0.28& 0.97& 0.1\\ \cline{2-20}
+& min\_samples\_split& 2& 18& 11& 6& 18& 20& 19& 3& 6& 14& 12& 8& 12& 17& 2& 11& 5& 16\\ \cline{2-20}
+& min\_samples\_leaf& 1& 3& 19& 6& 1& 4& 2& 14& 1& 2& 6& 2& 19& 4& 6& 15& 1& 17\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.86& 0.61& 0.71& 0.17& 1& 1& 0.87& 1& 1& 1& 0.97& 1& 0.41& 0.33& 1& 0.83& 0.94\\ \cline{2-20}
+& max\_feature& None& 0.05& 0.34& 0.31& 0.45& 0.54& 0.94& 0.93& 0.81& 0.01& 1& 0.69& 0.42& 1& 0.01& 0.01& 0.75& 1\\ \cline{2-20}
+& max\_leaf\_nodes& None& 16& 11& 38& 47& 18& 38& 27& 33& 16& 24& 41& 50& 15& 15& 30& 47& 28\\ \cline{2-20}
+& min\_samples\_split& 2& 3& 3& 4& 19& 17& 19& 18& 5& 13& 19& 1& 5& 2& 6& 7& 11& 11\\ \cline{2-20}
+& min\_samples\_leaf& 1& 7& 11& 10& 16& 8& 14& 4& 2& 7& 14& 12& 7& 10& 12& 7& 8& 4\\ \cline{2-20}
+& n\_estimators& 100& 85& 111& 99& 121& 128& 140& 141& 63& 100& 69& 99& 109& 123& 88& 125& 107& 131\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of prec.}\label{fig:preselect}
+\end{figure*}
+
+%%%%parameters for F %%%%%%
+\begin{figure*}[!ht]
+
+\resizebox{\textwidth}{!}{
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.02& 0.72& 0.97& 0.01& 0.87& 1& 0.59& 0.49& 0.77& 0.38& 0.25& 0.94& 0.01& 0.81& 0.53& 0.83& 0.99\\ \cline{2-20}
+& infoPrune& 0.33& 0.13& 0.64& 0.57& 0.33& 0.92& 0.37& 0.43& 0.53& 0.68& 0.56& 0.55& 0.74& 0.04& 0.34& 0.62& 1& 0.36\\ \cline{2-20}
+& min\_sample\_split& 4& 5& 1& 1& 5& 3& 3& 8& 9& 2& 4& 6& 2& 2& 2& 2& 9& 7\\ \cline{2-20}
+& min\_Size& 0.5& 0.59& 0.56& 0.29& 0.03& 0.64& 0.5& 1.0& 0.45& 1& 0.79& 0.22& 0.97& 1& 0.6& 0.68& 0.47& 0.35\\ \cline{2-20}
+& wriggle& 0.2& 0.51& 0.88& 0.92& 0.67& 0.81& 0.82& 0.45& 0.93& 0.39& 0.92& 0.16& 0.48& 0.22& 0.98& 0.7& 0.57& 0.02\\ \cline{2-20}
+& depthMin& 2& 4& 2& 5& 3& 2& 1& 5& 2& 2& 1& 3& 3& 3& 1& 4& 2& 5\\ \cline{2-20}
+& depthMax& 10& 16& 12& 1& 11& 19& 12& 20& 7& 8& 17& 19& 17& 12& 9& 9& 13& 3\\ \cline{2-20}
+& wherePrune& False& True& True& False& False& False& True& False& False& True& False& False& True& False& False& False& False& False\\ \cline{2-20}
+& treePrune& True& True& False& False& False& True& False& False& False& True& True& False& False& False& False& True& False& False\\ \cline{2-20}
+\hline
+\multirow{4}{*}{CART}
+& threshold& 0.5& 0.06& 0.63& 0.99& 0.01& 1& 0.98& 0.47& 0.74& 0.99& 0.36& 0.6& 0.95& 0.01& 0.01& 0.01& 0.43& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.3& 0.81& 0.01& 1& 0.98& 0.26& 0.36& 0.76& 0.29& 0.5& 0.12& 0.01& 0.01& 0.01& 0.16& 0.96& 0.01\\ \cline{2-20}
+& min\_samples\_split& 2& 13& 10& 15& 14& 13& 7& 7& 4& 5& 5& 15& 20& 8& 20& 6& 10& 2\\ \cline{2-20}
+& min\_samples\_leaf& 1& 9& 17& 1& 9& 1& 20& 1& 20& 17& 4& 9& 3& 12& 10& 16& 4& 8\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.92& 0.49& 0.24& 0.01& 1& 1& 1& 1& 1& 0.7& 0.21& 1& 0.01& 0.17& 0.4& 0.81& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.02& 0.55& 0.01& 0.01& 0.81& 0.52& 0.01& 0.76& 0.01& 0.01& 0.67& 0.3& 0.01& 0.06& 0.36& 0.34& 0.93\\ \cline{2-20}
+& max\_leaf\_nodes& None& 13& 10& 34& 10& 15& 25& 34& 24& 40& 20& 33& 14& 27& 40& 47& 44& 41\\ \cline{2-20}
+& min\_samples\_split& 2& 8& 1& 15& 15& 10& 11& 10& 5& 1& 9& 6& 7& 13& 13& 12& 15& 15\\ \cline{2-20}
+& min\_samples\_leaf& 1& 2& 14& 17& 19& 5& 13& 5& 2& 3& 11& 17& 2& 5& 9& 7& 18& 14\\ \cline{2-20}
+& n\_estimators& 100& 132& 50& 81& 150& 63& 59& 85& 141& 96& 106& 71& 95& 121& 135& 112& 104& 92\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of F.}\label{fig:fselect}
+\end{figure*}
+
+\subsection{Tuning is Fast}\label{sect:fast}
+
+The number of evaluations/runtimes used by our optimizers is shown in \fig{etimes}.
+WHERE's runtimes are slower than CART and Random Forest since WHERE has yet to benefit from decades
+of implementation experience with these older algorithms. For example, SciKitLearn's  CART and Random Forest
+ make extensive use of an underlying ``C'' library whereas WHERE is a purely interpreted Python.
+
+Looking over \fig{etimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
+improvements reported in this paper. 
+50 to 80 evaluations is  much less than our pre-experimental intuition.
+Prior to this paper, the authors have conducted numerous explorations of evolutionary algorithms
+for search-based SE applications~\cite{krall15,krall15:hm,fea02a,me07f,Green}. Based
+on that work, our expectations were that non-parametric evolutionary optimization would
+take thousands, if not millions, of evaluations of candidate tunings. Hence, originally,
+we used Storn's advise on the size of {\em np} and ran our optimizers for 24 hours. 
+Then, just
+to get a baseline, we tried {\em np=10} and the early stopping rules (number of lives used in
+Algorithm~1 on line 5) and obtained the results of this paper
+
+\subsection{Do not use ``off-the-shelf''  Default Tunings}\label{sect:variance}
+
+ \fig{preselect} and \fig{fselect} show the tunings learned by differential evolution. 
+The left hand side columns shows some standard default values. Note that:
+\bi
+\item
+The tunings learned by DE
+we often very different to the default. That is, to achieve the performance improvements seen in the paper,
+the default tuning parameters required a wide range of adjustments.
+\item The tunings learned by DE were different in different data sets and for different goals.
+That is, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
+sets are changed.
+\ei
+Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
+tuning is so easy and so fast (at least for defect predictors from static code attributes).
+\section{Conclusions}
+
+Prior to this work, our intuition was that tuning would change the behavior or a data miner. Nevertheless, we rarely tuned
+since we reasoned:
+\bi
+\item A data miner's default tunings have been well-explored by the developers of those algorithms. Hence, tuning may rarely improve a data miner.
+\item 
+Tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.
+\ei
+The results of this paper show that neither of these points is supportable, at least for learning
+defect detectors for static code attributes.
+
+Using differential evolution, this paper has found that it is remarkably simple to find effective tunings. We have seen in this paper that:
+\bi
+\item
+Tuning improves the performance scores of a predictor.
+That improvement is usually positive (see \fig{deltas} and sometimes
+it can be quite   dramatic (precision changing from 2\% to 98\%). 
+\item Tuning changes conclusions on what learners are better than others.
+Hence, it is time to revisit numerous prior publications of our own~\cite{me07b}
+and others~\cite{lessmann2008benchmarking,hall11}.
+\item
+Tuning changes conclusions about what factors are most important in software development.
+Once again, this means that old papers may need to be revised including those
+some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
+\item
+Data miners should not be used ``off-the-shelf'' with their default tunings. 
+\fig{preselect} and \fig{fselect}    show just how much tuning can alter default settings
+both for different data sets and for different goals. Hence, tuning needs to be repeated
+whenever data or goals are changed.
+\item
+Fortunately, the cost of find good tunings is not excessive since, at least for
+static code defect predictors, tuning is easy and fast.
+\ei
+These conclusions need two caveats.
+Firstly, the tuning results shown here only came from one  software analytics task 
+(defect prediction from static code attributes).
+There are many other kinds of software analytics tasks 
+(software development effort estimation, social network mining,
+detecting duplicate issue reports, etc) and the implication of this
+study for those tasks is unclear. 
+However,  those other tasks often use the same kinds of learners
+explored in this paper so it is quite possible that
+the conclusions of this paper apply to other SE analytics tasks as well.
+
+Secondly, it would be incorrect to say that this paper is arguing that
+software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
+In the age of the Internet and global access to software engineering data,
+there exists the  problem of information overload. {\em Something} must be done to
+allow analysts to make conclusions via an automatic analysis over a lot of data.
+The results of this paper is that for a particular local context
+(a specific data set and a specific goal) there exists  
+methods for optimizing the conclusions reached in that context.  
+Those conclusions
+may not generalize to other contexts but this  is not a council for despair. While there may
+not exist general conclusions, there does seem to exist general methods for finding
+local conclusions in a particular context. Further, as shown above, those
+methods may be very simple to implement and very fast to execute.
+
+\section{Future Work}
+ This paper has explored  {\em some} learners using {\em one}  optimizer. Hence, we can make
+no claim that DE is the {\em best} optimizer for {\em all} learners.
+Rather, our point is that there exists at least some learners
+whose performance can be dramatically improved by 
+at least one simple optimization scheme.  We hope that this work inspires
+much future work as this community develops and debugs best practices for tuning
+software analytics.
+
+More speculatively,  this notion of using an optimizer to tune
+a data miner might need revisiting. As noted by
+F\"{u}rnkranz~\cite{furnkranz05}, data mining is inherently a multi-objective optimization
+problem that seeks the smallest model with the highest performance, 
+that generalizes best for
+future examples (perhaps learned in minimal time using the least amount of data).
+In this view, we are using DE to optimize an optimizer. Perhaps a better approach might be
+to dispense with the separation of ``optimizer'' and ``learner'' and combine them both
+into one system that learns how to tune itself as it executes. If this view is useful,
+then instead of adding elaborations to data miners (as done in this paper, or by researchers
+exploring hyper-heuristics~\cite{jia2013learning}), it should be possible to radically simplify optimization and data
+mining with a single system that rapidly performs both task.
 
 \section{Acknowledgments}
+The work has partially funded by a National Science Foundation CISE CCF award \#1506586.
 
@@
  \scriptsize
-\bibliographystyle{unsrt}
+\bibliographystyle{plain}
+
+\balance
 \bibliography{tuningpredictor}

### 2015-03-16 dm101.tex
typos

@@
 to use standard data mining technology to learn where the probability of software defects is highest.
-Such defect  defect predictors learned from
+Such defect predictors learned from
 static code attributes are   {\em easy to
@@
 Other methods, like  manual code reviews, are far slower and far more labor-intensive.
-For example, depending on the review methods 8 to 20 LOC/minute can be
+For example, depending on the review methods, 8 to 20 LOC/minute can be
 inspected and this effort repeats for all members of the review team,

### 2015-03-16 learners.tex
typos

@@
 For this task, we do not use traditional parametric numeric optimizer  
-such as  gradient descent optimizers~\cite{saltelli00} that require models comprise
+such as  gradient descent optimizers~\cite{saltelli00} that require models comprised of
 differential functions (i.e. functions of real-valued variables whose derivative exists at each point in its domain).
 This is impractical  for  our learners since their internal states are   not a smoothly differential continuous function.
-Rather, learners being tuned  contains many regions with many different properties (tuning options can
+Rather, learners being tuned  contain many regions with many different properties (tuning options can
 drive the learner into very different modes with very different performance properties).
@@
 evolutionary algorithm based on decomposition~\cite{zhang07}) is a generic framework that decomposes a multiobjective optimization problem into many smaller single problems, then applies a second optimizer to each smaller subproblem, simultaneously.
-Other work in this arena are the response surface methods
+Other work in this area are the response surface methods
 that quickly find multiple approximations to the problem, each of which holds for a very tiny region.
@@
 DEs have been applied before for   parameter tuning (e.g. see~\cite{omran2005differential, chiha2012tuning}) but this is the first time they have been applied to
-optimizing defect prediction from static code attributes.
+optimize defect prediction from static code attributes.

### 2015-03-16 tuningpredictor.tex
typos

@@
 {\em without} first conducting a tuning optimization study.
-The implications for other kinds of software analytics is now an open and pressing questions.
+The implications for other kinds of software analytics are now open and pressing questions.
 
@@
 \section{Introduction}
-
-\begin{raggedleft}
-{\em ``So those who are last now will be first then, \\
-and those who are first will be last.''}\\ 
--- Matthew 20:16
-
- \end{raggedleft}
 
@@
 That was a very limited study, applied to a  single defect data set.
-The analysis of this paper is far more extensive and offers the following novel result:
+The analysis of this paper is far more extensive and offers the following novel results:
 \bi
@@
 
-Thirdly, it is standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
+Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
 we have defended that approach on methodological grounds arguing that it
@@
 
-In summary,it is now an open and pressing research issue to check if
+In summary, it is now an open and pressing research issue to check if
 analytics without parameter tuning is considered {\em harmful} or, at the 
@@
 not just the complex data miners discussed later in the paper but also 
-applies for even very simple  learning schemes.
+applies for even very simple  learning scheme.
 
@@
 
-That researcher might test that belief by using studying historical
+That researcher might test that belief by studying historical
 defect logs with 
@@
 This means that, as the loop progresses, the {\em Population} is full of increasiningly
-more valuable solutions. This, in turn, also improves  the candidates (which are generated
+more valuable solutions. This, in turn, also improves  the candidates, which are generated
 from the {\em Population}.
 
-For this experiments of this paper, we collect performance
+For the experiments of this paper, we collect performance
 values from a data mining, from which a {\em Goal} function extracts one 
-performance value$^{27}$ (so we tun this code many times, each time with
-a different {\em Goal}$^2$).  Technically, this makes this a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
+performance value$^{27}$ (so we run this code many times, each time with
+a different {\em Goal}$^2$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
 
@@
 
-The following experimental aims to compare the performance of three learners, tuned and untuned, on 17
+The following experiment aims to compare the performance of three learners, tuned and untuned, on 17
 sets of data.
@@
 It pertains to 
-open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene}, {\it 
-synapse}, {\it velocity}, {\it xalan} and {\it xerces}.
+open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
+{\it poi},{\it synapse}, {\it velocity} and {\it xerces}.
 
@@
 
-For this experiment, we uses data sets with at least three  
+For this experiment, we use data sets with at least three  
 consecutive releases  (where release $i+1$ was built after release $i$).
@@
 
-In {\em Better-faster-cheaper}, we seek  project changes that lead
-to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
+In {\em Better-faster-cheaper},   project want changes that lead
+to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
 
@@
    {\em Training} data is used by  differential evolution when it builds
-    a model (using one set of possible tunings) and that model is tested on {\em tunings}.
+    a model (using one set of possible tunings) and that model is tested on {\em tuning} data.
     Finally, the best model from by DE is applied to {\em testing}.  
@@
 
-All the above vary from zero to one. For $pf$, the {\em better} scores and {\em smaller}.
+All the above vary from zero to one. For $pf$, the {\em better} scores are {\em smaller}.
 For all other scores, the {\em better} scores are {\em larger}.
@@
 that impressive.
-To some extend, this can be explained by
-the properties of of the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare).
+To some extent, this can be explained by
+the properties of of the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).
 
@@
 \subsection{Tuning Changes Learner Rankings}\label{sect:rank}
-Researchers often use performance criteria to assert that one learner is better is another~\cite{lessmann2008benchmarking,hall11,me07b}.
+Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,hall11,me07b}.
 Such conclusions are   not reliable since they can change when we elect to tune for different goals.
@@
 camelV1 & {\bf 34} & {\rfour} & {\bf 34} & {\rfour} & 31 &         & 32 & {\rone} & 33 & {\rthree} & 31 &        \\
-ivyV0 & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
+ivy & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
 jeditV0 & 50 &         & 56 & {\rtwo} & 56 & {\rtwo} & 54 & {\rone} & {\bf 61} & {\rfour} & 59 & {\rfour}\\
@@
 jeditV2 & 4 &         & 8 & {\rtwo} & 5 &         & {\bf 11} & {\rfour} & 9 & {\rthree} & 9 & {\rthree}\\
-log4jV0 & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
-luceneV0 & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
+log4j & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
+lucene & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
 poiV0 & {\bf 78} & {\rfour} & 64 &         & 74 & {\rthree} & 68 & {\rone} & 73 & {\rthree} & 69 & {\rone}\\
 poiV1 & 5 &         & {\bf 78} & {\rfour} & 21 & {\rone} & {\bf 78} & {\rfour} & 76 & {\rfour} & {\bf 78} & {\rfour}\\
-synapseV0 & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
-velocityV0 & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
+synapse & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
+velocity & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
 xercesV0 & 22 & {\rone} & 20 &         & 21 &         & {\bf 27} & {\rfour} & 23 & {\rtwo} & 20 &        \\
@@
 \fig{counts} shows how the objective goal (in this case,
-{\em pd} (recall) or precision, or the f-measure) changed what attributes were used
+ precision or the f-measure) changed what attributes were used
 in the decision tree learners
@@
 DE explores a {\em Population} of size {\em np=10}. This is a very small population size since
-Rainer Storm (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
+Rainer Storn (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
 of attributes being optimized~\cite{storn1997differential}.
@@
     camelV1 & 60 /  1551.51 & 26.87 & 60 /  18.47 & 0.28 & 80 /  37.96 & 0.73\\
-    ivyV0 & 80 /  83.80 & 1.01 & 50 /  3.07 & 0.07 & 60 /  7.63 & 0.17\\
+    ivy & 80 /  83.80 & 1.01 & 50 /  3.07 & 0.07 & 60 /  7.63 & 0.17\\
     jeditV0 & 60 /  349.99 & 5.95 & 70 /  8.33 & 0.11 & 50 /  13.40 & 0.30\\
@@
     jeditV2 & 50 /  360.04 & 7.90 & 60 /  8.63 & 0.12 & 60 /  14.33 & 0.38\\
-    log4jV0 & 60 /  97.23 & 1.49 & 70 /  3.31 & 0.06 & 80 /  8.79 & 0.17\\
-    luceneV0 & 70 /  206.41 & 2.89 & 80 /  6.90 & 0.08 & 60 /  10.30 & 0.25\\
+    log4j & 60 /  97.23 & 1.49 & 70 /  3.31 & 0.06 & 80 /  8.79 & 0.17\\
+    lucene & 70 /  206.41 & 2.89 & 80 /  6.90 & 0.08 & 60 /  10.30 & 0.25\\
     poiV0 & 70 /  338.44 & 4.28 & 60 /  6.47 & 0.13 & 60 /  12.45 & 0.29\\
     poiV1 & 60 /  468.73 & 7.95 & 50 /  7.24 & 0.14 & 70 /  17.66 & 0.30\\
-    synapseV0 & 50 /  111.30 & 1.87 & 60 /  3.85 & 0.05 & 60 /  7.82 & 0.15\\
-    velocityV0 & 60 /  192.83 & 2.66 & 90 /  6.11 & 0.06 & 80 /  12.99 & 0.22\\
+    synapse & 50 /  111.30 & 1.87 & 60 /  3.85 & 0.05 & 60 /  7.82 & 0.15\\
+    velocity & 60 /  192.83 & 2.66 & 90 /  6.11 & 0.06 & 80 /  12.99 & 0.22\\
     xercesV0 & 70 /  139.33 & 2.23 & 60 /  6.47 & 0.11 & 50 /  8.89 & 0.25\\
@@
 
+%%%%time for F %%%%%%
+\begin{figure*}[!ht]
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{r|c |c |c |c |c |c }
+    \hline\hline
+    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
+    \hline
+    antV0 & 70 / 95.34 & 1.18 & 50 / 3.09 & 0.06 & 60 / 6.89 & 0.13\\
+    antV1 & 50 / 130.69 & 2.24 & 50 / 4.47 & 0.08 & 60 / 9.03 & 0.19\\
+    antV2 & 50 / 296.68 & 6.66 & 60 / 7.29 & 0.15 & 60 / 12.74 & 0.31\\
+    camelV0 & 60 / 496.70 & 8.01 & 60 / 10.43 & 0.17 & 70 / 17.32 & 0.30\\
+    camelV1 & 70 / 1732.99 & 23.35 & 60 / 15.93 & 0.22 & 60 / 24.71 & 0.71\\
+    ivy & 70 / 58.81 & 1.03 & 70 / 4.07 & 0.06 & 60 / 7.37 & 0.16\\
+    jeditV0 & 90 / 412.23 & 5.17 & 70 / 6.59 & 0.08 & 60 / 10.56 & 0.28\\
+    jeditV1 & 70 / 425.18 & 6.61 & 60 / 6.15 & 0.10 & 60 / 13.00 & 0.31\\
+    jeditV2 & 60 / 398.86 & 6.97 & 50 / 5.90 & 0.12 & 60 / 13.63 & 0.35\\
+    log4j & 50 / 68.17 & 1.37 & 60 / 2.46 & 0.04 & 70 / 6.37 & 0.15\\
+    lucene & 50 / 147.78 & 2.74 & 50 / 3.79 & 0.07 & 60 / 7.98 & 0.24\\
+    poiV0 & 60 / 251.48 & 3.90 & 60 / 5.65 & 0.09 & 70 / 11.25 & 0.30\\
+    poiV1 & 60 / 404.96 & 7.22 & 70 / 8.10 & 0.11 & 60 / 12.74 & 0.28\\
+    synapse & 50 / 95.37 & 1.80 & 60 / 3.69 & 0.06 & 60 / 7.65 & 0.14\\
+    velocity & 60 / 176.80 & 3.40 & 50 / 4.14 & 0.07 & 50 / 7.36 & 0.23\\
+    xercesV0 & 60 / 177.48 & 2.34 & 50 / 6.53 & 0.09 & 50 / 14.91 & 0.33\\
+    xercesV1 & 50 / 762.28 & 13.33 & 70/ 12.84 & 0.15 & 60/ 16.63 & 0.40\\
+  \end{tabular}
+  \caption{Evaluations/runtimes  (in seconds), optimizing for  ``F''.  }\label{fig:ftimes}
+\end{figure*}
+
 %%%%parameters for prec %%%%%%
@@
 
+\renewcommand{\baselinestretch}{0.9}
 \resizebox{\textwidth}{!}{
@@
     \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
  \hline
@@
 }
-  \caption{Parameters tuned on different models over the objective of prec.}\label{fig:preselect}
+  \caption{Parameters tuned on different models over the objective of precision.}\label{fig:preselect}
 \end{figure*}
@@
 \resizebox{\textwidth}{!}{
+\renewcommand{\baselinestretch}{0.9}
 \scriptsize
@@
 
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
  \hline
@@
 }
-  \caption{Parameters tuned on different models over the objective of F.}\label{fig:fselect}
+  \caption{Parameters tuned on different models over the objective of ``F''.}\label{fig:fselect}
 \end{figure*}
@@
 
-The number of evaluations/runtimes used by our optimizers is shown in \fig{etimes}.
+The number of evaluations/runtimes used by our optimizers is shown in \fig{etimes}
+and \fig{ftimes}.
 WHERE's runtimes are slower than CART and Random Forest since WHERE has yet to benefit from decades
@@
 
-Looking over \fig{etimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
+Looking over \fig{etimes} and \fig{ftimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
 improvements reported in this paper. 

### 2015-03-16 dm101.tex
Updates from ShareLaTeX

@@
 inspected and this effort repeats for all members of the review team,
-which can be as large as four or six~\cite{me02f}.
+which can be as large as four or six people~\cite{me02f}.
 

### 2015-03-16 learners.tex
Updates from ShareLaTeX

@@
 github.com/ai-se/where.
-
 \fig{parameters} shows the tuning parameters of these learners.
-WHERE has the most tuning parameters. This turns out
-to be important since, in the experiments shown below, tuned WHERE 
-out-performed the other learners-- a result suggesting that
-if you are going to tune learners, then use one with many tuning options.
 
@@
 
-From all the above methods, how do we select which optimizers to apply to tuning data miners.
+From all the above methods, how do we select which optimizers to apply to tuning data miners?
 Cohen~\cite{cohen95} advises comparing any supposedly more

### 2015-03-16 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \numberofauthors{1}
-\author{\alignauthor Wei Fu, Tim Menzies, Vivek Nair\\
+\author{\alignauthor Wei Fu, Tim Menzies \\
        \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
-       fuwei.ee, tim.menzies, vivekaxl@gmail.com}
+       fuwei.ee, tim.menzies@gmail.com}
 \maketitle
@@
 like test-case generation and code refactorings.
-
 To the best of our knowledge, this paper is the first extensive exploration 
@@
 (though see~\cite{cora10,balogh12,Minku13,minku13z} for tuning effort estimators).
-The one similar study  we can find in the period 2004 to 2014\footnote{See the GECCO and SSBSE proceedings at    goo.gl/2MY602 and goo.gl/uzvU8e.} was
-Bouktiff et al.~\cite{Bouktif06} who used  simulated annealing to tune Bayes classifiers.
-That was a very limited study, applied to a  single defect data set.
-The analysis of this paper is far more extensive and offers the following novel results:
+
+Prior to this work, our intuition was that tuning would change the behavior or a data miner, to some degree. Nevertheless, we rarely tuned our  defect predictors 
+since we reasoned
+that a data miner's default tunings have been well-explored by the developers of those algorithms, in which case
+tuning would not lead to large performance improvements.
+Also, we suspected that
+tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.
+
+The results of this paper show that neither of these points is supportable, att least when learning
+defect detectors from static code attributes since:
 \bi
@@
 encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
-can no longer be condoned. For example, one such default setting
-  in the Python \mbox{SciKitLearn} toolkit~\cite{scikit-learn}
-is to use $F=10$ decision trees in  Random Forest classifiers.
+can no longer be condoned. For example, suppose our default
+number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation). 
 Our optimizer settled on  $F$ values that were nowhere near that default:
 
+% {\scriptsize
+% \[F \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
+%                                 108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
+% \]}
+
 {\scriptsize
-\[F \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
-                                108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
+\[F \in \left\{\begin{array}{l} 50, 59, 63, 63, 69, 71, 81, 85,85, 88,\\
+                                92, 95, 96, 99, 99,  100, 104, 106, 107,\\
+                                109, 111, 112, 121, 121, 123, 125, 128,\\
+                                131, 132, 135, 140, 141, 141, 150   \end{array}\right\}
 \]}
@@
 {\em without} first conducting an tuning optimizations study.
+
+Before beginning, we digress for one important clarification.
+It would be incorrect to say that this paper is arguing that
+software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
+In the age of the Internet and global access to software engineering data,
+there exists the  problem of information overload. {\em Something} must be done to
+allow analysts to make conclusions via an automatic analysis over a lot of data.
+The results of this paper is that for a particular local context
+(a specific data set and a specific goal) there exists  
+methods for optimizing the conclusions reached in that context.  
+Those conclusions
+may not generalize to other contexts but this  is not a council for despair. While there may
+not exist general conclusions, there does seem to exist general methods for finding
+local conclusions in a particular context. Further, as shown above, those
+methods may be very simple to implement and very fast to execute.
 
@@
 \noindent
-We now explore how tuning can alter the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
+We now explore how tuning can change the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
 are used to call an inspection
@@
 
-\begin{figure}[!t]
+\begin{figure}[!b]
 
@@
 
-One   lesson from  \fig{pd1} is that the ``best'' tunings are context
-specific. For mission critical systems (e.g. a nuclear power plant), management
-might accept the cost of high false alarm rates if it meant increasing the probability
-of detecting errors. For such contexts, we might recommend some very small value of $T$.
-
-The other   lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
+The    lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
 detector can work just as well as seemingly better ones.
@@
 
-\section{Experimental Design}
+\section{Experimental Design}\label{sect:design}
 
@@
 This approach ensures   all treatments 
-are assessed on the same tests.
+are assessed on the same tests. Note that we did consider
+one other experimental design but rejected it for reasons of
+internal validity (see \tion{construct}).
 
@@
 
-\begin{figure}[!b]
+\begin{figure}[!t]
 \small
@@
 
-In {\em Better-faster-cheaper},   project want changes that lead
+In {\em Better-faster-cheaper},   managers want changes that lead
 to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
@@
 pf=&C/(A+C)\\ 
-pf'=& 1 - pf\\
-prec=precision=&D/(D+C) 
+prec=precision=&D/(D+C) \\
+F =&2*pd*prec/(pd + prec)
 \end{array}
@@
 For all other scores, the {\em better} scores are {\em larger}.
-
-The following results make no assumption that (e.g.) minimizing false alarms is 
+One technical detail:   {\em prec}
+and {\em F} refer to {\em both} the defect and non-defective modules. This is different to {\em pf} and {\em recall} which only
+refer to either non-defective or defective modules (repsectively).
+
+Our analysis results make no assumption that (e.g.) minimizing false alarms is 
 more important than maximizing   precision. That determination 
@@
 
-\begin{figure}[!b]
+\begin{figure}[!h]
 \begin{center}
@@
 
- \fig{preselect} and \fig{fselect} show the tunings learned by differential evolution. 
+ \fig{preselect} and \fig{fselect} show   tunings learned by DE. 
 The left hand side columns shows some standard default values. Note that:
@@
 The tunings learned by DE
-we often very different to the default. That is, to achieve the performance improvements seen in the paper,
+were often very different to the default. That is, to achieve the performance improvements seen in the paper,
 the default tuning parameters required a wide range of adjustments.
@@
 tuning is so easy and so fast (at least for defect predictors from static code attributes).
-\section{Conclusions}
-
-Prior to this work, our intuition was that tuning would change the behavior or a data miner. Nevertheless, we rarely tuned
-since we reasoned:
+
+\section{Reliability and Validity}\label{sect:construct}
+
+{\em Reliability} refers to the consistency of the results obtained
+from the research.  For example,   how well independent researchers
+could reproduce the study? To increase external
+reliability, this paper has taken care to either  clearly define our
+algorithms or use implementations from the public domain
+(SciKitLearn). Also, all the data used in this work is available
+on-line in the PROMISE code repository and all our algorithms
+are on-line at github.com/a-se/where.
+
+{\em Validity} refers to the extent to which a piece of research actually
+investigates what the researcher purports to investigate.
+{\em Internal validity} checks that if the differences found in
+the treatments can be ascribed to the treatments under study. 
+One internal validity issue with our experiments is the choice
+of {\em training, tuning, and testing} data sets discussed in 
+\tion{design}. Recall that while all our learners used the same
+{\em testing} data set, our untuned learners were only given
+access to {\em training} while DEs could get feedback from
+{\em training} and
+{\em tuning}.  This mean that, potentially,  the performance increases
+reported above are merely an artificat of the DEs being able to access
+more data. However:
 \bi
-\item A data miner's default tunings have been well-explored by the developers of those algorithms. Hence, tuning may rarely improve a data miner.
-\item 
-Tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.
+\item Note that
+DEs assess their performance using a model built from {\em training}
+then applied to the {\em tuning} data. If we gave the untuned
+learners double the training data, then this would be inherently
+biased against DEs.
+\item In practice, this is much ado about nothing. We have
+repeated all the experiments of this paper with the untuned
+learners building models from {\em training} + {\em tuning}.
+While the exact numbers found in this way
+may differ from the above in some small way, we can report that 
+those repeated runs do not substantively change the above conclusions.
 \ei
-The results of this paper show that neither of these points is supportable, at least for learning
-defect detectors for static code attributes.
-
-Using differential evolution, this paper has found that it is remarkably simple to find effective tunings. We have seen in this paper that:
-\bi
-\item
-Tuning improves the performance scores of a predictor.
-That improvement is usually positive (see \fig{deltas} and sometimes
-it can be quite   dramatic (precision changing from 2\% to 98\%). 
-\item Tuning changes conclusions on what learners are better than others.
-Hence, it is time to revisit numerous prior publications of our own~\cite{me07b}
-and others~\cite{lessmann2008benchmarking,hall11}.
-\item
-Tuning changes conclusions about what factors are most important in software development.
-Once again, this means that old papers may need to be revised including those
-some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
-\item
-Data miners should not be used ``off-the-shelf'' with their default tunings. 
-\fig{preselect} and \fig{fselect}    show just how much tuning can alter default settings
-both for different data sets and for different goals. Hence, tuning needs to be repeated
-whenever data or goals are changed.
-\item
-Fortunately, the cost of find good tunings is not excessive since, at least for
-static code defect predictors, tuning is easy and fast.
-\ei
-These conclusions need two caveats.
-Firstly, the tuning results shown here only came from one  software analytics task 
+{\em External validity} checks if the results are of relevance
+for other cases, or can be generalized from samples
+to populations.  
+The tuning results shown here only came from one  software analytics task 
 (defect prediction from static code attributes).
@@
 
-Secondly, it would be incorrect to say that this paper is arguing that
-software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
-In the age of the Internet and global access to software engineering data,
-there exists the  problem of information overload. {\em Something} must be done to
-allow analysts to make conclusions via an automatic analysis over a lot of data.
-The results of this paper is that for a particular local context
-(a specific data set and a specific goal) there exists  
-methods for optimizing the conclusions reached in that context.  
-Those conclusions
-may not generalize to other contexts but this  is not a council for despair. While there may
-not exist general conclusions, there does seem to exist general methods for finding
-local conclusions in a particular context. Further, as shown above, those
-methods may be very simple to implement and very fast to execute.
-
-\section{Future Work}
- This paper has explored  {\em some} learners using {\em one}  optimizer. Hence, we can make
-no claim that DE is the {\em best} optimizer for {\em all} learners.
-Rather, our point is that there exists at least some learners
-whose performance can be dramatically improved by 
-at least one simple optimization scheme.  We hope that this work inspires
-much future work as this community develops and debugs best practices for tuning
-software analytics.
-
-More speculatively,  this notion of using an optimizer to tune
-a data miner might need revisiting. As noted by
+That said, there exist some class of data mining papers for which
+tuning may not be required. Consider  Le Goues et al.'s 2012
+ICSE paper that used a evolutionary program to learn
+repairs to code~\cite{leGoues12}. The performance criteria
+in that paper was ``can we fix any of the known bugs?''. Note
+that this criteria is a ``{\em competency}'' statement, and
+not a ``{\em better than}'' statement (the difference being that
+one is 
+``can do'' and the other is ``can do better''). For such
+competency claims, tuning is not necessary. However, as soon
+as {\em better than} enters the performance criteria then this
+becomes a race between competing methods. In such a race,
+it is unfair to hobble one competitor with poor tunings.
+
+\section{Conclusions}
+
+When learning defect predictors for static code
+attributes,   analytics without parameter tuning is considered {\em harmful} and {\em misleading}:
+\bi
+\item Tuning improves the performance scores of a predictor.
+That improvement is usually positive (see \fig{deltas}) and sometimes
+it can be quite   dramatic (e.g. precision changing from 2\% to 98\%). \item 
+Tuning changes conclusions on what learners are better than others.
+Hence, it is time to revisit numerous prior publications of our own~\cite{me07b}
+and others~\cite{lessmann2008benchmarking,hall11}.
+\item
+Tuning changes also changes conclusions on what factors are most important in software development.
+Once again, this means that old papers may need to be revised including those
+some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
+\ei
+Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
+\fig{preselect} and \fig{fselect}    show just how much tuning can alter default settings
+both for different data sets and for different goals.
+
+Since the results from tuning are unstable,
+tuning needs to be repeated
+whenever data or goals are changed.
+Fortunately, the cost of find good tunings is not excessive since, at least for
+static code defect predictors, tuning is easy and fast.
+
+As to future work:
+\bi
+\item
+ As noted by
 F\"{u}rnkranz~\cite{furnkranz05}, data mining is inherently a multi-objective optimization
@@
 exploring hyper-heuristics~\cite{jia2013learning}), it should be possible to radically simplify optimization and data
-mining with a single system that rapidly performs both task.
+mining with a single system that rapidly performs both tasks.
+\item
+Another issue for future work is the implications of these
+conclusions to other kinds of software analytics.
+ This paper has explored  {\em some} learners using {\em one}  optimizer. Hence, we can make
+no claim that DE is the {\em best} optimizer for {\em all} learners.
+Rather, our point is that there exists at least some learners
+whose performance can be dramatically improved by 
+at least one simple optimization scheme.  We hope that this work inspires
+much future work as this community develops and debugs best practices for tuning
+software analytics.
+\ei
 

### 2015-03-16 dm101.tex
Updates from ShareLaTeX

@@
 	& infoPrune & 0.33 &[0.01,1]& The percentage of features to consider for the best 
-split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
-one is for clustering and the second one is building prediction model. we explicitly call Where-
-clustering tree and CART tree, respectively}. \\ \cline{2-5} 
+split to build its final decision tree. \\ \cline{2-5} 
 	 & min\_sample\_split & 4& [1,10]& The minimum number of samples required to split an internal node of
-CART tree. \\ \cline{2-5} 
+its final  decision tree. \\ \cline{2-5} 
 	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_sample 
-in Where-clustering trees  using  ${n\_samples}^ {min\_Size}$.
+in the initial clustering tree  using  ${n\_samples}^ {min\_Size}$.
 \end{tabular} \\ \cline{2-5} 
-    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
-	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
+    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  the initial clustering tree to be pruned\\ \cline{2-5}
+	 & depthMin & 2 & [1,6]&The minimum depth of the initial clustering tree below which no pruning for the
 clustering tree. \\ \cline{2-5} 
-	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
-	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
-	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
+	 & depthMax & 10 &[1,20]& The maximum depth of the initial clustering tree. \\ \cline{2-5} 
+	 & wherePrune & False &T/F& Whether or not to prune the initial clustering tree. \\ \cline{2-5}
+	 & treePrune & True &T/F& Whether or not to prune the final decision tree. \\ \cline{2-5} 
 \hline

### 2015-03-16 learners.tex
Updates from ShareLaTeX

@@
 This section describes this study's learners: CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
-and WHERE~\cite{menzies2013local}.
+and WHERE-based learner~\cite{menzies2013local}.
 The implementations
 for CART and Random Forest comes from 
-SciKitLearn~\cite{scikit-learn}.
+SciKitLearn~\cite{scikit-learn}. WHERE-based learner is a decision tree learner, which is built based on
+the clusters generated by the WHERE algorithm.
 WHERE is available from
@@
 
-This paper presents results with WHERE since, as shown below,
+This paper presents results with WHERE-based learner since, as shown below,
 it offers an interesting case study on the benefits of tuning.
@@
 
-CART, Random Forest, and WHERE are all  tree learners that divide a data set, then recurse
+CART, Random Forest, and WHERE-based learner are all  tree learners that divide a data set, then recurse
 on each split.
-If data contains more than {\em min sample split}, then a split is attempted.
-On the other hand, if a split contains no more than {\em min samples leaf}, then recursion stops. For CART and Random Forest use a 
-user-supplied constant for this parameter while
-WHERE computes $m$={\em min samples leaf} from the size of the data
-sets via  $m=\mathit{size}^\mathit{min size}$ (so, for WHERE,
-{\em min size} is the parameter to be tuned).
-
-These learners
+All these learners
 generate numeric predictions which are converted
 into binary ``yes/no'' decisions via \eq{yesno}. Hence, they all use the {\em threshold} value $T$ discussed in \tion{eg}.
+
+The splitting process is controlled by numerous tuning parameters.
+If data contains more than {\em min\_sample\_split}, then a split is attempted.
+On the other hand, if a split contains no more than {\em min\_samples\_leaf}, then recursion stops. For CART and Random Forest use a 
+user-supplied constant for this parameter while
+WHERE-based learner firstly computes this parameter $m$={\em min\_samples\_leaf} from the size of the data
+sets via  $m=\mathit{size}^\mathit{min\_size}$ to build an initial  clustering tree.
+Note that WHERE builds {\em two} trees: the initial clustering tree (to find similar sets of data)
+then a final decision tree (to learn rules that predict for each similar cluster)\footnote{A
+frequently asked question is why WHERE so complex?
+Would not   a single tree suffice? The answer is, as shown below,  tuned WHERE's twin-tree approach 
+generates very precise predictors.}.
+The tuning parameter  {\em min\_sample\_ split } controls the construction of the
+final decision tree (so, for WHERE-based learner,
+{\em min\_size} and {\em min\_sample\_split} are the parameters to be tuned).
 
@@
 \item
-WHERE projects the data on to a dimension it synthesizes from the raw data using
+When building the initial cluster tree, WHERE projects the data on to a dimension it synthesizes from the raw data using
 a process analogous to principle component analysis\footnote{
@@
 variables are effectively ignored since    they  do not contribute to the variance in the data.}.
-WHERE   divides  at the median point of that projection. On recursion,
-this generates a dendogram, the leaves of which are clusters of  very similar examples.
+WHERE  divides  at the median point of that projection.
+On recursion,
+this generates the initial clustering tree, the leaves of which are clusters of  very similar examples. After that, when building 
+the final decision tree, WHERE pretends its clusters are ``classes'', then 
+asks the InfoGain of the
+Fayyad-Irani discretizer~\cite{FayIra93Multi}, to rank the attriubutes, where {\em infoPrune} is used.
+WHERE's final decision tree generator then ignores everything except the top   {\em infoPrune} percent of the sorted
+attributes.
 \ei
-WHERE's {\em infoPrune} tuning parameter then choices the
-attributes   that best select  different clusters.
-WHERE pretends its clusters are ``classes'', then 
-asks the InfoGain of the
-Fayyad-Irani discretizer~\cite{FayIra93Multi}, to rank the attriubutes.
-WHERE then ignores everything except the top   {\em infoPrune} percent of the sorted
-attributes.
-
-Optionally, if the {\em where prune} option is set, 
-WHERE  continues to applies infogain criteria  recursively to build a tree that selects for the
-different clusters. If WHERE's {\em tree prune} parameter is enabled, then WHERE also prunes  superfluous sub-trees. For example, if a sub-tree and its parent have the same 
-majority cluster
-(one that occurs most frequently), then we prune the sub-tree.
-This tree pruning  sometimes
-prunes aways all  cluster selectors branches. To tame this effect, the {\em wriggle} parameter
-blocks tree pruning for at least the first {\em wriggle} number of initial branches.
-
-Other tuning parameters are learner specific. For example,
-{\em max feature} is used by
+Some tuning parameters are learner specific:
+\bi
+\item
+{\em Max feature} is used by
 CART and Random Forest to select the number of attributes
@@
 of attributes.
-Also,
-  {\em max leaf nodes} is the upper bound on leaf notes generated in a 
+\item
+  {\em Max leaf nodes} is the upper bound on leaf notes generated in a 
   Random Forest.
+ \item
+WHERE's initial clustering
+tree generation will always split up to {\em depthMin} number of branches.
+After that, WHERE will only split data if the mean performance scores of the two halves
+is ``trivially small'' (where ``trivially small'' is set by the   {\em wriggle} parameter). 
+\item
+WHERE's   {\em tree\_prune} setting controls how   
+WHERE prunes back superflous parts of the final decision tree. 
+If a decision sub-tree and its parent have the same 
+majority cluster
+(one that occurs most frequently), then if {\em tree\_prune} is enabled, we prune that decision sub-tree.
+\ei
 
@@
 
-\input{algo}
-
 Another approach uses

### 2015-03-16 tuningpredictor.tex
Updates from ShareLaTeX

@@
 since we reasoned
-that a data miner's default tunings have been well-explored by the developers of those algorithms, in which case
-tuning would not lead to large performance improvements.
+that a data miner's default tunings have been well-explored by the developers of those algorithms (in which case
+tuning would not lead to large performance improvements).
 Also, we suspected that
@@
 number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation). 
-Our optimizer settled on  $F$ values that were nowhere near that default:
+After tuning, we see that our optimizer often used $F$ values that were nowhere near that default:
 
@@
 not exist general conclusions, there does seem to exist general methods for finding
-local conclusions in a particular context. Further, as shown above, those
+local conclusions in a particular context. Further, as shown here, those
 methods may be very simple to implement and very fast to execute.
@@
 
+\input{algo}
+
 \section{Experimental Design}\label{sect:design}
@@
 
-\subsection{Data Sets}
+\subsection{Data Sets}\label{sect:dataa}
 
@@
 
-\begin{figure}[!t]
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-One style
-of measure is to check the {\em variability} of that predictor.
-For example,
-in their study on reproducibility of SE results,
- Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
-Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
-
-There exist other goals that combine defect prediction with other economic
-factors.
-Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
-say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
-that contain the most bugs.
-
-Yin et al. are concerned about
- {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
-These bugs occur  when (say) developers try to fix parts of the code
-where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
-for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
-
-In {\em Better-faster-cheaper},   managers want changes that lead
-to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
-
-Another  {\em  rush-to-market} approach is yet another economic-based optimization measure.
-A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
-as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
-in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
-used to subsequently fix any issues with version 1.0)~\cite{huang06}.\\\hline
-\end{tabular}
-\caption{Many ways to assess defect predictors.}\label{fig:criteria}
-\end{figure}
  \begin{figure*}[!t]
@@
 
-   \caption{Ratios of defective instances in each experimental data set. 
+   \caption{Data used in this data. 
    E.g., the top left data set has 20 defective classes out of 125 total.
-   This paper runs one experiment for each column
-   shown in this figure. The {\em training} set is used by an untuned learner
-   to build a model, which is then tested on the {\em testing} data.
-   {\em Training} data is used by  differential evolution when it builds
-    a model (using one set of possible tunings) and that model is tested on {\em tuning} data.
-    Finally, the best model from by DE is applied to {\em testing}.  
+   See \tion{dataa} for explanation of {\em training, tuning, testing} sets.
    }\label{fig:data1}
@@
 refer to either non-defective or defective modules (repsectively).
+
+\begin{figure}[!b]
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+One style
+of measure is to check the {\em variability} of that predictor.
+For example,
+in their study on reproducibility of SE results,
+ Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
+Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
+
+There exist other goals that combine defect prediction with other economic
+factors.
+Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
+say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
+that contain the most bugs.
+
+Yin et al. are concerned about
+ {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
+These bugs occur  when (say) developers try to fix parts of the code
+where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
+for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
+
+In {\em Better-faster-cheaper},   managers want changes that lead
+to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
+
+Another  {\em  rush-to-market} approach is yet another economic-based optimization measure.
+A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
+as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
+in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
+used to subsequently fix any issues with version 1.0)~\cite{huang06}.\\\hline
+\end{tabular}
+\caption{Many ways to assess defect predictors.}\label{fig:criteria}
+\end{figure}
 
@@
 
-\subsection{Tuning Can  Improves Performance Scores}\label{sect:precision}
-
-\fig{precisionbars} shows precision results before and after tuning using three different learners.
-For each data set, the maximum precision values for each data set are shown in {\bf bold}.
-
-These results offer support for the prior conclusions of  
- Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
-\bi
-\item
-Untuned CART is indeed the worst learner (none of its
-untuned results are best and {\bf bold}). 
-\item 
-In $\frac{15}{17}$ cases, untuned Random Forest out-performs  untuned CART.  
-\ei
-Some of the data sets in \fig{precisionbars} proved challenging for all learners;
-e.g. the precision results for {\em ivy} are less
-that impressive.
-To some extent, this can be explained by
-the properties of of the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).
-
-That said,  tuning can improve those poor performing detectors:
-\bi
-\item
-For {\em xercesV0}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 85\% precision.  
-\item A similar pattern can be seen in results from {\em camelV0},   and {\em jeditV2}.
-In those two data sets, nearly all the precision values are   low {\em except} for
-tuned WHERE that scored 83\% and 98\%.
-\ei
-Finally, note the  {\em jeditV2} result for the WHERE learner.
-Here, tuning changes precision from 2\% to 98\%.
-
-\fig{deltas} shows that tuning usually has a positive effect on performance scores. This figure sorts
-the deltas in the precision and the F-measure    between tuned and untuned learners. Our reading of this
-figure is that, overall, tuning rarely makes performance   worse and usually can make it much better.
-
-\begin{figure}[!t]
+\begin{figure}[!b]
 \renewcommand{\baselinestretch}{0.8}
@@
 
-\begin{figure}[!h]
+\subsection{Tuning Can  Improves Performance Scores}\label{sect:precision}
+
+\fig{precisionbars} shows precision results before and after tuning using three different learners.
+For each data set, the maximum precision values for each data set are shown in {\bf bold}.
+
+These results offer support for the prior conclusions of  
+ Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
+\bi
+\item
+Untuned CART is indeed the worst learner (none of its
+untuned results are best and {\bf bold}). 
+\item 
+In $\frac{15}{17}$ cases, untuned Random Forest out-performs  untuned CART.  
+\ei
+Some of the data sets in \fig{precisionbars} proved challenging for all learners;
+e.g. the precision results for {\em ivy} are less
+that impressive.
+To some extent, this is due to
+the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).
+
+That said,  tuning can improve those poor performing detectors:
+\bi
+\item
+For {\em xercesV0}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 85\% precision.  
+\item A similar pattern can be seen in results from {\em camelV0},   and {\em jeditV2}.
+In those two data sets, nearly all the precision values are   low {\em except} for
+tuned WHERE that scored 83\% and 98\%.
+\ei
+Finally, note the  {\em jeditV2} result for the WHERE learner.
+Here, tuning changes precision from 2\% to 98\%.
+
+\fig{deltas} shows that tuning usually has a positive effect on performance scores. This figure sorts
+the deltas in the precision and the F-measure    between tuned and untuned learners. Our reading of this
+figure is that, overall, tuning rarely makes performance   worse and usually can make it much better.
+
+\begin{figure}[!t]
 \begin{center}
@@
 
-\subsection{Tuning Changes Learner Rankings}\label{sect:rank}
+\subsection{Tuning Changes the Rankings of Learner  }\label{sect:rank}
 Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,hall11,me07b}.
@@
 
-\subsection{Tuning Changes Factors Rankings }\label{sect:import}
+\subsection{Tuning Changes the Ranking of Project Factors  }\label{sect:import}
 
 Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.
-As above, we can show that such conclusions are not reliable since they can be changed by tuning.
-
-\fig{counts} shows how the objective goal (in this case,
- precision or the f-measure) changed what attributes were used
-in the decision tree learners
-(in this case, WHERE building trees to select for different clusters).
-
+\fig{counts} shows that such conclusions are not reliable since they can be changed by tuning.
+This figure shows what attributes appeared in WHERE's final decision trees when optimizing for different goals.
 Note that the counts in the {\em tuned} column are   usually
@@
 \end{figure*}
+
+\subsection{Tuning is Fast}\label{sect:fast}
+
+The number of evaluations/runtimes used by our optimizers is shown in \fig{etimes}
+and \fig{ftimes}.
+WHERE's runtimes are slower than CART and Random Forest since WHERE has yet to benefit from decades
+of implementation experience with these older algorithms. For example, SciKitLearn's  CART and Random Forest
+ make extensive use of an underlying ``C'' library whereas WHERE is a purely interpreted Python.
+
+Looking over \fig{etimes} and \fig{ftimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
+improvements reported in this paper. 
+50 to 80 evaluations is  much less than our pre-experimental intuition.
+Prior to this paper, the authors have conducted numerous explorations of evolutionary algorithms
+for search-based SE applications~\cite{krall15,krall15:hm,fea02a,me07f,Green}. Based
+on that work, our expectations were that non-parametric evolutionary optimization would
+take thousands, if not millions, of evaluations of candidate tunings. Hence, originally,
+we used Storn's advise on the size of {\em np} and ran our optimizers for 24 hours. 
+Then, just
+to get a baseline, we tried {\em np=10} and the early stopping rules (number of lives used in
+Algorithm~1 on line 5) and obtained the results of this paper
+
+\subsection{Do not use ``off-the-shelf''  Default Tunings}\label{sect:variance}
+
+ \fig{preselect} and \fig{fselect} show   tunings learned by DE. 
+The left hand side columns shows some standard default values. Note that:
+\bi
+\item
+The tunings learned by DE
+were often very different to the default. That is, to achieve the performance improvements seen in the paper,
+the default tuning parameters required a wide range of adjustments.
+\item The tunings learned by DE were different in different data sets and for different goals.
+That is, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
+sets are changed.
+\ei
+Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
+tuning is so easy and so fast (at least for defect predictors from static code attributes).
 
@@
 \end{figure*}
-
-\subsection{Tuning is Fast}\label{sect:fast}
-
-The number of evaluations/runtimes used by our optimizers is shown in \fig{etimes}
-and \fig{ftimes}.
-WHERE's runtimes are slower than CART and Random Forest since WHERE has yet to benefit from decades
-of implementation experience with these older algorithms. For example, SciKitLearn's  CART and Random Forest
- make extensive use of an underlying ``C'' library whereas WHERE is a purely interpreted Python.
-
-Looking over \fig{etimes} and \fig{ftimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
-improvements reported in this paper. 
-50 to 80 evaluations is  much less than our pre-experimental intuition.
-Prior to this paper, the authors have conducted numerous explorations of evolutionary algorithms
-for search-based SE applications~\cite{krall15,krall15:hm,fea02a,me07f,Green}. Based
-on that work, our expectations were that non-parametric evolutionary optimization would
-take thousands, if not millions, of evaluations of candidate tunings. Hence, originally,
-we used Storn's advise on the size of {\em np} and ran our optimizers for 24 hours. 
-Then, just
-to get a baseline, we tried {\em np=10} and the early stopping rules (number of lives used in
-Algorithm~1 on line 5) and obtained the results of this paper
-
-\subsection{Do not use ``off-the-shelf''  Default Tunings}\label{sect:variance}
-
- \fig{preselect} and \fig{fselect} show   tunings learned by DE. 
-The left hand side columns shows some standard default values. Note that:
-\bi
-\item
-The tunings learned by DE
-were often very different to the default. That is, to achieve the performance improvements seen in the paper,
-the default tuning parameters required a wide range of adjustments.
-\item The tunings learned by DE were different in different data sets and for different goals.
-That is, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
-sets are changed.
-\ei
-Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
-tuning is so easy and so fast (at least for defect predictors from static code attributes).
 

### 2015-03-24 tuningpredictor.tex
Updates from ShareLaTeX

@@
 researchers in empirical SE
-use  data miners  to (e.g.) generate 
+use  data miners  to generate 
 defect predictors from static code measures.
@@
 
-The results of this paper show that neither of these points is supportable, att least when learning
+The results of this paper show that neither of these points is supportable, at least when learning
 defect detectors from static code attributes since:
@@
   Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
-antV0 & 30 &         & {\bf 89} & {\rfour} & 27 &         & {\bf 89} & {\rfour} & 39 &         & {\bf 89 }& {\rfour}\\
-antV1 & 32 & {\rtwo} & {\bf 74} & {\rfour} & 41 & {\rtwo} & {\bf 74 }& {\rfour} & 43 & {\rtwo} & 0 &        \\
-antV2 & {\bf 78} & {\rfour} & {\bf 78} & {\rfour} & 52 &         & 68 & {\rthree} & 66 & {\rtwo} & 67 & {\rtwo}\\
-camelV0 & {\bf 83} & {\rfour} & {\bf 83} & {\rfour} & 26 &         & 33 &         & 34 &         & 45 & {\rone}\\
-camelV1 & 22 &         & {\bf 28} & {\rfour} & 23 &         & 24 & {\rone} & {\bf 28} & {\rfour} & {\bf 28} & {\rfour}\\
-ivy & 16 &         & {\bf 23} & {\rfour} & 18 & {\rone} & 21 & {\rthree} & 21 & {\rthree} & 20 & {\rtwo}\\
-jeditV0 & 35 &         & {\bf 75} & {\rfour} & 49 & {\rone} & 56 & {\rtwo} & 50 & {\rone} & 48 & {\rone}\\
-jeditV1 & 24 &         & {\bf 87} & {\rfour} & 28 &         & 86 & {\rfour} & 36 &         & 39 & {\rone}\\
-jeditV2 & 2 &         & {\bf 98 }& {\rfour} & 3 &         & 18 &         & 5 &         & 5 &        \\
-log4j & 94 &         & {\bf 100} & {\rfour} & 97 & {\rtwo} & {\bf 100} & {\rfour} & {\bf 100} & {\rfour} & {\bf 100 }& {\rfour}\\
-lucene & 61 &         & 74 & {\rfour} & 67 & {\rone} & 70 & {\rtwo} & 72 & {\rthree} & {\bf 77} & {\rfour}\\
-poiV0 & 70 &         & 68 &         & 77 & {\rfour} & 72 & {\rone} & {\bf 79} & {\rfour} & 76 & {\rthree}\\
-poiV1 & {\bf  100} & {\rfour} & 90 & {\rthree} & 73 &         & 89 & {\rtwo} & 81 & {\rone} & {\bf 100} & {\rfour}\\
-synapse & 66 &         & 66 &         & 71 & {\rone} & {\bf 100} & {\rfour} & 59 &         & 80 & {\rtwo}\\
-velocity & 34 &         & 39 & {\rthree} & 34 &         & 40 & {\rfour} & 40 & {\rfour} & {\bf 41} & {\rfour}\\
-xercesV0 & 13 &         & {\bf 85} & {\rfour} & 14 &         & 13 &         & 15 &         & 13 &        \\
-xercesV1 & {\bf 56} & {\rfour} & 26 &         & 50 & {\rthree} & 26 &         & 41 & {\rtwo} & 26 &        \\
+antV0 & 30 &   & {\bf 89} &   & 27 &   & {\bf 89} &   & 28 &   & {\bf 89} &  \\
+antV1 & 32 &   & {\bf 74} &   & 36 &   & {\bf 74} &   & 41 &   & {\bf 74} &  \\
+antV2 & 78 &   & 52 &   & 52 &   & 56 &   & 64 &   & {\bf 100} &  \\
+camelV0 & {\bf 83} &   & {\bf 83} &   & 26 &   & 34 &   & 50 &   & 78 &  \\
+camelV1 & 22 &   & 81 &   & 24 &   & {\bf 83} &   & 25 &   & 31 &  \\
+ivy & 16 &   & {\bf 89} &   & 17 &   & 25 &   & 16 &   & 21 &  \\
+jeditV0 & 35 &   & 48 &   & 49 &   & {\bf 61} &   & 44 &   & 50 &  \\
+jeditV1 & 24 &   & {\bf 87} &   & 28 &   & 62 &   & 28 &   & 37 &  \\
+jeditV2 & 2 &   & {\bf 98} &   & 3 &   & 18 &   & 5 &   & 5 &  \\
+log4j & 94 &   & {\bf 100} &   & 97 &   & {\bf 100} &   & 99 &   & {\bf 100} &  \\
+lucene & 61 &   & 76 &   & 67 &   & 70 &   & 67 &   & {\bf 77} &  \\
+poiV0 & 74 &   & 74 &   & {\bf 79} &   & 75 &   & 77 &   & 78 &  \\
+poiV1 & {\bf 100} &   & 75 &   & 73 &   & 89 &   & 82 &   & {\bf 100} &  \\
+synapse & 66 &   & 66 &   & 71 &   & {\bf 100} &   & 65 &   & {\bf 100} &  \\
+velocity & 34 &   & {\bf 43} &   & 34 &   & 39 &   & 34 &   & 42 &  \\
+xercesV0 & 13 &   & {\bf 85} &   & 14 &   & 47 &   & 15 &   & 14 &  \\
+xercesV1 & {\bf 56} &   & 26 &   & 49 &   & 26 &   & 49 &   & 26 &  \\
 \end{tabular}
@@
 \item
-Untuned CART is indeed the worst learner (none of its
-untuned results are best and {\bf bold}). 
-\item 
-In $\frac{15}{17}$ cases, untuned Random Forest out-performs  untuned CART.  
+Untuned CART is indeed the worst learner (only one of its
+untuned results is best and {\bf bold}). 
+\item 
+In $\frac{13}{17}$ cases, the performance of untuned Random Forest is better than or equal to untuned CART.  
 \ei
-Some of the data sets in \fig{precisionbars} proved challenging for all learners;
-e.g. the precision results for {\em ivy} are less
-that impressive.
-To some extent, this is due to
-the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).
+% Some of the data sets in \fig{precisionbars} proved challenging for all learners;
+% e.g. the precision results for {\em ivy} are less
+% that impressive.
+% To some extent, this is due to
+% the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).
 
@@
 \item
-For {\em xercesV0}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 85\% precision.  
-\item A similar pattern can be seen in results from {\em camelV0},   and {\em jeditV2}.
+For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
+\item A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
 In those two data sets, nearly all the precision values are   low {\em except} for
-tuned WHERE that scored 83\% and 98\%.
+tuned WHERE that scored 89\% and 85\%.
 \ei
@@
   Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
-antV0 & {\bf 39} & {\rfour} & 25 & {\rtwo} & 32 & {\rthree} & 31 & {\rthree} & {\bf 39} & {\rfour} & 12 &        \\
-antV1 & 11 &         & 6 &         & 40 & {\rfour} & {\bf 45} & {\rfour} & 39 & {\rfour} & 44 & {\rfour}\\
-antV2 & 0 &         & {\bf 87} & {\rfour} & 44 & {\rtwo} & 1 &         & 50 & {\rtwo} & 51 & {\rtwo}\\
-camelV0 & 0 &         & 28 & {\rfour} & 9 & {\rone} & 28 & {\rfour} & {\bf 34} & {\rfour} & 30 & {\rfour}\\
-camelV1 & {\bf 34} & {\rfour} & {\bf 34} & {\rfour} & 31 &         & 32 & {\rone} & 33 & {\rthree} & 31 &        \\
-ivy & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
-jeditV0 & 50 &         & 56 & {\rtwo} & 56 & {\rtwo} & 54 & {\rone} & {\bf 61} & {\rfour} & 59 & {\rfour}\\
-jeditV1 & 37 & {\rone} & 33 &         & 36 &         & {\bf 49} & {\rfour} & 45 & {\rthree} & 47 & {\rfour}\\
-jeditV2 & 4 &         & 8 & {\rtwo} & 5 &         & {\bf 11} & {\rfour} & 9 & {\rthree} & 9 & {\rthree}\\
-log4j & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
-lucene & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
-poiV0 & {\bf 78} & {\rfour} & 64 &         & 74 & {\rthree} & 68 & {\rone} & 73 & {\rthree} & 69 & {\rone}\\
-poiV1 & 5 &         & {\bf 78} & {\rfour} & 21 & {\rone} & {\bf 78} & {\rfour} & 76 & {\rfour} & {\bf 78} & {\rfour}\\
-synapse & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
-velocity & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
-xercesV0 & 22 & {\rone} & 20 &         & 21 &         & {\bf 27} & {\rfour} & 23 & {\rtwo} & 20 &        \\
-xercesV1 & 25 &         & 39 & {\rone} & 18 &         & 53 & {\rthree} & 68 & {\rfour} & {\bf 73} & {\rfour}\\
+antV0 & 39 &   & 20 &   & 32 &   & 40 &   & {\bf 41} &   & 21 &  \\
+antV1 & 11 &   & 5 &   & 38 &   & 49 &   & 37 &   & {\bf 55} &  \\
+antV2 & 0 &   & 3 &   & 44 &   & {\bf 48} &   & 47 &   & 46 &  \\
+camelV0 & 0 &   & {\bf 91} &   & 9 &   & 28 &   & 4 &   & 31 &  \\
+camelV1 & 35 &   & 35 &   & 31 &   & 33 &   & {\bf 37} &   & 33 &  \\
+ivy & 28 &   & 32 &   & 28 &   & 30 &   & 27 &   & {\bf 33} &  \\
+jeditV0 & 50 &   & {\bf 57} &   & 56 &   & {\bf 57} &   & 56 &   & {\bf 57} &  \\
+jeditV1 & 37 &   & 38 &   & 36 &   & 45 &   & 43 &   & {\bf 49} &  \\
+jeditV2 & 4 &   & 6 &   & 5 &   & {\bf 9} &   & {\bf 9} &   & 8 &  \\
+log4j & {\bf 61} &   & 54 &   & 47 &   & 46 &   & 57 &   & 45 &  \\
+lucene & 70 &   & 74 &   & 56 &   & 74 &   & 70 &   & {\bf 75} &  \\
+poiV0 & 82 &   & 71 &   & 79 &   & 62 &   & {\bf 83} &   & 73 &  \\
+poiV1 & 5 &   & {\bf 78} &   & 21 &   & {\bf 78} &   & 19 &   & {\bf 78} &  \\
+synapse & 0 &   & 2 &   & 40 &   & 55 &   & 41 &   & {\bf 56} &  \\
+velocity & 51 &   & 51 &   & 49 &   & {\bf 53} &   & 51 &   & 51 &  \\
+xercesV0 & 22 &   & 23 &   & 21 &   & {\bf 27} &   & 24 &   & 20 &  \\
+xercesV1 & 23 &   & 4 &   & 18 &   & {\bf 47} &   & 18 &   & 40 &  \\
 \end{tabular}
@@
 
-noc &		  &    &    &   \\
-ca  &    &    &    &    &    &\\   
-max\_cc  &    &  1  &    &  1  &    &  2\\
-ce  &    &  1  &    &  2  &    &  3\\
-moa  &    &  1  &    &  2  &    &  3\\
-cbo  &    &  1  &    &  4  &    &  5\\
-avg\_cc  &    &  3  &    &  2  &    &  5\\
-lcom  &    &  3  &    &  3  &    &  6\\
-npm  &    &  5  &    &  4  &    &  9\\
-cbm  &  6  &  3  &  4  &  3  &  10  &  6\\
-amc  &  4  &  3  &  4  &  5  &  8  &  8\\
-rfc  &  4  &  5  &  4  &  9  &  8  &  14\\
-ic  &  7  &  4  &  9  &  4  &  16  &  8\\
-wmc  &  5  &  6  &  5  &  11  &  10  &  17\\
-dit  &  8  &  6  &  8  &  6  &  16  &  12\\
-lcom3  &  9  &  7  &  9  &  7  &  18  &  14\\
-loc  &  8  &  6  &  9  &  12  &  17  &  18\\
-cam  &  9  &  8  &  9  &  10  &  18  &  18\\
-dam  &  14  &  9  &  14  &  11  &  28  &  20\\
-mfa  &  16  &  11  &  16  &  13  &  32  &  24
+max\_cc& & & &  & & \\
+noc& & & & & & \\
+ca& & & & & & \\
+cbo& & 1& & & & 1\\
+moa& & 1& & & & 1\\
+ce& & 2& & 1& & 3\\
+avg\_cc& & 2& & 2& & 4\\
+npm& 1& 2& 1& 1&2 & 3\\
+lcom& 1& 2& 1& 1& 2& 3\\
+amc& 4& 2& 4& 2& 8& 4\\
+cbm& 5& 2& 5& 3& 10& 5\\
+rfc& 3& 6& 3& 8& 6& 14\\
+wmc& 5& 4& 5& 9& 10& 13\\
+dit& 8& 3& 7& 7& 15& 10\\
+ic& 8& 3& 8& 6& 16 & 9\\
+lcom3& 8& 6& 8& 8&16 & 14\\
+cam& 9& 7& 9& 7& 18& 14\\
+loc& 9& 5& 9& 11& 18& 16\\
+dam& 13& 6& 13& 11& 26& 17 \\
+mfa& 16& 9& 16& 9&32 & 18\\
 
@@
     \hline
-    antV0 & 50 /  77.16 & 1.30 & 60 /  3.47 & 0.07 & 50 /  6.54 & 0.14\\
-    antV1 & 50 /  135.16 & 2.33 & 60 /  4.84 & 0.08 & 50 /  8.61 & 0.19\\
-    antV2 & 50 /  368.50 & 6.23 & 60 /  6.67 & 0.14 & 50 /  11.75 & 0.40\\
-    camelV0 & 50 /  479.03 & 8.25 & 60 /  11.73 & 0.18 & 60 /  15.69 & 0.31\\
-    camelV1 & 60 /  1551.51 & 26.87 & 60 /  18.47 & 0.28 & 80 /  37.96 & 0.73\\
-    ivy & 80 /  83.80 & 1.01 & 50 /  3.07 & 0.07 & 60 /  7.63 & 0.17\\
-    jeditV0 & 60 /  349.99 & 5.95 & 70 /  8.33 & 0.11 & 50 /  13.40 & 0.30\\
-    jeditV1 & 50 /  442.35 & 7.48 & 70 /  8.63 & 0.11 & 70 /  15.52 & 0.37\\
-    jeditV2 & 50 /  360.04 & 7.90 & 60 /  8.63 & 0.12 & 60 /  14.33 & 0.38\\
-    log4j & 60 /  97.23 & 1.49 & 70 /  3.31 & 0.06 & 80 /  8.79 & 0.17\\
-    lucene & 70 /  206.41 & 2.89 & 80 /  6.90 & 0.08 & 60 /  10.30 & 0.25\\
-    poiV0 & 70 /  338.44 & 4.28 & 60 /  6.47 & 0.13 & 60 /  12.45 & 0.29\\
-    poiV1 & 60 /  468.73 & 7.95 & 50 /  7.24 & 0.14 & 70 /  17.66 & 0.30\\
-    synapse & 50 /  111.30 & 1.87 & 60 /  3.85 & 0.05 & 60 /  7.82 & 0.15\\
-    velocity & 60 /  192.83 & 2.66 & 90 /  6.11 & 0.06 & 80 /  12.99 & 0.22\\
-    xercesV0 & 70 /  139.33 & 2.23 & 60 /  6.47 & 0.11 & 50 /  8.89 & 0.25\\
-    xercesV1 & 50 /  759.82 & 13.11 & 50 /  8.62 & 0.14 & 60 /  16.90 & 0.37\\
+    antV0 & 50 / 90.18 & 1.57 & 60 / 4.36 & 0.09 & 50 / 8.12 & 0.18\\
+    antV1 & 50 / 174.67 & 2.90 & 50 / 6.35 & 0.10 & 50 / 11.77 & 0.27\\
+    antV2 & 50 / 403.63 & 6.92 & 70 / 9.71 & 0.16 & 60 / 13.28 & 0.35\\
+    camelV0 & 50 / 537.53 & 8.60 & 50 / 9.14 & 0.18 & 50 / 13.73 & 0.31\\
+    camelV1 & 60 / 1640.54 & 24.57 & 60 / 17.06 & 0.24 & 70 / 31.53 & 0.73\\
+    ivy & 70 / 77.75 & 1.02 & 60 / 3.86 & 0.06 & 50 / 8.00 & 0.17\\
+    jeditV0 & 80 / 472.57 & 5.49 & 60 / 6.30 & 0.09 & 70 / 13.01 & 0.30\\
+    jeditV1 & 60 / 489.45 & 6.82 & 70 / 7.61 & 0.11 & 60 / 12.87 & 0.32\\
+    jeditV2 & 50 / 435.43 & 7.21 & 50 / 6.46 & 0.12 & 90 / 20.34 & 0.37\\
+    log4j & 70 / 113.73 & 1.36 & 70 / 3.25 & 0.05 & 60 / 7.07 & 0.16\\
+    lucene & 70 / 224.39 & 2.70 & 50 / 4.07 & 0.08 & 50 / 8.87 & 0.26\\
+    poiV0 & 60 / 261.06 & 4.00 & 60 / 6.23 & 0.10 & 50 / 10.57 & 0.29\\
+    poiV1 & 80 / 607.85 & 7.18 & 60 / 7.69 & 0.13 & 50 / 11.39 & 0.29\\
+    synapse & 50 / 116.04 & 1.87 & 60 / 4.07 & 0.05 & 70 / 9.74 & 0.16\\
+    velocity & 60 / 195.27 & 2.75 & 60 / 4.49 & 0.06 & 80 / 12.15 & 0.21\\
+    xercesV0 & 60 / 143.69 & 2.17 & 70 / 7.26 & 0.09 & 60 / 10.28 & 0.23\\
+    xercesV1 & 50 / 794.50 & 13.37 & 50 / 8.24 & 0.15 & 60 / 14.54 & 0.38\\
+
   \end{tabular}
@@
     \hline
-    antV0 & 70 / 95.34 & 1.18 & 50 / 3.09 & 0.06 & 60 / 6.89 & 0.13\\
-    antV1 & 50 / 130.69 & 2.24 & 50 / 4.47 & 0.08 & 60 / 9.03 & 0.19\\
-    antV2 & 50 / 296.68 & 6.66 & 60 / 7.29 & 0.15 & 60 / 12.74 & 0.31\\
-    camelV0 & 60 / 496.70 & 8.01 & 60 / 10.43 & 0.17 & 70 / 17.32 & 0.30\\
-    camelV1 & 70 / 1732.99 & 23.35 & 60 / 15.93 & 0.22 & 60 / 24.71 & 0.71\\
-    ivy & 70 / 58.81 & 1.03 & 70 / 4.07 & 0.06 & 60 / 7.37 & 0.16\\
-    jeditV0 & 90 / 412.23 & 5.17 & 70 / 6.59 & 0.08 & 60 / 10.56 & 0.28\\
-    jeditV1 & 70 / 425.18 & 6.61 & 60 / 6.15 & 0.10 & 60 / 13.00 & 0.31\\
-    jeditV2 & 60 / 398.86 & 6.97 & 50 / 5.90 & 0.12 & 60 / 13.63 & 0.35\\
-    log4j & 50 / 68.17 & 1.37 & 60 / 2.46 & 0.04 & 70 / 6.37 & 0.15\\
-    lucene & 50 / 147.78 & 2.74 & 50 / 3.79 & 0.07 & 60 / 7.98 & 0.24\\
-    poiV0 & 60 / 251.48 & 3.90 & 60 / 5.65 & 0.09 & 70 / 11.25 & 0.30\\
-    poiV1 & 60 / 404.96 & 7.22 & 70 / 8.10 & 0.11 & 60 / 12.74 & 0.28\\
-    synapse & 50 / 95.37 & 1.80 & 60 / 3.69 & 0.06 & 60 / 7.65 & 0.14\\
-    velocity & 60 / 176.80 & 3.40 & 50 / 4.14 & 0.07 & 50 / 7.36 & 0.23\\
-    xercesV0 & 60 / 177.48 & 2.34 & 50 / 6.53 & 0.09 & 50 / 14.91 & 0.33\\
-    xercesV1 & 50 / 762.28 & 13.33 & 70/ 12.84 & 0.15 & 60/ 16.63 & 0.40\\
+    antV0 & 50 / 94.08 & 1.71 & 60 / 4.55 & 0.08 & 60 / 10.79 & 0.21\\
+    antV1 & 60 / 193.74 & 3.02 & 70 / 7.77 & 0.09 & 60 / 12.30 & 0.25\\
+    antV2 & 80 / 643.94 & 7.59 & 60 / 8.38 & 0.15 & 70 / 16.99 & 0.41\\
+    camelV0 & 60 / 662.56 & 9.97 & 60 / 13.19 & 0.23 & 80 / 26.11 & 0.32\\
+    camelV1 & 60 / 1800.64 & 24.25 & 50 / 15.02 & 0.28 & 50 / 28.52 & 0.78\\
+    ivy & 60 / 69.95 & 1.03 & 50 / 3.35 & 0.08 & 70 / 9.40 & 0.18\\
+    jeditV0 & 90 / 553.80 & 5.58 & 50 / 5.58 & 0.09 & 60 / 15.08 & 0.33\\
+    jeditV1 & 60 / 519.75 & 8.76 & 50 / 7.43 & 0.13 & 60 / 18.13 & 0.41\\
+    jeditV2 & 70 / 621.32 & 8.98 & 50 / 9.71 & 0.15 & 60 / 17.38 & 0.63\\
+    log4j & 70 / 125.29 & 1.73 & 50 / 2.90 & 0.06 & 60 / 8.76 & 0.19\\
+    lucene & 50 / 221.99 & 3.52 & 50 / 5.20 & 0.10 & 50 / 10.09 & 0.33\\
+    poiV0 & 60 / 327.48 & 5.13 & 50 / 6.56 & 0.11 & 50 / 12.88 & 0.36\\
+    poiV1 & 50 / 523.85 & 8.95 & 80 / 12.26 & 0.14 & 60 / 19.56 & 0.35\\
+    synapse & 70 / 148.23 & 1.91 & 60 / 3.96 & 0.06 & 60 / 8.19 & 0.16\\
+    velocity & 50 / 156.51 & 2.75 & 60 / 4.27 & 0.06 & 50 / 7.70 & 0.22\\
+    xercesV0 & 60 / 142.83 & 2.01 & 70 / 7.15 & 0.08 & 60 / 9.61 & 0.20\\
+    xercesV1 & 50 / 751.92 & 12.98 & 60 / 9.28 & 0.16 & 50 / 12.69 & 0.38\\
+
   \end{tabular}
@@
 \multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.53& 0.57& 0.14& 0.67& 0.9& 1& 1& 0.72& 0.91& 0.96& 0.67& 1.0& 0.41& 0.24& 1& 0.47& 0.74\\ \cline{2-20}
-& infoPrune& 0.33& 0.68& 0.45& 0.53& 0.26& 0.81& 0.42& 0.39& 0.21& 0.05& 0.57& 0.35& 0.53& 0.68& 0.52& 0.56& 0.5& 0.75\\ \cline{2-20}
-& min\_sample\_split& 4& 3& 9& 9& 8& 6& 5& 2& 8& 6& 1& 3& 7& 1& 4& 6& 9& 7\\ \cline{2-20}
-& min\_Size& 0.5& 0.07& 0.26& 0.39& 0.73& 0.29& 0.49& 0.19& 0.44& 0.36& 1.0& 0.93& 0.45& 0.52& 0.22& 0.91& 0.19& 0.87\\ \cline{2-20}
-& wriggle& 0.2& 0.91& 0.63& 0.31& 0.18& 0.97& 0.74& 0.98& 0.59& 0.61& 0.34& 0.92& 0.71& 1& 0.95& 0.25& 0.01& 0.17\\ \cline{2-20}
-& depthMin& 2& 4& 5& 1& 5& 3& 1& 4& 1& 3& 3& 1& 3& 1& 2& 5& 3& 2\\ \cline{2-20}
-& depthMax& 10& 10& 17& 6& 6& 12& 19& 14& 15& 12& 12& 18& 19& 11& 8& 10& 11& 18\\ \cline{2-20}
-& wherePrune& False& True& True& True& False& True& True& True& True& False& False& True& True& True& True& False& True& True\\ \cline{2-20}
-& treePrune& True& True& True& False& False& False& True& True& False& False& False& False& False& True& False& False& True& False\\ \cline{2-20}
+& threshold& 0.5& 0.98& 0.98& 0.43& 0.24& 0.64& 1& 1& 0.98& 0.98& 1& 1& 0.87& 0.59& 0.98& 1& 0.98& 0.98\\ \cline{2-20}
+& infoPrune& 0.33& 0.05& 0.05& 0.71& 0.54& 0.45& 0.41& 0.3& 0.05& 0.05& 0.54& 0.84& 0.01& 1& 0.05& 0.68& 0.43& 0.05\\ \cline{2-20}
+& min\_sample\_size& 4& 7& 7& 9& 8& 6& 10& 1& 5& 7& 8& 7& 9& 3& 7& 7& 1& 7\\ \cline{2-20}
+& min\_Size& 0.5& 0.51& 0.51& 0.59& 0.46& 0.13& 0.38& 0.66& 0.27& 0.51& 0.46& 0.47& 0.77& 0.48& 0.51& 0.66& 0.22& 0.51\\ \cline{2-20}
+& wriggle& 0.2& 0.6& 0.6& 0.83& 0.52& 0.19& 0.01& 0.26& 0.6& 0.6& 0.52& 0.19& 0.83& 0.01& 0.6& 0.26& 0.55& 0.6\\ \cline{2-20}
+& depthMin& 2& 1& 1& 2& 3& 5& 2& 3& 3& 1& 1& 2& 4& 2& 1& 3& 2& 1\\ \cline{2-20}
+& depthMax& 10& 8& 8& 13& 19& 19& 18& 7& 8& 8& 19& 1& 19& 18& 8& 11& 18& 8\\ \cline{2-20}
+& wherePrune& False& False& False& False& False& True& True& False& False& False& False& False& True& True& False& False& True& False\\ \cline{2-20}
+& treePrune& True& False& False& False& True& True& True& False& False& False& True& True& False& False& False& False& True& False\\ \cline{2-20}
 \hline
 \multirow{4}{*}{CART}
-& threshold& 0.5& 0.83& 1& 0.99& 0.85& 0.9& 0.93& 1& 0.98& 0.88& 0.9& 0.7& 1& 0.63& 1& 1& 0.91& 0.81\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.35& 0.35& 0.73& 0.63& 0.76& 0.76& 0.01& 0.13& 0.01& 0.83& 0.01& 0.02& 0.19& 0.28& 0.97& 0.1\\ \cline{2-20}
-& min\_samples\_split& 2& 18& 11& 6& 18& 20& 19& 3& 6& 14& 12& 8& 12& 17& 2& 11& 5& 16\\ \cline{2-20}
-& min\_samples\_leaf& 1& 3& 19& 6& 1& 4& 2& 14& 1& 2& 6& 2& 19& 4& 6& 15& 1& 17\\ \cline{2-20}
+& threshold& 0.5& 0.69& 0.99& 1& 0.3& 0.83& 1& 0.99& 0.58& 0.72& 1& 0.71& 0.46& 0.72& 1& 0.85& 1& 0.64\\ \cline{2-20}
+& max\_feature& None& 0.01& 0.58& 0.65& 0.66& 0.73& 0.67& 0.56& 0.01& 0.97& 0.54& 0.52& 0.32& 0.01& 0.74& 0.73& 0.01& 0.1\\ \cline{2-20}
+& min\_samples\_split& 2& 7& 16& 18& 5& 11& 6& 15& 6& 17& 4& 16& 12& 5& 14& 11& 4& 10\\ \cline{2-20}
+& min\_samples\_leaf& 1& 13& 14& 10& 4& 3& 15& 16& 9& 6& 7& 6& 1& 4& 6& 7& 11& 7\\ \cline{2-20}
+& max\_depth& None& 14& 1& 41& 34& 1& 22& 29& 1& 1& 1& 14& 19& 8& 40& 4& 1& 1\\ \cline{2-20}
 \hline
 \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.86& 0.61& 0.71& 0.17& 1& 1& 0.87& 1& 1& 1& 0.97& 1& 0.41& 0.33& 1& 0.83& 0.94\\ \cline{2-20}
-& max\_feature& None& 0.05& 0.34& 0.31& 0.45& 0.54& 0.94& 0.93& 0.81& 0.01& 1& 0.69& 0.42& 1& 0.01& 0.01& 0.75& 1\\ \cline{2-20}
-& max\_leaf\_nodes& None& 16& 11& 38& 47& 18& 38& 27& 33& 16& 24& 41& 50& 15& 15& 30& 47& 28\\ \cline{2-20}
-& min\_samples\_split& 2& 3& 3& 4& 19& 17& 19& 18& 5& 13& 19& 1& 5& 2& 6& 7& 11& 11\\ \cline{2-20}
-& min\_samples\_leaf& 1& 7& 11& 10& 16& 8& 14& 4& 2& 7& 14& 12& 7& 10& 12& 7& 8& 4\\ \cline{2-20}
-& n\_estimators& 100& 85& 111& 99& 121& 128& 140& 141& 63& 100& 69& 99& 109& 123& 88& 125& 107& 131\\ \cline{2-20}
+& threshold& 0.5& 0.84& 0.9& 0.83& 0.33& 1& 0.99& 0.91& 1& 1& 0.83& 0.98& 0.9& 0.86& 0.83& 1& 1& 1\\ \cline{2-20}
+& max\_feature& None& 0.61& 0.13& 0.89& 0.37& 0.01& 0.98& 0.52& 0.75& 0.35& 0.01& 0.98& 0.84& 0.73& 0.01& 0.48& 0.51& 0.01\\ \cline{2-20}
+& max\_leaf\_nodes& None& 37& 35& 38& 21& 36& 45& 10& 38& 10& 30& 20& 43& 11& 13& 15& 39& 10\\ \cline{2-20}
+& min\_samples\_split& 2& 8& 16& 17& 13& 14& 2& 3& 2& 2& 18& 19& 9& 4& 4& 9& 20& 1\\ \cline{2-20}
+& min\_samples\_leaf& 1& 19& 5& 2& 4& 2& 4& 7& 17& 7& 16& 12& 2& 3& 2& 2& 2& 3\\ \cline{2-20}
+& n\_estimators& 100& 138& 112& 77& 74& 125& 130& 107& 85& 96& 111& 103& 82& 59& 149& 150& 63& 58\\ \cline{2-20}
 \hline  \end{tabular}
@@
 \multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.02& 0.72& 0.97& 0.01& 0.87& 1& 0.59& 0.49& 0.77& 0.38& 0.25& 0.94& 0.01& 0.81& 0.53& 0.83& 0.99\\ \cline{2-20}
-& infoPrune& 0.33& 0.13& 0.64& 0.57& 0.33& 0.92& 0.37& 0.43& 0.53& 0.68& 0.56& 0.55& 0.74& 0.04& 0.34& 0.62& 1& 0.36\\ \cline{2-20}
-& min\_sample\_split& 4& 5& 1& 1& 5& 3& 3& 8& 9& 2& 4& 6& 2& 2& 2& 2& 9& 7\\ \cline{2-20}
-& min\_Size& 0.5& 0.59& 0.56& 0.29& 0.03& 0.64& 0.5& 1.0& 0.45& 1& 0.79& 0.22& 0.97& 1& 0.6& 0.68& 0.47& 0.35\\ \cline{2-20}
-& wriggle& 0.2& 0.51& 0.88& 0.92& 0.67& 0.81& 0.82& 0.45& 0.93& 0.39& 0.92& 0.16& 0.48& 0.22& 0.98& 0.7& 0.57& 0.02\\ \cline{2-20}
-& depthMin& 2& 4& 2& 5& 3& 2& 1& 5& 2& 2& 1& 3& 3& 3& 1& 4& 2& 5\\ \cline{2-20}
-& depthMax& 10& 16& 12& 1& 11& 19& 12& 20& 7& 8& 17& 19& 17& 12& 9& 9& 13& 3\\ \cline{2-20}
-& wherePrune& False& True& True& False& False& False& True& False& False& True& False& False& True& False& False& False& False& False\\ \cline{2-20}
-& treePrune& True& True& False& False& False& True& False& False& False& True& True& False& False& False& False& True& False& False\\ \cline{2-20}
+& threshold& 0.5& 0.04& 0.44& 0.44& 0.98& 0.65& 0.77& 1& 0.65& 0.98& 0.44& 0.44& 0.87& 0.04& 0.77& 0.24& 0.44& 0.77\\ \cline{2-20}
+& infoPrune& 0.33& 0.51& 0.68& 0.88& 0.47& 0.07& 0.31& 0.48& 0.68& 0.57& 0.12& 0.68& 0.01& 0.51& 0.14& 0.54& 0.68& 0.14\\ \cline{2-20}
+& min\_sample\_size& 4& 6& 4& 6& 1& 6& 8& 8& 4& 6& 7& 4& 9& 6& 2& 8& 4& 8\\ \cline{2-20}
+& min\_Size& 0.5& 0.18& 0.4& 0.56& 0.51& 0.65& 0.59& 0.97& 0.4& 0.51& 0.8& 0.4& 0.77& 0.18& 0.62& 0.46& 0.4& 0.66\\ \cline{2-20}
+& wriggle& 0.2& 0.25& 0.29& 0.76& 0.6& 0.63& 0.26& 1& 0.51& 0.17& 0.36& 0.51& 0.83& 0.25& 0.5& 0.52& 0.29& 0.26\\ \cline{2-20}
+& depthMin& 2& 3& 3& 3& 1& 5& 3& 2& 3& 5& 5& 3& 4& 3& 3& 3& 3& 3\\ \cline{2-20}
+& depthMax& 10& 16& 15& 15& 8& 19& 10& 7& 15& 5& 15& 15& 19& 16& 6& 19& 15& 10\\ \cline{2-20}
+& wherePrune& False& False& True& True& True& True& True& True& False& False& True& True& True& False& True& False& False& True\\ \cline{2-20}
+& treePrune& True& False& True& True& False& False& False& False& False& True& True& True& False& False& False& True& True& False\\ \cline{2-20}
 \hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.06& 0.63& 0.99& 0.01& 1& 0.98& 0.47& 0.74& 0.99& 0.36& 0.6& 0.95& 0.01& 0.01& 0.01& 0.43& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.3& 0.81& 0.01& 1& 0.98& 0.26& 0.36& 0.76& 0.29& 0.5& 0.12& 0.01& 0.01& 0.01& 0.16& 0.96& 0.01\\ \cline{2-20}
-& min\_samples\_split& 2& 13& 10& 15& 14& 13& 7& 7& 4& 5& 5& 15& 20& 8& 20& 6& 10& 2\\ \cline{2-20}
-& min\_samples\_leaf& 1& 9& 17& 1& 9& 1& 20& 1& 20& 17& 4& 9& 3& 12& 10& 16& 4& 8\\ \cline{2-20}
+\multirow{5}{*}{CART}
+& threshold& 0.5& 0.34& 0.25& 0.01& 0.01& 0.73& 0.53& 0.92& 0.8& 0.74& 0.54& 0.03& 0.91& 0.01& 0.01& 0.55& 1& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.01& 0.01& 0.29& 0.01& 0.46& 0.75& 0.79& 0.74& 0.41& 0.81& 0.61& 0.72& 0.01& 0.01& 0.01& 0.25& 0.18\\ \cline{2-20}
+& min\_samples\_split& 2& 18& 20& 12& 2& 15& 11& 2& 18& 13& 9& 17& 16& 10& 4& 8& 3& 15\\ \cline{2-20}
+& min\_samples\_leaf& 1& 19& 16& 15& 17& 1& 1& 13& 10& 4& 3& 7& 5& 20& 7& 8& 1& 6\\ \cline{2-20}
+& max\_depth& None& 12& 2& 15& 1& 41& 20& 44& 15& 13& 5& 23& 14& 1& 5& 17& 47& 13\\ \cline{2-20}
 \hline
 \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.92& 0.49& 0.24& 0.01& 1& 1& 1& 1& 1& 0.7& 0.21& 1& 0.01& 0.17& 0.4& 0.81& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.02& 0.55& 0.01& 0.01& 0.81& 0.52& 0.01& 0.76& 0.01& 0.01& 0.67& 0.3& 0.01& 0.06& 0.36& 0.34& 0.93\\ \cline{2-20}
-& max\_leaf\_nodes& None& 13& 10& 34& 10& 15& 25& 34& 24& 40& 20& 33& 14& 27& 40& 47& 44& 41\\ \cline{2-20}
-& min\_samples\_split& 2& 8& 1& 15& 15& 10& 11& 10& 5& 1& 9& 6& 7& 13& 13& 12& 15& 15\\ \cline{2-20}
-& min\_samples\_leaf& 1& 2& 14& 17& 19& 5& 13& 5& 2& 3& 11& 17& 2& 5& 9& 7& 18& 14\\ \cline{2-20}
-& n\_estimators& 100& 132& 50& 81& 150& 63& 59& 85& 141& 96& 106& 71& 95& 121& 135& 112& 104& 92\\ \cline{2-20}
+& threshold& 0.5& 0.01& 0.35& 0.3& 0.01& 0.9& 0.97& 0.63& 1& 0.73& 0.68& 0.01& 1.0& 0.01& 0.07& 0.22& 1& 0.82\\ \cline{2-20}
+& max\_feature& None& 0.63& 0.17& 0.01& 0.01& 0.88& 0.74& 0.76& 0.73& 0.01& 0.03& 0.39& 0.02& 0.01& 0.56& 0.36& 0.51& 0.89\\ \cline{2-20}
+& max\_leaf\_nodes& None& 40& 33& 46& 22& 11& 16& 38& 34& 30& 31& 12& 49& 25& 47& 15& 39& 24\\ \cline{2-20}
+& min\_samples\_split& 2& 10& 16& 20& 1& 1& 1& 1& 4& 20& 19& 11& 14& 2& 17& 19& 20& 19\\ \cline{2-20}
+& min\_samples\_leaf& 1& 4& 15& 9& 13& 18& 11& 3& 16& 17& 6& 10& 7& 19& 13& 11& 2& 14\\ \cline{2-20}
+& n\_estimators& 100& 120& 73& 75& 130& 97& 144& 125& 97& 80& 111& 96& 101& 50& 67& 74& 63& 66\\ \cline{2-20}
 \hline  \end{tabular}

### 2015-04-09 dm101.tex
Updates from ShareLaTeX

@@
 Since programming inherently
-introduces defects into  programs, is important to thoroughly {\em test} software before it is {\em used}.
-Such testing  can be very expensive.
+introduces defects into  programs, is important to test it before it is used.
+Testing is expensive.
 Software assessment budgets are finite
@@
 exponentially with assessment effort.
-Lowry et al. warn that  
-the state space explosion problem imposes
-strict limits on how much a system can be explored
-via automatic formal methods~\cite{lowrey98}.
-For standard black-box testing methods,
+For example, for  black-box testing methods,
 a {\em linear} increase
 in the confidence $C$ that we have found all defects
-can take {\em exponentially} more effort.
-For example, for one-in-a-thousand detects,
-moving $C$ from  
-90\% to 98\% nearly doubles the number of  tests (2301 to   3910 black box
-probes, respectively)\footnote{A randomly selected 
+can take {\em exponentially} more effort)\footnote{A randomly selected 
 input to a program will find a fault with probability $p$.
@@
  $N(C,p)=log(1 -
-C)/log(1-p)$. For example, $N(0.90,10^{-3})=2301$.}.
-
-Exponential costs quickly exhaust finite resources.
-Standard practice is to apply the best
-available assessment methods on the sections of the program that the
-best available domain knowledge declares is most critical.  We endorse
-this approach.  Clearly, the most critical sections require the best
-known assessment methods. However, this focus on certain sections
-can blind us to defects in other areas.
-Therefore, standard practice should be augmented
-with a  {\em
-lightweight sampling policy} to explore the rest of the system.  This
+C)/log(1-p)$. For example, $N(0.90,10^{-3})=2301$
+but $N(0.98,10^{-3})=3901$ (nearly double the number of tests).}.
+Exponential costs quickly exhaust finite resources so
+standard practice is to apply the best
+available  methods on code sections that seem   most critical. 
+But 
+Any method that focuses on parts of the code
+can blind us to defects in other areas. Some  {\em
+lightweight sampling policy} should be used to explore the rest of the system.  This
 sampling policy will always be incomplete.
@@
 One such lightweight sampling policy is defect predictors learned from static code attributes.
-Given software described using (for example) the attributes of \fig{ck}, it is possible
-to use standard data mining technology to learn where the probability of software defects is highest.
-Such defect predictors learned from
-static code attributes are   {\em easy to
+Given software described in (e.g.) the attributes of \fig{ck},   data miners can
+learn where the probability of software defects is highest.
+This approach is   {\em easy to
 use}, {\em widely-used}, and {\em useful} to use.
@@
 \hline
-\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
+\multirow{5}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
 	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
@@
 	 & min\_samples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{1-5}  
+node. \\ \cline{2-5} 
+     & max\_depth & None & [1, 50]& The maximum depth of the tree. \\
+     \cline{1-5}  
        \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
@@
 to decide which modules are worthy of manual inspections.
-For several  years, one of us (Menzies) worked on-site at the NASA software Independent Verification
-and Validation facility
-and he
-knows of several large government software contractors that won't
-review software modules {\em unless} tools like McCabe predict that
-they are fault prone.
 
@@
 of the defects in code~\cite{me07b}.
-Defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey).
-When the inspection teams focused on the modules that trigger the defect predictors, they found up to 70\% of the defects using just 40\% of their QA effort (measured in staff hours)~\cite{tosun10}.
-A subsequent study on the Turkish software
-compared how much code needs to be inspected using
-random selection vs. selection via defect
-predictors. Using random testing, 87\% of the files
-would have to be inspected in order to detect 87\%
-of the defects. Further, if the inspection process
-was restricted to the 25\% of the files that trigger
-the defect predictors, then 88\% of the defects
-could be found. That is, the same level of defect
-detection (after inspection) can be achieved using
-$(87-25)/87=71$\%less effort
-\cite{tosun09}.
-
-Defect predicting technology has been
-commercialized in many tools including {\it Predictive}~\cite{turner06}, a
- product suite to analyze and predict
-defects in software projects. Predictive was observed to
-highlight similar issues to those found   with the more expensive tools. Significantly,
-Predictive was able to faster process a larger code
-base than the more expensive tool~\cite{turner06}.
-
+Defect predictors have some level of generality:
+predictors learned at NASA~\cite{me07b} have also been found useful elsewhere
+(e.g. in Turkey~\cite{tosun10,tosun09}.
 The success of this method in  predictors in finding bugs is   markedly
@@
 Note only do static code defect predictors perform well compared to manual methods,
-they also are competititve with certain automatic methods.
-At ICSE'14, Rahman et al.~\cite{rahman14:icse} compared:
-\bi
-\item The static code analysis tools FindBugs, Jlint, and Pmd;
-\item Against static code defect predictors
-(which they called ``statistical defect prediction'') build using logistic regression.
-\ei
+they also are competitive with certain automatic methods.
+A recent study at ICSE'14, Rahman et al.~\cite{rahman14:icse} compared
+(a) static code analysis tools FindBugs, Jlint, and Pmd and (b)
+static code defect predictors
+(which they called ``statistical defect prediction'') built using logistic regression.
 They found  no significant differences in the cost-effectiveness

### 2015-04-09 learners.tex
Updates from ShareLaTeX

@@
-This section describes this study's learners: CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
-and WHERE-based learner~\cite{menzies2013local}.
-The implementations
-for CART and Random Forest comes from 
-SciKitLearn~\cite{scikit-learn}. WHERE-based learner is a decision tree learner, which is built based on
-the clusters generated by the WHERE algorithm.
+There are many ways to build defect predictors
+such as  CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
+and WHERE~\cite{menzies2013local}.
+For this study, we use the CART and Random Forest  from 
+SciKitLearn~\cite{scikit-learn} (and
 WHERE is available from
-github.com/ai-se/where.
-\fig{parameters} shows the tuning parameters of these learners.
+github.com/ai-se/where).
+\fig{parameters} shows these learner's tuning options.
 
-\subsection{Why Study These Algorithms?}
+ We use  these algorithms, for the following reasons.
+CART and Random Forest were mentioned in
+a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 21  
+learners for  defect prediction.
+That study ranked  CART  worst  and Random Forest as best.
+In a demonstration of the impact of tuning,
+this paper shows  we can {\em reverse} those rankings (sometimes)
+such that  the worst learner found by Lessmann et al. (CART) can perform better
+than Random Forest.
 
-This paper presents results with WHERE-based learner since, as shown below,
+This
+ paper also presents results with WHERE-based learner since, as shown below,
 it offers an interesting case study on the benefits of tuning.
-
-This paper also studies  CART and Random Forest since  these were used in 
-a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 21 different 
-learners for software defect prediction:
-\bi
-\item
-{\em Statistical classifiers:}
-Linear    discriminant analysis,
-Quadratic discriminant analysis,
-Logistic regression,
-Naive Bayes,
-Bayesian networks,
-Least-angle regression,
-Relevance vector machine,
-
-\item
-{\em Nearest neighbor methods:}
-k-nearest neighbor,
-K-Star
-
-\item
-{\em Neural networks:}
-Multi-Layer Perceptron,
-Radial bias functions,
-
-\item
-{\em Support vector machine-based classifiers:}
-Support vector machine,
-Lagrangian SVM
-Least squares SVM,
-Linear programming,
-Voted perceptron,
-
-\item
-{\em Decision-tree approaches:}
-C4.5,
-CART,
-Alternating DTs
-\item
-{\em Ensemble methods:}
-Random Forest,
-Logistic Model Tree.
-\ei
-In that study, CART  was ranked last  and Random Forest was
-the standout best method.
-We show below that we can reverse those rankings such that, under certain conditions,
-  the worst learner found by Lessmann et al. (CART) performed better
-than Random Forest.
 
@@
 \item
-{\em Max feature} is used by
+{\em Max\_feature} is used by
 CART and Random Forest to select the number of attributes
@@
 \item
-  {\em Max leaf nodes} is the upper bound on leaf notes generated in a 
+  {\em Max\_leaf\_nodes} is the upper bound on leaf notes generated in a 
   Random Forest.
+\item {\em Max\_depth} is the upper bound on the depth of the CART tree.  
  \item

### 2015-04-09 tuningpredictor.tex
Updates from ShareLaTeX

@@
-\documentclass{sig-alternative}
+% \documentclass{sig-alternative}
+\documentclass[conference]{IEEEtran}
 \usepackage{multirow}
@@
 \usepackage[shortlabels]{enumitem}
-\usepackage{times}
 
@@
 \DeclareMathSizes{7}{7}{7}{7} 
-\pagenumbering{arabic}
 \setlength{\columnsep}{7mm}
@@
 \begin{document}
-
-\conferenceinfo{FSE}{'15 Bergamo, Italy}
-\title{ Analytics Without Parameter Tuning Considered Harmful?}
-\numberofauthors{1}
-\author{\alignauthor Wei Fu, Tim Menzies \\
+% \conferenceinfo{FSE}{'15 Bergamo, Italy}
+\title{ Analytics Without  Tuning Considered Harmful?}
+% \numberofauthors{1}
+\author{\alignauthor Wei Fu, Tim Menzies, Xipeng Shen \\
        \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
-       fuwei.ee, tim.menzies@gmail.com}
+       fuwei.ee, tim.menzies, xipengshen@gmail.com}
 \maketitle
+\pagestype{plain}
 \begin{abstract}
 One of the ``black arts'' of data mining is setting the tuning
-parameters that control   choices within a data miner.  We offer a simple,
+parameters that control  the miner.  We offer a simple,
 automatic, and very effective  method for finding those tunings.
-
 For the purposes of learning
-software defect predictors this optimization strategy can quickly
+software defect predictors this  methid can quickly
 find  good tunings that  dramatically change   the performance of a learner.
@@
 it is no longer enough to just run a data miner and present the result
-{\em without} first conducting a tuning optimization study.
-The implications for other kinds of software analytics are now open and pressing questions.
+{\em without}  conducting a tuning optimization study.
+The implications for other kinds of  analytics is now  an open and pressing issue.
 
@@
 even for very large software systems~\cite{nagappan05}.
-In addition, they have  some generality
-across multiple projects: e.g. defect
-predictors developed at NASA~\cite{me07b} have also been successfully
-applied in Turkey~\cite{tosun09}.
-Such detectors reduce the effort required for 
-defect prediction: if 
-inspection teams let themselves be guided by defect predictors then
-they can find 80\% to 88\% of the defects
-after inspecting  20\% to 25\% of the code~\cite{ostrand04,tosun10}.
 
@@
 parameters that control  the choices within that data miner.
-Many researchers have applied automatic optimizers to find good tunings.
-The search-based SE community has   developed techniques
-for tuning that treat parameters  as a configuration
-search space~\cite{cora10,Krogmann10}. 
-The field of {\em hyper-heuristics} explores methods for auto-adapting
-options within the device searching for solutions~\cite{jia2013learning} in applications
-like test-case generation and code refactorings.
-To the best of our knowledge, this paper is the first extensive exploration 
-of applying automatic optimizers to tune data miners for defect prediction,
-(though see~\cite{cora10,balogh12,Minku13,minku13z} for tuning effort estimators).
-
 Prior to this work, our intuition was that tuning would change the behavior or a data miner, to some degree. Nevertheless, we rarely tuned our  defect predictors 
@@
 \item
-Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
-of those learners. 
+Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}. 
 \ei
@@
 
-Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
-we have defended that approach on methodological grounds arguing that it
+Thirdly, it is standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
+we have defended that approach, arguing that it
 encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
@@
 
+% {\scriptsize
+% \[F \in \left\{\begin{array}{l} 50, 59, 63, 63, 69, 71, 81, 85,85, 88,\\
+%                                 92, 95, 96, 99, 99,  100, 104, 106, 107,\\
+%                                 109, 111, 112, 121, 121, 123, 125, 128,\\
+%                                 131, 132, 135, 140, 141, 141, 150   \end{array}\right\}
+% \]}
+
 {\scriptsize
-\[F \in \left\{\begin{array}{l} 50, 59, 63, 63, 69, 71, 81, 85,85, 88,\\
-                                92, 95, 96, 99, 99,  100, 104, 106, 107,\\
-                                109, 111, 112, 121, 121, 123, 125, 128,\\
-                                131, 132, 135, 140, 141, 141, 150   \end{array}\right\}
+\[F \in \left\{\begin{array}{l} 50, 58, 59, 63, 63, 66, 67, 73, 74, 74, \\
+                                75, 77, 80, 82, 85, 96, 96, 97, 97, 101, \\
+                                103, 107, 111, 111, 112, 120, 125, 125,  \\
+                                130,130, 138, 144, 149, 150   \end{array}\right\}
 \]}
@@
 very least, {\em misleading}.
-Clearly, we must now doubt  conclusions based on
+Clearly, we  now doubt  conclusions based on
 ``off-the-shelf'' tunings.
@@
 
-Before beginning, we digress for one important clarification.
-It would be incorrect to say that this paper is arguing that
-software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
+Before beginning, we digress for one  clarification.
+This paper is {\bf not} arguing that
+software analytics is somehow wrong-headed or misguided.
 In the age of the Internet and global access to software engineering data,
@@
 Those conclusions
-may not generalize to other contexts but this  is not a council for despair. While there may
-not exist general conclusions, there does seem to exist general methods for finding
-local conclusions in a particular context. Further, as shown here, those
-methods may be very simple to implement and very fast to execute.
+may not generalize to other contexts but this  is not a council for despair. 
+As shown here, 
+there  exists general methods for finding
+local conclusions in a particular context. Further,
+those
+methods are  very simple to implement and very fast to execute.
 
@@
 
-This section offers a small demonstration
-of the impact of tuning parameters. It also demonstrates that this issue of tuning effects 
-not just the complex data miners discussed later in the paper but also 
-applies for even very simple  learning scheme.
-
-One way to generate a  defect predictor from
-static code is to use 
-linear  regression.
-This is a standard statistical
-method that fits a straight line to a set of points. The line
-offers a set of predicted values.
-If the points are somewhat
-scattered, then a single regression line cannot pass through all points and the distance from these predicted values to the actual
-values is a measure of the error associated with that line.
-Linear regression search for a line that minimizes that
+This section is  a  demonstration
+of the impact of tuning.
+
+Linear  regression fits a  line to a set of points in order to minimize  predictive
 error and maximizes the correlation\footnote{
@@
 correlation is  $c=S_{\mathit{PA}}/\sqrt{S_pS_a}$.}  denoted as $c$.
-
 Suppose  a researcher wants to use linear regression
@@
 mere lines of code for predicting
-software defects.  That researcher might argue that Halstead's cognitive approach to
+software defects.  That researcher might believe that Halstead's cognitive approach to
 software bugs is better suited to code refactoring tools since it offers 
@@
 
-That researcher might test that belief by studying historical
-defect logs with 
-linear regression. Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
+To test that belief, our  researcher applies regression to  some defect logs.
+ Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
 that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
@@
 Note that the Halstead correlation $c_2$
-is worse than those from lines of code $c_1$. This result  seems to suggest that
-despite their potential support for refactoring, our researchers should not use Halstead.
+is worse than the $c_1$ correlation  from lines of code-- which suggests
+ our researcher should not use Halstead .
 
@@
 at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
-problem, we can increase $T$. \fig{pd1} reports that the false alarm rate falls below
+problem, we can increase $T$:   the false alarm rate falls below
 20\% at $T=0.45$ (for Halstead).
 
-\begin{figure}[!b]
+\begin{figure}[!t]
 
@@
 
-The    lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
-detector can work just as well as seemingly better ones.
 Note that either the Halstead or LOC detector can reach some desired
@@
 This section is our standard introduction to defect prediction~\cite{me15:book1},
-plus   some new results from Rahman et al.'s   2014 FSE paper~\cite{rahman14:icse}.
+plus    new results from Rahman et al.~\cite{rahman14:icse}.
 
@@
 \end{center}
-\caption{OO measures used in our defect data sets.  Last line is
-the dependent attribute (whether a defect is reported to  a
-post-release bug-tracking system).}\label{fig:ck}
+\caption{OO measures used in our defect data sets.}\label{fig:ck}
 \end{figure*}
@@
 \begin{center}
-\includegraphics[width=1.25in]{precision1.pdf}\includegraphics[width=1.25in]{F1.pdf}
+\includegraphics[width=1.25in]{precision_W.eps}\includegraphics[width=1.25in]{F_W.eps}
  \end{center}
@@
 
-\begin{figure}[!t]
+\begin{figure}[!ht]
 

### 2015-04-09 dm101.tex
Updates from ShareLaTeX

@@
 a {\em linear} increase
-in the confidence $C$ that we have found all defects
+in the confidence $C$ of finding  defects
 can take {\em exponentially} more effort)\footnote{A randomly selected 
@@
 C)/log(1-p)$. For example, $N(0.90,10^{-3})=2301$
-but $N(0.98,10^{-3})=3901$ (nearly double the number of tests).}.
+but $N(0.98,10^{-3})=3901$; i.e. nearly double the number of tests.}.
 Exponential costs quickly exhaust finite resources so

### 2015-04-09 learners.tex
Updates from ShareLaTeX

@@
 github.com/ai-se/where).
-\fig{parameters} shows these learner's tuning options.
-
  We use  these algorithms, for the following reasons.
@@
 In a demonstration of the impact of tuning,
-this paper shows  we can {\em reverse} those rankings (sometimes)
-such that  the worst learner found by Lessmann et al. (CART) can perform better
-than Random Forest.
-
+this paper shows  we can {\em reverse} the conclusions of  Lessmann et al. such that CART
+performs just as well as
+ Random Forest.
 This
@@
 \subsection{Learners and Their Tunings}
+
+Our learners use the tuning parameters of \fig{parameters}. This section describes those parameters.
 
@@
 then a final decision tree (to learn rules that predict for each similar cluster)\footnote{A
-frequently asked question is why WHERE so complex?
-Would not   a single tree suffice? The answer is, as shown below,  tuned WHERE's twin-tree approach 
+frequently asked question is why does WHERE build two trees--
+would not   a single tree suffice? The answer is, as shown below,  tuned WHERE's twin-tree approach 
 generates very precise predictors.}.
@@
 Non-parametric  optimizers   make no assumption
-about the model being only differential functions. One such optimizer
-is simulated annealing. SA generates {\em new} solutions
- by randomly perturbing (a.k.a. ``mutating'') some part of an {\em old}
- solution.  {\em New} replaces {\em old} if (a) it scores higher; or
- (b) it reaches some probability set by a ``temperature'' constant. Initially,
- temperature is high so SA jumps to sub-optimal solutions (this allows
- the algorithm to escape from local minima). Subsequently, the
- ``temperature'' cools and SA only ever moves to better {\em new}
- solutions. 
- SA is often used in search-based SE
- e.g.~\cite{fea02a,me07f}, perhaps due to its simplicity.
-
-SA was invented   in the 1950s, when
- computer RAM was very small~\cite{kirkpatrick83}. A standard SA algorithm needs
- only space for three solutions {\em new, old} and the {\em best} seen so far.
-  In the 1960s, when more RAM became available, it became standard to
- generate many {\em new} mutants, and then combine together parts of
- promising solutions~\cite{goldberg79}.  Such {\em evolutionary
-   algorithms} (EA) work in {\em generations} over a population of
- candidate solutions.  Initially, the population is created at random.
- Subsequently, each generation makes use of select+crossover+mutate
- operators to pick promising solutions, mix them up in some way, and
- then slightly adjust them.
- EAs are also often used in search-based
- software engineering, particularly in test case generation~\cite{andrews07,andrews10}
- or refactoring~\cite{Weimer:2009}
-
- Later work focused on smarter  
- mutations. Tabu search and scatter search
- work to bias new mutations away from prior
- mutations~\cite{Glover1986563,Beausoleil2006426,Molina05sspmo:a,4455350}.
- Particle swarm
- optimization randomly mutates multiple solutions
- (which are called ``particles''), but biases those
- mutations towards the best solution seen by one
- particle and/or by the neighborhood around that
- particle~\cite{pan08}.
- Differential evolution mutates solutions by
- interpolating between items in the current
- population~\cite{storn1997differential}.
-
-Another approach uses
+about the internal structure of the model.
+There are many such optimizers:
+\bi
+\item
+Simulated annealing~\cite{fea02a,me07f};
+\item
+A wide range of genetic algorithms~\cite{goldberg79} augmented by
+techniques such as differential evolution~\cite{storn1997differential}, tabu search and scatter search~\cite{Glover1986563,Beausoleil2006426,Molina05sspmo:a,4455350};
+\item
+Particle swarm optimization~\cite{pan08}; 
+\item 
+Numerous ``decomposition approaches'' that uses
     heuristics to decompose the total space into   small problems,   then applies a
-    simpler optimizer to each region. 
-In $\mathcal{E}$-domination~\cite{deb05}, the  user is asked
-`what is the lower threshold $\mathcal{E}$ on the size of a useful effect?''. The solution space
-is then divided into boxes of size $\mathcal{E}$ and linked such that  the  set $X.\mathit{lower}$ contains boxes with worse objective scores that $X$.
-Solutions in pairs boxes are  quickly compared  using   small samples from each  and, if some box $X$ is found to be inferior, then it is quickly pruned along with all
-solutions in the $X.\mathit{lower}$ boxes.
-Later research generalized this approach. MOEA/D (multiobjective
-evolutionary algorithm based on decomposition~\cite{zhang07}) is a generic framework that decomposes a multiobjective optimization problem into many smaller single problems, then applies a second optimizer to each smaller subproblem, simultaneously.
-Other work in this area are the response surface methods
-that quickly find multiple approximations to the problem, each of which holds for a very tiny region.
-Each region has a ``slope'' and examples in that region are pushed along the slope towards better
-solutions~\cite{krall15,Zuluaga:13}.
-
- \subsubsection{Selecting a Tuning Algorithm}
-
+    simpler optimizer to each region including \mbox{$\varepsilon$-domination}~\cite{deb05} and MOEA/D ~\cite{zhang07};
+    \item 
+    Response surface methods~\cite{krall15,Zuluaga:13};
+    \item
+    And many others as well.
+    \ei
 From all the above methods, how do we select which optimizers to apply to tuning data miners?
-Cohen~\cite{cohen95} advises comparing any supposedly more
-sophisticated method against the simplest possible alternative. For
-example, in one study with ``floor effects'', Holte showed that,
-often, much of the performance of complex multi-level decision trees
-could be easily achieved using a much simpler single-level decision
-tree learner called 1R~\cite{holte93}. He therefore recommends a very simple rule learner
-(called ``1R'') as a
-kind of ``scout'' that can do a quick preliminary analysis of a data
-set and which can report back if that data really requires a more
-complex analysis.
+Cohen~\cite{cohen95} advises comparing new 
+ methods against the simplest possible alternative. 
+Holte~\cite{holte93} recommends using very simple  learners
+ as a
+kind of ``scout'' for a  preliminary analysis of a data
+set (to check if that data really requires a more
+complex analysis).
 
 To find our ``scout'',  we used engineering judgement to sort  the above algorithms from simplest to most complex.
-The three simplest optimizers are SA, $\mathcal{E}$-domination, and 
+Of the optimizers listed above, the simplest are are SA  and 
 differential evolution (each can be coded in less than a page of some high-level scripting language). Our reading of the current literature is that there are more  advocates for
 differential evolution than
-  SA or $\mathcal{E}$-domination:
+  SA:
   \bi
@@
   \item
- Vesterstrom and Thomsen~\cite{Vesterstrom04} report that DE is competitive with 
-   particle swarm optimization and a genetic algorithm. 
+ Vesterstrom and Thomsen~\cite{Vesterstrom04} found DE to be competitive with 
+   particle swarm optimization and other GAs.
    \ei

### 2015-04-09 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \maketitle 
-\pagestype{plain}
+\thispagestyle{plain}
+\pagestyle{plain}
 \begin{abstract}
@@
 use  data miners  to generate 
-defect predictors from static code measures.
+{\em defect predictors from static code measures}.
 Such   measures can be
@@
 One of the ``black arts'' of data mining is setting the tuning
-parameters that control  the choices within that data miner.
+parameters that control  the choices within a data miner.
 Prior to this work, our intuition was that tuning would change the behavior or a data miner, to some degree. Nevertheless, we rarely tuned our  defect predictors 
@@
 defect detectors from static code attributes since:
-\bi
-\item
-Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}. 
-\ei
+\be
+\item
+Tuning  defect predictors is {\em remarkably simple};
+\item
+And can {\em dramatically improve the performance}. 
+\ee
 Prior to these experiments, our expectation was tuning
@@
 For example,
-after tuning, the worst untuned learner (CART) can out-perform the supposedly
-best learner (Random Forests). Hence, all those prior results that ranked learners for software
-analytics now need to be revisited and perhaps revised.
+after tuning, the worst untuned learner (CART) can perform just as well as the supposedly
+best learner (Random Forest). Hence, all those prior results that ranked learners for software
+analytics now need to be revisited (and perhaps revised).
 
@@
 
-Linear  regression fits a  line to a set of points in order to minimize  predictive
-error and maximizes the correlation\footnote{
-{\em Correlation}
-measures how closely two variables co-vary.  It ranges from   from -1
-(perfect negative correlation) through 0 (no correlation) to +1
- (perfect positive correlation).
-Let  $a_i$ and $p_i$ denote some actual and predicted values respectively; and  $n$ and $\overline{x}$ denote
- the number of observations and the mean of the $n$ observations, 
-respectively. Then:
-$S_{\mathit{PA}}=(\sum_i (p_i - \overline{p})(a_i -
-  \overline{a}))/(n-1)$ and
-$S_{p}=(\sum_i (p_i - \overline{p})^2)(n-1)$
-and 
-$S_{a}=(\sum_i (a_i - \overline{a})^2)/(n-1)$ and
-correlation is  $c=S_{\mathit{PA}}/\sqrt{S_pS_a}$.}  denoted as $c$.
 Suppose  a researcher wants to use linear regression
@@
 issuing a request to an inspection team to review some module).  
-Hence, it is important to explore tuning
-so the rest of this paper repeats the analysis of this section, but for 
+Hence, it is important to explore tuning.
+
+The rest of this paper repeats the analysis of this section, but for 
 more complex learners.
@@
 This section is our standard introduction to defect prediction~\cite{me15:book1},
-plus    new results from Rahman et al.~\cite{rahman14:icse}.
+plus    some new results from Rahman et al.~\cite{rahman14:icse}.
 
@@
 
-\input{learners}
-
+There are many ways to build defect predictors
+such as  CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
+and WHERE~\cite{menzies2013local}.
+For this study, we use the CART and Random Forest  from 
+SciKitLearn~\cite{scikit-learn} (and
+WHERE is available from
+github.com/ai-se/where).
+ We use  these algorithms, for the following reasons.
+CART and Random Forest were mentioned in
+a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 21  
+learners for  defect prediction.
+That study ranked  CART  worst  and Random Forest as best.
+In a demonstration of the impact of tuning,
+this paper shows  we can {\em reverse} the conclusions of  Lessmann et al. such that CART
+performs just as well as
+ Random Forest.
+This
+ paper also presents results with WHERE-based learner since, as shown below,
+it offers an interesting case study on the benefits of tuning.
+
+\subsection{Learners and Their Tunings}
+
+Our learners use the tuning parameters of \fig{parameters}. This section describes those parameters.
+
+CART, Random Forest, and WHERE-based learner are all  tree learners that divide a data set, then recurse
+on each split.
+All these learners
+generate numeric predictions which are converted
+into binary ``yes/no'' decisions via \eq{yesno}. Hence, they all use the {\em threshold} value $T$ discussed in \tion{eg}.
+
+The splitting process is controlled by numerous tuning parameters.
+If data contains more than {\em min\_sample\_split}, then a split is attempted.
+On the other hand, if a split contains no more than {\em min\_samples\_leaf}, then recursion stops. For CART and Random Forest use a 
+user-supplied constant for this parameter while
+WHERE-based learner firstly computes this parameter $m$={\em min\_samples\_leaf} from the size of the data
+sets via  $m=\mathit{size}^\mathit{min\_size}$ to build an initial  clustering tree.
+Note that WHERE builds {\em two} trees: the initial clustering tree (to find similar sets of data)
+then a final decision tree (to learn rules that predict for each similar cluster)\footnote{A
+frequently asked question is why does WHERE build two trees--
+would not   a single tree suffice? The answer is, as shown below,  tuned WHERE's twin-tree approach 
+generates very precise predictors.}.
+The tuning parameter  {\em min\_sample\_ split } controls the construction of the
+final decision tree (so, for WHERE-based learner,
+{\em min\_size} and {\em min\_sample\_split} are the parameters to be tuned).
+
+These learners use different techniques to explore the splits:
+\bi
+\item
+CART finds the attributes whose ranges contain rows with least variance in the number
+of defects\footnote{If an attribute ranges $r_i$ is found in 
+$n_i$ rows each with a  defect count variance of $v_i$, then CART seeks the attributes
+whose ranges minimizes $\sum_i \left(\sqrt{v_i}\times n_i/(\sum_i n_i)\right)$.}.
+\item
+Random Forest    divides data like CART then  builds $F>1$  trees,
+each time using some random subset of
+the attributes. 
+\item
+When building the initial cluster tree, WHERE projects the data on to a dimension it synthesizes from the raw data using
+a process analogous to principle component analysis\footnote{
+PCA  synthesises  new
+attributes $e_i, e_2,...$
+that extends across the dimension of greatest  variance in the data  with attributes $d$.  
+This process  combines
+redundant  variables into a smaller set of variables  (so $e \ll d$) since those
+redundancies become (approximately) parallel lines
+in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
+can ignore $j$ 
+since effects that change over $j$ also
+change in the same way over $i$.
+PCA is also useful for skipping over noisy variables from $d$-- these
+variables are effectively ignored since    they  do not contribute to the variance in the data.}.
+WHERE  divides  at the median point of that projection.
+On recursion,
+this generates the initial clustering tree, the leaves of which are clusters of  very similar examples. After that, when building 
+the final decision tree, WHERE pretends its clusters are ``classes'', then 
+asks the InfoGain of the
+Fayyad-Irani discretizer~\cite{FayIra93Multi}, to rank the attriubutes, where {\em infoPrune} is used.
+WHERE's final decision tree generator then ignores everything except the top   {\em infoPrune} percent of the sorted
+attributes.
+\ei
+Some tuning parameters are learner specific:
+\bi
+\item
+{\em Max\_feature} is used by
+CART and Random Forest to select the number of attributes
+used to build one tree.
+CART's default is to use all the attributes while 
+Random Forest usually selects the square root of the number
+of attributes.
+\item
+  {\em Max\_leaf\_nodes} is the upper bound on leaf notes generated in a 
+  Random Forest.
+\item {\em Max\_depth} is the upper bound on the depth of the CART tree.  
+ \item
+WHERE's initial clustering
+tree generation will always split up to {\em depthMin} number of branches.
+After that, WHERE will only split data if the mean performance scores of the two halves
+is ``trivially small'' (where ``trivially small'' is set by the   {\em wriggle} parameter). 
+\item
+WHERE's   {\em tree\_prune} setting controls how   
+WHERE prunes back superflous parts of the final decision tree. 
+If a decision sub-tree and its parent have the same 
+majority cluster
+(one that occurs most frequently), then if {\em tree\_prune} is enabled, we prune that decision sub-tree.
+\ei
+
+\subsection{Tuning Algorithms}
+
+ \subsubsection{Parametric Tuning Algorithms}
+The  goal of this paper is to adjust the tuning parameters of \fig{parameters}
+in order to   optimize (improve) some particular performance scores
+generated by a particular learner being applied to  a particular data set.
+For this task, we do not use traditional parametric numeric optimizer  
+such as  gradient descent optimizers~\cite{saltelli00} that require models comprised of
+differential functions (i.e. functions of real-valued variables whose derivative exists at each point in its domain).
+This is impractical  for  our learners since their internal states are   not a smoothly differential continuous function.
+Rather, learners being tuned  contain many regions with many different properties (tuning options can
+drive the learner into very different modes with very different performance properties).
+
+ \subsubsection{Non-Parametric Tuning Algorithms}
+
+Non-parametric  optimizers   make no assumption
+about the internal structure of the model.
+There are many such optimizers:
+\bi
+\item
+Simulated annealing~\cite{fea02a,me07f};
+\item
+A wide range of genetic algorithms~\cite{goldberg79} augmented by
+techniques such as differential evolution~\cite{storn1997differential}, tabu search and scatter search~\cite{Glover1986563,Beausoleil2006426,Molina05sspmo:a,4455350};
+\item
+Particle swarm optimization~\cite{pan08}; 
+\item 
+Numerous ``decomposition approaches'' that uses
+    heuristics to decompose the total space into   small problems,   then applies a
+    simpler optimizer to each region including \mbox{$\varepsilon$-domination}~\cite{deb05} and MOEA/D ~\cite{zhang07};
+    \item 
+    Response surface methods~\cite{krall15,Zuluaga:13};
+    \item
+    And many others as well.
+    \ei
+From all the above methods, how do we select which optimizers to apply to tuning data miners?
+Cohen~\cite{cohen95} advises comparing new 
+ methods against the simplest possible alternative. 
+Holte~\cite{holte93} recommends using very simple  learners
+ as a
+kind of ``scout'' for a  preliminary analysis of a data
+set (to check if that data really requires a more
+complex analysis).
+
+To find our ``scout'',  we used engineering judgement to sort  the above algorithms from simplest to most complex.
+Of the optimizers listed above, the simplest are are SA  and 
+differential evolution (each can be coded in less than a page of some high-level scripting language). Our reading of the current literature is that there are more  advocates for
+differential evolution than
+  SA:
+  \bi
+  \item
+  When the MOEA/D community requires a secondary optimizer, they often use  differential evolution~\cite{zhang07,5583335}.
+  \item
+ Vesterstrom and Thomsen~\cite{Vesterstrom04} found DE to be competitive with 
+   particle swarm optimization and other GAs.
+   \ei
+DEs have been applied before for   parameter tuning (e.g. see~\cite{omran2005differential, chiha2012tuning}) but this is the first time they have been applied to
+optimize defect prediction from static code attributes.  
 The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
-Note that, as we describe the algorithm,
-  any superscript number denotes a line in that algorithm.
-
-DE is an evolutionary algorithm where next {\em NewGeneration} is learnt from
-a current {\em Population}.  If the new is no better than  current, then
-we lose one life (terminating when lives is zero)$^5$.
-
+In the following description, 
+    superscript numbers denotes a line in that figure.
+
+ \begin{figure*}[!t]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{c c c c c c c c c c }\hline
+  Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
+\\\hline
+  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
+\\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
+\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
+\\ \hline
+  Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
+\\\hline
+  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
+\\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
+\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
+\\  \end{tabular}
+
+   \caption{Data used in this data. 
+   E.g., the top left data set has 20 defective classes out of 125 total.
+   See \tion{dataa} for explanation of {\em training, tuning, testing} sets.
+   }\label{fig:data1}
+\end{figure*}
+
+DE is an evolutionary algorithm where the next {\em NewGeneration} is learnt from
+a current {\em Population}.  Our DE's lose one ``life''
+when e new is no better than  current (terminating when ``life'' is zero)$^5$.
 Each candidate solution in the {\em Population}  
@@
 This means that, as the loop progresses, the {\em Population} is full of increasiningly
-more valuable solutions. This, in turn, also improves  the candidates, which are generated
+more valuable solutions. This, in turn, also improves  the candidates, which are {\em Extrapolate}d
 from the {\em Population}.
@@
 
-Our defect data comes from the PROMISE repository\footnote{http://openscience.us/repo}.
-It pertains to 
+Our defect data comes from the PROMISE repository (http://openscience.us/repo)
+and pertains to 
 open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
@@
 in training.  There are many ways to design a experiment that satisfies this principle.
-Some of those methods have  limitations:
-\bi
-\item  Leave-one-out is too slow for large data sets;
-\item Cross-validation can mix up older and newer data sets so it may well be that
-data from the {\em future} is used to test on {\em past data}.
-\ei
+Some of those methods have  limitations; e.g.
+{\em leave-one-out} is too slow for large data sets and
+{\em cross-validation}   mixes up older and newer data  (such that
+data from the {\em future} may be used to test on {\em past data}).
+
 To avoid these problems, we used an incremental learning approach. The following
@@
 data.
-
 For this experiment, we use data sets with at least three  
@@
 
- \begin{figure*}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{c c c c c c c c c c }\hline
-  Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
-\\\hline
-  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
-\\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
-\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
-\\ \hline
-  Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
-\\\hline
-  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
-\\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
-\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
-\\  \end{tabular}
-
-   \caption{Data used in this data. 
-   E.g., the top left data set has 20 defective classes out of 125 total.
-   See \tion{dataa} for explanation of {\em training, tuning, testing} sets.
-   }\label{fig:data1}
-\end{figure*}
-
 \subsection{Optimization Goals}
@@
  optimization goal. This section lists those optimization goals.
-
 Let $\{A,B,C,D\}$ denote the
@@
 
-All the above vary from zero to one. For $pf$, the {\em better} scores are {\em smaller}.
+For $pf$, the {\em better} scores are {\em smaller}.
 For all other scores, the {\em better} scores are {\em larger}.
@@
 
-\begin{figure}[!b]
+\begin{figure}[!t]
 \small
 \begin{tabular}{|p{.95\linewidth}|}\hline
-One style
-of measure is to check the {\em variability} of that predictor.
-For example,
-in their study on reproducibility of SE results,
+
  Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
@@
 
-There exist other goals that combine defect prediction with other economic
-factors.
 Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
@@
 
-In {\em Better-faster-cheaper},   managers want changes that lead
-to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
-
-Another  {\em  rush-to-market} approach is yet another economic-based optimization measure.
-A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
-as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
-in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
-used to subsequently fix any issues with version 1.0)~\cite{huang06}.\\\hline
+In {\em Better-faster-cheaper},   managers want
+ fewer defects,  faster development,  using less resources~\cite{Green,elrawas10,me07f,me09f}.
+\\\hline
 \end{tabular}
@@
 
-Our analysis results make no assumption that (e.g.) minimizing false alarms is 
-more important than maximizing   precision. That determination 
-depends on current business conditions:
-\be
-\item
-For safety critical applications, high false alarm rates may be acceptable if the cost
-of overlooking any critical can outweigh the inconvenience of having to inspect a few more
+This paper does not assume that (e.g.) minimizing false alarms is 
+more important than maximizing   precision. Such a determination 
+depends on   business conditions.
+For example,
+(1) for safety critical applications, high false alarm rates are  acceptable if the cost
+of overlooking  critical issues outweighs the inconvenience of   inspecting a few more
 modules. 
-\item
-On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
+On the other hand, (2) when rushing a product to market,  there is a business case to 
 avoid the extra rework associated with false alarms.  In that business context, 
 managers might be willing to lower the recall somewhat in order to minimize the false alarms.
-\ee
 These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
 and there is insufficient space in this paper to explore all the above optimization goals.
-What we can do, however, is show examples of how  changing  optimization goals can also change 
-the conclusions made from that learner on that data. Those examples only relate to precision, recall, and the F-measure
-but the general principle (that the search bias changes the search conclusions) would hold for all the goals
-listed in the previous paragraph.  Hence, we warn that it is important not to overstate  empirical results from software analytics.
+
+In this paper, what we can  show are examples of how  changing  optimization goals can also change 
+the conclusions made from that learner on that data. Accordingly, we warn that it is important not to overstate  empirical results from software analytics.
 Rather, those results need to be expressed {\em along with} the context within which they are
@@
 
-The introduction of this article made several claims about tuning defect predictor
-that use static code attributes. This section presents
-support for those claims:
+This section offers empirical support for six claims:
 \be
@@
 \item
-Similarly, the tuner
-could achieve near zero false alarm rates by effectively turning off
-the detector (driving recall to zero).
+Similarly,  tuning
+can achieve near zero false alarm rates by effectively turning off
+the detector (when recall is zero).
 \ei
-Hence, in the
-following, we explore performance measures that comment on all the possible
+Accordingly,  this paper  explores performance measures that comment on all 
 target classes (i.e. precision and ``F'').
@@
 
-These results offer support for the prior conclusions of  
- Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
-\bi
-\item
-Untuned CART is indeed the worst learner (only one of its
+These results offer support for  prior conclusions that CART is worse than Random Forest. As might have been
+ predicted by Lessmann et al.~\cite{lessmann2008benchmarking}, 
+untuned CART is indeed the worst learner (only one of its
 untuned results is best and {\bf bold}). 
-\item 
-In $\frac{13}{17}$ cases, the performance of untuned Random Forest is better than or equal to untuned CART.  
-\ei
+Also, 
+in $\frac{13}{17}$ cases, the performance of untuned Random Forest is better than or equal to untuned CART.  
 % Some of the data sets in \fig{precisionbars} proved challenging for all learners;
@@
 
-That said,  tuning can improve those poor performing detectors:
-\bi
-\item
+That said,  tuning can improve those poor performing detectors.
 For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
-\item A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
+A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
 In those two data sets, nearly all the precision values are   low {\em except} for
 tuned WHERE that scored 89\% and 85\%.
-\ei
 Finally, note the  {\em jeditV2} result for the WHERE learner.
@@
 \begin{center}
-\includegraphics[width=1.25in]{precision_W.eps}\includegraphics[width=1.25in]{F_W.eps}
+\includegraphics[width=1.5in]{precision_W.eps}\includegraphics[width=1.5in]{F_W.eps}
  \end{center}
@@
 Such conclusions are   not reliable since they can change when we elect to tune for different goals. 
-
 For example, given the poor showing of untuned CART and the good performance of tuned WHERE
@@
 
-\renewcommand{\baselinestretch}{0.8}
+\renewcommand{\baselinestretch}{0.75}
 \scriptsize
@@
   \begin{tabular}{r|c |c |c |c |c |c }
-    \hline\hline
     Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
@@
 \end{figure*}
-
 %%%%time for F %%%%%%
 \begin{figure*}[!ht]
-\renewcommand{\baselinestretch}{0.8}
+\renewcommand{\baselinestretch}{0.75}
 \scriptsize
@@
   \begin{tabular}{r|c |c |c |c |c |c } 
-    \hline\hline
     Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
@@
 to populations.  
-The tuning results shown here only came from one  software analytics task 
+The examples of this paper  only relate to precision, recall, and the F-measure
+but the general principle (that the search bias changes the search conclusions)  holds for all any set if goals. 
+Also,
+the tuning results shown here only came from one  software analytics task 
 (defect prediction from static code attributes).

### 2015-04-10 dm101.tex
correct typos and remove section II.

@@
 Since programming inherently
-introduces defects into  programs, is important to test it before it is used.
+introduces defects into  programs, it is important to test them before they're used.
 Testing is expensive.
@@
 its final  decision tree. \\ \cline{2-5} 
-	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_sample 
+	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_samples\_leaf 
 in the initial clustering tree  using  ${n\_samples}^ {min\_Size}$.

### 2015-04-10 tuningpredictor.tex
correct typos and remove section II.

@@
 For the purposes of learning
-software defect predictors this  methid can quickly
+software defect predictors this  method can quickly
 find  good tunings that  dramatically change   the performance of a learner.
@@
 that are readily available to researchers~\cite{rod12}.
-For example,  the time of this writing (Feb  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
+For example, at the time of this writing (Feb  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
 
@@
 of the tuning is altered.
-Hence, many old papers    need to be revisted  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
+Hence, many old papers    need to be revisited  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
 For example, one of us (Menzies) used data miners
@@
 
-Thirdly, it is standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
+Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
 we have defended that approach, arguing that it
@@
 number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation). 
-After tuning, we see that our optimizer often used $F$ values that were nowhere near that default:
+After tuning, we see that our optimizer often uses $F$ values that are nowhere near that default:
 
@@
 
-\section{Motivating Example}\label{sect:eg}
-
-This section is  a  demonstration
-of the impact of tuning.
-
-Suppose  a researcher wants to use linear regression
-to test if Halstead's~\cite{halstead77} measures
-of   function complexity
-(number of symbols programmers has to understand) are   {\em better than}
-mere lines of code for predicting
-software defects.  That researcher might believe that Halstead's cognitive approach to
-software bugs is better suited to code refactoring tools since it offers 
-more ways to alter functions that just some coarse grain lines of code measure.
-
-To test that belief, our  researcher applies regression to  some defect logs.
- Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
-that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
-software module (in this case, a  function).
-Note that the Halstead correlation $c_2$
-is worse than the $c_1$ correlation  from lines of code-- which suggests
- our researcher should not use Halstead .
-
-{\scriptsize \[
-\begin{array}{l|l|ll}
-\mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
-\mathit{LOC}   &d_1= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
-\mathit{Halstead} & d_2= 0.231 + 0.00344N  +  0.0009V    \\    
-                 &   - 0.185L- 0.0343D      - 0.00541I  \\ 
-                 & + 0.000019E + 0.711B  - 0.00047T  & c_2=-0.36  
-\end{array}
-\]
-}
-
-\noindent
-We now explore how tuning can change the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
-are used to call an inspection
-team to check for errors in   parts of the code using:
-\begin{equation}\label{eq:yesno}\scriptsize
-\mathit{inspect}= \left\{
-\begin{array}{ll}
-d_i \ge T \rightarrow \mathit{Yes}\\
-d_i <   T \rightarrow \mathit{No} 
-\end{array}\right.
-\end{equation}
-\fig{pd1} shows the effects of tuning. Not surprisingly,
-at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
-problem, we can increase $T$:   the false alarm rate falls below
-20\% at $T=0.45$ (for Halstead).
-
-\begin{figure}[!t]
-
-\renewcommand{\baselinestretch}{0.8}
-{\scriptsize
-\begin{center}
-
-\% recall (probability of detection):
-
-\includegraphics[width=3in]{lsrvscostpd.pdf}
-
-\% false alarms:
-
-\includegraphics[width=3in]{lsrvscostpf.pdf}
-\end{center}}
-\caption{
- Y-axis shows probability of false alarm,
-  and
-  probability of recognizing defective modules  seen using \mbox{$d_i \ge T$}.
-  Curves calculated from the KC2 dataset from the PROMISE repository goo.gl/pGDfvp.
- }\label{fig:pd1}
- \end{figure}
-
-Note that either the Halstead or LOC detector can reach some desired
-level of recall, regardless of their correlations, just by
-selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
-found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
-were very similar: 14\% and 19\%).
-
-The  point here is that   the true value of a detector
-could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
-issuing a request to an inspection team to review some module).  
-Hence, it is important to explore tuning.
-
-The rest of this paper repeats the analysis of this section, but for 
-more complex learners.
+% \section{Motivating Example}\label{sect:eg}
+
+% This section is  a  demonstration
+% of the impact of tuning.
+
+% Suppose  a researcher wants to use linear regression
+% to test if Halstead's~\cite{halstead77} measures
+% of   function complexity
+% (number of symbols programmers has to understand) are   {\em better than}
+% mere lines of code for predicting
+% software defects.  That researcher might believe that Halstead's cognitive approach to
+% software bugs is better suited to code refactoring tools since it offers 
+% more ways to alter functions that just some coarse grain lines of code measure.
+
+% To test that belief, our  researcher applies regression to  some defect logs.
+%  Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
+% that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
+% software module (in this case, a  function).
+% Note that the Halstead correlation $c_2$
+% is worse than the $c_1$ correlation  from lines of code-- which suggests
+%  our researcher should not use Halstead .
+
+% {\scriptsize \[
+% \begin{array}{l|l|ll}
+% \mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
+% \mathit{LOC}   &d_1= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
+% \mathit{Halstead} & d_2= 0.231 + 0.00344N  +  0.0009V    \\    
+%                  &   - 0.185L- 0.0343D      - 0.00541I  \\ 
+%                  & + 0.000019E + 0.711B  - 0.00047T  & c_2=-0.36  
+% \end{array}
+% \]
+% }
+
+% \noindent
+% We now explore how tuning can change the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
+% are used to call an inspection
+% team to check for errors in   parts of the code using:
+% \begin{equation}\label{eq:yesno}\scriptsize
+% \mathit{inspect}= \left\{
+% \begin{array}{ll}
+% d_i \ge T \rightarrow \mathit{Yes}\\
+% d_i <   T \rightarrow \mathit{No} 
+% \end{array}\right.
+% \end{equation}
+% \fig{pd1} shows the effects of tuning. Not surprisingly,
+% at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
+% problem, we can increase $T$:   the false alarm rate falls below
+% 20\% at $T=0.45$ (for Halstead).
+
+% \begin{figure}[!t]
+
+% \renewcommand{\baselinestretch}{0.8}
+% {\scriptsize
+% \begin{center}
+
+% \% recall (probability of detection):
+
+% \includegraphics[width=3in]{lsrvscostpd.pdf}
+
+% \% false alarms:
+
+% \includegraphics[width=3in]{lsrvscostpf.pdf}
+% \end{center}}
+% \caption{
+%  Y-axis shows probability of false alarm,
+%   and
+%   probability of recognizing defective modules  seen using \mbox{$d_i \ge T$}.
+%   Curves calculated from the KC2 dataset from the PROMISE repository goo.gl/pGDfvp.
+%  }\label{fig:pd1}
+%  \end{figure}
+
+% Note that either the Halstead or LOC detector can reach some desired
+% level of recall, regardless of their correlations, just by
+% selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
+% found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
+% were very similar: 14\% and 19\%).
+
+% The  point here is that   the true value of a detector
+% could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
+% issuing a request to an inspection team to review some module).  
+% Hence, it is important to explore tuning.
+
+% The rest of this paper repeats the analysis of this section, but for 
+% more complex learners.
 
@@
 To find our ``scout'',  we used engineering judgement to sort  the above algorithms from simplest to most complex.
-Of the optimizers listed above, the simplest are are SA  and 
-differential evolution (each can be coded in less than a page of some high-level scripting language). Our reading of the current literature is that there are more  advocates for
+Of the optimizers listed above, the simplest are are simulated annealing (SA)  and 
+differential evolution (DE), each of which can be coded in less than a page of some high-level scripting language. Our reading of the current literature is that there are more  advocates for
 differential evolution than
@@
 
-   \caption{Data used in this data. 
+   \caption{Data used in this experiment. 
    E.g., the top left data set has 20 defective classes out of 125 total.
@@
 a current {\em Population}.  Our DE's lose one ``life''
-when e new is no better than  current (terminating when ``life'' is zero)$^5$.
+when e new is no better than  current (terminating when ``life'' is zero)$^{L5}$.
 Each candidate solution in the {\em Population}  
@@
 \fig{parameters} and {\em Scores} come from training a learner using those parameters
-and applying it     test data$^{23-28}$.
+and applying it     test data$^{L23-L28}$.
 
 The premise of DE  is that the best way to mutate existing tunings
-is to {\em Extrapolate}$^{29}$
+is to {\em Extrapolate}$^{L29}$
 between current solutions.  Three solutions $a,b,c$ are selected at random.
@@
 \item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
-controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
+controlling the cross-over amount.  The {\em trim} function$^{L39}$ limits the new
 value to the legal range min..max of that parameter.
@@
 \ei
-The main loop of DE$^7$ runs over the {\em Population}, replacing old items
+The main loop of DE$^{L7}$ runs over the {\em Population}, replacing old items
 with new {\em Candidate}s (if the new candidate is better than the old item).
@@
 values from a data mining, from which a {\em Goal} function extracts one 
-performance value$^{27}$ (so we run this code many times, each time with
-a different {\em Goal}$^2$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
+performance value$^{L27}$ (so we run this code many times, each time with
+a different {\em Goal}$^{L2}$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
 
@@
    build some model using some the tunings found in some {\em Candidate}.
-   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
+   \item The {\em second} release was used on line 25 of Algorithm~\ref{alg:DE} to 
    test the model found on line 24.
@@
 explored via tuning, optimizing defect prediction from static code
-measures is much {\em smaller} than standard optimization.
+measures is much {\em smaller} than the standard optimization.
 
@@
 investigates what the researcher purports to investigate.
-{\em Internal validity} checks that if the differences found in
+{\em Internal validity} checks if the differences found in
 the treatments can be ascribed to the treatments under study. 
@@
 
-\section{Acknowledgments}
+\section*{Acknowledgments}
 The work has partially funded by a National Science Foundation CISE CCF award \#1506586.
@@
 
- \scriptsize
 \bibliographystyle{plain}

### 2015-08-03 tuningpredictor.tex
updates

@@
-% \documentclass{sig-alternative}
-\documentclass[conference]{IEEEtran}
+\documentclass{sig-alternative}
+% \documentclass[conference]{IEEEtran}
 \usepackage{multirow}
@@
 \usepackage{cite}
-
 \usepackage{rotating}
@@
 \definecolor{LightGray}{gray}{0.975}
-
-\newcommand{\rone}{}
-\newcommand{\rtwo}{}
-\newcommand{\rthree}{}
-\newcommand{\rfour}{} 
-\newcommand{\rfive}{}
-
+% \newcommand{\rone}{}
+% \newcommand{\rtwo}{}
+% \newcommand{\rthree}{}
+% \newcommand{\rfour}{} 
+% \newcommand{\rfive}{}
 \newcommand{\wei}[1]{\textcolor{red}{Wei: #1}}
@@
 \usepackage[shortlabels]{enumitem}  
-
 \usepackage{url}
-\def\baselinestretch{1}
-
-\setlist{nosep}
- \usepackage[font={small}]{caption, subfig}
-\setlength{\abovecaptionskip}{1ex}
- \setlength{\belowcaptionskip}{1ex}
-
- \setlength{\floatsep}{1ex}
- \setlength{\textfloatsep}{1ex}
- \newcommand{\subparagraph}{}
-
-\usepackage[compact,small]{titlesec}
-\DeclareMathSizes{7}{7}{7}{7} 
-\setlength{\columnsep}{7mm}
+% \def\baselinestretch{1}
+
+% \setlist{nosep}
+%  \usepackage[font={small}]{caption, subfig}
+% \setlength{\abovecaptionskip}{1ex}
+%  \setlength{\belowcaptionskip}{1ex}
+
+%  \setlength{\floatsep}{1ex}
+%  \setlength{\textfloatsep}{1ex}
+%  \newcommand{\subparagraph}{}
+
+% \usepackage[compact,small]{titlesec}
+% \DeclareMathSizes{7}{7}{7}{7} 
+% \setlength{\columnsep}{7mm}
 
@@
 {\em without}  conducting a tuning optimization study.
-The implications for other kinds of  analytics is now  an open and pressing issue.
+The implication for other kinds of  analytics is now  an open and pressing issue.
 
@@
 
+\pagenumbering{arabic} %XXX delete before submission
+
 \section{Introduction}
@@
 that are readily available to researchers~\cite{rod12}.
-For example, at the time of this writing (Feb  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
+For example, at the time of this writing (May  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
 
@@
 \ee
-Prior to these experiments, our expectation was tuning
-would be an  extensive and expensive evolutionary optimization procedure. 
-A standard run of such evolutionary optimizers requires   thousands,
-if not millions, of evaluations.
-To
-our surprise, we achieved dramatic improvements in the performance scores
-of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
-optimizer  called differential evolution~\cite{storn1997differential}.
-Better yet,  those  tunings (found so quickly)   
-  have a dramatic change to the performance of a learner. For example,
-in this paper we show that tuning can alter the precision of
-a software defect predictor from 2\% to 98\%.
-
-These results challenge much prior work. 
-Firstly, there exist research papers
-that use data miners to   show that certain factors
-are more influential than others for (say)
-predicting defects. As shown below, such conclusions can be dramatically
-changed by the tuning process since those  ``influential'' factors are very different pre- and post- tuning. Also, those factors tend to  change from project to project or if the goal
-of the tuning is altered.
-Hence, many old papers    need to be revisited  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
-For example, one of us (Menzies) used data miners
-to assert that some factors were more important than others for predicting
-successful software reuse~\cite{me02k}. That assertion should now be doubted since that
-Menzies study did not conduct a tuning study before reporting what factors the data miners
-found where most influential.
-
-Secondly, several  prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
-that learnerX is better than learnerY for some software analytics task.
-For example, a recent IEEE TSE article claimed that the 
-CART decision tree learner was far worse than Random Forests for
-software defect prediction~\cite{lessmann2008benchmarking}. 
-Such conclusions do not survive tuning.
-For example,
-after tuning, the worst untuned learner (CART) can perform just as well as the supposedly
-best learner (Random Forest). Hence, all those prior results that ranked learners for software
-analytics now need to be revisited (and perhaps revised).
-
-Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
-we have defended that approach, arguing that it
-encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
-can no longer be condoned. For example, suppose our default
-number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation). 
-After tuning, we see that our optimizer often uses $F$ values that are nowhere near that default:
-
-% {\scriptsize
-% \[F \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
-%                                 108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
-% \]}
-
-% {\scriptsize
-% \[F \in \left\{\begin{array}{l} 50, 59, 63, 63, 69, 71, 81, 85,85, 88,\\
-%                                 92, 95, 96, 99, 99,  100, 104, 106, 107,\\
-%                                 109, 111, 112, 121, 121, 123, 125, 128,\\
-%                                 131, 132, 135, 140, 141, 141, 150   \end{array}\right\}
-% \]}
-
-{\scriptsize
-\[F \in \left\{\begin{array}{l} 50, 58, 59, 63, 63, 66, 67, 73, 74, 74, \\
-                                75, 77, 80, 82, 85, 96, 96, 97, 97, 101, \\
-                                103, 107, 111, 111, 112, 120, 125, 125,  \\
-                                130,130, 138, 144, 149, 150   \end{array}\right\}
-\]}
-
-In summary, it is now an open and pressing research issue to check if
-analytics without parameter tuning is considered {\em harmful} or, at the 
-very least, {\em misleading}.
-Clearly, we  now doubt  conclusions based on
-``off-the-shelf'' tunings.
-Further,
-it is no longer enough to just run a data miner and report the result
-{\em without} first conducting an tuning optimizations study.
-
+More specifically,
+this paper explores six research questions about tuning defect predictors for
+static code measures:
+\bi
+\item RQ1: {\em Does   tuning    improve the performance scores of a predictor?} We will show below
+ examples of truly dramatic improvement;
+e.g.  precision changes from 2\% to 98\%.
+\item RQ2: {\em Does tuning change conclusions on what learners are better than others?} 
+Numerous recent SE papers (e.g. \cite{lessmann2008benchmarking,hall11,me07b}) claim that some learners are better than others. We show that at least
+some of those conclusions are completely changed by tuning.
+\item RQ3: {\em Does tuning change conclusions about what factors are most important in software engineering?} Numerous recent SE papers (e.g.
+~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,%
+herzig2013predicting}) use data miners to conclude that {\em this}
+is more important than {\em that} for (e.g.) reducing software project defects.
+Given the  tuning results of this paper, we show that such conclusions need to be revisited.
+\item  RQ4: {\em Is tuning easy?} We show that one of the simpler multi-objective optimizers
+(differential evolution~\cite{storn1997differential}) works very well for tuning defect predictors. 
+\item RQ5: {\em Is tuning impractically slow?}. We achieved dramatic improvements in the performance scores
+of our data miners in less than 100 evaluations (!!); i.e. very
+quickly.
+\item RQ6: {\em Should data miners be used ``off-the-shelf'' with their default tunings?} 
+At least for defect prediction from static code measures, our answer is an emphatic ``no'' (and
+the implication for other kinds of software analytics is now an open and urgent question).
+\ei
 Before beginning, we digress for one  clarification.
-This paper is {\bf not} arguing that
+This paper is {\em not} arguing that
 software analytics is somehow wrong-headed or misguided.
@@
 
-% \section{Motivating Example}\label{sect:eg}
-
-% This section is  a  demonstration
-% of the impact of tuning.
-
-% Suppose  a researcher wants to use linear regression
-% to test if Halstead's~\cite{halstead77} measures
-% of   function complexity
-% (number of symbols programmers has to understand) are   {\em better than}
-% mere lines of code for predicting
-% software defects.  That researcher might believe that Halstead's cognitive approach to
-% software bugs is better suited to code refactoring tools since it offers 
-% more ways to alter functions that just some coarse grain lines of code measure.
-
-% To test that belief, our  researcher applies regression to  some defect logs.
-%  Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
-% that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
-% software module (in this case, a  function).
-% Note that the Halstead correlation $c_2$
-% is worse than the $c_1$ correlation  from lines of code-- which suggests
-%  our researcher should not use Halstead .
-
-% {\scriptsize \[
-% \begin{array}{l|l|ll}
-% \mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
-% \mathit{LOC}   &d_1= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
-% \mathit{Halstead} & d_2= 0.231 + 0.00344N  +  0.0009V    \\    
-%                  &   - 0.185L- 0.0343D      - 0.00541I  \\ 
-%                  & + 0.000019E + 0.711B  - 0.00047T  & c_2=-0.36  
-% \end{array}
-% \]
-% }
-
-% \noindent
-% We now explore how tuning can change the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
-% are used to call an inspection
-% team to check for errors in   parts of the code using:
-% \begin{equation}\label{eq:yesno}\scriptsize
-% \mathit{inspect}= \left\{
-% \begin{array}{ll}
-% d_i \ge T \rightarrow \mathit{Yes}\\
-% d_i <   T \rightarrow \mathit{No} 
-% \end{array}\right.
-% \end{equation}
-% \fig{pd1} shows the effects of tuning. Not surprisingly,
-% at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
-% problem, we can increase $T$:   the false alarm rate falls below
-% 20\% at $T=0.45$ (for Halstead).
-
-% \begin{figure}[!t]
-
-% \renewcommand{\baselinestretch}{0.8}
+\section{But is This a New Result?}
+
+In  other fields, the impact of tuning is well understood. However, as we argue
+in this section, this result is not properly  acknowledged  in the field of software analytics.
+
+The formal definitions of data mining stresses that these learners are heuristic explorers
+of a truly   vast space of the possible models within a data set~\cite{mitchell1982generalization}. For example, given 20 columns of boolean variables,
+there are $2^{20}$ possible models. Data mining is practical since various heuristics
+allow automatic algorithms to ignore most of those possibilities.
+
+While that heuristic search makes data mining possible, it also means that tunings
+can significantly affect what comes out of a data miner.
+When we tune a data miner, what we are really doing is changing how a learner applies
+its heuristics. This means tuned data miners use different heuristics, which means they ignore different possible models, which means they return different models.
+
+The fact that {\em how} we learn changes {\em what} we learn is not acknowledged
+in the field of software analytics.
+There exists many research papers
+that use data miners to   show that certain factors
+are more influential than others for (say)
+predicting defects. As shown below, such conclusions can be dramatically
+changed by the tuning process since those  ``influential'' factors are very different pre- and post- tuning. Also, those factors tend to  change from project to project or if the goal
+of the tuning is altered.
+Hence, many old papers    need to be revisited  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
+For example, one of us (Menzies) used data miners
+to assert that some factors were more important than others for predicting
+successful software reuse~\cite{me02k}. That assertion should now be doubted since that
+Menzies did not conduct a tuning study before reporting what factors the data miners
+found were most influential.
+
+Further, several  prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
+that learnerX is better than learnerY for some software analytics task.
+For example, a recent IEEE TSE article claimed that the 
+CART decision tree learner was far worse than Random Forests for
+software defect prediction~\cite{lessmann2008benchmarking}. 
+Such conclusions do not survive tuning.
+For example,
+after tuning, the worst learner (CART) can perform just as well as the supposedly
+best learner (Random Forest). Hence, all those prior results that ranked learners for software
+analytics now need to be revisited (and perhaps revised).
+
+Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
+we have defended that approach, arguing that it
+encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
+can no longer be condoned. For example, suppose our default
+number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation).
+After tuning, we see that our optimizer often uses $F$ values that are nowhere near that default:
+
 % {\scriptsize
-% \begin{center}
-
-% \% recall (probability of detection):
-
-% \includegraphics[width=3in]{lsrvscostpd.pdf}
-
-% \% false alarms:
-
-% \includegraphics[width=3in]{lsrvscostpf.pdf}
-% \end{center}}
-% \caption{
-%  Y-axis shows probability of false alarm,
-%   and
-%   probability of recognizing defective modules  seen using \mbox{$d_i \ge T$}.
-%   Curves calculated from the KC2 dataset from the PROMISE repository goo.gl/pGDfvp.
-%  }\label{fig:pd1}
-%  \end{figure}
-
-% Note that either the Halstead or LOC detector can reach some desired
-% level of recall, regardless of their correlations, just by
-% selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
-% found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
-% were very similar: 14\% and 19\%).
-
-% The  point here is that   the true value of a detector
-% could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
-% issuing a request to an inspection team to review some module).  
-% Hence, it is important to explore tuning.
-
-% The rest of this paper repeats the analysis of this section, but for 
-% more complex learners.
-
-\section{Background Notes}
-
-\subsection{Defect Prediction}
-
-This section is our standard introduction to defect prediction~\cite{me15:book1},
-plus    some new results from Rahman et al.~\cite{rahman14:icse}.
-
-\begin{figure*}[!t]
+% \[F \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
+%                                 108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
+% \]}
+
+% {\scriptsize
+% \[F \in \left\{\begin{array}{l} 50, 59, 63, 63, 69, 71, 81, 85,85, 88,\\
+%                                 92, 95, 96, 99, 99,  100, 104, 106, 107,\\
+%                                 109, 111, 112, 121, 121, 123, 125, 128,\\
+%                                 131, 132, 135, 140, 141, 141, 150   \end{array}\right\}
+% \]}
+
+{\scriptsize
+\[F \in \left\{\begin{array}{l} 50, 58, 59, 63, 63, 66, 67, 73, 74, 74, \\
+                                75, 77, 80, 82, 85, 96, 96, 97, 97, 101, \\
+                                103, 107, 111, 111, 112, 120, 125, 125,  \\
+                                130,130, 138, 144, 149, 150   \end{array}\right\}
+\]}
+
+\begin{figure*}[t]
 \renewcommand{\baselinestretch}{0.8}\begin{center}
@@
 
+The  good news of this paper  is that {\em tuning is very easy}.
+This result is both novel and unexpected.
+A standard run of such evolutionary optimizers requires   thousands,
+if not millions, of evaluations. However, in a result that we found startling, that  differential evolution can find useful settings for learners generating defect predictors
+in less than 100 evaluations (i.e. very quickly).
+Hence,   the ``problem'' (that
+tuning changes the conclusions) is really
+an exciting opportunity. At least for defect prediction,
+ learners are very   amenable to tuning. Hence, 
+ they are  also very
+amenable to significant performance improvements. Given the low
+number of evaluations required, then we assert that tuning
+  should be standard practice
+for anyone building defect predictors.
+
+That said, the bad news is that, for defect
+prediction, tuning results in dramatic changes in
+  what is learned from that data. Therefore, it is now an open and pressing research issue to check if
+analytics without parameter tuning is considered {\em harmful} or, at the 
+very least, {\em misleading}.
+Clearly, we  must now revisit all prior results   based on
+``off-the-shelf'' tunings.
+Further,
+it is no longer enough to just run a data miner and report the result
+{\em without} first conducting an tuning optimizations study.
+
+% \section{Motivating Example}\label{sect:eg}
+
+% This section is  a  demonstration
+% of the impact of tuning.
+
+% Suppose  a researcher wants to use linear regression
+% to test if Halstead's~\cite{halstead77} measures
+% of   function complexity
+% (number of symbols programmers has to understand) are   {\em better than}
+% mere lines of code for predicting
+% software defects.  That researcher might believe that Halstead's cognitive approach to
+% software bugs is better suited to code refactoring tools since it offers 
+% more ways to alter functions that just some coarse grain lines of code measure.
+
+% To test that belief, our  researcher applies regression to  some defect logs.
+%  Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
+% that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
+% software module (in this case, a  function).
+% Note that the Halstead correlation $c_2$
+% is worse than the $c_1$ correlation  from lines of code-- which suggests
+%  our researcher should not use Halstead .
+
+% {\scriptsize \[
+% \begin{array}{l|l|ll}
+% \mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
+% \mathit{LOC}   &d_1= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
+% \mathit{Halstead} & d_2= 0.231 + 0.00344N  +  0.0009V    \\    
+%                  &   - 0.185L- 0.0343D      - 0.00541I  \\ 
+%                  & + 0.000019E + 0.711B  - 0.00047T  & c_2=-0.36  
+% \end{array}
+% \]
+% }
+
+% \noindent
+% We now explore how tuning can change the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
+% are used to call an inspection
+% team to check for errors in   parts of the code using:
+% \begin{equation}\label{eq:yesno}\scriptsize
+% \mathit{inspect}= \left\{
+% \begin{array}{ll}
+% d_i \ge T \rightarrow \mathit{Yes}\\
+% d_i <   T \rightarrow \mathit{No} 
+% \end{array}\right.
+% \end{equation}
+% \fig{pd1} shows the effects of tuning. Not surprisingly,
+% at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
+% problem, we can increase $T$:   the false alarm rate falls below
+% 20\% at $T=0.45$ (for Halstead).
+
+% \begin{figure}[!t]
+
+% \renewcommand{\baselinestretch}{0.8}
+% {\scriptsize
+% \begin{center}
+
+% \% recall (probability of detection):
+
+% \includegraphics[width=3in]{lsrvscostpd.pdf}
+
+% \% false alarms:
+
+% \includegraphics[width=3in]{lsrvscostpf.pdf}
+% \end{center}}
+% \caption{
+%  Y-axis shows probability of false alarm,
+%   and
+%   probability of recognizing defective modules  seen using \mbox{$d_i \ge T$}.
+%   Curves calculated from the KC2 dataset from the PROMISE repository goo.gl/pGDfvp.
+%  }\label{fig:pd1}
+%  \end{figure}
+
+% Note that either the Halstead or LOC detector can reach some desired
+% level of recall, regardless of their correlations, just by
+% selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
+% found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
+% were very similar: 14\% and 19\%).
+
+% The  point here is that   the true value of a detector
+% could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
+% issuing a request to an inspection team to review some module).  
+% Hence, it is important to explore tuning.
+
+% The rest of this paper repeats the analysis of this section, but for 
+% more complex learners.
+
+\section{Background Notes}
+
+\subsection{Defect Prediction}
+
+This section is our standard introduction to defect prediction~\cite{me15:book1},
+plus    some new results from Rahman et al.~\cite{rahman14:icse}.
+
 \input{dm101}
@@
 
-CART, Random Forest, and WHERE-based learner are all  tree learners that divide a data set, then recurse
+CART, Random Forest, and WHERE-based learners are all  tree learners that divide a data set, then recurse
 on each split.
@@
 generate numeric predictions which are converted
-into binary ``yes/no'' decisions via \eq{yesno}. Hence, they all use the {\em threshold} value $T$ discussed in \tion{eg}.
-
+into binary ``yes/no'' decisions via \eq{yesno}.
+
+\begin{equation}\label{eq:yesno}\scriptsize
+\mathit{inspect}= \left\{
+\begin{array}{ll}
+d_i \ge T \rightarrow \mathit{Yes}\\
+d_i <   T \rightarrow \mathit{No} ,
+\end{array}\right.
+\end{equation}
 The splitting process is controlled by numerous tuning parameters.
 If data contains more than {\em min\_sample\_split}, then a split is attempted.
-On the other hand, if a split contains no more than {\em min\_samples\_leaf}, then recursion stops. For CART and Random Forest use a 
+On the other hand, if a split contains no more than {\em min\_samples\_leaf}, then recursion stops. CART and Random Forest use a 
 user-supplied constant for this parameter while
@@
 To find our ``scout'',  we used engineering judgement to sort  the above algorithms from simplest to most complex.
-Of the optimizers listed above, the simplest are are simulated annealing (SA)  and 
+Of the optimizers listed above, the simplest are simulated annealing (SA)  and 
 differential evolution (DE), each of which can be coded in less than a page of some high-level scripting language. Our reading of the current literature is that there are more  advocates for
@@
     superscript numbers denotes a line in that figure.
+
+\input{algo}
 
@@
 a current {\em Population}.  Our DE's lose one ``life''
-when e new is no better than  current (terminating when ``life'' is zero)$^{L5}$.
+when e new is no better than  current (terminating when ``life'' is zero)$^{5}$.
 Each candidate solution in the {\em Population}  
@@
 \fig{parameters} and {\em Scores} come from training a learner using those parameters
-and applying it     test data$^{L23-L28}$.
+and applying it     test data$^{23-28}$.
 
 The premise of DE  is that the best way to mutate existing tunings
-is to {\em Extrapolate}$^{L29}$
+is to {\em Extrapolate}$^{29}$
 between current solutions.  Three solutions $a,b,c$ are selected at random.
@@
 \item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
-controlling the cross-over amount.  The {\em trim} function$^{L39}$ limits the new
+controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
 value to the legal range min..max of that parameter.
@@
 \ei
-The main loop of DE$^{L7}$ runs over the {\em Population}, replacing old items
+The main loop of DE$^{7}$ runs over the {\em Population}, replacing old items
 with new {\em Candidate}s (if the new candidate is better than the old item).
@@
 values from a data mining, from which a {\em Goal} function extracts one 
-performance value$^{L27}$ (so we run this code many times, each time with
-a different {\em Goal}$^{L2}$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
+performance value$^{27}$ (so we run this code many times, each time with
+a different {\em Goal}$^{2}$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
 
@@
 %\end{algorithm}
-
-\input{algo}
 
@@
 
-\section{Experimental Results}
-
-This section offers empirical support for six claims:
-\be
-\item  Tuning    improves the performance scores of a predictor;
-e.g.  precision changes from 2\% to 98\%: see \tion{precision};
-\item Tuning changes conclusions on what learners are better than others: see \tion{rank};
-\item Tuning changes conclusions about what factors are most important: see \tion{import};
-\item  Tuning is easy: see \tion{easy};
-\item Tuning is fast: see \tion{fast};
-\item Data miners should not be used ``off-the-shelf'' with their default tunings: see \tion{variance}.
-\ee
-
-One comment before continuing. The following text does not
+\subsection{An Aside}
+
+One comment before presenting the results. The following text does not
 show results for tuning on recall
@@
 
-\begin{figure}[!b]
+\begin{figure}[!tb]
 \renewcommand{\baselinestretch}{0.8}
@@
 
-\subsection{Tuning Can  Improves Performance Scores}\label{sect:precision}
-
-\fig{precisionbars} shows precision results before and after tuning using three different learners.
+\section{Experimental Results}
+\subsection{RQ1:  Does  Tuning  Improve Performance? }\label{sect:precision}
+
+\fig{precisionbars} shows precision results before and after tuning with precision as the performance criteria 
+using three different learners.
 For each data set, the maximum precision values for each data set are shown in {\bf bold}.
@@
 
-\fig{deltas} shows that tuning usually has a positive effect on performance scores. This figure sorts
+\fig{deltas} shows that the answer to RQ1 is ``yes''; i.e. tuning usually has a positive effect on performance scores. This figure sorts
 the deltas in the precision and the F-measure    between tuned and untuned learners. Our reading of this
@@
 
-\subsection{Tuning Changes the Rankings of Learner  }\label{sect:rank}
-Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,hall11,me07b}.
+\subsection{RQ2:  Does Tuning Change a Learner's Ranking Regarding Different Goals?}\label{sect:rank}
+Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}.
+In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets.
+In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking.
 Such conclusions are not reliable since they can change when we elect to tune for different goals.
-For example, given the poor showing of untuned CART and the good performance of tuned WHERE
-in   \fig{precisionbars}, we might recommend
-{\em not} to use CART and {\em always} used tuned WHERE. In turns out that this
-conclusion is not stable across the tuning process.
-
-\fig{fbars} shows what happens when we tune for the f-measure. 
-As before, untuned Random Forest generally beats CART. However:
-\bi
-\item
-In  a result that is the direct opposite of   
- Lessmann et al.~\cite{lessmann2008benchmarking}, tuned CART does better than Random Forest;
- \item 
+
+22 learners are compared over NASA MDP data sets in terms of the AUC in \cite{lessmann2008benchmarking}.
+Some learners are tuned using manual methods, like C4.5, CART and Random Forests and some are tuned by searching algorithms, like grid search for SVM-Type learners.
+In our expeirment, when we tune CART and Random Forests for precisoin and F-measure, the rankings of these two learners are changed.
+
+In \fig{precisionbars} and \fig{fbars}, the tuned CART are better than or equal to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
+terms of precision and F-measure, respectively. Results from the non-parametric Kolmogorov-Smirnov Test turn out that the performance 
+scores of tuned CART and tuned Random Forests are not statistically different. This is the pposite of   
+ Lessmann et al.~\cite{lessmann2008benchmarking}, the tuned Random Forest is not significantly better than tuned CART.
  In another result that is the reverse of \fig{precisionbars}, tuned WHERE is not necessarily
  any better than anything else.
- \ei
-The lesson here is that, given a particular task (e.g. optimizing for precision), tuning can offer
+
+ Therefore, it's not always safe to say ``LearnerX'' is the best or better than ``learnerY'' without pointing out the performance criteria or applying tuning techniques.
+That is, the answer to RQ2 is ``yes'' since tuning a set of learners
+ changes the rankings of those learners regarding different criteria.
+
+The  important lesson here is that, given a particular task (e.g. optimizing for precision), tuning can offer
 substantial benefits. However, when that task changes (e.g. to optimizing for the F-measure),
@@
 
-\subsection{Tuning Changes the Ranking of Project Factors  }\label{sect:import}
+\subsection{RQ3: Does Tuning Select Different Project Factors? }\label{sect:import}
 
 Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.
-\fig{counts} shows that such conclusions are not reliable since they can be changed by tuning.
-This figure shows what attributes appeared in WHERE's final decision trees when optimizing for different goals.
-Note that the counts in the {\em tuned} column are   usually
-different to those in the {\em default} columns (the tuned learners used more attributes
-than otherwise as witnessed by the taller columns of numbers in the ``tuned'' column).
-
-\subsection{Tuning is Easy}\label{sect:easy}
+\fig{features} shows that such conclusions are not reliable since they can be changed by tuning.
+For space limitation, from each data set, we just select one experiment, like antV0, as representative.
+This figure shows what attributes appeared in WHERE's final decision trees when optimizing for different goals, precision and F-measure.
+Note that the attributes selected by tuned WHERE in each row shown in bold are usually different from default WHERE.
+Meanwhile, Tuning for different goals will usually select different attributes.
+In $\frac{9}{10}$ representative experiments, tuning select different attributes for precision and F-measure.
+% Note that the counts in the {\em tuned} column are   usually
+% different to those in the {\em default} columns (the tuned learners used more attributes
+% than otherwise as witnessed by the taller columns of numbers in the ``tuned'' column).
+
+That is, our answer to RQ3 is ``yes'', tuning changes our
+conclusions about what factors are most in important in software engineering.
+
+\subsection{RQ4: Is Tuning Easy?}\label{sect:easy}
 
@@
 (see next section).
+
+Hence we answer RQ4 as ``yes'', tuning is surprisingly easy (at least
+for defect predictors).
+% list some features
+\begin{figure*}[!ht]
+
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{c|l|l}
+    \multicolumn{1}{c|}{ Data set}  &   \multicolumn{1}{c|}{Precision} & \multicolumn{1}{c}{F} \\ \hline
+  \multirow{2}{*}{antV0} & {\bf mfa} &  {\bf None} \\
+         & mfa, dam, wmc, ic & mfa, dam, wmc, ic\\
+  \hline
+ \multirow{2}{*}{camelV0} & {\bf mfa, rfc, lcom3, cam, amc, loc, ic} &{\bf  mfa, wmc, cam, dam, loc, lcom3, rfc, ic, dit }\\
+        & mfa, rfc, lcom3, cam, dam, loc & mfa, rfc, lcom3, cam, dam, loc\\
+  \hline
+ \multirow{2}{*}{ivy} & {\bf dam, cam} &{\bf  cam, dit, npm, dam, wmc, lcom3 }  \\
+       & cam, dit, dam, ic & cam, dit, dam, ic \\
+  \hline
+ \multirow{2}{*}{jeditV0} &{\bf  mfa, dam, rfc, avg\_cc, lcom3, dit }&{\bf  dam, rfc, mfa, wmc, ce, cam, loc, avg\_cc}\\
+         & mfa, dam, lcom3, dit, ic, cbm & mfa, dam, lcom3, dit, ic, cbm \\
+  \hline
+ \multirow{2}{*}{log4j} & {\bf lcom3, mfa, loc, cbm, wmc }&{\bf  mfa, wmc}\\
+         & lcom3, mfa, loc, cbm, dit & lcom3, mfa, loc, ic \\
+   \hline
+  \multirow{2}{*}{lucene} & {\bf rfc, mfa, npm, cam} & {\bf mfa, dam, wmc, loc, rfc, ic}\\
+         & mfa, lcom3, cam, dam, ic & mfa, lcom3, cam, dam, ic\\
+   \hline
+   \multirow{2}{*}{poiV0} & {\bf loc }& {\bf loc} \\
+        & mfa, loc, amc, wmc, npm, lcom & mfa, loc, amc, wmc,npm, lcom\\
+   \hline
+   \multirow{2}{*}{synapse} &{\bf  dam} & {\bf loc, dam} \\
+        & dam, loc, mfa, cam & dam, loc, mfa, cam\\
+    \hline
+   \multirow{2}{*}{velocity} & {\bf dit, dam, cam, rfc, cbo, lcom3, wmc, ic, cbm }& {\bf dam, dit, loc, amc, lcom3, ic, mfa }\\
+        & dit, dam, lcom3, ic, mfa  & dit, dam, lcom3, ic, mfa\\
+    \hline
+   \multirow{2}{*}{xercesV0} &{\bf  None }&{\bf  dam, rfc, avg\_cc, dit, loc, lcom3, cam }\\
+        & cam, loc, dam, mfa, amc &  cam, loc, dam, mfa, amc \\
+    \hline
+
+  \end{tabular}
+
+    \caption{Features selected by different goals(features selected by tuning shown in bold). 
+    }\label{fig:features}
+\end{figure*}
 
@@
 
-\subsection{Tuning is Fast}\label{sect:fast}
+\subsection{RQ5: Is Tuning Impractically Slow?}\label{sect:fast}
 
@@
 to get a baseline, we tried {\em np=10} and the early stopping rules (number of lives used in
-Algorithm~1 on line 5) and obtained the results of this paper
-
-\subsection{Do not use ``off-the-shelf''  Default Tunings}\label{sect:variance}
+Algorithm~1 on line 5) and obtained the results of this paper.
+
+Hence, we answer RQ5 as ``no''. Tuning is so fast that
+it could (and should) be used by anyone using defect predictors.
+
+\subsection{RQ6: Should we use ``off-the-shelf'' Tunings?}\label{sect:variance}
 
@@
 \item The tunings learned by DE were different in different data sets and for different goals.
-That is, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
+Hence, we answer RQ6 as ``no'' since, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
 sets are changed.
@@
 The examples of this paper  only relate to precision, recall, and the F-measure
-but the general principle (that the search bias changes the search conclusions)  holds for all any set if goals. 
+but the general principle (that the search bias changes the search conclusions)  holds for all any set of goals. 
 Also,
@@
 
-When learning defect predictors for static code
+Our exploration of the six research
+questions listed in the introduction
+show that when learning defect predictors for static code
 attributes,   analytics without parameter tuning is considered {\em harmful} and {\em misleading}:
@@
 \item
-Tuning changes also changes conclusions on what factors are most important in software development.
+Also,
+tuning changes  changes conclusions on what factors are most important in software development.
 Once again, this means that old papers may need to be revised including those
@@
 
-As to future work:
-\bi
-\item
+\section{Future Work}
+
  As noted by
@@
 mining with a single system that rapidly performs both tasks.
-\item
+
 Another issue for future work is the implications of these
@@
 software analytics.
-\ei
 

### 2015-08-04 tuningpredictor.tex
updates: typos, revise according to reviewers

@@
 \usepackage{colortbl} 
+\usepackage{times}
 \usepackage{balance}
@@
 \newcommand{\wei}[1]{\textcolor{red}{Wei: #1}} 
+\newcommand{\Menzies}[1]{\textcolor{red}{Dr.Menzies: #1}}
 
@@
 \newcommand{\fig}[1]{Figure~\ref{fig:#1}}
+\newcommand{\tab}[1]{Table ~\ref{tab:#1}}
 \newcommand{\eq}[1]{Equation~\ref{eq:#1}}
@@
 \item RQ5: {\em Is tuning impractically slow?}. We achieved dramatic improvements in the performance scores
-of our data miners in less than 100 evaluations (!!); i.e. very
+of our data miners in less than 100 evaluations (!!); i.e., very
 quickly.
@@
 to assert that some factors were more important than others for predicting
-successful software reuse~\cite{me02k}. That assertion should now be doubted since that
-Menzies did not conduct a tuning study before reporting what factors the data miners
+successful software reuse~\cite{me02k}. That assertion should now be doubted since Menzies did not conduct a tuning study before reporting what factors the data miners
 found were most influential.
@@
 
-\begin{figure*}[t]
+\begin{table*}[t]
 \renewcommand{\baselinestretch}{0.8}\begin{center}
@@
 \end{center}
-\caption{OO measures used in our defect data sets.}\label{fig:ck}
-\end{figure*}
+\caption{OO measures used in our defect data sets.}\label{tab:ck}
+\end{table*}
 
@@
 That said, the bad news is that, for defect
-prediction, tuning results in dramatic changes in
+prediction, tuning dramatically changes
   what is learned from that data. Therefore, it is now an open and pressing research issue to check if
@@
 it is no longer enough to just run a data miner and report the result
-{\em without} first conducting an tuning optimizations study.
+{\em without} first conducting a tuning optimization study.
 
@@
 
-Our learners use the tuning parameters of \fig{parameters}. This section describes those parameters.
-
-CART, Random Forest, and WHERE-based learners are all  tree learners that divide a data set, then recurse
+Our learners use the tuning parameters of \tab{parameters}. This section describes those parameters.
+
+\wei{added HERE!} As shown in \tab{parameters}, default parameters for the Where-based learner are set using authors' engineering judgment and default parameters for CART and Random Forests are set by SciKitLearn.
+Those default parameters might not be the standard parameters for practical defect learners in reality, but it's a rule of thumb that most researchers would use just use the default parameters in the software without changes\cite{me07b} (\wei{MORE references should be cited here to support this statement}.
+)The tuning range is set according to the corresponding default parameters.
+The reason for this is to tell whether tuning with a small range can get a performance improvement (\Menzies{is this correct?})
+
+CART, Random Forest, and WHERE-based learners are all  tree learners that divide a data set, then recur
 on each split.
@@
  \subsubsection{Parametric Tuning Algorithms}
-The  goal of this paper is to adjust the tuning parameters of \fig{parameters}
+The  goal of this paper is to adjust the tuning parameters of \tab{parameters}
 in order to   optimize (improve) some particular performance scores
@@
 
- \begin{figure*}[!t]
+ \begin{table*}[!t]
 
@@
    }\label{fig:data1}
-\end{figure*}
+\end{table*}
 
@@
 is a pair of {\em (Tunings, Scores)}.  {\em Tunings} are selected from
-\fig{parameters} and {\em Scores} come from training a learner using those parameters
+\tab{parameters} and {\em Scores} come from training a learner using those parameters
 and applying it     test data$^{23-28}$.
@@
 
-Our defect data comes from the PROMISE repository (http://openscience.us/repo)
+Our defect data comes from the PROMISE repository \footnote{http://openscience.us/repo}
 and pertains to 
-open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
+open source Java systems defined in terms of \tab{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
 {\it poi},{\it synapse}, {\it velocity} and {\it xerces}.
@@
 
-\begin{figure}[!tb]
+\begin{table}[!tb]
 \renewcommand{\baselinestretch}{0.8}
@@
 \caption{Precision results (best results  shown in {\bf bold}).}
-\label{fig:precisionbars}
-\end{figure}
+\label{tab:precisionbars}
+\end{table}
 
@@
 
-\fig{precisionbars} shows precision results before and after tuning with precision as the performance criteria 
+\tab{precisionbars} shows precision results before and after tuning with precision as the performance criteria 
 using three different learners.
@@
  \end{center}
-\caption{Deltas in performance  seen in \fig{precisionbars} (left)
-and \fig{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
+\caption{Deltas in performance  seen in \tab{precisionbars} (left)
+and \tab{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
  \end{figure}
@@
 
-In \fig{precisionbars} and \fig{fbars}, the tuned CART are better than or equal to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
+In \tab{precisionbars} and \tab{fbars}, the tuned CART are better than or equal to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
 terms of precision and F-measure, respectively. Results from the non-parametric Kolmogorov-Smirnov Test turn out that the performance 
-scores of tuned CART and tuned Random Forests are not statistically different. This is the pposite of   
+scores of tuned CART and tuned Random Forests are not statistically different. This is the opposite of   
  Lessmann et al.~\cite{lessmann2008benchmarking}, the tuned Random Forest is not significantly better than tuned CART.
- In another result that is the reverse of \fig{precisionbars}, tuned WHERE is not necessarily
+ In another result that is the reverse of \tab{precisionbars}, tuned WHERE is not necessarily
  any better than anything else.
@@
 
-\begin{figure}[!t]
+\begin{table}[!t]
 \renewcommand{\baselinestretch}{0.8}
@@
 \caption{F-value results (best results  shown in {\bf bold}).}
-\label{fig:fbars}
-\end{figure}
+\label{tab:fbars}
+\end{table}
 
@@
 Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.
-\fig{features} shows that such conclusions are not reliable since they can be changed by tuning.
+\tab{features} shows that such conclusions are not reliable since they can be changed by tuning.
 For space limitation, from each data set, we just select one experiment, like antV0, as representative.
@@
 Note that the attributes selected by tuned WHERE in each row shown in bold are usually different from default WHERE.
-Meanwhile, Tuning for different goals will usually select different attributes.
-In $\frac{9}{10}$ representative experiments, tuning select different attributes for precision and F-measure.
+Meanwhile, in $\frac{9}{10}$ representative experiments, for the same data set, tuning selects different attributes for precision and F-measure.
+
+\Menzies{I suggest replace \tab{counts} with \tab{features}, because this new table is more straightforward. \begin{itemize}
+\item Do you have any insights into this figure 8?
+\item like, are there any specific features considered very important in Default WHERE but not showing up in Tuning WHERE? . 
+\item WHY???
+\end{itemize}
+}
 % Note that the counts in the {\em tuned} column are   usually
@@
 % than otherwise as witnessed by the taller columns of numbers in the ``tuned'' column). 
+According to default WHERE, {\it mfa} is considered as the most important factor because it's selected in $\frac{9}{10}$ experiments for both goals.
+However, in tuning process, this factor has only shown as key factor in $\frac{5}{10}$ experiments for both precision and F-measure.
 
 That is, our answer to RQ3 is ``yes'', tuning changes our
-conclusions about what factors are most in important in software engineering.
+conclusions about what factors are most important in software engineering.
 
@@
 
-From \fig{parameters},
+From \tab{parameters},
 we see that Storn would therefore recommend {\em np} values of
@@
 
+\Menzies{probably, here we should have an experiment to compare np = 10 with np = 90(the recommended population) for at least one learner, to justify np = 10 is enough and tuning is easy }
+
+\Menzies{can we answer why the searching is so easy, what's the reason leading less than 100 evaluations that can find a better solution}
+
 Another measure showing that tuning is easy 
@@
 % list some features
-\begin{figure*}[!ht]
+\begin{table*}[!ht]
 
@@
 
-    \caption{Features selected by different goals(features selected by tuning shown in bold). 
-    }\label{fig:features}
-\end{figure*}
-
-\begin{figure}[!ht]
+    \caption{Features selected by tuned WHERE with different goals(features selected by tuning shown in bold). 
+    }\label{tab:features}
+\end{table*}
+
+\begin{table}[!ht]
 
@@
 one cell in the ``precision'' or ``F'' column is 17.  
-    }\label{fig:counts}
-\end{figure}
-
-\begin{figure*}[!ht]
+    }\label{tab:counts}
+\end{table}
+
+\begin{table*}[!ht]
 
@@
   \end{tabular}
-  \caption{Evaluations/runtimes  (in seconds), optimizing for  precision.  }\label{fig:etimes}
-\end{figure*}
+  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for  precision.  }\label{tab:etimes}
+\end{table*}
 %%%%time for F %%%%%%
-\begin{figure*}[!ht]
+\begin{table*}[!ht]
 \renewcommand{\baselinestretch}{0.75}
@@
   \end{tabular}
-  \caption{Evaluations/runtimes  (in seconds), optimizing for  ``F''.  }\label{fig:ftimes}
-\end{figure*}
+  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for  ``F''.  }\label{tab:ftimes}
+\end{table*}
 
@@
 
-The number of evaluations/runtimes used by our optimizers is shown in \fig{etimes}
-and \fig{ftimes}.
+The number of evaluations/runtimes used by our optimizers is shown in \tab{etimes}
+and \tab{ftimes}.
 WHERE's runtimes are slower than CART and Random Forest since WHERE has yet to benefit from decades
 of implementation experience with these older algorithms. For example, SciKitLearn's  CART and Random Forest
- make extensive use of an underlying ``C'' library whereas WHERE is a purely interpreted Python.
-
-Looking over \fig{etimes} and \fig{ftimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
+ make extensive use of an underlying C library whereas WHERE is a purely interpreted Python.
+
+Looking over \tab{etimes} and \tab{ftimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
 improvements reported in this paper. 
@@
 
+(\Menzies{do we need to give some empirical answers to WHY?}\wei{added HERE!}) The possible reason that tuning is so fast is that the searching space for defect prediction is not complicated, which might result from the tuning range set in \tab{parameters}
+
 \subsection{RQ6: Should we use ``off-the-shelf'' Tunings?}\label{sect:variance}
 
- \fig{preselect} and \fig{fselect} show   tunings learned by DE. 
+ \tab{preselect} and \tab{fselect} show  tunings learned by DE. 
 The left hand side columns shows some standard default values. Note that:
@@
 %%%%parameters for prec %%%%%%
-\begin{figure*}[!ht]
+\begin{table*}[!ht]
 
@@
 }
-  \caption{Parameters tuned on different models over the objective of precision.}\label{fig:preselect}
-\end{figure*}
+  \caption{Parameters tuned on different models over the objective of precision.}\label{tab:preselect}
+\end{table*}
 
 %%%%parameters for F %%%%%%
-\begin{figure*}[!ht]
+\begin{table*}[!ht]
 
@@
 }
-  \caption{Parameters tuned on different models over the objective of ``F''.}\label{fig:fselect}
-\end{figure*}
+  \caption{Parameters tuned on different models over the objective of ``F''.}\label{tab:fselect}
+\end{table*}
 
@@
 on-line in the PROMISE code repository and all our algorithms
-are on-line at github.com/a-se/where.
+are on-line at github.com/ai-se/where.
 
@@
 {\em training} and
-{\em tuning}.  This mean that, potentially,  the performance increases
+{\em tuning}.  This means that, potentially,  the performance increases
 reported above are merely an artificat of the DEs being able to access
@@
 Also,
-tuning changes  changes conclusions on what factors are most important in software development.
+tuning changes conclusions on what factors are most important in software development.
 Once again, this means that old papers may need to be revised including those
@@
 Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
-\fig{preselect} and \fig{fselect}    show just how much tuning can alter default settings
+\tab{preselect} and \tab{fselect}    show just how much tuning can alter default settings
 both for different data sets and for different goals.

### 2015-08-05 tuningpredictor.tex
updates

@@
 
-\Menzies{I suggest replace \tab{counts} with \tab{features}, because this new table is more straightforward. \begin{itemize}
-\item Do you have any insights into this figure 8?
+\Menzies{
+\begin{itemize}
+\item Do you have any insights into this table 6?
 \item like, are there any specific features considered very important in Default WHERE but not showing up in Tuning WHERE? . 
@@
 
-\begin{table}[!ht]
-
-\renewcommand{\baselinestretch}{0.8}
-\scriptsize
-\centering
-  \begin{tabular}{c|c c|c c|c c|c c| c c }
-
-    &   \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{F} &  \multicolumn{2}{c|}{SUM}\\
- &&&&&&&\\
-Features&   
-  default
-& tuned
-& default
-& tuned
-& default
-& tuned
-\\\hline
-
-max\_cc& & & &  & & \\
-noc& & & & & & \\
-ca& & & & & & \\
-cbo& & 1& & & & 1\\
-moa& & 1& & & & 1\\
-ce& & 2& & 1& & 3\\
-avg\_cc& & 2& & 2& & 4\\
-npm& 1& 2& 1& 1&2 & 3\\
-lcom& 1& 2& 1& 1& 2& 3\\
-amc& 4& 2& 4& 2& 8& 4\\
-cbm& 5& 2& 5& 3& 10& 5\\
-rfc& 3& 6& 3& 8& 6& 14\\
-wmc& 5& 4& 5& 9& 10& 13\\
-dit& 8& 3& 7& 7& 15& 10\\
-ic& 8& 3& 8& 6& 16 & 9\\
-lcom3& 8& 6& 8& 8&16 & 14\\
-cam& 9& 7& 9& 7& 18& 14\\
-loc& 9& 5& 9& 11& 18& 16\\
-dam& 13& 6& 13& 11& 26& 17 \\
-mfa& 16& 9& 16& 9&32 & 18\\
-
-  \end{tabular}
-    \caption{Counts of features selected by different goals.Given that we are processing 17 data sets, the maximum counts for any 
-one cell in the ``precision'' or ``F'' column is 17.  
-    }\label{tab:counts}
-\end{table}
+% %%% repalce this table with the new one
+% \begin{table}[!ht]
+
+% \renewcommand{\baselinestretch}{0.8}
+% \scriptsize
+% \centering
+%   \begin{tabular}{c|c c|c c|c c|c c| c c }
+
+%     &   \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{F} &  \multicolumn{2}{c|}{SUM}\\
+%  &&&&&&&\\
+% Features&   
+%   default
+% & tuned
+% & default
+% & tuned
+% & default
+% & tuned
+% \\\hline
+
+% max\_cc& & & &  & & \\
+% noc& & & & & & \\
+% ca& & & & & & \\
+% cbo& & 1& & & & 1\\
+% moa& & 1& & & & 1\\
+% ce& & 2& & 1& & 3\\
+% avg\_cc& & 2& & 2& & 4\\
+% npm& 1& 2& 1& 1&2 & 3\\
+% lcom& 1& 2& 1& 1& 2& 3\\
+% amc& 4& 2& 4& 2& 8& 4\\
+% cbm& 5& 2& 5& 3& 10& 5\\
+% rfc& 3& 6& 3& 8& 6& 14\\
+% wmc& 5& 4& 5& 9& 10& 13\\
+% dit& 8& 3& 7& 7& 15& 10\\
+% ic& 8& 3& 8& 6& 16 & 9\\
+% lcom3& 8& 6& 8& 8&16 & 14\\
+% cam& 9& 7& 9& 7& 18& 14\\
+% loc& 9& 5& 9& 11& 18& 16\\
+% dam& 13& 6& 13& 11& 26& 17 \\
+% mfa& 16& 9& 16& 9&32 & 18\\
+
+%   \end{tabular}
+%     \caption{Counts of features selected by different goals.Given that we are processing 17 data sets, the maximum counts for any 
+% one cell in the ``precision'' or ``F'' column is 17.  
+%     }\label{tab:counts}
+% \end{table}
 
@@
 
- \tab{preselect} and \tab{fselect} show  tunings learned by DE. 
+ \wei{remove those two figures here! need to complete here}show  tunings learned by DE. 
 The left hand side columns shows some standard default values. Note that:
@@
 
-%%%%parameters for prec %%%%%%
-\begin{table*}[!ht]
-
-\renewcommand{\baselinestretch}{0.9}
-\resizebox{\textwidth}{!}{
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.98& 0.98& 0.43& 0.24& 0.64& 1& 1& 0.98& 0.98& 1& 1& 0.87& 0.59& 0.98& 1& 0.98& 0.98\\ \cline{2-20}
-& infoPrune& 0.33& 0.05& 0.05& 0.71& 0.54& 0.45& 0.41& 0.3& 0.05& 0.05& 0.54& 0.84& 0.01& 1& 0.05& 0.68& 0.43& 0.05\\ \cline{2-20}
-& min\_sample\_size& 4& 7& 7& 9& 8& 6& 10& 1& 5& 7& 8& 7& 9& 3& 7& 7& 1& 7\\ \cline{2-20}
-& min\_Size& 0.5& 0.51& 0.51& 0.59& 0.46& 0.13& 0.38& 0.66& 0.27& 0.51& 0.46& 0.47& 0.77& 0.48& 0.51& 0.66& 0.22& 0.51\\ \cline{2-20}
-& wriggle& 0.2& 0.6& 0.6& 0.83& 0.52& 0.19& 0.01& 0.26& 0.6& 0.6& 0.52& 0.19& 0.83& 0.01& 0.6& 0.26& 0.55& 0.6\\ \cline{2-20}
-& depthMin& 2& 1& 1& 2& 3& 5& 2& 3& 3& 1& 1& 2& 4& 2& 1& 3& 2& 1\\ \cline{2-20}
-& depthMax& 10& 8& 8& 13& 19& 19& 18& 7& 8& 8& 19& 1& 19& 18& 8& 11& 18& 8\\ \cline{2-20}
-& wherePrune& False& False& False& False& False& True& True& False& False& False& False& False& True& True& False& False& True& False\\ \cline{2-20}
-& treePrune& True& False& False& False& True& True& True& False& False& False& True& True& False& False& False& False& True& False\\ \cline{2-20}
-\hline
-\multirow{4}{*}{CART}
-& threshold& 0.5& 0.69& 0.99& 1& 0.3& 0.83& 1& 0.99& 0.58& 0.72& 1& 0.71& 0.46& 0.72& 1& 0.85& 1& 0.64\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.58& 0.65& 0.66& 0.73& 0.67& 0.56& 0.01& 0.97& 0.54& 0.52& 0.32& 0.01& 0.74& 0.73& 0.01& 0.1\\ \cline{2-20}
-& min\_samples\_split& 2& 7& 16& 18& 5& 11& 6& 15& 6& 17& 4& 16& 12& 5& 14& 11& 4& 10\\ \cline{2-20}
-& min\_samples\_leaf& 1& 13& 14& 10& 4& 3& 15& 16& 9& 6& 7& 6& 1& 4& 6& 7& 11& 7\\ \cline{2-20}
-& max\_depth& None& 14& 1& 41& 34& 1& 22& 29& 1& 1& 1& 14& 19& 8& 40& 4& 1& 1\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.84& 0.9& 0.83& 0.33& 1& 0.99& 0.91& 1& 1& 0.83& 0.98& 0.9& 0.86& 0.83& 1& 1& 1\\ \cline{2-20}
-& max\_feature& None& 0.61& 0.13& 0.89& 0.37& 0.01& 0.98& 0.52& 0.75& 0.35& 0.01& 0.98& 0.84& 0.73& 0.01& 0.48& 0.51& 0.01\\ \cline{2-20}
-& max\_leaf\_nodes& None& 37& 35& 38& 21& 36& 45& 10& 38& 10& 30& 20& 43& 11& 13& 15& 39& 10\\ \cline{2-20}
-& min\_samples\_split& 2& 8& 16& 17& 13& 14& 2& 3& 2& 2& 18& 19& 9& 4& 4& 9& 20& 1\\ \cline{2-20}
-& min\_samples\_leaf& 1& 19& 5& 2& 4& 2& 4& 7& 17& 7& 16& 12& 2& 3& 2& 2& 2& 3\\ \cline{2-20}
-& n\_estimators& 100& 138& 112& 77& 74& 125& 130& 107& 85& 96& 111& 103& 82& 59& 149& 150& 63& 58\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of precision.}\label{tab:preselect}
-\end{table*}
-
-%%%%parameters for F %%%%%%
-\begin{table*}[!ht]
-
-\resizebox{\textwidth}{!}{
-\renewcommand{\baselinestretch}{0.9}
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.04& 0.44& 0.44& 0.98& 0.65& 0.77& 1& 0.65& 0.98& 0.44& 0.44& 0.87& 0.04& 0.77& 0.24& 0.44& 0.77\\ \cline{2-20}
-& infoPrune& 0.33& 0.51& 0.68& 0.88& 0.47& 0.07& 0.31& 0.48& 0.68& 0.57& 0.12& 0.68& 0.01& 0.51& 0.14& 0.54& 0.68& 0.14\\ \cline{2-20}
-& min\_sample\_size& 4& 6& 4& 6& 1& 6& 8& 8& 4& 6& 7& 4& 9& 6& 2& 8& 4& 8\\ \cline{2-20}
-& min\_Size& 0.5& 0.18& 0.4& 0.56& 0.51& 0.65& 0.59& 0.97& 0.4& 0.51& 0.8& 0.4& 0.77& 0.18& 0.62& 0.46& 0.4& 0.66\\ \cline{2-20}
-& wriggle& 0.2& 0.25& 0.29& 0.76& 0.6& 0.63& 0.26& 1& 0.51& 0.17& 0.36& 0.51& 0.83& 0.25& 0.5& 0.52& 0.29& 0.26\\ \cline{2-20}
-& depthMin& 2& 3& 3& 3& 1& 5& 3& 2& 3& 5& 5& 3& 4& 3& 3& 3& 3& 3\\ \cline{2-20}
-& depthMax& 10& 16& 15& 15& 8& 19& 10& 7& 15& 5& 15& 15& 19& 16& 6& 19& 15& 10\\ \cline{2-20}
-& wherePrune& False& False& True& True& True& True& True& True& False& False& True& True& True& False& True& False& False& True\\ \cline{2-20}
-& treePrune& True& False& True& True& False& False& False& False& False& True& True& True& False& False& False& True& True& False\\ \cline{2-20}
-\hline
-\multirow{5}{*}{CART}
-& threshold& 0.5& 0.34& 0.25& 0.01& 0.01& 0.73& 0.53& 0.92& 0.8& 0.74& 0.54& 0.03& 0.91& 0.01& 0.01& 0.55& 1& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.01& 0.29& 0.01& 0.46& 0.75& 0.79& 0.74& 0.41& 0.81& 0.61& 0.72& 0.01& 0.01& 0.01& 0.25& 0.18\\ \cline{2-20}
-& min\_samples\_split& 2& 18& 20& 12& 2& 15& 11& 2& 18& 13& 9& 17& 16& 10& 4& 8& 3& 15\\ \cline{2-20}
-& min\_samples\_leaf& 1& 19& 16& 15& 17& 1& 1& 13& 10& 4& 3& 7& 5& 20& 7& 8& 1& 6\\ \cline{2-20}
-& max\_depth& None& 12& 2& 15& 1& 41& 20& 44& 15& 13& 5& 23& 14& 1& 5& 17& 47& 13\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.01& 0.35& 0.3& 0.01& 0.9& 0.97& 0.63& 1& 0.73& 0.68& 0.01& 1.0& 0.01& 0.07& 0.22& 1& 0.82\\ \cline{2-20}
-& max\_feature& None& 0.63& 0.17& 0.01& 0.01& 0.88& 0.74& 0.76& 0.73& 0.01& 0.03& 0.39& 0.02& 0.01& 0.56& 0.36& 0.51& 0.89\\ \cline{2-20}
-& max\_leaf\_nodes& None& 40& 33& 46& 22& 11& 16& 38& 34& 30& 31& 12& 49& 25& 47& 15& 39& 24\\ \cline{2-20}
-& min\_samples\_split& 2& 10& 16& 20& 1& 1& 1& 1& 4& 20& 19& 11& 14& 2& 17& 19& 20& 19\\ \cline{2-20}
-& min\_samples\_leaf& 1& 4& 15& 9& 13& 18& 11& 3& 16& 17& 6& 10& 7& 19& 13& 11& 2& 14\\ \cline{2-20}
-& n\_estimators& 100& 120& 73& 75& 130& 97& 144& 125& 97& 80& 111& 96& 101& 50& 67& 74& 63& 66\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of ``F''.}\label{tab:fselect}
-\end{table*}
+% %%%%parameters for prec %%%%%%
+% \begin{table*}[!ht]
+
+% \renewcommand{\baselinestretch}{0.9}
+% \resizebox{\textwidth}{!}{
+% \scriptsize
+% \centering
+%   \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+%     \hline
+%   \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
+%  \hline
+% \multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+% & threshold& 0.5& 0.98& 0.98& 0.43& 0.24& 0.64& 1& 1& 0.98& 0.98& 1& 1& 0.87& 0.59& 0.98& 1& 0.98& 0.98\\ \cline{2-20}
+% & infoPrune& 0.33& 0.05& 0.05& 0.71& 0.54& 0.45& 0.41& 0.3& 0.05& 0.05& 0.54& 0.84& 0.01& 1& 0.05& 0.68& 0.43& 0.05\\ \cline{2-20}
+% & min\_sample\_size& 4& 7& 7& 9& 8& 6& 10& 1& 5& 7& 8& 7& 9& 3& 7& 7& 1& 7\\ \cline{2-20}
+% & min\_Size& 0.5& 0.51& 0.51& 0.59& 0.46& 0.13& 0.38& 0.66& 0.27& 0.51& 0.46& 0.47& 0.77& 0.48& 0.51& 0.66& 0.22& 0.51\\ \cline{2-20}
+% & wriggle& 0.2& 0.6& 0.6& 0.83& 0.52& 0.19& 0.01& 0.26& 0.6& 0.6& 0.52& 0.19& 0.83& 0.01& 0.6& 0.26& 0.55& 0.6\\ \cline{2-20}
+% & depthMin& 2& 1& 1& 2& 3& 5& 2& 3& 3& 1& 1& 2& 4& 2& 1& 3& 2& 1\\ \cline{2-20}
+% & depthMax& 10& 8& 8& 13& 19& 19& 18& 7& 8& 8& 19& 1& 19& 18& 8& 11& 18& 8\\ \cline{2-20}
+% & wherePrune& False& False& False& False& False& True& True& False& False& False& False& False& True& True& False& False& True& False\\ \cline{2-20}
+% & treePrune& True& False& False& False& True& True& True& False& False& False& True& True& False& False& False& False& True& False\\ \cline{2-20}
+% \hline
+% \multirow{4}{*}{CART}
+% & threshold& 0.5& 0.69& 0.99& 1& 0.3& 0.83& 1& 0.99& 0.58& 0.72& 1& 0.71& 0.46& 0.72& 1& 0.85& 1& 0.64\\ \cline{2-20}
+% & max\_feature& None& 0.01& 0.58& 0.65& 0.66& 0.73& 0.67& 0.56& 0.01& 0.97& 0.54& 0.52& 0.32& 0.01& 0.74& 0.73& 0.01& 0.1\\ \cline{2-20}
+% & min\_samples\_split& 2& 7& 16& 18& 5& 11& 6& 15& 6& 17& 4& 16& 12& 5& 14& 11& 4& 10\\ \cline{2-20}
+% & min\_samples\_leaf& 1& 13& 14& 10& 4& 3& 15& 16& 9& 6& 7& 6& 1& 4& 6& 7& 11& 7\\ \cline{2-20}
+% & max\_depth& None& 14& 1& 41& 34& 1& 22& 29& 1& 1& 1& 14& 19& 8& 40& 4& 1& 1\\ \cline{2-20}
+% \hline
+% \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+% & threshold& 0.5& 0.84& 0.9& 0.83& 0.33& 1& 0.99& 0.91& 1& 1& 0.83& 0.98& 0.9& 0.86& 0.83& 1& 1& 1\\ \cline{2-20}
+% & max\_feature& None& 0.61& 0.13& 0.89& 0.37& 0.01& 0.98& 0.52& 0.75& 0.35& 0.01& 0.98& 0.84& 0.73& 0.01& 0.48& 0.51& 0.01\\ \cline{2-20}
+% & max\_leaf\_nodes& None& 37& 35& 38& 21& 36& 45& 10& 38& 10& 30& 20& 43& 11& 13& 15& 39& 10\\ \cline{2-20}
+% & min\_samples\_split& 2& 8& 16& 17& 13& 14& 2& 3& 2& 2& 18& 19& 9& 4& 4& 9& 20& 1\\ \cline{2-20}
+% & min\_samples\_leaf& 1& 19& 5& 2& 4& 2& 4& 7& 17& 7& 16& 12& 2& 3& 2& 2& 2& 3\\ \cline{2-20}
+% & n\_estimators& 100& 138& 112& 77& 74& 125& 130& 107& 85& 96& 111& 103& 82& 59& 149& 150& 63& 58\\ \cline{2-20}
+% \hline  \end{tabular}
+% }
+%   \caption{Parameters tuned on different models over the objective of precision.}\label{tab:preselect}
+% \end{table*}
+
+% %%%%parameters for F %%%%%%
+% \begin{table*}[!ht]
+
+% \resizebox{\textwidth}{!}{
+% \renewcommand{\baselinestretch}{0.9}
+% \scriptsize
+% \centering
+%   \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+%     \hline
+
+%   \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
+%  \hline
+% \multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+% & threshold& 0.5& 0.04& 0.44& 0.44& 0.98& 0.65& 0.77& 1& 0.65& 0.98& 0.44& 0.44& 0.87& 0.04& 0.77& 0.24& 0.44& 0.77\\ \cline{2-20}
+% & infoPrune& 0.33& 0.51& 0.68& 0.88& 0.47& 0.07& 0.31& 0.48& 0.68& 0.57& 0.12& 0.68& 0.01& 0.51& 0.14& 0.54& 0.68& 0.14\\ \cline{2-20}
+% & min\_sample\_size& 4& 6& 4& 6& 1& 6& 8& 8& 4& 6& 7& 4& 9& 6& 2& 8& 4& 8\\ \cline{2-20}
+% & min\_Size& 0.5& 0.18& 0.4& 0.56& 0.51& 0.65& 0.59& 0.97& 0.4& 0.51& 0.8& 0.4& 0.77& 0.18& 0.62& 0.46& 0.4& 0.66\\ \cline{2-20}
+% & wriggle& 0.2& 0.25& 0.29& 0.76& 0.6& 0.63& 0.26& 1& 0.51& 0.17& 0.36& 0.51& 0.83& 0.25& 0.5& 0.52& 0.29& 0.26\\ \cline{2-20}
+% & depthMin& 2& 3& 3& 3& 1& 5& 3& 2& 3& 5& 5& 3& 4& 3& 3& 3& 3& 3\\ \cline{2-20}
+% & depthMax& 10& 16& 15& 15& 8& 19& 10& 7& 15& 5& 15& 15& 19& 16& 6& 19& 15& 10\\ \cline{2-20}
+% & wherePrune& False& False& True& True& True& True& True& True& False& False& True& True& True& False& True& False& False& True\\ \cline{2-20}
+% & treePrune& True& False& True& True& False& False& False& False& False& True& True& True& False& False& False& True& True& False\\ \cline{2-20}
+% \hline
+% \multirow{5}{*}{CART}
+% & threshold& 0.5& 0.34& 0.25& 0.01& 0.01& 0.73& 0.53& 0.92& 0.8& 0.74& 0.54& 0.03& 0.91& 0.01& 0.01& 0.55& 1& 0.01\\ \cline{2-20}
+% & max\_feature& None& 0.01& 0.01& 0.29& 0.01& 0.46& 0.75& 0.79& 0.74& 0.41& 0.81& 0.61& 0.72& 0.01& 0.01& 0.01& 0.25& 0.18\\ \cline{2-20}
+% & min\_samples\_split& 2& 18& 20& 12& 2& 15& 11& 2& 18& 13& 9& 17& 16& 10& 4& 8& 3& 15\\ \cline{2-20}
+% & min\_samples\_leaf& 1& 19& 16& 15& 17& 1& 1& 13& 10& 4& 3& 7& 5& 20& 7& 8& 1& 6\\ \cline{2-20}
+% & max\_depth& None& 12& 2& 15& 1& 41& 20& 44& 15& 13& 5& 23& 14& 1& 5& 17& 47& 13\\ \cline{2-20}
+% \hline
+% \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+% & threshold& 0.5& 0.01& 0.35& 0.3& 0.01& 0.9& 0.97& 0.63& 1& 0.73& 0.68& 0.01& 1.0& 0.01& 0.07& 0.22& 1& 0.82\\ \cline{2-20}
+% & max\_feature& None& 0.63& 0.17& 0.01& 0.01& 0.88& 0.74& 0.76& 0.73& 0.01& 0.03& 0.39& 0.02& 0.01& 0.56& 0.36& 0.51& 0.89\\ \cline{2-20}
+% & max\_leaf\_nodes& None& 40& 33& 46& 22& 11& 16& 38& 34& 30& 31& 12& 49& 25& 47& 15& 39& 24\\ \cline{2-20}
+% & min\_samples\_split& 2& 10& 16& 20& 1& 1& 1& 1& 4& 20& 19& 11& 14& 2& 17& 19& 20& 19\\ \cline{2-20}
+% & min\_samples\_leaf& 1& 4& 15& 9& 13& 18& 11& 3& 16& 17& 6& 10& 7& 19& 13& 11& 2& 14\\ \cline{2-20}
+% & n\_estimators& 100& 120& 73& 75& 130& 97& 144& 125& 97& 80& 111& 96& 101& 50& 67& 74& 63& 66\\ \cline{2-20}
+% \hline  \end{tabular}
+% }
+%   \caption{Parameters tuned on different models over the objective of ``F''.}\label{tab:fselect}
+% \end{table*}
 
@@
 Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
-\tab{preselect} and \tab{fselect}    show just how much tuning can alter default settings
+\wei{remove those two figures here, need to compelete sentence with new ones} show just how much tuning can alter default settings
 both for different data sets and for different goals.

### 2015-08-07 tuningpredictor.tex

@@
 \usepackage{algpseudocode}
+\usepackage[export]{adjustbox}
 \renewcommand{\footnotesize}{\scriptsize}
@@
 
-\subsection{RQ3: Does Tuning Select Different Project Factors? }\label{sect:import}
-
-Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.
-\tab{features} shows that such conclusions are not reliable since they can be changed by tuning.
-For space limitation, from each data set, we just select one experiment, like antV0, as representative.
-This figure shows what attributes appeared in WHERE's final decision trees when optimizing for different goals, precision and F-measure.
-Note that the attributes selected by tuned WHERE in each row shown in bold are usually different from default WHERE.
-Meanwhile, in $\frac{9}{10}$ representative experiments, for the same data set, tuning selects different attributes for precision and F-measure.
-
-\Menzies{
-\begin{itemize}
-\item Do you have any insights into this table 6?
-\item like, are there any specific features considered very important in Default WHERE but not showing up in Tuning WHERE? . 
-\item WHY???
-\end{itemize}
-}
-% Note that the counts in the {\em tuned} column are   usually
-% different to those in the {\em default} columns (the tuned learners used more attributes
-% than otherwise as witnessed by the taller columns of numbers in the ``tuned'' column). 
-According to default WHERE, {\it mfa} is considered as the most important factor because it's selected in $\frac{9}{10}$ experiments for both goals.
-However, in tuning process, this factor has only shown as key factor in $\frac{5}{10}$ experiments for both precision and F-measure.
-
-That is, our answer to RQ3 is ``yes'', tuning changes our
-conclusions about what factors are most important in software engineering.
-
-\subsection{RQ4: Is Tuning Easy?}\label{sect:easy}
-
-In terms of the search space
-explored via tuning, optimizing defect prediction from static code
-measures is much {\em smaller} than the standard optimization.
-
-To see this,
-recall from Algorithm~1 that
-DE explores a {\em Population} of size {\em np=10}. This is a very small population size since
-Rainer Storn (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
-of attributes being optimized~\cite{storn1997differential}.
-
-From \tab{parameters},
-we see that Storn would therefore recommend {\em np} values of
-90, 50, 60 for WHERE, CART and Random Forests (respectively). Yet we achieve our results
-using a constant {\em np=10}; i.e. $\frac{10}{90}, \frac{10}{50}, \frac{10}{60}$ of the
-recommended search space.
-
-\Menzies{probably, here we should have an experiment to compare np = 10 with np = 90(the recommended population) for at least one learner, to justify np = 10 is enough and tuning is easy }
-
-\Menzies{can we answer why the searching is so easy, what's the reason leading less than 100 evaluations that can find a better solution}
-
-Another measure showing that tuning is easy 
-(for static code defect predictors)
-is the number of evaluations required to complete optimization
-(see next section).
-
-Hence we answer RQ4 as ``yes'', tuning is surprisingly easy (at least
-for defect predictors).
 % list some features
@@
 
+\subsection{RQ3: Does Tuning Select Different Project Factors? }\label{sect:import}
+
+Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.
+\tab{features} shows that such conclusions are not reliable since they can be changed by tuning.
+For space limitation, from each data set, we just select one experiment, like antV0, as representative.
+This figure shows what attributes appeared in WHERE's final decision trees when optimizing for different goals, precision and F-measure.
+Note that the attributes selected by tuned WHERE in each row shown in bold are usually different from default WHERE.
+Meanwhile, in $\frac{9}{10}$ representative experiments, for the same data set, tuning selects different attributes for precision and F-measure.
+
+\Menzies{
+\begin{itemize}
+\item Do you have any insights into this table 6?
+\item like, are there any specific features considered very important in Default WHERE but not showing up in Tuning WHERE? . 
+\item WHY???
+\end{itemize}
+}
+% Note that the counts in the {\em tuned} column are   usually
+% different to those in the {\em default} columns (the tuned learners used more attributes
+% than otherwise as witnessed by the taller columns of numbers in the ``tuned'' column). 
+According to default WHERE, {\it mfa} is considered as the most important factor because it's selected in $\frac{9}{10}$ experiments for both goals.
+However, in tuning process, this factor has only shown as key factor in $\frac{5}{10}$ experiments for both precision and F-measure.
+
+That is, our answer to RQ3 is ``yes'', tuning changes our
+conclusions about what factors are most important in software engineering.
+
+\begin{figure}[!b]
+\includegraphics[width=3.5in,left]{np_10_90.eps}
+\caption{Deltas in terms of F when using 10 and 90 as the population in DE. np=90 is better when the deltas are above zero.}\label{fig:deltas_np}
+ \end{figure}
+
+\subsection{RQ4: Is Tuning Easy?}\label{sect:easy}
+
+In terms of the search space
+explored via tuning, optimizing defect prediction from static code
+measures is much {\em smaller} than the standard optimization.
+
+To see this,
+recall from Algorithm~1 that
+DE explores a {\em Population} of size {\em np=10}. This is a very small population size since
+Rainer Storn (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
+of attributes being optimized~\cite{storn1997differential}.
+
+From \tab{parameters},
+we see that Storn would therefore recommend {\em np} values of
+90, 50, 60 for WHERE, CART and Random Forests (respectively). Yet we achieve our results
+using a constant {\em np=10}; i.e. $\frac{10}{90}, \frac{10}{50}, \frac{10}{60}$ of the
+recommended search space.
+
+\wei{added!} To justify that {\em np=10} is enough, we did another tuning study, 
+where all the settings are the same as before but we chose {\em np=90} as recommended by Storn. 
+The tuning performance of learners is evaluated
+by F.
+To compare the results of {\em np=10} and {\em np=90}, we plot the delta in the performance as \fig{deltas}.
+In \fig{deltas_np}, 5 data sets are better but 4 data sets are worse when {\em np = 90} for WHERE.
+For CART and Random Forest, the numbers of better and worse data sets are both 4.
+The improvement for those better data sets is negligible to some extent but the deterioration is not.
+From this study, {\em np = 90}, which is recommended for WHERE and more than the number for CART and Random Forest, does not bring any significant improvement over {\em np=10}.
+Therefore, the searching space is very simple for tuning defect predictor, which makes tuning very simple.
+
+Another measure showing that tuning is easy 
+(for static code defect predictors)
+is the number of evaluations required to complete optimization
+(see next section).
+
+Hence we answer RQ4 as ``yes'', tuning is surprisingly easy (at least
+for defect predictors).
+
 % %%% repalce this table with the new one
@@
 it could (and should) be used by anyone using defect predictors.
-
-(\Menzies{do we need to give some empirical answers to WHY?}\wei{added HERE!}) The possible reason that tuning is so fast is that the searching space for defect prediction is not complicated, which might result from the tuning range set in \tab{parameters}
+The possible reason that tuning is so fast is that the searching space for defect prediction is not complicated, which might result from the tuning range set for each parameter in \tab{parameters}.
+The early stopping rules applied in this study also helps make tuning fast\wei{added HERE!}
 

### 2015-08-07 tuningpredictor.tex
Updates from ShareLaTeX

@@
 
- \wei{remove those two figures here! need to complete here}show  tunings learned by DE. 
-The left hand side columns shows some standard default values. Note that:
+ In \fig{features}, we show how tuning selects the optimal values for parameters.
+For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our supporting documents\footnote{\url{https://goo.gl/aHQKtU}}.
+The default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$. Note that:
 \bi
@@
 \item The tunings learned by DE were different in different data sets and for different goals.
+\ei
 Hence, we answer RQ6 as ``no'' since, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
-sets are changed.
-\ei
-Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
+sets are changed.Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
 tuning is so easy and so fast (at least for defect predictors from static code attributes).
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=1.5in]{features_precision.eps}\includegraphics[width=1.5in]{features_F.eps}
+ \end{center}
+\caption{Four representative tuning values in WHERE with  precision and F as tuning goal,respectively. }\label{fig:features}
+ \end{figure}
 

### 2015-08-08 tuningpredictor.tex

@@
  \end{center}
-\caption{Four representative tuning values in WHERE with  precision and F as tuning goal,respectively. }\label{fig:features}
+\caption{Four representative tuning values in WHERE with  precision and F as the tuning goal, respectively.
+The default values for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$.
+}\label{fig:features}
  \end{figure}
@@
 Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
-\wei{remove those two figures here, need to compelete sentence with new ones} show just how much tuning can alter default settings
+\fig{features} shows just how much tuning can alter default settings
 both for different data sets and for different goals.

### 2015-08-09 tuningpredictor.tex
Updates from ShareLaTeX

@@
 
+% \begin{figure}[!t]
+% \begin{center}
+% \includegraphics[width=1.5in]{svm_rbf.eps}\includegraphics[width=1.5in]{svm_sigmoid.eps}
+%  \end{center}
+% \caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
+%  \end{figure}
+
 \begin{table}[!t]
@@
 \begin{figure}[!b]
-\includegraphics[width=3.5in,left]{np_10_90.eps}
-\caption{Deltas in terms of F when using 10 and 90 as the population in DE. np=90 is better when the deltas are above zero.}\label{fig:deltas_np}
+\begin{center}
+\includegraphics[width=1.5in]{np_10_90_precision.eps}\includegraphics[width=1.5in]{np_10_90_f.eps}
+ \end{center}
+\caption{Deltas in terms of precision and F when using 10 and 90 as the population in DE. np=90 is better when the deltas are above zero.}\label{fig:deltas_np}
  \end{figure}
@@
 
-\wei{added!} To justify that {\em np=10} is enough, we did another tuning study, 
-where all the settings are the same as before but we chose {\em np=90} as recommended by Storn. 
-The tuning performance of learners is evaluated
-by F.
+\wei{added!I will run np=90,50,60 for WHERE, CART and RF,respectively} To justify that {\em np=10} is enough, we did another tuning study, 
+where all the settings are the same as before but we chose {\em np=90} as recommended for tuning WHEREby Storn. 
+To make the study simple, we also set {\em np=90} for CART. The tuning performance of learners is evaluated
+by precision and F.
 To compare the results of {\em np=10} and {\em np=90}, we plot the delta in the performance as \fig{deltas}.
-In \fig{deltas_np}, 5 data sets are better but 4 data sets are worse when {\em np = 90} for WHERE.
+As shown in \fig{deltas_np}, WHERE,CART has been improved in 7 datasets and deteriorated in 2.
+5 data sets are better but 4 data sets are worse when {\em np = 90} for WHERE.
 For CART and Random Forest, the numbers of better and worse data sets are both 4.

### 2015-08-12 tuningpredictor.tex
Updates from ShareLaTeX

--- 2015-08-08 tuningpredictor.tex
@@
 
-\wei{added HERE!} As shown in \tab{parameters}, default parameters for the Where-based learner are set using authors' engineering judgment and default parameters for CART and Random Forests are set by SciKitLearn.
-Those default parameters might not be the standard parameters for practical defect learners in reality, but it's a rule of thumb that most researchers would use just use the default parameters in the software without changes\cite{me07b} (\wei{MORE references should be cited here to support this statement}.
-)The tuning range is set according to the corresponding default parameters.
-The reason for this is to tell whether tuning with a small range can get a performance improvement (\Menzies{is this correct?})
+As shown in \tab{parameters}, default parameters for the Where-based learner are set using authors' engineering judgment and default parameters for CART and Random Forests are set by SciKitLearn.
+Those default parameters might not be the standard parameters for practical defect learners in reality, but it's a rule of thumb that most researchers would use just use the default parameters in the software without any tuning\cite{me07b,moser2008comparative,herzig2013predicting,zimmermann2007predicting}.
+The tuning range is set according to the corresponding default parameters.
+The reason for this is to justify whether tuning with a small range can get a performance improvement (\Menzies{is this correct?})
 
@@
 
-\subsection{RQ2:  Does Tuning Change a Learner's Ranking Regarding Different Goals?}\label{sect:rank}
+\subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
 Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}.
@@
 In practice, this means that tuning needs to be repeated for each new context.
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
+ \end{center}
+\caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
+ \end{figure}
+
+% \begin{figure}[!t]
+% \begin{center}
+% \includegraphics[width=1.5in]{svm_rbf.eps}\includegraphics[width=1.5in]{svm_sigmoid.eps}
+%  \end{center}
+% \caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
+%  \end{figure}
 
@@
 \begin{figure}[!b]
-\includegraphics[width=3.5in,left]{np_10_90.eps}
-\caption{Deltas in terms of F when using 10 and 90 as the population in DE. np=90 is better when the deltas are above zero.}\label{fig:deltas_np}
+\begin{center}
+\includegraphics[width=1.5in]{np_precision.eps}\includegraphics[width=1.5in]{np_f.eps}
+ \end{center}
+\caption{Deltas in performance between {\em np = 10} and the recommended np's.
+The recommended np is better when deltas are above zero.
+{\em np = 90, 50 and 60} are recommended population size for WHERE, CART and Random Forest by Storn.}\label{fig:deltas_np}
  \end{figure}
@@
 
-\wei{added!} To justify that {\em np=10} is enough, we did another tuning study, 
-where all the settings are the same as before but we chose {\em np=90} as recommended by Storn. 
-The tuning performance of learners is evaluated
-by F.
-To compare the results of {\em np=10} and {\em np=90}, we plot the delta in the performance as \fig{deltas}.
-In \fig{deltas_np}, 5 data sets are better but 4 data sets are worse when {\em np = 90} for WHERE.
-For CART and Random Forest, the numbers of better and worse data sets are both 4.
-The improvement for those better data sets is negligible to some extent but the deterioration is not.
-From this study, {\em np = 90}, which is recommended for WHERE and more than the number for CART and Random Forest, does not bring any significant improvement over {\em np=10}.
-Therefore, the searching space is very simple for tuning defect predictor, which makes tuning very simple.
+To justify that {\em np=10} is enough, we did another tuning study, 
+where all the settings were the same as before but we set{\em np= 90, 50} and {\em np = 60} for WHERE, CART and Random Forests as recommended by Storn. The tuning performance of learners was evaluated
+by precision and F.
+To compare performance of each learner with different np's, we plot the delta in the performance as \fig{deltas}.
+As shown in \fig{deltas_np}, in terms of precision, the recommended {\em np} will improve the performance of WHERE, CART and Random Forests in 2, 5, and 4 data sets.
+However, in 6, 4, and 4 data sets, those numbers  will degrade the performance compared with {\em np = 10}.
+For F as the tuning goal, we can observe the similar pattern.
+
+ From this study, with the same experimental condition, the recommended {\em np's} for WHERE, CART and Random Forest, do not bring any significant improvements over {\em np = 10}.
+We're not arguing that {\em np = 10} is the optimal settings for tuning defect predictors.
+But it suffices to make tuning easy and generate a competitive performance.
 

### 2015-08-12 tuningpredictor.tex

@@
 
-\subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
+\subsection{RQ2:  Does Tuning Change a Learner's Ranking Regarding Different Goals?}\label{sect:rank}
 Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}.
@@
 In practice, this means that tuning needs to be repeated for each new context.
-
-\begin{figure}[!t]
-\begin{center}
-\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
- \end{center}
-\caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
- \end{figure}
 
@@
 As shown in \fig{deltas_np}, in terms of precision, the recommended {\em np} will improve the performance of WHERE, CART and Random Forests in 2, 5, and 4 data sets.
-However, in 6, 4, and 4 data sets, those numbers  will degrade the performance compared with {\em np = 10}.
+However, in 6, 4, and 4 data sets, those numbers  will deteriorate the performance compared with {\em np = 10}.
 For F as the tuning goal, we can observe the similar pattern.

### 2015-08-12 tuningpredictor.tex
add a figure about Logistic Regression to refute that systematic literature review paper.

--- 2015-08-12 tuningpredictor.tex
@@
 In this paper, what we can  show are examples of how  changing  optimization goals can also change 
-the conclusions made from that learner on that data. Accordingly, we warn that it is important not to overstate  empirical results from software analytics.
+the conclusions made from that learner on that data. Accordingly, we warn that it is 
+important not to overstate  empirical results from software analytics.
 Rather, those results need to be expressed {\em along with} the context within which they are
@@
 \subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
-Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}.
-In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets.
-In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking.
-Such conclusions are not reliable since they can change when we elect to tune for different goals.
+Researchers often use performance criteria to assert that one learner is better than 
+another~\cite{lessmann2008benchmarking,me07b,hall2012systematic}. In\cite{me07b},
+naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets.
+In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically 
+better than CART in terms of the AUC ranking. In the systematic literature review 
+\cite{hall2012systematic}, authors claimed that defect predictors based on simple 
+modeling techniques such as Logistic Regress perform well. Such conclusions are 
+not stable across tuning process.
 
 22 learners are compared over NASA MDP data sets in terms of the AUC in \cite{lessmann2008benchmarking}.
-Some learners are tuned using manual methods, like C4.5, CART and Random Forests and some are tuned by searching algorithms, like grid search for SVM-Type learners.
-In our expeirment, when we tune CART and Random Forests for precisoin and F-measure, the rankings of these two learners are changed.
-
-In \tab{precisionbars} and \tab{fbars}, the tuned CART are better than or equal to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
-terms of precision and F-measure, respectively. Results from the non-parametric Kolmogorov-Smirnov Test turn out that the performance 
-scores of tuned CART and tuned Random Forests are not statistically different. This is the opposite of   
- Lessmann et al.~\cite{lessmann2008benchmarking}, the tuned Random Forest is not significantly better than tuned CART.
+Some learners are tuned using manual methods, like C4.5, CART and Random Forests 
+and some are tuned by searching algorithms, like grid search for SVM-Type learners. 
+In our expeirment, when we tune CART and Random Forests for precisoin and F-measure, 
+the rankings of these two learners are changed.
+
+In \tab{precisionbars} and \tab{fbars}, the tuned CART are better than or equal
+to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
+terms of precision and F-measure, respectively. Results from the non-parametric
+Kolmogorov-Smirnov Test turn out that the performance 
+scores of tuned CART and tuned Random Forests are not statistically different.
+This is the opposite of Lessmann et al.~\cite{lessmann2008benchmarking}, 
+the tuned Random Forest is not significantly better than tuned CART.
+
+\wei{added here!} In \fig{lr}, Logistic Regression performs better than untuned CART and Random
+Forests over 17 data sets in terms of precision, which conforms with the statement
+in \cite{hall2012systematic}: simple modeling techniques just perform well.
+However, if we tuned CART and Random Forests, both of their performance was improved greatly. In some
+data sets, CART and Random Forests are much better than Logistic Regression.
+
 In another result that is the reverse of \tab{precisionbars}, tuned WHERE is not necessarily
@@
 
- Therefore, it's not always safe to say ``LearnerX'' is the best or better than ``learnerY'' without pointing out the performance criteria or applying tuning techniques.
-That is, the answer to RQ2 is ``yes'' since tuning a set of learners
+ Therefore, it's not always safe to say ``LearnerX'' is the best or better than ``learnerY'' 
+ without applying tuning techniques. That is, the answer to RQ2 is ``yes'' since tuning a set of learners
  changes the rankings of those learners regarding different criteria.
@@
  \end{center}
-\caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
+\caption{Comparison between Logistic Regression and CART as well as Random Forests before and after tuning. }\label{fig:lr}
  \end{figure}
@@
  In \fig{features}, we show how tuning selects the optimal values for parameters.
-For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our supporting documents\footnote{\url{https://goo.gl/aHQKtU}}.
-The default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$. Note that:
+For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our online support documents\footnote{\url{https://goo.gl/aHQKtU}}.
+The default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$ as indicated in \tab{parameters}.  Note that:
 \bi

### 2015-08-18 dm101.tex
typo

@@
 in the confidence $C$ of finding  defects
-can take {\em exponentially} more effort)\footnote{A randomly selected 
+can take {\em exponentially} more effort\footnote{A randomly selected 
 input to a program will find a fault with probability $p$.
@@
 But 
-Any method that focuses on parts of the code
+any method that focuses on parts of the code
 can blind us to defects in other areas. Some  {\em
@@
 sampling policy will always be incomplete.
-Nevertheless, it is the recommended option when
-resources do not permit a complete assessment of the whole system.
+Nevertheless, it is the only option when
+resources prevent a complete assessment of everything.
 
 One such lightweight sampling policy is defect predictors learned from static code attributes.
-Given software described in (e.g.) the attributes of \fig{ck},   data miners can
+Given software described in (e.g.) the attributes of \tab{ck},   data miners can
 learn where the probability of software defects is highest.
-This approach is   {\em easy to
+
+The rest of this section argues that such defect predictors are   {\em easy to
 use}, {\em widely-used}, and {\em useful} to use.
@@
 
-%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
-\renewcommand\arraystretch{1.2}
-\begin{figure*}[t!]
-\scriptsize
-  \centering
-	\begin{tabular}{|c|c|c|c|l|}
-	\cline{1-5}
-	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
-\multicolumn{1}{c|}{Description} \\ \hline
-	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
-	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
-	& infoPrune & 0.33 &[0.01,1]& The percentage of features to consider for the best 
-split to build its final decision tree. \\ \cline{2-5} 
-	 & min\_sample\_split & 4& [1,10]& The minimum number of samples required to split an internal node of
-its final  decision tree. \\ \cline{2-5} 
-	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_samples\_leaf 
-in the initial clustering tree  using  ${n\_samples}^ {min\_Size}$.
-\end{tabular} \\ \cline{2-5} 
-    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  the initial clustering tree to be pruned\\ \cline{2-5}
-	 & depthMin & 2 & [1,6]&The minimum depth of the initial clustering tree below which no pruning for the
-clustering tree. \\ \cline{2-5} 
-	 & depthMax & 10 &[1,20]& The maximum depth of the initial clustering tree. \\ \cline{2-5} 
-	 & wherePrune & False &T/F& Whether or not to prune the initial clustering tree. \\ \cline{2-5}
-	 & treePrune & True &T/F& Whether or not to prune the final decision tree. \\ \cline{2-5} 
-\hline
-\multirow{5}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
-	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5}
-
-	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_samples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{2-5} 
-     & max\_depth & None & [1, 50]& The maximum depth of the tree. \\
-     \cline{1-5}  
-       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
-\cline{2-5} 
-	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
-split. \\ \cline{2-5} 
-	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
-	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
-internal node. \\ \cline{2-5} 
-	 & min\_samples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
-node. \\ \cline{2-5} 
-	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
-	 \hline
-
-	\end{tabular}
-    \caption {List of parameters to be tuned.}
-\label{fig:parameters}
-\end{figure*}
-{\em Widely used:} Many researchers and industrial practitioners  use static attributes to guide software 
+{\em Widely used:}  Researchers and industrial practitioners  use static attributes to guide software 
 quality predictions.
  Defect prediction models have been reported
-to have been used at Google~\cite{lewis13}.
+  at Google~\cite{lewis13}.
 Verification and validation (V\&V) textbooks
 (\cite{rakitin01}) advise using static code complexity attributes
-to decide which modules are worthy of manual inspections.
+to decide which modules are worth manual inspections.
 
@@
 
-Note only do static code defect predictors perform well compared to manual methods,
+Not only do static code defect predictors perform well compared to manual methods,
 they also are competitive with certain automatic methods.
@@
 static code defect prediction can be quickly adapted to new languages by building lightweight
-parsers that find   information like \fig{ck}. The same is not true for   static code analyzers-- these need  extensive modification before they can be used on new
+parsers that find   information like \tab{ck}. The same is not true for   static code analyzers-- these need  extensive modification before they can be used on new
 languages.

### 2015-08-18 tuningpredictor.tex
typo

--- 2015-08-12 tuningpredictor.tex
@@
 % \conferenceinfo{FSE}{'15 Bergamo, Italy}
-\title{ Analytics Without  Tuning Considered Harmful?}
+\title{ Tuning for Software Analytics: is it Really Necessary?}
 % \numberofauthors{1}
@@
 automatic, and very effective  method for finding those tunings.
-For the purposes of learning
+
+Contrary to our prior expectations, finding these tunings
+ was remarkably simple: it only required tens, not thousands, of attempts
+ to obtain very good results.
+For example, when  learning
 software defect predictors this  method can quickly
-find  good tunings that  dramatically change   the performance of a learner.
-For example,
-in this paper we show   tunings that  alter detection  precision  
+found tunings  that  alter detection  precision  
  from 2\% to 98\%.
 
-These results prompt for a change to standard methods in software analytics.
+Given that (1)~the improvements are so large, and (2)~the tuning is so simple,
+these results prompt for a change to standard methods in software analytics.
 At least for defect prediction, 
@@
 
-In the $21^{st}$ century, it is now impossible
-to manually browse all the available software project
+In the $21^{st}$ century, it is  impossible
+to manually browse all  available software project
 data. The PROMISE repository of SE data has grown to 200+ projects~\cite{promise15}
@@
 that are readily available to researchers~\cite{rod12}.
-For example, at the time of this writing (May  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
-
-Faced with this information overload,
+For example, at the time of this writing (Aug  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
+
+Faced with this data overload,
 researchers in empirical SE
@@
 
-The results of this paper show that neither of these points is supportable, at least when learning
-defect detectors from static code attributes since:
+The results of this paper show that the above points are
+false,  at least for
+defect prediction from  code attributes:
 \be
@@
 \item RQ1: {\em Does   tuning    improve the performance scores of a predictor?} We will show below
- examples of truly dramatic improvement;
-e.g.  precision changes from 2\% to 98\%.
+ examples of truly dramatic improvement:
+ usually by 5 to 20\% and often by much more (in one extreme case, precision improved from 2\% to 98\%);
 \item RQ2: {\em Does tuning change conclusions on what learners are better than others?} 
-Numerous recent SE papers (e.g. \cite{lessmann2008benchmarking,hall11,me07b}) claim that some learners are better than others. We show that at least
-some of those conclusions are completely changed by tuning.
+Recent SE papers~\cite{lessmann2008benchmarking,hall11} claim that some learners are better than others. 
+Some of those conclusions are completely changed by tuning. 
 \item RQ3: {\em Does tuning change conclusions about what factors are most important in software engineering?} Numerous recent SE papers (e.g.
-~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,%
+~\cite{bell2013limited,rahman2013how,me02k,Moser:2008,zimmermann2007predicting,%
 herzig2013predicting}) use data miners to conclude that {\em this}
-is more important than {\em that} for (e.g.) reducing software project defects.
+is more important than {\em that} for reducing software project defects.
 Given the  tuning results of this paper, we show that such conclusions need to be revisited.
@@
 (differential evolution~\cite{storn1997differential}) works very well for tuning defect predictors. 
-\item RQ5: {\em Is tuning impractically slow?}. We achieved dramatic improvements in the performance scores
-of our data miners in less than 100 evaluations (!!); i.e., very
+\item RQ5: {\em Is tuning impractically slow?} We achieved dramatic improvements in the performance scores
+of our data miners in less than 100 evaluations (!); i.e., very
 quickly.
 \item RQ6: {\em Should data miners be used ``off-the-shelf'' with their default tunings?} 
-At least for defect prediction from static code measures, our answer is an emphatic ``no'' (and
-the implication for other kinds of software analytics is now an open and urgent question).
+For defect prediction from static code measures, our answer is an emphatic ``no'' (and
+the implication for other kinds of  analytics is now an open and urgent question).
 \ei
-Before beginning, we digress for one  clarification.
-This paper is {\em not} arguing that
-software analytics is somehow wrong-headed or misguided.
-In the age of the Internet and global access to software engineering data,
-there exists the  problem of information overload. {\em Something} must be done to
-allow analysts to make conclusions via an automatic analysis over a lot of data.
-The results of this paper is that for a particular local context
-(a specific data set and a specific goal) there exists  
-methods for optimizing the conclusions reached in that context.  
-Those conclusions
-may not generalize to other contexts but this  is not a council for despair. 
-As shown here, 
-there  exists general methods for finding
-local conclusions in a particular context. Further,
-those
-methods are  very simple to implement and very fast to execute.
-
-\section{But is This a New Result?}
-
-In  other fields, the impact of tuning is well understood. However, as we argue
-in this section, this result is not properly  acknowledged  in the field of software analytics.
+%Before beginning, we digress for one  clarification.
+%This paper is {\em not} arguing that
+%software analytics is somehow wrong-headed or misguided.
+%In the age of the Internet and global access to software engineering data,
+%there exists the  problem of information overload. {\em Something} must be %done to
+%allow analysts to make conclusions via an automatic analysis over a lot of %data.
+%The results of this paper is that for a particular local context
+%(a specific data set and a specific goal) there exists  
+%methods for optimizing the conclusions reached in that context.  
+%Those conclusions
+%may not generalize to other contexts but this  is not a council for despair. 
+%As shown here, 
+%there  exists general methods for finding
+%local conclusions in a particular context. Further,
+%those
+%methods are  very simple to implement and very fast to execute.
+
+\section{Background}
+
+\subsection{Issues of Tuning: Important and Ignored?}
+In  other fields, the impact of tuning is well understood~\cite{Bergstra2012}. 
+Yet, as argued in this section, issues of tuning  are rarely or poorly addressed
+in the defect prediction literature.
 
@@
 allow automatic algorithms to ignore most of those possibilities. 
-
-While that heuristic search makes data mining possible, it also means that tunings
+While  heuristic search makes data mining possible, it also means that tunings
 can significantly affect what comes out of a data miner.
 When we tune a data miner, what we are really doing is changing how a learner applies
-its heuristics. This means tuned data miners use different heuristics, which means they ignore different possible models, which means they return different models.
-
-The fact that {\em how} we learn changes {\em what} we learn is not acknowledged
-in the field of software analytics.
-There exists many research papers
-that use data miners to   show that certain factors
-are more influential than others for (say)
-predicting defects. As shown below, such conclusions can be dramatically
-changed by the tuning process since those  ``influential'' factors are very different pre- and post- tuning. Also, those factors tend to  change from project to project or if the goal
-of the tuning is altered.
-Hence, many old papers    need to be revisited  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
-For example, one of us (Menzies) used data miners
-to assert that some factors were more important than others for predicting
-successful software reuse~\cite{me02k}. That assertion should now be doubted since Menzies did not conduct a tuning study before reporting what factors the data miners
-found were most influential.
-
-Further, several  prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
-that learnerX is better than learnerY for some software analytics task.
-For example, a recent IEEE TSE article claimed that the 
-CART decision tree learner was far worse than Random Forests for
-software defect prediction~\cite{lessmann2008benchmarking}. 
-Such conclusions do not survive tuning.
-For example,
-after tuning, the worst learner (CART) can perform just as well as the supposedly
-best learner (Random Forest). Hence, all those prior results that ranked learners for software
-analytics now need to be revisited (and perhaps revised).
-
-Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
-we have defended that approach, arguing that it
-encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
-can no longer be condoned. For example, suppose our default
-number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation).
-After tuning, we see that our optimizer often uses $F$ values that are nowhere near that default:
+its heuristics.
+This means tuned data miners use different heuristics, which means they ignore different possible models, which means they return different models; i.e.
+{\em how} we learn changes {\em what} we learn.
+
+Are the impacts of tuning addressed in the defect prediction literature?
+To answer that question,  in August 2015 we searched scholar.google.com for the conjunction of  "data mining" and "software engineering" and  "defect prediction".
+After sorting by the citation count and discarding the non-SE papers (and those without a pdf link), we read over this sample
+of  50 highly-cited SE defect prediction papers. 
+What we found in that sample was that few authors
+acknowledged the impact of tunings (exceptions: ~\cite{hall11,lessmann2008benchmarking}).
+Overall,  80\% of papers in our sample {\em did not} adjust
+the ``off-the-shelf'' configuration of the data miner (e.g. ~\cite{me07b,Moser:2008,herzig2013predicting,zimmermann2007predicting}). Of the remaining papers:
+\bi
+\item
+Some papers in our sample  explored   data super-sampling~\cite{4271036} or data sub-sampling techniques via  automatic methods (e.g. ~\cite{Gao:2011,me07b,4271036,Kim:2011}) 
+or via some domain principle (e.g. ~\cite{Moser:2008,Nagappan:2008,Hassan:2009}).
+As an example of the latter, Nagappan et al.~\cite{Nagappan:2008} checked if metrics related to organizational structure were relatively more powerful for predicting software defects. 
+However, it should be notes that  these studies varied the input data but
+not the   ``off-the-shelf''   settings of the data miner.
+\item
+A few other papers did acknowledge that one data miner may not be appropriate
+for all data sets.  Those papers tested  different  
+``off-the-shelf'' data miners on the same data set.
+For example, Elish et al.\cite{Elish2008649}  compared support vector
+machines to other data miners for the purposes of defect prediction. SVM's execute via a ``kernel function'' which should be specially selected for different data sets and
+the Elish et al. paper  makes no mention of any SVM tuning study.  
+To be fair to Elish et al., we hasten to add that we
+ourselves have  published
+papers using ``off-the-shelf'' tunings~\cite{me07b} since,
+prior to this paper it was unclear to us how to effectively
+navigate the large space of possible tunings.
+\ei
+Over our entire sample, there was only  one paper that conducted a somewhat extensive tuning study.
+Lessmann et al. tuned parameters for some of their algorithms using  a {\em grid search}; i.e. divide all $C$ configuration
+options into $N$ values, then try all   $N^C$ combinations.
+This is a slow approach-- we have explored grid search for 
+defect prediction and found it takes days to terminate~\cite{me07b}.
+Not only that, we found that grid search can miss
+important optimizations~\cite{baker07}.
+Every grid has ``gaps'' between each grid division which means
+that a supposedly rigorous grid search can still miss
+important configurations~\cite{Bergstra2012}. 
+Bergstra and Bengio~\cite{Bergstra2012} comment for most data sets only a few of the tuning parameters really matter-- which means that
+much of the runtimes associated with grid search is actually wasted.
+Worse still, Bergstra and Bengio  comment that 
+the 
+important tunings are   different   for different
+data sets-- a 
+ phenomenon makes grid search a poor choice for configuring data mining
+ algorithms for new data sets.
+
+%We found only one paper in our sample from scholar.google.com 
+%%that explored anything like the range of configuation values
+%that we explore in this paper. Lessmann et %al.~\cite{lessmann2008benchmarking
+%}
+%explreod 22 learners
+%Worse, in the rare paper
+%that explores those options, it does so using a method that
+%is known to perform poorly (the {\em grid search} method, discussed %below~\cite{Bergstra2012}).
+
+%%Further, several  prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
+%that learnerX is better than learnerY for some software analytics task.
+%For example, a recent IEEE TSE article claimed that the 
+%CART decision tree learner was far worse than Random Forests for
+%software defect prediction~\cite{lessmann2008benchmarking}. 
+%Such conclusions do not survive tuning.
+%For example,
+%after tuning, the worst learner (CART) can perform just as well as the supposedly
+%best learner (Random Forest). Hence, all those prior results that ranked learners for software
+%analytics now need to be revisited (and perhaps revised).
+
+%Returning now to the issue
+%of using  ``off-the-shelf'' tunings  for data mining tools: previously
+%we have defended that approach, arguing that it
+%encourages reproducibility~\cite{me15:book1}. Based on the results
+%of this paper, it must be said that that ``off-the-shelf''  policy
+%can no longer be condoned. For example, suppose our default
+%number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation).
+%After tuning, we see that our optimizer often uses $F$ values that are nowhere near that default:
 
@@
 % \]}
-
-{\scriptsize
-\[F \in \left\{\begin{array}{l} 50, 58, 59, 63, 63, 66, 67, 73, 74, 74, \\
-                                75, 77, 80, 82, 85, 96, 96, 97, 97, 101, \\
-                                103, 107, 111, 111, 112, 120, 125, 125,  \\
-                                130,130, 138, 144, 149, 150   \end{array}\right\}
-\]}
 
@@
 
-The  good news of this paper  is that {\em tuning is very easy}.
+Since the Lessmann et al. paper, much progress has been made in 
+configuration algorithms
+and we can now report that  {\em finding useful tunings is very easy}.
 This result is both novel and unexpected.
-A standard run of such evolutionary optimizers requires   thousands,
-if not millions, of evaluations. However, in a result that we found startling, that  differential evolution can find useful settings for learners generating defect predictors
+A standard run of grid search (and other  evolutionary algorithms)
+is  that optimization requires   thousands,
+if not millions, of evaluations.  However, in a result that we found startling, that  {\em differential evolution} (described below) can find useful settings for learners generating defect predictors
 in less than 100 evaluations (i.e. very quickly).
@@
 
-That said, the bad news is that, for defect
-prediction, tuning dramatically changes
-  what is learned from that data. Therefore, it is now an open and pressing research issue to check if
-analytics without parameter tuning is considered {\em harmful} or, at the 
-very least, {\em misleading}.
-Clearly, we  must now revisit all prior results   based on
-``off-the-shelf'' tunings.
-Further,
-it is no longer enough to just run a data miner and report the result
-{\em without} first conducting a tuning optimization study.
+%That said, the bad news is that, for defect
+%prediction, tuning dramatically changes
+%  what is learned from that data. Therefore, it is now an open and %pressing research issue to check if
+%analytics without parameter tuning is considered {\em harmful} or, at %the 
+%very least, {\em misleading}.
+%Clearly, we  must now revisit all prior results   based on
+%``off-the-shelf'' tunings.
+%Further,
+%it is no longer enough to just run a data miner and report the result
+%{\em without} first conducting a tuning optimization study.
 
@@
 
-\section{Background Notes}
-
 \subsection{Defect Prediction}
@@
 such as  CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
-and WHERE~\cite{menzies2013local}.
-For this study, we use the CART and Random Forest  from 
+ WHERE~\cite{menzies2013local} and LR (logistic regression).
+For this study, we use WHERE-based learner, CART, Random Forest and LR versions  from 
 SciKitLearn~\cite{scikit-learn} (and
@@
  We use  these algorithms, for the following reasons.
+
 CART and Random Forest were mentioned in
-a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 21  
+a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 22  
 learners for  defect prediction.
@@
  Random Forest.
-This
- paper also presents results with WHERE-based learner since, as shown below,
+
+LR was  mentioned by Hall et al.~\cite{hall11}
+as usually being as good or better as more complex learners (e.g.
+Random Forests). In a finding that endorses the Hall et al. result,
+we show that untuned LR performs better than 
+untuned Random Forests (at least, for the data sets studied here). However,
+we will show that tuning raises doubts about the optimality of the
+Hall et al. recommendation.
+
+Finally,  this
+ paper uses WHERE since, as shown below,
 it offers an interesting case study on the benefits of tuning.
 
+%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
+\renewcommand\arraystretch{1.2}
+\begin{table*}[t!]
+\scriptsize
+  \centering
+	\begin{tabular}{|c|c|c|c|l|}
+	\cline{1-5}
+	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
+\multicolumn{1}{c|}{Description} \\ \hline
+	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
+	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
+	& infoPrune & 0.33 &[0.01,1]& The percentage of features to consider for the best 
+split to build its final decision tree. \\ \cline{2-5} 
+	 & min\_sample\_split & 4& [1,10]& The minimum number of samples required to split an internal node of
+its final  decision tree. \\ \cline{2-5} 
+	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_samples\_leaf 
+in the initial clustering tree  using  ${n\_samples}^ {min\_Size}$.
+\end{tabular} \\ \cline{2-5} 
+    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  the initial clustering tree to be pruned\\ \cline{2-5}
+	 & depthMin & 2 & [1,6]&The minimum depth of the initial clustering tree below which no pruning for the
+clustering tree. \\ \cline{2-5} 
+	 & depthMax & 10 &[1,20]& The maximum depth of the initial clustering tree. \\ \cline{2-5} 
+	 & wherePrune & False &T/F& Whether or not to prune the initial clustering tree. \\ \cline{2-5}
+	 & treePrune & True &T/F& Whether or not to prune the final decision tree. \\ \cline{2-5} 
+\hline
+\multirow{5}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5}
+
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_samples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{2-5} 
+     & max\_depth & None & [1, 50]& The maximum depth of the tree. \\
+     \cline{1-5}  
+       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
+\cline{2-5} 
+	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
+split. \\ \cline{2-5} 
+	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
+	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
+internal node. \\ \cline{2-5} 
+	 & min\_samples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
+node. \\ \cline{2-5} 
+	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
+	 \hline 
+Logistic 	 Regression&\multicolumn{4}{l|}{This study uses untuned LR in order to check
+a conclusion of~\cite{hall11}. }\\\hline
+
+	\end{tabular}
+    \caption {List of parameters tuned by this paper.}
+\label{tab:parameters}
+\end{table*}
+
 \subsection{Learners and Their Tunings}
@@
 Our learners use the tuning parameters of \tab{parameters}. This section describes those parameters.
-
-As shown in \tab{parameters}, default parameters for the Where-based learner are set using authors' engineering judgment and default parameters for CART and Random Forests are set by SciKitLearn.
-Those default parameters might not be the standard parameters for practical defect learners in reality, but it's a rule of thumb that most researchers would use just use the default parameters in the software without any tuning\cite{me07b,moser2008comparative,herzig2013predicting,zimmermann2007predicting}.
-The tuning range is set according to the corresponding default parameters.
-The reason for this is to justify whether tuning with a small range can get a performance improvement (\Menzies{is this correct?})
+The default parameters for CART and Random Forests are set by 
+the SciKitLearn authors and the
+default parameters for WHERE-based learner are set via our own expert judgement.
+When we say a learner is used ``off-the-shelf'', we mean
+that they use the defaults shown in \tab{parameters}.
+
+As to the value of those defaults, it could be argued that these defaults are 
+not the best  parameters needed for practical defect prediction.
+That said,  prior to this paper, two things were true:
+\bi
+\item 
+Many data scientists in SE use the standard defaults
+in their data miners, 
+without   tuning (e.g.~\cite{me07b,Moser:2008,herzig2013predicting,zimmermann2007predicting}).
+\item
+The effort involved to adjust those tunings seemed so onerous, that
+many researchers in this field were content to take our prior advice
+of ``do not tune... it is just too hard''~\cite{me15:book1}.
+\ei
+As to the details of these learners, LR is a parametric
+modeling approach. Given $f = \beta_0 + \sum_i\beta_ix_i$,
+where $x_i$ is some measurement in a data set, and $\beta_i$
+is learned via regression, LR
+converts that into a function $0 \le g \le 1$
+using $g=1/\left(1+e^{- f}\right)$. This function reports how much
+we believe in a particular class.
 
@@
  \item
-WHERE's initial clustering
+WHERE's  
 tree generation will always split up to {\em depthMin} number of branches.
@@
 
- \subsubsection{Parametric Tuning Algorithms}
-The  goal of this paper is to adjust the tuning parameters of \tab{parameters}
-in order to   optimize (improve) some particular performance scores
-generated by a particular learner being applied to  a particular data set.
-For this task, we do not use traditional parametric numeric optimizer  
-such as  gradient descent optimizers~\cite{saltelli00} that require models comprised of
-differential functions (i.e. functions of real-valued variables whose derivative exists at each point in its domain).
-This is impractical  for  our learners since their internal states are   not a smoothly differential continuous function.
-Rather, learners being tuned  contain many regions with many different properties (tuning options can
-drive the learner into very different modes with very different performance properties).
-
- \subsubsection{Non-Parametric Tuning Algorithms}
-
-Non-parametric  optimizers   make no assumption
-about the internal structure of the model.
-There are many such optimizers:
-\bi
-\item
-Simulated annealing~\cite{fea02a,me07f};
-\item
-A wide range of genetic algorithms~\cite{goldberg79} augmented by
-techniques such as differential evolution~\cite{storn1997differential}, tabu search and scatter search~\cite{Glover1986563,Beausoleil2006426,Molina05sspmo:a,4455350};
-\item
-Particle swarm optimization~\cite{pan08}; 
-\item 
-Numerous ``decomposition approaches'' that uses
-    heuristics to decompose the total space into   small problems,   then applies a
-    simpler optimizer to each region including \mbox{$\varepsilon$-domination}~\cite{deb05} and MOEA/D ~\cite{zhang07};
-    \item 
-    Response surface methods~\cite{krall15,Zuluaga:13};
-    \item
-    And many others as well.
-    \ei
-From all the above methods, how do we select which optimizers to apply to tuning data miners?
+How should researchers select which optimizers to apply to tuning data miners?
 Cohen~\cite{cohen95} advises comparing new 
  methods against the simplest possible alternative. 
-Holte~\cite{holte93} recommends using very simple  learners
+Similarly, Holte~\cite{holte93} recommends using very simple  learners
  as a
@@
 complex analysis).
-
-To find our ``scout'',  we used engineering judgement to sort  the above algorithms from simplest to most complex.
-Of the optimizers listed above, the simplest are simulated annealing (SA)  and 
+Accordingly,
+to find our ``scout'',  we used engineering judgement to sort  candidate algorithms from simplest to  complex. For
+example, here is a list of optimizers used widely in research:
+{\em 
+simulated annealing}~\cite{fea02a,me07f};
+ various {\em genetic algorithms}~\cite{goldberg79} augmented by
+techniques such as {\em differential evolution}~\cite{storn1997differential}, 
+{\em tabu search} and {\em scatter search}~\cite{Glover1986563,Beausoleil2006426,Molina05sspmo:a,4455350};
+{\em particle swarm optimization}~\cite{pan08}; 
+numerous {\em decomposition} approaches that use
+    heuristics to decompose the total space into   small problems,   then apply a
+    {\em response surface methods}~\cite{krall15,Zuluaga:13}.
+Of these,  the simplest are simulated annealing (SA)  and 
 differential evolution (DE), each of which can be coded in less than a page of some high-level scripting language. Our reading of the current literature is that there are more  advocates for
 differential evolution than
-  SA:
-  \bi
-  \item
-  When the MOEA/D community requires a secondary optimizer, they often use  differential evolution~\cite{zhang07,5583335}.
-  \item
- Vesterstrom and Thomsen~\cite{Vesterstrom04} found DE to be competitive with 
+  SA. For example,  Vesterstrom and Thomsen~\cite{Vesterstrom04} found DE to be competitive with 
    particle swarm optimization and other GAs.
-   \ei
+
 DEs have been applied before for   parameter tuning (e.g. see~\cite{omran2005differential, chiha2012tuning}) but this is the first time they have been applied to
@@
    See \tion{dataa} for explanation of {\em training, tuning, testing} sets.
-   }\label{fig:data1}
+   }\label{tab:data1}
 \end{table*}
 
-DE is an evolutionary algorithm where the next {\em NewGeneration} is learnt from
+DE evolves a {\em NewGeneration} of candidates  from
 a current {\em Population}.  Our DE's lose one ``life''
-when e new is no better than  current (terminating when ``life'' is zero)$^{5}$.
+when e new is no better than  current (terminating when ``life'' is zero)$^{4}$.
 Each candidate solution in the {\em Population}  
@@
 \tab{parameters} and {\em Scores} come from training a learner using those parameters
-and applying it     test data$^{23-28}$.
+and applying it     test data$^{23-27}$.
 
 The premise of DE  is that the best way to mutate existing tunings
-is to {\em Extrapolate}$^{29}$
+is to {\em Extrapolate}$^{28}$
 between current solutions.  Three solutions $a,b,c$ are selected at random.
 For each tuning parameter $i$, at some probability {\em cr}, we replace
-the old tuning $x_i$ with $y_i$:
-\bi
-\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
-controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
+the old tuning $x_i$ with $y_i$. For booleans, we use $y_i= \neg x_i$ (see line 36). For numerics, $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
+controlling  cross-over.  The {\em trim} function$^{39}$ limits the new
 value to the legal range min..max of that parameter.
-\item (For booleans) $y_i= \neg x_i$ (see line 37).
-\ei
-The main loop of DE$^{7}$ runs over the {\em Population}, replacing old items
-with new {\em Candidate}s (if the new candidate is better than the old item).
-This means that, as the loop progresses, the {\em Population} is full of increasiningly
+
+The main loop of DE$^{6}$ runs over the {\em Population}, replacing old items
+with new {\em Candidate}s (if  new candidate is better).
+This means that, as the loop progresses, the {\em Population} is full of increasingly
 more valuable solutions. This, in turn, also improves  the candidates, which are {\em Extrapolate}d
@@
 values from a data mining, from which a {\em Goal} function extracts one 
-performance value$^{27}$ (so we run this code many times, each time with
-a different {\em Goal}$^{2}$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
+performance value$^{26}$ (so we run this code many times, each time with
+a different {\em Goal}$^{1}$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
 
@@
    \ei
-This approach ensures   all treatments 
-are assessed on the same tests. Note that we did consider
-one other experimental design but rejected it for reasons of
-internal validity (see \tion{construct}).
+% This approach ensures   all treatments 
+% are assessed on the same tests. Note that we did consider
+% one other experimental design but rejected it for reasons of
+% internal validity (see \tion{construct}).
 
@@
  \ei 
-These data sets are displayed in \fig{data1}.
+These data sets are displayed in \tab{data1}.
+
+As an aside, an alternate experimental design would be to 
+learn a baseline learner from the first {\em and} second release
+instead of, as shown above,  just the first release. On the one hand,
+this would mean that the baseline could be learned from more data.
+On the other hand, this adds a conflation to our experimental design
+since the optimizer uses the second release for pruning, not growing a data set set.  Happily, from 
+piror work~\cite{Menzies:2008aa} we know that defect predictors usually {\em saturates} (i.e.
+does not generate better predictors) after 100 examples, which is a number smaller than all our first release data sets. Hence, their would
+be little value in generating the baselines using the first and second
+releases.
 
@@
 
-\begin{figure}[!t]
+\begin{figure}[!b]
 \small
@@
 
-In this paper, what we can  show are examples of how  changing  optimization goals can also change 
-the conclusions made from that learner on that data. Accordingly, we warn that it is important not to overstate  empirical results from software analytics.
+In this paper, what we can  show  examples where  changing  optimization goals can also change 
+the conclusions made from that learner on that data. Accordingly, we warn that it is 
+important not to overstate  empirical results from  analytics.
 Rather, those results need to be expressed {\em along with} the context within which they are
@@
 show results for tuning on recall
-or false alarms. The reason is that false alarm and recall focus on {\em only}
-the non-defective and defective modules (respectively). Hence:
-\bi
-\item
-When DE tunes for recall, we can achieve near
+or false alarms. Those goals focus on {\em only}
+the  defective or non-defective modules (respectively). Hence.
+when DE tunes for recall, we can achieve near
 100\% recall-- but the cost of a near 100\% false alarms.
-\item
 Similarly,  tuning
@@
 the detector (when recall is zero).
-\ei
 Accordingly,  this paper  explores performance measures that comment on all 
@@
 
-\begin{table}[!tb]
+\section{Experimental Results}
+
+In the following, we explore the effects of tuning WHERE, Random Forests,
+and CART. LR will be used, untuned, in order to check one of the recommendations
+made by Hall et al.~\cite{hall11}.
+
+\subsection{RQ1:  Does  Tuning  Improve Performance? }\label{sect:precision}
+
+\fig{deltas} says  that the answer to RQ1 is ``yes''-- tuning  has a positive effect on performance scores. This figure sorts
+ deltas in the precision and the F-measure    between tuned and untuned learners. Our reading of this
+figure is that, overall, tuning rarely makes performance   worse and usually can make it much better.
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=1.5in]{precision_W.eps}\includegraphics[width=1.5in]{F_W.eps}
+ \end{center}
+\caption{Deltas in performance  seen in \tab{precisionbars} (left)
+and \tab{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
+ \end{figure}
+
+\tab{precisionbars} and \tab{fbars} show the
+the specific values seen before and after tuning (two separate experiments with different tuning goals). 
+For each data set, the maximum precision values for each data set are shown in {\bf bold}.
+As might have been
+ predicted by Lessmann et al.~\cite{lessmann2008benchmarking}, 
+untuned CART is indeed the worst learner (only one of its
+untuned results is best and {\bf bold}). 
+And, 
+in $\frac{13}{17}$ cases, the   untuned Random Forest performs better than or equal to untuned CART.  
+% Some of the data sets in \fig{precisionbars} proved challenging for all learners;
+% e.g. the precision results for {\em ivy} are less
+% that impressive.
+% To some extent, this is due to
+% the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).
+
+That said,  tuning can improve those poor performing detectors.
+For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
+A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
+In those two data sets, nearly all the precision values are   low {\em except} for
+tuned WHERE that scored 89\% and 85\%.
+Finally, note the  {\em jeditV2} result for the WHERE learner.
+Here, tuning changes precision from 2\% to 98\%.
+
+\begin{table}[!t]
 \renewcommand{\baselinestretch}{0.8}
@@
 
-\section{Experimental Results}
-\subsection{RQ1:  Does  Tuning  Improve Performance? }\label{sect:precision}
-
-\tab{precisionbars} shows precision results before and after tuning with precision as the performance criteria 
-using three different learners.
-For each data set, the maximum precision values for each data set are shown in {\bf bold}.
-
-These results offer support for  prior conclusions that CART is worse than Random Forest. As might have been
- predicted by Lessmann et al.~\cite{lessmann2008benchmarking}, 
-untuned CART is indeed the worst learner (only one of its
-untuned results is best and {\bf bold}). 
-Also, 
-in $\frac{13}{17}$ cases, the performance of untuned Random Forest is better than or equal to untuned CART.  
-% Some of the data sets in \fig{precisionbars} proved challenging for all learners;
-% e.g. the precision results for {\em ivy} are less
-% that impressive.
-% To some extent, this is due to
-% the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).
-
-That said,  tuning can improve those poor performing detectors.
-For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
-A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
-In those two data sets, nearly all the precision values are   low {\em except} for
-tuned WHERE that scored 89\% and 85\%.
-Finally, note the  {\em jeditV2} result for the WHERE learner.
-Here, tuning changes precision from 2\% to 98\%.
-
-\fig{deltas} shows that the answer to RQ1 is ``yes''; i.e. tuning usually has a positive effect on performance scores. This figure sorts
-the deltas in the precision and the F-measure    between tuned and untuned learners. Our reading of this
-figure is that, overall, tuning rarely makes performance   worse and usually can make it much better.
-
-\begin{figure}[!t]
-\begin{center}
-\includegraphics[width=1.5in]{precision_W.eps}\includegraphics[width=1.5in]{F_W.eps}
- \end{center}
-\caption{Deltas in performance  seen in \tab{precisionbars} (left)
-and \tab{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
- \end{figure}
-
-\subsection{RQ2:  Does Tuning Change a Learner's Ranking Regarding Different Goals?}\label{sect:rank}
-Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}.
-In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets.
-In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking.
-Such conclusions are not reliable since they can change when we elect to tune for different goals.
-
-22 learners are compared over NASA MDP data sets in terms of the AUC in \cite{lessmann2008benchmarking}.
-Some learners are tuned using manual methods, like C4.5, CART and Random Forests and some are tuned by searching algorithms, like grid search for SVM-Type learners.
-In our expeirment, when we tune CART and Random Forests for precisoin and F-measure, the rankings of these two learners are changed.
-
-In \tab{precisionbars} and \tab{fbars}, the tuned CART are better than or equal to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
-terms of precision and F-measure, respectively. Results from the non-parametric Kolmogorov-Smirnov Test turn out that the performance 
-scores of tuned CART and tuned Random Forests are not statistically different. This is the opposite of   
- Lessmann et al.~\cite{lessmann2008benchmarking}, the tuned Random Forest is not significantly better than tuned CART.
- In another result that is the reverse of \tab{precisionbars}, tuned WHERE is not necessarily
- any better than anything else.
-
- Therefore, it's not always safe to say ``LearnerX'' is the best or better than ``learnerY'' without pointing out the performance criteria or applying tuning techniques.
-That is, the answer to RQ2 is ``yes'' since tuning a set of learners
- changes the rankings of those learners regarding different criteria.
-
-The  important lesson here is that, given a particular task (e.g. optimizing for precision), tuning can offer
-substantial benefits. However, when that task changes (e.g. to optimizing for the F-measure),
-it should not be assumed that conclusions from the previous tuning will hold in the new context.
-In practice, this means that tuning needs to be repeated for each new context.
-
-% \begin{figure}[!t]
-% \begin{center}
-% \includegraphics[width=1.5in]{svm_rbf.eps}\includegraphics[width=1.5in]{svm_sigmoid.eps}
-%  \end{center}
-% \caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
-%  \end{figure}
-
 \begin{table}[!t]
@@
 
+\subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
+Researchers often use performance criteria to assert that one learner is better than 
+another~\cite{lessmann2008benchmarking,me07b,hall11}. For example:
+\be
+\item
+Lessmann et al.~\cite{lessmann2008benchmarking} conclude that
+Random Forest is considered to be statistically 
+better than CART. 
+\item
+Also, in Hall et al.'s   systematic literature review\cite{hall11} it is argued 
+that defect predictors based on simple 
+modeling techniques such as LR perform better than complicated techniques such as Random Forests\footnote{By three measures,
+Random Forests
+is the more complicated than LR. Firstly, LR builds one model
+while Random Forests builds many models. Secondly, LR is just
+a model construction tool while Random Forests needs both
+a tool to construct its forests {\em and} a second tool
+to  infer some conclusion from all the members of that forest.
+Thirdly, the LR model can be printed in a few lines while the multiple
+models learned by Random
+Forest model would take up multiple pages of output.}.
+\ee
+Given tuning, how stable are these  conclusions?
+Before answering issue, we digress for two comments.
+
+Firstly, it is important to comment on why it is  so important to check the conclusions
+of these particular papers. 
+These  papers are prominent publications (to say the least).
+Hall et al.~\cite{hall11} is the fourth most-cited IEEE TSE
+paper for 2009 to 2014 with 176 citations (see goo.gl/MGrGr7)
+while the Lessmann et al. paper~\cite{lessmann2008benchmarking} has 394 citations (see
+goo.gl/khTp97)-- which is quite remarkable for a paper published in 2009.
+Given the prominence
+of these papers, researchers might believe it is
+appropriate to
+  use  their advice without testing that advice on local data sets.
+
+Secondly, while we are critical of the results of
+Lessmann et al. and Hall et al., it needs to be said that  their analysis  was 
+excellent and exemplary given the state-of-the-art of the tools used when those papers were written.  
+While Hall et al. did not perform any new experiments, 
+their
+summarization of so many defect prediction papers have not been equalled
+before (or since).
+As to the Lessmann et al. paper, they  compared
+22 data miners using various   data sets (mostly from NASA)~\cite{lessmann2008benchmarking}.
+In that study, some learners were tuned using manual methods 
+(C4.5, CART and Random Forests)
+and some are tuned automatic  grid search for the SVM-Type learners (for more on grid search, see   {\S}2.1).
+
+That said, our tuning results show that it is time to revise
+the recommendations of those papers. 
+  \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forests).
+ In a result that might have been predicted Hall et al., Logistic Regression does perform better than untuned Random
+Forests over 17 data sets. 
+However, it turns out that advice is sensitive to the tunings
+used with Random Forests. After tuning, we find that Random Forests
+is often competitive, and sometimes even better, than Logistic Regression.
+
+As to Lessmann et al.'s advice (that Random Forest is better than 
+CART),  
+in \tab{precisionbars} and \tab{fbars}, we saw that counter-examples
+to that statement.
+Recall in those tables,
+tuned CART are better than or equal
+to tuned Random Forests in $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
+terms of precision and F-measure, respectively. Results from the non-parametric
+Kolmogorov-Smirnov Test show that the performance 
+scores of tuned CART and tuned Random Forests are not statistically different.
+Note that this  result that Random Forest is  not significantly better than   CART, would not have been
+predicted by   Lessmann et al.
+
+Hence we answer RQ2 as ``yes'': tuning can change how  data miners are comparatively ranked.
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
+ \end{center}
+\caption{Comparison between Logistic Regression and Random Forests before and after tuning. }\label{fig:lr}
+ \end{figure}
+
+% \begin{figure}[!t]
+% \begin{center}
+% \includegraphics[width=1.5in]{svm_rbf.eps}\includegraphics[width=1.5in]{svm_sigmoid.eps}
+%  \end{center}
+% \caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
+%  \end{figure}
+
 % list some features
-\begin{table*}[!ht]
+\begin{table}[!ht]
 
@@
 \centering
-  \begin{tabular}{c|l|l}
+  \begin{tabular}{c|p{1in}|p{1in}}
     \multicolumn{1}{c|}{ Data set}  &   \multicolumn{1}{c|}{Precision} & \multicolumn{1}{c}{F} \\ \hline 
@@
 
-    \caption{Features selected by tuned WHERE with different goals(features selected by tuning shown in bold). 
+    \caption{Features selected by tuned WHERE with different goals:
+    {\bf bold} features are those found useful by the tuned WHERE.
+    Also, features shown in plain text are those found useful by the untuned WHERE.
     }\label{tab:features}
-\end{table*}
+\end{table}
 
@@
 
-Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.
-\tab{features} shows that such conclusions are not reliable since they can be changed by tuning.
-For space limitation, from each data set, we just select one experiment, like antV0, as representative.
-This figure shows what attributes appeared in WHERE's final decision trees when optimizing for different goals, precision and F-measure.
-Note that the attributes selected by tuned WHERE in each row shown in bold are usually different from default WHERE.
-Meanwhile, in $\frac{9}{10}$ representative experiments, for the same data set, tuning selects different attributes for precision and F-measure.
-
-\Menzies{
-\begin{itemize}
-\item Do you have any insights into this table 6?
-\item like, are there any specific features considered very important in Default WHERE but not showing up in Tuning WHERE? . 
-\item WHY???
-\end{itemize}
-}
-% Note that the counts in the {\em tuned} column are   usually
-% different to those in the {\em default} columns (the tuned learners used more attributes
-% than otherwise as witnessed by the taller columns of numbers in the ``tuned'' column). 
-According to default WHERE, {\it mfa} is considered as the most important factor because it's selected in $\frac{9}{10}$ experiments for both goals.
-However, in tuning process, this factor has only shown as key factor in $\frac{5}{10}$ experiments for both precision and F-measure.
-
-That is, our answer to RQ3 is ``yes'', tuning changes our
+Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,Moser:2008,zimmermann2007predicting,herzig2013predicting}. 
+\tab{features} comments that such tests are unreliable since the factors selected by a data miner are much altered before and 
+after tuning.
+
+\tab{features} shows what features are found in the trees generated by the WHERE algorithm
+(bold shows the features found by the trees from tuned WHERE; plain text shows the features seen
+in the untuned study). Note that different features are selected depending on whether or not
+we tune an algorithm.
+
+For example, consider {\em mfa} which is the
+number of methods inherited by a class plus the number of methods accessible by member methods of the class.
+For both goals (precision and ``F'') {\em mfa} is selected for nine and five data sets,
+for the untuned and tuned data miner (respectively).
+Similar differences can be seen with other attributes.
+
+As to why different tunings select for different features,  recall from {\S}2.1 that tuning changes how data miners
+heuristically explore a large space of possible models. As we change how that exploration proceeds,
+so we change what features are found by that exploration.
+
+In any case, our answer to RQ3 is ``yes'', tuning changes our
 conclusions about what factors are most important in software engineering.
-
-\begin{figure}[!b]
+Hence, many old papers    need to be revisited  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,Moser:2008,zimmermann2007predicting,herzig2013predicting}.  
+For example, one of us (Menzies) used data miners
+to assert that some factors were more important than others for predicting
+successful software reuse~\cite{me02k}. That assertion should now be doubted since Menzies did not conduct a tuning study before reporting what factors the data miners
+found were most influential.
+
+\begin{figure}[!t]
 \begin{center}
@@
 To justify that {\em np=10} is enough, we did another tuning study, 
-where all the settings were the same as before but we set{\em np= 90, 50} and {\em np = 60} for WHERE, CART and Random Forests as recommended by Storn. The tuning performance of learners was evaluated
-by precision and F.
-To compare performance of each learner with different np's, we plot the delta in the performance as \fig{deltas}.
-As shown in \fig{deltas_np}, in terms of precision, the recommended {\em np} will improve the performance of WHERE, CART and Random Forests in 2, 5, and 4 data sets.
-However, in 6, 4, and 4 data sets, those numbers  will deteriorate the performance compared with {\em np = 10}.
-For F as the tuning goal, we can observe the similar pattern.
-
- From this study, with the same experimental condition, the recommended {\em np's} for WHERE, CART and Random Forest, do not bring any significant improvements over {\em np = 10}.
-We're not arguing that {\em np = 10} is the optimal settings for tuning defect predictors.
-But it suffices to make tuning easy and generate a competitive performance.
-
+where all the settings were the same as before but we set {\em np= 90, 50} and {\em np = 60} for WHERE, CART and Random Forests, respectively (i.e. the settings
+as recommended by Storn). The tuning performance of learners was evaluated
+by precision and F. To compare performance of each learner with different {\em np}'s, we computed the delta in the performance between {\em np=10} and {\em np} using any of \{90,50,60\}.
+
+Those deltas, shown in \fig{deltas_np}, are sorted along the x-axis. In those plots, a zero or negative $y$ value means that {\em np=10} performs as well or better than  {\em np $\in \{90,50,60\}$}. 
+In those
+plots we see:
+\bi
+\item The median improvement is zero; i.e. {\em np=10} usually does as well as anything else;
+\item The plots are nearly {\em balanced}-- for every case where {\em np=10} does worse,
+there is another when it performs as well or better.
+\ei
+One technical note: the data set orderings in \fig{deltas_np} on the x-axis are not the same. That is,
+if {\em np $>$ 10} was useful for optimizing one data set's precision score, it was not useful for that data set's F-measure score.
+
+Hence, in these results, there is no consistent pattern showing that {\em np=10} is a poor choice of search space size.
 Another measure showing that tuning is easy 
@@
 is the number of evaluations required to complete optimization
-(see next section).
-
-Hence we answer RQ4 as ``yes'', tuning is surprisingly easy (at least
-for defect predictors).
+(see next section). That is, we answer RQ4 as ``yes'', tuning is surprisingly easy-- at least
+for defect predictors and using DE.
 
@@
 on that work, our expectations were that non-parametric evolutionary optimization would
-take thousands, if not millions, of evaluations of candidate tunings. Hence, originally,
-we used Storn's advise on the size of {\em np} and ran our optimizers for 24 hours. 
-Then, just
-to get a baseline, we tried {\em np=10} and the early stopping rules (number of lives used in
-Algorithm~1 on line 5) and obtained the results of this paper.
-
-Hence, we answer RQ5 as ``no''. Tuning is so fast that
+take thousands, if not millions, of evaluations of candidate tunings. This turned out not
+to be case.
+
+Hence, we answer RQ5 as ``no'': tuning is so fast that
 it could (and should) be used by anyone using defect predictors. 
-The possible reason that tuning is so fast is that the searching space for defect prediction is not complicated, which might result from the tuning range set for each parameter in \tab{parameters}.
-The early stopping rules applied in this study also helps make tuning fast\wei{added HERE!}
-
-\subsection{RQ6: Should we use ``off-the-shelf'' Tunings?}\label{sect:variance}
-
- In \fig{features}, we show how tuning selects the optimal values for parameters.
-For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our supporting documents\footnote{\url{https://goo.gl/aHQKtU}}.
-The default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$. Note that:
-\bi
-\item
-The tunings learned by DE
-were often very different to the default. That is, to achieve the performance improvements seen in the paper,
-the default tuning parameters required a wide range of adjustments.
-\item The tunings learned by DE were different in different data sets and for different goals.
-\ei
-Hence, we answer RQ6 as ``no'' since, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
-sets are changed.Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
-tuning is so easy and so fast (at least for defect predictors from static code attributes).
-
-\begin{figure}[!t]
+%The possible reason that tuning is so fast is that the searching space for defect prediction is not complicated, which might result from the tuning range set for each parameter in \tab{parameters}.
+
+\begin{figure}
 \begin{center}
@@
  \end{center}
-\caption{Four representative tuning values in WHERE with  precision and F as the tuning goal, respectively.
-The default values for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$.
-}\label{fig:features}
+\caption{Four representative tuning values in WHERE with  precision and F as the tuning goal, respectively.   }\label{fig:features}
  \end{figure}
+
+\subsection{RQ6: Should we use ``off-the-shelf'' Tunings?}\label{sect:variance}
+
+ In \fig{features}, we show how tuning selects the optimal values for parameters.
+For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our online support documents\footnote{\url{https://goo.gl/aHQKtU}}.
+ Note that
+ the tunings learned were different in different data sets and for different goals.
+Also, the tunings learned by DE
+were often very different to the default (the default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$, respectively).
+That is, to achieve the performance improvements seen in the paper,
+the default tuning parameters required a wide range of adjustments.
+
+Hence, we answer RQ6 as ``no'' since, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
+sets are changed. Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
+tuning is so easy and so fast (at least for defect predictors from static code attributes).
 
@@
 
-\section{Reliability and Validity}\label{sect:construct}
+\newpage\section{Reliability and Validity}\label{sect:construct}
 
@@
 
-{\em Validity} refers to the extent to which a piece of research actually
-investigates what the researcher purports to investigate.
-{\em Internal validity} checks if the differences found in
-the treatments can be ascribed to the treatments under study. 
-One internal validity issue with our experiments is the choice
-of {\em training, tuning, and testing} data sets discussed in 
-\tion{design}. Recall that while all our learners used the same
-{\em testing} data set, our untuned learners were only given
-access to {\em training} while DEs could get feedback from
-{\em training} and
-{\em tuning}.  This means that, potentially,  the performance increases
-reported above are merely an artificat of the DEs being able to access
-more data. However:
-\bi
-\item Note that
-DEs assess their performance using a model built from {\em training}
-then applied to the {\em tuning} data. If we gave the untuned
-learners double the training data, then this would be inherently
-biased against DEs.
-\item In practice, this is much ado about nothing. We have
-repeated all the experiments of this paper with the untuned
-learners building models from {\em training} + {\em tuning}.
-While the exact numbers found in this way
-may differ from the above in some small way, we can report that 
-those repeated runs do not substantively change the above conclusions.
-\ei
 {\em External validity} checks if the results are of relevance
@@
 Once again, this means that old papers may need to be revised including those
-some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
+some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,Moser:2008,zimmermann2007predicting,herzig2013predicting}. 
 \ei
@@
 
+\newpage
 \section{Future Work}

### 2015-08-20 tuningpredictor.tex
add KS test table
Updates from ShareLaTeX

@@
 \ee
-More specifically,
-this paper explores six research questions about tuning defect predictors for
-static code measures:
+Those results were found by   exploring six research questions:
 \bi
@@
 \ei
+Based on our answers to these  questions,  we strongly advise that:
+\bi
+\item
+Data miners should not be used ``off-the-shelf'' with their default tunings (since
+we show below just how much tuning can alter default settings
+both for different data sets and for different goals).
+\item
+Any future paper on defect prediction should include a 
+tuning study. Here, we have found  an algorithm called differential
+evolution to be a useful method for conducting such
+tunings.
+\item
+Tuning needs to be repeated
+whenever data or goals are changed.
+Fortunately, the cost of find good tunings is not excessive since, at least for
+static code defect predictors, tuning is easy and fast.
+\ei
+
 %Before beginning, we digress for one  clarification.
@@
 
-\section{Background}
-
+\section{Preliminaries}
 \subsection{Issues of Tuning: Important and Ignored?}
@@
 
-\subsection{Defect Prediction}
+\subsection{Notes on Defect Prediction}
 
@@
 
- \subsection{Data Mining Algorithms}
+ \subsection{Notes on Data Miners}
 
@@
 
-\subsection{Learners and Their Tunings}
+\subsection{ Learners and Their Tunings}
 
@@
 \ei
+As to why we used the "Tuning Range" shown in \tab{parameters}, and not some other ranges,
+we note that (1)~those ranges included the defaults; (2)~the results shown below
+show that by exploring those ranges,   we achieved large gains in the performance of our defect predictors.
+This is not to say that {\em larger} tuning ranges might not result in {\em greater} improvements.
+However, for the goals of this paper (to show that some tunings do matter), exploring
+just these ranges shown in \tab{parameters} will suffice.
+
 As to the details of these learners, LR is a parametric
@@
 \section{Experimental Design}\label{sect:design}
-
-The following experiment aims to compare the performance of three learners, tuned and untuned, on 17
-sets of data.
 
@@
 number of methods inherited by a class plus the number of methods accessible by member methods of the class.
-For both goals (precision and ``F'') {\em mfa} is selected for nine and five data sets,
+For both goals (precision and ``F'') {\em mfa} is selected for 9 and 5 data sets,
 for the untuned and tuned data miner (respectively).
-Similar differences can be seen with other attributes.
+Similar differences are   seen with other attributes.
 
@@
 
-Those deltas, shown in \fig{deltas_np}, are sorted along the x-axis. In those plots, a zero or negative $y$ value means that {\em np=10} performs as well or better than  {\em np $\in \{90,50,60\}$}. 
-In those
-plots we see:
-\bi
-\item The median improvement is zero; i.e. {\em np=10} usually does as well as anything else;
-\item The plots are nearly {\em balanced}-- for every case where {\em np=10} does worse,
-there is another when it performs as well or better.
-\ei
-One technical note: the data set orderings in \fig{deltas_np} on the x-axis are not the same. That is,
-if {\em np $>$ 10} was useful for optimizing one data set's precision score, it was not useful for that data set's F-measure score.
-
-Hence, in these results, there is no consistent pattern showing that {\em np=10} is a poor choice of search space size.
+Those deltas, shown in \fig{deltas_np}, are sorted along the x-axis.
+In those plots, a zero or negative $y$ value means that {\em np=10} performs as well or better than  {\em np $\in \{90,50,60\}$}.
+One technical aside: the data set orderings in \fig{deltas_np} on the x-axis are not the same (that is,
+if {\em np $>$ 10} was useful for optimizing one data set's precision score, it was not useful for that data set's F-measure score).
+
+  \fig{deltas_np} shows that
+the median improvement is zero; i.e. {\em np=10} usually does as well as anything else. This observation is
+supported by the   KS
+  results of \tab{ks}. At a 95\% confidence, the
+KS threshold  is $1.36\sqrt{34/(17*17)} = 0.46$ which is greater than  the values in \fig{deltas_np}.
+That is, no result in  \fig{deltas_np} is significantly different to any other-- which is to say that
+there is no evidence that   {\em np=10} is a poor choice of search space size.
+
 Another measure showing that tuning is easy 
@@
 for defect predictors and using DE.
+
+% \begin{table}[!t]
+% \centering
+% \scriptsize
+% \begin{tabular}{|l|c|c|}
+% \hline
+% Learner & CART & WHERE \\ \hline
+% CART    & -    & 0.42  \\ \hline
+% R.Forest      & 0.29 & 0.18  \\ \hline
+% \end{tabular}
+% \begin{tabular}{|l|c|c|}
+% \hline
+% Learner & CART & WHERE \\ \hline
+% CART    & -    & 0.24  \\ \hline
+% R.Forest      & 0.24 & 0.29  \\ \hline
+% \end{tabular}
+% \caption{Kolmogorov-Smirnov Tests for numbers seen in \fig{deltas_np}: Precision(left) and F(right).}
+% \end{table}
+
+\begin{table}[!t]
+\renewcommand{\baselinestretch}{0.8}
+\scriptsize
+\centering
+  \begin{tabular}{c|c c|cc}
+    &   \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c}{F} \\ \hline 
+    Learner & CART  & WHERE & CART & WHERE \\
+\hline
+    CART & - & 0.42 & - & 0.24 \\
+    R. Forest &  0.29 & 0.18 & 0.24 & 0.29 \\
+  \end{tabular}
+    \caption{Kolmogorov-Smirnov Tests for distributions of  \fig{deltas_np}}\label{tab:ks}
+\end{table}
 
@@
 
-\begin{figure}
+\begin{figure}[!t]
 \begin{center}
@@
 
-\newpage\section{Reliability and Validity}\label{sect:construct}
+\section{Reliability and Validity}\label{sect:construct}
 
@@
 
-That said, there exist some class of data mining papers for which
-tuning may not be required. Consider  Le Goues et al.'s 2012
-ICSE paper that used a evolutionary program to learn
-repairs to code~\cite{leGoues12}. The performance criteria
-in that paper was ``can we fix any of the known bugs?''. Note
-that this criteria is a ``{\em competency}'' statement, and
-not a ``{\em better than}'' statement (the difference being that
-one is 
-``can do'' and the other is ``can do better''). For such
-competency claims, tuning is not necessary. However, as soon
-as {\em better than} enters the performance criteria then this
-becomes a race between competing methods. In such a race,
-it is unfair to hobble one competitor with poor tunings.
+%That said, there exist some class of data mining papers for which
+%tuning may not be required. Consider  Le Goues et al.'s 2012
+%ICSE paper that used a evolutionary program to learn
+%repairs to code~\cite{leGoues12}. The performance criteria
+%in that paper was ``can we fix any of the known bugs?''. Note
+%that this criteria is a ``{\em competency}'' statement, and
+%not a ``{\em better than}'' statement (the difference being that
+%one is 
+%``can do'' and the other is ``can do better''). For such
+%competency claims, tuning is not necessary. However, as soon
+%as {\em better than} enters the performance criteria then this
+%becomes a race between competing methods. In such a race,
+%it is unfair to hobble one competitor with poor tunings.
 
@@
 \ei
-Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
-\fig{features} shows just how much tuning can alter default settings
-both for different data sets and for different goals.
-
-Since the results from tuning are unstable,
-tuning needs to be repeated
-whenever data or goals are changed.
-Fortunately, the cost of find good tunings is not excessive since, at least for
-static code defect predictors, tuning is easy and fast.
-
-\newpage
-\section{Future Work}
-
- As noted by
-F\"{u}rnkranz~\cite{furnkranz05}, data mining is inherently a multi-objective optimization
+As to future work, it is now important
+to explore the implications of these
+conclusions to other kinds of software analytics.
+ This paper has investifated  {\em some} learners using {\em one}  optimizer. Hence, we can make
+no claim that DE is the {\em best} optimizer for {\em all} learners.
+Rather, our point is that there exists at least some learners
+whose performance can be dramatically improved by 
+at least one simple optimization scheme.  We hope that this work inspires
+much future work as this community develops and debugs best practices for tuning
+software analytics.
+
+Finally, on a more general note, we point out
+that 
+F\"{u}rnkranz~\cite{furnkranz05} says data mining is inherently a multi-objective optimization
 problem that seeks the smallest model with the highest performance, 
@@
 
-Another issue for future work is the implications of these
-conclusions to other kinds of software analytics.
- This paper has explored  {\em some} learners using {\em one}  optimizer. Hence, we can make
-no claim that DE is the {\em best} optimizer for {\em all} learners.
-Rather, our point is that there exists at least some learners
-whose performance can be dramatically improved by 
-at least one simple optimization scheme.  We hope that this work inspires
-much future work as this community develops and debugs best practices for tuning
-software analytics.
-
 \section*{Acknowledgments}

### 2015-08-20 tuningpredictor.tex
test
move .eps into eps folder

@@
 \begin{center}
-\includegraphics[width=1.5in]{precision_W.eps}\includegraphics[width=1.5in]{F_W.eps}
+\includegraphics[width=1.5in]{./eps/precision_W.eps}\includegraphics[width=1.5in]{./eps/F_W.eps}
  \end{center}
@@
 \begin{center}
-\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
+\includegraphics[width=1.5in]{./eps/LR_untuned.eps}\includegraphics[width=1.5in]{./eps/LR_tuned.eps}
  \end{center}
@@
 \begin{center}
-\includegraphics[width=1.5in]{np_precision.eps}\includegraphics[width=1.5in]{np_f.eps}
+\includegraphics[width=1.5in]{./eps/np_precision.eps}\includegraphics[width=1.5in]{./eps/np_f.eps}
  \end{center}
@@
 \end{table}
+
+% \begin{table}[!t]
+% \renewcommand{\baselinestretch}{0.8}
+% \scriptsize
+% \centering
+%   \begin{tabular}{c|c |c}
+%     &   \multicolumn{1}{c|}{Precision} & \multicolumn{1}{c}{F} \\ \hline 
+%     Learner  & np = 10 & recommended np \\
+% \hline
+%     WHERE & 0.18 & 0.24 \\
+%     CART  & 0.12 & 0.12  \\
+%     R. Forest &  0.12 & 0.12 \\
+%   \end{tabular}
+%     \caption{Kolmogorov-Smirnov Tests for distributions of each learner with np = 10 and recommended np's }\label{tab:ks}
+% \end{table}
 
@@
 \begin{center}
-\includegraphics[width=1.5in]{features_precision.eps}\includegraphics[width=1.5in]{features_F.eps}
+\includegraphics[width=1.5in]{./eps/features_precision.eps}\includegraphics[width=1.5in]{./eps/features_F.eps}
  \end{center}

### 2015-08-21 gen_eps/plot_improvements_F_precision.m
update

@@ -1,0 +1,40 @@
+clf
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[-19.0, -19.0, -11.0, -7.0, -6.0, 0.0, 0.0, 1.0, 1.0, 2.0, 2.0, 3.0, 4.0, 4.0, 7.0, 73.0, 91.0], '-r*')
+hold on
+plot(x,[-17.0, -1.0, 1.0, 2.0, 2.0, 4.0, 4.0, 4.0, 6.0, 8.0, 9.0, 11.0, 15.0, 18.0, 19.0, 29.0, 57.0],'-b+')
+hold on
+plot(x,[-20.0, -12.0, -10.0, -4.0, -4.0, -1.0, -1.0, 0.0, 1.0, 5.0, 6.0, 6.0, 15.0, 18.0, 22.0, 27.0, 59.0], '-gx')
+axis([1 17 -100 100])
+legend('WHERE','CART','R.Forest','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[-50,0,50,100])
+hline = refline([0 0]);
+set(hline,'Color','k')
+title('F')
+legend('boxoff')
+xlabel('improvements, sorted')
+
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[-30.0, -26.0, -25.0, 0.0, 0.0, 0.0, 6.0, 9.0, 13.0, 15.0, 42.0, 59.0, 59.0, 63.0, 72.0, 73.0, 96.0], '-r*')
+hold on
+plot(x,[-23.0, -4.0, 3.0, 3.0, 4.0, 5.0, 8.0, 8.0, 12.0, 15.0, 16.0, 29.0, 33.0, 34.0, 38.0, 59.0, 62.0],'-b+')
+hold on
+plot(x,[-23.0, -1.0, 0.0, 1.0, 1.0, 5.0, 6.0, 6.0, 8.0, 9.0, 10.0, 18.0, 28.0, 33.0, 35.0, 36.0, 61.0], '-gx')
+axis([1 17 -100 100])
+legend('WHERE','CART','R.Forest','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[-50,0,50,100])
[…]

### 2015-08-21 gen_eps/plot_np_10_90.m

@@ -1,0 +1,40 @@
+clf
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[-90, -48, -18, -4, -1, -1, 0, 0, 0, 2, 2, 4, 35, 74, 77, 80, 92], '-r*')
+hold on
+plot(x,[-46,-6,-5,-1,0,0,0,0,0,1,2,2,2,3,4,11,62],'-b+')
+hold on
+plot(x,[-55,-21,-5,-3,-3,-2,0,0,0,0,0,1,1,1,2,3,9], '-gx')
+axis([1 17 -100 100])
+legend('WHERE','CART','R.Forest','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[-50,0,50,100])
+hline = refline([0 0]);
+set(hline,'Color','k')
+title('F')
+legend('boxoff')
+xlabel('improvements, sorted')
+
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[-40,-38,-25,-24,-5,-2,0,0,0,0,0,0,0,0,0,27,74], '-r*')
+hold on
+plot(x,[-44,-42,-12,-2,-1,0,0,0,2,2,3,3,13,24,25,29,74],'-b+')
+hold on
+plot(x,[-24,-11,-4,-3,-1,-1,0,0,0,0,0,0,1,3,3,10,74], '-gx')
+axis([1 17 -100 100])
+legend('WHERE','CART','R.Forest','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[-50,0,50,100])
+hline = refline([0 0]);
+set(hline,'Color','k')
+title('Precision')
+legend('boxoff')
+xlabel('improvements, sorted')

### 2015-08-21 gen_eps/plot_where_features_range.m

@@ -1,0 +1,43 @@
+clf
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[0.24, 0.43, 0.59, 0.64, 0.87, 0.98, 0.98, 0.98, 0.98, 0.98, 0.98, 0.98, 1, 1, 1, 1, 1], '-r*')
+hold on
+plot(x,[0.01, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.3, 0.41, 0.43, 0.45, 0.54, 0.54, 0.68, 0.71, 0.84, 1],'-b+')
+hold on
+plot(x,[0.13, 0.22, 0.27, 0.38, 0.46, 0.46, 0.47, 0.48, 0.51, 0.51, 0.51, 0.51, 0.51, 0.59, 0.66, 0.66, 0.77], '-gx')
+hold on
+plot(x,[0.01, 0.01, 0.19, 0.19, 0.26, 0.26, 0.52, 0.52, 0.55, 0.6, 0.6, 0.6, 0.6, 0.6, 0.6, 0.83, 0.83],'-ks')
+axis([1 17 -0.5 1.2])
+legend('threshold','infoPrune','min\_{Size}','wriggle','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[0,0.2,0.33,0.5,1])
+hline = refline([0 0]);
+set(hline,'Color','k')
+title('Precision')
+legend('boxoff')
+xlabel('tuning value, sorted')
+
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+x = [1:17]
+box on 
+hold on
+plot(x,[0.04, 0.04, 0.24, 0.44, 0.44, 0.44, 0.44, 0.44, 0.65, 0.65, 0.77, 0.77, 0.77, 0.87, 0.98, 0.98, 1], '-r*')
+hold on
+plot(x,[0.01, 0.07, 0.12, 0.14, 0.14, 0.31, 0.47, 0.48, 0.51, 0.51, 0.54, 0.57, 0.68, 0.68, 0.68, 0.68, 0.88],'-b+')
+hold on
+plot(x,[0.18, 0.18, 0.4, 0.4, 0.4, 0.4, 0.46, 0.51, 0.51, 0.56, 0.59, 0.62, 0.65, 0.66, 0.77, 0.8, 0.97], '-gx')
+hold on
[…]

### 2015-08-21 tuningpredictor.tex
Updates from ShareLaTeX

@@
 Over our entire sample, there was only  one paper that conducted a somewhat extensive tuning study.
-Lessmann et al. tuned parameters for some of their algorithms using  a {\em grid search}; i.e. divide all $C$ configuration
+Lessmann et al.\cite{lessmann2008benchmarking} tuned parameters for some of their algorithms using  a {\em grid search}; i.e. divide all $C$ configuration
 options into $N$ values, then try all   $N^C$ combinations.
@@
   \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forests).
- In a result that might have been predicted Hall et al., Logistic Regression does perform better than untuned Random
+ In a result that might have been predicted as Hall et al., Logistic Regression does perform better than untuned Random
 Forests over 17 data sets. 
@@
 CART),  
-in \tab{precisionbars} and \tab{fbars}, we saw that counter-examples
+in \tab{precisionbars} and \tab{fbars}, we saw those counter-examples
 to that statement.
@@
 One technical aside: the data set orderings in \fig{deltas_np} on the x-axis are not the same (that is,
-if {\em np $>$ 10} was useful for optimizing one data set's precision score, it was not useful for that data set's F-measure score).
+if {\em np $>$ 10} was useful for optimizing one data set's precision score, it was not necessary for that data set's F-measure score).
 
@@
  In \fig{features}, we show how tuning selects the optimal values for parameters.
-For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our online support documents\footnote{\url{https://goo.gl/aHQKtU}}.
+For space limitation, only four parameters from WHERE learner are selected as representatives and all the others can be found in our online support documents\footnote{\url{https://goo.gl/aHQKtU}}.
  Note that
@@
 
+\section{Guidelines \wei{added!}}
+
+As discussed above, tuning is helpful and easy to do.
+Any defect prediction study based on data mining should include a tuning study.
+However, if tuning is not done properly, performance may not be improved but degraded to some extent.
+Here're some tips for tuning:
+
+{\em Tuning Data} is important for the whole tuning process.
+If available data size for the study is very small, k-fold cross evaluation method can be used to split data and generate new training data as well as tuning data.
+On the other hand, if the study concerns more about chronology, incremental learning approach can be adopted.
+
+{\em Tuning Range} will determine how large the searching space the tuner will explore and how good the parameter got from tuning.
+The recommended range will set the default value as the median of the range with a reasonable distance.
+If the performance from tuning dose not better than the default parameter, adjust ranges accordingly.
+
+{\em Searching algorithm} is the engine of the tuning process.
+Since tuning has to be repeatedly done for different goals and different data sets, simple searching algorithms, like DE and Generic algorithms, are good choice to complete this task.
+Other more advanced algorithms, like NSGA III \cite{deb2014evolutionary} and GALE\cite{krall15}, can also be used if multi-objective tuning is considered.
+
 \section{Reliability and Validity}\label{sect:construct}

### 2015-08-21 gen_eps/plot_improvements_F_precision.m
update x-axis

@@ -17,7 +17,7 @@ hline = refline([0 0]);
 set(hline,'Color','k')
 title('F')
 legend('boxoff')
-xlabel('improvements, sorted')
+xlabel('data sets, sorted')
 
  FigHandle = figure('Position', [220, 300, 200, 400]);
 %plot([1:17],[0:0])
@@ -37,4 +37,4 @@ hline = refline([0 0]);
 set(hline,'Color','k')
 title('precision')
 legend('boxoff')
-xlabel('improvements, sorted')
+xlabel('data sets, sorted')

### 2015-08-21 gen_eps/plot_np_10_90.m

@@ -17,7 +17,7 @@ hline = refline([0 0]);
 set(hline,'Color','k')
 title('F')
 legend('boxoff')
-xlabel('improvements, sorted')
+xlabel('data sets, sorted')
 
  FigHandle = figure('Position', [220, 300, 200, 400]);
 %plot([1:17],[0:0])
@@ -37,4 +37,4 @@ hline = refline([0 0]);
 set(hline,'Color','k')
 title('Precision')
 legend('boxoff')
-xlabel('improvements, sorted')
+xlabel('data sets, sorted')

### 2015-08-21 gen_eps/plot_where_features_range.m

@@ -19,7 +19,7 @@ hline = refline([0 0]);
 set(hline,'Color','k')
 title('Precision')
 legend('boxoff')
-xlabel('tuning value, sorted')
+xlabel('data sets, sorted')
 
  FigHandle = figure('Position', [220, 300, 200, 400]);
 x = [1:17]
@@ -40,4 +40,4 @@ hline = refline([0 0]);
 set(hline,'Color','k')
 title('F')
 legend('boxoff')
-xlabel('tuning value, sorted')
+xlabel('data sets, sorted')

### 2015-08-21 tuningpredictor.tex
Updates from ShareLaTeX
typos, grammer mistakes fixed.

@@
 \newcommand{\fig}[1]{Figure~\ref{fig:#1}}
-\newcommand{\tab}[1]{Table ~\ref{tab:#1}}
+\newcommand{\tab}[1]{Table~\ref{tab:#1}}
 \newcommand{\eq}[1]{Equation~\ref{eq:#1}}
@@
        \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
-       fuwei.ee, tim.menzies, xipengshen@gmail.com}
+       fuwei.ee, tim.menzies@gmail.com, xshen5@ncsu.edu }
 \maketitle 
@@
 For example, when  learning
-software defect predictors this  method can quickly
+software defect predictors, this  method can quickly
 found tunings  that  alter detection  precision  
@@
 \noindent
-{\bf Keywords:} defect prediction, CART, random forests,
+{\bf Keywords:} defect prediction, CART, random forest,
 differential evolution,
@@
 Some of those conclusions are completely changed by tuning. 
-\item RQ3: {\em Does tuning change conclusions about what factors are most important in software engineering?} Numerous recent SE papers (e.g.
-~\cite{bell2013limited,rahman2013how,me02k,Moser:2008,zimmermann2007predicting,%
+\item RQ3: {\em Does tuning change conclusions about what factors are most important in software engineering?} Numerous recent SE papers (e.g.~\cite{bell2013limited,rahman2013how,me02k,Moser:2008,zimmermann2007predicting,%
 herzig2013predicting}) use data miners to conclude that {\em this}
@@
 whenever data or goals are changed.
-Fortunately, the cost of find good tunings is not excessive since, at least for
+Fortunately, the cost of finding good tunings is not excessive since, at least for
 static code defect predictors, tuning is easy and fast.
@@
 there are $2^{20}$ possible models. Data mining is practical since various heuristics
-allow automatic algorithms to ignore most of those possibilities. 
-While  heuristic search makes data mining possible, it also means that tunings
+allow automatic algorithms to ignore most of those possibilities. While heuristic search makes data mining possible, it also means that tunings
 can significantly affect what comes out of a data miner.
@@
 Are the impacts of tuning addressed in the defect prediction literature?
-To answer that question,  in August 2015 we searched scholar.google.com for the conjunction of  "data mining" and "software engineering" and  "defect prediction".
+To answer that question,  in August 2015 we searched scholar.google.com for the conjunction of  "data mining" and "software engineering" and  "defect prediction"\footnote{https://goo.gl/Inl9nF}.
 After sorting by the citation count and discarding the non-SE papers (and those without a pdf link), we read over this sample
@@
 What we found in that sample was that few authors
-acknowledged the impact of tunings (exceptions: ~\cite{hall11,lessmann2008benchmarking}).
+acknowledged the impact of tunings (exceptions:~\cite{Gao:2011,lessmann2008benchmarking}).
 Overall,  80\% of papers in our sample {\em did not} adjust
-the ``off-the-shelf'' configuration of the data miner (e.g. ~\cite{me07b,Moser:2008,herzig2013predicting,zimmermann2007predicting}). Of the remaining papers:
+the ``off-the-shelf'' configuration of the data miner (e.g.~\cite{me07b,Moser:2008,Elish2008649}). Of the remaining papers:
 \bi
@@
 important configurations~\cite{Bergstra2012}. 
-Bergstra and Bengio~\cite{Bergstra2012} comment for most data sets only a few of the tuning parameters really matter-- which means that
+Bergstra and Bengio~\cite{Bergstra2012} comment that for most data sets only a few of the tuning parameters really matter-- which means that
 much of the runtimes associated with grid search is actually wasted.
@@
 github.com/ai-se/where). 
- We use  these algorithms, for the following reasons.
+ We use  these algorithms for the following reasons.
 
@@
 as usually being as good or better as more complex learners (e.g.
-Random Forests). In a finding that endorses the Hall et al. result,
+Random Forest). In a finding that endorses the Hall et al. result,
 we show that untuned LR performs better than 
-untuned Random Forests (at least, for the data sets studied here). However,
+untuned Random Forest (at least, for the data sets studied here). However,
 we will show that tuning raises doubts about the optimality of the
@@
 Our learners use the tuning parameters of \tab{parameters}. This section describes those parameters.
-The default parameters for CART and Random Forests are set by 
+The default parameters for CART and Random Forest are set by 
 the SciKitLearn authors and the
@@
 optimize defect prediction from static code attributes.  
-The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
+The pseudocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
 In the following description, 
-    superscript numbers denotes a line in that figure.
+    superscript numbers denote lines in that pseudocode.
 
@@
 a current {\em Population}.  Our DE's lose one ``life''
-when e new is no better than  current (terminating when ``life'' is zero)$^{4}$.
+when thee new population is no better than  current one (terminating when ``life'' is zero)$^{4}$.
 Each candidate solution in the {\em Population}  
@@
 the old tuning $x_i$ with $y_i$. For booleans, we use $y_i= \neg x_i$ (see line 36). For numerics, $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
-controlling  cross-over.  The {\em trim} function$^{39}$ limits the new
+controlling  cross-over.  The {\em trim} function$^{38}$ limits the new
 value to the legal range min..max of that parameter.
@@
 open source Java systems defined in terms of \tab{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
-{\it poi},{\it synapse}, {\it velocity} and {\it xerces}.
+{\it poi}, {\it synapse}, {\it velocity} and {\it xerces}.
 
@@
 {\em cross-validation} mixes up older and newer data  (such that
-data from the {\em future} may be used to test on {\em past data}).
+data from the {\em past} may be used to test on {\em future data}).
 
@@
    reported below from (a)~the model generated by the untuned learner or (b)~the
-   best model found by differential evolution.
+   best model found by DE.
    \ei
@@
  \bi
- \item AntV0: first,second,third = versions 1,2,3
- \item AntV1: first,second,third = versions 2,3,4
- \item AntV2: first,second,third = versions 3,4,5
+ \item AntV0: first, second, third = versions 1, 2, 3
+ \item AntV1: first, second, third = versions 2, 3, 4
+ \item AntV2: first, second, third = versions 3, 4, 5
  \ei 
@@
 
-In the following, we explore the effects of tuning WHERE, Random Forests,
+In the following, we explore the effects of tuning WHERE, Random Forest,
 and CART. LR will be used, untuned, in order to check one of the recommendations
@@
 \begin{center}
-\includegraphics[width=1.5in]{./eps/precision_W.eps}\includegraphics[width=1.5in]{./eps/F_W.eps}
+\includegraphics[width=1.5in]{./eps/improvements_precision.eps}\includegraphics[width=1.5in]{./eps/improvements_F.eps}
  \end{center}
@@
 the specific values seen before and after tuning (two separate experiments with different tuning goals). 
-For each data set, the maximum precision values for each data set are shown in {\bf bold}.
+For each data set, the maximum precision or F values for each data set are shown in {\bf bold}.
 As might have been
@@
 \item
-Also, in Hall et al.'s   systematic literature review\cite{hall11} it is argued 
+Also, in Hall et al.'s   systematic literature review\cite{hall11}, it is argued
 that defect predictors based on simple 
-modeling techniques such as LR perform better than complicated techniques such as Random Forests\footnote{By three measures,
-Random Forests
+modeling techniques such as LR perform better than complicated techniques such as Random Forest\footnote{By three measures,
+Random Forest
 is the more complicated than LR. Firstly, LR builds one model
-while Random Forests builds many models. Secondly, LR is just
-a model construction tool while Random Forests needs both
+while Random Forest builds many models. Secondly, LR is just
+a model construction tool while Random Forest needs both
 a tool to construct its forests {\em and} a second tool
@@
 
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=1.5in]{./eps/LR_untuned.eps}\includegraphics[width=1.5in]{./eps/LR_tuned.eps}
+ \end{center}
+\caption{Comparison between Logistic Regression and Random Forest before and after tuning. }\label{fig:lr}
+ \end{figure}
+
 Secondly, while we are critical of the results of
@@
 In that study, some learners were tuned using manual methods 
-(C4.5, CART and Random Forests)
+(C4.5, CART and Random Forest)
 and some are tuned automatic  grid search for the SVM-Type learners (for more on grid search, see   {\S}2.1).
@@
 the recommendations of those papers. 
-  \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forests).
- In a result that might have been predicted as Hall et al., Logistic Regression does perform better than untuned Random
+  \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forest).
+ In a result that might have been predicted by Hall et al., Logistic Regression does perform better than untuned Random
 Forests over 17 data sets. 
 However, it turns out that advice is sensitive to the tunings
-used with Random Forests. After tuning, we find that Random Forests
+used with Random Forest. After tuning, we find that Random Forest
 is often competitive, and sometimes even better, than Logistic Regression.
@@
 tuned CART are better than or equal
-to tuned Random Forests in $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
+to tuned Random Forest in $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
 terms of precision and F-measure, respectively. Results from the non-parametric
 Kolmogorov-Smirnov Test show that the performance 
-scores of tuned CART and tuned Random Forests are not statistically different.
-Note that this  result that Random Forest is  not significantly better than   CART, would not have been
+scores of tuned CART and tuned Random Forest are not statistically different.
+Note that Random Forest is  not significantly better than CART, would not have been
 predicted by   Lessmann et al.
@@
 Hence we answer RQ2 as ``yes'': tuning can change how  data miners are comparatively ranked.
-
-\begin{figure}[!t]
-\begin{center}
-\includegraphics[width=1.5in]{./eps/LR_untuned.eps}\includegraphics[width=1.5in]{./eps/LR_tuned.eps}
- \end{center}
-\caption{Comparison between Logistic Regression and Random Forests before and after tuning. }\label{fig:lr}
- \end{figure}
 
@@
 % list some features
-\begin{table}[!ht]
+\begin{table}[!b]
 
@@
 recall from Algorithm~1 that
-DE explores a {\em Population} of size {\em np=10}. This is a very small population size since
+DE explores a {\em Population} of size {\em np = 10}. This is a very small population size since
 Rainer Storn (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
@@
 we see that Storn would therefore recommend {\em np} values of
-90, 50, 60 for WHERE, CART and Random Forests (respectively). Yet we achieve our results
-using a constant {\em np=10}; i.e. $\frac{10}{90}, \frac{10}{50}, \frac{10}{60}$ of the
+90, 50, 60 for WHERE, CART and Random Forest (respectively). Yet we achieve our results
+using a constant {\em np = 10}; i.e. $\frac{10}{90}, \frac{10}{50}, \frac{10}{60}$ of the
 recommended search space.
 
-To justify that {\em np=10} is enough, we did another tuning study, 
-where all the settings were the same as before but we set {\em np= 90, 50} and {\em np = 60} for WHERE, CART and Random Forests, respectively (i.e. the settings
+To justify that {\em np = 10} is enough, we did another tuning study, 
+where all the settings were the same as before but we set {\em np = 90, np = 50} and {\em np = 60} for WHERE, CART and Random Forest, respectively (i.e. the settings
 as recommended by Storn). The tuning performance of learners was evaluated
-by precision and F. To compare performance of each learner with different {\em np}'s, we computed the delta in the performance between {\em np=10} and {\em np} using any of \{90,50,60\}.
+by precision and F. To compare performance of each learner with different {\em np}'s, we computed the delta in the performance between {\em np = 10} and {\em np} using any of \{90, 50, 60\}.
 
 Those deltas, shown in \fig{deltas_np}, are sorted along the x-axis.
-In those plots, a zero or negative $y$ value means that {\em np=10} performs as well or better than  {\em np $\in \{90,50,60\}$}.
+In those plots, a zero or negative $y$ value means that {\em np = 10} performs as well or better than  {\em np $\in \{90, 50, 60\}$}.
 One technical aside: the data set orderings in \fig{deltas_np} on the x-axis are not the same (that is,
@@
   \fig{deltas_np} shows that
-the median improvement is zero; i.e. {\em np=10} usually does as well as anything else. This observation is
+the median improvement is zero; i.e. {\em np = 10} usually does as well as anything else. This observation is
 supported by the   KS
@@
 That is, no result in  \fig{deltas_np} is significantly different to any other-- which is to say that
-there is no evidence that   {\em np=10} is a poor choice of search space size.
+there is no evidence that   {\em np = 10} is a poor choice of search space size.
 
@@
 improvements reported in this paper. 
-50 to 80 evaluations is  much less than our pre-experimental intuition.
+50 to 80 evaluations are  much fewer than our pre-experimental intuition.
 Prior to this paper, the authors have conducted numerous explorations of evolutionary algorithms
@@
 take thousands, if not millions, of evaluations of candidate tunings. This turned out not
-to be case.
+to be that case.
 
@@
 show that when learning defect predictors for static code
-attributes,   analytics without parameter tuning is considered {\em harmful} and {\em misleading}:
+attributes,   analytics without parameter tuning are considered {\em harmful} and {\em misleading}:
 \bi
@@
 conclusions to other kinds of software analytics.
- This paper has investifated  {\em some} learners using {\em one}  optimizer. Hence, we can make
+ This paper has investigated  {\em some} learners using {\em one}  optimizer. Hence, we can make
 no claim that DE is the {\em best} optimizer for {\em all} learners.

### 2015-08-28 dm101.tex
typos, grammer mistakes fixed.
ready to go!

@@
 One such lightweight sampling policy is defect predictors learned from static code attributes.
-Given software described in (e.g.) the attributes of \tab{ck},   data miners can
+Given software described in the attributes of \tab{ck},   data miners can
 learn where the probability of software defects is highest.
@@
 Verification and validation (V\&V) textbooks
-(\cite{rakitin01}) advise using static code complexity attributes
+\cite{rakitin01} advise using static code complexity attributes
 to decide which modules are worth manual inspections.
@@
 predictors learned at NASA~\cite{me07b} have also been found useful elsewhere
-(e.g. in Turkey~\cite{tosun10,tosun09}.
+(e.g. in Turkey~\cite{tosun10,tosun09}).
 The success of this method in  predictors in finding bugs is   markedly
@@
 of defects.
-In other work, 
+In another work, 
 Raffo documents the typical    defect detection capability of

### 2015-08-28 tuningpredictor.tex
ready to go!

@@
 software defect predictors, this  method can quickly
-found tunings  that  alter detection  precision  
+find tunings  that  alter detection  precision  
  from 2\% to 98\%.
@@
 Also, we suspected that
-tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.
+tuning would take so long time and be so CPU intensive that the benefits gained   would not be worth effort.
 
@@
  examples of truly dramatic improvement:
- usually by 5 to 20\% and often by much more (in one extreme case, precision improved from 2\% to 98\%);
+ usually by 5 to 20\% and often by much more (in one extreme case, precision improved from 2\% to 98\%).
 \item RQ2: {\em Does tuning change conclusions on what learners are better than others?} 
@@
 \item
-Data miners should not be used ``off-the-shelf'' with their default tunings (since
-we show below just how much tuning can alter default settings
-both for different data sets and for different goals).
+Data miners should not be used ``off-the-shelf'' with default tunings.
 \item
@@
 
-The formal definitions of data mining stresses that these learners are heuristic explorers
+The formal definition of data mining stresses that these learners are heuristic explorers
 of a truly   vast space of the possible models within a data set~\cite{mitchell1982generalization}. For example, given 20 columns of boolean variables,
@@
 Some papers in our sample  explored   data super-sampling~\cite{4271036} or data sub-sampling techniques via  automatic methods (e.g. ~\cite{Gao:2011,me07b,4271036,Kim:2011}) 
-or via some domain principle (e.g. ~\cite{Moser:2008,Nagappan:2008,Hassan:2009}).
+or via some domain principles (e.g. ~\cite{Moser:2008,Nagappan:2008,Hassan:2009}).
 As an example of the latter, Nagappan et al.~\cite{Nagappan:2008} checked if metrics related to organizational structure were relatively more powerful for predicting software defects. 
-However, it should be notes that  these studies varied the input data but
+However, it should be noted that  these studies varied the input data but
 not the   ``off-the-shelf''   settings of the data miner.
@@
 
-There are many ways to build defect predictors
-such as  CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
+There  are ways to make defect predictors
+using  CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
  WHERE~\cite{menzies2013local} and LR (logistic regression).
-For this study, we use WHERE-based learner, CART, Random Forest and LR versions  from 
-SciKitLearn~\cite{scikit-learn} (and
-WHERE is available from
-github.com/ai-se/where). 
+For this study, we use CART, Random Forest and LR versions  from 
+SciKitLearn~\cite{scikit-learn} and
+WHERE, which is available from
+github.com/ai-se/where. 
  We use  these algorithms for the following reasons.
@@
 In a demonstration of the impact of tuning,
-this paper shows  we can {\em reverse} the conclusions of  Lessmann et al. such that CART
+this paper shows  we can {\em refute} the conclusions of  Lessmann et al.
+in the sense that, after tuning,
+CART
 performs just as well as
@@
 If data contains more than {\em min\_sample\_split}, then a split is attempted.
-On the other hand, if a split contains no more than {\em min\_samples\_leaf}, then recursion stops. CART and Random Forest use a 
+On the other hand, if a split contains no more than {\em min\_samples\_leaf}, then the recursion stops. CART and Random Forest use a 
 user-supplied constant for this parameter while
@@
 a current {\em Population}.  Our DE's lose one ``life''
-when thee new population is no better than  current one (terminating when ``life'' is zero)$^{4}$.
+when the new population is no better than  current one (terminating when ``life'' is zero)$^{4}$.
 Each candidate solution in the {\em Population}  
@@
 On the other hand, this adds a conflation to our experimental design
-since the optimizer uses the second release for pruning, not growing a data set set.  Happily, from 
+since the optimizer uses the second release for pruning, not growing a data set.  Happily, from 
 piror work~\cite{Menzies:2008aa} we know that defect predictors usually {\em saturates} (i.e.
@@
 or false alarms. Those goals focus on {\em only}
-the  defective or non-defective modules (respectively). Hence.
+the  defective or non-defective modules (respectively). Hence,
 when DE tunes for recall, we can achieve near
@@
 \tab{precisionbars} and \tab{fbars} show the
-the specific values seen before and after tuning (two separate experiments with different tuning goals). 
+the specific values seen before and after tuning (two separate experiments with two different tuning goals: {\em precision} and {\em ``F''}). 
 For each data set, the maximum precision or F values for each data set are shown in {\bf bold}.
@@
 in $\frac{13}{17}$ cases, the   untuned Random Forest performs better than or equal to untuned CART.  
+% Note that the size of the improvement is sometimes small; e.g. the precision results improve more than the ``F'' measure.
+% But even when the {\em median} change is small, there still may exist
+% interesting (i.e.  exceptionally
+% large) improvements from tuning-- for example, 
+%  see the last  two ``F'' improvements for WHERE in \fig{deltas} where the improvements were greater than 70\%.
 % Some of the data sets in \fig{precisionbars} proved challenging for all learners;
@@
 That said,  tuning can improve those poor performing detectors.
-For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
+In some cases, the median changes may be small (e.g. the ``F'' results for WHERE) but even in
+those cases, there are enough large changes to motivate the use of tuning. For example:
+\bi
+\item
+For WHERE's ``F'' improvement, there are two improvements over 70\%;
+\item
+Regarding precision, 
+for {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
 A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
@@
 Here, tuning changes precision from 2\% to 98\%.
+\ei
+
+% To complete the discussion in this section, we note that in the Lessmann et al. study,  Random Forest dramatically out-performed CART.
+% In this study, we show that  
+% tuned CART is now comparable to Random Forest. So our new results
+% do not complete reverse the results of Lessmann et al. However, they
+% do show that the Lessmann results are ``brittle'', in the sense that
+% tuning can remove the effect they report.
 
@@
 \end{tabular}
-\caption{F-value results (best results  shown in {\bf bold}).}
+\caption{F-measure results (best results  shown in {\bf bold}).}
 \label{tab:fbars}
@@
 Random Forest
-is the more complicated than LR. Firstly, LR builds one model
+is more complicated than LR. Firstly, LR builds one model
 while Random Forest builds many models. Secondly, LR is just
 a model construction tool while Random Forest needs both
-a tool to construct its forests {\em and} a second tool
+a tool to construct its forest {\em and} a second tool
 to  infer some conclusion from all the members of that forest.
@@
 (C4.5, CART and Random Forest)
-and some are tuned automatic  grid search for the SVM-Type learners (for more on grid search, see   {\S}2.1).
+and some, like SVM-Type learners, were tuned by automatic grid search (for more on grid search, see   {\S}2.1).
 
@@
 terms of precision and F-measure, respectively. Results from the non-parametric
-Kolmogorov-Smirnov Test show that the performance 
+Kolmogorov-Smirnov(KS) Test show that the performance 
 scores of tuned CART and tuned Random Forest are not statistically different.
@@
 as recommended by Storn). The tuning performance of learners was evaluated
-by precision and F. To compare performance of each learner with different {\em np}'s, we computed the delta in the performance between {\em np = 10} and {\em np} using any of \{90, 50, 60\}.
+by precision and ``F'' as before.
+To compare performance of each learner with different {\em np}'s, we computed the delta in the performance between {\em np = 10} and {\em np} using any of \{90, 50, 60\}.
 
@@
   results of \tab{ks}. At a 95\% confidence, the
-KS threshold  is $1.36\sqrt{34/(17*17)} = 0.46$ which is greater than  the values in \fig{deltas_np}.
+KS threshold  is $1.36\sqrt{34/(17*17)} = 0.46$, which is greater than  the values in \fig{deltas_np}.
 That is, no result in  \fig{deltas_np} is significantly different to any other-- which is to say that
@@
 \end{table}
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=1.5in]{./eps/features_precision.eps}\includegraphics[width=1.5in]{./eps/features_F.eps}
+ \end{center}
+\caption{Four representative tuning values in WHERE with  precision and F-measure as the tuning goal, respectively.   }\label{fig:features}
+ \end{figure}
 
@@
   \end{tabular}
-  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for  ``F''.  }\label{tab:ftimes}
+  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for F-measure.  }\label{tab:ftimes}
 \end{table*}
@@
 
-\begin{figure}[!t]
-\begin{center}
-\includegraphics[width=1.5in]{./eps/features_precision.eps}\includegraphics[width=1.5in]{./eps/features_F.eps}
- \end{center}
-\caption{Four representative tuning values in WHERE with  precision and F as the tuning goal, respectively.   }\label{fig:features}
- \end{figure}
+As to why DE can tune defect predictors so quickly, that is an
+open question. One possibility is that the search space within
+the control space of these data miners has  many accumulative effects such that one
+decision can cascade into another (and the combination of decisions
+is better than each separate  one). DE would be a natural  tool for reasoning
+about such ``cascades'', due to the way it mashes candidates together,
+then inserts the result back into the frontier (making them available
+for even more mashing at the next step of the inference).
 
@@
 
- In \fig{features}, we show how tuning selects the optimal values for parameters.
+ In \fig{features}, we show how tuning selects the optimal values for tuned parameters.
 For space limitation, only four parameters from WHERE learner are selected as representatives and all the others can be found in our online support documents\footnote{\url{https://goo.gl/aHQKtU}}.
@@
 Also, the tunings learned by DE
-were often very different to the default (the default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$, respectively).
+were often very different to the default (the default values for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$, respectively).
 That is, to achieve the performance improvements seen in the paper,
@@
 
-\section{Guidelines \wei{added!}}
-
-As discussed above, tuning is helpful and easy to do.
+% \section{Guidelines \wei{added!}}
+
+% As discussed above, tuning is helpful and easy to do.
 Any defect prediction study based on data mining should include a tuning study.
@@
 
-{\em Tuning Data} is important for the whole tuning process.
+% {\em Tuning Data} is important for the whole tuning process.
 If available data size for the study is very small, k-fold cross evaluation method can be used to split data and generate new training data as well as tuning data.
@@
 
-{\em Tuning Range} will determine how large the searching space the tuner will explore and how good the parameter got from tuning.
+% {\em Tuning Range} will determine how large the searching space the tuner will explore and how good the parameter got from tuning.
 The recommended range will set the default value as the median of the range with a reasonable distance.
@@
 
-{\em Searching algorithm} is the engine of the tuning process.
+% {\em Searching algorithm} is the engine of the tuning process.
 Since tuning has to be repeatedly done for different goals and different data sets, simple searching algorithms, like DE and Generic algorithms, are good choice to complete this task.
@@
 The examples of this paper  only relate to precision, recall, and the F-measure
-but the general principle (that the search bias changes the search conclusions)  holds for all any set of goals. 
+but the general principle (that the search bias changes the search conclusions)  holds for any set of goals. 
 Also,

### 2015-09-08 old/gen_eps/plot_improvements_F_precision.m
upload

@@ -1,0 +1,40 @@
+clf
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[-19.0, -19.0, -11.0, -7.0, -6.0, 0.0, 0.0, 1.0, 1.0, 2.0, 2.0, 3.0, 4.0, 4.0, 7.0, 73.0, 91.0], '-r*')
+hold on
+plot(x,[-17.0, -1.0, 1.0, 2.0, 2.0, 4.0, 4.0, 4.0, 6.0, 8.0, 9.0, 11.0, 15.0, 18.0, 19.0, 29.0, 57.0],'-b+')
+hold on
+plot(x,[-20.0, -12.0, -10.0, -4.0, -4.0, -1.0, -1.0, 0.0, 1.0, 5.0, 6.0, 6.0, 15.0, 18.0, 22.0, 27.0, 59.0], '-gx')
+axis([1 17 -100 100])
+legend('WHERE','CART','R.Forest','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[-50,0,50,100])
+hline = refline([0 0]);
+set(hline,'Color','k')
+title('F')
+legend('boxoff')
+xlabel('data sets, sorted')
+
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[-30.0, -26.0, -25.0, 0.0, 0.0, 0.0, 6.0, 9.0, 13.0, 15.0, 42.0, 59.0, 59.0, 63.0, 72.0, 73.0, 96.0], '-r*')
+hold on
+plot(x,[-23.0, -4.0, 3.0, 3.0, 4.0, 5.0, 8.0, 8.0, 12.0, 15.0, 16.0, 29.0, 33.0, 34.0, 38.0, 59.0, 62.0],'-b+')
+hold on
+plot(x,[-23.0, -1.0, 0.0, 1.0, 1.0, 5.0, 6.0, 6.0, 8.0, 9.0, 10.0, 18.0, 28.0, 33.0, 35.0, 36.0, 61.0], '-gx')
+axis([1 17 -100 100])
+legend('WHERE','CART','R.Forest','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[-50,0,50,100])
[…]

### 2015-09-08 old/gen_eps/plot_where_features_range.m

@@ -1,0 +1,43 @@
+clf
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+%plot([1:17],[0:0])
+x = [1:17]
+box on 
+hold on
+plot(x,[0.24, 0.43, 0.59, 0.64, 0.87, 0.98, 0.98, 0.98, 0.98, 0.98, 0.98, 0.98, 1, 1, 1, 1, 1], '-r*')
+hold on
+plot(x,[0.01, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.3, 0.41, 0.43, 0.45, 0.54, 0.54, 0.68, 0.71, 0.84, 1],'-b+')
+hold on
+plot(x,[0.13, 0.22, 0.27, 0.38, 0.46, 0.46, 0.47, 0.48, 0.51, 0.51, 0.51, 0.51, 0.51, 0.59, 0.66, 0.66, 0.77], '-gx')
+hold on
+plot(x,[0.01, 0.01, 0.19, 0.19, 0.26, 0.26, 0.52, 0.52, 0.55, 0.6, 0.6, 0.6, 0.6, 0.6, 0.6, 0.83, 0.83],'-ks')
+axis([1 17 -0.5 1.2])
+legend('threshold','infoPrune','min\_{Size}','wriggle','Location','South')
+set(gca,'XTick', [1,4,8,12,17])
+set(gca, 'YTick',[0,0.2,0.33,0.5,1])
+hline = refline([0 0]);
+set(hline,'Color','k')
+title('Precision')
+legend('boxoff')
+xlabel('data sets, sorted')
+
+ FigHandle = figure('Position', [220, 300, 200, 400]);
+x = [1:17]
+box on 
+hold on
+plot(x,[0.04, 0.04, 0.24, 0.44, 0.44, 0.44, 0.44, 0.44, 0.65, 0.65, 0.77, 0.77, 0.77, 0.87, 0.98, 0.98, 1], '-r*')
+hold on
+plot(x,[0.01, 0.07, 0.12, 0.14, 0.14, 0.31, 0.47, 0.48, 0.51, 0.51, 0.54, 0.57, 0.68, 0.68, 0.68, 0.68, 0.88],'-b+')
+hold on
+plot(x,[0.18, 0.18, 0.4, 0.4, 0.4, 0.4, 0.46, 0.51, 0.51, 0.56, 0.59, 0.62, 0.65, 0.66, 0.77, 0.8, 0.97], '-gx')
+hold on
[…]

### 2015-09-08 tuningpredictor.tex

@@
   Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
-antV0 & 30 &   & {\bf 89} &   & 27 &   & {\bf 89} &   & 28 &   & {\bf 89} &  \\
-antV1 & 32 &   & {\bf 74} &   & 36 &   & {\bf 74} &   & 41 &   & {\bf 74} &  \\
-antV2 & 78 &   & 52 &   & 52 &   & 56 &   & 64 &   & {\bf 100} &  \\
-camelV0 & {\bf 83} &   & {\bf 83} &   & 26 &   & 34 &   & 50 &   & 78 &  \\
-camelV1 & 22 &   & 81 &   & 24 &   & {\bf 83} &   & 25 &   & 31 &  \\
-ivy & 16 &   & {\bf 89} &   & 17 &   & 25 &   & 16 &   & 21 &  \\
-jeditV0 & 35 &   & 48 &   & 49 &   & {\bf 61} &   & 44 &   & 50 &  \\
-jeditV1 & 24 &   & {\bf 87} &   & 28 &   & 62 &   & 28 &   & 37 &  \\
-jeditV2 & 2 &   & {\bf 98} &   & 3 &   & 18 &   & 5 &   & 5 &  \\
-log4j & 94 &   & {\bf 100} &   & 97 &   & {\bf 100} &   & 99 &   & {\bf 100} &  \\
-lucene & 61 &   & 76 &   & 67 &   & 70 &   & 67 &   & {\bf 77} &  \\
-poiV0 & 74 &   & 74 &   & {\bf 79} &   & 75 &   & 77 &   & 78 &  \\
-poiV1 & {\bf 100} &   & 75 &   & 73 &   & 89 &   & 82 &   & {\bf 100} &  \\
-synapse & 66 &   & 66 &   & 71 &   & {\bf 100} &   & 65 &   & {\bf 100} &  \\
-velocity & 34 &   & {\bf 43} &   & 34 &   & 39 &   & 34 &   & 42 &  \\
-xercesV0 & 13 &   & {\bf 85} &   & 14 &   & 47 &   & 15 &   & 14 &  \\
-xercesV1 & {\bf 56} &   & 26 &   & 49 &   & 26 &   & 49 &   & 26 &  \\
+antV0 & 24 &   & 35 &   & 27 &   & {\bf 60} &   & 28 &   & 44 &  \\
+antV1 & 0 &   & {\bf 60} &   & 36 &   & 56 &   & 41 &   & 50 &  \\
+antV2 & 0 &   & 55 &   & 52 &   & 52 &   & 64 &   & {\bf 67} &  \\
+camelV0 & 0 &   & 30 &   & 26 &   & 50 &   & 50 &   & {\bf 79} &  \\
+camelV1 & 27 &   & {\bf 28} &   & 24 &   & {\bf 28} &   & 25 &   & 27 &  \\
+ivy & 18 &   & 21 &   & 17 &   & {\bf 26} &   & 16 &   & 20 &  \\
+jeditV0 & 35 &   & 37 &   & 49 &   & {\bf 78} &   & 44 &   & 60 &  \\
+jeditV1 & 24 &   & 42 &   & 28 &   & {\bf 64} &   & 28 &   & 37 &  \\
+jeditV2 & 2 &   & {\bf 22} &   & 3 &   & 17 &   & 5 &   & 6 &  \\
+log4j & 94 &   & 91 &   & 97 &   & 98 &   & 99 &   & {\bf 100} &  \\
+lucene & 60 &   & 75 &   & 67 &   & 70 &   & 67 &   & {\bf 77} &  \\
+poiV0 & 72 &   & 70 &   & 79 &   & 71 &   & {\bf 83} &   & 69 &  \\
+poiV1 & 90 &   & 76 &   & 73 &   & 90 &   & 82 &   & {\bf 100} &  \\
+synapse & 0 &   & 50 &   & 71 &   & {\bf 100} &   & 65 &   & 60 &  \\
+velocity & 34 &   & {\bf 44} &   & 34 &   & {\bf 44} &   & 34 &   & 42 &  \\
+xercesV0 & 12 &   & {\bf 17} &   & 14 &   & 14 &   & 15 &   & 14 &  \\
+xercesV1 & 53 &   & 54 &   & 49 &   & {\bf 100} &   & 49 &   & 27 &  \\
 \end{tabular}
@@
   Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
-antV0 & 39 &   & 20 &   & 32 &   & 40 &   & {\bf 41} &   & 21 &  \\
-antV1 & 11 &   & 5 &   & 38 &   & 49 &   & 37 &   & {\bf 55} &  \\
-antV2 & 0 &   & 3 &   & 44 &   & {\bf 48} &   & 47 &   & 46 &  \\
-camelV0 & 0 &   & {\bf 91} &   & 9 &   & 28 &   & 4 &   & 31 &  \\
-camelV1 & 35 &   & 35 &   & 31 &   & 33 &   & {\bf 37} &   & 33 &  \\
-ivy & 28 &   & 32 &   & 28 &   & 30 &   & 27 &   & {\bf 33} &  \\
-jeditV0 & 50 &   & {\bf 57} &   & 56 &   & {\bf 57} &   & 56 &   & {\bf 57} &  \\
-jeditV1 & 37 &   & 38 &   & 36 &   & 45 &   & 43 &   & {\bf 49} &  \\
-jeditV2 & 4 &   & 6 &   & 5 &   & {\bf 9} &   & {\bf 9} &   & 8 &  \\
-log4j & {\bf 61} &   & 54 &   & 47 &   & 46 &   & 57 &   & 45 &  \\
-lucene & 70 &   & 74 &   & 56 &   & 74 &   & 70 &   & {\bf 75} &  \\
-poiV0 & 82 &   & 71 &   & 79 &   & 62 &   & {\bf 83} &   & 73 &  \\
-poiV1 & 5 &   & {\bf 78} &   & 21 &   & {\bf 78} &   & 19 &   & {\bf 78} &  \\
-synapse & 0 &   & 2 &   & 40 &   & 55 &   & 41 &   & {\bf 56} &  \\
-velocity & 51 &   & 51 &   & 49 &   & {\bf 53} &   & 51 &   & 51 &  \\
-xercesV0 & 22 &   & 23 &   & 21 &   & {\bf 27} &   & 24 &   & 20 &  \\
-xercesV1 & 23 &   & 4 &   & 18 &   & {\bf 47} &   & 18 &   & 40 &  \\
+antV0 & 23 &   & 20 &   & 32 &   & 40 &   & {\bf 41} &   & 38 &  \\
+antV1 & 0 &   & 38 &   & 38 &   & {\bf 49} &   & 37 &   & {\bf 49} &  \\
+antV2 & 0 &   & 50 &   & 44 &   &  49 &   & 47 &   & {\bf 56} &  \\
+camelV0 & 0 &   & 28 &   & 9 &   & 28 &   & 4 &   & {\bf 30} &  \\
+camelV1 & 35 &   & 34 &   & 31 &   & 32 &   & {\bf 37} &   & 33 &  \\
+ivy & 30 &   & 34 &   & 28 &   & {\bf 40} &   & 27 &   &  33 &  \\
+jeditV0 & 51 &   & 47 &   & 56 &   & 57 &   & 56 &   & {\bf 59} &  \\
+jeditV1 & 35 &   & 44 &   & 36 &   & 47 &   & 43 &   & {\bf 48} &  \\
+jeditV2 & 4 &   & {\bf 11} &   & 5 &   & 10 &   & 9 &   & 9 &  \\
+log4j & 54 &   & 50 &   & 47 &   & 37 &   & {\bf 57} &   & 47 &  \\
+lucene & 72 &   & 73 &   & 56 &   & 72 &   & 70 &   & {\bf 76} &  \\
+poiV0 & 78 &   & 74 &   & {\bf 79} &   & 64 &   & 77 &   & 77 &  \\
+poiV1 & 12 &   & {\bf 78} &   & 21 &   & 69 &   & 19 &   & {\bf 78} &  \\
+synapse & 0 &   & 56 &   & 40 &   & {\bf 60} &   & 41 &   & 53 &  \\
+velocity & 51 &   & {\bf 53} &   & 49 &   & 51 &   & 51 &   & 51 &  \\
+xercesV0 & 20 &   & 22 &   & 21 &   & {\bf 26} &   & 24 &   & 21 &  \\
+xercesV1 & 25 &   & 70 &   & 18 &   & 35 &   & 18 &   & {\bf 71} &  \\
 \end{tabular}
@@
     \multicolumn{1}{c|}{ Data set}  &   \multicolumn{1}{c|}{Precision} & \multicolumn{1}{c}{F} \\ \hline 
- \multirow{2}{*}{antV0} & {\bf mfa} &  {\bf None} \\
-         & mfa, dam, wmc, ic & mfa, dam, wmc, ic\\
+ \multirow{2}{*}{antV0} & {\bf rfc} &  {\bf None} \\
+         & mfa, loc, cam, dit, dam, lcom3 & mfa, loc, cam, dit, dam, lcom3\\
   \hline
- \multirow{2}{*}{camelV0} & {\bf mfa, rfc, lcom3, cam, amc, loc, ic} &{\bf  mfa, wmc, cam, dam, loc, lcom3, rfc, ic, dit }\\
-        & mfa, rfc, lcom3, cam, dam, loc & mfa, rfc, lcom3, cam, dam, loc\\
+ \multirow{2}{*}{camelV0} & {\bf mfa, wmc, lcom3} &{\bf None }\\
+        & mfa, wmc, rfc, loc, cam, lcom3 & mfa, wmc, rfc, loc, cam, lcom3\\
   \hline
- \multirow{2}{*}{ivy} & {\bf dam, cam} &{\bf  cam, dit, npm, dam, wmc, lcom3 }  \\
-       & cam, dit, dam, ic & cam, dit, dam, ic \\
+ \multirow{2}{*}{ivy} & {\bf cam, dam, npm, loc, rfc, wmc} &{\bf cam, dam, npm, loc, rfc, wmc }  \\
+       & loc, cam, dam, wmc, lcom3 & loc, cam, dam, wmc, lcom3 \\
   \hline
- \multirow{2}{*}{jeditV0} &{\bf  mfa, dam, rfc, avg\_cc, lcom3, dit }&{\bf  dam, rfc, mfa, wmc, ce, cam, loc, avg\_cc}\\
-         & mfa, dam, lcom3, dit, ic, cbm & mfa, dam, lcom3, dit, ic, cbm \\
+ \multirow{2}{*}{jeditV0} &{\bf mfa, dam, loc }&{\bf mfa, dam, loc}\\
+         & mfa, lcom3, dam, dit, ic & mfa, lcom3, dam, dit, ic \\
   \hline
- \multirow{2}{*}{log4j} & {\bf lcom3, mfa, loc, cbm, wmc }&{\bf  mfa, wmc}\\
-         & lcom3, mfa, loc, cbm, dit & lcom3, mfa, loc, ic \\
+ \multirow{2}{*}{log4j} & {\bf loc, ic, dit }&{\bf mfa, wmc, rfc, loc, npm}\\
+         & mfa, lcom3, loc, ic & mfa, lcom3, loc, ic \\
    \hline
-  \multirow{2}{*}{lucene} & {\bf rfc, mfa, npm, cam} & {\bf mfa, dam, wmc, loc, rfc, ic}\\
-         & mfa, lcom3, cam, dam, ic & mfa, lcom3, cam, dam, ic\\
+  \multirow{2}{*}{lucene} & {\bf dit, cam, wmc, lcom3, dam, rfc, cbm, mfa, ic} & {\bf dit, lcom3, dam, mfa}\\
+         & dit, cam, dam, ic & dit, cam, dam, cbm, ic\\
    \hline
-   \multirow{2}{*}{poiV0} & {\bf loc }& {\bf loc} \\
-        & mfa, loc, amc, wmc, npm, lcom & mfa, loc, amc, wmc,npm, lcom\\
+   \multirow{2}{*}{poiV0} & {\bf mfa, amc, dam }& {\bf mfa, amc, dam} \\
+        & mfa, loc, amc, dam, wmc, lcom & mfa, loc, amc, dam, wmc, lcom\\
    \hline
-   \multirow{2}{*}{synapse} &{\bf  dam} & {\bf loc, dam} \\
-        & dam, loc, mfa, cam & dam, loc, mfa, cam\\
+   \multirow{2}{*}{synapse} &{\bf loc, dit, rfc, cam, wmc, dam, lcom,  mfa,  lcom3} & {\bf dam} \\
+        & loc, mfa, cam, lcom, dam, lcom3 & loc, mfa, cam, lcom, dam, lcom3\\
     \hline
-   \multirow{2}{*}{velocity} & {\bf dit, dam, cam, rfc, cbo, lcom3, wmc, ic, cbm }& {\bf dam, dit, loc, amc, lcom3, ic, mfa }\\
-        & dit, dam, lcom3, ic, mfa  & dit, dam, lcom3, ic, mfa\\
+   \multirow{2}{*}{velocity} & {\bf dit, wmc, cam, rfc, cbo, moa, dam }& {\bf mfa, dit }\\
+        & dit, dam, lcom3, ic, mfa, cbm  & dit, dam, lcom3, ic, mfa\\
     \hline
-   \multirow{2}{*}{xercesV0} &{\bf  None }&{\bf  dam, rfc, avg\_cc, dit, loc, lcom3, cam }\\
-        & cam, loc, dam, mfa, amc &  cam, loc, dam, mfa, amc \\
+   \multirow{2}{*}{xercesV0} &{\bf  wmc }&{\bf cam, dam, avg\_cc, loc, wmc,  dit,  mfa, ce, lcom3 }\\
+        & wmc, mfa, lcom3, cam, dam &  wmc, mfa, lcom3, cam, dam \\
     \hline
@@
 
+% \begin{table*}[!ht]
+
+% \renewcommand{\baselinestretch}{0.75}
+% \scriptsize
+% \centering
+%   \begin{tabular}{r|c |c |c |c |c |c }
+%     Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
+%     \hline
+%     antV0 & 50 / 90.18 & 1.57 & 60 / 4.36 & 0.09 & 50 / 8.12 & 0.18\\
+%     antV1 & 50 / 174.67 & 2.90 & 50 / 6.35 & 0.10 & 50 / 11.77 & 0.27\\
+%     antV2 & 50 / 403.63 & 6.92 & 70 / 9.71 & 0.16 & 60 / 13.28 & 0.35\\
+%     camelV0 & 50 / 537.53 & 8.60 & 50 / 9.14 & 0.18 & 50 / 13.73 & 0.31\\
+%     camelV1 & 60 / 1640.54 & 24.57 & 60 / 17.06 & 0.24 & 70 / 31.53 & 0.73\\
+%     ivy & 70 / 77.75 & 1.02 & 60 / 3.86 & 0.06 & 50 / 8.00 & 0.17\\
+%     jeditV0 & 80 / 472.57 & 5.49 & 60 / 6.30 & 0.09 & 70 / 13.01 & 0.30\\
+%     jeditV1 & 60 / 489.45 & 6.82 & 70 / 7.61 & 0.11 & 60 / 12.87 & 0.32\\
+%     jeditV2 & 50 / 435.43 & 7.21 & 50 / 6.46 & 0.12 & 90 / 20.34 & 0.37\\
+%     log4j & 70 / 113.73 & 1.36 & 70 / 3.25 & 0.05 & 60 / 7.07 & 0.16\\
+%     lucene & 70 / 224.39 & 2.70 & 50 / 4.07 & 0.08 & 50 / 8.87 & 0.26\\
+%     poiV0 & 60 / 261.06 & 4.00 & 60 / 6.23 & 0.10 & 50 / 10.57 & 0.29\\
+%     poiV1 & 80 / 607.85 & 7.18 & 60 / 7.69 & 0.13 & 50 / 11.39 & 0.29\\
+%     synapse & 50 / 116.04 & 1.87 & 60 / 4.07 & 0.05 & 70 / 9.74 & 0.16\\
+%     velocity & 60 / 195.27 & 2.75 & 60 / 4.49 & 0.06 & 80 / 12.15 & 0.21\\
+%     xercesV0 & 60 / 143.69 & 2.17 & 70 / 7.26 & 0.09 & 60 / 10.28 & 0.23\\
+%     xercesV1 & 50 / 794.50 & 13.37 & 50 / 8.24 & 0.15 & 60 / 14.54 & 0.38\\
+
+%   \end{tabular}
+%   \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for  precision.  }\label{tab:etimes}
+% \end{table*}
+% %%%%time for F %%%%%%
+% \begin{table*}[!ht]
+% \renewcommand{\baselinestretch}{0.75}
+% \scriptsize
+% \centering
+%   \begin{tabular}{r|c |c |c |c |c |c } 
+%     Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
+%     \hline
+%     antV0 & 50 / 94.08 & 1.71 & 60 / 4.55 & 0.08 & 60 / 10.79 & 0.21\\
+%     antV1 & 60 / 193.74 & 3.02 & 70 / 7.77 & 0.09 & 60 / 12.30 & 0.25\\
+%     antV2 & 80 / 643.94 & 7.59 & 60 / 8.38 & 0.15 & 70 / 16.99 & 0.41\\
+%     camelV0 & 60 / 662.56 & 9.97 & 60 / 13.19 & 0.23 & 80 / 26.11 & 0.32\\
+%     camelV1 & 60 / 1800.64 & 24.25 & 50 / 15.02 & 0.28 & 50 / 28.52 & 0.78\\
+%     ivy & 60 / 69.95 & 1.03 & 50 / 3.35 & 0.08 & 70 / 9.40 & 0.18\\
+%     jeditV0 & 90 / 553.80 & 5.58 & 50 / 5.58 & 0.09 & 60 / 15.08 & 0.33\\
+%     jeditV1 & 60 / 519.75 & 8.76 & 50 / 7.43 & 0.13 & 60 / 18.13 & 0.41\\
+%     jeditV2 & 70 / 621.32 & 8.98 & 50 / 9.71 & 0.15 & 60 / 17.38 & 0.63\\
+%     log4j & 70 / 125.29 & 1.73 & 50 / 2.90 & 0.06 & 60 / 8.76 & 0.19\\
+%     lucene & 50 / 221.99 & 3.52 & 50 / 5.20 & 0.10 & 50 / 10.09 & 0.33\\
+%     poiV0 & 60 / 327.48 & 5.13 & 50 / 6.56 & 0.11 & 50 / 12.88 & 0.36\\
+%     poiV1 & 50 / 523.85 & 8.95 & 80 / 12.26 & 0.14 & 60 / 19.56 & 0.35\\
+%     synapse & 70 / 148.23 & 1.91 & 60 / 3.96 & 0.06 & 60 / 8.19 & 0.16\\
+%     velocity & 50 / 156.51 & 2.75 & 60 / 4.27 & 0.06 & 50 / 7.70 & 0.22\\
+%     xercesV0 & 60 / 142.83 & 2.01 & 70 / 7.15 & 0.08 & 60 / 9.61 & 0.20\\
+%     xercesV1 & 50 / 751.92 & 12.98 & 60 / 9.28 & 0.16 & 50 / 12.69 & 0.38\\
+
+%   \end{tabular}
+%   \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for F-measure.  }\label{tab:ftimes}
+% \end{table*}
+
+%%%%time for prec %%%%%%
 \begin{table*}[!ht]
-
 \renewcommand{\baselinestretch}{0.75}
@@
   \begin{tabular}{r|c |c |c |c |c |c }
-    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
+    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
     \hline
-    antV0 & 50 / 90.18 & 1.57 & 60 / 4.36 & 0.09 & 50 / 8.12 & 0.18\\
-    antV1 & 50 / 174.67 & 2.90 & 50 / 6.35 & 0.10 & 50 / 11.77 & 0.27\\
-    antV2 & 50 / 403.63 & 6.92 & 70 / 9.71 & 0.16 & 60 / 13.28 & 0.35\\
-    camelV0 & 50 / 537.53 & 8.60 & 50 / 9.14 & 0.18 & 50 / 13.73 & 0.31\\
-    camelV1 & 60 / 1640.54 & 24.57 & 60 / 17.06 & 0.24 & 70 / 31.53 & 0.73\\
-    ivy & 70 / 77.75 & 1.02 & 60 / 3.86 & 0.06 & 50 / 8.00 & 0.17\\
-    jeditV0 & 80 / 472.57 & 5.49 & 60 / 6.30 & 0.09 & 70 / 13.01 & 0.30\\
-    jeditV1 & 60 / 489.45 & 6.82 & 70 / 7.61 & 0.11 & 60 / 12.87 & 0.32\\
-    jeditV2 & 50 / 435.43 & 7.21 & 50 / 6.46 & 0.12 & 90 / 20.34 & 0.37\\
-    log4j & 70 / 113.73 & 1.36 & 70 / 3.25 & 0.05 & 60 / 7.07 & 0.16\\
-    lucene & 70 / 224.39 & 2.70 & 50 / 4.07 & 0.08 & 50 / 8.87 & 0.26\\
-    poiV0 & 60 / 261.06 & 4.00 & 60 / 6.23 & 0.10 & 50 / 10.57 & 0.29\\
-    poiV1 & 80 / 607.85 & 7.18 & 60 / 7.69 & 0.13 & 50 / 11.39 & 0.29\\
-    synapse & 50 / 116.04 & 1.87 & 60 / 4.07 & 0.05 & 70 / 9.74 & 0.16\\
-    velocity & 60 / 195.27 & 2.75 & 60 / 4.49 & 0.06 & 80 / 12.15 & 0.21\\
-    xercesV0 & 60 / 143.69 & 2.17 & 70 / 7.26 & 0.09 & 60 / 10.28 & 0.23\\
-    xercesV1 & 50 / 794.50 & 13.37 & 50 / 8.24 & 0.15 & 60 / 14.54 & 0.38\\
-
+    antV0 & 50 / 95.47 & 1.65 & 60 / 5.08 & 0.08 & 60 / 9.78 & 0.20\\
+    antV1 & 60 / 224.67 & 3.03 & 50 / 6.52 & 0.12 & 60 / 14.13 & 0.25\\
+    antV2 & 70 / 644.99 & 8.24 & 50 / 9.00 & 0.24 & 60 / 16.75 & 0.44\\
+    camelV0 & 70 / 690.62 & 7.93 & 70 / 12.68 & 0.24 & 110 / 28.49 & 0.34\\
+    camelV1 & 60 / 1596.77 & 23.56 & 60 / 17.13 & 0.27 & 70 / 33.96 & 0.77\\
+    ivy & 60 / 66.69 & 0.97 & 60 / 4.26 & 0.07 & 60 / 8.89 & 0.19\\
+    jeditV0 & 80 / 459.30 & 5.33 & 80 / 8.69 & 0.11 & 90 / 18.40 & 0.32\\
+    jeditV1 & 60 / 421.56 & 6.59 & 80 / 9.05 & 0.12 & 80 / 17.93 & 0.36\\
+    jeditV2 & 90 / 595.56 & 6.88 & 60 / 7.90 & 0.14 & 110 / 27.34 & 0.38\\
+    log4j & 50 / 76.09 & 1.33 & 50 / 2.60 & 0.06 & 80 / 9.69 & 0.15\\
+    lucene & 80 / 236.45 & 2.60 & 70 / 6.07 & 0.10 & 60 / 9.77 & 0.25\\
+    poiV0 & 60 / 263.12 & 3.92 & 70 / 7.42 & 0.09 & 130 / 25.86 & 0.28\\
+    poiV1 & 50 / 398.33 & 6.94 & 70 / 9.31 & 0.13 & 50 / 12.67 & 0.29\\
+    synapse & 70 / 144.09 & 1.85 & 50 / 3.88 & 0.07 & 50 / 8.13 & 0.19\\
+    velocity & 60 / 184.10 & 2.68 & 50 / 4.27 & 0.07 & 100 / 15.18 & 0.21\\
+    xercesV0 & 60 / 136.87 & 1.98 & 80 / 9.17 & 0.10 & 70 / 14.17 & 0.22\\
+    xercesV1 & 80 / 1173.92 & 12.78 & 60 / 10.47 & 0.16 & 50 / 18.27 & 0.40\\
   \end{tabular}
-  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for  precision.  }\label{tab:etimes}
+  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for precision.}
+  \label{tab:etimes}
 \end{table*}
+
 %%%%time for F %%%%%%
@@
   \begin{tabular}{r|c |c |c |c |c |c }
-    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
+    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
     \hline
-    antV0 & 50 / 94.08 & 1.71 & 60 / 4.55 & 0.08 & 60 / 10.79 & 0.21\\
-    antV1 & 60 / 193.74 & 3.02 & 70 / 7.77 & 0.09 & 60 / 12.30 & 0.25\\
-    antV2 & 80 / 643.94 & 7.59 & 60 / 8.38 & 0.15 & 70 / 16.99 & 0.41\\
-    camelV0 & 60 / 662.56 & 9.97 & 60 / 13.19 & 0.23 & 80 / 26.11 & 0.32\\
-    camelV1 & 60 / 1800.64 & 24.25 & 50 / 15.02 & 0.28 & 50 / 28.52 & 0.78\\
-    ivy & 60 / 69.95 & 1.03 & 50 / 3.35 & 0.08 & 70 / 9.40 & 0.18\\
-    jeditV0 & 90 / 553.80 & 5.58 & 50 / 5.58 & 0.09 & 60 / 15.08 & 0.33\\
-    jeditV1 & 60 / 519.75 & 8.76 & 50 / 7.43 & 0.13 & 60 / 18.13 & 0.41\\
-    jeditV2 & 70 / 621.32 & 8.98 & 50 / 9.71 & 0.15 & 60 / 17.38 & 0.63\\
-    log4j & 70 / 125.29 & 1.73 & 50 / 2.90 & 0.06 & 60 / 8.76 & 0.19\\
-    lucene & 50 / 221.99 & 3.52 & 50 / 5.20 & 0.10 & 50 / 10.09 & 0.33\\
-    poiV0 & 60 / 327.48 & 5.13 & 50 / 6.56 & 0.11 & 50 / 12.88 & 0.36\\
-    poiV1 & 50 / 523.85 & 8.95 & 80 / 12.26 & 0.14 & 60 / 19.56 & 0.35\\
-    synapse & 70 / 148.23 & 1.91 & 60 / 3.96 & 0.06 & 60 / 8.19 & 0.16\\
-    velocity & 50 / 156.51 & 2.75 & 60 / 4.27 & 0.06 & 50 / 7.70 & 0.22\\
-    xercesV0 & 60 / 142.83 & 2.01 & 70 / 7.15 & 0.08 & 60 / 9.61 & 0.20\\
-    xercesV1 & 50 / 751.92 & 12.98 & 60 / 9.28 & 0.16 & 50 / 12.69 & 0.38\\
-
+    antV0 & 50 / 93.38 & 1.39 & 50 / 3.52 & 0.08 & 70 / 9.89 & 0.17\\
+    antV1 & 60 / 186.95 & 3.18 & 50 / 6.18 & 0.12 & 60 / 13.39 & 0.25\\
+    antV2 & 90 / 654.34 & 8.08 & 60 / 8.79 & 0.18 & 120 / 27.56 & 0.36\\
+    camel & 50 / 543.28 & 9.65 & 80 / 17.00 & 0.28 & 70 / 22.52 & 0.41\\
+    camelV1 & 60 / 1808.03 & 26.98 & 110 / 31.92 & 0.28 & 70 / 37.00 & 0.85\\
+    ivy & 60 / 74.50 & 1.18 & 60 / 4.72 & 0.08 & 60 / 10.39 & 0.21\\
+    jeditV0 & 80 / 518.47 & 6.11 & 60 / 7.9
+ & 0.10 & 60 / 14.32 & 0.37\\
+    jeditV1 & 70 / 576.29 & 6.89 & 70 / 8.13 & 0.10 & 70 / 17.42 & 0.34\\
+    jeditV2 & 80 / 657.59 & 7.93 & 70 / 10.34 & 0.15 & 80 / 20.20 & 0.40\\
+    log4j & 70 / 123.48 & 1.59 & 50 / 2.92 & 0.08 & 50 / 7.67 & 0.17\\
+    lucene & 60 / 219.02 & 3.68 & 60 / 6.89 & 0.12 & 70 / 13.06 & 0.35\\
+    poiV0 & 60 / 314.53 & 4.82 & 60 / 7.80 & 0.10 & 80 / 19.29 & 0.32\\
+    poiV1 & 50 / 446.05 & 7.55 & 50 / 7.62 & 0.14 & 110 / 27.23 & 0.36\\
+    synapse & 60 / 138.75 & 1.83 & 60 / 4.87 & 0.08 & 90 / 13.29 & 0.17\\
+    velocity & 60 / 211.88 & 3.13 & 60 / 5.51 & 0.10 & 60 / 11.58 & 0.27\\
+    xercesV0 & 80 / 178.49 & 2.02 & 60 / 7.47 & 0.11 & 80 / 17.31 & 0.28\\
+    xercesV1 & 80 / 1370.89 & 14.42 & 60 / 11.07 & 0.19 & 80 / 25.27 & 0.46\\
   \end{tabular}
-  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for F-measure.  }\label{tab:ftimes}
+  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for F-Measure.}
+\label{tab:ftimes}
 \end{table*}

### 2016-01-06 tuningpredictor.tex
update all figures!
Updates from ShareLaTeX

@@
 software defect predictors, this  method can quickly
-find tunings  that  alter detection  precision  
- from 2\% to 98\%.
+find tunings  that  alter detection  F-Measure  
+ from 12\% to 78\%.
 
@@
  examples of truly dramatic improvement:
- usually by 5 to 20\% and often by much more (in one extreme case, precision improved from 2\% to 98\%).
+ usually by 5 to 20\% and often by much more (in one extreme case, F-Measure improved from 12\% to 78\%).
 \item RQ2: {\em Does tuning change conclusions on what learners are better than others?} 
@@
 And, 
-in $\frac{13}{17}$ cases, the   untuned Random Forest performs better than or equal to untuned CART.  
+in $\frac{14}{17}$ cases, the  untuned Random Forest performs better than or equal to untuned CART in terms of precision.  
 % Note that the size of the improvement is sometimes small; e.g. the precision results improve more than the ``F'' measure.
@@
 That said,  tuning can improve those poor performing detectors.
-In some cases, the median changes may be small (e.g. the ``F'' results for WHERE) but even in
+In some cases, the median changes may be small (e.g. the ``F'' results for WHERE and Random Forests) but even in
 those cases, there are enough large changes to motivate the use of tuning. For example:
@@
 \item
-For WHERE's ``F'' improvement, there are two improvements over 70\%;
-\item
-Regarding precision, 
-for {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
-A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
-In those two data sets, nearly all the precision values are   low {\em except} for
-tuned WHERE that scored 89\% and 85\%.
-Finally, note the  {\em jeditV2} result for the WHERE learner.
-Here, tuning changes precision from 2\% to 98\%.
+For ``F'' improvement, there are two improvements over 50\% for both WHERE and Random Forests.
+Also, in {\em camelV0}, all untuned learners report ``F'' of under 10\%, tuning changes those scores over 25\%.
+Finally, note the  {\em poiV1} result for the WHERE learner.
+Here, tuning changes precision from 12\% to 78\%.
+\item
+Regarding precision, for {\em antV1, antV2, camelV0} and {\em synapse}, untuned WHERE reports precision of 0. But tuned WHERE scores 60, 55, 30 and 50(the similar pattern can seen in ``F'').
+
 \ei
@@
 tuned CART are better than or equal
-to tuned Random Forest in $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
+to tuned Random Forest in $\frac{12}{17}$ and $\frac{10}{17}$ data sets in
 terms of precision and F-measure, respectively. Results from the non-parametric
@@
 number of methods inherited by a class plus the number of methods accessible by member methods of the class.
-For both goals (precision and ``F'') {\em mfa} is selected for 9 and 5 data sets,
+For both goals (precision and ``F'') {\em mfa} is selected for 8 and 5 data sets,
 for the untuned and tuned data miner (respectively).
@@
 \hline
-    CART & - & 0.42 & - & 0.24 \\
-    R. Forest &  0.29 & 0.18 & 0.24 & 0.29 \\
+    CART & - & 0.41 & - & 0.24 \\
+    R. Forest &  0.12 & 0.35 & 0.18 & 0.18 \\
   \end{tabular}
@@
 That improvement is usually positive (see \fig{deltas}) and sometimes
-it can be quite   dramatic (e.g. precision changing from 2\% to 98\%). \item 
+it can be quite   dramatic (e.g. ``F'' changing from 12\% to 78\%). \item 
 Tuning changes conclusions on what learners are better than others.
@@
 
+  %%%%parameters for F %%%%%%
+\begin{table*}[!ht]
+
+\resizebox{\textwidth}{!}{
+% \renewcommand{\baselinestretch}{0.9}
+\scriptsize
+\centering
+  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+    \hline
+
+  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
+ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+& threshold& 0.5& 0.04& 0.44& 0.44& 0.98& 0.65& 0.77& 1& 0.65& 0.98& 0.44& 0.44& 0.87& 0.04& 0.77& 0.24& 0.44& 0.77\\ \cline{2-20}
+& infoPrune& 0.33& 0.51& 0.68& 0.88& 0.47& 0.07& 0.31& 0.48& 0.68& 0.57& 0.12& 0.68& 0.01& 0.51& 0.14& 0.54& 0.68& 0.14\\ \cline{2-20}
+& min\_sample\_size& 4& 6& 4& 6& 1& 6& 8& 8& 4& 6& 7& 4& 9& 6& 2& 8& 4& 8\\ \cline{2-20}
+& min\_Size& 0.5& 0.18& 0.4& 0.56& 0.51& 0.65& 0.59& 0.97& 0.4& 0.51& 0.8& 0.4& 0.77& 0.18& 0.62& 0.46& 0.4& 0.66\\ \cline{2-20}
+& wriggle& 0.2& 0.25& 0.29& 0.76& 0.6& 0.63& 0.26& 1& 0.51& 0.17& 0.36& 0.51& 0.83& 0.25& 0.5& 0.52& 0.29& 0.26\\ \cline{2-20}
+& depthMin& 2& 3& 3& 3& 1& 5& 3& 2& 3& 5& 5& 3& 4& 3& 3& 3& 3& 3\\ \cline{2-20}
+& depthMax& 10& 16& 15& 15& 8& 19& 10& 7& 15& 5& 15& 15& 19& 16& 6& 19& 15& 10\\ \cline{2-20}
+& wherePrune& False& False& True& True& True& True& True& True& False& False& True& True& True& False& True& False& False& True\\ \cline{2-20}
+& treePrune& True& False& True& True& False& False& False& False& False& True& True& True& False& False& False& True& True& False\\ \cline{2-20}
+\hline
+\multirow{5}{*}{CART}
+& threshold& 0.5& 0.34& 0.25& 0.01& 0.01& 0.73& 0.53& 0.92& 0.8& 0.74& 0.54& 0.03& 0.91& 0.01& 0.01& 0.55& 1& 0.01\\ \cline{2-20}
+& max\_feature& None& 0.01& 0.01& 0.29& 0.01& 0.46& 0.75& 0.79& 0.74& 0.41& 0.81& 0.61& 0.72& 0.01& 0.01& 0.01& 0.25& 0.18\\ \cline{2-20}
+& min\_samples\_split& 2& 18& 20& 12& 2& 15& 11& 2& 18& 13& 9& 17& 16& 10& 4& 8& 3& 15\\ \cline{2-20}
+& min\_samples\_leaf& 1& 19& 16& 15& 17& 1& 1& 13& 10& 4& 3& 7& 5& 20& 7& 8& 1& 6\\ \cline{2-20}
+& max\_depth& None& 12& 2& 15& 1& 41& 20& 44& 15& 13& 5& 23& 14& 1& 5& 17& 47& 13\\ \cline{2-20}
+\hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+& threshold& 0.5& 0.01& 0.35& 0.3& 0.01& 0.9& 0.97& 0.63& 1& 0.73& 0.68& 0.01& 1.0& 0.01& 0.07& 0.22& 1& 0.82\\ \cline{2-20}
+& max\_feature& None& 0.63& 0.17& 0.01& 0.01& 0.88& 0.74& 0.76& 0.73& 0.01& 0.03& 0.39& 0.02& 0.01& 0.56& 0.36& 0.51& 0.89\\ \cline{2-20}
+& max\_leaf\_nodes& None& 40& 33& 46& 22& 11& 16& 38& 34& 30& 31& 12& 49& 25& 47& 15& 39& 24\\ \cline{2-20}
+& min\_samples\_split& 2& 10& 16& 20& 1& 1& 1& 1& 4& 20& 19& 11& 14& 2& 17& 19& 20& 19\\ \cline{2-20}
+& min\_samples\_leaf& 1& 4& 15& 9& 13& 18& 11& 3& 16& 17& 6& 10& 7& 19& 13& 11& 2& 14\\ \cline{2-20}
+& n\_estimators& 100& 120& 73& 75& 130& 97& 144& 125& 97& 80& 111& 96& 101& 50& 67& 74& 63& 66\\ \cline{2-20}
+\hline  \end{tabular}
+}
+  \caption{Parameters tuned on different models over the objective of ``F''.}\label{tab:fselect}
+\end{table*}
+
 \end{document}

### 2016-01-13 tuningpredictor.tex

@@
-\documentclass{sig-alternative}
+% \documentclass{sig-alternative}
 % \documentclass[conference]{IEEEtran}
+\documentclass[smallextended]{svjour3}
 \usepackage{multirow}
@@
 \begin{document}
-% \conferenceinfo{FSE}{'15 Bergamo, Italy}
+
 \title{ Tuning for Software Analytics: is it Really Necessary?}
 % \numberofauthors{1}
-\author{\alignauthor Wei Fu, Tim Menzies, Xipeng Shen \\
-       \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
-       fuwei.ee, tim.menzies@gmail.com, xshen5@ncsu.edu }
+\author{Wei Fu \and Tim Menzies \and Xipeng Shen}
+\institute{North Carolina State University, Raleigh, NC, USA
+      Wei Fu \email{w}}
+% \email{fuwei.ee \and tim.menzies@gmail.com \and xshen5@ncsu.edu }
 \maketitle 
@@
   Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
-antV0 & 24 &   & 35 &   & 27 &   & {\bf 60} &   & 28 &   & 44 &  \\
-antV1 & 0 &   & {\bf 60} &   & 36 &   & 56 &   & 41 &   & 50 &  \\
-antV2 & 0 &   & 55 &   & 52 &   & 52 &   & 64 &   & {\bf 67} &  \\
-camelV0 & 0 &   & 30 &   & 26 &   & 50 &   & 50 &   & {\bf 79} &  \\
-camelV1 & 27 &   & {\bf 28} &   & 24 &   & {\bf 28} &   & 25 &   & 27 &  \\
-ivy & 18 &   & 21 &   & 17 &   & {\bf 26} &   & 16 &   & 20 &  \\
-jeditV0 & 35 &   & 37 &   & 49 &   & {\bf 78} &   & 44 &   & 60 &  \\
-jeditV1 & 24 &   & 42 &   & 28 &   & {\bf 64} &   & 28 &   & 37 &  \\
-jeditV2 & 2 &   & {\bf 22} &   & 3 &   & 17 &   & 5 &   & 6 &  \\
-log4j & 94 &   & 91 &   & 97 &   & 98 &   & 99 &   & {\bf 100} &  \\
-lucene & 60 &   & 75 &   & 67 &   & 70 &   & 67 &   & {\bf 77} &  \\
-poiV0 & 72 &   & 70 &   & 79 &   & 71 &   & {\bf 83} &   & 69 &  \\
-poiV1 & 90 &   & 76 &   & 73 &   & 90 &   & 82 &   & {\bf 100} &  \\
-synapse & 0 &   & 50 &   & 71 &   & {\bf 100} &   & 65 &   & 60 &  \\
-velocity & 34 &   & {\bf 44} &   & 34 &   & {\bf 44} &   & 34 &   & 42 &  \\
-xercesV0 & 12 &   & {\bf 17} &   & 14 &   & 14 &   & 15 &   & 14 &  \\
-xercesV1 & 53 &   & 54 &   & 49 &   & {\bf 100} &   & 49 &   & 27 &  \\
+antV0 & 0 &   & 35 &   & 15 &   & {\bf 60} &   & 21 &   & 44 &  \\
+antV1 & 0 &   & 60 &   & 54 &   & 56 &   & {\bf 67} &   & 50 &  \\
+antV2 & 45 &   & 55 &   & 42 &   & 52 &   & 56 &   & {\bf 67} &  \\
+camelV0 & 20 &   & 30 &   & 30 &   & 50 &   & 28 &   & {\bf 79} &  \\
+camelV1 & 27 &   & 28 &   & {\bf 38} &   & 28 &   & 34 &   & 27 &  \\
+ivy & 25 &   & 21 &   & 21 &   & {\bf 26} &   & 23 &   & 20 &  \\
+jeditV0 & 34 &   & 37 &   & 56 &   & {\bf 78} &   & 52 &   & 60 &  \\
+jeditV1 & 30 &   & 42 &   & 32 &   & {\bf 64} &   & 32 &   & 37 &  \\
+jeditV2 & 4 &   & {\bf 22} &   & 6 &   & 17 &   & 4 &   & 6 &  \\
+log4j & 96 &   & 91 &   & 95 &   & 98 &   & 95 &   & {\bf 100} &  \\
+lucene & 61 &   & 75 &   & 67 &   & 70 &   & 63 &   & {\bf 77} &  \\
+poiV0 & 70 &   & 70 &   & 65 &   & {\bf 71} &   &  67 &   & 69 &  \\
+poiV1 & 74 &   & 76 &   & 72 &   & 90 &   & 78 &   & {\bf 100} &  \\
+synapse & 61 &   & 50 &   & 50 &   & {\bf 100} &   & 60 &   & 60 &  \\
+velocity & 34 &   & {\bf 44} &   & 39 &   & {\bf 44} &   & 40 &   & 42 &  \\
+xercesV0 & 14 &   & 17 &   & 17 &   & 14 &   & {\bf 28} &   & 14 &  \\
+xercesV1 & 86 &   & 54 &   & 72 &   & {\bf 100} &   & 78 &   & 27 &  \\
 \end{tabular}
@@
   Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
-antV0 & 23 &   & 20 &   & 32 &   & 40 &   & {\bf 41} &   & 38 &  \\
-antV1 & 0 &   & 38 &   & 38 &   & {\bf 49} &   & 37 &   & {\bf 49} &  \\
-antV2 & 0 &   & 50 &   & 44 &   &  49 &   & 47 &   & {\bf 56} &  \\
-camelV0 & 0 &   & 28 &   & 9 &   & 28 &   & 4 &   & {\bf 30} &  \\
-camelV1 & 35 &   & 34 &   & 31 &   & 32 &   & {\bf 37} &   & 33 &  \\
-ivy & 30 &   & 34 &   & 28 &   & {\bf 40} &   & 27 &   &  33 &  \\
-jeditV0 & 51 &   & 47 &   & 56 &   & 57 &   & 56 &   & {\bf 59} &  \\
-jeditV1 & 35 &   & 44 &   & 36 &   & 47 &   & 43 &   & {\bf 48} &  \\
-jeditV2 & 4 &   & {\bf 11} &   & 5 &   & 10 &   & 9 &   & 9 &  \\
-log4j & 54 &   & 50 &   & 47 &   & 37 &   & {\bf 57} &   & 47 &  \\
-lucene & 72 &   & 73 &   & 56 &   & 72 &   & 70 &   & {\bf 76} &  \\
-poiV0 & 78 &   & 74 &   & {\bf 79} &   & 64 &   & 77 &   & 77 &  \\
-poiV1 & 12 &   & {\bf 78} &   & 21 &   & 69 &   & 19 &   & {\bf 78} &  \\
-synapse & 0 &   & 56 &   & 40 &   & {\bf 60} &   & 41 &   & 53 &  \\
-velocity & 51 &   & {\bf 53} &   & 49 &   & 51 &   & 51 &   & 51 &  \\
-xercesV0 & 20 &   & 22 &   & 21 &   & {\bf 26} &   & 24 &   & 21 &  \\
-xercesV1 & 25 &   & 70 &   & 18 &   & 35 &   & 18 &   & {\bf 71} &  \\
+antV0 & 0 &   & 20 &   & 20 &   & {\bf 40} &   & 28 &   & 38 &  \\
+antV1 & 0 &   & 38 &   & 37 &   & {\bf 49} &   & 38 &   & {\bf 49} &  \\
+antV2 & 47 &   & 50 &   & 45 &   &  49 &   & {\bf 57} &   & 56 &  \\
+camelV0 & 31 &   & 28 &   & 39 &   & 28 &   & {\bf 40} &   & 30 &  \\
+camelV1 & 34 &   & 34 &   & 38 &   & 32 &   & {\bf 42} &   & 33 &  \\
+ivy & 39 &   & 34 &   & 28 &   & {\bf 40} &   & 35 &   &  33 &  \\
+jeditV0 & 45 &   & 47 &   & 56 &   & 57 &   & {\bf 63} &   & 59 &  \\
+jeditV1 & 43 &   & 44 &   & 44 &   & 47 &   & 46 &   & {\bf 48} &  \\
+jeditV2 & 8 &   & {\bf 11} &   & 10 &   & 10 &   & 8 &   & 9 &  \\
+log4j & 47 &   & 50 &   & 53 &   & 37 &   & {\bf 60} &   & 47 &  \\
+lucene & 73 &   & 73 &   & 65 &   & 72 &   & 70 &   & {\bf 76} &  \\
+poiV0 & 50 &   & 74 &   & 31 &   & 64 &   & 45 &   & {\bf 77} &  \\
+poiV1 & 75 &   & {\bf 78} &   & 68 &   & 69 &   & 77 &   & {\bf 78} &  \\
+synapse & 49 &   & 56 &   & 43 &   & {\bf 60} &   & 52 &   & 53 &  \\
+velocity & 51 &   & 53 &   & 53 &   & 51 &   & {\bf 56} &   & 51 &  \\
+xercesV0 & 19 &   & 22 &   & 19 &   & {\bf 26} &   & 34 &   & 21 &  \\
+xercesV1 & 32 &   & 70 &   & 34 &   & 35 &   & 42 &   & {\bf 71} &  \\
 \end{tabular}

### 2016-01-14 tuningpredictor.tex

@@
 software defect predictors, this  method can quickly
-find tunings  that  alter detection  F-Measure  
- from 12\% to 78\%.
+find tunings  that  alter detection  precision
+ from 0\% to 60\%.
 
@@
 that are readily available to researchers~\cite{rod12}.
-For example, at the time of this writing (Aug  2015), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
+For example, at the time of this writing (Jan 2016), our web searches show that Mozilla Firefox has over 1.1 million bug reports, and platforms such as GitHub host over 14 million projects.
 
@@
  examples of truly dramatic improvement:
- usually by 5 to 20\% and often by much more (in one extreme case, F-Measure improved from 12\% to 78\%).
+ usually by 5 to 20\% and often by much more (in one extreme case,  precision improved from 0\% to 60\%).
 \item RQ2: {\em Does tuning change conclusions on what learners are better than others?} 
@@
 Are the impacts of tuning addressed in the defect prediction literature?
-To answer that question,  in August 2015 we searched scholar.google.com for the conjunction of  "data mining" and "software engineering" and  "defect prediction"\footnote{https://goo.gl/Inl9nF}.
+To answer that question,  in Jan 2016 we searched scholar.google.com for the conjunction of ``data mining" and ``software engineering" and  ``defect prediction"\footnote{More details can be found at https://goo.gl/Inl9nF}.
 After sorting by the citation count and discarding the non-SE papers (and those without a pdf link), we read over this sample
@@
 {\scriptsize
-\begin{tabular}{c|l|p{4.7in}}
+\begin{tabular}{c|l|p{0.5\textwidth}}
 amc & average method complexity & e.g. number of JAVA byte codes\\\hline
@@
 
-There  are ways to make defect predictors
+There are several ways to make defect predictors
 using  CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
@@
   \centering
-	\begin{tabular}{|c|c|c|c|l|}
+	\begin{tabular}{|c|c|c|c|p{5cm}|}
 	\cline{1-5}
@@
 \multicolumn{1}{c|}{Description} \\ \hline
-	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
+ 	\multirow{8}{*}{%\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}
+ 	WHERE} 
 	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
@@
 	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_samples\_leaf 
-in the initial clustering tree  using  ${n\_samples}^ {min\_Size}$.
+in the initial clustering tree\\  using ${n\_samples}^ {min\_Size}$.
 \end{tabular} \\ \cline{2-5} 
@@
 	 \hline 
-Logistic 	 Regression&\multicolumn{4}{l|}{This study uses untuned LR in order to check
-a conclusion of~\cite{hall11}. }\\\hline
+% Logistic\\ Regression&\multicolumn{4}{c|}{This study uses untuned LR in order to check
+% a conclusion of~\cite{hall11}. }\\\hline
 
@@
 a current {\em Population}.  Our DE's lose one ``life''
-when the new population is no better than  current one (terminating when ``life'' is zero)$^{4}$.
+when the new population is no better than  current one (terminating when ``life'' is zero)$^{L4}$.
 Each candidate solution in the {\em Population}  
@@
 \tab{parameters} and {\em Scores} come from training a learner using those parameters
-and applying it     test data$^{23-27}$.
-
-The premise of DE  is that the best way to mutate existing tunings
-is to {\em Extrapolate}$^{28}$
+and applying it     test data$^{L23-L27}$.
+
+The premise of DE  is that the best way to mutate the existing tunings
+is to {\em Extrapolate}$^{L28}$
 between current solutions.  Three solutions $a,b,c$ are selected at random.
@@
 the old tuning $x_i$ with $y_i$. For booleans, we use $y_i= \neg x_i$ (see line 36). For numerics, $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
-controlling  cross-over.  The {\em trim} function$^{38}$ limits the new
+controlling  cross-over.  The {\em trim} function$^{L38}$ limits the new
 value to the legal range min..max of that parameter.
 
-The main loop of DE$^{6}$ runs over the {\em Population}, replacing old items
+The main loop of DE$^{L6}$ runs over the {\em Population}, replacing old items
 with new {\em Candidate}s (if  new candidate is better).
@@
 values from a data mining, from which a {\em Goal} function extracts one 
-performance value$^{26}$ (so we run this code many times, each time with
-a different {\em Goal}$^{1}$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
+performance value$^{L26}$ (so we run this code many times, each time with
+a different {\em Goal}$^{L1}$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).
 
@@
 For this experiment, we use data sets with at least three  
-consecutive releases  (where release $i+1$ was built after release $i$).
+consecutive releases  (where release $i+1$ was built after release $i$). When tuning a learner,
 \bi 
-\item The {\em first} release was used for some  {\em training}, to collect a baseline
-   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
+% \item {\em Tuned learner}: the {\em first} release is used  on line 24 of Algorithm~\ref{alg:DE} to
+%   build some model using some the tunings found in some {\em Candidate}. The {\em second} release was used on line 25 of Algorithm~\ref{alg:DE} to 
+%   test the model found on line 24. The {\em third} release was used as a testing data to gather the performance statistics
+%   reported below from the best model found by DE.
+% \item {\em untuned learner}:
+
+\item The {\em first} release was used  on line 24 of Algorithm~\ref{alg:DE} to
    build some model using some the tunings found in some {\em Candidate}.
  \item The {\em second} release was used on line 25 of Algorithm~\ref{alg:DE} to 
-   test the model found on line 24.
+   test the candidate model found on line 24.
    \item Finally the {\em third} release was used to gather the performance statistics
-   reported below from (a)~the model generated by the untuned learner or (b)~the
-   best model found by DE.
+   reported below from the best model found by DE.
  \ei
+
+ To be fair for the untuned learner, the {\em first} and {\em second} releases used in tuning experiments
+ will be combined as the training data to build a model. Then the performance of this untuned learner 
+ will be evaluated by the same {\em third} release.
+
 % This approach ensures   all treatments 
@@
 
-As an aside, an alternate experimental design would be to 
-learn a baseline learner from the first {\em and} second release
-instead of, as shown above,  just the first release. On the one hand,
-this would mean that the baseline could be learned from more data.
-On the other hand, this adds a conflation to our experimental design
-since the optimizer uses the second release for pruning, not growing a data set.  Happily, from 
-piror work~\cite{Menzies:2008aa} we know that defect predictors usually {\em saturates} (i.e.
-does not generate better predictors) after 100 examples, which is a number smaller than all our first release data sets. Hence, their would
-be little value in generating the baselines using the first and second
-releases.
+% As an aside, an alternate experimental design would be to 
+% learn a baseline learner from the first {\em and} second release
+% instead of, as shown above,  just the first release. On the one hand,
+% this would mean that the baseline could be learned from more data.
+% On the other hand, this adds a conflation to our experimental design
+% since the optimizer uses the second release for pruning, not growing a data set.  Happily, from 
+% piror work~\cite{Menzies:2008aa} we know that defect predictors usually {\em saturates} (i.e.
+% does not generate better predictors) after 100 examples, which is a number smaller than all our first release data sets. Hence, their would
+% be little value in generating the baselines using the first and second
+% releases.
 
@@
 And, 
-in $\frac{14}{17}$ cases, the  untuned Random Forest performs better than or equal to untuned CART in terms of precision.  
+in $\frac{12}{17}$ cases, the  untuned Random Forest performs better than or equal to untuned CART in terms of precision.  
 % Note that the size of the improvement is sometimes small; e.g. the precision results improve more than the ``F'' measure.
@@
 \item
-For ``F'' improvement, there are two improvements over 50\% for both WHERE and Random Forests.
-Also, in {\em camelV0}, all untuned learners report ``F'' of under 10\%, tuning changes those scores over 25\%.
-Finally, note the  {\em poiV1} result for the WHERE learner.
-Here, tuning changes precision from 12\% to 78\%.
-\item
-Regarding precision, for {\em antV1, antV2, camelV0} and {\em synapse}, untuned WHERE reports precision of 0. But tuned WHERE scores 60, 55, 30 and 50(the similar pattern can seen in ``F'').
+For ``F'' improvement, there are two improvements over 25\% for both WHERE and Random Forests.
+Also, in {\em poiV0}, all untuned learners report ``F'' of under 50\%, tuning changes those scores by 25\%.
+Finally, note the  {\em xercesV1} result for the WHERE learner.
+Here, tuning changes precision from 32\% to 70\%.
+\item
+Regarding precision, for {\em antV0}, and {\em antV1} untuned WHERE reports precision of 0. But tuned WHERE scores 35 and 60 (the similar pattern can seen in ``F'').
 
@@
 tuned CART are better than or equal
-to tuned Random Forest in $\frac{12}{17}$ and $\frac{10}{17}$ data sets in
-terms of precision and F-measure, respectively. Results from the non-parametric
+to tuned Random Forest in $\frac{12}{17}$ and $\frac{7}{17}$ data sets in
+terms of precision and F-measure, respectively. Prior to tuning experiments, those
+numbers are $\frac{5}{17}$ and $\frac{1}{17}$. Results from the non-parametric
 Kolmogorov-Smirnov(KS) Test show that the performance 
@@
 That improvement is usually positive (see \fig{deltas}) and sometimes
-it can be quite   dramatic (e.g. ``F'' changing from 12\% to 78\%). \item 
+it can be quite   dramatic (e.g. precision changing from 0 to 60\%). \item 
 Tuning changes conclusions on what learners are better than others.

### 2016-01-14 tuningpredictor.tex
changed all results and texts based on the new results.

@@
 
+%  \begin{table*}[!t]
+
+% \renewcommand{\baselinestretch}{0.8}
+% \scriptsize
+% \centering
+%   \begin{tabular}{c c c c c c c c c c }\hline
+%   Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
+% \\\hline
+%   training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
+% \\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
+% \\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
+% \\ \hline
+%   Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
+% \\\hline
+%   training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
+% \\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
+% \\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
+% \\  \end{tabular}
+
+%   \caption{Data used in this experiment. 
+%   E.g., the top left data set has 20 defective classes out of 125 total.
+%   See \tion{dataa} for explanation of {\em training, tuning, testing} sets.
+%   }\label{tab:data1}
+% \end{table*}
+
  \begin{table*}[!t]
@@
 \centering
-  \begin{tabular}{c c c c c c c c c c }\hline
+  \begin{tabular}{p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}}\hline
   Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
@@
 \renewcommand{\baselinestretch}{0.8} 
-
+% \centering
 \scriptsize
@@
 \renewcommand{\baselinestretch}{0.8} 
-
+% \centering
 \scriptsize  
@@
 \begin{figure}[!t]
-\begin{center}
+% \begin{center}
 \includegraphics[width=1.5in]{./eps/LR_untuned.eps}\includegraphics[width=1.5in]{./eps/LR_tuned.eps}
- \end{center}
+%  \end{center}
 \caption{Comparison between Logistic Regression and Random Forest before and after tuning. }\label{fig:lr}
@@
  In a result that might have been predicted by Hall et al., Logistic Regression does perform better than untuned Random
-Forests over 17 data sets. 
+Forests over 13 out of 17 data sets. 
 However, it turns out that advice is sensitive to the tunings
@@
 \scriptsize
-\centering
+% \centering
   \begin{tabular}{c|p{1in}|p{1in}}
@@
 \begin{figure}[!t]
-\begin{center}
+% \begin{center}
 \includegraphics[width=1.5in]{./eps/np_precision.eps}\includegraphics[width=1.5in]{./eps/np_f.eps}
- \end{center}
+%  \end{center}
 \caption{Deltas in performance between {\em np = 10} and the recommended np's.
@@
 \scriptsize
-\centering
+% \centering
   \begin{tabular}{c|c c|cc}
@@
 \begin{figure}[!t]
-\begin{center}
+% \begin{center}
 \includegraphics[width=1.5in]{./eps/features_precision.eps}\includegraphics[width=1.5in]{./eps/features_F.eps}
- \end{center}
+%  \end{center}
 \caption{Four representative tuning values in WHERE with  precision and F-measure as the tuning goal, respectively.   }\label{fig:features}

### 2016-01-18 tuningpredictor.tex
Updates from ShareLaTeX

@@
 
+\section{Digression}
+
+Before starting, we offer the following aside.
+An important principle in tuning is that
+{\em you can't always get \underline{all} you want}.
+In the following, we present tuning as a multi-objective optimization problem
+and, with some problems, it is not always possible to optimize for every goals.
+For example, the following text does not
+show results for tuning on recall
+or false alarms since otpimizing {\em only} for those goals can lead
+to some undesirable side effects. For example: 
+\bi
+\item
+{\em Recall} reports the percentage of  predictions that are actual examples of  what we are looking for.
+When we tune for {\em recall}, we can achieve near
+100\% recall-- but the cost of a near 100\% false alarms.
+\item
+{\em False alarms} is the percentage of other examples that are reported  (by the learner)
+to be part of the targeted examples.
+When we tune for {\em false alarms}, we 
+can achieve near zero percent false alarm rates by effectively turning off
+the detector (so the  recall falls to nearly zero).
+\ei
+Accordingly,  this paper  explores performance measures that comment on all 
+target classes (see the  precision and ``F'' measures discussed in \fig{xxx}).
+
 \section{Preliminaries}
+
 \subsection{Issues of Tuning: Important and Ignored?}
@@
 
-The formal definition of data mining stresses that these learners are heuristic explorers
-of a truly   vast space of the possible models within a data set~\cite{mitchell1982generalization}. For example, given 20 columns of boolean variables,
-there are $2^{20}$ possible models. Data mining is practical since various heuristics
-allow automatic algorithms to ignore most of those possibilities. While heuristic search makes data mining possible, it also means that tunings
-can significantly affect what comes out of a data miner.
 When we tune a data miner, what we are really doing is changing how a learner applies
@@
 
-\subsection{An Aside}
-
-One comment before presenting the results. The following text does not
-show results for tuning on recall
-or false alarms. Those goals focus on {\em only}
-the  defective or non-defective modules (respectively). Hence,
-when DE tunes for recall, we can achieve near
-100\% recall-- but the cost of a near 100\% false alarms.
-Similarly,  tuning
-can achieve near zero false alarm rates by effectively turning off
-the detector (when recall is zero).
-Accordingly,  this paper  explores performance measures that comment on all 
-target classes (i.e. precision and ``F'').
-
 \section{Experimental Results}
@@
 
-\begin{figure}[!t]
-% \begin{center}
-\includegraphics[width=1.5in]{./eps/LR_untuned.eps}\includegraphics[width=1.5in]{./eps/LR_tuned.eps}
-%  \end{center}
-\caption{Comparison between Logistic Regression and Random Forest before and after tuning. }\label{fig:lr}
- \end{figure}
-
 Secondly, while we are critical of the results of
@@
 
+\begin{figure}[!t]
+% \begin{center}
+\includegraphics[width=1.5in]{./eps/LR_untuned.eps}\includegraphics[width=1.5in]{./eps/LR_tuned.eps}
+%  \end{center}
+\caption{Comparison between Logistic Regression and Random Forest before and after tuning. }\label{fig:lr}
+ \end{figure}
+
 That said, our tuning results show that it is time to revise
 the recommendations of those papers. 
-  \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forest).
- In a result that might have been predicted by Hall et al., Logistic Regression does perform better than untuned Random
-Forests over 13 out of 17 data sets. 
+  \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forest)L
+  \bi
+  \item
+ In a result that might have been predicted by Hall et al.,  
+ untuned Random
+Forests performs comparatively worse than
+ Logistic Regression. Specifically, untuned
+ Random Forest performs worse than Linear regression in in 13 out of   17 data sets. 
+\item
 However, it turns out that advice is sensitive to the tunings
-used with Random Forest. After tuning, we find that Random Forest
-is often competitive, and sometimes even better, than Logistic Regression.
+used with Random Forest. After tuning, we find that tuned Random Forest
+loses to Logistic Regression in only 6 out of 17 data sets. 
+\ei
 
@@
 
+ \subsection{RQ3: Does Tuning Select Different Project Factors? }\label{sect:import}
+
+Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,Moser:2008,zimmermann2007predicting,herzig2013predicting}. 
+\tab{features} comments that such tests are unreliable since the factors selected by a data miner are much altered before and 
+after tuning.
+
+\tab{features} shows what features are found in the trees generated by the WHERE algorithm
+(bold shows the features found by the trees from tuned WHERE; plain text shows the features seen
+in the untuned study). Note that different features are selected depending on whether or not
+we tune an algorithm.
+
 % list some features
-\begin{table}[!b]
+\begin{table}[!t]
 
@@
 \end{table}
-
- \subsection{RQ3: Does Tuning Select Different Project Factors? }\label{sect:import}
-
-Researchers often use data miners to  test what factors have most impact on software projects~\cite{bell2013limited,rahman2013how,me02k,Moser:2008,zimmermann2007predicting,herzig2013predicting}. 
-\tab{features} comments that such tests are unreliable since the factors selected by a data miner are much altered before and 
-after tuning.
-
-\tab{features} shows what features are found in the trees generated by the WHERE algorithm
-(bold shows the features found by the trees from tuned WHERE; plain text shows the features seen
-in the untuned study). Note that different features are selected depending on whether or not
-we tune an algorithm.
 

### 2016-01-21 dm101.tex
change to IST format

@@
 
+\begin{table*}[t]
+\renewcommand{\baselinestretch}{0.8}\begin{center}
+{\scriptsize
+\begin{tabular}{c|l|p{0.5\textwidth}}
+amc & average method complexity & e.g. number of JAVA byte codes\\\hline
+avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
+in class\\\hline
+ca & afferent couplings & how many other classes use the specific
+class. \\\hline
+cam & cohesion amongst classes & summation of number of different
+types of method parameters in every method divided by a multiplication
+of number of different method parameter types in whole class and
+number of methods. \\\hline
+cbm &coupling between methods &  total number of new/redefined methods
+to which all the inherited methods are coupled\\\hline
+cbo & coupling between objects & increased when the methods of one
+class access services of another.\\\hline
+ce & efferent couplings & how many other classes is used by the
+specific class. \\\hline
+dam & data access & ratio of the number of private (protected)
+attributes to the total number of attributes\\\hline
+dit & depth of inheritance tree &\\\hline
+ic & inheritance coupling &  number of parent classes to which a given
+class is coupled (includes counts of methods and variables inherited)
+\\\hline
+lcom & lack of cohesion in methods &number of pairs of methods that do
+not share a reference to an instance variable.\\\hline
+locm3 & another lack of cohesion measure & if $m,a$ are  the number of
+$methods,attributes$
+in a class number and $\mu(a)$  is the number of methods accessing an
+attribute, 
+then
+$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
+\\\hline
+loc & lines of code &\\\hline
+max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
+in class\\\hline
+mfa & functional abstraction & number of methods inherited by a class
+plus number of methods accessible by member methods of the
+class\\\hline
+moa &  aggregation &  count of the number of data declarations (class
+fields) whose types are user defined classes\\\hline
+noc &  number of children &\\\hline
+npm & number of public methods & \\\hline
+rfc & response for a class &number of  methods invoked in response to
+a message to the object.\\\hline
+wmc & weighted methods per class &\\\hline
+\rowcolor{lightgray}
+defect & defect & Boolean: where defects found in post-release bug-tracking systems.
+\end{tabular}
+}
+\end{center}
+\caption{OO measures used in our defect data sets.}\label{tab:ck}
+\end{table*}
+
 {\em Easy to use:} Static code attributes can be automatically collected, even for very large systems~\cite{nagappan05}.
@@
 which can be as large as four or six people~\cite{me02f}. 
-
 {\em Widely used:}  Researchers and industrial practitioners  use static attributes to guide software 

### 2016-01-21 tuningpredictor.tex
change to IST format

@@
+\documentclass[final,twocolumn,5p]{elsarticle}
 % \documentclass{sig-alternative}
 % \documentclass[conference]{IEEEtran}
-\documentclass[smallextended]{svjour3}
+% \documentclass[smallextended]{svjour3}
+% \documentclass[preprint,12pt,3p,number]{elsarticle}
 \usepackage{multirow}
+% \usepackage{natbib}
 \usepackage{color}
 \usepackage{graphics} 
-\usepackage{cite}
+% \usepackage{cite}
 \usepackage{rotating}
@@
 \begin{document}
-
+\begin{frontmatter}
 \title{ Tuning for Software Analytics: is it Really Necessary?}
-% \numberofauthors{1}
-\author{Wei Fu \and Tim Menzies \and Xipeng Shen}
-\institute{North Carolina State University, Raleigh, NC, USA
-      Wei Fu \email{w}}
-% \email{fuwei.ee \and tim.menzies@gmail.com \and xshen5@ncsu.edu }
-\maketitle 
-\thispagestyle{plain}
-\pagestyle{plain}
+\author{Wei Fu\corref{cor1}}
+\ead{wfu@ncsu.edu}
+\author{Tim Menzies\corref{cor1}}
+\ead{tim.menzies@gmail.com}
+\author{Xipeng Shen}
+\ead{ xshen5@ncsu.edu}
+\cortext[cor1]{Corresponding author}
+\address{Department of Computer Science, North Carolina State University, Raleigh, NC, USA}
+
+% % \numberofauthors{1}
+% \author{Wei Fu \and Tim Menzies \and Xipeng Shen}
+% \institute{North Carolina State University, Raleigh, NC, USA
+%       Wei Fu \email{w}}
+% % \email{fuwei.ee \and tim.menzies@gmail.com \and xshen5@ncsu.edu }
+
+% \thispagestyle{plain}
+% \pagestyle{plain}
 \begin{abstract}
-One of the ``black arts'' of data mining is setting the tuning
-parameters that control  the miner.  We offer a simple,
-automatic, and very effective  method for finding those tunings.
-
-Contrary to our prior expectations, finding these tunings
+\textbf{Context:} Data miners have been widely used to generate defect predictors from static code measures.
+Static code defect predictors perform well compared to manual methods, and they are easy to use and useful to use.
+\\
+\textbf{Objective:} One of the ``black arts'' of data mining is setting the tuning that control the miner.
+Prior to  this  work,  our  intuition  was  that  tuning  would  change  the behavior  or  a  data  miner, to  some  degree.
+We offer a simple, automatic, and very effective  method for finding those tunings.\\
+\textbf{Method:} We run differential evolution as an optimizer to explore the tuning space and fit the data miners with the best tunings afterwards.\\
+\textbf{Results:} Contrary to our prior expectations, finding these tunings
  was remarkably simple: it only required tens, not thousands, of attempts
- to obtain very good results.
-For example, when  learning
-software defect predictors, this  method can quickly
+ to obtain very good results.For example, when  learning software defect predictors, this  method can quickly
  find tunings  that  alter detection  precision
- from 0\% to 60\%.
-
-Given that (1)~the improvements are so large, and (2)~the tuning is so simple,
+ from 0\% to 60\%. \\
+\textbf{Conclusion:} Given that (1)~the improvements are so large, and (2)~the tuning is so simple,
 these results prompt for a change to standard methods in software analytics.
@@
 
-%RQ1: Does tuning affect learners' performance?
-%RQ2: How to choose
-
 \end{abstract}
+\end{frontmatter}
 
@@
 search-based software engineering.
-
+%  \maketitle 
 \pagenumbering{arabic} %XXX delete before submission
@@
 
-\section{Digression}
-
-Before starting, we offer the following aside.
-An important principle in tuning is that
-{\em you can't always get \underline{all} you want}.
-In the following, we present tuning as a multi-objective optimization problem
-and, with some problems, it is not always possible to optimize for every goals.
+\section{Preliminaries}
+
+\subsection{You Can't Always Get What You Want}\label{sect:goals}
+In the following, we present tuning as a multi-objective optimization problem.
+With such optimizations,  it is not always possible to optimize for every goals.
 For example, the following text does not
 show results for tuning on recall
-or false alarms since otpimizing {\em only} for those goals can lead
-to some undesirable side effects. For example: 
+or false alarms since optimizing {\em only} for those goals can lead
+to some undesirable side effects:
 \bi
@@
 Accordingly,  this paper  explores performance measures that comment on all 
-target classes (see the  precision and ``F'' measures discussed in \fig{xxx}).
-
-\section{Preliminaries}
-
-\subsection{Issues of Tuning: Important and Ignored?}
+target classes: see the  precision and ``F'' measures discussed below: see {\em Optimization Goals}.
+That said, we are sometimes asked what good is a learner if it optimizers for (say) precision
+at the expense of (say) recall.
+
+Our reply is that software engineering is a very diverse enterprise
+and that different kinds of development need to optimize for different goals
+(which may not necessarily be ``optimize for recall''):
+\bi
+\item
+Anda, Sjoberg and Mockus are concerned with {\em reproducibility}  and so
+assess their models using the the ``coefficient of variation'' $C\frac{stddev}{mean}$) ~\cite{anda09}.
+\item
+Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12} are concerned with reducing the work load associated with someone
+else reading a learned model, then applying it. Hence, they assess their models using  {\em reward}; i.e.   the fewest lines of code
+  containing the most bugs.
+\item
+Yin et al. are concerned about
+ {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
+These bugs occur  when (say) developers try to fix parts of the code
+where they have very little experience~\cite{yin11}.  Hence, they assess a learned
+model using a measure that selects for  the most number of bugs in regions that {\em the most programmers have worked with before}.
+\item
+For safety critical applications, high false alarm rates are  acceptable if the cost
+of overlooking  critical issues outweighs the inconvenience of   inspecting a few more
+modules. 
+\item
+When rushing a product to market,  there is a business case to 
+avoid the extra rework associated with false alarms.  In that business context, 
+managers might be willing to lower the recall somewhat in order to minimize the false alarms.
+\item
+When the second author worked with contractors at  NASA's software independent verification
+and validation facility, he found  new contractors  
+only reported issues that were most certainly important defects; i.e. they minimized
+  false alarms even if that damaged their precision (since, they felt, 
+it was better to silent than wrong). Later on, once
+those contractors had acquired a reputation of being insightful members of the team,
+they improved their precision scores (even if it means some more false alarms).
+\ei
+Accordingly, this paper does not assume that (e.g.) minimizing false alarms is 
+more important than maximizing   precision. Such a determination 
+depends on   business conditions.
+Rather, what we can  show  examples where  changing  optimization goals can also change 
+the conclusions made from that learner on that data. More generally, we caution that it is 
+important not to overstate  empirical results from  analytics.
+Rather, those results need to be expressed {\em along with} the context within which they are
+relevant (and by ``context'', we mean the optimization goal).
+
+\subsection{Tuning: Important and Ignored}
+Having made the business case for tuning with respect to the business context,
+we now show that tuning is an under-explored area in   SE.
+
 In  other fields, the impact of tuning is well understood~\cite{Bergstra2012}. 
-Yet, as argued in this section, issues of tuning  are rarely or poorly addressed
+Yet issues of tuning  are rarely or poorly addressed
 in the defect prediction literature.
-
 When we tune a data miner, what we are really doing is changing how a learner applies
@@
 
-\begin{table*}[t]
-\renewcommand{\baselinestretch}{0.8}\begin{center}
-{\scriptsize
-\begin{tabular}{c|l|p{0.5\textwidth}}
-amc & average method complexity & e.g. number of JAVA byte codes\\\hline
-avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
-in class\\\hline
-ca & afferent couplings & how many other classes use the specific
-class. \\\hline
-cam & cohesion amongst classes & summation of number of different
-types of method parameters in every method divided by a multiplication
-of number of different method parameter types in whole class and
-number of methods. \\\hline
-cbm &coupling between methods &  total number of new/redefined methods
-to which all the inherited methods are coupled\\\hline
-cbo & coupling between objects & increased when the methods of one
-class access services of another.\\\hline
-ce & efferent couplings & how many other classes is used by the
-specific class. \\\hline
-dam & data access & ratio of the number of private (protected)
-attributes to the total number of attributes\\\hline
-dit & depth of inheritance tree &\\\hline
-ic & inheritance coupling &  number of parent classes to which a given
-class is coupled (includes counts of methods and variables inherited)
-\\\hline
-lcom & lack of cohesion in methods &number of pairs of methods that do
-not share a reference to an instance variable.\\\hline
-locm3 & another lack of cohesion measure & if $m,a$ are  the number of
-$methods,attributes$
-in a class number and $\mu(a)$  is the number of methods accessing an
-attribute, 
-then
-$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
-\\\hline
-loc & lines of code &\\\hline
-max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
-in class\\\hline
-mfa & functional abstraction & number of methods inherited by a class
-plus number of methods accessible by member methods of the
-class\\\hline
-moa &  aggregation &  count of the number of data declarations (class
-fields) whose types are user defined classes\\\hline
-noc &  number of children &\\\hline
-npm & number of public methods & \\\hline
-rfc & response for a class &number of  methods invoked in response to
-a message to the object.\\\hline
-wmc & weighted methods per class &\\\hline
-\rowcolor{lightgray}
-defect & defect & Boolean: where defects found in post-release bug-tracking systems.
-\end{tabular}
-}
-\end{center}
-\caption{OO measures used in our defect data sets.}\label{tab:ck}
-\end{table*}
-
 Since the Lessmann et al. paper, much progress has been made in 
@@
   \centering
-	\begin{tabular}{|c|c|c|c|p{5cm}|}
+	\begin{tabular}{|c|c|c|c|l|}
 	\cline{1-5}
@@
 	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}Finds min\_samples\_leaf 
-in the initial clustering tree\\  using ${n\_samples}^ {min\_Size}$.
+in the initial clustering tree using ${n\_samples}^ {min\_Size}$.
 \end{tabular} \\ \cline{2-5} 
@@
 Certain standard measures can be computed from
-$A,B,C,D$:
+$A,B,C,D$, as shown below. Note that for $pf$, the {\em better} scores are {\em smaller}
+while
+for all other scores, the {\em better} scores are {\em larger}.
 
@@
 
-For $pf$, the {\em better} scores are {\em smaller}.
-For all other scores, the {\em better} scores are {\em larger}.
-One technical detail:   {\em prec}
-and {\em F} refer to {\em both} the defect and non-defective modules. This is different to {\em pf} and {\em recall} which only
-refer to either non-defective or defective modules (repsectively).
-
-\begin{figure}[!b]
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-
- Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
-Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
-
-Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
-say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
-that contain the most bugs.
-
-Yin et al. are concerned about
- {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
-These bugs occur  when (say) developers try to fix parts of the code
-where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
-for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
-
-In {\em Better-faster-cheaper},   managers want
- fewer defects,  faster development,  using less resources~\cite{Green,elrawas10,me07f,me09f}.
-\\\hline
-\end{tabular}
-\caption{Many ways to assess defect predictors.}\label{fig:criteria}
-\end{figure}
-
-This paper does not assume that (e.g.) minimizing false alarms is 
-more important than maximizing   precision. Such a determination 
-depends on   business conditions.
-For example,
-(1) for safety critical applications, high false alarm rates are  acceptable if the cost
-of overlooking  critical issues outweighs the inconvenience of   inspecting a few more
-modules. 
-On the other hand, (2) when rushing a product to market,  there is a business case to 
-avoid the extra rework associated with false alarms.  In that business context, 
-managers might be willing to lower the recall somewhat in order to minimize the false alarms.
-These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
-and there is insufficient space in this paper to explore all the above optimization goals.
-
-In this paper, what we can  show  examples where  changing  optimization goals can also change 
-the conclusions made from that learner on that data. Accordingly, we warn that it is 
-important not to overstate  empirical results from  analytics.
-Rather, those results need to be expressed {\em along with} the context within which they are
-relevant (and by ``context'', we mean the optimization goal).
+The rest of this paper explores tuning for {\em prec} and {\em F}. As discussed
+in \tion{goals}, our point is not that these are best or most important optimization goals.
+Indeed, the list of ``most important'' goals is domain-specific (see \tion{goals})
+and we only explore these two to illustrate how conclusions can change dramatically
+when moving from one goal to another.
 
@@
 
-\bibliographystyle{plain}
-
-\balance
+% \bibliographystyle{plain}
+\bibliographystyle{elsarticle-num}
+% \balance
 \bibliography{tuningpredictor}
 
-  %%%%parameters for F %%%%%%
-\begin{table*}[!ht]
-
-\resizebox{\textwidth}{!}{
-% \renewcommand{\baselinestretch}{0.9}
-\scriptsize
-\centering
-  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
-    \hline
-
-  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
- \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
-& threshold& 0.5& 0.04& 0.44& 0.44& 0.98& 0.65& 0.77& 1& 0.65& 0.98& 0.44& 0.44& 0.87& 0.04& 0.77& 0.24& 0.44& 0.77\\ \cline{2-20}
-& infoPrune& 0.33& 0.51& 0.68& 0.88& 0.47& 0.07& 0.31& 0.48& 0.68& 0.57& 0.12& 0.68& 0.01& 0.51& 0.14& 0.54& 0.68& 0.14\\ \cline{2-20}
-& min\_sample\_size& 4& 6& 4& 6& 1& 6& 8& 8& 4& 6& 7& 4& 9& 6& 2& 8& 4& 8\\ \cline{2-20}
-& min\_Size& 0.5& 0.18& 0.4& 0.56& 0.51& 0.65& 0.59& 0.97& 0.4& 0.51& 0.8& 0.4& 0.77& 0.18& 0.62& 0.46& 0.4& 0.66\\ \cline{2-20}
-& wriggle& 0.2& 0.25& 0.29& 0.76& 0.6& 0.63& 0.26& 1& 0.51& 0.17& 0.36& 0.51& 0.83& 0.25& 0.5& 0.52& 0.29& 0.26\\ \cline{2-20}
-& depthMin& 2& 3& 3& 3& 1& 5& 3& 2& 3& 5& 5& 3& 4& 3& 3& 3& 3& 3\\ \cline{2-20}
-& depthMax& 10& 16& 15& 15& 8& 19& 10& 7& 15& 5& 15& 15& 19& 16& 6& 19& 15& 10\\ \cline{2-20}
-& wherePrune& False& False& True& True& True& True& True& True& False& False& True& True& True& False& True& False& False& True\\ \cline{2-20}
-& treePrune& True& False& True& True& False& False& False& False& False& True& True& True& False& False& False& True& True& False\\ \cline{2-20}
-\hline
-\multirow{5}{*}{CART}
-& threshold& 0.5& 0.34& 0.25& 0.01& 0.01& 0.73& 0.53& 0.92& 0.8& 0.74& 0.54& 0.03& 0.91& 0.01& 0.01& 0.55& 1& 0.01\\ \cline{2-20}
-& max\_feature& None& 0.01& 0.01& 0.29& 0.01& 0.46& 0.75& 0.79& 0.74& 0.41& 0.81& 0.61& 0.72& 0.01& 0.01& 0.01& 0.25& 0.18\\ \cline{2-20}
-& min\_samples\_split& 2& 18& 20& 12& 2& 15& 11& 2& 18& 13& 9& 17& 16& 10& 4& 8& 3& 15\\ \cline{2-20}
-& min\_samples\_leaf& 1& 19& 16& 15& 17& 1& 1& 13& 10& 4& 3& 7& 5& 20& 7& 8& 1& 6\\ \cline{2-20}
-& max\_depth& None& 12& 2& 15& 1& 41& 20& 44& 15& 13& 5& 23& 14& 1& 5& 17& 47& 13\\ \cline{2-20}
-\hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
-& threshold& 0.5& 0.01& 0.35& 0.3& 0.01& 0.9& 0.97& 0.63& 1& 0.73& 0.68& 0.01& 1.0& 0.01& 0.07& 0.22& 1& 0.82\\ \cline{2-20}
-& max\_feature& None& 0.63& 0.17& 0.01& 0.01& 0.88& 0.74& 0.76& 0.73& 0.01& 0.03& 0.39& 0.02& 0.01& 0.56& 0.36& 0.51& 0.89\\ \cline{2-20}
-& max\_leaf\_nodes& None& 40& 33& 46& 22& 11& 16& 38& 34& 30& 31& 12& 49& 25& 47& 15& 39& 24\\ \cline{2-20}
-& min\_samples\_split& 2& 10& 16& 20& 1& 1& 1& 1& 4& 20& 19& 11& 14& 2& 17& 19& 20& 19\\ \cline{2-20}
-& min\_samples\_leaf& 1& 4& 15& 9& 13& 18& 11& 3& 16& 17& 6& 10& 7& 19& 13& 11& 2& 14\\ \cline{2-20}
-& n\_estimators& 100& 120& 73& 75& 130& 97& 144& 125& 97& 80& 111& 96& 101& 50& 67& 74& 63& 66\\ \cline{2-20}
-\hline  \end{tabular}
-}
-  \caption{Parameters tuned on different models over the objective of ``F''.}\label{tab:fselect}
-\end{table*}
+%   %%%%parameters for F %%%%%%
+% \begin{table*}[!ht]
+
+% \resizebox{\textwidth}{!}{
+% % \renewcommand{\baselinestretch}{0.9}
+% \scriptsize
+% \centering
+%   \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
+%     \hline
+
+%   \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\
+%  \hline
+% \multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
+% & threshold& 0.5& 0.04& 0.44& 0.44& 0.98& 0.65& 0.77& 1& 0.65& 0.98& 0.44& 0.44& 0.87& 0.04& 0.77& 0.24& 0.44& 0.77\\ \cline{2-20}
+% & infoPrune& 0.33& 0.51& 0.68& 0.88& 0.47& 0.07& 0.31& 0.48& 0.68& 0.57& 0.12& 0.68& 0.01& 0.51& 0.14& 0.54& 0.68& 0.14\\ \cline{2-20}
+% & min\_sample\_size& 4& 6& 4& 6& 1& 6& 8& 8& 4& 6& 7& 4& 9& 6& 2& 8& 4& 8\\ \cline{2-20}
+% & min\_Size& 0.5& 0.18& 0.4& 0.56& 0.51& 0.65& 0.59& 0.97& 0.4& 0.51& 0.8& 0.4& 0.77& 0.18& 0.62& 0.46& 0.4& 0.66\\ \cline{2-20}
+% & wriggle& 0.2& 0.25& 0.29& 0.76& 0.6& 0.63& 0.26& 1& 0.51& 0.17& 0.36& 0.51& 0.83& 0.25& 0.5& 0.52& 0.29& 0.26\\ \cline{2-20}
+% & depthMin& 2& 3& 3& 3& 1& 5& 3& 2& 3& 5& 5& 3& 4& 3& 3& 3& 3& 3\\ \cline{2-20}
+% & depthMax& 10& 16& 15& 15& 8& 19& 10& 7& 15& 5& 15& 15& 19& 16& 6& 19& 15& 10\\ \cline{2-20}
+% & wherePrune& False& False& True& True& True& True& True& True& False& False& True& True& True& False& True& False& False& True\\ \cline{2-20}
+% & treePrune& True& False& True& True& False& False& False& False& False& True& True& True& False& False& False& True& True& False\\ \cline{2-20}
+% \hline
+% \multirow{5}{*}{CART}
+% & threshold& 0.5& 0.34& 0.25& 0.01& 0.01& 0.73& 0.53& 0.92& 0.8& 0.74& 0.54& 0.03& 0.91& 0.01& 0.01& 0.55& 1& 0.01\\ \cline{2-20}
+% & max\_feature& None& 0.01& 0.01& 0.29& 0.01& 0.46& 0.75& 0.79& 0.74& 0.41& 0.81& 0.61& 0.72& 0.01& 0.01& 0.01& 0.25& 0.18\\ \cline{2-20}
+% & min\_samples\_split& 2& 18& 20& 12& 2& 15& 11& 2& 18& 13& 9& 17& 16& 10& 4& 8& 3& 15\\ \cline{2-20}
+% & min\_samples\_leaf& 1& 19& 16& 15& 17& 1& 1& 13& 10& 4& 3& 7& 5& 20& 7& 8& 1& 6\\ \cline{2-20}
+% & max\_depth& None& 12& 2& 15& 1& 41& 20& 44& 15& 13& 5& 23& 14& 1& 5& 17& 47& 13\\ \cline{2-20}
+% \hline
+% \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
+% & threshold& 0.5& 0.01& 0.35& 0.3& 0.01& 0.9& 0.97& 0.63& 1& 0.73& 0.68& 0.01& 1.0& 0.01& 0.07& 0.22& 1& 0.82\\ \cline{2-20}
+% & max\_feature& None& 0.63& 0.17& 0.01& 0.01& 0.88& 0.74& 0.76& 0.73& 0.01& 0.03& 0.39& 0.02& 0.01& 0.56& 0.36& 0.51& 0.89\\ \cline{2-20}
+% & max\_leaf\_nodes& None& 40& 33& 46& 22& 11& 16& 38& 34& 30& 31& 12& 49& 25& 47& 15& 39& 24\\ \cline{2-20}
+% & min\_samples\_split& 2& 10& 16& 20& 1& 1& 1& 1& 4& 20& 19& 11& 14& 2& 17& 19& 20& 19\\ \cline{2-20}
+% & min\_samples\_leaf& 1& 4& 15& 9& 13& 18& 11& 3& 16& 17& 6& 10& 7& 19& 13& 11& 2& 14\\ \cline{2-20}
+% & n\_estimators& 100& 120& 73& 75& 130& 97& 144& 125& 97& 80& 111& 96& 101& 50& 67& 74& 63& 66\\ \cline{2-20}
+% \hline  \end{tabular}
+% }
+%   \caption{Parameters tuned on different models over the objective of ``F''.}\label{tab:fselect}
+% \end{table*}
 

### 2016-03-14 tuningpredictor.tex

@@
 \usepackage{colortbl} 
-\usepackage{times}
+%\usepackage{times}
+ \usepackage{mathptmx} \usepackage[scaled=.90]{helvet} \usepackage{courier}
 \usepackage{balance}
@@
 \ead{ xshen5@ncsu.edu}
-\cortext[cor1]{Corresponding author}
+\cortext[cor1]{Corresponding author: Tel.:+1 304-376-2859 (Tim Menzies)}
 \address{Department of Computer Science, North Carolina State University, Raleigh, NC, USA}
@@
 \\
-\textbf{Objective:} One of the ``black arts'' of data mining is setting the tuning that control the miner.
-Prior to  this  work,  our  intuition  was  that  tuning  would  change  the behavior  or  a  data  miner, to  some  degree.
-We offer a simple, automatic, and very effective  method for finding those tunings.\\
-\textbf{Method:} We run differential evolution as an optimizer to explore the tuning space and fit the data miners with the best tunings afterwards.\\
-\textbf{Results:} Contrary to our prior expectations, finding these tunings
+\textbf{Objective:} One of the ``black arts'' of data mining is setting the tuning that control the miner. We offer a simple, automatic, and very effective  method for finding those tunings.\\
+\textbf{Method:} For each experiment with different data sets, we run differential evolution as an optimizer to explore the tuning space as the first step and  fit the data miners with the best tunings afterwards.\\
+\textbf{Results:} Contrary to our prior expectations, we found these tunings
  was remarkably simple: it only required tens, not thousands, of attempts
@@
 
-% A category with the (minimum) three required fields
-\vspace{1mm}
-\noindent
-{\bf Categories/Subject Descriptors:} 
-D.2.8 [Software Engineering]: Product metrics;
-I.2.6 [Artificial Intelligence]: Induction
+% % A category with the (minimum) three required fields
+% \vspace{1mm}
+% \noindent
+% {\bf Categories/Subject Descriptors:} 
+% D.2.8 [Software Engineering]: Product metrics;
+% I.2.6 [Artificial Intelligence]: Induction
 
@@
 \section{Preliminaries}
-
-\subsection{You Can't Always Get What You Want}\label{sect:goals}
-In the following, we present tuning as a multi-objective optimization problem.
-With such optimizations,  it is not always possible to optimize for every goals.
-For example, the following text does not
-show results for tuning on recall
-or false alarms since optimizing {\em only} for those goals can lead
-to some undesirable side effects:
-\bi
-\item
-{\em Recall} reports the percentage of  predictions that are actual examples of  what we are looking for.
-When we tune for {\em recall}, we can achieve near
-100\% recall-- but the cost of a near 100\% false alarms.
-\item
-{\em False alarms} is the percentage of other examples that are reported  (by the learner)
-to be part of the targeted examples.
-When we tune for {\em false alarms}, we 
-can achieve near zero percent false alarm rates by effectively turning off
-the detector (so the  recall falls to nearly zero).
-\ei
-Accordingly,  this paper  explores performance measures that comment on all 
-target classes: see the  precision and ``F'' measures discussed below: see {\em Optimization Goals}.
-That said, we are sometimes asked what good is a learner if it optimizers for (say) precision
-at the expense of (say) recall.
-
-Our reply is that software engineering is a very diverse enterprise
-and that different kinds of development need to optimize for different goals
-(which may not necessarily be ``optimize for recall''):
-\bi
-\item
-Anda, Sjoberg and Mockus are concerned with {\em reproducibility}  and so
-assess their models using the the ``coefficient of variation'' $C\frac{stddev}{mean}$) ~\cite{anda09}.
-\item
-Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12} are concerned with reducing the work load associated with someone
-else reading a learned model, then applying it. Hence, they assess their models using  {\em reward}; i.e.   the fewest lines of code
-  containing the most bugs.
-\item
-Yin et al. are concerned about
- {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
-These bugs occur  when (say) developers try to fix parts of the code
-where they have very little experience~\cite{yin11}.  Hence, they assess a learned
-model using a measure that selects for  the most number of bugs in regions that {\em the most programmers have worked with before}.
-\item
-For safety critical applications, high false alarm rates are  acceptable if the cost
-of overlooking  critical issues outweighs the inconvenience of   inspecting a few more
-modules. 
-\item
-When rushing a product to market,  there is a business case to 
-avoid the extra rework associated with false alarms.  In that business context, 
-managers might be willing to lower the recall somewhat in order to minimize the false alarms.
-\item
-When the second author worked with contractors at  NASA's software independent verification
-and validation facility, he found  new contractors  
-only reported issues that were most certainly important defects; i.e. they minimized
-  false alarms even if that damaged their precision (since, they felt, 
-it was better to silent than wrong). Later on, once
-those contractors had acquired a reputation of being insightful members of the team,
-they improved their precision scores (even if it means some more false alarms).
-\ei
-Accordingly, this paper does not assume that (e.g.) minimizing false alarms is 
-more important than maximizing   precision. Such a determination 
-depends on   business conditions.
-Rather, what we can  show  examples where  changing  optimization goals can also change 
-the conclusions made from that learner on that data. More generally, we caution that it is 
-important not to overstate  empirical results from  analytics.
-Rather, those results need to be expressed {\em along with} the context within which they are
-relevant (and by ``context'', we mean the optimization goal).
 
@@
 
+ \subsection{You Can't Always Get What You Want}\label{sect:goals}
+
+In the following, we present tuning as a multi-objective optimization problem.
+With such optimizations,  it is not always possible to optimize for every goal.
+For example, the following text does not
+show results for tuning on recall
+or false alarms since optimizing {\em only} for those goals can lead
+to some undesirable side effects:
+\bi
+\item
+{\em Recall} reports the percentage of  predictions that are actual examples of  what we are looking for.
+When we tune for {\em recall}, we can achieve near
+100\% recall-- but the cost of a near 100\% false alarms.
+\item
+{\em False alarms} is the percentage of other examples that are reported  (by the learner)
+to be part of the targeted examples.
+When we tune for {\em false alarms}, we 
+can achieve near zero percent false alarm rates by effectively turning off
+the detector (so the  recall falls to nearly zero).
+\ei
+Accordingly,  this paper  explores performance measures that comment on all 
+target classes: see the  precision and ``F'' measures discussed below: see {\em Optimization Goals}.
+That said, we are sometimes asked what good is a learner if it optimizers for (say) precision
+at the expense of (say) recall.
+
+Our reply is that software engineering is a very diverse enterprise
+and that different kinds of development need to optimize for different goals
+(which may not necessarily be ``optimize for recall''):
+\bi
+\item
+Anda, Sjoberg and Mockus are concerned with {\em reproducibility}  and so
+assess their models using the the ``coefficient of variation'' $C\frac{stddev}{mean}$) ~\cite{anda09}.
+\item
+Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12} are concerned with reducing the work load associated with someone
+else reading a learned model, then applying it. Hence, they assess their models using  {\em reward}; i.e.   the fewest lines of code
+  containing the most bugs.
+\item
+Yin et al. are concerned about
+ {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
+These bugs occur  when (say) developers try to fix parts of the code
+where they have very little experience~\cite{yin11}.  Hence, they assess a learned
+model using a measure that selects for  the most number of bugs in regions that {\em the most programmers have worked with before}.
+\item
+For safety critical applications, high false alarm rates are  acceptable if the cost
+of overlooking  critical issues outweighs the inconvenience of   inspecting a few more
+modules. 
+\item
+When rushing a product to market,  there is a business case to 
+avoid the extra rework associated with false alarms.  In that business context, 
+managers might be willing to lower the recall somewhat in order to minimize the false alarms.
+\item
+When the second author worked with contractors at  NASA's software independent verification
+and validation facility, he found  new contractors  
+only reported issues that were most certainly important defects; i.e. they minimized
+  false alarms even if that damaged their precision (since, they felt, 
+it was better to silent than wrong). Later on, once
+those contractors had acquired a reputation of being insightful members of the team,
+they improved their precision scores (even if it means some more false alarms).
+\ei
+Accordingly, this paper does not assume that (e.g.) minimizing false alarms is 
+more important than maximizing   precision. Such a determination 
+depends on   business conditions.
+Rather, what we can  show  examples where  changing  optimization goals can also change 
+the conclusions made from that learner on that data. More generally, we caution that it is 
+important not to overstate  empirical results from  analytics.
+Rather, those results need to be expressed {\em along with} the context within which they are
+relevant (and by ``context'', we mean the optimization goal).
+
 \subsection{Notes on Defect Prediction}
@@
 	\cline{1-5}
-	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
+	\begin{tabular}[c]{@{}c@{}}Learner Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
 \multicolumn{1}{c|}{Description} \\ \hline
- 	\multirow{8}{*}{%\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}
- 	WHERE} 
+ 	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}}
+%  	WHERE-based  Learner} 
 	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
@@
 	 \hline 
-% Logistic\\ Regression&\multicolumn{4}{c|}{This study uses untuned LR in order to check
-% a conclusion of~\cite{hall11}. }\\\hline
+Logistic Regression&\multicolumn{4}{c|}{This study uses untuned LR in order to check
+a conclusion of~\cite{hall11}. }\\\hline
 
@@
  will be combined as the training data to build a model. Then the performance of this untuned learner 
- will be evaluated by the same {\em third} release.
+ will be evaluated by the same {\em third} release as in the tuning experiment.
 
@@
 \tab{precisionbars} and \tab{fbars} show the
-the specific values seen before and after tuning (two separate experiments with two different tuning goals: {\em precision} and {\em ``F''}). 
-For each data set, the maximum precision or F values for each data set are shown in {\bf bold}.
+the specific values seen before and after tuning with {\em precision}
+and {\em ``F''} as different optimization goals(the corresponding  ``F'' and precision values for
+\tab{precisionbars} and \tab{fbars} are not provided for the space limitation).
+For each data set, the maximum precision or ``F'' values for each data set are shown in {\bf bold}.
 As might have been
@@
 \scriptsize
-% \centering
+\centering
   \begin{tabular}{c|p{1in}|p{1in}}
@@
 \scriptsize
-% \centering
+ \centering
   \begin{tabular}{c|c c|cc}
@@
 \begin{figure}[!t]
-% \begin{center}
+\begin{center}
 \includegraphics[width=1.5in]{./eps/features_precision.eps}\includegraphics[width=1.5in]{./eps/features_F.eps}
-%  \end{center}
+\end{center}
 \caption{Four representative tuning values in WHERE with  precision and F-measure as the tuning goal, respectively.   }\label{fig:features}
@@
 
+\balance
+
 \end{document}

### 2016-04-03 tuningpredictor.tex
Updates from ShareLaTeX

@@
 \ead{ xshen5@ncsu.edu}
-\cortext[cor1]{Corresponding author: Tel.:+1 304-376-2859 (Tim Menzies)}
+\cortext[cor1]{Corresponding author: Tel:19195345251(Wei)}
 \address{Department of Computer Science, North Carolina State University, Raleigh, NC, USA}
@@
 \begin{abstract}
-\textbf{Context:} Data miners have been widely used to generate defect predictors from static code measures.
-Static code defect predictors perform well compared to manual methods, and they are easy to use and useful to use.
-\\
-\textbf{Objective:} One of the ``black arts'' of data mining is setting the tuning that control the miner. We offer a simple, automatic, and very effective  method for finding those tunings.\\
-\textbf{Method:} For each experiment with different data sets, we run differential evolution as an optimizer to explore the tuning space as the first step and  fit the data miners with the best tunings afterwards.\\
+\textbf{Context:} Data miners have been widely used in
+software engineering to, say,  generate defect predictors from static code measures.
+Such static code defect predictors perform well compared to manual methods, and they are easy to use and useful to use.
+But
+one of the ``black arts'' of data mining is setting the tunings that control the miner. \\
+\textbf{Objective:} We seek  simple, automatic, and very effective  method for finding those tunings.\\
+\textbf{Method:} For each experiment with different data sets (from open source JAVA systems), we ran differential evolution as an optimizer to explore the tuning space
+(as a first step) then tested the tunings
+using hold-out data.\\
 \textbf{Results:} Contrary to our prior expectations, we found these tunings
- was remarkably simple: it only required tens, not thousands, of attempts
- to obtain very good results.For example, when  learning software defect predictors, this  method can quickly
+ were remarkably simple: it only required tens, not thousands, of attempts
+ to obtain very good results. For example, when  learning software defect predictors, this  method can quickly
  find tunings  that  alter detection  precision
  from 0\% to 60\%. \\
-\textbf{Conclusion:} Given that (1)~the improvements are so large, and (2)~the tuning is so simple,
-these results prompt for a change to standard methods in software analytics.
+\textbf{Conclusion:} Since the (1)~the improvements are so large, and (2)~the tuning is so simple, we need 
+to change  standard methods in software analytics.
 At least for defect prediction, 
@@
 The results of this paper show that the above points are
-false,  at least for
+false since, at least for
 defect prediction from  code attributes:
@@
 \subsection{Tuning: Important and Ignored}
-Having made the business case for tuning with respect to the business context,
-we now show that tuning is an under-explored area in   SE.
+This section argues that   tuning is an under-explored software analytics-- particularly in the apparently  well-explored field of defect prediction.
 
@@
 
-In the following, we present tuning as a multi-objective optimization problem.
-With such optimizations,  it is not always possible to optimize for every goal.
+ Having made the case that tuning needs to be explored more,
+ but before we get into the technical details of this
+ paper, this section discusses some
+ general matters about setting goals during tuning
+ experiments.
+
+ This paper characterizes tuning as an optimization problem (how to change the settings on the learner
+ in order to best improve the output).
+With such optimizations,  it is not always possible to optimize for all goals at the same time.
 For example, the following text does not
@@
 Accordingly, this paper does not assume that (e.g.) minimizing false alarms is 
-more important than maximizing   precision. Such a determination 
+more important than maximizing   precision or recall. Such a determination 
 depends on   business conditions.
+
 Rather, what we can  show  examples where  changing  optimization goals can also change 
@@
 important not to overstate  empirical results from  analytics.
-Rather, those results need to be expressed {\em along with} the context within which they are
+Those results need to be expressed {\em along with} the context within which they are
 relevant (and by ``context'', we mean the optimization goal).
@@
 
-This section is our standard introduction to defect prediction~\cite{me15:book1},
-plus    some new results from Rahman et al.~\cite{rahman14:icse}.
+This section discusses defect prediction,
+which is the particular
+task explored by our optimizers.
+Note that this section repeats much of 
+our standard introduction to defect prediction~\cite{me15:book1},
+as well as presenting    some new results from Rahman et al.~\cite{rahman14:icse}.
 
@@
 \centering
-  \begin{tabular}{p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}}\hline
+%   \begin{tabular}{p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}p{0.75cm}}\hline
+  \begin{tabular}{c c c c c c c c c c } \hline
   Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
@@
  deltas in the precision and the F-measure    between tuned and untuned learners. Our reading of this
-figure is that, overall, tuning rarely makes performance   worse and usually can make it much better.
+figure is that, overall, tuning rarely makes performance   worse and often can make it much better.
 

### 2016-04-21 tuningpredictor.tex
fix typos

@@
  from 0\% to 60\%. \\
-\textbf{Conclusion:} Since the (1)~the improvements are so large, and (2)~the tuning is so simple, we need 
+\textbf{Conclusion:} Since (1)~the improvements are so large, and (2)~the tuning is so simple, we need 
 to change  standard methods in software analytics.
@@
 Bergstra and Bengio~\cite{Bergstra2012} comment that for most data sets only a few of the tuning parameters really matter-- which means that
-much of the runtimes associated with grid search is actually wasted.
+much of the runtime associated with grid search is actually wasted.
 Worse still, Bergstra and Bengio  comment that 
@@
 data sets-- a 
- phenomenon makes grid search a poor choice for configuring data mining
+ phenomenon that makes grid search a poor choice for configuring data mining
  algorithms for new data sets.
@@
 When we tune for {\em recall}, we can achieve near
-100\% recall-- but the cost of a near 100\% false alarms.
+100\% recall-- but at the cost of a near 100\% false alarms.
 \item
@@
 target classes: see the  precision and ``F'' measures discussed below: see {\em Optimization Goals}.
-That said, we are sometimes asked what good is a learner if it optimizers for (say) precision
+That said, we are sometimes asked what good is a learner if it optimizes for (say) precision
 at the expense of (say) recall.
@@
 Anda, Sjoberg and Mockus are concerned with {\em reproducibility}  and so
-assess their models using the the ``coefficient of variation'' $C\frac{stddev}{mean}$) ~\cite{anda09}.
+assess their models using the the ``coefficient of variation'' ($CV = \frac{stddev}{mean}$) ~\cite{anda09}.
 \item
@@
   false alarms even if that damaged their precision (since, they felt, 
-it was better to silent than wrong). Later on, once
+it was better to be silent than wrong). Later on, once
 those contractors had acquired a reputation of being insightful members of the team,
@@
 As to the value of those defaults, it could be argued that these defaults are 
-not the best  parameters needed for practical defect prediction.
+not the best  parameters for practical defect prediction.
 That said,  prior to this paper, two things were true:
@@
 When building the initial cluster tree, WHERE projects the data on to a dimension it synthesizes from the raw data using
-a process analogous to principle component analysis\footnote{
-PCA  synthesises  new
-attributes $e_i, e_2,...$
-that extends across the dimension of greatest  variance in the data  with attributes $d$.  
-This process  combines
-redundant  variables into a smaller set of variables  (so $e \ll d$) since those
-redundancies become (approximately) parallel lines
-in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
-can ignore $j$ 
-since effects that change over $j$ also
-change in the same way over $i$.
-PCA is also useful for skipping over noisy variables from $d$-- these
-variables are effectively ignored since    they  do not contribute to the variance in the data.}.
+a process analogous to principle component analysis~\cite{jolliffe2002principal}
+
+% \footnote{
+% PCA  synthesises  new
+% attributes $e_i, e_2,...$
+% that extends across the dimension of greatest  variance in the data  with attributes $d$.  
+% This process  combines
+% redundant  variables into a smaller set of variables  (so $e \ll d$) since those
+% redundancies become (approximately) parallel lines
+% in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
+% can ignore $j$ 
+% since effects that change over $j$ also
+% change in the same way over $i$.
+% PCA is also useful for skipping over noisy variables from $d$-- these
+% variables are effectively ignored since    they  do not contribute to the variance in the data.}.
 WHERE  divides  at the median point of that projection.
@@
 the final decision tree, WHERE pretends its clusters are ``classes'', then 
-asks the InfoGain of the
-Fayyad-Irani discretizer~\cite{FayIra93Multi}, to rank the attriubutes, where {\em infoPrune} is used.
+asks the InfoGain algorithm of the
+Fayyad-Irani discretizer~\cite{FayIra93Multi}, to rank the attributes, where {\em infoPrune} is used.
 WHERE's final decision tree generator then ignores everything except the top   {\em infoPrune} percent of the sorted
@@
 WHERE's   {\em tree\_prune} setting controls how   
-WHERE prunes back superflous parts of the final decision tree. 
+WHERE prunes back superfluous parts of the final decision tree. 
 If a decision sub-tree and its parent have the same 
@@
 Given tuning, how stable are these  conclusions?
-Before answering issue, we digress for two comments.
+Before answering this issue, we digress for two comments.
 
@@
 their
-summarization of so many defect prediction papers have not been equalled
+summarization of so many defect prediction papers has not been equalled
 before (or since).
@@
  Logistic Regression. Specifically, untuned
- Random Forest performs worse than Linear regression in in 13 out of   17 data sets. 
+ Random Forest performs worse than Logistic regression in  13 out of   17 data sets. 
 \item
@@
 scores of tuned CART and tuned Random Forest are not statistically different.
-Note that Random Forest is  not significantly better than CART, would not have been
+Note that Random Forest is  not significantly better than CART, which would not have been
 predicted by   Lessmann et al.
@@
 %   \end{tabular}
-%   \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for  precision.  }\label{tab:etimes}
+%   \caption{Evaluations/runtime and runtime for tuned and default learners(in sec), optimizing for  precision.  }\label{tab:etimes}
 % \end{table*}
@@
 %   \end{tabular}
-%   \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for F-measure.  }\label{tab:ftimes}
+%   \caption{Evaluations/runtime and runtime for tuned and default learners(in sec), optimizing for F-measure.  }\label{tab:ftimes}
 % \end{table*}
@@
   \end{tabular}
-  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for precision.}
+  \caption{Evaluations/runtime and runtime for tuned and default learners(in sec), optimizing for precision.}
   \label{tab:etimes}
@@
   \end{tabular}
-  \caption{Evaluations/runtimes and runtimes for tuned and default learners(in sec), optimizing for F-Measure.}
+  \caption{Evaluations/runtime and runtime for tuned and default learners(in sec), optimizing for F-Measure.}
 \label{tab:ftimes}
@@
 
-The number of evaluations/runtimes used by our optimizers is shown in \tab{etimes}
+The number of evaluations/runtime used by our optimizers is shown in \tab{etimes}
 and \tab{ftimes}.
-WHERE's runtimes are slower than CART and Random Forest since WHERE has yet to benefit from decades
+WHERE's runtime are slower than CART and Random Forest since WHERE has yet to benefit from decades
 of implementation experience with these older algorithms. For example, SciKitLearn's  CART and Random Forest

### 2016-04-26 replytoreviewer.tex
Updates from ShareLaTeX

\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\documentclass[final,twocolumn,5p]{elsarticle}
\begin{document}
\clearpage
\pagenumbering{roman}
\setcounter{page}{1} 
\section*{Reply to Reviews}

Thank your for your comments. The typos listed by reviewers
have been fixed and the remainder of the paper has been given
a careful proof read.

The reviewers raised certain issues which we respond  to as follows.-

{\it I am concerned about the reproduction of work from elsewhere. Although the relevant paper and book are cited in section 2.3 ([27, 28]) the amount of material that is reproduced is surprisingly large. I am also unsure what "presenting some new results from Rahman et al. [28]" actually means. It would obviously be wrong to present other researchers' results as if newly discovered but I doubt that this is the intention. Indeed, on checking the other paper, there is no obvious overlap. This needs to be clarified.}

Apologies to the reviewer for our unclear text that suggests
that this paper inappropriately copied  content from
elsewhere. This is not the case since nearly all of this paper has not been submitted
or published to another venue. The exception to that is:
\begin{itemize}
\item Section 2.3 and Table1 contains 1 page of tutorial material which we have adapted from other papers.
e.g. as the reviewer correctly points out,
the  'Easy to use' paragraph is taken nearly verbatim from [28], as are the 'widely-used', and 'useful' paragraphs.
\end{itemize}
Note that apart from Section 2.3,  10 of the 11 pages of this text are   completely new.

As to the reference to " presenting some new results from Rahman et al. [28]", that refers to one paragraph (120 words) end of section 2.3. 
Please note that we have removed the misleading text that raised that confusion
(start of 2.3).

{\em I think the way that the results are presented does not do justice to the findings in the abstract (that the improvements are large, and the tuning is simple). In particular, tables 8 and 9 are not very clear; why show the naive column?}

Thank for your that comment- we have simplified that presentation by separating the tuning \#evaluations from the runtimes-- see Table 8 and the new Table 9.

{\em I am distracted by the frequent use of footnotes. If the material is important and worthy of mention then it should be included in the main body of the paper. However, a reference to the relevant work may be sufficient and is sometimes preferable to using a footnote.}

Quite true- those footnotes are needlessly distracted.
They have now been incorporated into the text.

{\em  Eq 1 - what are d and T? - please use a where clause}

That where clause is now added after Equation 1. That clause says

\begin{quote} ... where  $d_i$ is the number of observed issues and $T$
is some threshold defined by an engineering judgement; we use $T=1$.\end{quote}

\end{document}

### 2016-04-26 old/dm101.tex
Updates from ShareLaTeX

--- 2016-01-21 dm101.tex
@@
 in the confidence $C$ of finding  defects
-can take {\em exponentially} more effort\footnote{A randomly selected 
+can take {\em exponentially} more effort:
+\bi
+\item
+A randomly selected 
 input to a program will find a fault with probability $p$.
+\item
 After $N$ random black-box tests, the chances of the inputs 
 not revealing any fault 
-is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
+is $(1-p)^N$. 
+\item
+Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
 which can be rearranged to 
  $N(C,p)=log(1 -
-C)/log(1-p)$. For example, $N(0.90,10^{-3})=2301$
-but $N(0.98,10^{-3})=3901$; i.e. nearly double the number of tests.}.
+C)/log(1-p)$. 
+\item
+For example, $N(0.90,10^{-3})=2301$
+but $N(0.98,10^{-3})=3901$; i.e. nearly double the number of tests.
+\ei
 Exponential costs quickly exhaust finite resources so
@@
 {\scriptsize
-\begin{tabular}{c|l|p{0.5\textwidth}}
+\begin{tabular}{c|l|p{4.7in}}
 amc & average method complexity & e.g. number of JAVA byte codes\\\hline

### 2016-04-26 old/fred.tex
Updates from ShareLaTeX

--- 2015-08-28 dm101.tex
@@
-Human programmers are clever, but flawed. Coding  adds functionality, but also defects.
-Hence, software sometimes crashes (perhaps at the most awkward or dangerous moment) or delivers
-the wrong functionality. For a very long list of software-related errors,
-see  Peter Neumann's ``Risk Digest'' at catless.ncl.ac.uk/Risks.
-
-Since programming inherently
-introduces defects into  programs, it is important to test them before they're used.
-Testing is expensive.
-Software assessment budgets are finite
-while assessment effectiveness increases 
-exponentially with assessment effort.
-For example, for  black-box testing methods,
-a {\em linear} increase
-in the confidence $C$ of finding  defects
-can take {\em exponentially} more effort\footnote{A randomly selected 
-input to a program will find a fault with probability $p$.
-After $N$ random black-box tests, the chances of the inputs 
-not revealing any fault 
-is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
-which can be rearranged to 
- $N(C,p)=log(1 -
-C)/log(1-p)$. For example, $N(0.90,10^{-3})=2301$
-but $N(0.98,10^{-3})=3901$; i.e. nearly double the number of tests.}.
-Exponential costs quickly exhaust finite resources so
-standard practice is to apply the best
-available  methods on code sections that seem   most critical. 
-But 
-any method that focuses on parts of the code
-can blind us to defects in other areas. Some  {\em
-lightweight sampling policy} should be used to explore the rest of the system.  This
-sampling policy will always be incomplete.
-Nevertheless, it is the only option when
-resources prevent a complete assessment of everything.
-
-One such lightweight sampling policy is defect predictors learned from static code attributes.
-Given software described in the attributes of \tab{ck},   data miners can
-learn where the probability of software defects is highest.
-
-The rest of this section argues that such defect predictors are   {\em easy to
-use}, {\em widely-used}, and {\em useful} to use.
-
-{\em Easy to use:} Static code attributes can be automatically collected, even for very large systems~\cite{nagappan05}.
-Other methods, like  manual code reviews, are far slower and far more labor-intensive.
-For example, depending on the review methods, 8 to 20 LOC/minute can be
-inspected and this effort repeats for all members of the review team,
-which can be as large as four or six people~\cite{me02f}.
-
-{\em Widely used:}  Researchers and industrial practitioners  use static attributes to guide software 
-quality predictions.
- Defect prediction models have been reported
-  at Google~\cite{lewis13}.
-Verification and validation (V\&V) textbooks
-\cite{rakitin01} advise using static code complexity attributes
-to decide which modules are worth manual inspections.
-
-{\em Useful:}
-Defect predictors often  find the location of  70\% (or more)
-of the defects in code~\cite{me07b}.
-Defect predictors have some level of generality:
-predictors learned at NASA~\cite{me07b} have also been found useful elsewhere
-(e.g. in Turkey~\cite{tosun10,tosun09}).
-The success of this method in  predictors in finding bugs is   markedly
-higher than other currently-used
-industrial
-methods such as manual code reviews. For example, 
-a  panel at {\em IEEE Metrics
-2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
-of defects.
-In another work, 
-Raffo documents the typical    defect detection capability of
-industrial review methods:   around 50\%
- for full Fagan inspections~\cite{fagan76} to
-21\% for less-structured inspections.
-
 Not only do static code defect predictors perform well compared to manual methods,

### 2016-04-26 tuningpredictor.tex
Updates from ShareLaTeX

@@
 Are the impacts of tuning addressed in the defect prediction literature?
-To answer that question,  in Jan 2016 we searched scholar.google.com for the conjunction of ``data mining" and ``software engineering" and  ``defect prediction"\footnote{More details can be found at https://goo.gl/Inl9nF}.
+To answer that question,  in Jan 2016 we searched scholar.google.com for the conjunction of ``data mining" and ``software engineering" and  ``defect prediction"
+(more details can be found at https://goo.gl/Inl9nF).
 After sorting by the citation count and discarding the non-SE papers (and those without a pdf link), we read over this sample
@@
 task explored by our optimizers.
-Note that this section repeats much of 
-our standard introduction to defect prediction~\cite{me15:book1},
-as well as presenting    some new results from Rahman et al.~\cite{rahman14:icse}.
-
-\input{dm101}
+
+Human programmers are clever, but flawed. Coding  adds functionality, but also defects.
+Hence, software sometimes crashes (perhaps at the most awkward or dangerous moment) or delivers
+the wrong functionality. For a very long list of software-related errors,
+see  Peter Neumann's ``Risk Digest'' at catless.ncl.ac.uk/Risks.
+
+Since programming inherently
+introduces defects into  programs, it is important to test them before they're used.
+Testing is expensive.
+Software assessment budgets are finite
+while assessment effectiveness increases 
+exponentially with assessment effort.
+For example, for  black-box testing methods,
+a {\em linear} increase
+in the confidence $C$ of finding  defects
+can take {\em exponentially} more effort:
+\bi
+\item
+A randomly selected 
+input to a program will find a fault with probability $p$.
+\item
+After $N$ random black-box tests, the chances of the inputs 
+not revealing any fault 
+is $(1-p)^N$. 
+\item
+Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
+which can be rearranged to 
+ $N(C,p)=log(1 -
+C)/log(1-p)$. 
+\item
+For example, $N(0.90,10^{-3})=2301$
+but $N(0.98,10^{-3})=3901$; i.e. nearly double the number of tests.
+\ei
+Exponential costs quickly exhaust finite resources so
+standard practice is to apply the best
+available  methods on code sections that seem   most critical. 
+But 
+any method that focuses on parts of the code
+can blind us to defects in other areas. Some  {\em
+lightweight sampling policy} should be used to explore the rest of the system.  This
+sampling policy will always be incomplete.
+Nevertheless, it is the only option when
+resources prevent a complete assessment of everything.
+
+One such lightweight sampling policy is defect predictors learned from static code attributes.
+Given software described in the attributes of \tab{ck},   data miners can
+learn where the probability of software defects is highest.
+
+The rest of this section argues that such defect predictors are   {\em easy to
+use}, {\em widely-used}, and {\em useful} to use.
+
+\begin{table*}[t]
+\renewcommand{\baselinestretch}{0.8}\begin{center}
+{\scriptsize
+\begin{tabular}{c|l|p{4.7in}}
+amc & average method complexity & e.g. number of JAVA byte codes\\\hline
+avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
+in class\\\hline
+ca & afferent couplings & how many other classes use the specific
+class. \\\hline
+cam & cohesion amongst classes & summation of number of different
+types of method parameters in every method divided by a multiplication
+of number of different method parameter types in whole class and
+number of methods. \\\hline
+cbm &coupling between methods &  total number of new/redefined methods
+to which all the inherited methods are coupled\\\hline
+cbo & coupling between objects & increased when the methods of one
+class access services of another.\\\hline
+ce & efferent couplings & how many other classes is used by the
+specific class. \\\hline
+dam & data access & ratio of the number of private (protected)
+attributes to the total number of attributes\\\hline
+dit & depth of inheritance tree &\\\hline
+ic & inheritance coupling &  number of parent classes to which a given
+class is coupled (includes counts of methods and variables inherited)
+\\\hline
+lcom & lack of cohesion in methods &number of pairs of methods that do
+not share a reference to an instance variable.\\\hline
+locm3 & another lack of cohesion measure & if $m,a$ are  the number of
+$methods,attributes$
+in a class number and $\mu(a)$  is the number of methods accessing an
+attribute, 
+then
+$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
+\\\hline
+loc & lines of code &\\\hline
+max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
+in class\\\hline
+mfa & functional abstraction & number of methods inherited by a class
+plus number of methods accessible by member methods of the
+class\\\hline
+moa &  aggregation &  count of the number of data declarations (class
+fields) whose types are user defined classes\\\hline
+noc &  number of children &\\\hline
+npm & number of public methods & \\\hline
+rfc & response for a class &number of  methods invoked in response to
+a message to the object.\\\hline
+wmc & weighted methods per class &\\\hline
+\rowcolor{lightgray}
+defect & defect & Boolean: where defects found in post-release bug-tracking systems.
+\end{tabular}
+}
+\end{center}
+\caption{OO measures used in our defect data sets.}\label{tab:ck}
+\end{table*}
+
+{\em Easy to use:} Static code attributes can be automatically collected, even for very large systems~\cite{nagappan05}.
+Other methods, like  manual code reviews, are far slower and far more labor-intensive.
+For example, depending on the review methods, 8 to 20 LOC/minute can be
+inspected and this effort repeats for all members of the review team,
+which can be as large as four or six people~\cite{me02f}. 
+{\em Widely used:}  Researchers and industrial practitioners  use static attributes to guide software 
+quality predictions.
+ Defect prediction models have been reported
+  at Google~\cite{lewis13}.
+Verification and validation (V\&V) textbooks
+\cite{rakitin01} advise using static code complexity attributes
+to decide which modules are worth manual inspections.
+
+{\em Useful:}
+Defect predictors often  find the location of  70\% (or more)
+of the defects in code~\cite{me07b}.
+Defect predictors have some level of generality:
+predictors learned at NASA~\cite{me07b} have also been found useful elsewhere
+(e.g. in Turkey~\cite{tosun10,tosun09}).
+The success of this method in  predictors in finding bugs is   markedly
+higher than other currently-used
+industrial
+methods such as manual code reviews. For example, 
+a  panel at {\em IEEE Metrics
+2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
+of defects.
+In another work, 
+Raffo documents the typical    defect detection capability of
+industrial review methods:   around 50\%
+ for full Fagan inspections~\cite{fagan76} to
+21\% for less-structured inspections.
+
+Not only do static code defect predictors perform well compared to manual methods,
+they also are competitive with certain automatic methods.
+A recent study at ICSE'14, Rahman et al.~\cite{rahman14:icse} compared
+(a) static code analysis tools FindBugs, Jlint, and Pmd and (b)
+static code defect predictors
+(which they called ``statistical defect prediction'') built using logistic regression.
+They found  no significant differences in the cost-effectiveness
+of these  approaches. Given this equivalence, it is significant to note that 
+static code defect prediction can be quickly adapted to new languages by building lightweight
+parsers that find   information like \tab{ck}. The same is not true for   static code analyzers-- these need  extensive modification before they can be used on new
+languages.
 
@@
 \end{equation}
+where $d_i$ is the number of observed issues and $T$
+is some threshold defined by an engineering judgement; we use $T=1$.
+
 The splitting process is controlled by numerous tuning parameters.
@@
 Note that WHERE builds {\em two} trees: the initial clustering tree (to find similar sets of data)
-then a final decision tree (to learn rules that predict for each similar cluster)\footnote{A
+then a final decision tree (to learn rules that predict for each similar cluster).
+A
 frequently asked question is why does WHERE build two trees--
 would not   a single tree suffice? The answer is, as shown below,  tuned WHERE's twin-tree approach 
-generates very precise predictors.}.
-The tuning parameter  {\em min\_sample\_ split } controls the construction of the
+generates very precise predictors.
+As to the rest of WHERE's parameters, the 
+ parameter  {\em min\_sample\_ split } controls the construction of the
 final decision tree (so, for WHERE-based learner,
@@
 CART finds the attributes whose ranges contain rows with least variance in the number
-of defects\footnote{If an attribute ranges $r_i$ is found in 
+of defects. If an attribute ranges $r_i$ is found in 
 $n_i$ rows each with a  defect count variance of $v_i$, then CART seeks the attributes
-whose ranges minimizes $\sum_i \left(\sqrt{v_i}\times n_i/(\sum_i n_i)\right)$.}.
+whose ranges minimizes $\sum_i \left(\sqrt{v_i}\times n_i/(\sum_i n_i)\right)$.
 \item
@@
 
-\input{algo}
+\begin{algorithm}[!t]
+
+\scriptsize
+\begin{algorithmic}[1]
+\Require $\mathit{np} = 10$, $f=0.75$, $cr=0.3$, $\mathit{life} = 5$, $\mathit{Goal} \in \{\mathit{pd},f,...\}$
+\Ensure $S_{best}$
+\vspace{2mm}
+\Function{DE}{$\mathit{np}$, $f$, $cr$, $\mathit{life}$, $\mathit{Goal}$}
+ \State $Population  \gets $ InitializePopulation($\mathit{np}$)   
+ \State $S_{best} \gets $GetBestSolution($Population $)
+ \While{$\mathit{life} > 0$}
+\State $NewGeneration \gets \emptyset$
+\For{$i=0 \to \mathit{np}-1$}
+\State $S_i \gets$ Extrapolate($Population [i], Population , cr, f$)
+\If {Score($S_i$) >Score($Population [i]$)}
+\State $NewGeneration$.append($S_i$)
+\Else
+\State $NewGeneration$.append($Population [i]$)
+\EndIf
+\EndFor
+\State $Population  \gets NewGeneration$
+\If{$\neg$ Improve($Population $)}
+\State $life -=1$
+\EndIf
+\State $S_{best} \gets$ GetBestSolution($Population $)
+ \EndWhile
+\State \Return $S_{best}$
+\EndFunction
+\Function{Score}{$Candidate$}
+   \State set tuned parameters according to $Candidate$
+   \State $model \gets$TrainLearner()
+   \State $result \gets$TestLearner($model$)   
+   \State \Return$\mathit{Goal}(result)$  
+\EndFunction
+\Function{Extrapolate}{$old, pop, cr, f$}
+  \State $a, b, c\gets threeOthers(pop,old)$  
+  \State $newf \gets \emptyset$
+  \For{$i=0 \to \mathit{np}-1$}
+       \If{$cr < random()$}
+         \State $newf$.append($old[i]$)
+                \Else
+                  \If{typeof($old[i]$) == bool}
+                    \State $newf$.append(not $old[i]$)
+         \Else
+          \State $newf$.append(trim($i$,($a[i] + f * (b[i] - c[i]$)))) 
+         \EndIf
+       \EndIf
+  \EndFor
+ \State \Return $newf$
+\EndFunction
+        \end{algorithmic} 
+\caption{Pseudocode for DE with Early Termination}
+\label{alg:DE}
+\end{algorithm}
 
@@
 
-Our defect data comes from the PROMISE repository \footnote{http://openscience.us/repo}
+Our defect data comes from the PROMISE repository (http://openscience.us/repo/defect)
 and pertains to 
@@
 that defect predictors based on simple 
-modeling techniques such as LR perform better than complicated techniques such as Random Forest\footnote{By three measures,
+modeling techniques such as LR perform better than ``complicated'' techniques such as Random Forest.
+To explain that comment, we note that
+by three measures,
 Random Forest
-is more complicated than LR. Firstly, LR builds one model
-while Random Forest builds many models. Secondly, LR is just
+is more complicated than LR:
+\be
+\item
+CART builds one model
+while Random Forest builds many models. 
+\item
+LR is just
 a model construction tool while Random Forest needs both
@@
 to  infer some conclusion from all the members of that forest.
-Thirdly, the LR model can be printed in a few lines while the multiple
+\item
+the LR model can be printed in a few lines while the multiple
 models learned by Random
-Forest model would take up multiple pages of output.}.
+Forest model would take up multiple pages of output.
+\ee
 \ee
@@
 
-%%%%time for prec %%%%%%
+\subsection{RQ5: Is Tuning Impractically Slow?}\label{sect:fast}
+
+%%%%evaluations for pre and F %%%%%%
+\begin{table}[!ht]
+\renewcommand{\baselinestretch}{0.75}
+\scriptsize
+\centering
+  \begin{tabular}{r|c c|c c|c c }
+    Datasets & \multicolumn{2}{c|}{Tuned\_Where}  & \multicolumn{2}{c|}{Tuned\_CART} &  \multicolumn{2}{c}{Tuned\_RanFst}  \\
+    \hline
+    & precision  & F  & precision  & F & precision  & F  \\
+    \hline
+    antV0 & 50  &50 & 60&50  &60&  70 \\
+    antV1 & 60  &60 &50& 50  &60&  60 \\
+    antV2 & 70  &90& 50&60  &60& 120 \\
+    camelV0 & 70  &50& 70 &80   &110&  70 \\
+    camelV1 & 60  &60&60&110   &70&  70\\
+    ivy & 60 &60&  60&60   &60&  60 \\
+    jeditV0 & 80  &80&80& 60   &90&  60 \\
+    jeditV1 & 60  &70&80&  70   &80& 70 \\
+    jeditV2 & 90  &80&60&70  &110&  80 \\
+    log4j & 50 &70& 50&50   &80&  50 \\
+    lucene & 80 &60& 70&60  &60&  70 \\
+    poiV0 & 60  &60& 70 &60  &130&  80 \\
+    poiV1 & 50 &50& 70 &50   &50&  110 \\
+    synapse & 70  &60&50&  60   &50&  90 \\
+    velocity & 60  &60&50& 60   &100&  60 \\
+    xercesV0 & 60  &80&80& 60   &70& 80 \\
+    xercesV1 & 80  &80&60& 60   &50&  80 \\
+  \end{tabular}
+  \caption{Number of evaluations for tuned learners, optimizing for precision and F-Measure.}
+\label{tab:eval}
+\end{table}
+
+%%%%runtime for prec and F %%%%%%
 \begin{table*}[!ht]
@@
 \centering
-  \begin{tabular}{r|c |c |c |c |c |c }
-    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
+  \begin{tabular}{r|c c|c c|c c|c c|c c|c c }
+    Datasets & \multicolumn{2}{c|}{Tuned\_Where} & \multicolumn{2}{c|}{Naive\_Where} & \multicolumn{2}{c|}{Tuned\_CART} & \multicolumn{2}{c|}{Naive\_CART} & \multicolumn{2}{c|}{Tuned\_RanFst} & \multicolumn{2}{c}{Naive\_RanFst}\\
     \hline
-    antV0 & 50 / 95.47 & 1.65 & 60 / 5.08 & 0.08 & 60 / 9.78 & 0.20\\
-    antV1 & 60 / 224.67 & 3.03 & 50 / 6.52 & 0.12 & 60 / 14.13 & 0.25\\
-    antV2 & 70 / 644.99 & 8.24 & 50 / 9.00 & 0.24 & 60 / 16.75 & 0.44\\
-    camelV0 & 70 / 690.62 & 7.93 & 70 / 12.68 & 0.24 & 110 / 28.49 & 0.34\\
-    camelV1 & 60 / 1596.77 & 23.56 & 60 / 17.13 & 0.27 & 70 / 33.96 & 0.77\\
-    ivy & 60 / 66.69 & 0.97 & 60 / 4.26 & 0.07 & 60 / 8.89 & 0.19\\
-    jeditV0 & 80 / 459.30 & 5.33 & 80 / 8.69 & 0.11 & 90 / 18.40 & 0.32\\
-    jeditV1 & 60 / 421.56 & 6.59 & 80 / 9.05 & 0.12 & 80 / 17.93 & 0.36\\
-    jeditV2 & 90 / 595.56 & 6.88 & 60 / 7.90 & 0.14 & 110 / 27.34 & 0.38\\
-    log4j & 50 / 76.09 & 1.33 & 50 / 2.60 & 0.06 & 80 / 9.69 & 0.15\\
-    lucene & 80 / 236.45 & 2.60 & 70 / 6.07 & 0.10 & 60 / 9.77 & 0.25\\
-    poiV0 & 60 / 263.12 & 3.92 & 70 / 7.42 & 0.09 & 130 / 25.86 & 0.28\\
-    poiV1 & 50 / 398.33 & 6.94 & 70 / 9.31 & 0.13 & 50 / 12.67 & 0.29\\
-    synapse & 70 / 144.09 & 1.85 & 50 / 3.88 & 0.07 & 50 / 8.13 & 0.19\\
-    velocity & 60 / 184.10 & 2.68 & 50 / 4.27 & 0.07 & 100 / 15.18 & 0.21\\
-    xercesV0 & 60 / 136.87 & 1.98 & 80 / 9.17 & 0.10 & 70 / 14.17 & 0.22\\
-    xercesV1 & 80 / 1173.92 & 12.78 & 60 / 10.47 & 0.16 & 50 / 18.27 & 0.40\\
+     & precision  & F    &  precision  & F  & precision  & F & precision  & F & precision  & F & precision  & F\\
+    \hline
+    antV0 & 95.47  &93.58  & 1.65 &1.39&  5.08 &3.52& 0.08 &0.08& 9.78 &9.89& 0.20 &0.17\\
+    antV1 & 224.67 &186.95 & 3.03 &3.18&  6.52 &6.18& 0.12 &0.12&  14.13 &13.39& 0.25 &0.25\\
+    antV2 & 644.99 &654.34 & 8.24 &8.08&  9.00 &8.79& 0.24 &0.18&  16.75 &27.56& 0.44&0.36\\
+    camelV0 & 690.62 & 543.28 & 7.93 &9.65&  12.68 &17.00& 0.24 &0.28&  28.49 &22.52& 0.34&0.41\\
+    camelV1 & 1596.77 & 1808.03 & 23.56 & 26.98 &  17.13 &31.92& 0.27 &0.28&  33.96 &37.00& 0.77&0.85\\
+    ivy & 66.69 & 74.50 & 0.97 &1.18 &  4.26 &4.72& 0.07 &0.08& 8.89 &10.39& 0.19&0.21\\
+    jeditV0 & 459.30&518.47 & 5.33 & 6.11 &  8.69 &7.9& 0.11 &0.10& 18.40 &14.32& 0.32&0.37\\
+    jeditV1 & 421.56&576.29 & 6.59 & 6.89 &  9.05 &8.13& 0.12 &0.10& 17.93 &17.42& 0.36&0.34\\
+    jeditV2 & 595.56&657.59 & 6.88 & 7.93 &  7.90 &10.34& 0.14 &0.15& 27.34 &20.20& 0.38&0.40\\
+    log4j & 76.09 &123.48 & 1.33 & 1.59 &  2.60 &2.92& 0.06 &0.08& 9.69 &7.67& 0.15&0.17\\
+    lucene & 236.45& 219.02& 2.60 & 3.68 &  6.07 &6.89 & 0.10 &0.12& 9.77 &13.06& 0.25&0.35\\
+    poiV0 & 263.12 &314.53 & 3.92 & 4.82 &  7.42 &7.80& 0.09 &0.10& 25.86 &19.29& 0.28&0.32\\
+    poiV1 & 398.33 & 446.05 & 6.94 & 7.55 &  9.31 &7.62& 0.13 &0.14& 12.67 &27.23& 0.29&0.36\\
+    synapse & 144.09 & 138.75 & 1.85 & 1.83 &  3.88 &4.87& 0.07 &0.08& 8.13 &13.29& 0.19&0.17\\
+    velocity & 184.10 &211.88 & 2.68 & 3.13 &  4.27 &5.51& 0.07 &0.10& 15.18 &11.58& 0.21&0.27\\
+    xercesV0 & 136.87 & 178.49 & 1.98 & 2.02 &  9.17 &7.47& 0.10 &0.11& 14.17 &17.31& 0.22&0.28\\
+    xercesV1 & 1173.92 & 1370.89 & 12.78 &14.42 &  10.47 &11.07 & 0.16 &0.19& 18.27 &25.27& 0.40&0.46\\
   \end{tabular}
-  \caption{Evaluations/runtime and runtime for tuned and default learners(in sec), optimizing for precision.}
-  \label{tab:etimes}
+  \caption{Runtime for tuned and default learners(in sec), optimizing for precision and F-Measure.}
+  \label{tab:runtime}
 \end{table*}
 
-%%%%time for F %%%%%%
-\begin{table*}[!ht]
-\renewcommand{\baselinestretch}{0.75}
-\scriptsize
-\centering
-  \begin{tabular}{r|c |c |c |c |c |c }
-    Datasets & Tuned\_Where & Naive\_Where & Tuned\_CART & Naive\_CART & Tuned\_RanFst & Naive\_RanFst\\
-    \hline
-    antV0 & 50 / 93.38 & 1.39 & 50 / 3.52 & 0.08 & 70 / 9.89 & 0.17\\
-    antV1 & 60 / 186.95 & 3.18 & 50 / 6.18 & 0.12 & 60 / 13.39 & 0.25\\
-    antV2 & 90 / 654.34 & 8.08 & 60 / 8.79 & 0.18 & 120 / 27.56 & 0.36\\
-    camel & 50 / 543.28 & 9.65 & 80 / 17.00 & 0.28 & 70 / 22.52 & 0.41\\
-    camelV1 & 60 / 1808.03 & 26.98 & 110 / 31.92 & 0.28 & 70 / 37.00 & 0.85\\
-    ivy & 60 / 74.50 & 1.18 & 60 / 4.72 & 0.08 & 60 / 10.39 & 0.21\\
-    jeditV0 & 80 / 518.47 & 6.11 & 60 / 7.9
- & 0.10 & 60 / 14.32 & 0.37\\
-    jeditV1 & 70 / 576.29 & 6.89 & 70 / 8.13 & 0.10 & 70 / 17.42 & 0.34\\
-    jeditV2 & 80 / 657.59 & 7.93 & 70 / 10.34 & 0.15 & 80 / 20.20 & 0.40\\
-    log4j & 70 / 123.48 & 1.59 & 50 / 2.92 & 0.08 & 50 / 7.67 & 0.17\\
-    lucene & 60 / 219.02 & 3.68 & 60 / 6.89 & 0.12 & 70 / 13.06 & 0.35\\
-    poiV0 & 60 / 314.53 & 4.82 & 60 / 7.80 & 0.10 & 80 / 19.29 & 0.32\\
-    poiV1 & 50 / 446.05 & 7.55 & 50 / 7.62 & 0.14 & 110 / 27.23 & 0.36\\
-    synapse & 60 / 138.75 & 1.83 & 60 / 4.87 & 0.08 & 90 / 13.29 & 0.17\\
-    velocity & 60 / 211.88 & 3.13 & 60 / 5.51 & 0.10 & 60 / 11.58 & 0.27\\
-    xercesV0 & 80 / 178.49 & 2.02 & 60 / 7.47 & 0.11 & 80 / 17.31 & 0.28\\
-    xercesV1 & 80 / 1370.89 & 14.42 & 60 / 11.07 & 0.19 & 80 / 25.27 & 0.46\\
-  \end{tabular}
-  \caption{Evaluations/runtime and runtime for tuned and default learners(in sec), optimizing for F-Measure.}
-\label{tab:ftimes}
-\end{table*}
-
-\subsection{RQ5: Is Tuning Impractically Slow?}\label{sect:fast}
-
-The number of evaluations/runtime used by our optimizers is shown in \tab{etimes}
-and \tab{ftimes}.
+The number of evaluations and runtime used by our optimizers are shown in \tab{eval}
+and \tab{runtime}.
 WHERE's runtime are slower than CART and Random Forest since WHERE has yet to benefit from decades
@@
 
-Looking over \tab{etimes} and \tab{ftimes}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
+Looking over \tab{eval}, the general pattern is that 50 to 80 evaluations suffice for finding the tuning
 improvements reported in this paper. 
@@
 take thousands, if not millions, of evaluations of candidate tunings. This turned out not
-to be that case.
+to be that case. By comparing the runtime of tuned and default learners shown in \tab{runtime}, we notice
+that the actual tuning time for most data sets is not extremely long.
 
@@
  In \fig{features}, we show how tuning selects the optimal values for tuned parameters.
-For space limitation, only four parameters from WHERE learner are selected as representatives and all the others can be found in our online support documents\footnote{\url{https://goo.gl/aHQKtU}}.
+For space limitation, only four parameters from WHERE learner are selected as representatives and all the others can be found in our online support documents (https://goo.gl/aHQKtU).
  Note that
@@
 
-\balance
+% \clearpage
+% \pagenumbering{roman}
+% \setcounter{page}{1} 
+% \section*{Reply to Reviews}
+
+% Thank your for your comments. The typos listed by reviewers
+% have been fixed and the remainder of the paper has been given
+% a careful proof read.
+
+% The reviewers raised certain issues which we respond  to as follows.
+
+% {\em I am concerned about the reproduction of work from elsewhere.
+Although the relevant paper and book are cited in section 2.3 ([27, 28]) the amount of material that is reproduced is surprisingly large.
+I am also unsure what "presenting some new results from Rahman et al.
+[28]" actually means.
+It would obviously be wrong to present other researchers' results as if newly discovered but I doubt that this is the intention.
+Indeed, on checking the other paper, there is no obvious overlap.
+This needs to be clarified.}
+
+% Apologies to the reviewer for our unclear text that suggests
+% that this paper inappropriately copied  content from
+% elsewhere. This is not the case since nearly all of this paper has not been submitted
+% or published to another venue. The exception to that is:
+% \bi
+% \item Section 2.3 and Table1 contains 1 page of tutorial material which we have adapted from other papers.
+% e.g. as the reviewer correctly points out,
+% the  'Easy to use' paragraph is taken nearly verbatim from [28], as are the 'widely-used', and 'useful' paragraphs.
+% \ei
+% Note that apart from Section 2.3,  10 of the 11 pages of this text are   completely new.
+
+% As to the reference to " presenting some new results from Rahman et al. [28]", that refers to one paragraph (120 words) end of section 2.3. 
+% Please note that we have removed the misleading text that raised that confusion
+% (start of 2.3).
+
+% {\em I think the way that the results are presented does not do justice to the findings in the abstract (that the improvements are large, and the tuning is simple).
+In particular, tables 8 and 9 are not very clear; why show the naive column?}
+
+% Thank for your that comment- we have simplified that presentation by separating the tuning \#evaluations from the runtimes-- see Table 8 and the new Table 9.
+
+% {\em I am distracted by the frequent use of footnotes.
+If the material is important and worthy of mention then it should be included in the main body of the paper.
+However, a reference to the relevant work may be sufficient and is sometimes preferable to using a footnote.}
+
+% Quite true- those footnotes are needlessly distracted.
+% They have now been incorporated into the text.
+
+% {\em  Eq 1 - what are d and T? - please use a where clause}
+
+% That where clause is now added after Equation 1. That clause says
+
+% \begin{quote} ... where  $d_i$ is the number of observed issues and $T$
+% is some threshold defined by an engineering judgement; we use $T=1$.\end{quote}
 

### 2016-04-26 gen_eps/plot_improvements_F_precision.m

@@ -1,40 +1,0 @@
-clf
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[-19.0, -19.0, -11.0, -7.0, -6.0, 0.0, 0.0, 1.0, 1.0, 2.0, 2.0, 3.0, 4.0, 4.0, 7.0, 73.0, 91.0], '-r*')
-hold on
-plot(x,[-17.0, -1.0, 1.0, 2.0, 2.0, 4.0, 4.0, 4.0, 6.0, 8.0, 9.0, 11.0, 15.0, 18.0, 19.0, 29.0, 57.0],'-b+')
-hold on
-plot(x,[-20.0, -12.0, -10.0, -4.0, -4.0, -1.0, -1.0, 0.0, 1.0, 5.0, 6.0, 6.0, 15.0, 18.0, 22.0, 27.0, 59.0], '-gx')
-axis([1 17 -100 100])
-legend('WHERE','CART','R.Forest','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-set(gca, 'YTick',[-50,0,50,100])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('F')
-legend('boxoff')
-xlabel('data sets, sorted')
-
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[-30.0, -26.0, -25.0, 0.0, 0.0, 0.0, 6.0, 9.0, 13.0, 15.0, 42.0, 59.0, 59.0, 63.0, 72.0, 73.0, 96.0], '-r*')
-hold on
-plot(x,[-23.0, -4.0, 3.0, 3.0, 4.0, 5.0, 8.0, 8.0, 12.0, 15.0, 16.0, 29.0, 33.0, 34.0, 38.0, 59.0, 62.0],'-b+')
-hold on
-plot(x,[-23.0, -1.0, 0.0, 1.0, 1.0, 5.0, 6.0, 6.0, 8.0, 9.0, 10.0, 18.0, 28.0, 33.0, 35.0, 36.0, 61.0], '-gx')
-axis([1 17 -100 100])
-legend('WHERE','CART','R.Forest','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-set(gca, 'YTick',[-50,0,50,100])
[…]

### 2016-04-26 gen_eps/plot_logistic_others.m

@@ -1,40 +1,0 @@
-clf
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[8,13,24,33,41,42,46,56,59,64,65,77,78,83,85,87,100], '-r*')
-hold on
-% plot(x,[3,14,17,34,36,24,28,26,49,27,52,71,67,49,79,73,97],'-b+')
-% hold on
-plot(x,[5,15,16,34,41,25,28,50,44,28,64,65,67,49,77,82,99], '-gx')
-axis([1 17 0 100])
-legend('Logistic Regression','Untuned R.Forest','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-% set(gca, 'YTick',[0,50,100])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('Precision')
-legend('boxoff')
-xlabel('data sets, sorted')
-
-FigHandle = figure('Position', [220, 300, 200, 400]);
-% plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[8,13,24,33,41,42,46,56,59,64,65,77,78,83,85,87,100], '-r*')
-hold on
-% plot(x,[18,47,25,39,74,83,62,34,61,89,56,100,70,26,75,89,100],'-b+')
-% hold on
-plot(x,[5,14,21,42,74,31,37,78,50,89,100,100,77,26,78,100,100], '-gx')
-axis([1 17 0 100])
-legend('Logistic Regression','Tuned R.Forest','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-% set(gca, 'YTick',[-50,0,50,100])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('Precision')
-legend('boxoff')
-xlabel('data sets, sorted')

### 2016-04-26 gen_eps/plot_np_10_90.m

@@ -1,40 +1,0 @@
-clf
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[-90, -48, -18, -4, -1, -1, 0, 0, 0, 2, 2, 4, 35, 74, 77, 80, 92], '-r*')
-hold on
-plot(x,[-46,-6,-5,-1,0,0,0,0,0,1,2,2,2,3,4,11,62],'-b+')
-hold on
-plot(x,[-55,-21,-5,-3,-3,-2,0,0,0,0,0,1,1,1,2,3,9], '-gx')
-axis([1 17 -100 100])
-legend('WHERE','CART','R.Forest','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-set(gca, 'YTick',[-50,0,50,100])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('F')
-legend('boxoff')
-xlabel('data sets, sorted')
-
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[-40,-38,-25,-24,-5,-2,0,0,0,0,0,0,0,0,0,27,74], '-r*')
-hold on
-plot(x,[-44,-42,-12,-2,-1,0,0,0,2,2,3,3,13,24,25,29,74],'-b+')
-hold on
-plot(x,[-24,-11,-4,-3,-1,-1,0,0,0,0,0,0,1,3,3,10,74], '-gx')
-axis([1 17 -100 100])
-legend('WHERE','CART','R.Forest','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-set(gca, 'YTick',[-50,0,50,100])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('Precision')
-legend('boxoff')
-xlabel('data sets, sorted')

### 2016-04-26 gen_eps/plot_svm.m

@@ -1,44 +1,0 @@
-clf
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[93,27,82,94,0,5,37,23,98,51,83,71,0,3,0,0,5], '-r*')
-hold on
-plot(x,[31,2,81,94,0,56,38,24,99,52,85,75,28,41,50,72,78],'-b+')
-hold on
-plot(x,[-62,-24,-1,0,0,0,1,1,1,1,2,4,28,38,50,72,73], '-gx')
-hold on
-% plot(x,[0.01, 0.01, 0.19, 0.19, 0.26, 0.26, 0.52, 0.52, 0.55, 0.6, 0.6, 0.6, 0.6, 0.6, 0.6, 0.83, 0.83],'-ks')
-axis([1 17 -60 120])
-legend('Naive\_rbf','Tuned\_rbf','Improvements','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-set(gca, 'YTick',[-60,-40,-20,0,20,40,60,80,100])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('F')
-legend('boxoff')
-xlabel('17 experiments, sorted')
-
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[20,78,51,0,0,0,0,0,0,0,0,0,0,0,0,0,0], '-r*')
-hold on
-plot(x,[20,78,51,4,20,23,26,28,33,36,40,42,50,75,78,85,96],'-b+')
-hold on
-plot(x,[0,0,0,4,20,23,26,28,33,36,40,42,50,75,78,85,96], '-gx')
-hold on
-% plot(x,[0.01, 0.01, 0.19, 0.19, 0.26, 0.26, 0.52, 0.52, 0.55, 0.6, 0.6, 0.6, 0.6, 0.6, 0.6, 0.83, 0.83],'-ks')
-axis([1 17 -60 120])
-legend('Naive\_sigmoid','Tuned\_sigmoid','Improvements','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-set(gca, 'YTick',[-60,-40,-20,0,20,40,60,80,100])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('F')
-legend('boxoff')
-xlabel('17 experiments, sorted')

### 2016-04-26 gen_eps/plot_where_features_range.m

@@ -1,43 +1,0 @@
-clf
- FigHandle = figure('Position', [220, 300, 200, 400]);
-%plot([1:17],[0:0])
-x = [1:17]
-box on 
-hold on
-plot(x,[0.24, 0.43, 0.59, 0.64, 0.87, 0.98, 0.98, 0.98, 0.98, 0.98, 0.98, 0.98, 1, 1, 1, 1, 1], '-r*')
-hold on
-plot(x,[0.01, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.3, 0.41, 0.43, 0.45, 0.54, 0.54, 0.68, 0.71, 0.84, 1],'-b+')
-hold on
-plot(x,[0.13, 0.22, 0.27, 0.38, 0.46, 0.46, 0.47, 0.48, 0.51, 0.51, 0.51, 0.51, 0.51, 0.59, 0.66, 0.66, 0.77], '-gx')
-hold on
-plot(x,[0.01, 0.01, 0.19, 0.19, 0.26, 0.26, 0.52, 0.52, 0.55, 0.6, 0.6, 0.6, 0.6, 0.6, 0.6, 0.83, 0.83],'-ks')
-axis([1 17 -0.5 1.2])
-legend('threshold','infoPrune','min\_{Size}','wriggle','Location','South')
-set(gca,'XTick', [1,4,8,12,17])
-set(gca, 'YTick',[0,0.2,0.33,0.5,1])
-hline = refline([0 0]);
-set(hline,'Color','k')
-title('Precision')
-legend('boxoff')
-xlabel('data sets, sorted')
-
- FigHandle = figure('Position', [220, 300, 200, 400]);
-x = [1:17]
-box on 
-hold on
-plot(x,[0.04, 0.04, 0.24, 0.44, 0.44, 0.44, 0.44, 0.44, 0.65, 0.65, 0.77, 0.77, 0.77, 0.87, 0.98, 0.98, 1], '-r*')
-hold on
-plot(x,[0.01, 0.07, 0.12, 0.14, 0.14, 0.31, 0.47, 0.48, 0.51, 0.51, 0.54, 0.57, 0.68, 0.68, 0.68, 0.68, 0.88],'-b+')
-hold on
-plot(x,[0.18, 0.18, 0.4, 0.4, 0.4, 0.4, 0.46, 0.51, 0.51, 0.56, 0.59, 0.62, 0.65, 0.66, 0.77, 0.8, 0.97], '-gx')
-hold on
[…]
